### 2020-04-30 LaTeX/sections/abstract.tex
New code (static array) + test cases

% !TEX root = ../main.tex

\begin{abstract}

Abstract goes here

\end{abstract}

### 2020-04-30 LaTeX/sections/paper.tex
New code (static array) + test cases

% !TEX root = ../main.tex

\section{Introductory Remarks}

% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =

\section{Related Work}

% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
%Mahsa
%Notes related to design and implementations

% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =

\section{Concluding Remarks}

%\subsubsection*{Acknowledgements.} J. Clark thanks ...

### 2020-04-30 Code/Truffle/migrations/10_deploy_Orderbook_V21.js

@@ -1,29 +1,0 @@
-var Orderbook_V21 = artifacts.require("./Orderbook_V21.sol"); 
-//const BN = require('bn.js');
-
-
-// module.exports = async function(deployer) {
-//     deployer.deploy(modularExp).then(() => {
-//         return deployer.deploy(modularExp);
-//     }).then(async () => {
-//         //var modularExp = await modularExp.deployed();
-//         await modularExp.js_call();       
-//     });      
-//     };
-
-module.exports = function (deployer) {
-    deployer.deploy(Orderbook_V21);
-    //Orderbook_V8Instance = await Orderbook_V8.deployed();
-    console.log("I was deployed!");
-    //HelloInstance.show_result().on('data', event => console.log(event));
-
-    //var output = await app.toy();
-    //console.log("This is the output:", output);
-    //console.log("-------------")
-    //console.log(output.logs[0])
-    //var a = new BN(output.logs[0]);
-    //event show_result(bytes byteValue, bool boolValue, uint uintValue);
-    //console.log("output is:", a);
-
-
-};

### 2020-04-30 Code/Truffle/migrations/12_deploy_Orderbook_V23.js

@@ -1,4 +1,4 @@
-var Orderbook_V22 = artifacts.require("./Orderbook_V22.sol"); 
+var Orderbook_V23 = artifacts.require("./Orderbook_V23.sol"); 
 //const BN = require('bn.js');
 
 
@@ -12,7 +12,7 @@ var Orderbook_V22 = artifacts.require("./Orderbook_V22.sol");
 //     };
 
 module.exports = function (deployer) {
-    deployer.deploy(Orderbook_V22);
+    deployer.deploy(Orderbook_V23, 5);
     //Orderbook_V8Instance = await Orderbook_V8.deployed();
     console.log("I was deployed!");
     //HelloInstance.show_result().on('data', event => console.log(event));

### 2020-04-30 Code/Truffle/migrations/3_deploy_Orderbook_V9.js

@@ -1,29 +1,0 @@
-var Orderbook_V9 = artifacts.require("./Orderbook_V9.sol"); //Hello is the name of the contract
-//const BN = require('bn.js');
-
-
-// module.exports = async function(deployer) {
-//     deployer.deploy(modularExp).then(() => {
-//         return deployer.deploy(modularExp);
-//     }).then(async () => {
-//         //var modularExp = await modularExp.deployed();
-//         await modularExp.js_call();       
-//     });      
-//     };
-
-module.exports = function (deployer) {
-    deployer.deploy(Orderbook_V9);
-    //Orderbook_V8Instance = await Orderbook_V8.deployed();
-    console.log("I was deployed!");
-    //HelloInstance.show_result().on('data', event => console.log(event));
-
-    //var output = await HelloInstance.js_call();
-    //console.log("This is the output:", output);
-    //console.log("-------------")
-    //console.log(output.logs[0])
-    //var a = new BN(output.logs[0]);
-    //event show_result(bytes byteValue, bool boolValue, uint uintValue);
-    //console.log("output is:", a);
-
-
-};

### 2020-04-30 Code/Truffle/migrations/4_deploy_Orderbook_V10.js

@@ -1,29 +1,0 @@
-var Orderbook_V10 = artifacts.require("./Orderbook_V10.sol"); 
-//const BN = require('bn.js');
-
-
-// module.exports = async function(deployer) {
-//     deployer.deploy(modularExp).then(() => {
-//         return deployer.deploy(modularExp);
-//     }).then(async () => {
-//         //var modularExp = await modularExp.deployed();
-//         await modularExp.js_call();       
-//     });      
-//     };
-
-module.exports = function (deployer) {
-    deployer.deploy(Orderbook_V10);
-    //Orderbook_V8Instance = await Orderbook_V8.deployed();
-    console.log("I was deployed!");
-    //HelloInstance.show_result().on('data', event => console.log(event));
-
-    //var output = await app.toy();
-    //console.log("This is the output:", output);
-    //console.log("-------------")
-    //console.log(output.logs[0])
-    //var a = new BN(output.logs[0]);
-    //event show_result(bytes byteValue, bool boolValue, uint uintValue);
-    //console.log("output is:", a);
-
-
-};

### 2020-04-30 Code/Truffle/migrations/5_deploy_Orderbook_V11.js

@@ -1,29 +1,0 @@
-var Orderbook_V11 = artifacts.require("./Orderbook_V11.sol"); 
-//const BN = require('bn.js');
-
-
-// module.exports = async function(deployer) {
-//     deployer.deploy(modularExp).then(() => {
-//         return deployer.deploy(modularExp);
-//     }).then(async () => {
-//         //var modularExp = await modularExp.deployed();
-//         await modularExp.js_call();       
-//     });      
-//     };
-
-module.exports = function (deployer) {
-    deployer.deploy(Orderbook_V11);
-    //Orderbook_V8Instance = await Orderbook_V8.deployed();
-    console.log("I was deployed!");
-    //HelloInstance.show_result().on('data', event => console.log(event));
-
-    //var output = await app.toy();
-    //console.log("This is the output:", output);
-    //console.log("-------------")
-    //console.log(output.logs[0])
-    //var a = new BN(output.logs[0]);
-    //event show_result(bytes byteValue, bool boolValue, uint uintValue);
-    //console.log("output is:", a);
-
-
-};

### 2020-04-30 Code/Truffle/migrations/7_deploy_Contcatenation.js

@@ -1,29 +1,0 @@
-var Contcatenation = artifacts.require("./Contcatenation.sol"); 
-//const BN = require('bn.js');
-
-
-// module.exports = async function(deployer) {
-//     deployer.deploy(modularExp).then(() => {
-//         return deployer.deploy(modularExp);
-//     }).then(async () => {
-//         //var modularExp = await modularExp.deployed();
-//         await modularExp.js_call();       
-//     });      
-//     };
-
-module.exports = function (deployer) {
-    deployer.deploy(Contcatenation);
-    //Orderbook_V8Instance = await Orderbook_V8.deployed();
-    console.log("I was deployed!");
-    //HelloInstance.show_result().on('data', event => console.log(event));
-
-    //var output = await app.toy();
-    //console.log("This is the output:", output);
-    //console.log("-------------")
-    //console.log(output.logs[0])
-    //var a = new BN(output.logs[0]);
-    //event show_result(bytes byteValue, bool boolValue, uint uintValue);
-    //console.log("output is:", a);
-
-
-};

### 2020-04-30 Code/Truffle/migrations/8_deploy_Orderbook_V12.js

@@ -1,29 +1,0 @@
-var Orderbook_V12 = artifacts.require("./Orderbook_V12.sol"); 
-//const BN = require('bn.js');
-
-
-// module.exports = async function(deployer) {
-//     deployer.deploy(modularExp).then(() => {
-//         return deployer.deploy(modularExp);
-//     }).then(async () => {
-//         //var modularExp = await modularExp.deployed();
-//         await modularExp.js_call();       
-//     });      
-//     };
-
-module.exports = function (deployer) {
-    deployer.deploy(Orderbook_V12);
-    //Orderbook_V8Instance = await Orderbook_V8.deployed();
-    console.log("I was deployed!");
-    //HelloInstance.show_result().on('data', event => console.log(event));
-
-    //var output = await app.toy();
-    //console.log("This is the output:", output);
-    //console.log("-------------")
-    //console.log(output.logs[0])
-    //var a = new BN(output.logs[0]);
-    //event show_result(bytes byteValue, bool boolValue, uint uintValue);
-    //console.log("output is:", a);
-
-
-};

### 2020-04-30 Code/Truffle/migrations/9_deploy_Orderbook_V20.js

@@ -1,29 +1,0 @@
-var Orderbook_V20 = artifacts.require("./Orderbook_V20.sol"); 
-//const BN = require('bn.js');
-
-
-// module.exports = async function(deployer) {
-//     deployer.deploy(modularExp).then(() => {
-//         return deployer.deploy(modularExp);
-//     }).then(async () => {
-//         //var modularExp = await modularExp.deployed();
-//         await modularExp.js_call();       
-//     });      
-//     };
-
-module.exports = function (deployer) {
-    deployer.deploy(Orderbook_V20);
-    //Orderbook_V8Instance = await Orderbook_V8.deployed();
-    console.log("I was deployed!");
-    //HelloInstance.show_result().on('data', event => console.log(event));
-
-    //var output = await app.toy();
-    //console.log("This is the output:", output);
-    //console.log("-------------")
-    //console.log(output.logs[0])
-    //var a = new BN(output.logs[0]);
-    //event show_result(bytes byteValue, bool boolValue, uint uintValue);
-    //console.log("output is:", a);
-
-
-};

### 2020-04-30 Code/Truffle/test/1_DappToken_test.js

@@ -30,7 +30,7 @@ contract('DappToken', function(accounts) {
     //      console.log(DappTokenInstance.address);
     //  });
     //*******************Test 2*************************
-    // it('should return the balance of the accounts[0], async()=>{
+    // it('should return the balance of the accounts[0]', async()=>{
     //     const DappTokenInstance = await DappToken.deployed();
     //     const result =  await DappTokenInstance.balanceOf(accounts[0]);
     //     console.log(result.toNumber());
@@ -117,7 +117,7 @@ describe('Orderbook', function(accounts) {
     //     //console.log(state.toString());
         
          accounts = await web3.eth.getAccounts();
-         for(let j = 1; j < 101 ; j++) 
+         for(let j = 1; j < 31 ; j++) 
              await OrderbookInstance.submitAsk (j, 1, {from: accounts[0]});
          
          //await OrderbookInstance.submitAsk (10, 1, {from: accounts[0]});
@@ -162,7 +162,7 @@ describe('Orderbook', function(accounts) {
         const OrderbookInstance = await Orderbook.deployed(); 
        
         accounts = await web3.eth.getAccounts();
-        for(let j = 1; j < 101 ; j++) 
+        for(let j = 1; j < 31 ; j++) 
             await OrderbookInstance.submitBid (j, 1, {from: accounts[1]});
         
         
@@ -196,7 +196,7 @@ describe('Orderbook', function(accounts) {
         const state =  await OrderbookInstance.getState();
         console.log('Market is currently:',state.toString());
         
-        await OrderbookInstance.MatchOrders();
+        //await OrderbookInstance.MatchOrders();
         
         const result = await OrderbookInstance.BuyListPeak.call();
         const {0: addsender, 1: intprice, 2: auxprice, 2: intvolume} = result;

### 2020-04-30 Code/Truffle/test/2_MatchGasCost_test.js

@@ -1,0 +1,306 @@
+const DappToken = artifacts.require('DappToken');
+const Orderbook = artifacts.require('Orderbook_V23');
+var Orderbookaddress;
+var tokenaddress;
+var accounts;
+
+
+// Obtain gas used from the receipt
+//const receipt = await DappTokenInstance.transfer (accounts[1], 1, {from: accounts[0]});
+//const gasUsed = receipt.receipt.gasUsed;
+//console.log(`GasUsed for transfering: ${receipt.receipt.gasUsed}`);
+
+
+contract('Orderbook', function(accounts) {
+    it('should store the address of the orderbook into the var orderbookaddress', async() => {
+        const OrderbookInstance = await Orderbook.deployed(); 
+        Orderbookaddress = OrderbookInstance.address;
+        console.log('The address of the orderbook contract is:', OrderbookInstance.address);
+        
+    });
+
+
+
+
+});
+
+
+
+
+contract('DappToken', function(accounts) {
+
+    it('should approve transfer of 100 tokens from account[0] to the orderbook contract ', async ()=> {
+        const DappTokenInstance = await DappToken.deployed();
+        tokenaddress = DappTokenInstance.address;
+        const receipt = await DappTokenInstance.approve (Orderbookaddress, 100, {from: accounts[0]});
+        const result = await DappTokenInstance.allowance(accounts[0],Orderbookaddress);
+        console.log('Account[0] allowes the orderbook contract to spend:',result.toNumber());
+        
+        console.log('********************************************');
+        const gasUsed = receipt.receipt.gasUsed;
+        console.log(`GasUsed for approving: ${receipt.receipt.gasUsed}`);
+    
+    });   
+
+});
+
+//*******************New test Block for the already deployed orderbook contract *************************
+describe('Orderbook', function(accounts) {
+    this.timeout(0);
+    
+    //*******************Test 1*************************
+    it('should deposit 100 tokens from accounst[0] to the orderbook contract', async() => {
+        
+        const OrderbookInstance = await Orderbook.deployed(); 
+
+        accounts = await web3.eth.getAccounts();
+       
+        const receipt = await OrderbookInstance.DepositToken (tokenaddress, 100, {from: accounts[0]});
+        
+        const totalbalance = await OrderbookInstance.TotalTokenBalance(accounts[0], tokenaddress);
+        const availablebalance = await OrderbookInstance.AvailableTokenBalance(accounts[0], tokenaddress);
+        
[…]

### 2020-05-04 LaTeX/sections/paper.tex
Updates: Code, testcase, cost table (using static arrays)

@@
 
+%============= Ghazal with Auction Costs Table==================== %
+\begin{table}[t]
+\centering
+\begin{tabular}{|c|c|c|c|}
+\hline
+\textbf{\shortstack{Number \\of \\Buy Orders}} & \textbf{\shortstack{Number \\of \\Sell Orders}} & \textbf{\shortstack{Total Number \\of\\ Orders}}  & \textbf{\shortstack{Gas Cost \\in\\ Ether}}  \\ \hline
+1 & 1 & 2 & 144,689 \\
+3 & 3 & 6 & 324,457 \\
+5 & 5 & 10 & 527,289 \\
+7 & 7 & 14 & 710,050 \\
+9 & 9 & 18 & 964,894 \\
+11 & 11 & 22 & 1,176,905 \\
+13 & 13 & 26 & 1,370,191 \\
+15 & 15 & 30 & 1,650,273 \\
+17 & 17 & 34 & 1,953,406 \\
+19 & 19 & 38 & 2,205,141 \\
+21 & 21 & 42 & 2,416,221 \\
+23 & 23 & 46 & 2,713,313 \\
+25 & 25 & 50 & 1,788,509 \\
+27 & 27 & 54 & 2,004,824 \\
+
+\hline
+29 & 29 & 58 & \textbf{out of gas}\\
+\hline
+\end{tabular}
+\caption{\footnotesize{Gas used for Match function when using fixed arrays to store the heap.}\label{}}
+\end{table}
+%======================================== %
 % = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =

### 2020-05-04 Code/Truffle/migrations/12_deploy_Orderbook_V23.js

@@ -12,7 +12,7 @@ var Orderbook_V23 = artifacts.require("./Orderbook_V23.sol");
 //     };
 
 module.exports = function (deployer) {
-    deployer.deploy(Orderbook_V23, 5);
+    deployer.deploy(Orderbook_V23, 58);
     //Orderbook_V8Instance = await Orderbook_V8.deployed();
     console.log("I was deployed!");
     //HelloInstance.show_result().on('data', event => console.log(event));

### 2020-05-04 Code/Truffle/test/2_OrderBook_V23_test.js

@@ -67,8 +67,6 @@ describe('Orderbook', function(accounts) {
         const gasUsed = receipt.receipt.gasUsed;
         console.log(`GasUsed for depositting 100 tokens: ${receipt.receipt.gasUsed}`);
 
-
-
     });
 
     //*******************Test 2*************************
@@ -110,7 +108,7 @@ describe('Orderbook', function(accounts) {
         
 
         accounts = await web3.eth.getAccounts();
-        for(let j = 1; j <= 2  ; j++){
+        for(let j = 1; j <= 29  ; j++){
             receipt = await OrderbookInstance.submitAsk (j, 1, {from: accounts[0]});
         
             const gasUsed = receipt.receipt.gasUsed;
@@ -166,11 +164,12 @@ describe('Orderbook', function(accounts) {
         const OrderbookInstance = await Orderbook.deployed(); 
        
         accounts = await web3.eth.getAccounts();
-        for(let j = 1; j <= 3 ; j++) 
+        for(let j = 1; j <= 29 ; j++){
             await OrderbookInstance.submitBid (j, 1, {from: accounts[1]});
+        } 
         
         
-   });
+    });
    //*******************Test 9*************************
     it('should return the BuyList peak', async() => {
         const OrderbookInstance = await Orderbook.deployed(); 
@@ -238,11 +237,23 @@ describe('Orderbook', function(accounts) {
         const state =  await OrderbookInstance.getState();
         console.log('Market is currently:',state.toString());
         
-        await OrderbookInstance.MatchOrders();
+        const receipt = await OrderbookInstance.MatchOrders();
         
         const result = await OrderbookInstance.BuyListPeak.call();
         const {0: addsender, 1: intprice, 2: auxprice, 2: intvolume} = result;
         console.log('The Buylist peak after matching orders is:', intprice);
+
+
+        console.log('********************************************');
+        const gasUsed = receipt.receipt.gasUsed;
+        console.log(`GasUsed for Matching: ${receipt.receipt.gasUsed}`);
+        
+        //const contract = new web3.eth.Contract(OrderbookInstance.abi, OrderbookInstance.address);
+
+        //Now get evens depending on what you need
+        //contract.getPastEvents("allEvents", {fromBlock: 0, toBlock: "latest"}) .then(console.log) ;
+
+    
     
     });
 
@@ -293,6 +304,39 @@ describe('Orderbook', function(accounts) {
         console.log('The BuyIndex after match is:', buyindex.toNumber());
 
     });
+
[…]

### 2020-05-11 LaTeX/sections/paper.tex
Gas cost tables (fixed and dynamic arrays)

@@
 %============= Ghazal with Auction Costs Table==================== %
+\begin{table}[t]
+\centering
+\begin{tabular}{|c|c|c|c|}
+\hline
+\textbf{\shortstack{Number \\of \\Buy Orders}} & \textbf{\shortstack{Number \\of \\Sell Orders}} & \textbf{\shortstack{Total Number \\of\\ Orders}}  & \textbf{\shortstack{Gas Cost \\in\\ Ether}}  \\ \hline
+1 & 1 & 2 & 127,959 \\
+3 & 3 & 6 &  274,265\\
+5 & 5 & 10 & 449,684 \\
+7 & 7 & 14 & 603,057 \\
+9 & 9 & 18 & 817,224 \\
+11 & 11 & 22 & 982,549 \\
+13 & 13 & 26 & 1,210,410 \\
+15 & 15 & 30 &  1,403,040\\
+17 & 17 & 34 &  1,609,720\\
+19 & 19 & 38 & 1,862,796 \\
+21 & 21 & 42 & 2,057,234 \\
+23 & 23 & 46 &  2,266,225\\
+\hline
+25 & 25 & 50 & \textbf{out of gas} \\
+
+\hline
+
+\end{tabular}
+\caption{\footnotesize{Gas used for Match function when using dynamic arrays to store the heap.}\label{}} %Orderbook_V22
+\end{table}
+
 \begin{table}[t]
@@
 \end{tabular}
-\caption{\footnotesize{Gas used for Match function when using fixed arrays to store the heap.}\label{}}
+\caption{\footnotesize{Gas used for Match function when using static arrays to store the heap.}\label{}} %Orderbook_V23
 \end{table}

### 2020-05-11 Code/Truffle/test/3_OrderBook_V23_test.js

@@ -108,7 +108,7 @@ describe('Orderbook', function(accounts) {
         
 
         accounts = await web3.eth.getAccounts();
-        for(let j = 1; j <= 29  ; j++){
+        for(let j = 1; j <= 1  ; j++){
             receipt = await OrderbookInstance.submitAsk (j, 1, {from: accounts[0]});
         
             const gasUsed = receipt.receipt.gasUsed;
@@ -164,7 +164,7 @@ describe('Orderbook', function(accounts) {
         const OrderbookInstance = await Orderbook.deployed(); 
        
         accounts = await web3.eth.getAccounts();
-        for(let j = 1; j <= 29 ; j++){
+        for(let j = 1; j <= 1 ; j++){
             await OrderbookInstance.submitBid (j, 1, {from: accounts[1]});
         } 
         

### 2020-05-12 LaTeX/sections/paper.tex
New code with mapping + three gas cost comaprison table

@@
 25 & 25 & 50 & \textbf{out of gas} \\
-
 \hline
@@
 27 & 27 & 54 & 2,004,824 \\
-
 \hline
@@
 \end{table}
+
+\begin{table}[t]
+\centering
+\begin{tabular}{|c|c|c|c|}
+\hline
+\textbf{\shortstack{Number \\of \\Buy Orders}} & \textbf{\shortstack{Number \\of \\Sell Orders}} & \textbf{\shortstack{Total Number \\of\\ Orders}}  & \textbf{\shortstack{Gas Cost \\in\\ Ether}}  \\ \hline
+1 & 1 & 2 & 177,622 \\
+3 & 3 & 6 &  341,393\\
+5 & 5 & 10 & 524,680 \\
+7 & 7 & 14 & 685,830\\
+9 & 9 & 18 & 919,636 \\
+11 & 11 & 22 & 1,094,503  \\
+13 & 13 & 26 & 1,347,199 \\
+15 & 15 & 30 & 1,559,796 \\
+17 & 17 & 34 & 1,792,040 \\
+19 & 19 & 38 & 2,076,422 \\
+21 & 21 & 42 & 2,294,229 \\
+23 & 23 & 46 & 2,532,674 \\
+25 & 25 & 50 & 2,776,988 \\
+27 & 27 & 54 & 3,069,163 \\
+29 & 29 & 58 & 3,306,749\\
+31 & 31 & 62 & 3,551,195\\
+\hline
+33 & 33 & 66 & \textbf{out of gas} \\
+\hline
+\end{tabular}
+\caption{\footnotesize{Gas used for Match function when storing the order structs in mappings and storing the keys in the dynamic arrays that represent sorted heap.}\label{}} %Orderbook_V24
+\end{table}
+
 %======================================== %

### 2020-06-06 Code/Truffle/test/10_Orderbook_V25_test.js
Updated linkedlist + tescases

@@ -1,0 +1,91 @@
+const DappToken = artifacts.require('DappToken');
+const Orderbook = artifacts.require('Orderbook_V25');
+var Orderbookaddress;
+var tokenaddress;
+var accounts;
+
+contract('Orderbook', function(accounts) {
+    
+    //*******************Test 1*************************
+    it('should submit 1 asks from accounst[0]', async() => {
+        const OrderbookInstance = await Orderbook.deployed(); 
+        var receipt = null;
+        var array = [];
+        
+
+        accounts = await web3.eth.getAccounts();
+        for(let j = 1; j <= 100  ; j++){
+            receipt = await OrderbookInstance.submitAsk (j, 1, {from: accounts[0]});
+        
+            const gasUsed = receipt.receipt.gasUsed;
+            array.push(gasUsed);
+            console.log(`GasUsed for a submitask tx is: ${receipt.receipt.gasUsed}`);
+
+        } 
+        
+        // Getting sum of numbers
+        // var sum = array.reduce(function(a, b){
+        //     return a + b;
+        // }, 0);
+
+        console.log(array.length,'asks has been succsessfully submitted');
+        console.log('Gas used for submitting the', array.length,'th ask is:');
+        console.log(`${receipt.receipt.gasUsed}`);
+        console.log('********************************************');
+
+        
+   });
+//*******************Test 2*************************
+
+   it('should submit 1 Bids from accounst[1]', async() => {
+    const OrderbookInstance = await Orderbook.deployed(); 
+    var receipt = null;
+    var array = [];
+   
+    accounts = await web3.eth.getAccounts();
+    for(let j = 1; j <= 100 ; j++){
+
+        receipt = await OrderbookInstance.submitBid (j, 1, {from: accounts[1]});
+
+        const gasUsed = receipt.receipt.gasUsed;
+        array.push(gasUsed);
+        console.log(`GasUsed for a submibid tx is: ${receipt.receipt.gasUsed}`);
+
+    } 
+    console.log(array.length,'bids has been succsessfully submitted');
+    console.log('Gas used for submitting the', array.length,'th bid is:');
+    console.log(`${receipt.receipt.gasUsed}`);
+    
+});
+//*******************Test 3*************************
+    it('should match the orders', async() => {
+    const OrderbookInstance = await Orderbook.deployed(); 
+    
+    
+    
+    const receipt = await OrderbookInstance.MatchOrders();
[…]

### 2020-06-06 Code/Truffle/test/9_Heap_Dynamic_Array_test.js

@@ -1,0 +1,71 @@
+const Heap_Dynamic_Array = artifacts.require('Heap_Dynamic_Array');
+
+
+contract('Heap_Dynamic_Array', function(accounts) {
+//*******************Test 1 (adding n elements to the Heap)*************************
+
+    it('should store n orders to the Heap', async() => {
+        const HeapInstance = await Heap_Dynamic_Array.deployed(); 
+        
+        var receipt = null;
+        var array = [];
+        accounts = await web3.eth.getAccounts();
+
+        for(let j = 1; j <= 10 ; j++){
+            receipt = await HeapInstance.submitorder (j, 1, {from: accounts[0]});
+            const gasUsed = receipt.receipt.gasUsed;
+            array.push(gasUsed);
+            console.log(`GasUsed for 1 submitorder tx is: ${receipt.receipt.gasUsed}`);
+        } 
+        // Getting sum of numbers
+        //var sum = array.reduce(function(a, b){
+            //return a + b;
+        //}, 0);
+
+        //console.log('cost of n submitorder txs is:',sum);   
+        console.log(array.length,'orders has been succsessfully submitted');
+        console.log('Gas used for submitting the', array.length,'th order is:');
+        console.log(`${receipt.receipt.gasUsed}`);
+        
+        console.log('*******************************************************'); 
+        //const result1 = HeapInstance.MaxHeapPeak();
+        //console.log(result1.toNumber());
+        //const result = await HeapInstance.MaxHeapPeak.call();
+        //const {0: addsender, 1: intprice, 2: auxprice, 2: intvolume} = result;
+        //console.log('The SellList peak is:', intprice);
+        
+        
+    });
+//*******************Test 2 (Removing n elements from the Heap)*************************
+
+    // it('should remove n orders from the Heap', async() => {
+    //     const HeapInstance = await Heap_Dynamic_Array.deployed();         
+    //     var receipt = null;
+    //     var array = [];
+
+    //     for(let j = 1; j <= 500 ; j++){
+    //         receipt = await HeapInstance.MaxHeapDelete();
+    //         const gasUsed = receipt.receipt.gasUsed;
+    //         array.push(gasUsed);
+    //         //console.log(`GasUsed for 1 MaxHeapDelete tx is: ${receipt.receipt.gasUsed}`);
+    //     } 
+    //     // Getting sum of numbers
+    //     //var sum = array.reduce(function(a, b){
+    //         //return a + b;
+    //     //}, 0);
+        
[…]

### 2020-06-06 Code/Truffle/truffle-config.js

@@ -34,6 +34,10 @@ module.exports = {
    *
    * $ truffle test --network <network-name>
    */
+  mocha: {
+    enableTimeouts: false,
+    //before_timeout: 2000000000 // Here is 2min but can be whatever timeout is suitable for you.
+  },
 
   networks: {
     // Useful for testing. The `development` name is special - truffle uses it by default
@@ -42,11 +46,12 @@ module.exports = {
     // tab if you use this network and you must also set the `host`, `port` and `network_id`
     // options below to some value.
     //
+    
     development: {
      host: "127.0.0.1",     // Localhost (default: none)
      port: 8545,            // Standard Ethereum port (default: none)
      network_id: "*",       // Any network (default: none)
-     gas: 4600000,
+     gas: 6700000,
      //gas: 10000000,           // Gas sent with each transaction (default: ~6700000)
 
     },
@@ -81,9 +86,9 @@ module.exports = {
   },
 
   // Set default mocha options here, use special reporters etc.
-  mocha: {
+  //mocha: {
     // timeout: 100000
-  },
+  //},
 
   // Configure your compilers
   compilers: {

### 2020-07-01 Code/New-Truffle/test/17_Worst_Case_Matching_test.js
tests(1&2)

@@ -1,15 +1,8 @@
 const CallMarket = artifacts.require('Call_Market.sol');
 const DappToken = artifacts.require('DappToken');
-const { expectRevert } = require('@openzeppelin/test-helpers');
-////const { outOfGas } = require('@openzeppelin/test-helpers/src/expectRevert');
-//import assertRevert from 'zeppelin-solidity/test/helpers/assertRevert';
-const truffleAssert = require('truffle-assertions');
-
 var CallMarketaddress;
 var tokenaddress;
 var accounts;
-
-
 
 
 //Test 1:
@@ -17,6 +10,7 @@ var accounts;
 //Note: this is a "worst case" matching where we use same prices for Bids and Asks. In this case, all the orders will be executed against each other.
 //The deliverables of this code are: (1) The maximum number of orders the match function can match (2) How much gas it uses (which should be close to the limit)
 
+//******************* Deploys the CallMaket and stores its address *************************
 contract('CallMarket', function(accounts) {
     it('should store the address of the CallMarket into the var CallMarketaddress', async() => {
         const CallMarketInstance = await CallMarket.deployed(); 
@@ -26,6 +20,7 @@ contract('CallMarket', function(accounts) {
     });
 
 });
+//******************* Deploys the DappToken and allows CallMarket to spend tokens from it *************************
 
 contract('DappToken', function(accounts) {
 
@@ -90,16 +85,15 @@ describe('CallMarket', function(accounts) {
     
     it('should submit asks from accounst[0]', async() => {
         const CallMarketInstance = await CallMarket.deployed(); 
-            var receipt = null;
-            var array = [];
-        
-
-            accounts = await web3.eth.getAccounts();
-            for(let j = 18; j >= 1  ; j--){
-                await CallMarketInstance.submitAsk (j, 1, {from: accounts[0]});
-                array.push(j);
-            } 
-            console.log(array.length,'asks has been succsessfully submitted');
+        var receipt = null;
+        var array = [];
+    
+        accounts = await web3.eth.getAccounts();
+        for(let j = 130; j >= 1  ; j--){
+            await CallMarketInstance.submitAsk (j, 1, {from: accounts[0]});
+            array.push(j);
+        } 
+        console.log(array.length,'asks have been succsessfully submitted');
          
     });
    
@@ -110,14 +104,13 @@ describe('CallMarket', function(accounts) {
         var receipt = null;
         var array = [];
         
-
[…]

### 2020-07-01 Code/New-Truffle/test/18_Average_Case_Matching_test.js

@@ -7,33 +7,23 @@ var maximum = 100;
 var minimum = 1;
 
 
-// const assert = require(‘assert’);
-// const ganache = require(‘ganache-cli’);
-// const Web3 = require(‘web3’);
-// const web3 = new Web3(ganache.provider());
-//const json = require(‘./../build/contracts/Auction.json’);
 
-
-
-
-
-//Test 1:
+//Test 2:
 //This truffle code tests 5 priority queues in terms of the number of matches the match function can handle.
 //Note: this is a "normal/average case" matching where we use random prices for Bids and Asks and obviously not all of them will be executed against each other.
 //The deliverables of this code are: (1) The maximum number of orders the match function can match (2) How much gas it uses (which should be close to the limit)
 
+//******************* Deploys the CallMaket and stores its address *************************
 contract('CallMarket', function(accounts) {
     it('should store the address of the CallMarket into the var CallMarketaddress', async() => {
         const CallMarketInstance = await CallMarket.deployed(); 
         CallMarketaddress = CallMarketInstance.address;
         console.log('The address of the CallMarket contract is:', CallMarketInstance.address);
         
-
-        
     });
 
 });
-
+//******************* Deploys the DappToken and allows CallMarket to spend tokens from it *************************
 contract('DappToken', function(accounts) {
 
     it('should approve transfer of 100 tokens from account[0] to the CallMarket contract ', async ()=> {
@@ -97,22 +87,19 @@ describe('CallMarket', function(accounts) {
     
     it('should submit asks from accounst[0]', async() => {
         const CallMarketInstance = await CallMarket.deployed(); 
-            var receipt = null;
-            var array = [];
+        var receipt = null;
+        var array = [];
         
-
-            accounts = await web3.eth.getAccounts();
-            
-            for(let j = 1; j <= 18  ; j++){
-                var randomnumber = Math.floor(Math.random() * (maximum - minimum + 1)) + minimum;
-                await CallMarketInstance.submitAsk (randomnumber, 1, {from: accounts[0]});
-                array.push(randomnumber);
-                console.log('Ask',j,'price is equal to:', randomnumber);
-            } 
-            console.log(array.length,'asks has been succsessfully submitted');
+        accounts = await web3.eth.getAccounts();
+        for(let j = 1; j <= 130  ; j++){
+            var randomnumber = Math.floor(Math.random() * (maximum - minimum + 1)) + minimum;
[…]

### 2020-07-01 LaTeX/sections/paper.tex
Updated linkedlist + tescases
tests data

@@
 
-%============= Ghazal with Auction Costs Table==================== %
+EIP-114, or the “1/64ths rule”
+EIP-114 mandates that certain stackdepth-creating opcodes withhold 1/64th of remaining gas from the stack they create. In practice this means:
+The gas required for a successful transaction can be greater than the actual gas spent (similar to how gas refunds behave).
+The extra gas required for a successful transaction varies depending on the transaction’s initial gasamount.
+A long-standing issue with Ganache has been the fact that we haven’t returned EIP-114 compliant gas estimations.
+This has caused our gas estimates to be too low in cases where a transaction executed certain opcodes.
+Gas exactimation addresses this by considering how the gas withheld at any nested stack depth/frame affects the gas needed outside of its execution context.
+Let’s see it in action
+
+Callstack Depth (hijacked stack/revert)
+
+External function calls can fail any time because they exceed the maximum call stack of 1024. In such situations, Solidity throws an exception.
+
+%If a transaction runs out of gas before successful completion, then all execution reverts.
+
+Also, Solidity \textit{delete()} function does not
+
+Clearing Mappings
+
+The Solidity type mapping (see Mapping Types) is a storage-only key-value data structure that does not keep track of the keys that were assigned a non-zero value.
+Because of that, cleaning a mapping without extra information about the written keys is not possible.
+(from : https://solidity.readthedocs.io/en/v0.5.12/security-considerations.html) So in order to wipe the unavailable Ether and token balances of all the market participants after matching is completed, we have to iterate over mapping using an array we use to store the mapping keys.
+
+In short, the sender of the transaction that causes the storage location to be freed (set to zero) will have an amount (a net 10000 gas per freed storage location) deducted from the total amount of gas used for the transaction.
+
+It's a bit more nuanced in reality:
+
+The gas cost of setting the location to zero is 5000 (G_sreset in the Yellow Paper).
+15000 gas is added into the refund counter (R_sclear in the Yellow Paper).
+At the end of a successful transaction the amount of gas in the refund counter (up to a cap of half the total gas used) is added to the unused gas and returned to the caller (Eqn 72 in the Yellow Paper).
+References above are to this version of the Yellow Paper, which discusses the Refund Counter in sections 6.1 and 6.2.
+
+The gas price is whatever gas price applies to the whole transaction in which the refund occurs
+
+delete a assigns the initial value for the type to a.
+I.e.
+for integers it is equivalent to a = 0, but it can also be used on arrays, where it assigns a dynamic array of length zero or a static array of the same length with all elements reset.
+For structs, it assigns a struct with all members reset.
+
+delete has no effect on whole mappings (as the keys of mappings may be arbitrary and are generally unknown).
+So if you delete a struct, it will reset all members that are not mappings and also recurse into the members unless they are mappings.
+However, individual keys and what they map to can be deleted.
+
+It is important to note that delete a really behaves like an assignment to a, i.e. it stores a new object in a.
+
+%============= Test 1 (17_Worst_Case_Matching_test.js) Tables==================== %
+ \section{Worst Case Matching}
+ We run the same truffle test on the five priority queues to examine them in terms of the number of order the call market contract can match.
+ Note that this is a worst case matching where we use same prices for bid and ask orders. In this case, all orders will be executed against each other.
+ Deliverables of this code are: (1) The maximum number of orders the call market can match (2) How much gas the match function uses (which should be close to the limit)
+Results are provided in Table~\ref{tab:worst_case_matching}.
+
 \begin{table}[t]
 \centering
-\begin{tabular}{|c|c|c|c|}
+\begin{tabular}{|c|c|c|}
 \hline
-\textbf{\shortstack{Number \\of \\Buy Orders}} & \textbf{\shortstack{Number \\of \\Sell Orders}} & \textbf{\shortstack{Total Number \\of\\ Orders}}  & \textbf{\shortstack{Gas Cost \\in\\ Ether}}  \\ \hline
-1 & 1 & 2 & 127,959 \\
-3 & 3 & 6 &  274,265\\
-5 & 5 & 10 & 449,684 \\
-7 & 7 & 14 & 603,057 \\
-9 & 9 & 18 & 817,224 \\
-11 & 11 & 22 & 982,549 \\
-13 & 13 & 26 & 1,210,410 \\
-15 & 15 & 30 &  1,403,040\\
-17 & 17 & 34 &  1,609,720\\
-19 & 19 & 38 & 1,862,796 \\
-21 & 21 & 42 & 2,057,234 \\
-23 & 23 & 46 &  2,266,225\\
-\hline
-25 & 25 & 50 & \textbf{out of gas} \\
-\hline
+\textbf{Priority Queue} & \textbf{Maximum Number of Matched Orders} & \textbf{Gas Cost in Ether}  \\ \hline
+
+Heap with Dynamic Array & 26 pairs & 3,274,994 \\ \hline
+Heap with Static Array & 28 pairs & 3,107,938 \\ \hline
+Mapping with keys stored in Heap & 40 pairs & 5,416,225 \\ \hline
+Linkedlist & 95 pairs & 3,336,416 \\ \hline
+Linkedlist with Mapping & 130 pairs & 3,302,908 \\ \hline
 
 \end{tabular}
-\caption{\footnotesize{Gas used for Match function when using dynamic arrays to store the heap.}\label{}} %Orderbook_V22
+\caption{\footnotesize{}\label{tab:worst_case_matching}}
+\end{table}
+
+%============= Test 1 (18_Average_Case_Matching_test.js) Tables==================== %
+ \section{Normal/Average Case Matching}
+
+PQ1 Heap with dynamic array:
+
+ PQ1 can handle 26 pairs at max (we got this from worst case matching), so we run the average test on it (for 5 times to get the average) with 26 asks and 26 bids BUT with random prices (so not all of them are going to match)
+%====%
+26 bids - 26 asks : 
+1- 16 matched, 3,022,922
+2- 14 matched, 2,630,179
+3- 13 matched, 2,756,139
+4- 14 matched, 2,677,851
+5 - 13 matched, 2,484,512
+%================================================%
+PQ2 Heap with static array:
+
+ PQ2 can handle 28 pairs at max (we got this from worst case matching), so we run the average test on it (for 5 times to get the average) with 28 asks and 28 bids BUT with random prices (so not all of them are going to match)
+%====%
+28 bids - 28 asks : 
+1- 11 matched, 1,768,494
+2- 12 matched, 2,045,830
+3- 16 matched, 2,420,384
+4- 17 matched, 2,523,974
+5- 14 matched, 2,234,141
+%================================================%
+PQ3 Mapping with keys stored in Heap:
+
+ PQ3 can handle 40 pairs at max (we got this from worst case matching), so we run the average test on it (for 5 times to get the average) with 40 asks and 40 bids BUT with random prices (so not all of them are going to match)
+%====%
+40 bids - 40 asks : 
+1- 23 matched, 4,349,561
+2- 20 matched, 3,888,163
+3- 20 matched, 3,915,233
+4- 20 matched, 3,899,789
+5- 23 matched, 4,308,653
+
+%================================================%
+PQ4 Linkedlist
+
+PQ4 can handle 95 pairs at max (we got this from worst case matching), so we run the average test on it (for 5 times to get the average) with 95 asks and 95 bids BUT with random prices (so not all of them are going to match)
+%====%
+95 bids - 95 asks : 
+1- 48 matched , 1,747,421
+2- 46 matched, 1,678,536
+3- 41 matched, 1,506,325
+4- 51 matched, 1,850,748
+5- 49 matched, 1,781,863
+
+%================================================%
+PQ5 Linkedlist with Mapping
+
+PQ5 can handle 130 pairs at max (we got this from worst case matching), so we run the average test on it (for 5 times to get the average) with 130 asks and 130 bids BUT with random prices (so not all of them are going to match)
+%====%
+130 bids - 130 asks : 
+1- 64 matched, 1,669,482
+2- 11 matched, 341,421
+3- 39 matched, 1,043,014
+4- 59 matched, 1,544,185
+5- 36 matched, 967,840
+
+ We run the same truffle test on the five priority queues to examine them in terms of the number of order the call market contract can match.
+ Note that this is an average case matching where we use random prices for bid and ask orders.
+ Deliverables of this code are: (1) The maximum number of orders the call market can match (2) How much gas the match function uses (which should be close to the limit)
+Results are provided in Table~\ref{tab:normal_case_matching}.
+
+\begin{table}[t]
+\centering
+\begin{tabular}{|c|c|c|}
+\hline
+\textbf{Priority Queue} & \textbf{Maximum Number of Matched Orders} & \textbf{Gas Cost in Ether}  \\ \hline
+
+Heap with Dynamic Array &  &  \\ \hline
+Heap with Static Array &  &  \\ \hline
+Mapping with keys stored in Heap &  &  \\ \hline
+Linkedlist &  &  \\ \hline
+Linkedlist with Mapping && \\ \hline
+
+\end{tabular}
+\caption{\footnotesize{}\label{tab:normal_case_matching}}
 \end{table}
@@
 %======================================== %
+\section{Performance Tests on Different Datastructures}
+
+%===Heap that is stored in dynamically sized array=== %
+\subsection{Heap that is stored in dynamically sized array}
+Here is the gas cost used for storing N order struct, sorting, and removing them from the heap
+Order structs are stored in a heap with dynamic array
+
+%\begin{table}[t]
+%\centering
+%\begin{tabular}{|c|c|c|}
+%\hline
+%\textbf{\shortstack{Number \\of \\ Orders}} & \textbf{\shortstack{Gas Cost \for Insertion\\ in Ether}}  \textbf{\shortstack{Gas Cost \for Removing\\ in Ether}} \\ \hline
+%1 & 105,118 & 24,430  \\
+%3 & 331,448 & 88,904 \\
+%5 & 603,874 & 184,089 \\
+%7 & 876,300 & 279,312 \\
+%9 & 1,194,820 & 430,737 \\
+%11 & 1,513,340 & 582,200 \\
+%13 & 1,831,860 & 733,663 \\
+%15 & 2,150,380 & 885,164 \\
+%17 & 2,514,996 & 1,092,829 \\
+%19 & 2,879,612 & 1,300,532 \\
+%21 & 3,244,228 & 1,508,235 \\
+%23 & 3,608,844 & 1,715,976 \\
+%25 & 3,973,460 & 1,923,679 \\
+%27 & 4,338,076 & 2,131,420 \\
+%29 & 4,702,692 & 2,339,161 \\
+%31 & 5,067,308 & 2,546,940 \\
+%33 & 5,478,020 & 2,810,845 \\
+%35 & 5,888,732 & 3,074,788\\
+%37 & 6,299,444 & 3,338,731\\
+%39 & 6,710,156 & 3,602,712 \\
+%41 &  &  \\
+%43 &  &  \\
+%45 &  &  \\
+%47 &  &  \\
+%39 &  &  \\
+%39 &  &  \\
+%37 &  &  \\
+%39 &  &  \\
+%
+%
+%
+%\hline
+%
+%
+%
+%
+%
+%
+%33 & 33 & 66 & \textbf{out of gas} \\
+%\hline
+%\end{tabular}
+%\caption{\footnotesize{Gas used for insertion() and remove() functions when using dynamic arrays to store the heap}\label{}} %Heap_Dynamic_Array.sol
+%\end{table}
+%======================================== %
+
 % = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =

### 2020-07-03 Code/New-Truffle/migrations/14_deploy_selfdestruct.js
fixing commits

@@ -1,29 +1,0 @@
-var selfdestruct = artifacts.require("./selfdestruct.sol"); 
-//const BN = require('bn.js');
-
-
-// module.exports = async function(deployer) {
-//     deployer.deploy(modularExp).then(() => {
-//         return deployer.deploy(modularExp);
-//     }).then(async () => {
-//         //var modularExp = await modularExp.deployed();
-//         await modularExp.js_call();       
-//     });      
-//     };
-
-module.exports = function (deployer) {
-    deployer.deploy(selfdestruct);
-    //Orderbook_V8Instance = await Orderbook_V8.deployed();
-    console.log("I was deployed!");
-    //HelloInstance.show_result().on('data', event => console.log(event));
-
-    //var output = await app.toy();
-    //console.log("This is the output:", output);
-    //console.log("-------------")
-    //console.log(output.logs[0])
-    //var a = new BN(output.logs[0]);
-    //event show_result(bytes byteValue, bool boolValue, uint uintValue);
-    //console.log("output is:", a);
-
-
-};

### 2020-07-03 Code/New-Truffle/migrations/15_deploy_Orderbook_V27.js

@@ -1,29 +1,0 @@
-var Orderbook_V27 = artifacts.require("./Orderbook_V27.sol"); 
-//const BN = require('bn.js');
-
-
-// module.exports = async function(deployer) {
-//     deployer.deploy(modularExp).then(() => {
-//         return deployer.deploy(modularExp);
-//     }).then(async () => {
-//         //var modularExp = await modularExp.deployed();
-//         await modularExp.js_call();       
-//     });      
-//     };
-
-module.exports = function (deployer) {
-    deployer.deploy(Orderbook_V27);
-    //Orderbook_V8Instance = await Orderbook_V8.deployed();
-    console.log("I was deployed!");
-    //HelloInstance.show_result().on('data', event => console.log(event));
-
-    //var output = await app.toy();
-    //console.log("This is the output:", output);
-    //console.log("-------------")
-    //console.log(output.logs[0])
-    //var a = new BN(output.logs[0]);
-    //event show_result(bytes byteValue, bool boolValue, uint uintValue);
-    //console.log("output is:", a);
-
-
-};

### 2020-07-03 Code/New-Truffle/migrations/16_deploy_Orderbook_V28.js

@@ -1,29 +1,0 @@
-var Orderbook_V28 = artifacts.require("./Orderbook_V28.sol"); 
-//const BN = require('bn.js');
-
-
-// module.exports = async function(deployer) {
-//     deployer.deploy(modularExp).then(() => {
-//         return deployer.deploy(modularExp);
-//     }).then(async () => {
-//         //var modularExp = await modularExp.deployed();
-//         await modularExp.js_call();       
-//     });      
-//     };
-
-module.exports = function (deployer) {
-    deployer.deploy(Orderbook_V28);
-    //Orderbook_V8Instance = await Orderbook_V8.deployed();
-    console.log("I was deployed!");
-    //HelloInstance.show_result().on('data', event => console.log(event));
-
-    //var output = await app.toy();
-    //console.log("This is the output:", output);
-    //console.log("-------------")
-    //console.log(output.logs[0])
-    //var a = new BN(output.logs[0]);
-    //event show_result(bytes byteValue, bool boolValue, uint uintValue);
-    //console.log("output is:", a);
-
-
-};

### 2020-07-03 Code/New-Truffle/migrations/17_deploy_Orderbook_V29.js

@@ -1,29 +1,0 @@
-var Orderbook_V29 = artifacts.require("./Orderbook_V29.sol"); 
-//const BN = require('bn.js');
-
-
-// module.exports = async function(deployer) {
-//     deployer.deploy(modularExp).then(() => {
-//         return deployer.deploy(modularExp);
-//     }).then(async () => {
-//         //var modularExp = await modularExp.deployed();
-//         await modularExp.js_call();       
-//     });      
-//     };
-
-module.exports = function (deployer) {
-    deployer.deploy(Orderbook_V29);
-    //Orderbook_V8Instance = await Orderbook_V8.deployed();
-    console.log("I was deployed!");
-    //HelloInstance.show_result().on('data', event => console.log(event));
-
-    //var output = await app.toy();
-    //console.log("This is the output:", output);
-    //console.log("-------------")
-    //console.log(output.logs[0])
-    //var a = new BN(output.logs[0]);
-    //event show_result(bytes byteValue, bool boolValue, uint uintValue);
-    //console.log("output is:", a);
-
-
-};

### 2020-07-03 Code/New-Truffle/migrations/7_deploy_Orderbook_V23.js

@@ -1,29 +1,0 @@
-var Orderbook_V23 = artifacts.require("./Orderbook_V23.sol"); 
-//const BN = require('bn.js');
-
-
-// module.exports = async function(deployer) {
-//     deployer.deploy(modularExp).then(() => {
-//         return deployer.deploy(modularExp);
-//     }).then(async () => {
-//         //var modularExp = await modularExp.deployed();
-//         await modularExp.js_call();       
-//     });      
-//     };
-
-module.exports = function (deployer) {
-    deployer.deploy(Orderbook_V23, 70);
-    //Orderbook_V8Instance = await Orderbook_V8.deployed();
-    console.log("I was deployed!");
-    //HelloInstance.show_result().on('data', event => console.log(event));
-
-    //var output = await app.toy();
-    //console.log("This is the output:", output);
-    //console.log("-------------")
-    //console.log(output.logs[0])
-    //var a = new BN(output.logs[0]);
-    //event show_result(bytes byteValue, bool boolValue, uint uintValue);
-    //console.log("output is:", a);
-
-
-};

### 2020-07-03 LaTeX/sections/paper.tex
Test 3&4 Data

@@
 
-EIP-114, or the “1/64ths rule”
-EIP-114 mandates that certain stackdepth-creating opcodes withhold 1/64th of remaining gas from the stack they create. In practice this means:
-The gas required for a successful transaction can be greater than the actual gas spent (similar to how gas refunds behave).
-The extra gas required for a successful transaction varies depending on the transaction’s initial gasamount.
-A long-standing issue with Ganache has been the fact that we haven’t returned EIP-114 compliant gas estimations.
-This has caused our gas estimates to be too low in cases where a transaction executed certain opcodes.
-Gas exactimation addresses this by considering how the gas withheld at any nested stack depth/frame affects the gas needed outside of its execution context.
-Let’s see it in action
+Executed orders are permanently deleted from the storage instantly.
 
-Callstack Depth (hijacked stack/revert)
+Deletion
+Ethereum gives us a gas refund when we delete variables. Its purpose is an incentive to save space on the blockchain, we use it to reduce the gas cost of our transactions.
+Deleting a variable refunds 15,000 gas up to a maximum of half the gas cost of the transaction.
+Deleting with the delete keyword is equivalent to assigning the initial value for the data type, such as 0 for integers.
 
-External function calls can fail any time because they exceed the maximum call stack of 1024. In such situations, Solidity throws an exception.
+Appendix G.
+Fee Schedule in the Yellow Paper-EIP-150, shows that a gas refund of 15,000 is given for each state slot that is set to zero.
+These refunds are calculated during execution but only paid back post-execution.
+The Fee Schedule also states that changing a store from a Zero value costs 20,000 but changing a non-Zero store costs only 5000. The notable difference being the 15,000 refund.
+So the net cost of a store and delete is 5000 gas.
+If the entire 20,000 gas or more was refunded, then there is effectively no net cost for storage operations and its IO overhead.
+A cheap attack could be launched by continuous store/delete.
 
-%If a transaction runs out of gas before successful completion, then all execution reverts.
+heap-mapping with delete mapping (30 orders) : 3,111,416
+heap-mapping without delete mapping (30 orders) : 3,582,291
+
+You should be aware the refund is done at the end of the transaction, you have to have enough gas to process each slot upfront. Also your refund can be at most half of the gas used
+Recall that the gas refund can give you up to half of your consumed gas back, so even in the best case, you won't actually break even.
+
+GasToken works by taking advantage of the storage refund in Ethereum
+
+Store data permanently on Ethereum is extremely expensive. It has no
+
+DApps on Ethereum execute arbitrary code provided by the owner of the DApp. While this code might be written
+in a high-level programming language like Solidity, it is compiled to a compact representation (called ‘bytecode’)
+that is a set of low-level instructions to the environment (Ethereum virtual machine or EVM). Because different
+functions will have different complexities, the user running the function pays in proportion to the number of
+instructions, the complexity of the instructions, and the storage requirements.
+This means that each operation has a fixed price.
+Naturally the operations might be priced in ETH, since it is the on-board currency, however this
+would cause the price of computation to be as volatile as Ether itself. Instead, Ethereum uses a pseudo-currency
+called gas.5 Each instruction has a fixed price in gas. A user who wants to run a function will offer to pay a certain
+amount of ETH per unit of gas to the miner who finalizes the function. Miners will generally choose which
+functions to run first based on how much ETH/gas they offer, and they might ignore functions that offer too little
+ETH/gas. We describe gas as a pseudo-currency because it cannot be directly stored or transacted, however we
+will revisit this below
+
+The obvious is answer is that you can receive gas refunds for releasing unused storage.
+In the yellow paper on page 25 'Appendix G.
+Fee Schedule', you can read the gas costs for each instruction.
+As you might know, SSTORE will generally create the most costs in your contracts with a significant cost of 20,000 gas per instruction.
+On the contrary, if you look at R_sclear:
+
+Refund given when the storage value is set to zero from non-zero.
+
+15,000 gas refund means you can actually get 75% of your storing costs back!
+That is a large amount, do not forget about this.
+And the solution is simple, just set a value back to 0 once you are sure it will not be used anymore.
+
+The only two OPCODEs with negative gas costs are STORAGEKILL(-15000) and GSUICIDEREFUND(-24000).
+
+These occur when storage values are deleted or contacts are suicided.
+
+These OPCODEs grant gas refunds because they free up space in the blockchain.
 
@@
 However, individual keys and what they map to can be deleted.
+
+EIP-114, or the “1/64ths rule”
+EIP-114 mandates that certain stackdepth-creating opcodes withhold 1/64th of remaining gas from the stack they create. In practice this means:
+The gas required for a successful transaction can be greater than the actual gas spent (similar to how gas refunds behave).
+The extra gas required for a successful transaction varies depending on the transaction’s initial gasamount.
+A long-standing issue with Ganache has been the fact that we haven’t returned EIP-114 compliant gas estimations.
+This has caused our gas estimates to be too low in cases where a transaction executed certain opcodes.
+Gas exactimation addresses this by considering how the gas withheld at any nested stack depth/frame affects the gas needed outside of its execution context.
+Let’s see it in action
+
+Callstack Depth (hijacked stack/revert)
+
+External function calls can fail any time because they exceed the maximum call stack of 1024. In such situations, Solidity throws an exception.
+
+%If a transaction runs out of gas before successful completion, then all execution reverts.
 

### 2020-07-28 Code/New-Truffle/migrations/1_initial_migration.js
adding the gas refund + cleaning up the test files

@@ -1,5 +1,6 @@
 const Migrations = artifacts.require("Migrations");
 
 module.exports = function(deployer) {
+  //deployer.deploy(Migrations, { gas: 1000000000 });
   deployer.deploy(Migrations);
 };

### 2020-07-28 Code/New-Truffle/test/17_Worst_Case_Matching_test.js

@@ -4,7 +4,7 @@ var CallMarketaddress;
 var tokenaddress;
 var accounts;
 
-//const delay = require('delay');
+
 
 
 //Test 1:
@@ -40,7 +40,7 @@ contract('DappToken', function(accounts) {
 
 //*******************New test Block for the already deployed CallMarket contract *************************
 describe('CallMarket', function(accounts) {
-    this.timeout(0);
+    //this.timeout(0);
    
     //*******************Test 1*************************
     it('should deposit tokens from accounst[0] to the CallMarket contract', async() => {
@@ -91,7 +91,7 @@ describe('CallMarket', function(accounts) {
         var array = [];
     
         accounts = await web3.eth.getAccounts();
-        for(let j = 1000; j >= 1  ; j--){
+        for(let j = 130; j >= 1  ; j--){
             await CallMarketInstance.submitAsk (j, 1, {from: accounts[0]});
             array.push(j);
         } 
@@ -107,7 +107,7 @@ describe('CallMarket', function(accounts) {
         var array = [];
         
         accounts = await web3.eth.getAccounts();
-        for(let j = 1001; j <= 2000  ; j++){
+        for(let j = 131; j <= 260  ; j++){
             await CallMarketInstance.submitBid (j, 1, {from: accounts[1]});
             array.push(j);
 
@@ -123,98 +123,33 @@ describe('CallMarket', function(accounts) {
     });
     
     //*******************Test 7*************************
-    it('should match the orders', async() => {
+    it('should return the Gasestimate for the match() function', async() => {
+        
         const CallMarketInstance = await CallMarket.deployed();
-        // process.on('unhandledRejection', (err) => {
-        //     throw err;
-        //    });
-       
-        //const gasEstimate = await CallMarketInstance.MatchOrders.estimateGas();
-        //const var1 = await web3.eth.getBlock("latest");
-        //const var2 = await var1.gasLimit;
+        const gasEstimate =  await CallMarketInstance.MatchOrders.estimateGas();
+        console.log(gasEstimate); 
+    });  
+
+    //*******************Test 8*************************
+    it('should match the orders', async() => {
         
-        //const receipt = await  CallMarketInstance.MatchOrders({gas: "4712388", from: accounts[4]});
+        const CallMarketInstance = await CallMarket.deployed();
+
         const receipt = await  CallMarketInstance.MatchOrders();
-        //const gasUsed = receipt.receipt.gasUsed;
[…]

### 2020-07-28 Code/New-Truffle/truffle-config.js

@@ -36,7 +36,9 @@ module.exports = {
    */
   mocha: {
     enableTimeouts: false,
-    //before_timeout: 2000000000 // Here is 2min but can be whatever timeout is suitable for you.
+    //before_timeout: 120000 // Here is 2min but can be whatever timeout is suitable for you.
+    //before_timeout: 300000 // Here is 5min but can be whatever timeout is suitable for you.
+
   },
 
   networks: {
@@ -48,19 +50,29 @@ module.exports = {
     //
     
     development: {
-     host: "127.0.0.1",     // Localhost (default: none)
-     port: 8545,            // Standard Ethereum port (default: none)
-     network_id: "*",       // Any network (default: none)
-     gasLimit: 9007199254740991,
-     gasPrice:1,
-     //gas: 6700000,           // Gas sent with each transaction (default: ~6700000)
-     //gas: 39721,
-     //gas: 6700000,
-     //gas: 4700000,
-     //gas: 4612388,
-     gas:100000000,           // Gas sent with each transaction (default: ~6700000)
+        host: "127.0.0.1",     // Localhost (default: none)
+        port: 8545,            // Standard Ethereum port (default: none)
+        network_id: "*",       // Any network (default: none)
+    
+    //Using the Ethereum current block gas limit and gas price (ganache-cli --gasLimit=0xB32937 --gasPrice=56000000000)
+        gasLimit: 11741495, 
+        gasPrice: 56000000000,        // 56 gwei (in wei), Ganache default is 20000000000 (20gwei)
+        gas:6700000,                  // Gas sent with each transaction (default: ~6700000)
+    
+    //for calculating the refund (ganache-cli --gasLimit=0x1fffffffffffff --gasPrice=1)
+        //gasLimit: 9007199254740991,
+        //gasPrice: 1, 
+        //gas:900000000000000,           
+    
+    //For 1000 orders (ganache-cli --gasLimit=0x1fffffffffffff --gasPrice=1)
+        //gasLimit: 9007199254740991,
+        //gasPrice:1,
+        //gas:900000000000000,  //dynamic array with ".timeout(90000);" at the end of match test in worst case testing
 
     },
+
+
+
 
     // Another network with more advanced options...
     // advanced: {

### 2020-07-28 LaTeX/sections/paper.tex
Test section of the paper + gas table + worst and normal submission plots

@@
 \section{Introductory Remarks}
+
+decentralized exchanges allow the market participants to be fully authoritative over their assets using their private keys. 
+One issue with decentralized
+
+Cryptocurrency trading on centralized exchanges has been shown to be vulnerable to cybersecurity hacking and internal frauds over the years, with the most infamous hacks being Mt.
+Gox and Coincheck.
+In addition, trading on centralized exchanges is not compatible with DeFi applications since it is technically infeasible to bridge between decentralized applications and centralized servers without compromising the trust model.
+
+Digitex is the intelligent combination of the speed and reliability of centralized servers with the trustless security of decentralized smart contracts.
+The Digitex Futures Exchange interacts with the smart contract so that it can update a trader’s available balance to reflect that trader’s outstanding margin liabilities and his trading profits and losses, but the exchange does not have physical possession of the trader’s funds and is unable to do anything else to the funds held in the smart contract.
+The
 
@@
 % = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
-%Mahsa
-%Notes related to design and implementations
+
+% Discussed in the meetings:
+% do the followings for the worst case matching:
+%	1- Find the actual gas limit for the Ethereum blockchain and set the gas limit of ganache to that number
+%	2- Try to find the actual gas cost before the refund for each PQ (and that number should be close to the gas limit). Have another column in the worst case matching table for that number
+
+% Have one chart with all the worst case submission and one for random case submission 
+% Increase the gas limit basically to the infinity and find the gas cost for matching 1000 orders (worst case matching).
+Why?
+because Ethereum might improve over the time and we'd like to know how would that affect each PQ in case of handling worst case matching.
+If you find a problem with Node.js we can just copy that error and discuss it inside the paper.
+In that chart, we can add horizontal lines for each gas limit (today, proposed, etc) (Ethereum (ETH) miners are currently voting to expand the block gas limit from 10,000,000 to 12,500,000 gas, according to a recent tweet from Bitfly, the parent company of Ethermine pool: https://cointelegraph.com/news/ethereum-miners-vote-to-increase-gas-limit-causing-community-debate)
+
+% Deleting the unavailable mapping remains a challenging issue to solve (have a little section in the paper to discuss our different solutions for it). 
+%	1- we can just create a new mapping everytime the market opens and have a modifier for the claim functions so that they could be called only when the market is closed. 
+%	2- we can have custom keys for the mapping (like a counter we define as a global variable and increment it at the end of the match function).
+So everytime the new market starts, we just use another portion of the mapping.
+%	3- we can have another smart contract which only stores the mapping and just delete that after the close function.
+
+% We use one-shot market for the sake of our performance tests on different datastructures. and once we have all the numbers we can think about iterated market.
+
+% Our two competitors are Uinswap and Loopring (that uses ZK roll ups):
+% 	1- Uniswap: we can argue that in traditional markets we have various traditional exchanges. Each of these exchanges have different trading rules and designs which work for different traders.
+%	2- Loopring:
+%		2-1: Barrier to entry: In order for a trader to trade specific ERC20 on Loopring, Loopring has to agree to support that token.
+It might not be difficult and they probably approve the token as long as it is standard compliant.
+%		2-2: ZK proofs are quick and cheap to verify but they are expensive and time consuming to generate: (1) now they are generating these proofs for free but later they charge traders for doing that.
+(2) Looping does not probably generate these proofs per every block so the settlement and 				clearing is not happening per block.
+So we have faster clearing and settlement as we clear everything per block.
+% 		2-3: Loopring is non-custodial, meaning that the money moves only when the proofs come, so there is a latency in transferring funds to the traders.
+
+Another important "limit" is that the gas refund is provided only 1 time, at the very end of the transaction's execution.
+This means that a transaction cannot use its own gas refund to pay for any part of its execution.
+A refund cannot be used to avoid Out of Gas exceptions
 
@@
 As you might know, SSTORE will generally create the most costs in your contracts with a significant cost of 20,000 gas per instruction.
-On the contrary, if you look at R_sclear:
+On the contrary, if you look at %R_sclear:
 
@@
 And the solution is simple, just set a value back to 0 once you are sure it will not be used anymore.
+
+Cost of a Transaction
+The total cost of a transaction in the Ethereum network is based on two factors:
+gasUsed is the total gas that is consumed
+gasPrice specified in the transaction
+<strong>Transaction Cost</strong>
+Total Transaction Cost = gasUsed * gasPrice
 
@@
 
-The gas cost of setting the location to zero is 5000 (G_sreset in the Yellow Paper).
-15000 gas is added into the refund counter (R_sclear in the Yellow Paper).
+The gas cost of setting the location to zero is 5000 %(G_sreset in the Yellow Paper).
+15000 gas is added into the refund counter %(R_sclear in the Yellow Paper).
 At the end of a successful transaction the amount of gas in the refund counter (up to a cap of half the total gas used) is added to the unused gas and returned to the caller (Eqn 72 in the Yellow Paper).
@@
 
-%============= Test 1 (17_Worst_Case_Matching_test.js) Tables==================== %
- \section{Worst Case Matching}
- We run the same truffle test on the five priority queues to examine them in terms of the number of order the call market contract can match.
- Note that this is a worst case matching where we use same prices for bid and ask orders. In this case, all orders will be executed against each other.
- Deliverables of this code are: (1) The maximum number of orders the call market can match (2) How much gas the match function uses (which should be close to the limit)
-Results are provided in Table~\ref{tab:worst_case_matching}.
+\section{Experiments}
+Our application was developed in Solidity using the Truffle development framework and deployed on Ganache-CLI.
+We used Javascript for testing by leveraging the Mocha testing framework.
+Followings outline the results of different tests we performed.
 
-\begin{table}[t]
+%============= Test 1 (17_Worst_Case_Matching_test.js) Tables=================== %
+
+ \subsection{Experiments on the \texttt{Match()} Function}
+
+We executed the same test on the the five different versions of the CallMarket we implemented using five priority queues to examine the cost of the \texttt{Match()} function as well as the maximum pairs of bid and ask orders it can handle in each case.
+The \texttt{Match()} function's computational cost and the maximum number of orders it can execute in each case (before running out of gas) are outlined in Table~\ref{tab:worst_case_matching}.
+Note that this is a \textit{worst case matching} test where all bids and asks are submitted as marketable limit orders with specified prices that would be filled undoubtedly, performed using the current Ethereum gas metrics (block gas limit $=$11,741,495 and 1 gas $=$ 56 gwei)~\footnote{https://ethstats.net/}.
+The last column of Table~\ref{tab:worst_case_matching} shows the gas cost of matching 1000 pairs of bids and asks for each priority queue for which we set the block gas limit to the maximum of  $2^{53}$ (the Javascript's max safe integer).
+
+%======= estimateGas() function = gasUsed + gasRefund =======%
+
+% Heap with Dynamic Array: match.estimateGas() = 7204994 => gasRefund = 7204994 - 3274994 = 3930000
+% Heap with Static Array: match.estimateGas() = 7337527 => gasRefund = 7337527 - 3107527 = 4230000
+% Mapping with keys stored in Heap: match.estimateGas() = 6644803 => gasRefund = 6644803 - 5414803 = 1230000
+% Linkedlist: match.estimateGas() = 7629847 => gasRefund = 7629847 -  3279847 = 4350000
+% Linkedlist with Mapping: match.estimateGas() = 7227717 => gasRefund = 7227717 -  3297717 = 3930000
+
+%===============================================%
+
+% = = = = = = = = = = = =Worst_Case_Matching Table = = = = = = = = = = = = =  %
+
+\begin{table}[]
 \centering
-\begin{tabular}{|c|c|c|}
+\begin{tabular}{|c|c|c|c|c|}
 \hline
-\textbf{Priority Queue} & \textbf{Maximum Number of Matched Orders} & \textbf{Gas Cost in Ether}  \\ \hline
 
-Heap with Dynamic Array & 26 pairs & 3,274,994 \\ \hline
-Heap with Static Array & 28 pairs & 3,107,938 \\ \hline
-Mapping with keys stored in Heap & 40 pairs & 5,416,225 \\ \hline
-Linkedlist & 95 pairs & 3,336,416 \\ \hline
-Linkedlist with Mapping & 130 pairs & 3,302,908 \\ \hline
+\textbf{Priority Queue}    & \textbf{\begin{tabular}[c]{@{}c@{}}Maximum Number \\ of \\ Matched Orders\end{tabular}}      & \textbf{Cost in Gas}      & \multicolumn{1}{l|}{\textbf{Gas Refund}}      & \textbf{\begin{tabular}[c]{@{}c@{}}Cost in Gas\\ for \\ 1000 Pairs of Orders\end{tabular}} \\ \hline
+
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
+	Heap with Dynamic Array         			& 26 pairs                & 3,274,994            & 3,930,000             & 457,326,935                      \\ \hline
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
+	Heap with Static Array           			& 28 pairs                & 3,107,527            & 4,230,000             & 333,656,805                       \\ \hline
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
+	Mapping with keys stored in Heap 		& 40 pairs                & 5,414,803            & 1,230,000              & 319,481,722                       \\ \hline
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
+	Linkedlist                       				& 90 pairs                & 3,279,847            & 4,350,000              & 35,823,601                        	\\ \hline
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
+	Linkedlist with Mapping          			& 130 pairs              & 3,297,717            & 3,930,000               & 25,095,370                        \\ \hline
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
 
@@
 
-%============= Test 1 (18_Average_Case_Matching_test.js) Tables==================== %
- \section{Normal/Average Case Matching}
+%============= Test 3 (17_Worst_Case_Submission_test.js) Figures==================== %
 
-PQ1 Heap with dynamic array:
+ \subsection{Experiments on \texttt{Submit Order()} Functions}
 
- PQ1 can handle 26 pairs at max (we got this from worst case matching), so we run the average test on it (for 5 times to get the average) with 26 asks and 26 bids BUT with random prices (so not all of them are going to match)
-%====%
-26 bids - 26 asks : 
-1- 16 matched, 3,022,922
-2- 14 matched, 2,630,179
-3- 13 matched, 2,756,139
-4- 14 matched, 2,677,851
-5 - 13 matched, 2,484,512
-%================================================%
-PQ2 Heap with static array:
+We executed another set of tests on the the five different versions of the CallMarket in which we sent 200 \texttt{SubmitBid} to the CallMarket to simulate two hundred of traders participating in the market.
+These tests were performed in two levels (i) worst case and (ii) average case submissions.
+%the data structure used for bids and asks is the same and hence the submission plots for 200 submitbids and 200 submitasks. Do we have to mention that here?
 
- PQ2 can handle 28 pairs at max (we got this from worst case matching), so we run the average test on it (for 5 times to get the average) with 28 asks and 28 bids BUT with random prices (so not all of them are going to match)
-%====%
-28 bids - 28 asks : 
-1- 11 matched, 1,768,494
-2- 12 matched, 2,045,830
-3- 16 matched, 2,420,384
-4- 17 matched, 2,523,974
-5- 14 matched, 2,234,141
-%================================================%
-PQ3 Mapping with keys stored in Heap:
+% = = = = = = = = = = = =Worst_Case_Submission = = = = = = = = = = = = =  %
 
- PQ3 can handle 40 pairs at max (we got this from worst case matching), so we run the average test on it (for 5 times to get the average) with 40 asks and 40 bids BUT with random prices (so not all of them are going to match)
-%====%
-40 bids - 40 asks : 
-1- 23 matched, 4,349,561
-2- 20 matched, 3,888,163
-3- 20 matched, 3,915,233
-4- 20 matched, 3,899,789
-5- 23 matched, 4,308,653
+\subsubsection{Worst Case Order Submission}
 
-%================================================%
-PQ4 Linkedlist
+Here each \texttt{SubmitBid()} transaction has a price that is smallest or second-smallest of the transactions after it.
+Doing so, we ensure all the orders move every time a new order is sent to the market.
+Figure~\ref{fig:worst_case_submission} shows the gas cost variations for submitting 200 orders in five versions of the CallMarket.
+The x-axis is the place in line (\eg the 10th person to submit the order) and the and y-axis is the gas cost for sending that transaction.
 
-PQ4 can handle 95 pairs at max (we got this from worst case matching), so we run the average test on it (for 5 times to get the average) with 95 asks and 95 bids BUT with random prices (so not all of them are going to match)
-%====%
-95 bids - 95 asks : 
-1- 48 matched , 1,747,421
-2- 46 matched, 1,678,536
-3- 41 matched, 1,506,325
-4- 51 matched, 1,850,748
-5- 49 matched, 1,781,863
+%And conversely each \texttt{SubmitAsk()} transaction has a price that is biggest or second-biggest of the transactions after it
 
-%================================================%
-PQ5 Linkedlist with Mapping
+% = = = = = = = = = = = =Worst_Case_Submission Figure = = = = = = = = = = = = =  %
 
-PQ5 can handle 130 pairs at max (we got this from worst case matching), so we run the average test on it (for 5 times to get the average) with 130 asks and 130 bids BUT with random prices (so not all of them are going to match)
-%====%
-130 bids - 130 asks : 
-1- 64 matched, 1,669,482
-2- 11 matched, 341,421
-3- 39 matched, 1,043,014
-4- 59 matched, 1,544,185
-5- 36 matched, 967,840
+\begin{figure}[htb!p]
+\centering
+\includegraphics[width=0.8\textwidth]{fig/worst_case_submission_3.png}
+\caption{\footnotesize{}  \label{fig:worst_case_submission}}
+\end{figure}
 
- We run the same truffle test on the five priority queues to examine them in terms of the number of order the call market contract can match.
- Note that this is an average case matching where we use random prices for bid and ask orders.
- Deliverables of this code are: (1) The maximum number of orders the call market can match (2) How much gas the match function uses (which should be close to the limit)
-Results are provided in Table~\ref{tab:normal_case_matching}.
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
 
-\begin{table}[t]
+% = = = = = = = = = = = =Average_Case_Submission = = = = = = = = = = = = =  %
+
+\subsubsection{Average Case Order Submission}
+
+Here we test the five versions of the CallMarket when 200 bid orders are entered in random ordering.
+To do so, we use JavaScript \texttt{Math.random()} function to generate pseudo-random integers between 1 and 100.
+Figure~\ref{fig:average_case_submission} shows the gas cost variations for submitting 200 orders in five versions of the CallMarket.
+Again the x-axis is the place in line (\eg the10th person to submit the order) and the and y-axis is the gas cost for submitting that transaction.
+
+% = = = = = = = = = = = =Average_Case_Submission Figure = = = = = = = = = = = = =  %
+
+\begin{figure}[htb!p]
 \centering
-\begin{tabular}{|c|c|c|}
-\hline
-\textbf{Priority Queue} & \textbf{Maximum Number of Matched Orders} & \textbf{Gas Cost in Ether}  \\ \hline
+\includegraphics[width=1\textwidth]{fig/average_case_submission_3.png}
+\caption{\footnotesize{}  \label{fig:average_case_submission}}
+\end{figure}
 
-Heap with Dynamic Array &  &  \\ \hline
-Heap with Static Array &  &  \\ \hline
-Mapping with keys stored in Heap &  &  \\ \hline
-Linkedlist &  &  \\ \hline
-Linkedlist with Mapping && \\ \hline
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
 
-\end{tabular}
-\caption{\footnotesize{}\label{tab:normal_case_matching}}
-\end{table}
-
-\begin{table}[t]
-\centering
-\begin{tabular}{|c|c|c|c|}
-\hline
-\textbf{\shortstack{Number \\of \\Buy Orders}} & \textbf{\shortstack{Number \\of \\Sell Orders}} & \textbf{\shortstack{Total Number \\of\\ Orders}}  & \textbf{\shortstack{Gas Cost \\in\\ Ether}}  \\ \hline
-1 & 1 & 2 & 144,689 \\
-3 & 3 & 6 & 324,457 \\
-5 & 5 & 10 & 527,289 \\
-7 & 7 & 14 & 710,050 \\
-9 & 9 & 18 & 964,894 \\
-11 & 11 & 22 & 1,176,905 \\
-13 & 13 & 26 & 1,370,191 \\
-15 & 15 & 30 & 1,650,273 \\
-17 & 17 & 34 & 1,953,406 \\
-19 & 19 & 38 & 2,205,141 \\
-21 & 21 & 42 & 2,416,221 \\
-23 & 23 & 46 & 2,713,313 \\
-25 & 25 & 50 & 1,788,509 \\
-27 & 27 & 54 & 2,004,824 \\
-\hline
-29 & 29 & 58 & \textbf{out of gas}\\
-\hline
-\end{tabular}
-\caption{\footnotesize{Gas used for Match function when using static arrays to store the heap.}\label{}} %Orderbook_V23
-\end{table}
-
-\begin{table}[t]
-\centering
-\begin{tabular}{|c|c|c|c|}
-\hline
-\textbf{\shortstack{Number \\of \\Buy Orders}} & \textbf{\shortstack{Number \\of \\Sell Orders}} & \textbf{\shortstack{Total Number \\of\\ Orders}}  & \textbf{\shortstack{Gas Cost \\in\\ Ether}}  \\ \hline
-1 & 1 & 2 & 177,622 \\
-3 & 3 & 6 &  341,393\\
-5 & 5 & 10 & 524,680 \\
-7 & 7 & 14 & 685,830\\
-9 & 9 & 18 & 919,636 \\
-11 & 11 & 22 & 1,094,503  \\
-13 & 13 & 26 & 1,347,199 \\
-15 & 15 & 30 & 1,559,796 \\
-17 & 17 & 34 & 1,792,040 \\
-19 & 19 & 38 & 2,076,422 \\
-21 & 21 & 42 & 2,294,229 \\
-23 & 23 & 46 & 2,532,674 \\
-25 & 25 & 50 & 2,776,988 \\
-27 & 27 & 54 & 3,069,163 \\
-29 & 29 & 58 & 3,306,749\\
-31 & 31 & 62 & 3,551,195\\
-\hline
-33 & 33 & 66 & \textbf{out of gas} \\
-\hline
-\end{tabular}
-\caption{\footnotesize{Gas used for Match function when storing the order structs in mappings and storing the keys in the dynamic arrays that represent sorted heap.}\label{}} %Orderbook_V24
-\end{table}
-
-%======================================== %
-\section{Performance Tests on Different Datastructures}
-
-%===Heap that is stored in dynamically sized array=== %
-\subsection{Heap that is stored in dynamically sized array}
-Here is the gas cost used for storing N order struct, sorting, and removing them from the heap
-Order structs are stored in a heap with dynamic array
-
-%\begin{table}[t]
-%\centering
-%\begin{tabular}{|c|c|c|}
-%\hline
-%\textbf{\shortstack{Number \\of \\ Orders}} & \textbf{\shortstack{Gas Cost \for Insertion\\ in Ether}}  \textbf{\shortstack{Gas Cost \for Removing\\ in Ether}} \\ \hline
-%1 & 105,118 & 24,430  \\
-%3 & 331,448 & 88,904 \\
-%5 & 603,874 & 184,089 \\
-%7 & 876,300 & 279,312 \\
-%9 & 1,194,820 & 430,737 \\
-%11 & 1,513,340 & 582,200 \\
-%13 & 1,831,860 & 733,663 \\
-%15 & 2,150,380 & 885,164 \\
-%17 & 2,514,996 & 1,092,829 \\
-%19 & 2,879,612 & 1,300,532 \\
-%21 & 3,244,228 & 1,508,235 \\
-%23 & 3,608,844 & 1,715,976 \\
-%25 & 3,973,460 & 1,923,679 \\
-%27 & 4,338,076 & 2,131,420 \\
-%29 & 4,702,692 & 2,339,161 \\
-%31 & 5,067,308 & 2,546,940 \\
-%33 & 5,478,020 & 2,810,845 \\
-%35 & 5,888,732 & 3,074,788\\
-%37 & 6,299,444 & 3,338,731\\
-%39 & 6,710,156 & 3,602,712 \\
-%41 &  &  \\
-%43 &  &  \\
-%45 &  &  \\
-%47 &  &  \\
-%39 &  &  \\
-%39 &  &  \\
-%37 &  &  \\
-%39 &  &  \\
-%
-%
-%
-%\hline
-%
-%
-%
-%
-%
-%
-%33 & 33 & 66 & \textbf{out of gas} \\
-%\hline
-%\end{tabular}
-%\caption{\footnotesize{Gas used for insertion() and remove() functions when using dynamic arrays to store the heap}\label{}} %Heap_Dynamic_Array.sol
-%\end{table}
 %======================================== %

### 2020-07-29 LaTeX/sections/paper.tex
edits on the table

@@
 
-\textbf{Priority Queue}    & \textbf{\begin{tabular}[c]{@{}c@{}}Maximum Number \\ of \\ Matched Orders\end{tabular}}      & \textbf{Cost in Gas}      & \multicolumn{1}{l|}{\textbf{Gas Refund}}      & \textbf{\begin{tabular}[c]{@{}c@{}}Cost in Gas\\ for \\ 1000 Pairs of Orders\end{tabular}} \\ \hline
+\textbf{\thead{Priority Queue}}    & \textbf{\thead{Maximum Number \\ of \\ Matched Orders}}      & \textbf{\thead{Cost in Gas}}      & \textbf{\thead{Cost in Gas \\ (before the \\ gas refund)}}    & \textbf{\thead{Cost in Gas\\ for \\ 1000 Pairs \\ of Orders}} \\ \hline
 
 % = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
-	Heap with Dynamic Array         			& 26 pairs                & 3,274,994            & 3,930,000             & 457,326,935                      \\ \hline
+	\textbf{\thead{Heap with \\ Dynamic Array}}         				& 26 pairs                & 3,274,994            & 7,204,994            & 457,326,935                      \\ \hline
 % = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
-	Heap with Static Array           			& 28 pairs                & 3,107,527            & 4,230,000             & 333,656,805                       \\ \hline
+	\textbf{\thead{Heap with \\ Static Array}}           				& 28 pairs                & 3,107,527            & 7,337,527             & 333,656,805                       \\ \hline
 % = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
-	Mapping with keys stored in Heap 		& 40 pairs                & 5,414,803            & 1,230,000              & 319,481,722                       \\ \hline
+	\textbf{\thead{Mapping with \\ keys stored \\ in Heap}} 		& 40 pairs                & 5,414,803            & 6,644,803              & 319,481,722                       \\ \hline
 % = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
-	Linkedlist                       				& 90 pairs                & 3,279,847            & 4,350,000              & 35,823,601                        	\\ \hline
+	\textbf{Linkedlist}                       							& 90 pairs                & 3,279,847            & 7,629,847              & 35,823,601                        	\\ \hline
 % = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
-	Linkedlist with Mapping          			& 130 pairs              & 3,297,717            & 3,930,000               & 25,095,370                        \\ \hline
+	\textbf{\thead{Linkedlist with \\ Mapping}}          				& 130 pairs              & 3,297,717            & 7,227,717               & 25,095,370                        \\ \hline
 % = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
@@
 \end{tabular}
-\caption{\footnotesize{}\label{tab:worst_case_matching}}
+\caption{\footnotesize{}
+\label{tab:worst_case_matching}}
 \end{table}
@@
 \centering
-\includegraphics[width=0.8\textwidth]{fig/worst_case_submission_3.png}
+\includegraphics[width=1\textwidth]{fig/worst_case_submission_3.png}
 \caption{\footnotesize{}  \label{fig:worst_case_submission}}

### 2020-08-03 LaTeX/sections/paper.tex
Uint testings section + results and figures

@@
 
+% = = = = = = = = = = = =Uint testing the PQs Table = = = = = = = = = = = = =  %
+
+\section{Unit Testing the Priority Queues}
+
+Here we execute the same JavaScrip test on the five priority queues with an end goal of unit testing them.
+We enter 50 unsigned integers to the priority queues in random ordering.
+To do so, we use JavaScript \texttt{Math.random()} function to generate pseudo-random integers between 1 and 200.
+Figure~\ref{fig:average_uints_insertion} shows the gas cost variations for entering 50 unsigned integers in the five data structures.
+The x-axis is the place in line (\eg the10th number entered in the priority queue) and the and y-axis is the cost of that transaction in gas.
+
+% = = = = = = = = = = = =average_uints_insertion Figure = = = = = = = = = = = = =  %
+
+\begin{figure}[htb!p]
+\centering
+\includegraphics[width=1\textwidth]{fig/average_uints_insertion.png}
+\caption{\footnotesize{}  \label{fig:average_uints_insertion}}
+\end{figure}
+
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
+
+Then, we call the \texttt{Dequeue()} function which iteratively removes the maximum value of the priority queue (until the data structure is empty).
+The computational costs for dequeuing 50 unsigned integers in each priority queue are outlined in Table~\ref{tab:PQ_UnitTests}.
+The tests are performed using the current Ethereum gas metrics (block gas limit $=$11,741,495 and 1 gas $=$ 56 gwei)~\footnote{https://ethstats.net/}.
+The second column of the table shows the net gas consumption (the gasUsed value derived from transaction receipts) for removing 50 integers from each priority queues.
+
+At the time of this writing, Ethereum transaction receipts only contain the net gas consumption and not the total gas consumption ( total gas consumption is defined as $gas refunded + gasUsed$ ) and we cannot find out the value of the EVM's refund counter from inside the EVM.
+
+So in order to account for refunds inside each priority queue smart contract, we can calculate them manually; first we figure out exactly how much storage is being cleared when dequeuing  the max integers and then we could multiply the number of storage slots cleared by 15,000 (see the last column of Table~\ref{tab:PQ_UnitTests}).
+
+Another way to know the amount of refund in each priority queue is to use \texttt{the estimateGas API} which provides a rough idea about the total amount of gas that is required for a transaction to go through.
+The \texttt{web3.eth.estimateGas} pretends the transaction is included in the block  and its functions (with the parameters passed) will be executed on the Ethereum blockchain.
+Doing so, it provides us an estimate of how much gas is needed to be sent with the transaction.
+The second and third columns of Table~\ref{tab:PQ_UnitTests}) show the total amount of gas required for dequeuing 50 integers from each priority queue (provided by estimateGas) as well as the amount of gas refund ($Total Gas Consumption - gasUsed$).
+
+Note that in order to urge miners to process smart contract with refunds, the accumulated gas refund can never exceed half the gas used up during computation~\cite{wood2014ethereum}.
+For example, the amount of gas that has been used when dequeuing 50 integers from the linkedlist with mapping data structure is 731,514 and since $3,000,000 > 731,514/2$, the accumulated refund through the transaction will be $731,514/2 = 365,757$.
+
+% = = = = = = = = = = = =Uint testing the PQs Table = = = = = = = = = = = = =  %
+
+\begin{table}[]
+\centering
+\begin{tabular}{|c|c|c|c|c|}
+\hline
+
+\textbf{\thead{Priority Queue}}    & \textbf{\thead{Net Cost\\in Gas}}      & \textbf{\thead{Total Cost\\in Gas\\(from estimateGas)}}      & \textbf{\thead{Gas Refund \\(from \texttt{estimateGas})}}    & \textbf{\thead{Gas Refund \\(Manually Calculated)}} \\ \hline
+
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
+	\textbf{\thead{Heap with \\ Dynamic Array}}         				& 2,547,031               & 3,312,378		& 765,347             & 750,000                       \\ \hline
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
+	\textbf{\thead{Heap with \\ Static Array}}           				& 1,324,856                & 2,090,182     	& 765,326             & 750,000                      \\ \hline
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
+	\textbf{\thead{Mapping with \\ keys stored \\ in Heap}} 		& 2,863,239                & 4,378,584       	& 1,515,345           & 1,500,000                     \\ \hline
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
+	\textbf{Linkedlist}                       							& 557,085               	& 1,772,085      	& 1,215,000           & 1,200,000                      \\ \hline
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
+	\textbf{\thead{Linkedlist with \\ Mapping}}          				& 731,514              	& 3,731,514       	& 3,000,000     	  &  3,765,000                       \\ \hline
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
+
+\end{tabular}
+\caption{\footnotesize{}
+\label{tab:PQ_UnitTests}}
+\end{table}
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
+
+%============= Experiments =================== %
 \section{Experiments}
+
 Our application was developed in Solidity using the Truffle development framework and deployed on Ganache-CLI.
@@
 \centering
-\begin{tabular}{|c|c|c|c|c|}
+\begin{tabular}{|c|c|c|c|}
 \hline
 
-\textbf{\thead{Priority Queue}}    & \textbf{\thead{Maximum Number \\ of \\ Matched Orders}}      & \textbf{\thead{Cost in Gas}}      & \textbf{\thead{Cost in Gas \\ (before the \\ gas refund)}}    & \textbf{\thead{Cost in Gas\\ for \\ 1000 Pairs \\ of Orders}} \\ \hline
+\textbf{\thead{Priority Queue}}    & \textbf{\thead{Maximum Number \\ of \\ Matched Orders}}      & \textbf{\thead{Net Cost\\in Gas}}          & \textbf{\thead{Net Cost in Gas\\ for \\ 1000 Pairs \\ of Orders}} \\ \hline
 
 % = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
-	\textbf{\thead{Heap with \\ Dynamic Array}}         				& 26 pairs                & 3,274,994            & 7,204,994            & 457,326,935                      \\ \hline
+	\textbf{\thead{Heap with \\ Dynamic Array}}         				& 26 pairs                & 3,274,994                   	& 457,326,935                      \\ \hline
 % = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
-	\textbf{\thead{Heap with \\ Static Array}}           				& 28 pairs                & 3,107,527            & 7,337,527             & 333,656,805                       \\ \hline
+	\textbf{\thead{Heap with \\ Static Array}}           				& 28 pairs                & 3,107,527                  	& 333,656,805                       \\ \hline
 % = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
-	\textbf{\thead{Mapping with \\ keys stored \\ in Heap}} 		& 40 pairs                & 5,414,803            & 6,644,803              & 319,481,722                       \\ \hline
+	\textbf{\thead{Mapping with \\ keys stored \\ in Heap}} 		& 40 pairs                & 5,414,803                     & 319,481,722                       \\ \hline
 % = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
-	\textbf{Linkedlist}                       							& 90 pairs                & 3,279,847            & 7,629,847              & 35,823,601                        	\\ \hline
+	\textbf{Linkedlist}                       							& 90 pairs                & 3,279,847                      & 35,823,601                        	\\ \hline
 % = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
-	\textbf{\thead{Linkedlist with \\ Mapping}}          				& 130 pairs              & 3,297,717            & 7,227,717               & 25,095,370                        \\ \hline
+	\textbf{\thead{Linkedlist with \\ Mapping}}          				& 130 pairs              & 3,297,717                       & 25,095,370                        \\ \hline
 % = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
@@
 
-%============= Test 3 (17_Worst_Case_Submission_test.js) Figures==================== %
-
- \subsection{Experiments on \texttt{Submit Order()} Functions}
-
-We executed another set of tests on the the five different versions of the CallMarket in which we sent 200 \texttt{SubmitBid} to the CallMarket to simulate two hundred of traders participating in the market.
+%%============= Test 3 (17_Worst_Case_Submission_test.js) Figures==================== %
+%
+% \subsection{Experiments on \texttt{Submit Order()} Functions}
+%
+%We executed another set of tests on the the five different versions of the CallMarket in which we sent 200 \texttt{SubmitBid} to the CallMarket to simulate two hundred of traders participating in the market.
 These tests were performed in two levels (i) worst case and (ii) average case submissions.
-%the data structure used for bids and asks is the same and hence the submission plots for 200 submitbids and 200 submitasks. Do we have to mention that here?
-
-% = = = = = = = = = = = =Worst_Case_Submission = = = = = = = = = = = = =  %
-
-\subsubsection{Worst Case Order Submission}
-
-Here each \texttt{SubmitBid()} transaction has a price that is smallest or second-smallest of the transactions after it.
+%%the data structure used for bids and asks is the same and hence the submission plots for 200 submitbids and 200 submitasks. Do we have to mention that here?
+%
+%% = = = = = = = = = = = =Worst_Case_Submission = = = = = = = = = = = = =  %
+%
+%\subsubsection{Worst Case Order Submission}
+%
+%Here each \texttt{SubmitBid()} transaction has a price that is smallest or second-smallest of the transactions after it.
 Doing so, we ensure all the orders move every time a new order is sent to the market.
@@
 The x-axis is the place in line (\eg the 10th person to submit the order) and the and y-axis is the gas cost for sending that transaction.
-
-%And conversely each \texttt{SubmitAsk()} transaction has a price that is biggest or second-biggest of the transactions after it
-
-% = = = = = = = = = = = =Worst_Case_Submission Figure = = = = = = = = = = = = =  %
-
-\begin{figure}[htb!p]
-\centering
-\includegraphics[width=1\textwidth]{fig/worst_case_submission_3.png}
-\caption{\footnotesize{}  \label{fig:worst_case_submission}}
-\end{figure}
-
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
-
-% = = = = = = = = = = = =Average_Case_Submission = = = = = = = = = = = = =  %
-
-\subsubsection{Average Case Order Submission}
-
-Here we test the five versions of the CallMarket when 200 bid orders are entered in random ordering.
+%
+%%And conversely each \texttt{SubmitAsk()} transaction has a price that is biggest or second-biggest of the transactions after it
+%
+%% = = = = = = = = = = = =Worst_Case_Submission Figure = = = = = = = = = = = = =  %
+%
+%\begin{figure}[htb!p]
+%\centering
+%\includegraphics[width=1\textwidth]{fig/worst_case_submission_3.png}
+%\caption{\footnotesize{}  \label{fig:worst_case_submission}}
+%\end{figure}
+%
+%% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
+%
+%
+%% = = = = = = = = = = = =Average_Case_Submission = = = = = = = = = = = = =  %
+%
+%\subsubsection{Average Case Order Submission}
+%
+%Here we test the five versions of the CallMarket when 200 bid orders are entered in random ordering.
 To do so, we use JavaScript \texttt{Math.random()} function to generate pseudo-random integers between 1 and 100.
@@
 Again the x-axis is the place in line (\eg the10th person to submit the order) and the and y-axis is the gas cost for submitting that transaction.
-
-% = = = = = = = = = = = =Average_Case_Submission Figure = = = = = = = = = = = = =  %
-
-\begin{figure}[htb!p]
-\centering
-\includegraphics[width=1\textwidth]{fig/average_case_submission_3.png}
-\caption{\footnotesize{}  \label{fig:average_case_submission}}
-\end{figure}
-
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
+%
+%% = = = = = = = = = = = =Average_Case_Submission Figure = = = = = = = = = = = = =  %
+%
+%\begin{figure}[htb!p]
+%\centering
+%\includegraphics[width=1\textwidth]{fig/average_case_submission_3.png}
+%\caption{\footnotesize{}  \label{fig:average_case_submission}}
+%\end{figure}
+%
+%% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
 

### 2020-08-03 LaTeX/sections/paper.tex
landscape of solutions for closing

@@
 
+% = = = = = = = = = = = =Who pays for the close function? = = = = = = = = = = = = =  %
+
+\section{Who Pays the Cost for the \texttt{CloseMarket()} Function?}
+
+Ethereum contracts can only run when a function is called.
+So if no one calls the \texttt{CloseMarket()} function at the end of the trading period, this function cannot self-execute to modify itself.
+In addition, upon closing the market the \texttt{Match()} function will be executed which consumes a significant amounts of gas, and the person who closes the market must have enough incentives to do so.
+We think it is useful to explore the landscape of possible designs for closing the market.
+
+\begin{enumerate}
+
+\item \textbf {Using the Meta Transactions.} Meta transactions enable users to execute Ethereum functions without paying the gas.
+Rather than spending gas, users sign their intended action using their private keys and broadcast it to the network with no cost.
+A third party process (\textit{a relayer}) then crafts the actual transaction on user's behalf, sends the transaction to the Ethereum blockchain, and charges the base contract with the associated fees (see Figure~\ref{fig:meta_tx}).
+The required gas to pay for the \texttt{Match()} function could be collected as fees.
+So market participants are charged with certain amounts of fees every time they submit an order, these fees are accumulated in the CallMarket contract and will be used to pay for executing the \texttt{CloseMarket()} function.
+
+% = = = = = = = = = = = =meta_tx Figure = = = = = = = = = = = = =  %
+
+\begin{figure}[htb!p]
+\centering
+\includegraphics[width=0.8\textwidth]{fig/meta_tx.png}
+\caption{\footnotesize{}  \label{fig:meta_tx}}
+\end{figure}
+
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
+
+\item \textbf{Using the "Contract Pays" Model.} An alternative solution is to design the market such that the last person to submit an order calls the \texttt{CloseMarket()} function, but in contrast to a normal transaction (where the person initiating the transaction must pay the fee), here the CallMarket contract pays the cost for closing the market and matching the orders respectively.
+To enforce this design we can use Solidity function modifiers; every time a new order is submitted, a function modifier checks whether (i) the auction period has to end and/or (ii) the maximum number of total orders has reached.
+If any of these two conditions are met, the \texttt{CloseMarket()} will be called.
+Again, market participants are charged with certain amounts of fees every time they submit an order, these fees are accumulated in the CallMarket.
+Once the \texttt{CloseMarket} is successfully executed and orders are matched, the contract transfers its funds to that person.
+Note that here the person must still have enough gas to cover the execution of the transaction as the funds will be only transferred after the transaction is fully executed.
+However, market participants are incentivized to do so as they may receive more ethers than they have spent.
+
+\end{enumerate}
+
 % = = = = = = = = = = = =Uint testing the PQs Table = = = = = = = = = = = = =  %
@@
 Doing so, it provides us an estimate of how much gas is needed to be sent with the transaction.
-The second and third columns of Table~\ref{tab:PQ_UnitTests}) show the total amount of gas required for dequeuing 50 integers from each priority queue (provided by estimateGas) as well as the amount of gas refund ($Total Gas Consumption - gasUsed$).
+The second and third columns of Table~\ref{tab:PQ_UnitTests}) show the total amount of gas required for dequeuing 50 integers from each priority queue (provided by estimateGas) and amount of gas refund ($Total Gas Consumption - gasUsed$) respectively.
 
 Note that in order to urge miners to process smart contract with refunds, the accumulated gas refund can never exceed half the gas used up during computation~\cite{wood2014ethereum}.
+So at the end of a successful transaction, the amount of gas in the refund counter (capped at half the net gas used) is returned to the caller.
 For example, the amount of gas that has been used when dequeuing 50 integers from the linkedlist with mapping data structure is 731,514 and since $3,000,000 > 731,514/2$, the accumulated refund through the transaction will be $731,514/2 = 365,757$.

### 2020-08-04 LaTeX/sections/paper.tex
Clearing the Mapping Section

@@
 
-decentralized exchanges allow the market participants to be fully authoritative over their assets using their private keys. 
-One issue with decentralized
-
-Cryptocurrency trading on centralized exchanges has been shown to be vulnerable to cybersecurity hacking and internal frauds over the years, with the most infamous hacks being Mt.
+%decentralized exchanges allow the market participants to be fully authoritative over their assets using their private keys. 
+%One issue with decentralized 
+%
+%Cryptocurrency trading on centralized exchanges has been shown to be vulnerable to cybersecurity hacking and internal frauds over the years, with the most infamous hacks being Mt.
 Gox and Coincheck.
 In addition, trading on centralized exchanges is not compatible with DeFi applications since it is technically infeasible to bridge between decentralized applications and centralized servers without compromising the trust model.
-
-Digitex is the intelligent combination of the speed and reliability of centralized servers with the trustless security of decentralized smart contracts.
-The Digitex Futures Exchange interacts with the smart contract so that it can update a trader’s available balance to reflect that trader’s outstanding margin liabilities and his trading profits and losses, but the exchange does not have physical possession of the trader’s funds and is unable to do anything else to the funds held in the smart contract.
-The
 
@@
 % Discussed in the meetings:
-% do the followings for the worst case matching:
+% do the followings for the worst case matching: (Done!)
 %	1- Find the actual gas limit for the Ethereum blockchain and set the gas limit of ganache to that number
@@
 
-% Have one chart with all the worst case submission and one for random case submission 
+% Have one chart with all the worst case submission and one for random case submission (Done!)
 % Increase the gas limit basically to the infinity and find the gas cost for matching 1000 orders (worst case matching).
@@
 In that chart, we can add horizontal lines for each gas limit (today, proposed, etc) (Ethereum (ETH) miners are currently voting to expand the block gas limit from 10,000,000 to 12,500,000 gas, according to a recent tweet from Bitfly, the parent company of Ethermine pool: https://cointelegraph.com/news/ethereum-miners-vote-to-increase-gas-limit-causing-community-debate)
-
-% Deleting the unavailable mapping remains a challenging issue to solve (have a little section in the paper to discuss our different solutions for it). 
-%	1- we can just create a new mapping everytime the market opens and have a modifier for the claim functions so that they could be called only when the market is closed. 
-%	2- we can have custom keys for the mapping (like a counter we define as a global variable and increment it at the end of the match function).
-So everytime the new market starts, we just use another portion of the mapping.
-%	3- we can have another smart contract which only stores the mapping and just delete that after the close function.
 
@@
 
-Another important "limit" is that the gas refund is provided only 1 time, at the very end of the transaction's execution.
-This means that a transaction cannot use its own gas refund to pay for any part of its execution.
-A refund cannot be used to avoid Out of Gas exceptions
+% = = = = = = = = = = = =Clearing Mappings = = = = = = = = = = = = =  %
+\section{Clearing Mappings}
 
-Executed orders are permanently deleted from the storage instantly.
+To facilitate a safe exchange among buyers and sellers, we implement the CallMarket smart contract in the form of a \textit{collateralized}; for market participants to be able to send bid and/or ask orders, they have to first supply assets (depending on what asset they aim to trade) as collaterals  by calling any of the  \texttt{DepositToken()} or \texttt{DepositEther()} methods.
+The collateralized CallMarket acts as a payment guarantees and market participants cannot default on payment or delivery of their assets.
 
-Deletion
-Ethereum gives us a gas refund when we delete variables. Its purpose is an incentive to save space on the blockchain, we use it to reduce the gas cost of our transactions.
-Deleting a variable refunds 15,000 gas up to a maximum of half the gas cost of the transaction.
-Deleting with the delete keyword is equivalent to assigning the initial value for the data type, such as 0 for integers.
+To maintain the collateral balance of each market participant, we use two Solidity type one-to-one mapping that map Ethereum addresses to 256 bits unsigned integers; \texttt{TotalBalance} and \texttt{UnavailableBalance}.
+Once market closes and orders are matched, the \texttt{UnavailableBalance} needs to be cleared.
+However, since it is not possible to delete the entire mapping without knowing the keys~\footnote{https://solidity.readthedocs.io/en/v0.5.12/security-considerations.html}, clearing the \texttt{UnavailableBalance} mapping remains a challenging issue to solve .
+Here we provide a landscape of solutions for that.
+%only individual keys and what they map to can be deleted.
 
-Appendix G.
-Fee Schedule in the Yellow Paper-EIP-150, shows that a gas refund of 15,000 is given for each state slot that is set to zero.
-These refunds are calculated during execution but only paid back post-execution.
-The Fee Schedule also states that changing a store from a Zero value costs 20,000 but changing a non-Zero store costs only 5000. The notable difference being the 15,000 refund.
-So the net cost of a store and delete is 5000 gas.
-If the entire 20,000 gas or more was refunded, then there is effectively no net cost for storage operations and its IO overhead.
-A cheap attack could be launched by continuous store/delete.
+\begin{enumerate}
 
-heap-mapping with delete mapping (30 orders) : 3,111,416
-heap-mapping without delete mapping (30 orders) : 3,582,291
+\item \textbf{Creating a New Mapping for \texttt{UnavailableBalance} Every Time the Market Opens.} Instead of clearing the \texttt{UnavailableBalance} of traders at the end of a matching process, we could create a new mapping every time the market opens.
+Note that using this solution, traders can only claim their funds (using the \texttt{ClaimEther()} and/or \texttt{ClaimToken} methods) only when the market is in state \texttt{Closed}.
 
-You should be aware the refund is done at the end of the transaction, you have to have enough gas to process each slot upfront. Also your refund can be at most half of the gas used
-Recall that the gas refund can give you up to half of your consumed gas back, so even in the best case, you won't actually break even.
+\item \textbf{Creating Custom Keys for the Mapping.} We can create custom keys for the mapping by defining a counter as a global variable inside the CallMarket smart contract.
+This counter is incremented at the end of the matching process.
+So instead of clearing the mapping, we only use another portion of it every time the market opens.
 
-GasToken works by taking advantage of the storage refund in Ethereum
+\item \textbf{Creating a Data-Contract that Stores the Mapping.} Another design pattern is to create a smart contract that only stores the \texttt{UnavailableBalance} mapping every time the market opens.
+This data contract will be killed at the end of the matching process.
 
-Store data permanently on Ethereum is extremely expensive. It has no
+\end{enumerate}
 
-DApps on Ethereum execute arbitrary code provided by the owner of the DApp. While this code might be written
-in a high-level programming language like Solidity, it is compiled to a compact representation (called ‘bytecode’)
-that is a set of low-level instructions to the environment (Ethereum virtual machine or EVM). Because different
-functions will have different complexities, the user running the function pays in proportion to the number of
-instructions, the complexity of the instructions, and the storage requirements.
-This means that each operation has a fixed price.
-Naturally the operations might be priced in ETH, since it is the on-board currency, however this
-would cause the price of computation to be as volatile as Ether itself. Instead, Ethereum uses a pseudo-currency
-called gas.5 Each instruction has a fixed price in gas. A user who wants to run a function will offer to pay a certain
-amount of ETH per unit of gas to the miner who finalizes the function. Miners will generally choose which
-functions to run first based on how much ETH/gas they offer, and they might ignore functions that offer too little
-ETH/gas. We describe gas as a pseudo-currency because it cannot be directly stored or transacted, however we
-will revisit this below
+ %Deleting the unavailable mapping remains a challenging issue to solve (have a little section in the paper to discuss our different solutions for it). 
+%	1- we can just create a new mapping everytime the market opens and have a modifier for the claim functions so that they could be called only when the market is closed. 
+%	2- we can have custom keys for the mapping (like a counter we define as a global variable and increment it at the end of the match function).
+So everytime the new market starts, we just use another portion of the mapping.
+%	3- we can have another smart contract which only stores the mapping and just delete that after the close function.
 
-The obvious is answer is that you can receive gas refunds for releasing unused storage.
-In the yellow paper on page 25 'Appendix G.
-Fee Schedule', you can read the gas costs for each instruction.
-As you might know, SSTORE will generally create the most costs in your contracts with a significant cost of 20,000 gas per instruction.
-On the contrary, if you look at %R_sclear:
-
-Refund given when the storage value is set to zero from non-zero.
-
-15,000 gas refund means you can actually get 75% of your storing costs back!
-That is a large amount, do not forget about this.
-And the solution is simple, just set a value back to 0 once you are sure it will not be used anymore.
-
-Cost of a Transaction
-The total cost of a transaction in the Ethereum network is based on two factors:
-gasUsed is the total gas that is consumed
-gasPrice specified in the transaction
-<strong>Transaction Cost</strong>
-Total Transaction Cost = gasUsed * gasPrice
-
-The only two OPCODEs with negative gas costs are STORAGEKILL(-15000) and GSUICIDEREFUND(-24000).
-
-These occur when storage values are deleted or contacts are suicided.
-
-These OPCODEs grant gas refunds because they free up space in the blockchain.
-
-Also, Solidity \textit{delete()} function does not
-
-Clearing Mappings
-
-The Solidity type mapping (see Mapping Types) is a storage-only key-value data structure that does not keep track of the keys that were assigned a non-zero value.
-Because of that, cleaning a mapping without extra information about the written keys is not possible.
-(from : https://solidity.readthedocs.io/en/v0.5.12/security-considerations.html) So in order to wipe the unavailable Ether and token balances of all the market participants after matching is completed, we have to iterate over mapping using an array we use to store the mapping keys.
-
-In short, the sender of the transaction that causes the storage location to be freed (set to zero) will have an amount (a net 10000 gas per freed storage location) deducted from the total amount of gas used for the transaction.
-
-It's a bit more nuanced in reality:
-
-The gas cost of setting the location to zero is 5000 %(G_sreset in the Yellow Paper).
-15000 gas is added into the refund counter %(R_sclear in the Yellow Paper).
-At the end of a successful transaction the amount of gas in the refund counter (up to a cap of half the total gas used) is added to the unused gas and returned to the caller (Eqn 72 in the Yellow Paper).
-References above are to this version of the Yellow Paper, which discusses the Refund Counter in sections 6.1 and 6.2.
-
-The gas price is whatever gas price applies to the whole transaction in which the refund occurs
-
-delete a assigns the initial value for the type to a.
-I.e.
-for integers it is equivalent to a = 0, but it can also be used on arrays, where it assigns a dynamic array of length zero or a static array of the same length with all elements reset.
-For structs, it assigns a struct with all members reset.
-
-delete has no effect on whole mappings (as the keys of mappings may be arbitrary and are generally unknown).
-So if you delete a struct, it will reset all members that are not mappings and also recurse into the members unless they are mappings.
-However, individual keys and what they map to can be deleted.
-
-EIP-114, or the “1/64ths rule”
-EIP-114 mandates that certain stackdepth-creating opcodes withhold 1/64th of remaining gas from the stack they create. In practice this means:
-The gas required for a successful transaction can be greater than the actual gas spent (similar to how gas refunds behave).
-The extra gas required for a successful transaction varies depending on the transaction’s initial gasamount.
-A long-standing issue with Ganache has been the fact that we haven’t returned EIP-114 compliant gas estimations.
-This has caused our gas estimates to be too low in cases where a transaction executed certain opcodes.
-Gas exactimation addresses this by considering how the gas withheld at any nested stack depth/frame affects the gas needed outside of its execution context.
-Let’s see it in action
-
-Callstack Depth (hijacked stack/revert)
-
-External function calls can fail any time because they exceed the maximum call stack of 1024. In such situations, Solidity throws an exception.
-
-%If a transaction runs out of gas before successful completion, then all execution reverts.
-
-It is important to note that delete a really behaves like an assignment to a, i.e. it stores a new object in a.
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
 

### 2020-08-04 LaTeX/sections/paper.tex
More edits

@@
 
-% Discussed in the meetings:
-% do the followings for the worst case matching: (Done!)
-%	1- Find the actual gas limit for the Ethereum blockchain and set the gas limit of ganache to that number
-%	2- Try to find the actual gas cost before the refund for each PQ (and that number should be close to the gas limit). Have another column in the worst case matching table for that number
-
-% Have one chart with all the worst case submission and one for random case submission (Done!)
-% Increase the gas limit basically to the infinity and find the gas cost for matching 1000 orders (worst case matching).
-Why?
-because Ethereum might improve over the time and we'd like to know how would that affect each PQ in case of handling worst case matching.
-If you find a problem with Node.js we can just copy that error and discuss it inside the paper.
-In that chart, we can add horizontal lines for each gas limit (today, proposed, etc) (Ethereum (ETH) miners are currently voting to expand the block gas limit from 10,000,000 to 12,500,000 gas, according to a recent tweet from Bitfly, the parent company of Ethermine pool: https://cointelegraph.com/news/ethereum-miners-vote-to-increase-gas-limit-causing-community-debate)
-
-% We use one-shot market for the sake of our performance tests on different datastructures. and once we have all the numbers we can think about iterated market.
+% = = = = = = = = = = = =Notes Discussed in Meetings = = = = = = = = = = = = =  %
 
@@
 % 		2-3: Loopring is non-custodial, meaning that the money moves only when the proofs come, so there is a latency in transferring funds to the traders.
+
+% The heap with dynamic array can do 26 pairs of matches at worst case matching whereas Linkedliat does 90 pairs.
+So if we want to cap the orders over 4 PQs, we’re basically increasing the heap size which makes match more expensive for nothing (every time a match happens and the root is deleted the whole heap is reheapified)
+
+% There will be no ties as we use 2 counters for buy and sell orders. These counters are concatenated them with the price. So we somehow enforce time priority
 
@@
 
-\item \textbf{Creating a New Mapping for \texttt{UnavailableBalance} Every Time the Market Opens.} Instead of clearing the \texttt{UnavailableBalance} of traders at the end of a matching process, we could create a new mapping every time the market opens.
+\item \textbf{Creating a New Mapping Every Time the Market Opens.} Instead of clearing the \texttt{UnavailableBalance} of traders at the end of a matching process, we could create a new mapping every time the market opens.
 Note that using this solution, traders can only claim their funds (using the \texttt{ClaimEther()} and/or \texttt{ClaimToken} methods) only when the market is in state \texttt{Closed}.
@@
 
-\item \textbf{Creating a Data-Contract that Stores the Mapping.} Another design pattern is to create a smart contract that only stores the \texttt{UnavailableBalance} mapping every time the market opens.
-This data contract will be killed at the end of the matching process.
+\item \textbf{Storing the Mapping in a Data-Contract.} Another design proposal is to create a smart contract every time the market opens, this data contract only stores the \texttt{UnavailableBalance} mapping and will be killed at the end of the matching process.
+
+\item \textbf{Storing the Mapping keys in an Array.} We can create an array that stores the traders' addresses (\ie the mapping keys).
+Knowing the keys enable us to iterate over the mapping and delete individual keys and what they map to at the end of the matching process.
+This is a gas-costly design pattern and would cause a high probability of exceeding the gas limitation inside the \texttt{Match()} function.
 
@@
 
-Another way to know the amount of refund in each priority queue is to use \texttt{the estimateGas API} which provides a rough idea about the total amount of gas that is required for a transaction to go through.
+Another way to know the amount of refund in each priority queue is to use the \texttt{estimateGas API} which provides a rough idea about the total amount of gas that is required for a transaction to go through.
 The \texttt{web3.eth.estimateGas} pretends the transaction is included in the block and its functions (with the parameters passed) will be executed on the Ethereum blockchain.
 Doing so, it provides us an estimate of how much gas is needed to be sent with the transaction.
-The second and third columns of Table~\ref{tab:PQ_UnitTests}) show the total amount of gas required for dequeuing 50 integers from each priority queue (provided by estimateGas) and amount of gas refund ($Total Gas Consumption - gasUsed$) respectively.
+The second and third columns of Table~\ref{tab:PQ_UnitTests}) show the total amount of gas required for dequeuing 50 integers from each priority queue (provided by estimateGas) and the amount of gas refund ($Total Gas Consumption - gasUsed$) respectively.
 
@@
 So at the end of a successful transaction, the amount of gas in the refund counter (capped at half the net gas used) is returned to the caller.
-For example, the amount of gas that has been used when dequeuing 50 integers from the linkedlist with mapping data structure is 731,514 and since $3,000,000 > 731,514/2$, the accumulated refund through the transaction will be $731,514/2 = 365,757$.
+For example, the amount of gas that has been used when dequeuing 50 integers from the linkedlist with mapping data structure is 731,514 and since $3,000,000 > 731,514/2$, the amount of refund returned to the caller is $731,514/2 = 365,757$.
 

### 2020-08-05 LaTeX/sections/paper.tex
Order books section

@@
 
-\section{Related Work}
+\section{Order Books}
+
+Order books are data structures that maintain lists of bid and ask orders for various assets (\eg currencies, stocks, bonds \etc) in specific markets.
+The most common version of order books is what we call a \textit{double auction}, where market participants submit their bid and ask orders and the market clearing price will be calculated as the average between the best bid and best ask prices.
+Order books often sort the orders based on their price and submission time (this order allocation technique is called price-time priority)~\cite{preis2011price}, where orders are prioritized from highest price to lowest and given any two orders with the same price, they will be sorted based on their submission timestamps.
+
+\par
+
+Looking more closely, order books are rather electronic ledgers that get updated over time.
+Given the definition of the Etehreum blockchain (\ie a distributed ledger), the idea of implementing an order book in the form of a smart contract will seemingly resolve the existing issues with centralized exchanges.
+However, this design is not feasible due to some crucial challenges that exist within blockchains:
+
+\begin{itemize}
+
+\item \textbf{Speed.}
+
+\item \textbf{Front-running and Censorship.}
+
+\item \textbf{Enforcing Time.}
+
+\end{itemize}
 

### 2020-08-06 Code/New-Truffle/test/17_Worst_Case_Matching_test.js
updates in the codes and test files

@@ -40,7 +40,7 @@ contract('DappToken', function(accounts) {
 
 //*******************New test Block for the already deployed CallMarket contract *************************
 describe('CallMarket', function(accounts) {
-    //this.timeout(0);
+    this.timeout(0);
    
     //*******************Test 1*************************
     it('should deposit tokens from accounst[0] to the CallMarket contract', async() => {
@@ -91,7 +91,7 @@ describe('CallMarket', function(accounts) {
         var array = [];
     
         accounts = await web3.eth.getAccounts();
-        for(let j = 130; j >= 1  ; j--){
+        for(let j = 86; j >= 1  ; j--){
             await CallMarketInstance.submitAsk (j, 1, {from: accounts[0]});
             array.push(j);
         } 
@@ -107,7 +107,7 @@ describe('CallMarket', function(accounts) {
         var array = [];
         
         accounts = await web3.eth.getAccounts();
-        for(let j = 131; j <= 260  ; j++){
+        for(let j = 87; j <= 172  ; j++){
             await CallMarketInstance.submitBid (j, 1, {from: accounts[1]});
             array.push(j);
 
@@ -123,12 +123,12 @@ describe('CallMarket', function(accounts) {
     });
     
     //*******************Test 7*************************
-    it('should return the Gasestimate for the match() function', async() => {
+    // it('should return the Gasestimate for the match() function', async() => {
         
-        const CallMarketInstance = await CallMarket.deployed();
-        const gasEstimate =  await CallMarketInstance.MatchOrders.estimateGas();
-        console.log(gasEstimate); 
-    });  
+    //     const CallMarketInstance = await CallMarket.deployed();
+    //     const gasEstimate =  await CallMarketInstance.MatchOrders.estimateGas();
+    //     console.log(gasEstimate); 
+    // });  
 
     //*******************Test 8*************************
     it('should match the orders', async() => {
@@ -137,9 +137,9 @@ describe('CallMarket', function(accounts) {
 
         const receipt = await  CallMarketInstance.MatchOrders();
         const gasUsed = receipt.receipt.gasUsed;
-        console.log(`GasUsed for openning the market: ${receipt.receipt.gasUsed}`); 
+        console.log(`GasUsed for Matching the orders: ${receipt.receipt.gasUsed}`); 
         
-    }).timeout(9000000000000000000);     
+    });//.timeout(9000000000000000000);     
     
    
     //*******************Test 9*************************

### 2020-08-06 Code/New-Truffle/test/21_Unit_Testing_PQs.js

@@ -1,4 +1,4 @@
-const PQ = artifacts.require('PQ5.sol');
+const PQ = artifacts.require('PQ1.sol');
 var maximum = 200;
 var minimum = 1;
 
@@ -19,15 +19,16 @@ contract('PQ', function(accounts) {
         
         for(let j = 1; j <= 50  ; j++){
 
-            var randomnumber = Math.floor(Math.random() * (maximum - minimum + 1)) + minimum;
-            receipt = await PQInstance.Enqueue (randomnumber);
+            //var randomnumber = Math.floor(Math.random() * (maximum - minimum + 1)) + minimum;
+            //receipt = await PQInstance.Enqueue (randomnumber);
+            receipt = await PQInstance.Enqueue (j);
             const gasUsed = receipt.receipt.gasUsed;
-            //console.log(`GasUsed for a inserting the integer is: ${receipt.receipt.gasUsed}`);
-            console.log(`${receipt.receipt.gasUsed}`);
-            array.push(randomnumber);
-
+            console.log(`GasUsed for a inserting the integer is: ${receipt.receipt.gasUsed}`);
+            //console.log(`${receipt.receipt.gasUsed}`);
+            //array.push(randomnumber);
+            array.push(j);
         } 
-        console.log(array.length,'integers has been succsessfully inserted');
+        console.log(array.length,'integers have been succsessfully inserted');
 
  
     });
@@ -38,8 +39,20 @@ contract('PQ', function(accounts) {
         const gasEstimate =  await PQInstance.Dequeue.estimateGas();
         console.log('Gas Estimate is:', gasEstimate); 
     });  
-    
     //*******************Test 3*************************
+    // it('should give the peek', async() => {
+            
+    //     const PQInstance = await PQ.deployed(); 
+    
+    //     const result = await PQInstance.Peek.call();
+    //     console.log('The peek is', result.toNumber());
+        
+    //     await PQInstance.RemoveMax();
+    //     const result2 = await PQInstance.Peek.call();
+    //     console.log('The peek is', result2.toNumber());
+            
+    // }); 
+    //*******************Test 4*************************
     it('should remove 50 numbers from the list', async() => {
             
         const PQInstance = await PQ.deployed(); 
@@ -49,5 +62,7 @@ contract('PQ', function(accounts) {
         
             
     });   
+    
+    
         
 });

### 2020-08-06 Code/New-Truffle/truffle-config.js

@@ -57,12 +57,8 @@ module.exports = {
     //Using the Ethereum current block gas limit and gas price (ganache-cli --gasLimit=0xB32937 --gasPrice=56000000000)
         gasLimit: 11741495, 
         gasPrice: 56000000000,        // 56 gwei (in wei), Ganache default is 20000000000 (20gwei)
-        gas:6700000,                  // Gas sent with each transaction (default: ~6700000)
-    
-    //for calculating the refund (ganache-cli --gasLimit=0x1fffffffffffff --gasPrice=1)
-        //gasLimit: 9007199254740991,
-        //gasPrice: 1, 
-        //gas:900000000000000,           
+        gas: 11000000,                  // Gas sent with each transaction (default: ~6700000)
+        
     
     //For 1000 orders (ganache-cli --gasLimit=0x1fffffffffffff --gasPrice=1)
         //gasLimit: 9007199254740991,

### 2020-08-06 LaTeX/sections/paper.tex
Update the gas tables values

@@
 Looking more closely, order books are rather electronic ledgers that get updated over time.
-Given the definition of the Etehreum blockchain (\ie a distributed ledger), the idea of implementing an order book in the form of a smart contract will seemingly resolve the existing issues with centralized exchanges.
+Given the definition of the Ethereum blockchain, that is a distributed ledger, the idea of implementing an order book in the form of a smart contract will seemingly resolve the existing issues with centralized exchanges.
 However, this design is not feasible due to some crucial challenges that exist within blockchains:
@@
 \item \textbf{Front-running and Censorship.}
+why cant you front run pt?
 
@@
 
-% = = = = = = = = = = = =Uint testing the PQs Table = = = = = = = = = = = = =  %
+% = = = = = = = = = = = =Uint testing the PQs Table with 50 Random Integers between 1 and 200 = = = = = = = = = = = = =  %
 
@@
 % = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
-	\textbf{\thead{Heap with \\ Dynamic Array}}         				& 2,547,031               & 3,312,378		& 765,347             & 750,000                       \\ \hline
+	\textbf{\thead{Heap with \\ Dynamic Array}}         				& 2,575,997               & 3,349,746		& 773,749             & 750,000                       \\ \hline
 % = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
@@
 \end{tabular}
-\caption{\footnotesize{}
+\caption{\footnotesize{PQUnitTests with 50 Random Integers between 1 and 200}
+\label{tab:PQUnitTests_random}}
+\end{table}
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
+
+% = = = = = = = = = = = =Uint testing the PQs Table with 50 Integers (NOT RANDOM!) = = = = = = = = = = = = =  %
+
+\begin{table}[]
+\centering
+\begin{tabular}{|c|c|c|c|c|}
+\hline
+
+\textbf{\thead{Priority Queue}}    & \textbf{\thead{Net Cost\\in Gas}}      & \textbf{\thead{Total Cost\\in Gas\\(from estimateGas)}}      & \textbf{\thead{Gas Refund \\(from \texttt{estimateGas})}}    & \textbf{\thead{Gas Refund \\(Manually Calculated)}} \\ \hline
+
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
+	\textbf{\thead{Heap with \\ Dynamic Array}}         				& 2,394,202                & 3,159,551           &765,349	    & 750,000                     \\ \hline
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
+	\textbf{\thead{Heap with \\ Static Array}}           				& 1,317,922                & 2,083,240   	& 765,318          & 750,000                     \\ \hline
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
+	\textbf{\thead{Mapping with \\ keys stored \\ in Heap}} 		& 2,629,191                & 4,144,536       	&1,515,345          & 1,500,000                     \\ \hline
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
+	\textbf{Linkedlist}                       							&557,085            		& 1,772,085      	&1,215,000          & 1,200,000                      \\ \hline
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
+	\textbf{\thead{Linkedlist with \\ Mapping}}          				&731,514              	&3,731,514      	& 3,000,000    	  &  3,765,000                       \\ \hline
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
+
+\end{tabular}
+\caption{\footnotesize{PQUnitTests}
 \label{tab:PQ_UnitTests}}
@@
 
+% gas sent with each transaction here is 11,000,000
 %======= estimateGas() function = gasUsed + gasRefund =======%
@@
 % = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
-	\textbf{\thead{Heap with \\ Dynamic Array}}         				& 26 pairs                & 3,274,994                   	& 457,326,935                      \\ \hline
+	\textbf{\thead{Heap with \\ Dynamic Array}}         				& 38 pairs                & 5,372,679                   	& 457,326,935                      \\ \hline
 % = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
-	\textbf{\thead{Heap with \\ Static Array}}           				& 28 pairs                & 3,107,527                  	& 333,656,805                       \\ \hline
+	\textbf{\thead{Heap with \\ Static Array}}           				& 42 pairs                & 5,247,636                  	& 333,656,805                       \\ \hline
 % = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
-	\textbf{\thead{Mapping with \\ keys stored \\ in Heap}} 		& 40 pairs                & 5,414,803                     & 319,481,722                       \\ \hline
+	\textbf{\thead{Mapping with \\ keys stored \\ in Heap}} 		& 46 pairs                & 5,285,275                     & 226,499,722                        \\ \hline
 % = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
-	\textbf{Linkedlist}                       							& 90 pairs                & 3,279,847                      & 35,823,601                        	\\ \hline
+	\textbf{Linkedlist}                       							& 152 pairs                & 5,495,265                     & 35,823,601                        \\ \hline
 % = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
-	\textbf{\thead{Linkedlist with \\ Mapping}}          				& 130 pairs              & 3,297,717                       & 25,095,370                        \\ \hline
+	\textbf{\thead{Linkedlist with \\ Mapping}}          				& 86 pairs                 & 5,433,259                     & 62,774,170                        \\ \hline
 % = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %

### 2020-08-06 LaTeX/sections/paper.tex
Linkedlist/Mapping Section

@@
 
-\item \textbf{Storing the Mapping keys in an Array.} We can create an array that stores the traders' addresses (\ie the mapping keys).
-Knowing the keys enable us to iterate over the mapping and delete individual keys and what they map to at the end of the matching process.
-This is a gas-costly design pattern and would cause a high probability of exceeding the gas limitation inside the \texttt{Match()} function.
+\item \textbf{Storing the Mapping keys in additional Array.} Another common pattern is to create an additional array on top of the mapping and iterate over that.
+This array (\eg address[]) stores the traders' addresses and enables us to iterate over the mapping and delete individual keys and what they map to at the end of the matching process.
+Not that this is a gas-costly design pattern as we would need to maintain a secondary data structure.
 
@@
 % = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
+\section{Design Details of PQs}
+
+\subsection {Linkedlist with Mapping}
+Every a trade happens inside the match function, the best bid and ask order have to be removed from the priority queue.
+There are two different ways to do so; (i) we can only update the head and tail pointers of the linkedlist and/or (ii) we can remove the mapping elements that contain best bid and ask orders from storage completely as well as updating the pointers of the linkedlist.
+\par
+
+Pros and Cons:
+
+Cons: Each order structs contains eight variables of multiple types and removing them from the storage is identical to setting eight variables to zero.
+Despite the gas refunds (\texttt{SSTORE} clear refunds 15.000 gas~\cite{wood2014ethereum}) this would yet increase the gas cost which then lowers down the maximum number of orders the \texttt{Match()} method could handle in this case.
+However, not removing uanessacry data on the Ethereum blockchain is not the best design practice.
+For this reason, we clear the best bid and ask orders every time a trade happens.
 

### 2020-08-07 LaTeX/sections/paper.tex
PQs sections added

--- 2020-08-06 LaTeX/sections/paper.tex
@@
 The most common version of order books is what we call a \textit{double auction}, where market participants submit their bid and ask orders and the market clearing price will be calculated as the average between the best bid and best ask prices.
-Order books often sort the orders based on their price and submission time (this order allocation technique is called price-time priority)~\cite{preis2011price}, where orders are prioritized from highest price to lowest and given any two orders with the same price, they will be sorted based on their submission timestamps.
+Order books often sort orders based on their price and submission time (this order allocation technique is called price-time priority)~\cite{preis2011price}, where orders are prioritized from highest price to lowest and given any two orders with the same price, they will be sorted based on their submission timestamps.
 
@@
 \item \textbf{Front-running and Censorship.}
-why cant you front run pt?
 
@@
 
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
+
 % = = = = = = = = = = = =Clearing Mappings = = = = = = = = = = = = =  %
@@
 
- %Deleting the unavailable mapping remains a challenging issue to solve (have a little section in the paper to discuss our different solutions for it). 
-%	1- we can just create a new mapping everytime the market opens and have a modifier for the claim functions so that they could be called only when the market is closed. 
-%	2- we can have custom keys for the mapping (like a counter we define as a global variable and increment it at the end of the match function).
-So everytime the new market starts, we just use another portion of the mapping.
-%	3- we can have another smart contract which only stores the mapping and just delete that after the close function.
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
 
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
+% = = = = = = = = = = Design Details of PQs = = = = = = = = = = = = = = %
+\section{Design Details of PQs}
 
-% = = = = = = = = = = = =Who pays for the close function? = = = = = = = = = = = = =  %
+%= = = = = =Mapping with Keys Stored in Heap = = = = = = =%
 
-\section{Who Pays the Cost for the \texttt{CloseMarket()} Function?}
+\subsection{Mapping with Keys Stored in a Heap}\label{sec:mapping_heap}
 
-Ethereum contracts can only run when a function is called.
-So if no one calls the \texttt{CloseMarket()} function at the end of the trading period, this function cannot self-execute to modify itself.
-In addition, upon closing the market the \texttt{Match()} function will be executed which consumes a significant amounts of gas, and the person who closes the market must have enough incentives to do so.
+To store the orders, here we use Solidity mapping that map orders' ids (256-bit integers) to order structs with their variables of different types.
+The mapping keys are then stored in a sorted heap that is implemented with a dynamic storage array.
+Every time a trade happens; (i) the mapping keys associated with the best bid and ask orders are deleted from the heap and the heap is re-sorted, and (ii) the mapping elements containing the best bid and ask orders are deleted from storage completely which refund 15000 gas~\cite{wood2014ethereum}.
+Deleting the mapping elements is yet a gas-costly operation which lowers down the maximum number of orders the \texttt{Match()} function could handle in this case.~\footnote{Every order structs contains multiple variables of different types and removing them from storage is identical to setting multiple variables to zero.} However, we clear the mapping element once a trade happens in our design as leaving unnecessary data is not a proper design practice.
+
+%= = = = = =Linkedlist = = = = = = =%
+
+\subsection {Linkedlist}
+Every time a trade happens, we use the \texttt{self-destruct} operation to remove the nodes (\ie smart contracts) containing the best bid and ask orders from the Ethereum blockchain.
+When a node is deleted, it transfers its funds (if any) to the payable address of the CallMarket contract that has been previously passed to it as a constructor argument.
+Also, removing a smart contract from the Ethereum blockchain refunds 24000 gas to the caller.
+
+%= = = = = =Linkedlist with Mapping = = = = = = =%
+
+\subsection {Linkedlist with Mapping}
+Every time a trade happens when the \texttt{Match()} function is executed, the best bid and ask orders need to be removed from the data structures.
+We could do this in two different ways; (i) update the head and tail pointers of the linkedlist and/or (ii) removing the mapping elements that contain the best bid and ask orders from storage completely as well as updating the pointers of the linkedlist.
+\par
+
+For the same reason we mentioned in~\ref{sec:mapping_heap}, we clear the best bid and ask order structs from the mapping every time a trade happens as well as updating the pointers.
+
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
+
+% = = = = = = = = = = = =Closing and Reopening the Market = = = = = = = = = = = = =  %
+
+\section{Closing and Reopening the Market}
+
+% We use one-shot market for the sake of our performance tests on different datastructures. and once we have all the numbers we can think about iterated market.
+
+At the end of the trading period, the market needs to be closed and reopened.
+However, there is no automatic process to called an Ethereum function and contracts can only run when a function is called.
+
+%when to close the market?
+%What time period?
+
+% = = = = = = = = = = = =How to enforce time on on the Ethereum blockchain? = = = = = = = = = = = = =  %
+
+\subsection{Enforcing Time on the Blockchain}
+
+% We want the market to run on a periodic schedule => it is difficult for market participants to call the \texttt{Close()} function periodically.
+
+% However there are incentives for them to do so: (i) they get paid and refunded (financial incentives), and (ii) Closing the market allow market participants to open it again and start their trading activities
+
+% Another solution pattern to enforce the time is to use the Ethereum Alarm Clock
+
+% = = = = = = = = = = = =Who Pays the Cost for Closing and Reopening the Market?= = = = = = = = = = = = =  %
+
+\subsection{Who Pays the Cost for Closing and Reopening the Market?}
+
+%%%%% Mahsa: Add whatever was discussed in the meeting %%%%%
+
 We think it is useful to explore the landscape of possible designs for closing the market.
@@
 \end{enumerate}
+
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
 

### 2020-08-10 LaTeX/sections/paper.tex
Added solutions to close

@@
 
+%= = = = = = Miners Close the Market = = = = = = =%
+
+%Jeremy: Miner could close the market as they get paid and the amount could be more than running the function. 
+\item \textbf {Miners Close and Reopen the Market.} The difference between the best bid and ask prices is called the \textit{bid-ask spread}.
+In our design, when the trade occurs between the the highest bid (the highest amount a buyer is willing to pay for an asset) and lowest ask (the lowest amount a seller is willing to accept for an asset) orders, the bid-ask spread is paid to the miner.
+In addition to this, a miner could close the market and get refunded.
+The refund amount could be potentially higher than the bid-ask spread which provides enough economic incentives for the miner to execute the \texttt{Close()} function.
+
+% = = = = = = = = = =Processing Orders in Groups= = = = = = = = = = = = = = = %
+% Mahsa: Title is good or needs to be changed?
+
+\item \textbf{Processing Orders in Groups.} Another solution pattern is to process certain number of bid and ask orders upon every execution of the \texttt{CloseMarket()} function rather than treating them as one substantial transaction.
+A market participant $P_i$ would process $n$ orders from the previous market (\texttt{CloseMarket(n)}) when sending new orders to the current market.
+This process continues until all the orders in the previous markets are processed.
+% incentive?
+=> contribution to the community!?
+
+%= = = = = =  = =  =  Meta txs =  = = = = = = = = =%
+
 \item \textbf {Using the Meta Transactions.} Meta transactions enable users to execute Ethereum functions without paying the gas.
@@
 
+%= = = = = =  = =  =  Users close and get refunded with the contract funds (collected as fees during order submissions) =  = = = = = = = = =%
+
 \item \textbf{Using the "Contract Pays" Model.} An alternative solution is to design the market such that the last person to submit an order calls the \texttt{CloseMarket()} function, but in contrast to a normal transaction (where the person initiating the transaction must pay the fee), here the CallMarket contract pays the cost for closing the market and matching the orders respectively.
@@
 Again, market participants are charged with certain amounts of fees every time they submit an order, these fees are accumulated in the CallMarket.
-Once the \texttt{CloseMarket} is successfully executed and orders are matched, the contract transfers its funds to that person.
+Once the \texttt{CloseMarket()} is successfully executed and orders are matched, the contract transfers its funds to that person.
 Note that here the person must still have enough gas to cover the execution of the transaction as the funds will be only transferred after the transaction is fully executed.
 However, market participants are incentivized to do so as they may receive more ethers than they have spent.
+
+%= = = = = =  = =  =  Rollups=  = = = = = = = = =%
+
+\item \textbf{Using Rollups.} Rollup is a scaling method that moves the storage and computation of the smart contracts off-chain while maintaining the transaction data on the main chain as call-data.
+In this technique, any Ethereum user can act as a validator; they can execute the \texttt{CloseMarket()}function and only post the new state of the contract (the updated balance of traders) in the form of \textit{assertions} to the main chain.
+Rollups improve scalability, provide faster and cheaper execution of the contracts, and eliminate the gas limit as the contract is no longer executed on-chain.
+In the followings we briefly discuss different rollup proposals and techniques. Each approach uses a different method to ensure correction of assertions:
+
+\begin{itemize}
+
+\item \textbf{{Non-interactive Rollups.}} In this rollup technique, assertions are posted together with a validity proof that would be later used by validators to check if the \texttt{CloseMarket()} function has been executed correctly.
+ZK-Rollup scheme is one of the solutions that uses ZK-SNARKs to prove the validity of the assertions in zero-knowledge.
+ZK proofs are quick and cheap to verify but they are expensive and time consuming to generate.
+These proofs could be generated (i) for free or (ii) we could charge market participants fo them.
+
+\item \textbf{{Optimistic Rollups.}} In this scheme, assertions are assumed to be valid if there is no dispute posted about them with a certain window of time (also known as the challenge period).
+Here, dispute resolution is a gas-costly method as the CallMarket contract would have to emulate the transaction on-chain to ensure the correctness the assertion.
+Also, assertions are publicly available and privacy of data is not protected.
+However, this does not affect our application as the new state only reflects the updated balances of traders and no secret is involved.
+
+\item \textbf {{Multi-round Interactive Rollups.}} In this design paradigm, \textit{pending assertions} are posted on-chain and they are open to dispute.
+Once the challenge period is over and no challenge is submitted, the assertion is confirmed and the CallMarket contract transitions to the new state (\ie updates traders' balances).
+This scheme takes the overhead for the CallMarket contract to execute the \texttt{Close()} on-chain by using rounds to the dispute resolutions.
+The two parties (asserter and challenger) must run an interactive protocol and the CallMarket smart contract would have to act as a referee and decides which party's claim is true.
+Arbitrum is an example of multi-round interactive rollups that uses an efficient challenge-based protocol to penalize the dishonest parties~\cite{kalodner2018arbitrum}.
+
+\end{itemize}
 

### 2020-08-10 LaTeX/sections/paper.tex
Added SGX for closing

@@
 ZK proofs are quick and cheap to verify but they are expensive and time consuming to generate.
-These proofs could be generated (i) for free or (ii) we could charge market participants fo them.
+These proofs could be generated (i) for free or (ii) the CallMarket contract could collect proportional fees for every trade that is successfully executed.
 
-\item \textbf{{Optimistic Rollups.}} In this scheme, assertions are assumed to be valid if there is no dispute posted about them with a certain window of time (also known as the challenge period).
+\item \textbf{{Optimistic Rollups.}} In this scheme, assertions are assumed to be valid if there is no dispute posted about them with a certain window of time (a.k.a.
+"the challenge period').
 Here, dispute resolution is a gas-costly method as the CallMarket contract would have to emulate the transaction on-chain to ensure the correctness the assertion.
@@
 \end{itemize}
+
+%= = = = = =  = =  =  SGX=  = = = = = = = = =%
+\item \textbf{{Using Intel SGX technology.}} Another solution pattern to close the market is to use SGX technology; a trusted execution environment~\cite{anati2013innovative}.
+In this method, the enclave can execute the \texttt{CloseMarket()} function offline and publishes an attestation Quote to the CallMarket contract.
+The contract then verifies the correctness of the Quote and if validated correctly, it transitions to the new state.
 

### 2020-08-11 LaTeX/sections/paper.tex
SGX solution completed

@@
 Here, dispute resolution is a gas-costly method as the CallMarket contract would have to emulate the transaction on-chain to ensure the correctness the assertion.
-Also, assertions are publicly available and privacy of data is not protected.
-However, this does not affect our application as the new state only reflects the updated balances of traders and no secret is involved.
+This scheme introduces a tradeoff between privacy and performance as all the assertions are publicly available and accessible.
+However, here the new state only reflects the updated balances of traders and no secret is involved.
 
@@
 %= = = = = =  = =  =  SGX=  = = = = = = = = =%
-\item \textbf{{Using Intel SGX technology.}} Another solution pattern to close the market is to use SGX technology; a trusted execution environment~\cite{anati2013innovative}.
-In this method, the enclave can execute the \texttt{CloseMarket()} function offline and publishes an attestation Quote to the CallMarket contract.
+
+\item \textbf{{Using Trusted Execution Environments.}} Another way of achieving execution of the \texttt{CloseMarket()} function is incorporating the Ethereum blockchain into the Trusted Execution Environments (TEEs) and decoupling the contract execution from consensus mechanism.
+TEEs enable secure execution of applications in an isolated processing environment called the \textit{enclave}.
+Here, the enclave could execute the \texttt{CloseMarket()} function off-chain in TEEs and publish an on-chain attestation Quote to the CallMarket contract.
 The contract then verifies the correctness of the Quote and if validated correctly, it transitions to the new state.
+Ekiden is an example that uses Intel SGX to solve the scalability and confidentiality issues with the smart contract execution~\cite{cheng2019ekiden}.
+A drawback of this scheme is in order to achieve confidentiality-preserving smart contracts we have to trust a trusted party in the form of the hardware manufacturer (\eg Intel).
 

### 2020-08-12 LaTeX/sections/paper.tex
Updates on the text

@@
 \begin{itemize}
-
+%---------+++++++++++++++++++-----------------
 \item \textbf{Speed.}
 
+%---------+++++++++++++++++++-----------------
 \item \textbf{Front-running and Censorship.}
 
+%---------+++++++++++++++++++-----------------
 \item \textbf{Enforcing Time.}
+
+%---------+++++++++++++++++++-----------------
 
@@
 % = = = = = = = = = = = =Clearing Mappings = = = = = = = = = = = = =  %
+
 \section{Clearing Mappings}
@@
 
+%---------+++++++++++++++++++-----------------
 \item \textbf{Creating a New Mapping Every Time the Market Opens.} Instead of clearing the \texttt{UnavailableBalance} of traders at the end of a matching process, we could create a new mapping every time the market opens.
@@
 
+%---------+++++++++++++++++++-----------------
 \item \textbf{Creating Custom Keys for the Mapping.} We can create custom keys for the mapping by defining a counter as a global variable inside the CallMarket smart contract.
@@
 
+%---------+++++++++++++++++++-----------------
 \item \textbf{Storing the Mapping in a Data-Contract.} Another design proposal is to create a smart contract every time the market opens, this data contract only stores the \texttt{UnavailableBalance} mapping and will be killed at the end of the matching process.
 
-\item \textbf{Storing the Mapping keys in additional Array.} Another common pattern is to create an additional array on top of the mapping and iterate over that.
+%---------+++++++++++++++++++-----------------
+\item \textbf{Storing the Mapping keys in an additional Array.} Another common pattern is to create an additional array on top of the mapping and iterate over that.
 This array (\eg address[]) stores the traders' addresses and enables us to iterate over the mapping and delete individual keys and what they map to at the end of the matching process.
 Not that this is a gas-costly design pattern as we would need to maintain a secondary data structure.
+
+%---------+++++++++++++++++++-----------------
 
@@
 
-%= = = = = =Mapping with Keys Stored in Heap = = = = = = =%
+%---------+++++++++++++++++++-----------------
 
@@
 
-%= = = = = =Linkedlist = = = = = = =%
-
+%---------+++++++++++++++++++-----------------
 \subsection {Linkedlist}
@@
 
-%= = = = = =Linkedlist with Mapping = = = = = = =%
-
+%---------+++++++++++++++++++-----------------
 \subsection {Linkedlist with Mapping}
@@
 \par
-
 For the same reason we mentioned in~\ref{sec:mapping_heap}, we clear the best bid and ask order structs from the mapping every time a trade happens as well as updating the pointers.
@@
 
-% We use one-shot market for the sake of our performance tests on different datastructures. and once we have all the numbers we can think about iterated market.
+% We use one-shot market for the sake of our performance tests on different data structures. and once we have all the numbers we can think about iterated market.
 
@@
 
-%%%%% Mahsa: Add whatever was discussed in the meeting %%%%%
-
 We think it is useful to explore the landscape of possible designs for closing the market.
@@
 
-%Jeremy: Miner could close the market as they get paid and the amount could be more than running the function. 
 \item \textbf {Miners Close and Reopen the Market.} The difference between the best bid and ask prices is called the \textit{bid-ask spread}.
 In our design, when the trade occurs between the the highest bid (the highest amount a buyer is willing to pay for an asset) and lowest ask (the lowest amount a seller is willing to accept for an asset) orders, the bid-ask spread is paid to the miner.
-In addition to this, a miner could close the market and get refunded.
-The refund amount could be potentially higher than the bid-ask spread which provides enough economic incentives for the miner to execute the \texttt{Close()} function.
+There are possibilities that (i) no trade occurs or (ii) the bid-ask spread is zero (\ie the best bid and best ask prices are identical).
+So there is enough economic incentive for the the miner to execute the \texttt{CloseMarket()} function and get refunded as the refund amount could be potentially higher than the bid-ask spread.
 
 % = = = = = = = = = =Processing Orders in Groups= = = = = = = = = = = = = = = %
-% Mahsa: Title is good or needs to be changed?
 

### 2020-08-24 LaTeX/sections/paper.tex
Paper - until PQs

@@
 % !TEX root = ../main.tex
+
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
 
@@
 
-%decentralized exchanges allow the market participants to be fully authoritative over their assets using their private keys. 
-%One issue with decentralized 
-%
-%Cryptocurrency trading on centralized exchanges has been shown to be vulnerable to cybersecurity hacking and internal frauds over the years, with the most infamous hacks being Mt.
-Gox and Coincheck.
-In addition, trading on centralized exchanges is not compatible with DeFi applications since it is technically infeasible to bridge between decentralized applications and centralized servers without compromising the trust model.
+Blockchain is a type of distributed database (or ledger) that is open to anyone who wants to participate, robust against a wide range of faulty and malicious behaviours, and runs without anyone in charge.
+When a participant looks at her local copy of the ledger, she is assured that (i) anyone has the exact same records and (ii) each record was validated by the "majority" (technically, a computational majority) of participants before it was written into the ledger.
+Blockchain technology has rapidly gained global interest and become one of the most significant technologies in recent years.
+It was first introduced in 2008 by Satoshi Nakamoto as an underlying technology of Bitcoin, a peer to peer electronic cash system~\cite{nakamoto2019bitcoin}, whose currency reached a market capitalization of \$137 billion as of January 2020.
+In 2014, a new blockchain based application known as Ethereum was introduced by Buterin~\cite{buterin2014next}.
+By implementing a decentralized virtual machine, Ethereum virtual machine (EVM), Ethereum allows network users to execute programmable smart contracts on it.
+So developers are now able to build decentralized applications (DApps) that are executed correctly according to the consensus rules of the Ethereum network.
+
+\section{Cryptocurrency Exchanges}
+Strong interest in blockchain and distributed ledger technologies has led into the high trading volume of digital assets and emergence of fast growing cryptocurrency exchanges all over the world.
+These crypto exchanges (hereafter referred to as exchanges) are similar to stock exchanges but, as the name suggests, facilitate the trading process of different cryptocurrency tokens.
+Basically, such exchanges provide a trading venue where market participants can buy and/or sell cryptocurrency assets among one another.
+In this section, we describe two types of trading systems and pinpoint why the need for a highly secure exchange and trading system for cryptocurrencies is crucial.
+
+\subsection{Centralized Exchanges (CEX)}\label{sec:CEX}
+This group of exchanges operate in a traditional manner by providing a centralized platform controlled by exchange operators.
+Essentially, the exchange acts as a trusted party whom the market participants must trust to handle their assets.
+Thus, traders transfer the ownership of their assets to the exchange who safeguards customer funds using different methods.
+Although this group of exchanges make it easier for users to trade digital assets (as it takes the burden of safeguarding off traders), it requires traders to fully trust the exchange operator in taking custody of their assets (\eg Coinbase).
+Like any other centralized platform, these exchanges are not completely immune to malicious activities.
+For example, in February 2014, a famous centralized Tokyo-based Bitcoin exchange called MtGox was hacked which led to loss of 650,000 Bitcoins~\cite{TheHisto45:online}.
+Also, a malicious exchange can simply steal users' funds, in February 2019, QuadrigaCX, one of Canada’s well-known centralized cryptocurrency exchanges, claimed that it cannot access to \$190-million worth of customers’ funds~\cite{SEBIOrde83:online}.
+
+\subsection{Decentralized Exchanges (DEX)}
+
+Unlike centralized exchanges, DEXes facilitate a secure automated peer-to-peer trading process on the blockchain (\eg Ethereum) for market participants with no third parties involved, hence solving the problems that are inherent in centralized exchanges.
+They provide a better security and privacy by enabling traders to remain fully authoritative over their funds and personal data.
+With rising of Decentralized Finance (DeFi) or Open Finance movements, the number of DEX platforms on Ethereum have recently exploded and large volume of trading now occurs on DeFi exchanges (\eg Uniswap).~\footnote{https://uniswap.org}
+
+However, building a fully decentralized exchange is associated with high costs and technical complexities and hence remains a big challenge.
+In the following section, we explore the idea of building a decentralized exchange on Ethereum.
 
@@
 
-\par
-
 Looking more closely, order books are rather electronic ledgers that get updated over time.
@@
 %---------+++++++++++++++++++-----------------
-\item \textbf{Speed.}
+\item \textbf{Speed.} All blockchains are slow in comparison with stock markets which move very fast.
+For example, high-frequency trading (HFT), is a trading method that uses active computers to process a large number of trades in fractions of a second.
+However, blockchains are slow-moving as it takes block intervals for transactions to get confirmed.
 
 %---------+++++++++++++++++++-----------------
-\item \textbf{Front-running and Censorship.}
-
-%---------+++++++++++++++++++-----------------
-\item \textbf{Enforcing Time.}
+\item \textbf{Front-running and Censorship.} Traders must broadcast their order messages to the network before they can be placed in the block (\ie order book).
+In such scenario, the privileged nodes and miners can front-run transactions or completely drop (censor) those that are competing with their own~\cite{eskandari2019sok}.
+Also, miners could almost control how the order book gets updated by inserting their own order messages after viewing all other orders and before mining the block .
 
@@
 
+\item \textbf{Enforcing Time.} There is no notion of time on blockchains.
+If two orders arrive at the same price, in the normal world whoever is the first wins.
+However, one cannot enforce the priority of orders in the blockchain space; if Alice is more well-connected to the network, her order gets broadcast better and executed first although she sends it after Bob.
+
+%---------+++++++++++++++++++-----------------
 \end{itemize}
+
+According to these issues blockchains cannot solve this particular problem.
+Many stock exchanges that currently operate on blockchains tackle this issue by using a private network (where not every network participant can be a node or miner) together with a central time-server that establishes the time priority.
+We propose a different method of implementing a fully decentralized exchange using an alternative data structure known as \textit{a call market} or \textit{frequent batch auction} instead of a time-sensitive order book~\cite{clark2014decentralizing}.
 
@@
 
-% = = = = = = = = = = = =Notes Discussed in Meetings = = = = = = = = = = = = =  %
+\section{Call Market}\label{sec:callmarket}
 
-% Our two competitors are Uinswap and Loopring (that uses ZK roll ups):
-% 	1- Uniswap: we can argue that in traditional markets we have various traditional exchanges. Each of these exchanges have different trading rules and designs which work for different traders.
-%	2- Loopring:
-%		2-1: Barrier to entry: In order for a trader to trade specific ERC20 on Loopring, Loopring has to agree to support that token.
-It might not be difficult and they probably approve the token as long as it is standard compliant.
-%		2-2: ZK proofs are quick and cheap to verify but they are expensive and time consuming to generate: (1) now they are generating these proofs for free but later they charge traders for doing that.
-(2) Looping does not probably generate these proofs per every block so the settlement and 				clearing is not happening per block.
-So we have faster clearing and settlement as we clear everything per block.
-% 		2-3: Loopring is non-custodial, meaning that the money moves only when the proofs come, so there is a latency in transferring funds to the traders.
+In this research work, we design and implement a call market on the Ethereum blockchain.
+In our design, time is treated as discrete and not continuous and orders are accumulated over predetermined time intervals and are processed in batch instead of serially in order of receipt.
+The trading day is divided into frequent but discrete time intervals; every time the market opens traders submit their ask and bid order messages.
+These orders are accumulated in a sorted data structure and when the trading period is over, orders are matched against each other.
+Our proposed decentralized exchange is both data structure and token agnostic (traders can trade any token that is ERC20 compliant).
+The upcoming orders are not stored in the Call Market contract, instead they are stored in a priority queue where each element is associated with a priority and is served according to its priority.
+A priority queue can be implemented using many of the data structures that differ in efficiency and costs.
+Our main \textit{Call Market} smart contract is written in 268 lines of Solidity, a high level programming language that is syntactically similar to Java~\cite{Ethereum41:online}, using the Truffle development framework and deployed on Ganache-CLI.
+We used Javascript for testing by leveraging the Mocha testing framework.
+To facilitate a safe exchange among buyers and sellers, we implement the Call Market smart contract in the form of a \textit{collateralized}; for market participants to be able to send bid and/or ask orders, they have to first supply tokens (depending on what ERC20 tokens they aim to trade) as collaterals by calling any of the  \texttt{DepositToken()} or \texttt{DepositEther()} methods.
+The collateralized Call Market acts as a payment guarantee so traders cannot default on payment or delivery of their assets.
 
-% The heap with dynamic array can do 26 pairs of matches at worst case matching whereas Linkedliat does 90 pairs.
-So if we want to cap the orders over 4 PQs, we’re basically increasing the heap size which makes match more expensive for nothing (every time a match happens and the root is deleted the whole heap is reheapified)
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
 
-% There will be no ties as we use 2 counters for buy and sell orders. These counters are concatenated them with the price. So we somehow enforce time priority
+\section{Priority Queues}
 
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
+As mentioned in~\ref{sec:callmarket}, a priority queue can be implemented using different data structures.
+We implemented five different generic priority queues that support four main functions (see Table~\ref{tab:PQ_API}).
+Followings describe each implementation.
+
+% = = = = = = = = = = = =Operations for a generic Priority Queue Table = = = = = = = = = = = = =  %
+\begin{table}[]
+\centering
+\begin{tabular}{|c|c|}
+\hline
+
+\textbf{Method}   & \textbf{Description}    \\ \hline
+
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
+	\textbf{Enqueue()}       				& inserts an element into the priority queue                        \\ \hline
+	\textbf{Dequeue()}					& removes and returns the highest priority element 		\\ \hline
+	\textbf{isEmpty()}						& checks if the priority queue is empty 					\\ \hline
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
+
+\end{tabular}
+\caption{\footnotesize{Operations for a generic Priority Queue}
+\label{tab:PQ_API}}
+\end{table}
+% = = = = = = = = = = = = = = = = = = = = =  = = = = = = = = = = =  = = = = = = = = = == = = =  %
+
+% = = = = = = = = = = = = = = = = = = = = =  = = =% 
+\subsection{Heap with Dynamic Array}
+
+A Heap is a type of binary tree data structure that comes in two forms of a (i) Max-Heap and (ii) Min-Heap.
+All the nodes of tree are in a specific order and the root of the tree always represents the highest priority item of the data structure (the largest and smallest values in the Max-Heap and Min-Heap respectively).
+We implemented a priority queue with a Heap that itself is implemented using Solidity dynamically-sized array.
+% = = = = = = = = = = = = = = = = = = = = =  = = =%
+
+\subsection{Heap with Static Array}
+
+%Here, we implemented a priority queue using the Heap that itself is stored in Solidity static arrays. Every time the priority queue contract i
+
+We enter 50 unsigned integers to the priority queues in random ordering.
+To do so, we use JavaScript \texttt{Math.random()} function to generate pseudo-random integers between 1 and 200.
+Figure~\ref{fig:average_uints_insertion} shows the gas cost variations for entering 50 unsigned integers in the five data structures.
+The x-axis is the place in line (\eg the10th number entered in the priority queue) and the and y-axis is the cost of that transaction in gas.
+
+% = = = = = = = = = = = =average_uints_insertion Figure = = = = = = = = = = = = =  %
+
+\begin{figure}[htb!p]
+\centering
+\includegraphics[width=1\textwidth]{fig/average_uints_insertion.png}
+\caption{\footnotesize{}  \label{fig:average_uints_insertion}}
+\end{figure}
+
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
+
+Then, we call the \texttt{Dequeue()} function which iteratively removes the highest priority number from the priority queue (until the data structure is empty).
+The computational costs for dequeuing 50 unsigned integers in each priority queue are outlined in Table~\ref{tab:PQ_UnitTests}.
+The tests are performed using the current Ethereum gas metrics (block gas limit $=$11,741,495 and 1 gas $=$ 56 gwei)~\footnote{https://ethstats.net/}.
+The second column of the table shows the net gas consumption (the gasUsed value derived from transaction receipts) for removing 50 integers from each priority queues.
+
+At the time of this writing, Ethereum transaction receipts only contain the net gas consumption and not the total gas consumption ( total gas consumption is defined as $gas refunded + gasUsed$ ) and we cannot find out the value of the EVM's refund counter from inside the EVM.
+
+So in order to account for refunds inside each priority queue smart contract, we can calculate them manually; first we figure out exactly how much storage is being cleared when dequeuing  the max integers and then we could multiply the number of storage slots cleared by 15,000 (see the last column of Table~\ref{tab:PQ_UnitTests}).
+
+Another way to know the amount of refund in each priority queue is to use the \texttt{estimateGas API} which provides a rough idea about the total amount of gas that is required for a transaction to go through.
+The \texttt{web3.eth.estimateGas} pretends the transaction is included in the block and its functions (with the parameters passed) will be executed on the Ethereum blockchain.
+Doing so, it provides us an estimate of how much gas is needed to be sent with the transaction.
+The second and third columns of Table~\ref{tab:PQ_UnitTests}) show the total amount of gas required for dequeuing 50 integers from each priority queue (provided by estimateGas) and the amount of gas refund ($Total Gas Consumption - gasUsed$) respectively.
+
+Note that in order to urge miners to process smart contract with refunds, the accumulated gas refund can never exceed half the gas used up during computation~\cite{wood2014ethereum}.
+So at the end of a successful transaction, the amount of gas in the refund counter (capped at half the net gas used) is returned to the caller.
+For example, the amount of gas that has been used when dequeuing 50 integers from the linkedlist with mapping data structure is 731,514 and since $3,000,000 > 731,514/2$, the amount of refund returned to the caller is $731,514/2 = 365,757$.
+
+\section{Unit Testing the Priority Queues}
+
+Here we execute the same JavaScrip test on the five priority queues with an end goal of unit testing them.
+We enter 50 unsigned integers to the priority queues in random ordering.
+To do so, we use JavaScript \texttt{Math.random()} function to generate pseudo-random integers between 1 and 200.
+Figure~\ref{fig:average_uints_insertion} shows the gas cost variations for entering 50 unsigned integers in the five data structures.
+The x-axis is the place in line (\eg the10th number entered in the priority queue) and the and y-axis is the cost of that transaction in gas.
+
+% = = = = = = = = = = = =average_uints_insertion Figure = = = = = = = = = = = = =  %
+
+\begin{figure}[htb!p]
+\centering
+\includegraphics[width=1\textwidth]{fig/average_uints_insertion.png}
+\caption{\footnotesize{}  \label{fig:average_uints_insertion}}
+\end{figure}
+
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
+
+Then, we call the \texttt{Dequeue()} function which iteratively removes the maximum value of the priority queue (until the data structure is empty).
+The computational costs for dequeuing 50 unsigned integers in each priority queue are outlined in Table~\ref{tab:PQ_UnitTests}.
+The tests are performed using the current Ethereum gas metrics (block gas limit $=$11,741,495 and 1 gas $=$ 56 gwei)~\footnote{https://ethstats.net/}.
+The second column of the table shows the net gas consumption (the gasUsed value derived from transaction receipts) for removing 50 integers from each priority queues.
+
+At the time of this writing, Ethereum transaction receipts only contain the net gas consumption and not the total gas consumption ( total gas consumption is defined as $gas refunded + gasUsed$ ) and we cannot find out the value of the EVM's refund counter from inside the EVM.
+
+So in order to account for refunds inside each priority queue smart contract, we can calculate them manually; first we figure out exactly how much storage is being cleared when dequeuing  the max integers and then we could multiply the number of storage slots cleared by 15,000 (see the last column of Table~\ref{tab:PQ_UnitTests}).
+
+Another way to know the amount of refund in each priority queue is to use the \texttt{estimateGas API} which provides a rough idea about the total amount of gas that is required for a transaction to go through.
+The \texttt{web3.eth.estimateGas} pretends the transaction is included in the block and its functions (with the parameters passed) will be executed on the Ethereum blockchain.
+Doing so, it provides us an estimate of how much gas is needed to be sent with the transaction.
+The second and third columns of Table~\ref{tab:PQ_UnitTests}) show the total amount of gas required for dequeuing 50 integers from each priority queue (provided by estimateGas) and the amount of gas refund ($Total Gas Consumption - gasUsed$) respectively.
+
+Note that in order to urge miners to process smart contract with refunds, the accumulated gas refund can never exceed half the gas used up during computation~\cite{wood2014ethereum}.
+So at the end of a successful transaction, the amount of gas in the refund counter (capped at half the net gas used) is returned to the caller.
+For example, the amount of gas that has been used when dequeuing 50 integers from the linkedlist with mapping data structure is 731,514 and since $3,000,000 > 731,514/2$, the amount of refund returned to the caller is $731,514/2 = 365,757$.
+
+% = = = = = = = = = = = =Uint testing the PQs Table with 50 Random Integers between 1 and 200 = = = = = = = = = = = = =  %
+
+\begin{table}[]
+\centering
+\begin{tabular}{|c|c|c|c|c|}
+\hline
+
+\textbf{\thead{Priority Queue}}    & \textbf{\thead{Net Cost\\in Gas}}      & \textbf{\thead{Total Cost\\in Gas\\(from estimateGas)}}      & \textbf{\thead{Gas Refund \\(from \texttt{estimateGas})}}    & \textbf{\thead{Gas Refund \\(Manually Calculated)}} \\ \hline
+
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
+	\textbf{\thead{Heap with \\ Dynamic Array}}         				& 2,575,997               & 3,349,746		& 773,749             & 750,000                       \\ \hline
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
+	\textbf{\thead{Heap with \\ Static Array}}           				& 1,324,856                & 2,090,182     	& 765,326             & 750,000                      \\ \hline
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
+	\textbf{\thead{Mapping with \\ keys stored \\ in Heap}} 		& 2,863,239                & 4,378,584       	& 1,515,345           & 1,500,000                     \\ \hline
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
+	\textbf{Linkedlist}                       							& 557,085               	& 1,772,085      	& 1,215,000           & 1,200,000                      \\ \hline
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
+	\textbf{\thead{Linkedlist with \\ Mapping}}          				& 731,514              	& 3,731,514       	& 3,000,000     	  &  3,765,000                       \\ \hline
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
+
+\end{tabular}
+\caption{\footnotesize{PQUnitTests with 50 Random Integers between 1 and 200}
+\label{tab:PQUnitTests_random}}
+\end{table}
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
+
+% = = = = = = = = = = = =Uint testing the PQs Table with 50 Integers (NOT RANDOM!) = = = = = = = = = = = = =  %
+
+\begin{table}[]
+\centering
+\begin{tabular}{|c|c|c|c|c|}
+\hline
+
+\textbf{\thead{Priority Queue}}    & \textbf{\thead{Net Cost\\in Gas}}      & \textbf{\thead{Total Cost\\in Gas\\(from estimateGas)}}      & \textbf{\thead{Gas Refund \\(from \texttt{estimateGas})}}    & \textbf{\thead{Gas Refund \\(Manually Calculated)}} \\ \hline
+
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
+	\textbf{\thead{Heap with \\ Dynamic Array}}         				& 2,394,202                & 3,159,551           &765,349	    & 750,000                     \\ \hline
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
+	\textbf{\thead{Heap with \\ Static Array}}           				& 1,317,922                & 2,083,240   	& 765,318          & 750,000                     \\ \hline
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
+	\textbf{\thead{Mapping with \\ keys stored \\ in Heap}} 		& 2,629,191                & 4,144,536       	&1,515,345          & 1,500,000                     \\ \hline
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
+	\textbf{Linkedlist}                       							&557,085            		& 1,772,085      	&1,215,000          & 1,200,000                      \\ \hline
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
+	\textbf{\thead{Linkedlist with \\ Mapping}}          				&731,514              	&3,731,514      	& 3,000,000    	  &  3,765,000                       \\ \hline
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
+
+\end{tabular}
+\caption{\footnotesize{PQUnitTests}
+\label{tab:PQ_UnitTests}}
+\end{table}
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
+
+ In order to choose the best priority queue ()
+
+Note that we have to carefully choose a proper implementation as they have different performance and costs. In order to examine 
+In order to examine the cost and performanmc
+
+%In order to enable our Call Market contract to act as an interface with any priority queue, we implemented generic types of priority queues that support four main functions (see Table~\ref{tab:PQ_API}).
+Followings describe each implementation.
 
@@
 \section{Clearing Mappings}
-
-To facilitate a safe exchange among buyers and sellers, we implement the CallMarket smart contract in the form of a \textit{collateralized}; for market participants to be able to send bid and/or ask orders, they have to first supply assets (depending on what asset they aim to trade) as collaterals  by calling any of the  \texttt{DepositToken()} or \texttt{DepositEther()} methods.
-The collateralized CallMarket acts as a payment guarantees and market participants cannot default on payment or delivery of their assets.
 
@@
 
+% = = = = = = = = = = = =Worst Case Matching on Linkedlist With Mapping Table = = = = = = = = = = = = =  %
+
+\begin{table}[]
+\centering
+\begin{tabular}{|c|c|c|c|}
+\hline
+
+\textbf{\thead{Linkedlist with Mapping}}    & \textbf{\thead{Maximum Number \\ of \\ Matched Orders}}      & \textbf{\thead{Net Cost\\in Gas}}          & \textbf{\thead{Net Cost in Gas\\ for \\ 1000 Pairs \\ of Orders}}    \\ \hline
+
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  = = = = = = = = = = = %
+	\textbf{\thead{Clearing the Mapping Elements}}         			& 38 pairs                					& 5,372,679                   				& 457,326,935                      \\ \hline
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  = = = = = = = = = = = %
+	\textbf{\thead{Using the \texttt{Selfdestruct()}}}           			& 210 pairs	                     				& 5,304,211 							& 25,099,713				\\ \hline
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  = = = = = = = = = = = %
+	\textbf{\thead{No On-chain Clearing}} 		                       	& 210 pairs							& 5,299,877							& 25,095,370				\\ \hline
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  = = = = = = = = = = = %
+
+\end{tabular}
+\caption{\footnotesize{}
+\label{tab:worst_case_matching}}
+\end{table}
+
 %%============= Test 3 (17_Worst_Case_Submission_test.js) Figures==================== %
@@
 
+% = = = = = = = = = = = =Notes Discussed in Meetings = = = = = = = = = = = = =  %
+
+% Our two competitors are Uinswap and Loopring (that uses ZK roll ups):
+% 	1- Uniswap: we can argue that in traditional markets we have various traditional exchanges. Each of these exchanges have different trading rules and designs which work for different traders.
+%	2- Loopring:
+%		2-1: Barrier to entry: In order for a trader to trade specific ERC20 on Loopring, Loopring has to agree to support that token.
+It might not be difficult and they probably approve the token as long as it is standard compliant.
+%		2-2: ZK proofs are quick and cheap to verify but they are expensive and time consuming to generate: (1) now they are generating these proofs for free but later they charge traders for doing that.
+(2) Looping does not probably generate these proofs per every block so the settlement and 				clearing is not happening per block.
+So we have faster clearing and settlement as we clear everything per block.
+% 		2-3: Loopring is non-custodial, meaning that the money moves only when the proofs come, so there is a latency in transferring funds to the traders.
+
+% The heap with dynamic array can do 26 pairs of matches at worst case matching whereas Linkedliat does 90 pairs.
+So if we want to cap the orders over 4 PQs, we’re basically increasing the heap size which makes match more expensive for nothing (every time a match happens and the root is deleted the whole heap is reheapified)
+
+% There will be no ties as we use 2 counters for buy and sell orders. These counters are concatenated them with the price. So we somehow enforce time priority
+
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
+
 %======================================== %

### 2020-08-25 LaTeX/sections/paper.tex
Paper - until LL vs LLMapping

@@
 The upcoming orders are not stored in the Call Market contract, instead they are stored in a priority queue where each element is associated with a priority and is served according to its priority.
-A priority queue can be implemented using many of the data structures that differ in efficiency and costs.
 Our main \textit{Call Market} smart contract is written in 268 lines of Solidity, a high level programming language that is syntactically similar to Java~\cite{Ethereum41:online}, using the Truffle development framework and deployed on Ganache-CLI.
-We used Javascript for testing by leveraging the Mocha testing framework.
 To facilitate a safe exchange among buyers and sellers, we implement the Call Market smart contract in the form of a \textit{collateralized}; for market participants to be able to send bid and/or ask orders, they have to first supply tokens (depending on what ERC20 tokens they aim to trade) as collaterals by calling any of the  \texttt{DepositToken()} or \texttt{DepositEther()} methods.
@@
 
-As mentioned in~\ref{sec:callmarket}, a priority queue can be implemented using different data structures.
-We implemented five different generic priority queues that support four main functions (see Table~\ref{tab:PQ_API}).
+ A priority queue can be implemented using many of the data structures that differ in performance and costs.
+In order to choose the appropriate data structure for better performance and costs, we implemented and examined five different generic priority queues that support four main functions (see Table~\ref{tab:PQ_API}).
 Followings describe each implementation.
 
-% = = = = = = = = = = = =Operations for a generic Priority Queue Table = = = = = = = = = = = = =  %
+% = = = = = = = = = = = =Operations for a generic Priority Queue Table = = =  = = = = = = = = = = = %
 \begin{table}[]
@@
 
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
 	\textbf{Enqueue()}       	& inserts an element into the priority queue                        \\ \hline
@@
 	\textbf{isEmpty()}			& checks if the priority queue is empty 					\\ \hline
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
 
@@
 \end{table}
-% = = = = = = = = = = = = = = = = = = = = =  = = = = = = = = = = =  = = = = = = = = = == = = =  %
+% = = = = = = = = = = = = = = = = = = = = =  = = = = = = = = = = =  = = = = = = = = = == = = =  = =%
 
-% = = = = = = = = = = = = = = = = = = = = =  = = =% 
-\subsection{Heap with Dynamic Array}
+\begin{enumerate}
 
-A Heap is a type of binary tree data structure that comes in two forms of a (i) Max-Heap and (ii) Min-Heap.
+%---------+++++++++++++++++++-----------------
+
+\item\textbf{{Heap with Dynamic Array.}} A Heap is a type of binary tree data structure that comes in two forms of a (i) Max-Heap and (ii) Min-Heap.
 All the nodes of tree are in a specific order and the root of the tree always represents the highest priority item of the data structure (the largest and smallest values in the Max-Heap and Min-Heap respectively).
-We implemented a priority queue with a Heap that itself is implemented using Solidity dynamically-sized array.
-% = = = = = = = = = = = = = = = = = = = = =  = = =%
+We implemented a priority queue with a Heap that itself is represented by Solidity dynamically-sized array.
 
-\subsection{Heap with Static Array}
+%---------+++++++++++++++++++-----------------
 
-%Here, we implemented a priority queue using the Heap that itself is stored in Solidity static arrays. Every time the priority queue contract i
+\item\textbf{{Heap with Static Array.}} A Heap can be also represented by a Solidity storage array in which the storage is statically allocated.
+To do this, we pass the required sized of the array as a smart contract constructor parameter.
 
-We enter 50 unsigned integers to the priority queues in random ordering.
-To do so, we use JavaScript \texttt{Math.random()} function to generate pseudo-random integers between 1 and 200.
-Figure~\ref{fig:average_uints_insertion} shows the gas cost variations for entering 50 unsigned integers in the five data structures.
-The x-axis is the place in line (\eg the10th number entered in the priority queue) and the and y-axis is the cost of that transaction in gas.
+%---------+++++++++++++++++++-----------------
 
-% = = = = = = = = = = = =average_uints_insertion Figure = = = = = = = = = = = = =  %
+\item\textbf{{Mapping with keys stored in Heap.}} This priority queue stores items inside a Solidity mapping that maps the mapping keys (256-bit integers) to these items.
+The mapping keys are then stored (based on the value they are mapped to) in a sorted Heap that is implemented with a dynamically-sized array.
+
+%---------+++++++++++++++++++-----------------
+
+\item\textbf{{Linked List.}} Here we used a sorted singly Linked List to implement the priority queue.
+A Linked List is a linear data structure made of a chain of items (also known as nodes) where each item contains a value and a pointer to the next node in the list.
+In our implementation, each node is represented by a smart contract that contains the data and a pointer to its next smart contract in the list.
+
+%---------+++++++++++++++++++-----------------
+
+\item\textbf{{Linked List with Mapping.}} Here we used Solidity mapping to implement our priority queue with a sorted doubly Linked List where every node points to it previous \textbf{and} next node in the list.
+The Linked List entries are first wrapped in an struct data type that contains (i) the unique id of that element, (ii) the unique id of its previous item in the list, and (iii) the unique id of its next item in the list.
+These structs are then stored in the mapping indexed by item id.
+
+%---------+++++++++++++++++++-----------------
+
+\end{enumerate}
+
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
+
+Next, we used Javascript for testing by leveraging the Mocha testing framework and performed our priority queue performance tests.
+We entered 50 pseudo-random integers between 1 and 200 to the priority queues and obtained the associated gas costs.
+Figure~\ref{fig:random_insertion} represents the gas costs variations for entering 50 unsigned integers to the five priority queues; the x-axis is the place in line (\eg the10th number entered in the priority queue) and the and y-axis is the cost of that transaction in gas.
+
+% = = = = = = = = = = = =random_insertion Figure = = = = = = = = = = = = =  %
 
@@
 \centering
-\includegraphics[width=1\textwidth]{fig/average_uints_insertion.png}
-\caption{\footnotesize{}  \label{fig:average_uints_insertion}}
+\includegraphics[width=1\textwidth]{fig/random_insertion.png}
+\caption{\footnotesize{Gas costs for entering 50 items into five different priority queues.}  \label{fig:random_insertion}}
 \end{figure}
@@
 
-Then, we call the \texttt{Dequeue()} function which iteratively removes the highest priority number from the priority queue (until the data structure is empty).
-The computational costs for dequeuing 50 unsigned integers in each priority queue are outlined in Table~\ref{tab:PQ_UnitTests}.
-The tests are performed using the current Ethereum gas metrics (block gas limit $=$11,741,495 and 1 gas $=$ 56 gwei)~\footnote{https://ethstats.net/}.
+Then, we called the \texttt{Dequeue()} function which iteratively removes the highest priority number from the priority queues (until the data structure is empty).
+The computational costs for dequeuing 50 unsigned integers in each priority queue are outlined in Table~\ref{tab:PQUnitTests}.
+These tests are performed using the current Ethereum gas metrics (block gas limit $=$11,741,495 and 1 gas $=$ 56 gwei)~\footnote{https://ethstats.net/}.
 The second column of the table shows the net gas consumption (the gasUsed value derived from transaction receipts) for removing 50 integers from each priority queues.
 
-At the time of this writing, Ethereum transaction receipts only contain the net gas consumption and not the total gas consumption ( total gas consumption is defined as $gas refunded + gasUsed$ ) and we cannot find out the value of the EVM's refund counter from inside the EVM.
-
-So in order to account for refunds inside each priority queue smart contract, we can calculate them manually; first we figure out exactly how much storage is being cleared when dequeuing  the max integers and then we could multiply the number of storage slots cleared by 15,000 (see the last column of Table~\ref{tab:PQ_UnitTests}).
-
-Another way to know the amount of refund in each priority queue is to use the \texttt{estimateGas API} which provides a rough idea about the total amount of gas that is required for a transaction to go through.
-The \texttt{web3.eth.estimateGas} pretends the transaction is included in the block and its functions (with the parameters passed) will be executed on the Ethereum blockchain.
-Doing so, it provides us an estimate of how much gas is needed to be sent with the transaction.
-The second and third columns of Table~\ref{tab:PQ_UnitTests}) show the total amount of gas required for dequeuing 50 integers from each priority queue (provided by estimateGas) and the amount of gas refund ($Total Gas Consumption - gasUsed$) respectively.
-
-Note that in order to urge miners to process smart contract with refunds, the accumulated gas refund can never exceed half the gas used up during computation~\cite{wood2014ethereum}.
-So at the end of a successful transaction, the amount of gas in the refund counter (capped at half the net gas used) is returned to the caller.
-For example, the amount of gas that has been used when dequeuing 50 integers from the linkedlist with mapping data structure is 731,514 and since $3,000,000 > 731,514/2$, the amount of refund returned to the caller is $731,514/2 = 365,757$.
-
-\section{Unit Testing the Priority Queues}
-
-Here we execute the same JavaScrip test on the five priority queues with an end goal of unit testing them.
-We enter 50 unsigned integers to the priority queues in random ordering.
-To do so, we use JavaScript \texttt{Math.random()} function to generate pseudo-random integers between 1 and 200.
-Figure~\ref{fig:average_uints_insertion} shows the gas cost variations for entering 50 unsigned integers in the five data structures.
-The x-axis is the place in line (\eg the10th number entered in the priority queue) and the and y-axis is the cost of that transaction in gas.
-
-% = = = = = = = = = = = =average_uints_insertion Figure = = = = = = = = = = = = =  %
-
-\begin{figure}[htb!p]
-\centering
-\includegraphics[width=1\textwidth]{fig/average_uints_insertion.png}
-\caption{\footnotesize{}  \label{fig:average_uints_insertion}}
-\end{figure}
-
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
-
-Then, we call the \texttt{Dequeue()} function which iteratively removes the maximum value of the priority queue (until the data structure is empty).
-The computational costs for dequeuing 50 unsigned integers in each priority queue are outlined in Table~\ref{tab:PQ_UnitTests}.
-The tests are performed using the current Ethereum gas metrics (block gas limit $=$11,741,495 and 1 gas $=$ 56 gwei)~\footnote{https://ethstats.net/}.
-The second column of the table shows the net gas consumption (the gasUsed value derived from transaction receipts) for removing 50 integers from each priority queues.
-
-At the time of this writing, Ethereum transaction receipts only contain the net gas consumption and not the total gas consumption ( total gas consumption is defined as $gas refunded + gasUsed$ ) and we cannot find out the value of the EVM's refund counter from inside the EVM.
-
-So in order to account for refunds inside each priority queue smart contract, we can calculate them manually; first we figure out exactly how much storage is being cleared when dequeuing  the max integers and then we could multiply the number of storage slots cleared by 15,000 (see the last column of Table~\ref{tab:PQ_UnitTests}).
-
-Another way to know the amount of refund in each priority queue is to use the \texttt{estimateGas API} which provides a rough idea about the total amount of gas that is required for a transaction to go through.
-The \texttt{web3.eth.estimateGas} pretends the transaction is included in the block and its functions (with the parameters passed) will be executed on the Ethereum blockchain.
-Doing so, it provides us an estimate of how much gas is needed to be sent with the transaction.
-The second and third columns of Table~\ref{tab:PQ_UnitTests}) show the total amount of gas required for dequeuing 50 integers from each priority queue (provided by estimateGas) and the amount of gas refund ($Total Gas Consumption - gasUsed$) respectively.
-
-Note that in order to urge miners to process smart contract with refunds, the accumulated gas refund can never exceed half the gas used up during computation~\cite{wood2014ethereum}.
-So at the end of a successful transaction, the amount of gas in the refund counter (capped at half the net gas used) is returned to the caller.
-For example, the amount of gas that has been used when dequeuing 50 integers from the linkedlist with mapping data structure is 731,514 and since $3,000,000 > 731,514/2$, the amount of refund returned to the caller is $731,514/2 = 365,757$.
-
-% = = = = = = = = = = = =Uint testing the PQs Table with 50 Random Integers between 1 and 200 = = = = = = = = = = = = =  %
+% = = = = = = = = = = = =Gas costs and refunds for Dequeueing 50 integers from each PQ  = = = = = = = = = = = = =  %
 
@@
 
-\textbf{\thead{Priority Queue}}    & \textbf{\thead{Net Cost\\in Gas}}      & \textbf{\thead{Total Cost\\in Gas\\(from estimateGas)}}      & \textbf{\thead{Gas Refund \\(from \texttt{estimateGas})}}    & \textbf{\thead{Gas Refund \\(Manually Calculated)}} \\ \hline
+\textbf{\thead{Priority Queue}}    & \textbf{\thead{Net Cost\\in Gas}}      & \textbf{\thead{Total Cost\\in Gas\\(From \texttt{estimateGas})}}      & \textbf{The Difference}    & \textbf{\thead{Gas Refund \\(Manually Calculated)}} \\ \hline
 
 % = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
-	\textbf{\thead{Heap with \\ Dynamic Array}}         				& 2,575,997               & 3,349,746		& 773,749             & 750,000                       \\ \hline
+	\textbf{\thead{Heap with \\ Dynamic Array}}         				& 2,518,131               & 3,283,480		& 765,349             & 750,000                       \\ \hline
 % = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
-	\textbf{\thead{Heap with \\ Static Array}}           				& 1,324,856                & 2,090,182     	& 765,326             & 750,000                      \\ \hline
+	\textbf{\thead{Heap with \\ Static Array}}           				& 1,385,307                & 2,150,625     	& 765,318             & 750,000                      \\ \hline
 % = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
-	\textbf{\thead{Mapping with \\ keys stored \\ in Heap}} 		& 2,863,239                & 4,378,584       	& 1,515,345           & 1,500,000                     \\ \hline
+	\textbf{\thead{Mapping with \\ keys stored \\ in Heap}} 		& 2,781,684                & 4,316,229       	& 1,534,545           & 1,500,000                     \\ \hline
 % = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
-	\textbf{Linkedlist}                       							& 557,085               	& 1,772,085      	& 1,215,000           & 1,200,000                      \\ \hline
+	\textbf{Linked List}                       							& 557,085               	& 1,772,085      	& 1,215,000           & 1,200,000                      \\ \hline
 % = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
-	\textbf{\thead{Linkedlist with \\ Mapping}}          				& 731,514              	& 3,731,514       	& 3,000,000     	  &  3,765,000                       \\ \hline
+	\textbf{\thead{Linked List with \\ Mapping}}          				& 731,514              	& 3,731,514       	& 3,000,000     	  &  3,765,000                       \\ \hline
 % = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
@@
 \end{tabular}
-\caption{\footnotesize{PQUnitTests with 50 Random Integers between 1 and 200}
-\label{tab:PQUnitTests_random}}
+\caption{\footnotesize{The gas metrics associated with dequeuing 50 items from five priority queues.}
+\label{tab:PQUnitTests}}
 \end{table}
@@
 
-% = = = = = = = = = = = =Uint testing the PQs Table with 50 Integers (NOT RANDOM!) = = = = = = = = = = = = =  %
+At the time of this writing, Ethereum transaction receipts only contain the net gas consumption and not the total gas consumption (total gas consumption is defined as $gas refunded + gasUsed$) and we cannot obtain the value of the EVM's refund counter from inside the EVM.
+So in order to account for refunds inside each priority queue smart contract, we can calculate them manually; first we figure out exactly how much storage is being cleared when dequeuing the highest priority elements and then we multiply the number of storage slots cleared by 15,000 (see the last column of Table~\ref{tab:PQUnitTests}).
 
+Another way to obtain the amount of refund in each priority queue is to use the \texttt{estimateGas API} which provides a rough idea about the total amount of gas that is required for a transaction to go through.
+The \texttt{web3.eth.estimateGas} pretends the transaction is included in the block and its functions (with the parameters passed) will be executed on the Ethereum blockchain.
+Doing so, it provides us an estimate of how much gas is needed to be sent with the transaction.
+The third and fourth columns of Table~\ref{tab:PQUnitTests}) show the total amount of gas required for dequeuing 50 integers from each priority queue (provided by estimateGas) and the amount of gas refund ($Total Gas Consumption - gasUsed$) respectively.
+
+Note that in order to urge miners to process smart contract with refunds, the accumulated gas refund can never exceed half the gas used up during computation~\cite{wood2014ethereum}.
+So at the end of a successful transaction, the amount of gas in the refund counter (capped at half the net gas used) is returned to the caller.
+For example, the amount of gas that has been used when dequeuing 50 integers from the linked list with mapping priority queue is 731,514 and since $3,000,000 > 731,514/2$, the amount of refund returned to the caller is $731,514/2 = 365,757$.
+
+Based on our tests results, the \textit{linked list} and \textit{linked list with mapping} priority queues show the best performance in compared to the different heap implementations.
+In the next section, we explore the differences between the two different implementations of the linked list priority queue.
+
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
+
+\subsection{Linked List \textit{vs.} Linked List with Mapping}
+
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
 \begin{table}[]
-\centering
 \begin{tabular}{|c|c|c|c|c|}
 \hline
-
-\textbf{\thead{Priority Queue}}    & \textbf{\thead{Net Cost\\in Gas}}      & \textbf{\thead{Total Cost\\in Gas\\(from estimateGas)}}      & \textbf{\thead{Gas Refund \\(from \texttt{estimateGas})}}    & \textbf{\thead{Gas Refund \\(Manually Calculated)}} \\ \hline
-
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
-	\textbf{\thead{Heap with \\ Dynamic Array}}         				& 2,394,202                & 3,159,551           &765,349	    & 750,000                     \\ \hline
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
-	\textbf{\thead{Heap with \\ Static Array}}           				& 1,317,922                & 2,083,240   	& 765,318          & 750,000                     \\ \hline
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
-	\textbf{\thead{Mapping with \\ keys stored \\ in Heap}} 		& 2,629,191                & 4,144,536       	&1,515,345          & 1,500,000                     \\ \hline
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
-	\textbf{Linkedlist}                       							&557,085            		& 1,772,085      	&1,215,000          & 1,200,000                      \\ \hline
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
-	\textbf{\thead{Linkedlist with \\ Mapping}}          				&731,514              	&3,731,514      	& 3,000,000    	  &  3,765,000                       \\ \hline
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
+\multirow{2}{*}{Gas Metrics}                        							& \multicolumn{2}{c|}{Linked List}           						& \multicolumn{2}{c|}{Linked List with Mapping}     					\\ \cline{2-5} 
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = %
+                                                                						& with \texttt{Self-destruct} 		& without \texttt{Self-destruct}                	& with \texttt{delete} 		& without \texttt{delete}              		\\ \hline                                                                                                                                                                                                                                                          % = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = %
+                   Net Cost in Gas                          					& 557,085                    			& 721,370                     				& 731,514                     	& 334,689                      				\\ \hline
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = %
+\thead{Total Cost in Gas \\ (from \texttt{estimateGas})} 		& 1,772,085                  			& 736,370                  					& 3,731,514                     	& 1,099,689                       				\\ \hline
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = %
+		    The Difference                                             		& 1,215,000                  			& 15,000                      				& 3,000,000                    	& 765,000                       				\\ \hline
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = %
 
 \end{tabular}
-\caption{\footnotesize{PQUnitTests}
-\label{tab:PQ_UnitTests}}
 \end{table}
 % = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
-
- In order to choose the best priority queue ()
-
-Note that we have to carefully choose a proper implementation as they have different performance and costs. In order to examine 
-In order to examine the cost and performanmc
-
-%In order to enable our Call Market contract to act as an interface with any priority queue, we implemented generic types of priority queues that support four main functions (see Table~\ref{tab:PQ_API}).
-Followings describe each implementation.
 
@@
 
-% = = = = = = = = = = = =Uint testing the PQs Table = = = = = = = = = = = = =  %
-
-\section{Unit Testing the Priority Queues}
-
-Here we execute the same JavaScrip test on the five priority queues with an end goal of unit testing them.
-We enter 50 unsigned integers to the priority queues in random ordering.
-To do so, we use JavaScript \texttt{Math.random()} function to generate pseudo-random integers between 1 and 200.
-Figure~\ref{fig:average_uints_insertion} shows the gas cost variations for entering 50 unsigned integers in the five data structures.
-The x-axis is the place in line (\eg the10th number entered in the priority queue) and the and y-axis is the cost of that transaction in gas.
-
-% = = = = = = = = = = = =average_uints_insertion Figure = = = = = = = = = = = = =  %
-
-\begin{figure}[htb!p]
-\centering
-\includegraphics[width=1\textwidth]{fig/average_uints_insertion.png}
-\caption{\footnotesize{}  \label{fig:average_uints_insertion}}
-\end{figure}
-
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
-
-Then, we call the \texttt{Dequeue()} function which iteratively removes the maximum value of the priority queue (until the data structure is empty).
-The computational costs for dequeuing 50 unsigned integers in each priority queue are outlined in Table~\ref{tab:PQ_UnitTests}.
-The tests are performed using the current Ethereum gas metrics (block gas limit $=$11,741,495 and 1 gas $=$ 56 gwei)~\footnote{https://ethstats.net/}.
-The second column of the table shows the net gas consumption (the gasUsed value derived from transaction receipts) for removing 50 integers from each priority queues.
-
-At the time of this writing, Ethereum transaction receipts only contain the net gas consumption and not the total gas consumption ( total gas consumption is defined as $gas refunded + gasUsed$ ) and we cannot find out the value of the EVM's refund counter from inside the EVM.
-
-So in order to account for refunds inside each priority queue smart contract, we can calculate them manually; first we figure out exactly how much storage is being cleared when dequeuing  the max integers and then we could multiply the number of storage slots cleared by 15,000 (see the last column of Table~\ref{tab:PQ_UnitTests}).
-
-Another way to know the amount of refund in each priority queue is to use the \texttt{estimateGas API} which provides a rough idea about the total amount of gas that is required for a transaction to go through.
-The \texttt{web3.eth.estimateGas} pretends the transaction is included in the block and its functions (with the parameters passed) will be executed on the Ethereum blockchain.
-Doing so, it provides us an estimate of how much gas is needed to be sent with the transaction.
-The second and third columns of Table~\ref{tab:PQ_UnitTests}) show the total amount of gas required for dequeuing 50 integers from each priority queue (provided by estimateGas) and the amount of gas refund ($Total Gas Consumption - gasUsed$) respectively.
-
-Note that in order to urge miners to process smart contract with refunds, the accumulated gas refund can never exceed half the gas used up during computation~\cite{wood2014ethereum}.
-So at the end of a successful transaction, the amount of gas in the refund counter (capped at half the net gas used) is returned to the caller.
-For example, the amount of gas that has been used when dequeuing 50 integers from the linkedlist with mapping data structure is 731,514 and since $3,000,000 > 731,514/2$, the amount of refund returned to the caller is $731,514/2 = 365,757$.
-
-% = = = = = = = = = = = =Uint testing the PQs Table with 50 Random Integers between 1 and 200 = = = = = = = = = = = = =  %
-
-\begin{table}[]
-\centering
-\begin{tabular}{|c|c|c|c|c|}
-\hline
-
-\textbf{\thead{Priority Queue}}    & \textbf{\thead{Net Cost\\in Gas}}      & \textbf{\thead{Total Cost\\in Gas\\(from estimateGas)}}      & \textbf{\thead{Gas Refund \\(from \texttt{estimateGas})}}    & \textbf{\thead{Gas Refund \\(Manually Calculated)}} \\ \hline
-
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
-	\textbf{\thead{Heap with \\ Dynamic Array}}         				& 2,575,997               & 3,349,746		& 773,749             & 750,000                       \\ \hline
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
-	\textbf{\thead{Heap with \\ Static Array}}           				& 1,324,856                & 2,090,182     	& 765,326             & 750,000                      \\ \hline
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
-	\textbf{\thead{Mapping with \\ keys stored \\ in Heap}} 		& 2,863,239                & 4,378,584       	& 1,515,345           & 1,500,000                     \\ \hline
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
-	\textbf{Linkedlist}                       							& 557,085               	& 1,772,085      	& 1,215,000           & 1,200,000                      \\ \hline
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
-	\textbf{\thead{Linkedlist with \\ Mapping}}          				& 731,514              	& 3,731,514       	& 3,000,000     	  &  3,765,000                       \\ \hline
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
-
-\end{tabular}
-\caption{\footnotesize{PQUnitTests with 50 Random Integers between 1 and 200}
-\label{tab:PQUnitTests_random}}
-\end{table}
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
-
-% = = = = = = = = = = = =Uint testing the PQs Table with 50 Integers (NOT RANDOM!) = = = = = = = = = = = = =  %
-
-\begin{table}[]
-\centering
-\begin{tabular}{|c|c|c|c|c|}
-\hline
-
-\textbf{\thead{Priority Queue}}    & \textbf{\thead{Net Cost\\in Gas}}      & \textbf{\thead{Total Cost\\in Gas\\(from estimateGas)}}      & \textbf{\thead{Gas Refund \\(from \texttt{estimateGas})}}    & \textbf{\thead{Gas Refund \\(Manually Calculated)}} \\ \hline
-
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
-	\textbf{\thead{Heap with \\ Dynamic Array}}         				& 2,394,202                & 3,159,551           &765,349	    & 750,000                     \\ \hline
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
-	\textbf{\thead{Heap with \\ Static Array}}           				& 1,317,922                & 2,083,240   	& 765,318          & 750,000                     \\ \hline
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
-	\textbf{\thead{Mapping with \\ keys stored \\ in Heap}} 		& 2,629,191                & 4,144,536       	&1,515,345          & 1,500,000                     \\ \hline
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
-	\textbf{Linkedlist}                       							&557,085            		& 1,772,085      	&1,215,000          & 1,200,000                      \\ \hline
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
-	\textbf{\thead{Linkedlist with \\ Mapping}}          				&731,514              	&3,731,514      	& 3,000,000    	  &  3,765,000                       \\ \hline
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
-
-\end{tabular}
-\caption{\footnotesize{PQUnitTests}
-\label{tab:PQ_UnitTests}}
-\end{table}
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
-
 %============= Experiments =================== %
@@
 
-%%============= Test 3 (17_Worst_Case_Submission_test.js) Figures==================== %
-%
-% \subsection{Experiments on \texttt{Submit Order()} Functions}
-%
-%We executed another set of tests on the the five different versions of the CallMarket in which we sent 200 \texttt{SubmitBid} to the CallMarket to simulate two hundred of traders participating in the market.
-These tests were performed in two levels (i) worst case and (ii) average case submissions.
-%%the data structure used for bids and asks is the same and hence the submission plots for 200 submitbids and 200 submitasks. Do we have to mention that here?
-%
-%% = = = = = = = = = = = =Worst_Case_Submission = = = = = = = = = = = = =  %
-%
-%\subsubsection{Worst Case Order Submission}
-%
-%Here each \texttt{SubmitBid()} transaction has a price that is smallest or second-smallest of the transactions after it.
-Doing so, we ensure all the orders move every time a new order is sent to the market.
-Figure~\ref{fig:worst_case_submission} shows the gas cost variations for submitting 200 orders in five versions of the CallMarket.
-The x-axis is the place in line (\eg the 10th person to submit the order) and the and y-axis is the gas cost for sending that transaction.
-%
-%%And conversely each \texttt{SubmitAsk()} transaction has a price that is biggest or second-biggest of the transactions after it
-%
-%% = = = = = = = = = = = =Worst_Case_Submission Figure = = = = = = = = = = = = =  %
-%
-%\begin{figure}[htb!p]
-%\centering
-%\includegraphics[width=1\textwidth]{fig/worst_case_submission_3.png}
-%\caption{\footnotesize{}  \label{fig:worst_case_submission}}
-%\end{figure}
-%
-%% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
-%
-%
-%% = = = = = = = = = = = =Average_Case_Submission = = = = = = = = = = = = =  %
-%
-%\subsubsection{Average Case Order Submission}
-%
-%Here we test the five versions of the CallMarket when 200 bid orders are entered in random ordering.
-To do so, we use JavaScript \texttt{Math.random()} function to generate pseudo-random integers between 1 and 100.
-Figure~\ref{fig:average_case_submission} shows the gas cost variations for submitting 200 orders in five versions of the CallMarket.
-Again the x-axis is the place in line (\eg the10th person to submit the order) and the and y-axis is the gas cost for submitting that transaction.
-%
-%% = = = = = = = = = = = =Average_Case_Submission Figure = = = = = = = = = = = = =  %
-%
-%\begin{figure}[htb!p]
-%\centering
-%\includegraphics[width=1\textwidth]{fig/average_case_submission_3.png}
-%\caption{\footnotesize{}  \label{fig:average_case_submission}}
-%\end{figure}
-%
-%% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
-
 % = = = = = = = = = = = =Notes Discussed in Meetings = = = = = = = = = = = = =  %

### 2020-08-27 LaTeX/sections/paper.tex
Paper- Finished LL vs LLMapping

@@
 In this research work, we design and implement a call market on the Ethereum blockchain.
-In our design, time is treated as discrete and not continuous and orders are accumulated over predetermined time intervals and are processed in batch instead of serially in order of receipt.
-The trading day is divided into frequent but discrete time intervals; every time the market opens traders submit their ask and bid order messages.
+We divide the trading day into frequent but discrete time intervals; every time the market opens traders submit their ask and bid order messages.
 These orders are accumulated in a sorted data structure and when the trading period is over, orders are matched against each other.
-Our proposed decentralized exchange is both data structure and token agnostic (traders can trade any token that is ERC20 compliant).
-The upcoming orders are not stored in the Call Market contract, instead they are stored in a priority queue where each element is associated with a priority and is served according to its priority.
-Our main \textit{Call Market} smart contract is written in 268 lines of Solidity, a high level programming language that is syntactically similar to Java~\cite{Ethereum41:online}, using the Truffle development framework and deployed on Ganache-CLI.
-To facilitate a safe exchange among buyers and sellers, we implement the Call Market smart contract in the form of a \textit{collateralized}; for market participants to be able to send bid and/or ask orders, they have to first supply tokens (depending on what ERC20 tokens they aim to trade) as collaterals by calling any of the  \texttt{DepositToken()} or \texttt{DepositEther()} methods.
-The collateralized Call Market acts as a payment guarantee so traders cannot default on payment or delivery of their assets.
+Our proposed decentralized exchange is both data structure and token agnostic (traders can trade any token that is ERC20 standard compliant).
+The upcoming orders are not stored in the call market contract, instead they are stored in a priority queue where each element is associated with a priority and is served according to its priority.
 
@@
 
+There are two main ways to implement each of the \textit{linked list} and \textit{linked list with mapping} priority queues.
+In this section, we perform a comprehensive comparison between these two with the purpose choosing the proper data structure for implementing the call market.
+
+%---------+++++++++++++++++++-----------------
+
+\subsubsection*{Linked List.} Removing the highest priority element from the list can be done in two ways.
+We can use the \texttt{self-destruct()} operation to remove the head node of the list (\ie smart contract) from the Ethereum blockchain and transfer its funds (if any) to a payable address (\eg the current block miner or the call market contract).
+Although the \texttt{self-destruct()} operation does not remove the initial byte code of the contract from the chain, but it frees up the state storage and refunds 24000 gas to the caller.
+Another design perspective is to only update the head pointer of the linked list and leave the previous head (\ie smart contract) on Ethereum blockchain when removing the highest priority element from the list.
+Although the first technique is a bit more costly (because it adds an extra operation \texttt{self-destruct()} to the \texttt{dequeue()} function), it results the in the less final net cost due to the 24000 gas refunds.
+Also, it is best to avoid storing unnecessary storage variables on chain.
+Table~\ref{tab:LLvsLLMapping} outlines different gas metrics for iteratively dequeuing the highest priority element from the two implementations of sorted linked lists that contain 50 unsigned integers.
+
+%---------+++++++++++++++++++-----------------
+
+\subsubsection*{Linked List with Mapping.} Similarly, linked list with mapping can be implemented in two ways.
+For dequeuing items from this priority queue we can use the \texttt{delete()} method and remove the mapping element that contains the highest priority item from storage completely  \textbf{and} update the head and tail pointers of the list.
+Deleting a storage variable is identical to setting a non-zero variable to zero (\texttt{SSTORE} 0) and costs in 5000 gas.
+So although the \texttt{delete()} method refunds in 15000 gas~\cite{wood2014ethereum}, it is yet a gas-costly operation  as it increases the overall gas cost of the transaction.
+In another technique, we can only update the head and tail pointers of the linked list when dequeueing the highest priority items and not delete the mapping element associated with the previous pointers.
+As it can be seen in Table~\ref{tab:LLvsLLMapping}, this scheme consumes less gas to dequeue 50 unsigned integers from this priority queue with respect to the previous technique where we clear up the chain, however, leaving unnecessary storage data on chain is not a proper design practice.
+
 % = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
@@
 % = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = %
-                                                                						& with \texttt{Self-destruct} 		& without \texttt{Self-destruct}                	& with \texttt{delete} 		& without \texttt{delete}              		\\ \hline                                                                                                                                                                                                                                                          % = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = %
+                                                                						& with \texttt{Self-destruct()} 		& without \texttt{Self-destruct()}                	& with \texttt{delete} 		& without \texttt{delete}              		\\ \hline                                                                                                                                                                                                                                                          % = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = %
                    Net Cost in Gas                          					& 557,085                    			& 721,370                     				& 731,514                     	& 334,689                      				\\ \hline
@@
 \end{tabular}
+\caption{\footnotesize{}
+\label{tab:LLvsLLMapping}}
 \end{table}
 % = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
+
+Based on Table~\ref{tab:LLvsLLMapping}, the linked list with \texttt{Self-destruct()} appears to be a good candidate for the call market implementation.
+However, as it can be seen in Figure~\ref{fig:random_insertion}, the associated cost for inserting elements into this priority queue is significantly greater than the linked list with mapping as insertion is identical to creating new contracts.
+Accordingly, we choose to implement the call market with the linked list with mapping that uses the  the \texttt{delete()} method to clear up the chain every time the highest priority element is removed from the list.
+In overall this priority queue introduces a moderate gas cost for both insertion (\ie order submission) and removal (\ie matching the orders).
+
+% = = = = = = = = = = = = = Experimentations = = = = = = = = = = = = = = = = = = =  %
+
+\section{Experimentations}
+
+As mentioned in~\ref{sec:callmarket}, Our system treats the time as discrete and not continuous; upcoming orders are accumulated over predetermined time intervals and are processed in batch instead of serially in order of receipt.
+The trading day is divided into frequent but discrete time intervals; every time the market opens traders submit their ask and bid order messages.
+These orders are accumulated in a linked list with mapping priority queue and when the trading period is over, orders are matched against each other.
+The call market smart contract is written in 268 lines of Solidity, a high level programming language that is syntactically similar to Java~\cite{Ethereum41:online}, using the Truffle development framework and deployed on Ganache-CLI.
+To facilitate a safe exchange among buyers and sellers, we implement the Call Market smart contract in the form of a \textit{collateralized}; for market participants to be able to send bid and/or ask orders, they have to first supply tokens (depending on what ERC20 tokens they aim to trade) as collaterals by calling any of the  \texttt{DepositToken()} or \texttt{DepositEther()} methods.
+The collateralized call market acts as a payment guarantee so traders cannot default on payment or delivery of their assets.
+ We used Javascript for testing by leveraging the Mocha testing framework. Followings outline the results of different tests we performed.
+
+%============= Test 1 (17_Worst_Case_Matching_test.js) Tables=================== %
+
+ \subsection{Experiments on the \texttt{Match()} Function}
+
+We executed the same test on the the five different versions of the CallMarket we implemented using five priority queues to examine the cost of the \texttt{Match()} function as well as the maximum pairs of bid and ask orders it can handle in each case.
+The \texttt{Match()} function's computational cost and the maximum number of orders it can execute in each case (before running out of gas) are outlined in Table~\ref{tab:worst_case_matching}.
+Note that this is a \textit{worst case matching} test where all bids and asks are submitted as marketable limit orders with specified prices that would be filled undoubtedly, performed using the current Ethereum gas metrics (block gas limit $=$11,741,495 and 1 gas $=$ 56 gwei)~\footnote{https://ethstats.net/}.
+The last column of Table~\ref{tab:worst_case_matching} shows the gas cost of matching 1000 pairs of bids and asks for each priority queue for which we set the block gas limit to the maximum of  $2^{53}$ (the Javascript's max safe integer).
 
@@
 % gas sent with each transaction here is 11,000,000
-%======= estimateGas() function = gasUsed + gasRefund =======%
-
-% Heap with Dynamic Array: match.estimateGas() = 7204994 => gasRefund = 7204994 - 3274994 = 3930000
-% Heap with Static Array: match.estimateGas() = 7337527 => gasRefund = 7337527 - 3107527 = 4230000
-% Mapping with keys stored in Heap: match.estimateGas() = 6644803 => gasRefund = 6644803 - 5414803 = 1230000
-% Linkedlist: match.estimateGas() = 7629847 => gasRefund = 7629847 -  3279847 = 4350000
-% Linkedlist with Mapping: match.estimateGas() = 7227717 => gasRefund = 7227717 -  3297717 = 3930000
 

### 2020-08-27 LaTeX/sections/paper.tex
Paper- callmarket completed (might have to totally change the gas section)

@@
 
-\textbf{Method}   & \textbf{Description}    \\ \hline
+\textbf{Operation}   & \textbf{Description}    \\ \hline
 
@@
 \end{tabular}
-\caption{\footnotesize{Operations for a generic Priority Queue}
+\caption{\footnotesize{Operations for a generic Priority Queue.}
 \label{tab:PQ_API}}
@@
 
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
+% A little explanation on gas metrics (Mahsa: please let me know if this is still unclear:)
+
+%First let's take a look at the following example:
+
+%Suppose we have a smart contract which uses up 14,000 gas. The gas limit that we have set up is 20,000 gas. The smart contract also includes an SSTORAGE command.
+%So, how much gas will the contract creator get back post computation?
+%Firstly, they will get back (20,000-14,000) = 6,000 units of unused gas.
+%Now, the SSTORAGE command has also been used, so theoretically they should get back 15,000 gas as well.
+%However, the amount of gas that has been used in the contract is 14,000 and since 15,000 > 14,000/2, the REFUND generated will be 14,000/2= 7000.
+%So the total gas that the creator is getting back in the end is 6000+7000 = 13,000.
+
+% +++++++++++++%
+% so in our case, let's take the first row of the above table:
+
+%The transaction consumes 2,518,131 gas
+%The gas limit is set up at  11,741,495
+%Firstly, they sender get back (11,741,495 - 2,518,13) = 9,223,364 units of unused gas.
+%However, the amount of gas that has been used in the contract is 2,518,131 and since 9,223,364 >2,518,131/2, the REFUND generated will be 2,518,131/2= 1,259,065.
+%
+%The total gas cost of transaction estimated by estimateGas is 3,283,480 
+%estimateGas - gasUsed = gasRefund => 3,283,480 - 2,518,131 = 765,349
+%
+%So we can argue that the estimateGas() gives us an approximate total cost of the transaction and it contains the capped refund counter.
+
+% error in estimateGas:  
+%   https://ethereum.stackexchange.com/questions/266/what-are-the-limitations-to-estimategas-and-when-would-its-estimate-be-considera
+%   https://github.com/trufflesuite/ganache-core/issues/26
+
+%from solidity readdocs: estimateGas Will call estimate the gas a method execution will take when executed in the EVM without.
+The estimation can differ from the actual gas used when later sending a transaction, as the state of the smart contract can be different at that time.
+% estimateGas works by pretending the transaction was actually being included in the blockchain, and then returning the exact gas amount that would have been charged if that pretend operation was real.
+In other words, it uses the exact same procedure a miner would use to calculate the actual fee.
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
+
 Based on our tests results, the \textit{linked list} and \textit{linked list with mapping} priority queues show the best performance in compared to the different heap implementations.
@@
 \subsubsection*{Linked List.} Removing the highest priority element from the list can be done in two ways.
-We can use the \texttt{self-destruct()} operation to remove the head node of the list (\ie smart contract) from the Ethereum blockchain and transfer its funds (if any) to a payable address (\eg the current block miner or the call market contract).
+We can use the \texttt{self-destruct()} operation to destroy the head node of the list (\ie smart contract) from the Ethereum blockchain and transfer its funds (if any) to a payable address (\eg the current block miner or the call market contract).
 Although the \texttt{self-destruct()} operation does not remove the initial byte code of the contract from the chain, but it frees up the state storage and refunds 24000 gas to the caller.
@@
 These orders are accumulated in a linked list with mapping priority queue and when the trading period is over, orders are matched against each other.
-The call market smart contract is written in 268 lines of Solidity, a high level programming language that is syntactically similar to Java~\cite{Ethereum41:online}, using the Truffle development framework and deployed on Ganache-CLI.
+The call market smart contract is written in 268 lines of Solidity, a high level programming language that is syntactically similar to Java~\cite{Ethereum41:online}, using the Truffle development framework and deployed on Ganache-CLI, Table~\ref{tab:callmarket_functions} represents the call market's primary operations.
+
+% = = = = = = = = = = = = = = = = = = = = =Call market operations Table = = = = = = = = = = = =  = = = = = =  %
+\begin{table}[]
+\begin{tabular}{|l|l|}
+\hline
+\multicolumn{1}{|c|}{\textbf{Operation}} & \multicolumn{1}{c|}{\textbf{Description}}                            			\\ \hline
+
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
+	DepositToken()                           & Deposits ERC20 standard compliant tokens in the call market contract \\ \hline
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
+	DepositEther()                           	& Deposits Ethers in the call market contract                         			 \\ \hline
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
+	OpenMarket()                             & Opens the market                                                    					 \\ \hline
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
+	CloseMarket()                            & Closes the market                                                    					\\ \hline
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
+	SubmitBid()                              & Inserts the upcoming bid order messages inside the priority queue    \\ \hline
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
+	SubmitAsk()                              & Inserts the upcoming ask order messages inside the priority queue    \\ \hline
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
+	MatchOrders()                           & Matches the orders against each other                                			\\ \hline
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
+	ClaimTokens()                           & Transfers collateral tokens back to the trader                       			\\ \hline
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
+	ClaimEther()                             & Transfers collateral Ethers back to the trader                       			\\ \hline
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
+\end{tabular}
+\caption{\footnotesize{Primary operations of the call market smart contract.}
+\label{tab:callmarket_functions}}
+\end{table}
+
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
+
 To facilitate a safe exchange among buyers and sellers, we implement the Call Market smart contract in the form of a \textit{collateralized}; for market participants to be able to send bid and/or ask orders, they have to first supply tokens (depending on what ERC20 tokens they aim to trade) as collaterals by calling any of the  \texttt{DepositToken()} or \texttt{DepositEther()} methods.
 The collateralized call market acts as a payment guarantee so traders cannot default on payment or delivery of their assets.
- We used Javascript for testing by leveraging the Mocha testing framework. Followings outline the results of different tests we performed.
 
-%============= Test 1 (17_Worst_Case_Matching_test.js) Tables=================== %
+Followings outline results of the experiments we performed using Javascript and leveraging Mocha testing framework.
 
- \subsection{Experiments on the \texttt{Match()} Function}
+%============= Worst_Case_Matching_test.js Tables=================== %
 
-We executed the same test on the the five different versions of the CallMarket we implemented using five priority queues to examine the cost of the \texttt{Match()} function as well as the maximum pairs of bid and ask orders it can handle in each case.
-The \texttt{Match()} function's computational cost and the maximum number of orders it can execute in each case (before running out of gas) are outlined in Table~\ref{tab:worst_case_matching}.
+ \subsection{Experiments}
+
+%  = = = = = = = = = = %
+
+Table~\ref{tab:worst_case_matching} outlines the \texttt{Match()} function's computational costs and performance for three different implementations of the call market.
+We used three different designs of the linked list with mapping priority queue.
+(1) Every time a trade happens, we use the \texttt{delete()} method to remove the mapping elements that contains best bid and ask orders item from storage completely \textbf{and} update the head and tail pointers of the list.
+(2) We only update the pointers of the priority queue and do not remove the best bid and ask orders during the entire matching process.
+Instead we destroy the priority queue smart contract~\footnote{We execute a public function defined in the priority queue smart contract which itself calls the \texttt{self-destruct()} operation and transfers its funds (if any) to the call market contract.} once the matching is completed.
+(3) In the last implementation, we allow the matching process to be completed and do not clear any on chain data.
+As it can be seen in Table~\ref{tab:worst_case_matching}, the \texttt{Match()} operatin shows a better performance when killing the priority contract and/or not clearing data from the chain.
+Although deleting the priority queue contract adds an extra external call to the \texttt{Match()} function and should technically increase the gas cost, the 24000 gas refunds from \texttt{selfdestruct()} would compensate the cost.
+So it can still match as same number of orders (before running out of gas)as in the no on chain clearing implementation.
+The last column of Table~\ref{tab:worst_case_matching} reflects the gas cost for matching 1000 pairs of bids and asks for which we set the block gas limit to the maximum of  $2^{53}$ (the Javascript's max safe integer).
+
 Note that this is a \textit{worst case matching} test where all bids and asks are submitted as marketable limit orders with specified prices that would be filled undoubtedly, performed using the current Ethereum gas metrics (block gas limit $=$11,741,495 and 1 gas $=$ 56 gwei)~\footnote{https://ethstats.net/}.
-The last column of Table~\ref{tab:worst_case_matching} shows the gas cost of matching 1000 pairs of bids and asks for each priority queue for which we set the block gas limit to the maximum of  $2^{53}$ (the Javascript's max safe integer).
+
+% = = = = = = = = = = = =Worst Case Matching on Linkedlist With Mapping Table = = = = = = = = = = = = =  %
+
+\begin{table}[]
+\centering
+\begin{tabular}{|c|c|c|c|}
+\hline
+
+\textbf{\thead{Linked List with Mapping}}    & \textbf{\thead{Maximum Number \\ of \\ Matched Orders}}      & \textbf{\thead{Net Cost\\in Gas}}          & \textbf{\thead{Net Cost in Gas\\ for \\ 1000 Pairs \\ of Orders}}    \\ \hline
+
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  = = = = = = = = = = = %
+	\textbf{\thead{Clearing the Mapping Elements}}         			& 38 pairs                					& 5,372,679                   				& 457,326,935                      \\ \hline
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  = = = = = = = = = = = %
+	\textbf{\thead{Deleting the Priority Queue Contract}}           	& 210 pairs	                     				& 5,304,211 							& 25,099,713				\\ \hline
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  = = = = = = = = = = = %
+	\textbf{\thead{No On-chain Clearing}} 		                       	& 210 pairs							& 5,299,877							& 25,095,370				\\ \hline
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  = = = = = = = = = = = %
+
+\end{tabular}
+\caption{\footnotesize{}
+\label{tab:worst_case_matching}}
+\end{table}
+
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
+
+%  = = = = = = = = = = % 
+%Mahsa: Im not sure which of these tables are good for this section!?
+%  = = = = = = = = = = %
+
+% = = = = = = = = = = = =Worst_Case_Matching Table = = = = = = = = = = = = =  %
+
+\begin{table}[]
+\centering
+\begin{tabular}{|c|c|c|c|}
+\hline
+
+\textbf{\thead{Priority Queue}}    & \textbf{\thead{Maximum Number \\ of \\ Matched Orders}}      & \textbf{\thead{Net Cost\\in Gas}}          & \textbf{\thead{Net Cost in Gas\\ for \\ 1000 Pairs \\ of Orders}} \\ \hline
+
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
+	\textbf{\thead{Heap with \\ Dynamic Array}}         				& 38 pairs                & 5,372,679                   	& 457,326,935                      \\ \hline
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
+	\textbf{\thead{Heap with \\ Static Array}}           				& 42 pairs                & 5,247,636                  	& 333,656,805                       \\ \hline
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
+	\textbf{\thead{Mapping with \\ keys stored \\ in Heap}} 		& 46 pairs                & 5,285,275                     & 226,499,722                        \\ \hline
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
+	\textbf{Linkedlist}                       							& 152 pairs                & 5,495,265                     & 35,823,601                        \\ \hline
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
+	\textbf{\thead{Linkedlist with \\ Mapping}}          				& 86 pairs                 & 5,433,259                     & 62,774,170                        \\ \hline
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
+
+\end{tabular}
+\caption{\footnotesize{}
+\label{tab:worst_case_matching}}
+\end{table}
 
@@
 
-%============= Experiments =================== %
-\section{Experiments}
-
-Our application was developed in Solidity using the Truffle development framework and deployed on Ganache-CLI.
-We used Javascript for testing by leveraging the Mocha testing framework.
-Followings outline the results of different tests we performed.
-
-%============= Test 1 (17_Worst_Case_Matching_test.js) Tables=================== %
-
- \subsection{Experiments on the \texttt{Match()} Function}
-
-We executed the same test on the the five different versions of the CallMarket we implemented using five priority queues to examine the cost of the \texttt{Match()} function as well as the maximum pairs of bid and ask orders it can handle in each case.
-The \texttt{Match()} function's computational cost and the maximum number of orders it can execute in each case (before running out of gas) are outlined in Table~\ref{tab:worst_case_matching}.
-Note that this is a \textit{worst case matching} test where all bids and asks are submitted as marketable limit orders with specified prices that would be filled undoubtedly, performed using the current Ethereum gas metrics (block gas limit $=$11,741,495 and 1 gas $=$ 56 gwei)~\footnote{https://ethstats.net/}.
-The last column of Table~\ref{tab:worst_case_matching} shows the gas cost of matching 1000 pairs of bids and asks for each priority queue for which we set the block gas limit to the maximum of  $2^{53}$ (the Javascript's max safe integer).
-
-% gas sent with each transaction here is 11,000,000
-
-%===============================================%
-
-% = = = = = = = = = = = =Worst_Case_Matching Table = = = = = = = = = = = = =  %
-
-\begin{table}[]
-\centering
-\begin{tabular}{|c|c|c|c|}
-\hline
-
-\textbf{\thead{Priority Queue}}    & \textbf{\thead{Maximum Number \\ of \\ Matched Orders}}      & \textbf{\thead{Net Cost\\in Gas}}          & \textbf{\thead{Net Cost in Gas\\ for \\ 1000 Pairs \\ of Orders}} \\ \hline
-
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
-	\textbf{\thead{Heap with \\ Dynamic Array}}         				& 38 pairs                & 5,372,679                   	& 457,326,935                      \\ \hline
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
-	\textbf{\thead{Heap with \\ Static Array}}           				& 42 pairs                & 5,247,636                  	& 333,656,805                       \\ \hline
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
-	\textbf{\thead{Mapping with \\ keys stored \\ in Heap}} 		& 46 pairs                & 5,285,275                     & 226,499,722                        \\ \hline
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
-	\textbf{Linkedlist}                       							& 152 pairs                & 5,495,265                     & 35,823,601                        \\ \hline
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
-	\textbf{\thead{Linkedlist with \\ Mapping}}          				& 86 pairs                 & 5,433,259                     & 62,774,170                        \\ \hline
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
-
-\end{tabular}
-\caption{\footnotesize{}
-\label{tab:worst_case_matching}}
-\end{table}
-
-% = = = = = = = = = = = =Worst Case Matching on Linkedlist With Mapping Table = = = = = = = = = = = = =  %
-
-\begin{table}[]
-\centering
-\begin{tabular}{|c|c|c|c|}
-\hline
-
-\textbf{\thead{Linkedlist with Mapping}}    & \textbf{\thead{Maximum Number \\ of \\ Matched Orders}}      & \textbf{\thead{Net Cost\\in Gas}}          & \textbf{\thead{Net Cost in Gas\\ for \\ 1000 Pairs \\ of Orders}}    \\ \hline
-
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  = = = = = = = = = = = %
-	\textbf{\thead{Clearing the Mapping Elements}}         			& 38 pairs                					& 5,372,679                   				& 457,326,935                      \\ \hline
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  = = = = = = = = = = = %
-	\textbf{\thead{Using the \texttt{Selfdestruct()}}}           			& 210 pairs	                     				& 5,304,211 							& 25,099,713				\\ \hline
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  = = = = = = = = = = = %
-	\textbf{\thead{No On-chain Clearing}} 		                       	& 210 pairs							& 5,299,877							& 25,095,370				\\ \hline
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  = = = = = = = = = = = %
-
-\end{tabular}
-\caption{\footnotesize{}
-\label{tab:worst_case_matching}}
-\end{table}
-
 % = = = = = = = = = = = =Notes Discussed in Meetings = = = = = = = = = = = = =  %

### 2020-08-28 LaTeX/sections/paper.tex
Paper- Changed the tables and the texts related to estimategas completely

@@
 \centering
-\begin{tabular}{|c|c|c|c|c|}
+\begin{tabular}{|c|c|c|}
 \hline
 
-\textbf{\thead{Priority Queue}}    & \textbf{\thead{Net Cost\\in Gas}}      & \textbf{\thead{Total Cost\\in Gas\\(From \texttt{estimateGas})}}      & \textbf{The Difference}    & \textbf{\thead{Gas Refund \\(Manually Calculated)}} \\ \hline
+\textbf{\thead{Priority Queue}}    & \textbf{\thead{Net Cost in Gas\\ (\texttt{gasUsed})}}             & \textbf{\thead{Gas Refunds from Deleting a Storage\\(Manually Calculated)}} \\ \hline
 
 % = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
-	\textbf{\thead{Heap with \\ Dynamic Array}}         				& 2,518,131               & 3,283,480		& 765,349             & 750,000                       \\ \hline
+	\textbf{\thead{Heap with \\ Dynamic Array}}         				& 2,518,131            		      & 750,000                       \\ \hline
 % = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
-	\textbf{\thead{Heap with \\ Static Array}}           				& 1,385,307                & 2,150,625     	& 765,318             & 750,000                      \\ \hline
+	\textbf{\thead{Heap with \\ Static Array}}           				& 1,385,307                             & 750,000                      \\ \hline
 % = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
-	\textbf{\thead{Mapping with \\ keys stored \\ in Heap}} 		& 2,781,684                & 4,316,229       	& 1,534,545           & 1,500,000                     \\ \hline
+	\textbf{\thead{Mapping with \\ keys stored \\ in Heap}} 		& 2,781,684                            & 1,500,000                     \\ \hline
 % = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
-	\textbf{Linked List}                       							& 557,085               	& 1,772,085      	& 1,215,000           & 1,200,000                      \\ \hline
+	\textbf{Linked List}                       							& 557,085               	           & 1,200,000                      \\ \hline
 % = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
-	\textbf{\thead{Linked List with \\ Mapping}}          				& 731,514              	& 3,731,514       	& 3,000,000     	  &  3,765,000                       \\ \hline
+	\textbf{\thead{Linked List with \\ Mapping}}          				& 731,514              	     	  &  3,765,000                       \\ \hline
 % = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
@@
 
-At the time of this writing, Ethereum transaction receipts only contain the net gas consumption and not the total gas consumption (total gas consumption is defined as $gas refunded + gasUsed$) and we cannot obtain the value of the EVM's refund counter from inside the EVM.
-So in order to account for refunds inside each priority queue smart contract, we can calculate them manually; first we figure out exactly how much storage is being cleared when dequeuing the highest priority elements and then we multiply the number of storage slots cleared by 15,000 (see the last column of Table~\ref{tab:PQUnitTests}).
+At the time of this writing, Ethereum transaction receipts only contain the net gas consumption (\texttt{gasUsed}) and we cannot obtain the value of the EVM's refund counter from inside the EVM~\cite{signer2018gas}.
+So in order to account for refunds inside each priority queue smart contract we calculate them manually; first we figure out exactly how much storage is being cleared when dequeuing the highest priority elements (\texttt{SSTORE} instruction) and then we multiply the number of storage slots cleared by 15,000 (see the last column of Table~\ref{tab:PQUnitTests}).
 
-Another way to obtain the amount of refund in each priority queue is to use the \texttt{estimateGas API} which provides a rough idea about the total amount of gas that is required for a transaction to go through.
-The \texttt{web3.eth.estimateGas} pretends the transaction is included in the block and its functions (with the parameters passed) will be executed on the Ethereum blockchain.
-Doing so, it provides us an estimate of how much gas is needed to be sent with the transaction.
-The third and fourth columns of Table~\ref{tab:PQUnitTests}) show the total amount of gas required for dequeuing 50 integers from each priority queue (provided by estimateGas) and the amount of gas refund ($Total Gas Consumption - gasUsed$) respectively.
+Note that in order to urge miners to process smart contracts with refunds, the accumulated gas refund can never exceed half the gas used up during computation~\cite{wood2014ethereum}.
+So at the end of a successful transaction, the amount of gas in the refund counter (capped at half the net gas used) is returned to the caller.
+Let's take a closer look at the last row of Table~\ref{tab:PQUnitTests}; gas that has been used for dequeuing 50 integers from the linked list with mapping priority queue is 731,514 and the gas limit has been set up to 11,741,495.
+Firstly, the caller will receive $(11,741,495 - 731,514) = 11,009,981$ units of unused gas.
+Also, the amount of refund we manually calculated based on the storage deletions is 3,765,000, and since this number is greater than half of he amount of gas that has been used in the contract ($3,765,000 > 731,514/2$), the refund generated will be $731,514/2 = 365,757$.
+So the caller of this transaction will eventually receive is $11,009,981 + 365,757 = 11,375,738$ units of gas.
 
-Note that in order to urge miners to process smart contract with refunds, the accumulated gas refund can never exceed half the gas used up during computation~\cite{wood2014ethereum}.
-So at the end of a successful transaction, the amount of gas in the refund counter (capped at half the net gas used) is returned to the caller.
-For example, the amount of gas that has been used when dequeuing 50 integers from the linked list with mapping priority queue is 731,514 and since $3,000,000 > 731,514/2$, the amount of refund returned to the caller is $731,514/2 = 365,757$.
-
+%& \textbf{\thead{Net Cost\\in Gas\\ (\texttt{gasUsed})}}  
 % = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
@@
 
-% +++++++++++++%
-% so in our case, let's take the first row of the above table:
-
-%The transaction consumes 2,518,131 gas
-%The gas limit is set up at  11,741,495
-%Firstly, they sender get back (11,741,495 - 2,518,13) = 9,223,364 units of unused gas.
-%However, the amount of gas that has been used in the contract is 2,518,131 and since 9,223,364 >2,518,131/2, the REFUND generated will be 2,518,131/2= 1,259,065.
-%
-%The total gas cost of transaction estimated by estimateGas is 3,283,480 
-%estimateGas - gasUsed = gasRefund => 3,283,480 - 2,518,131 = 765,349
-%
-%So we can argue that the estimateGas() gives us an approximate total cost of the transaction and it contains the capped refund counter.
-
-% error in estimateGas:  
-%   https://ethereum.stackexchange.com/questions/266/what-are-the-limitations-to-estimategas-and-when-would-its-estimate-be-considera
-%   https://github.com/trufflesuite/ganache-core/issues/26
-
-%from solidity readdocs: estimateGas Will call estimate the gas a method execution will take when executed in the EVM without.
-The estimation can differ from the actual gas used when later sending a transaction, as the state of the smart contract can be different at that time.
-% estimateGas works by pretending the transaction was actually being included in the blockchain, and then returning the exact gas amount that would have been charged if that pretend operation was real.
-In other words, it uses the exact same procedure a miner would use to calculate the actual fee.
 % = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
@@
 \subsubsection*{Linked List.} Removing the highest priority element from the list can be done in two ways.
-We can use the \texttt{self-destruct()} operation to destroy the head node of the list (\ie smart contract) from the Ethereum blockchain and transfer its funds (if any) to a payable address (\eg the current block miner or the call market contract).
-Although the \texttt{self-destruct()} operation does not remove the initial byte code of the contract from the chain, but it frees up the state storage and refunds 24000 gas to the caller.
+We can use the \texttt{SELFDESTRUCT} operation to destroy the head node of the list (\ie smart contract) from the Ethereum blockchain and transfer its funds (if any) to a payable address (\eg the current block miner or the call market contract).
+Although the \texttt{SELFDESTRUCT} operation does not remove the initial byte code of the contract from the chain, but it frees up the state storage and refunds 24000 gas to the caller.
 Another design perspective is to only update the head pointer of the linked list and leave the previous head (\ie smart contract) on Ethereum blockchain when removing the highest priority element from the list.
-Although the first technique is a bit more costly (because it adds an extra operation \texttt{self-destruct()} to the \texttt{dequeue()} function), it results the in the less final net cost due to the 24000 gas refunds.
+Although the first technique is a bit more costly (because it adds an extra operation \texttt{SELFDESTRUCT} to the \texttt{dequeue()} function), it results the in the less final net cost due to the 24000 gas refunds.
 Also, it is best to avoid storing unnecessary storage variables on chain.
@@
 \subsubsection*{Linked List with Mapping.} Similarly, linked list with mapping can be implemented in two ways.
-For dequeuing items from this priority queue we can use the \texttt{delete()} method and remove the mapping element that contains the highest priority item from storage completely  \textbf{and} update the head and tail pointers of the list.
-Deleting a storage variable is identical to setting a non-zero variable to zero (\texttt{SSTORE} 0) and costs in 5000 gas.
-So although the \texttt{delete()} method refunds in 15000 gas~\cite{wood2014ethereum}, it is yet a gas-costly operation  as it increases the overall gas cost of the transaction.
+For dequeuing items from this priority queue we can use the \texttt{DELETE} method and remove the mapping element that contains the highest priority item from storage completely  \textbf{and} update the head and tail pointers of the list.
+Deleting a storage variable is identical to setting a non-zero variable to zero (\texttt{SSTORE} 0) that costs 20,000 gas but with15,000 refunded~\cite{wood2014ethereum}.
+So although the \texttt{DELETE} method refunds in 15000 gas, it is yet a gas-costly operation  as it increases the overall gas cost of the transaction.
 In another technique, we can only update the head and tail pointers of the linked list when dequeueing the highest priority items and not delete the mapping element associated with the previous pointers.
@@
 \hline
-\multirow{2}{*}{Gas Metrics}                        							& \multicolumn{2}{c|}{Linked List}           						& \multicolumn{2}{c|}{Linked List with Mapping}     					\\ \cline{2-5} 
+\multirow{2}{*}{\textbf{Gas Metrics}}                        							& \multicolumn{2}{c|}{\textbf{Linked List}}           						& \multicolumn{2}{c|}{\textbf{Linked List with Mapping}}     					\\ \cline{2-5}
 % = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = %
-                                                                						& with \texttt{Self-destruct()} 		& without \texttt{Self-destruct()}                	& with \texttt{delete} 		& without \texttt{delete}              		\\ \hline                                                                                                                                                                                                                                                          % = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = %
-                   Net Cost in Gas                          					& 557,085                    			& 721,370                     				& 731,514                     	& 334,689                      				\\ \hline
+                                                                								& with \texttt{SELFDESTRUCT} 		& without \texttt{SELFDESTRUCT}                	& with \texttt{DELETE} 		& without \texttt{DELETE}              		\\ \hline                                                                                                                                                                                                                                                          % = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = %
+                  \textbf{\thead{Net Cost in Gas\\(\texttt{gasUsed})}}                        				& 557,085                    			& 721,370                     			& 731,514                     		& 334,689                      				\\ \hline
 % = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = %
-\thead{Total Cost in Gas \\ (from \texttt{estimateGas})} 		& 1,772,085                  			& 736,370                  					& 3,731,514                     	& 1,099,689                       				\\ \hline
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = %
-		    The Difference                                             		& 1,215,000                  			& 15,000                      				& 3,000,000                    	& 765,000                       				\\ \hline
+ \textbf{\thead{Gas Refund \\from Deleting a Storage\\(Manually Calculated)}}            & 1,200,000                 				& 0                      					& 3,765,000                    		& 765,000                       				\\ \hline
 % = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = %
@@
 
-Based on Table~\ref{tab:LLvsLLMapping}, the linked list with \texttt{Self-destruct()} appears to be a good candidate for the call market implementation.
+Based on Table~\ref{tab:LLvsLLMapping}, the linked list with \texttt{SELFDESTRUCT} appears to be a good candidate for the call market implementation.
 However, as it can be seen in Figure~\ref{fig:random_insertion}, the associated cost for inserting elements into this priority queue is significantly greater than the linked list with mapping as insertion is identical to creating new contracts.
-Accordingly, we choose to implement the call market with the linked list with mapping that uses the  the \texttt{delete()} method to clear up the chain every time the highest priority element is removed from the list.
+Accordingly, we choose to implement the call market with the linked list with mapping that uses the  the \texttt{DELETE} method to clear up the chain every time the highest priority element is removed from the list.
 In overall this priority queue introduces a moderate gas cost for both insertion (\ie order submission) and removal (\ie matching the orders).
@@
 We used three different designs of the linked list with mapping priority queue.
-(1) Every time a trade happens, we use the \texttt{delete()} method to remove the mapping elements that contains best bid and ask orders item from storage completely \textbf{and} update the head and tail pointers of the list.
+(1) Every time a trade happens, we use the \texttt{DELETE} method to remove the mapping elements that contains best bid and ask orders from storage completely \textbf{and} update the head and tail pointers of the list.
 (2) We only update the pointers of the priority queue and do not remove the best bid and ask orders during the entire matching process.
@@
 (3) In the last implementation, we allow the matching process to be completed and do not clear any on chain data.
-As it can be seen in Table~\ref{tab:worst_case_matching}, the \texttt{Match()} operatin shows a better performance when killing the priority contract and/or not clearing data from the chain.
-Although deleting the priority queue contract adds an extra external call to the \texttt{Match()} function and should technically increase the gas cost, the 24000 gas refunds from \texttt{selfdestruct()} would compensate the cost.
+As it can be seen in Table~\ref{tab:worst_case_matching}, the \texttt{Match()} operation shows a better performance when killing the priority contract and/or not clearing data from the chain.
+Although deleting the priority queue contract adds an extra external call to the \texttt{Match()} function and should technically increase the gas cost, the 24000 gas refunds from \texttt{SELFDESTRUCT} would compensate the cost.
 So it can still match as same number of orders (before running out of gas)as in the no on chain clearing implementation.
@@
 % = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  = = = = = = = = = = = %
-	\textbf{\thead{Deleting the Priority Queue Contract}}           	& 210 pairs	                     				& 5,304,211 							& 25,099,713				\\ \hline
+	\textbf{\thead{Destroying the Priority Queue Contract}}           	& 210 pairs	                     				& 5,304,211 							& 25,099,713				\\ \hline
 % = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  = = = = = = = = = = = %
@@
 \subsection {Linkedlist}
-Every time a trade happens, we use the \texttt{self-destruct} operation to remove the nodes (\ie smart contracts) containing the best bid and ask orders from the Ethereum blockchain.
+Every time a trade happens, we use the \texttt{SELFDESTRUCT} operation to remove the nodes (\ie smart contracts) containing the best bid and ask orders from the Ethereum blockchain.
 When a node is deleted, it transfers its funds (if any) to the payable address of the CallMarket contract that has been previously passed to it as a constructor argument.
@@
 
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
+%The tables I changed after estimateGas, Not sure which ones to keep. Should talk to Jeremy
+
+% = = = = = = = = = = = =Gas costs and refunds for Dequeueing 50 integers from each PQ  = = = = = = = = = = = = =  %
+
+\begin{table}[]
+\centering
+\begin{tabular}{|c|c|c|c|c|}
+\hline
+
+\textbf{\thead{Priority Queue}}    & \textbf{\thead{Net Cost\\in Gas}}      & \textbf{\thead{Total Cost\\in Gas\\(From \texttt{estimateGas})}}      & \textbf{The Difference}    & \textbf{\thead{Gas Refund \\(Manually Calculated)}} \\ \hline
+
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
+	\textbf{\thead{Heap with \\ Dynamic Array}}         				& 2,518,131               & 3,283,480		& 765,349             & 750,000                       \\ \hline
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
+	\textbf{\thead{Heap with \\ Static Array}}           				& 1,385,307                & 2,150,625     	& 765,318             & 750,000                      \\ \hline
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
+	\textbf{\thead{Mapping with \\ keys stored \\ in Heap}} 		& 2,781,684                & 4,316,229       	& 1,534,545           & 1,500,000                     \\ \hline
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
+	\textbf{Linked List}                       							& 557,085               	& 1,772,085      	& 1,215,000           & 1,200,000                      \\ \hline
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
+	\textbf{\thead{Linked List with \\ Mapping}}          				& 731,514              	& 3,731,514       	& 3,000,000     	  &  3,765,000                       \\ \hline
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
+
+\end{tabular}
+\caption{\footnotesize{The gas metrics associated with dequeuing 50 items from five priority queues.}
+\label{tab:PQUnitTests}}
+\end{table}
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
+
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
+\begin{table}[]
+\begin{tabular}{|c|c|c|c|c|}
+\hline
+\multirow{2}{*}{Gas Metrics}                        							& \multicolumn{2}{c|}{Linked List}           						& \multicolumn{2}{c|}{Linked List with Mapping}     					\\ \cline{2-5} 
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = %
+                                                                						& with \texttt{SELFDESTRUCT} 		& without \texttt{SELFDESTRUCT}                	& with \texttt{delete} 		& without \texttt{delete}              		\\ \hline                                                                                                                                                                                                                                                          % = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = %
+                   Net Cost in Gas                          					& 557,085                    			& 721,370                     				& 731,514                     	& 334,689                      				\\ \hline
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = %
+\thead{Total Cost in Gas \\ (from \texttt{estimateGas})} 		& 1,772,085                  			& 736,370                  					& 3,731,514                     	& 1,099,689                       				\\ \hline
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = %
+		    The Difference                                             		& 1,215,000                  			& 15,000                      				& 3,000,000                    	& 765,000                       				\\ \hline
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = %
+
+\end{tabular}
+\caption{\footnotesize{}
+\label{tab:LLvsLLMapping}}
+\end{table}
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
+
 %======================================== %

### 2020-08-31 LaTeX/sections/paper.tex
Paper - Updates on the tables and text

@@
 Another design perspective is to only update the head pointer of the linked list and leave the previous head (\ie smart contract) on Ethereum blockchain when removing the highest priority element from the list.
-Although the first technique is a bit more costly (because it adds an extra operation \texttt{SELFDESTRUCT} to the \texttt{dequeue()} function), it results the in the less final net cost due to the 24000 gas refunds.
+Although the first technique is a bit more costly (because it adds an extra operation \texttt{SELFDESTRUCT} to the \texttt{dequeue()} function), it results in the less final net cost due to the 24000 gas refunds.
 Also, it is best to avoid storing unnecessary storage variables on chain.
-Table~\ref{tab:LLvsLLMapping} outlines different gas metrics for iteratively dequeuing the highest priority element from the two implementations of sorted linked lists that contain 50 unsigned integers.
+Table~\ref{tab:LLvsLLMapping} outlines different gas metrics for iteratively dequeuing highest priority elements in the two implementations of sorted linked lists that contain 50 unsigned integers.
 
@@
 For dequeuing items from this priority queue we can use the \texttt{DELETE} method and remove the mapping element that contains the highest priority item from storage completely  \textbf{and} update the head and tail pointers of the list.
-Deleting a storage variable is identical to setting a non-zero variable to zero (\texttt{SSTORE} 0) that costs 20,000 gas but with15,000 refunded~\cite{wood2014ethereum}.
+Deleting a storage variable is identical to setting a non-zero variable to zero (\texttt{SSTORE} 0) that costs 20,000 gas but with 15,000 refunded~\cite{wood2014ethereum}.
 So although the \texttt{DELETE} method refunds in 15000 gas, it is yet a gas-costly operation  as it increases the overall gas cost of the transaction.
-In another technique, we can only update the head and tail pointers of the linked list when dequeueing the highest priority items and not delete the mapping element associated with the previous pointers.
-As it can be seen in Table~\ref{tab:LLvsLLMapping}, this scheme consumes less gas to dequeue 50 unsigned integers from this priority queue with respect to the previous technique where we clear up the chain, however, leaving unnecessary storage data on chain is not a proper design practice.
+In another technique, we can only update the head and tail pointers of the linked list when dequeueing the highest priority item and not delete the mapping element associated with the previous pointers.
+As it can be seen in the last two columns of Table~\ref{tab:LLvsLLMapping}, this scheme consumes less gas for dequeuing 50 unsigned integers compared to the previous technique where we clear up the chain, however, leaving unnecessary storage data on chain is not a proper design practice.
 
@@
 
-%  = = = = = = = = = = %
-
 Table~\ref{tab:worst_case_matching} outlines the \texttt{Match()} function's computational costs and performance for three different implementations of the call market.
@@
 % = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  = = = = = = = = = = = %
-	\textbf{\thead{Clearing the Mapping Elements}}         			& 38 pairs                					& 5,372,679                   				& 457,326,935                      \\ \hline
+	\textbf{\thead{Clearing the Mapping Elements}}         			& 86 pairs                					& 5,433,259                   				& 62,774,170                      \\ \hline
 % = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  = = = = = = = = = = = %
@@
 \caption{\footnotesize{}
-\label{tab:worst_case_matching}}
+\label{tab:LLMApping_worst_case_matching}}
 \end{table}
@@
 
+\section{Call Market Different Design and Implementation Details }
+
 % = = = = = = = = = = = =Clearing Mappings = = = = = = = = = = = = =  %
 
-\section{Clearing Mappings}
+\subsection{Clearing Mappings}
 
@@
 
-\section{Closing and Reopening the Market}
+\subsection{Closing and Reopening the Market}
 

### 2020-09-01 LaTeX/sections/paper.tex
Paper- Edits

@@
 
-\item\textbf{{Mapping with keys stored in Heap.}} This priority queue stores items inside a Solidity mapping that maps the mapping keys (256-bit integers) to these items.
+\item\textbf{{Mapping with Keys Stored in Heap.}} This priority queue stores items inside a Solidity mapping that maps the mapping keys (256-bit integers) to these items.
 The mapping keys are then stored (based on the value they are mapped to) in a sorted Heap that is implemented with a dynamically-sized array.
@@
 Then, we called the \texttt{Dequeue()} function which iteratively removes the highest priority number from the priority queues (until the data structure is empty).
-The computational costs for dequeuing 50 unsigned integers in each priority queue are outlined in Table~\ref{tab:PQUnitTests}.
+The computational costs for dequeuing 50 unsigned integers in each priority queue are outlined in Table~\ref{tab:PQUnitTests} where (\full) indicates the full refund and (\prt) means the amount of refund is bounded.
 These tests are performed using the current Ethereum gas metrics (block gas limit $=$11,741,495 and 1 gas $=$ 56 gwei)~\footnote{https://ethstats.net/}.
 The second column of the table shows the net gas consumption (the gasUsed value derived from transaction receipts) for removing 50 integers from each priority queues.
+
+%Truffle gas limit for the tests: 11741495
 
@@
 
+% Below is the same table but with "Full, Partial,None" for refunds
+
+\begin{table}[]
+\centering
+\begin{tabular}{|c|c|c|}
+\hline
+
+\textbf{\thead{Priority Queue}}    & \textbf{\thead{Net Cost in Gas\\ (\texttt{gasUsed})}}             & \textbf{\thead{Gas Refunds from Deleting a Storage}} \\ \hline
+
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
+	\textbf{\thead{Heap with \\ Dynamic Array}}         				& 2,518,131            		      & \full                      \\ \hline
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
+	\textbf{\thead{Heap with \\ Static Array}}           				& 1,385,307                             & \full                      \\ \hline
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
+	\textbf{\thead{Mapping with \\ keys stored \\ in Heap}} 		& 2,781,684                            & \full                     \\ \hline
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
+	\textbf{Linked List}                       							& 557,085               	           & \full                      \\ \hline
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
+	\textbf{\thead{Linked List with \\ Mapping}}          				& 731,514              	     	  &  \full                       \\ \hline
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
+
+\end{tabular}
+\caption{\footnotesize{The gas metrics associated with dequeuing 50 items from five priority queues.}
+\label{tab:PQUnitTests}}
+\end{table}
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
+
 At the time of this writing, Ethereum transaction receipts only contain the net gas consumption (\texttt{gasUsed}) and we cannot obtain the value of the EVM's refund counter from inside the EVM~\cite{signer2018gas}.
@@
 % = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
-% A little explanation on gas metrics (Mahsa: please let me know if this is still unclear:)
-
-%First let's take a look at the following example:
-
-%Suppose we have a smart contract which uses up 14,000 gas. The gas limit that we have set up is 20,000 gas. The smart contract also includes an SSTORAGE command.
-%So, how much gas will the contract creator get back post computation?
-%Firstly, they will get back (20,000-14,000) = 6,000 units of unused gas.
-%Now, the SSTORAGE command has also been used, so theoretically they should get back 15,000 gas as well.
-%However, the amount of gas that has been used in the contract is 14,000 and since 15,000 > 14,000/2, the REFUND generated will be 14,000/2= 7000.
-%So the total gas that the creator is getting back in the end is 6000+7000 = 13,000.
 
@@
 
-Based on our tests results, the \textit{linked list} and \textit{linked list with mapping} priority queues show the best performance in compared to the different heap implementations.
+Based on our tests results, the \textit{linked list} and \textit{linked list with mapping} priority queues show a better performance in compared to the different heap implementations.
 In the next section, we explore the differences between the two different implementations of the linked list priority queue.
@@
 
-\subsection{Linked List \textit{vs.} Linked List with Mapping}
+\subsection{Linked List \textit{vs.} Linked List with Mapping}\label{sec:LLvsLLMapping}
 
 There are two main ways to implement each of the \textit{linked list} and \textit{linked list with mapping} priority queues.
-In this section, we perform a comprehensive comparison between these two with the purpose choosing the proper data structure for implementing the call market.
+In this section, we perform a comprehensive comparison between these two with the purpose of choosing the proper data structure for implementing the call market.
 
@@
 
+% Below is the same table but with "Full, Partial,None" for refunds
+
+\begin{table}[]
+\begin{tabular}{|c|c|c|c|c|}
+\hline
+\multirow{2}{*}{\textbf{Gas Metrics}}                        							& \multicolumn{2}{c|}{\textbf{Linked List}}           						& \multicolumn{2}{c|}{\textbf{Linked List with Mapping}}     					\\ \cline{2-5}
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = %
+                                                                								& with \texttt{SELFDESTRUCT} 		& without \texttt{SELFDESTRUCT}                	& with \texttt{DELETE} 		& without \texttt{DELETE}              		\\ \hline                                                                                                                                                                                                                                                          % = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = %
+                  \textbf{\thead{Net Cost in Gas\\(\texttt{gasUsed})}}                    & 557,085                    			& 721,370                     			& 731,514                     		& 334,689                      				\\ \hline
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = %
+ \textbf{\thead{Gas Refund \\from Deleting a Storage}}            			& \full                 					& $\times$                 					& \full                    		& \prt                       				\\ \hline
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = %
+
+\end{tabular}
+\caption{\footnotesize{}
+\label{tab:LLvsLLMapping}}
+\end{table}
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
+
 Based on Table~\ref{tab:LLvsLLMapping}, the linked list with \texttt{SELFDESTRUCT} appears to be a good candidate for the call market implementation.
@@
 
+%GitHub repo:  \footnote{\CallMarketRepo}
 % = = = = = = = = = = = = = = = = = = = = =Call market operations Table = = = = = = = = = = = =  = = = = = =  %
@@
 As it can be seen in Table~\ref{tab:worst_case_matching}, the \texttt{Match()} operation shows a better performance when killing the priority contract and/or not clearing data from the chain.
-Although deleting the priority queue contract adds an extra external call to the \texttt{Match()} function and should technically increase the gas cost, the 24000 gas refunds from \texttt{SELFDESTRUCT} would compensate the cost.
-So it can still match as same number of orders (before running out of gas)as in the no on chain clearing implementation.
+However, leaving unnecessary storage data on chain is not a proper design practice (note that as mentioned in Section~\ref{sec:LLvsLLMapping}, destroying a smart contract does not remove the initial byte code of the contract from the chain but it frees up the state storage and refunds 24000 gas to the caller.)
 The last column of Table~\ref{tab:worst_case_matching} reflects the gas cost for matching 1000 pairs of bids and asks for which we set the block gas limit to the maximum of  $2^{53}$ (the Javascript's max safe integer).
@@
 Note that this is a \textit{worst case matching} test where all bids and asks are submitted as marketable limit orders with specified prices that would be filled undoubtedly, performed using the current Ethereum gas metrics (block gas limit $=$11,741,495 and 1 gas $=$ 56 gwei)~\footnote{https://ethstats.net/}.
+
+%Although deleting the priority queue contract adds an extra external call to the \texttt{Match()} function and should technically increase the gas cost, the 24000 gas refunds from \texttt{SELFDESTRUCT} would compensate the cost.
+So it can still match as same number of orders (before running out of gas) as in the no on chain clearing implementation.
 
@@
 % = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
-
-%  = = = = = = = = = = % 
-%Mahsa: Im not sure which of these tables are good for this section!?
-%  = = = = = = = = = = %
 
@@
 
-To maintain the collateral balance of each market participant, we use two Solidity type one-to-one mapping that map Ethereum addresses to 256 bits unsigned integers; \texttt{TotalBalance} and \texttt{UnavailableBalance}.
+To maintain the collateral balance of each market participant, we use two Solidity type one-to-one mappings that map Ethereum addresses to 256 bits unsigned integers; \texttt{TotalBalance} and \texttt{UnavailableBalance}.
 Once market closes and orders are matched, the \texttt{UnavailableBalance} needs to be cleared.
-However, since it is not possible to delete the entire mapping without knowing the keys~\footnote{https://solidity.readthedocs.io/en/v0.5.12/security-considerations.html}, clearing the \texttt{UnavailableBalance} mapping remains a challenging issue to solve .
+However, since it is not possible to delete the entire mapping without knowing the keys~\footnote{https://solidity.readthedocs.io/en/v0.5.12/security-considerations.html}, clearing the \texttt{UnavailableBalance} mapping remains a challenging issue to solve.
 Here we provide a landscape of solutions for that.
@@
 
-\begin{enumerate}
+\begin{itemize}
 
@@
 \item \textbf{Creating a New Mapping Every Time the Market Opens.} Instead of clearing the \texttt{UnavailableBalance} of traders at the end of a matching process, we could create a new mapping every time the market opens.
-Note that using this solution, traders can only claim their funds (using the \texttt{ClaimEther()} and/or \texttt{ClaimToken} methods) only when the market is in state \texttt{Closed}.
+Note that in this scheme traders can claim their funds back (using the \texttt{ClaimEther()} and/or \texttt{ClaimToken} methods) only when the market is closed (\ie the market is in the \texttt{Closed} state).
 
 %---------+++++++++++++++++++-----------------
-\item \textbf{Creating Custom Keys for the Mapping.} We can create custom keys for the mapping by defining a counter as a global variable inside the CallMarket smart contract.
-This counter is incremented at the end of the matching process.
+\item \textbf{Creating Custom Keys for the Mapping.} We can create custom keys for the mapping by defining a counter as a global variable inside the call market smart contract and increment it only once at the end of the matching process.
 So instead of clearing the mapping, we only use another portion of it every time the market opens.
@@
 %---------+++++++++++++++++++-----------------
-\item \textbf{Storing the Mapping in a Data-Contract.} Another design proposal is to create a smart contract every time the market opens, this data contract only stores the \texttt{UnavailableBalance} mapping and will be killed at the end of the matching process.
+\item \textbf{Storing the Mapping in a Data-Contract.} Another design proposal is to create a new smart contract every time the market opens, this data contract only stores the \texttt{UnavailableBalance} mapping and will be destroyed (using the \texttt{SELFDESTRUCT} operation) at the end of the matching process.
 
@@
 This array (\eg address[]) stores the traders' addresses and enables us to iterate over the mapping and delete individual keys and what they map to at the end of the matching process.
-Not that this is a gas-costly design pattern as we would need to maintain a secondary data structure.
+Note that this is a gas-costly design pattern as we would need to maintain a secondary data structure.
 
 %---------+++++++++++++++++++-----------------
-
-\end{enumerate}
-
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
-
-% = = = = = = = = = = Design Details of PQs = = = = = = = = = = = = = = %
-\section{Design Details of PQs}
-
-%---------+++++++++++++++++++-----------------
-
-\subsection{Mapping with Keys Stored in a Heap}\label{sec:mapping_heap}
-
-To store the orders, here we use Solidity mapping that map orders' ids (256-bit integers) to order structs with their variables of different types.
-The mapping keys are then stored in a sorted heap that is implemented with a dynamic storage array.
-Every time a trade happens; (i) the mapping keys associated with the best bid and ask orders are deleted from the heap and the heap is re-sorted, and (ii) the mapping elements containing the best bid and ask orders are deleted from storage completely which refund 15000 gas~\cite{wood2014ethereum}.
-Deleting the mapping elements is yet a gas-costly operation which lowers down the maximum number of orders the \texttt{Match()} function could handle in this case.~\footnote{Every order structs contains multiple variables of different types and removing them from storage is identical to setting multiple variables to zero.} However, we clear the mapping element once a trade happens in our design as leaving unnecessary data is not a proper design practice.
-
-%---------+++++++++++++++++++-----------------
-\subsection {Linkedlist}
-Every time a trade happens, we use the \texttt{SELFDESTRUCT} operation to remove the nodes (\ie smart contracts) containing the best bid and ask orders from the Ethereum blockchain.
-When a node is deleted, it transfers its funds (if any) to the payable address of the CallMarket contract that has been previously passed to it as a constructor argument.
-Also, removing a smart contract from the Ethereum blockchain refunds 24000 gas to the caller.
-
-%---------+++++++++++++++++++-----------------
-\subsection {Linkedlist with Mapping}
-Every time a trade happens when the \texttt{Match()} function is executed, the best bid and ask orders need to be removed from the data structures.
-We could do this in two different ways; (i) update the head and tail pointers of the linkedlist and/or (ii) removing the mapping elements that contain the best bid and ask orders from storage completely as well as updating the pointers of the linkedlist.
-\par
-For the same reason we mentioned in~\ref{sec:mapping_heap}, we clear the best bid and ask order structs from the mapping every time a trade happens as well as updating the pointers.
+\end{itemize}
 
@@
 
+\begin{itemize}
 % = = = = = = = = = = = =How to enforce time on on the Ethereum blockchain? = = = = = = = = = = = = =  %
 
-\subsection{Enforcing Time on the Blockchain}
+\item\textbf{{Enforcing Time on the Blockchain.}}
 
@@
 
-\subsection{Who Pays the Cost for Closing and Reopening the Market?}
+\item\textbf{{Who Pays the Cost for Closing and Reopening the Market?}}
 
@@
 
-\begin{enumerate}
+\begin{itemize}
 
 %= = = = = = Miners Close the Market = = = = = = =%
-
 \item \textbf {Miners Close and Reopen the Market.} The difference between the best bid and ask prices is called the \textit{bid-ask spread}.
@@
 So there is enough economic incentive for the the miner to execute the \texttt{CloseMarket()} function and get refunded as the refund amount could be potentially higher than the bid-ask spread.
-
 % = = = = = = = = = =Processing Orders in Groups= = = = = = = = = = = = = = = %
@@
 => contribution to the community!?
-
 %= = = = = =  = =  =  Meta txs =  = = = = = = = = =%
@@
 
-\end{enumerate}
+\end{itemize}
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
+\end{itemize}
+
+% = = = = = = = = = = = =Transferring the Collateral back to the traders = = = = = = = = = = = = =  %
+\subsection{Transferring the Collateral back to Traders.}
+
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
 

### 2020-09-02 LaTeX/sections/paper.tex
Paper- More edits

@@
 % = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
-
 \section{Introductory Remarks}
@@
 
+% = = = = = = = = = = = = = = = = =
+\subsection*{Contributions.}
+
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
 \section{Cryptocurrency Exchanges}
+
 Strong interest in blockchain and distributed ledger technologies has led into the high trading volume of digital assets and emergence of fast growing cryptocurrency exchanges all over the world.
-These crypto exchanges (hereafter referred to as exchanges) are similar to stock exchanges but, as the name suggests, facilitate the trading process of different cryptocurrency tokens.
+These crypto exchanges are similar to stock exchanges but, as the name suggests, facilitate the trading process of different cryptocurrency tokens.
 Basically, such exchanges provide a trading venue where market participants can buy and/or sell cryptocurrency assets among one another.
-In this section, we describe two types of trading systems and pinpoint why the need for a highly secure exchange and trading system for cryptocurrencies is crucial.
+In this section, we describe two types of crypto exchanges.
 
+% = = = = = = = = = = = = = = = = =
 \subsection{Centralized Exchanges (CEX)}\label{sec:CEX}
+
 This group of exchanges operate in a traditional manner by providing a centralized platform controlled by exchange operators.
 Essentially, the exchange acts as a trusted party whom the market participants must trust to handle their assets.
-Thus, traders transfer the ownership of their assets to the exchange who safeguards customer funds using different methods.
-Although this group of exchanges make it easier for users to trade digital assets (as it takes the burden of safeguarding off traders), it requires traders to fully trust the exchange operator in taking custody of their assets (\eg Coinbase).
-Like any other centralized platform, these exchanges are not completely immune to malicious activities.
-For example, in February 2014, a famous centralized Tokyo-based Bitcoin exchange called MtGox was hacked which led to loss of 650,000 Bitcoins~\cite{TheHisto45:online}.
-Also, a malicious exchange can simply steal users' funds, in February 2019, QuadrigaCX, one of Canada’s well-known centralized cryptocurrency exchanges, claimed that it cannot access to \$190-million worth of customers’ funds~\cite{SEBIOrde83:online}.
+Traders transfer the ownership of their assets to the exchange who safeguards customer funds using different methods.
+Centralized exchanges ease trading process of digital assets as they do not place the burden of safeguarding of the assets onto individualst, however, traders must fully trust the exchange operator in taking custody of their assets (\eg Coinbase).~\footnote{https://www.coinbase.com} Similar to any centralized platform these exchanges are not completely immune to malicious activities.
+For example in February 2014, a famous centralized Tokyo-based Bitcoin exchange called MtGox was hacked which led to loss of 650,000 Bitcoins~\cite{TheHisto45:online}.
+Also, a malicious exchange operator can simply steal users' funds; in February 2019, QuadrigaCX, Canada’s well-known centralized cryptocurrency exchange, claimed that it cannot access to \$190-million worth of customers’ funds~\cite{SEBIOrde83:online}.
 
+% = = = = = = = = = = = = = = = = =
 \subsection{Decentralized Exchanges (DEX)}
 
-Unlike centralized exchanges, DEXes facilitate a secure automated peer-to-peer trading process on the blockchain (\eg Ethereum) for market participants with no third parties involved, hence solving the problems that are inherent in centralized exchanges.
-They provide a better security and privacy by enabling traders to remain fully authoritative over their funds and personal data.
+Unlike centralized exchanges, DEXes facilitate a secure automated peer-to-peer trading process on blockchains (\eg Ethereum) for market participants with no third parties involved, hence solving the issues that are inherent in centralized exchanges.
+This group of exchanges provide a better security and privacy by enabling traders to remain fully authoritative over their funds and personal data.
 With rising of Decentralized Finance (DeFi) or Open Finance movements, the number of DEX platforms on Ethereum have recently exploded and large volume of trading now occurs on DeFi exchanges (\eg Uniswap).~\footnote{https://uniswap.org}
 
-However, building a fully decentralized exchange is associated with high costs and technical complexities and hence remains a big challenge.
+However due to the high cost and technical limitations introduced by blockchain technologies, building a fully decentralized exchange has remained a major challenge.
 In the following section, we explore the idea of building a decentralized exchange on Ethereum.
@@
 
-Order books are data structures that maintain lists of bid and ask orders for various assets (\eg currencies, stocks, bonds \etc) in specific markets.
-The most common version of order books is what we call a \textit{double auction}, where market participants submit their bid and ask orders and the market clearing price will be calculated as the average between the best bid and best ask prices.
-Order books often sort orders based on their price and submission time (this order allocation technique is called price-time priority)~\cite{preis2011price}, where orders are prioritized from highest price to lowest and given any two orders with the same price, they will be sorted based on their submission timestamps.
+Order books are electronic data structures that maintain lists of bid and ask orders for various assets (\eg currencies, stocks, bonds \etc) in specific markets.
+The most common version of order books is a \textit{double auction}, where market participants submit their bid and ask orders and the market clearing price will be calculated as the average between the best bid and ask prices.
+Order books often sort orders based on their price and submission time, this order allocation technique is called price-time priority~\cite{preis2011price} where orders are prioritized from highest price to lowest and given any two orders with the same price, they will be sorted based on their submission timestamps.
 
 Looking more closely, order books are rather electronic ledgers that get updated over time.
-Given the definition of the Ethereum blockchain, that is a distributed ledger, the idea of implementing an order book in the form of a smart contract will seemingly resolve the existing issues with centralized exchanges.
-However, this design is not feasible due to some crucial challenges that exist within blockchains:
+Given the definition of the Ethereum blockchain, that is a distributed ledger, the idea of implementing an order book in the form of a smart contract will seemingly resolve the existing issues with centralized exchanges (see Section~\ref{sec:CEX}).
+However, this design is not feasible due to some technical limitations that exist within blockchains:
 
+% = = = = = = = = = = = = = = = = =
 \begin{itemize}
 %---------+++++++++++++++++++-----------------
-\item \textbf{Speed.} All blockchains are slow in comparison with stock markets which move very fast.
-For example, high-frequency trading (HFT), is a trading method that uses active computers to process a large number of trades in fractions of a second.
-However, blockchains are slow-moving as it takes block intervals for transactions to get confirmed.
+
+\item \textbf{Speed.} All blockchains are slow-moving as it takes block intervals for transactions to get confirmed.
+On the other hand stock markets move very fast;  high-frequency trading (HFT) is a trading method example that uses active computers to process a large number of trades in fractions of a second.
 
 %---------+++++++++++++++++++-----------------
+
 \item \textbf{Front-running and Censorship.} Traders must broadcast their order messages to the network before they can be placed in the block (\ie order book).
-In such scenario, the privileged nodes and miners can front-run transactions or completely drop (censor) those that are competing with their own~\cite{eskandari2019sok}.
+In such scenario, privileged nodes and miners can front-run transactions or completely drop (censor) those that are competing with their own~\cite{eskandari2019sok}.
 Also, miners could almost control how the order book gets updated by inserting their own order messages after viewing all other orders and before mining the block .
@@
 
-\item \textbf{Enforcing Time.} There is no notion of time on blockchains.
-If two orders arrive at the same price, in the normal world whoever is the first wins.
-However, one cannot enforce the priority of orders in the blockchain space; if Alice is more well-connected to the network, her order gets broadcast better and executed first although she sends it after Bob.
+\item \textbf{Enforcing Time.} There is no notion of time on blockchains.I if two orders arrive at the same price, in the normal world whoever is the first wins.
+However, we cannot enforce the priority of orders in the blockchain space; if Alice is more well-connected to the network her order gets broadcast better and executed first although she sends it after Bob.
 
@@
 \end{itemize}
+% = = = = = = = = = = = = = = = = =
 
-According to these issues blockchains cannot solve this particular problem.
+Based on these issues blockchains cannot solve this particular problem.
 Many stock exchanges that currently operate on blockchains tackle this issue by using a private network (where not every network participant can be a node or miner) together with a central time-server that establishes the time priority.
@@
 These orders are accumulated in a sorted data structure and when the trading period is over, orders are matched against each other.
-Our proposed decentralized exchange is both data structure and token agnostic (traders can trade any token that is ERC20 standard compliant).
+Our proposed decentralized exchange is both data structure and token agnostic (traders can trade ERC20 standard compliant token).
 The upcoming orders are not stored in the call market contract, instead they are stored in a priority queue where each element is associated with a priority and is served according to its priority.
@@
 
-\section{Priority Queues}
+\subsection{Priority Queues}
 
 A priority queue can be implemented using many of the data structures that differ in performance and costs.
-In order to choose the appropriate data structure for better performance and costs, we implemented and examined five different generic priority queues that support four main functions (see Table~\ref{tab:PQ_API}).
-Followings describe each implementation.
+In order to choose the appropriate data structure, we implemented and examined five different generic priority queues that support four main functions (see Table~\ref{tab:PQ_API}).
+We discuss each implementation below.
 
@@
 
+% = = = = = = = = = = = = = = = = =
 \begin{enumerate}
@@
 
-\item\textbf{{Heap with Dynamic Array.}} A Heap is a type of binary tree data structure that comes in two forms of a (i) Max-Heap and (ii) Min-Heap.
+\item\textbf{{Heap with Dynamic Array.}} A heap is a type of binary tree data structure that comes in two forms of a (i) Max-Heap and (ii) Min-Heap.
 All the nodes of tree are in a specific order and the root of the tree always represents the highest priority item of the data structure (the largest and smallest values in the Max-Heap and Min-Heap respectively).
-We implemented a priority queue with a Heap that itself is represented by Solidity dynamically-sized array.
+We implemented a priority queue with a heap that itself is represented by a Solidity dynamically-sized array.
 
@@
 
-\item\textbf{{Heap with Static Array.}} A Heap can be also represented by a Solidity storage array in which the storage is statically allocated.
-To do this, we pass the required sized of the array as a smart contract constructor parameter.
+\item\textbf{{Heap with Static Array.}} A heap can be also represented by a Solidity storage array in which the storage is statically allocated.
+To do this, we pass the required size of the array as a constructor parameter to the priority queue smart contract.
 
@@
 
-\item\textbf{{Mapping with Keys Stored in Heap.}} This priority queue stores items inside a Solidity mapping that maps the mapping keys (256-bit integers) to these items.
-The mapping keys are then stored (based on the value they are mapped to) in a sorted Heap that is implemented with a dynamically-sized array.
+\item\textbf{{Mapping with Keys Stored in a Heap.}} This priority queue stores items inside a Solidity mapping that maps them to mapping keys (256-bit integers).
+These keys are then stored in a sorted heap (based on the value they are mapped to) that is implemented with a dynamically-sized array.
 
@@
 
-\item\textbf{{Linked List.}} Here we used a sorted singly Linked List to implement the priority queue.
-A Linked List is a linear data structure made of a chain of items (also known as nodes) where each item contains a value and a pointer to the next node in the list.
-In our implementation, each node is represented by a smart contract that contains the data and a pointer to its next smart contract in the list.
+\item\textbf{{Linked List.}} Here we used a sorted singly linked list to implement the priority queue.
+A linked list is a linear data structure made of a chain of items (also known as nodes) where each item contains a value and a pointer to the next node in the list.
+In an object-oriented programming language a linked list can be easily implemented with a recursive struct; struct that contains a member variable in its own type.
+However, Solidity does not support recursive structs because the size of the struct has to be finite.
+So in our implementation, each node is represented by a smart contract that contains the data and a pointer of its own type to its next smart contract in the list.
 
@@
 
-\item\textbf{{Linked List with Mapping.}} Here we used Solidity mapping to implement our priority queue with a sorted doubly Linked List where every node points to it previous \textbf{and} next node in the list.
+\item\textbf{{Linked List with Mapping.}} Here we used Solidity mapping to implement a sorted doubly linked list priority queue where every node points to it previous \textbf{and} next node in the list.
 The Linked List entries are first wrapped in an struct data type that contains (i) the unique id of that element, (ii) the unique id of its previous item in the list, and (iii) the unique id of its next item in the list.
@@
 \end{enumerate}
-
+% = = = = = = = = = = = = = = = = =
 % = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
 
-Next, we used Javascript for testing by leveraging the Mocha testing framework and performed our priority queue performance tests.
-We entered 50 pseudo-random integers between 1 and 200 to the priority queues and obtained the associated gas costs.
+In the next step, we used Javascript for testing by leveraging the Mocha testing framework and performed performance tests on the five priority queues.
+We entered 50 pseudo-random integers between 1 and 200 to the priority queues and obtained the associated gas costs for 200 transactions.
 Figure~\ref{fig:random_insertion} represents the gas costs variations for entering 50 unsigned integers to the five priority queues; the x-axis is the place in line (\eg the10th number entered in the priority queue) and the and y-axis is the cost of that transaction in gas.

### 2020-09-03 LaTeX/sections/paper.tex
Edits

@@
 % = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
-\section{Cryptocurrency Exchanges}
+\section{Preliminaries}
 
@@
 
+\subsection{Blockchain}
+
+* transparency, front-running
+* slow but is becoming more efficient over time, expensive
+* Gas model: gas limit, how much, per transaction vs per block, Solidity/EVM quirks: gas refunds
+
+At the time of this writing, Ethereum transaction receipts only contain the net gas consumption (\texttt{gasUsed}) and we cannot obtain the value of the EVM's refund counter from inside the EVM~\cite{signer2018gas}.
+So in order to account for refunds inside each priority queue smart contract we calculate them manually; first we figure out exactly how much storage is being cleared when dequeuing the highest priority elements (\texttt{SSTORE} instruction) and then we multiply the number of storage slots cleared by 15,000 (see the last column of Table~\ref{tab:PQUnitTests}).
+
+Note that in order to urge miners to process smart contracts with refunds, the accumulated gas refund can never exceed half the gas used up during computation~\cite{wood2014ethereum}.
+So at the end of a successful transaction, the amount of gas in the refund counter (capped at half the net gas used) is returned to the caller.
+
+Based on these issues blockchains cannot solve this particular problem.
+Many stock exchanges that currently operate on blockchains tackle this issue by using a private network (where not every network participant can be a node or miner) together with a central time-server that establishes the time priority.
+We propose a different method of implementing a fully decentralized exchange using an alternative data structure known as \textit{a call market} or \textit{frequent batch auction} instead of a time-sensitive order book~\cite{clark2014decentralizing}.
+
+\subsection{Exchanges}
+
 % = = = = = = = = = = = = = = = = =
-\subsection{Centralized Exchanges (CEX)}\label{sec:CEX}
+\subsubsection{Centralized Exchanges (CEX)}\label{sec:CEX}
 
@@
 % = = = = = = = = = = = = = = = = =
-\subsection{Decentralized Exchanges (DEX)}
+\subsubsection{Decentralized Exchanges (DEX)}
 
@@
 
-\section{Order Books}
+\subsection{Order Books}
 
@@
 
-Based on these issues blockchains cannot solve this particular problem.
-Many stock exchanges that currently operate on blockchains tackle this issue by using a private network (where not every network participant can be a node or miner) together with a central time-server that establishes the time priority.
-We propose a different method of implementing a fully decentralized exchange using an alternative data structure known as \textit{a call market} or \textit{frequent batch auction} instead of a time-sensitive order book~\cite{clark2014decentralizing}.
-
 % = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
 
-\section{Call Market}\label{sec:callmarket}
-
-In this research work, we design and implement a call market on the Ethereum blockchain.
-We divide the trading day into frequent but discrete time intervals; every time the market opens traders submit their ask and bid order messages.
-These orders are accumulated in a sorted data structure and when the trading period is over, orders are matched against each other.
-Our proposed decentralized exchange is both data structure and token agnostic (traders can trade ERC20 standard compliant token).
-The upcoming orders are not stored in the call market contract, instead they are stored in a priority queue where each element is associated with a priority and is served according to its priority.
-
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
-
-\subsection{Priority Queues}
-
-A priority queue can be implemented using many of the data structures that differ in performance and costs.
-In order to choose the appropriate data structure, we implemented and examined five different generic priority queues that support four main functions (see Table~\ref{tab:PQ_API}).
-We discuss each implementation below.
+\section{Priority Queue}\label{sec:pq}
 
 % = = = = = = = = = = = =Operations for a generic Priority Queue Table = = =  = = = = = = = = = = = %
-\begin{table}[]
+\begin{table}[t]
 \centering
@@
 
+In designing \cm, performance within Ethereum's limited gas model became the main bottleneck.
+Within a call market, recording trades and accessing them to close the market is the most time consuming step.
+For this reason, we decided to do a deep study of the best data-structure for this specific task.
+While data structures are well studied for many languages, Solidity/EVM have their own quirks (\eg gas refunds, a relatively cheap mapping data structure, and no actual support for object oriented programming) that make them difficult to assess which will perform best without actually deploying and evaluating each variant.
+
+When closing a call market, the orders are examined in order: highest to lowest price for bids, and lowest to highest price for asks.
+It most circumstances, the market closing algorithm does not have to consider any deeper bids/asks from the list when choosing whether the current best bid and ask can be fulfilled.
+The only exception is in the case of a tie on price, which we return to later.
+For this reason, the ideal data structure for storing bids/asks is a \textit{priority queue} (see Table~\ref{tab:PQ_API}) where each order's priority is its price.
+Specifically, we use two PQs---one for bids where the highest price is the highest priority, and one for asks where the lowest price is the highest priority.
+
+There are numerous ways of implementing a PQ.
+A PQ has an underlying list---common options include a static array, dynamic array, and linked list.
+The most expensive operation is keeping the data sorted---common options include (i) sorting during each enqueue, (ii) sorting for each dequeue, or (iii) splitting the difference by using a heap as the underlying data structure.
+Respectively, the time complexities are (i) linear enqueue and constant dequeue, (ii) constant enqueue and linear dequeue, and (iii) logarithmic enqueue and logarithmic dequeue.
+This said, Solidity/EVM has its own specific considerations to take into account.
+As closing the market is very expensive with any PQ, we rule out using (ii) as fully sorting while dequeuing would be prohibitive.
+We experiment with the following 5 options for (i) and (iii):
+
 % = = = = = = = = = = = = = = = = =
@@
 All the nodes of tree are in a specific order and the root of the tree always represents the highest priority item of the data structure (the largest and smallest values in the Max-Heap and Min-Heap respectively).
-We implemented a priority queue with a heap that itself is represented by a Solidity dynamically-sized array.
+We implemented a priority queue with a heap that stores its data in a dynamically-sized array.
 
@@
 
-\item\textbf{{Mapping with Keys Stored in a Heap.}} This priority queue stores items inside a Solidity mapping that maps them to mapping keys (256-bit integers).
-These keys are then stored in a sorted heap (based on the value they are mapped to) that is implemented with a dynamically-sized array.
+\item\textbf{{Heap with Mapping.}} In the above implementations, the heap stores the entire order (as a struct) in the heap.
+In this variant, we store the order struct in a Solidity mapping and store the mapping's key in the heap.
 
@@
 
-\item\textbf{{Linked List.}} Here we used a sorted singly linked list to implement the priority queue.
-A linked list is a linear data structure made of a chain of items (also known as nodes) where each item contains a value and a pointer to the next node in the list.
-In an object-oriented programming language a linked list can be easily implemented with a recursive struct; struct that contains a member variable in its own type.
-However, Solidity does not support recursive structs because the size of the struct has to be finite.
-So in our implementation, each node is represented by a smart contract that contains the data and a pointer of its own type to its next smart contract in the list.
+\item\textbf{{Linked List.}} In this variant, we insert a new element into its correct position (based on its price) when running enqueue.
+The PQ itself stores elements in a linked list (enabling us to efficiently insert a new element between two existing elements).
+Solidity is described as object-oriented but the equivalent of an object is an entire smart contract.
+Therefore an object-oriented linked list must either (i) create each node in the list as a struct---but this is not possible as Solidity does not support recursive structs---or (ii) make every node in the list its own contract.
+The latter option seems wasteful and unusual, but we try it out anyways.
+Thus each node is its own contract and contains the order data and a pointer to the address of the next contract in the list.
 
@@
 
-\item\textbf{{Linked List with Mapping.}} Here we used Solidity mapping to implement a sorted doubly linked list priority queue where every node points to it previous \textbf{and} next node in the list.
-The Linked List entries are first wrapped in an struct data type that contains (i) the unique id of that element, (ii) the unique id of its previous item in the list, and (iii) the unique id of its next item in the list.
-These structs are then stored in the mapping indexed by item id.
+\item\textbf{{Linked List with Mapping.}} Finally, we try a variant of a linked list using a Solidity mapping.
+The value of the mapping is a struct with order data and the key of the next (and previous) node in the list.
+The contract stores the key of the first node (head) in the list.
 
@@
 
-In the next step, we used Javascript for testing by leveraging the Mocha testing framework and performed performance tests on the five priority queues.
-We entered 50 pseudo-random integers between 1 and 200 to the priority queues and obtained the associated gas costs for 200 transactions.
-Figure~\ref{fig:random_insertion} represents the gas costs variations for entering 50 unsigned integers to the five priority queues; the x-axis is the place in line (\eg the10th number entered in the priority queue) and the and y-axis is the cost of that transaction in gas.
+\subsection{Priority Queue Evaluation}
+
+\subsubsection{Enqueue performance.} We implemented, deployed, and tested each priority queue using Truffle and Ganache.\footnote{Github: Link removed for anonymity.} We tried a variety of tests (including testing the full call market with each varient) with consistent results in performance.
+A simple test to showcase the performance profile is shown in Figure~\ref{fig:random_insertion}.
+We simply enqueue 50 integers chosen at random from a fixed interval in each PQ variant.
+The bigger the PQ gets, the longer enqueue takes---a linear increase for the linked list variants, and logarithmic for the heap variants.
 
@@
 
-\begin{figure}[htb!p]
+\begin{figure}[t]
 \centering
-\includegraphics[width=1\textwidth]{fig/random_insertion.png}
-\caption{\footnotesize{Gas costs for entering 50 items into five different priority queues.}  \label{fig:random_insertion}}
+\includegraphics[width=0.8\textwidth]{fig/random_insertion.png}
+\caption{\footnotesize{Gas costs for enqueuing random items into five different priority queue variants.
+For the x-axis, a value of 10 indicates it is the 10th number entered in the priority queue.
+The y-axis is the cost of enqueue in gas.}  \label{fig:random_insertion}}
 \end{figure}
+
+\input{tables/dequeue.tex}
 
@@
 
-Then, we called the \texttt{Dequeue()} function which iteratively removes the highest priority number from the priority queues (until the data structure is empty).
-The computational costs for dequeuing 50 unsigned integers in each priority queue are outlined in Table~\ref{tab:PQUnitTests} where (\full) indicates the full refund and (\prt) means the amount of refund is bounded.
-These tests are performed using the current Ethereum gas metrics (block gas limit $=$11,741,495 and 1 gas $=$ 56 gwei)~\footnote{https://ethstats.net/}.
-The second column of the table shows the net gas consumption (the gasUsed value derived from transaction receipts) for removing 50 integers from each priority queues.
+\subsubsection{Dequeue performance.} For each PQ variant storing 50 random integers, the \texttt{Dequeue()} function is iterated until the data structure is empty.
+The total gas cost for fully dequeuing the priority queue variants is outlined in Table~\ref{tab:PQUnitTests}.
+These tests are performed using the following Ethereum gas metrics: block gas limit $=$11,741,495 and 1 gas $=$ 56 gwei.\footnote{\[July 2020:\] https://ethstats.net/} Dequeuing removes data from the contract's storage.
+Recall this results in a gas refund.
+Based on our manual estimates (EVM does not expose the refund counter), every variant receives the maximum gas refund possible (\ie half the total cost of the transaction).
+In other words, each of them actually consumes twice the \texttt{gasUsed} amount in gas before the refund, however none of them are better or worst based on how much of a refund they generate.
 
-%Truffle gas limit for the tests: 11741495
-
-% = = = = = = = = = = = =Gas costs and refunds for Dequeueing 50 integers from each PQ  = = = = = = = = = = = = =  %
-
-\begin{table}[]
-\centering
-\begin{tabular}{|c|c|c|}
-\hline
-
-\textbf{\thead{Priority Queue}}    & \textbf{\thead{Net Cost in Gas\\ (\texttt{gasUsed})}}             & \textbf{\thead{Gas Refunds from Deleting a Storage\\(Manually Calculated)}} \\ \hline
-
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
-	\textbf{\thead{Heap with \\ Dynamic Array}}         				& 2,518,131            		      & 750,000                       \\ \hline
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
-	\textbf{\thead{Heap with \\ Static Array}}           				& 1,385,307                             & 750,000                      \\ \hline
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
-	\textbf{\thead{Mapping with \\ keys stored \\ in Heap}} 		& 2,781,684                            & 1,500,000                     \\ \hline
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
-	\textbf{Linked List}                       							& 557,085               	           & 1,200,000                      \\ \hline
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
-	\textbf{\thead{Linked List with \\ Mapping}}          				& 731,514              	     	  &  3,765,000                       \\ \hline
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
-
-\end{tabular}
-\caption{\footnotesize{The gas metrics associated with dequeuing 50 items from five priority queues.}
-\label{tab:PQUnitTests}}
-\end{table}
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
-
-% Below is the same table but with "Full, Partial,None" for refunds
-
-\begin{table}[]
-\centering
-\begin{tabular}{|c|c|c|}
-\hline
-
-\textbf{\thead{Priority Queue}}    & \textbf{\thead{Net Cost in Gas\\ (\texttt{gasUsed})}}             & \textbf{\thead{Gas Refunds from Deleting a Storage}} \\ \hline
-
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
-	\textbf{\thead{Heap with \\ Dynamic Array}}         				& 2,518,131            		      & \full                      \\ \hline
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
-	\textbf{\thead{Heap with \\ Static Array}}           				& 1,385,307                             & \full                      \\ \hline
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
-	\textbf{\thead{Mapping with \\ keys stored \\ in Heap}} 		& 2,781,684                            & \full                     \\ \hline
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
-	\textbf{Linked List}                       							& 557,085               	           & \full                      \\ \hline
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
-	\textbf{\thead{Linked List with \\ Mapping}}          				& 731,514              	     	  &  \full                       \\ \hline
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
-
-\end{tabular}
-\caption{\footnotesize{The gas metrics associated with dequeuing 50 items from five priority queues.}
-\label{tab:PQUnitTests}}
-\end{table}
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
-
-At the time of this writing, Ethereum transaction receipts only contain the net gas consumption (\texttt{gasUsed}) and we cannot obtain the value of the EVM's refund counter from inside the EVM~\cite{signer2018gas}.
-So in order to account for refunds inside each priority queue smart contract we calculate them manually; first we figure out exactly how much storage is being cleared when dequeuing the highest priority elements (\texttt{SSTORE} instruction) and then we multiply the number of storage slots cleared by 15,000 (see the last column of Table~\ref{tab:PQUnitTests}).
-
-Note that in order to urge miners to process smart contracts with refunds, the accumulated gas refund can never exceed half the gas used up during computation~\cite{wood2014ethereum}.
-So at the end of a successful transaction, the amount of gas in the refund counter (capped at half the net gas used) is returned to the caller.
-Let's take a closer look at the last row of Table~\ref{tab:PQUnitTests}; gas that has been used for dequeuing 50 integers from the linked list with mapping priority queue is 731,514 and the gas limit has been set up to 11,741,495.
-Firstly, the caller will receive $(11,741,495 - 731,514) = 11,009,981$ units of unused gas.
-Also, the amount of refund we manually calculated based on the storage deletions is 3,765,000, and since this number is greater than half of he amount of gas that has been used in the contract ($3,765,000 > 731,514/2$), the refund generated will be $731,514/2 = 365,757$.
-So the caller of this transaction will eventually receive is $11,009,981 + 365,757 = 11,375,738$ units of gas.
-
-%& \textbf{\thead{Net Cost\\in Gas\\ (\texttt{gasUsed})}}  
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
+\subsubsection{Decision.} Based on enqueing, the heap variants are the cheapest in terms of gas, while based on dequeuing, the link list variants are cheapest.
+This is in accordance with the theoretical worst-case time complexity for each.
+However, (i) the linked list variants are materially cheaper than the heap variants at dequeuing, and (ii) dequeuing in a call market must be done as a batch, whereas enqueuing is paid for one at a time by the trader submitting the order, and (iii) Ethereum will not permit more than hundreds of orders so the asymptotic behaviour is not a significant factor.
+For these reasons, we suggest using a linked list variant for this specific application.
+As it can be seen in Figure~\ref{fig:random_insertion}, the associated cost for inserting elements into a linked list PQ is significantly greater than the linked list with mapping, as each insertion cause the creation of a new contracts.
+Accordingly, we choose to implement the call market with the linked list with mapping.
+Overall this PQ balances a moderate gas cost for insertion (\ie order submission) with one for removal (\ie matching the orders).
 
@@
 
-Based on our tests results, the \textit{linked list} and \textit{linked list with mapping} priority queues show a better performance in compared to the different heap implementations.
-In the next section, we explore the differences between the two different implementations of the linked list priority queue.
+\subsection{Cost/Benefit of cleaning up after yourself}
+\label{sec:LLvsLLMapping}
+\label{sec:gasrefund}
 
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
-
-\subsection{Linked List \textit{vs.} Linked List with Mapping}\label{sec:LLvsLLMapping}
-
-There are two main ways to implement each of the \textit{linked list} and \textit{linked list with mapping} priority queues.
-In this section, we perform a comprehensive comparison between these two with the purpose of choosing the proper data structure for implementing the call market.
+\input{tables/cleaning.tex}
 
 %---------+++++++++++++++++++-----------------
+
+% With 50 selfdestructs
 
@@
 
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
-\begin{table}[]
-\begin{tabular}{|c|c|c|c|c|}
-\hline
-\multirow{2}{*}{\textbf{Gas Metrics}}                        							& \multicolumn{2}{c|}{\textbf{Linked List}}           						& \multicolumn{2}{c|}{\textbf{Linked List with Mapping}}     					\\ \cline{2-5}
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = %
-                                                                								& with \texttt{SELFDESTRUCT} 		& without \texttt{SELFDESTRUCT}                	& with \texttt{DELETE} 		& without \texttt{DELETE}              		\\ \hline                                                                                                                                                                                                                                                          % = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = %
-                  \textbf{\thead{Net Cost in Gas\\(\texttt{gasUsed})}}                        				& 557,085                    			& 721,370                     			& 731,514                     		& 334,689                      				\\ \hline
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = %
- \textbf{\thead{Gas Refund \\from Deleting a Storage\\(Manually Calculated)}}            			& 1,200,000                 					& 0                					& 3,765,000                    		& 765,000                       				\\ \hline
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = %
-
-\end{tabular}
-\caption{\footnotesize{}
-\label{tab:LLvsLLMapping}}
-\end{table}
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
-
-% Below is the same table but with "Full, Partial,None" for refunds
-
-\begin{table}[]
-\begin{tabular}{|c|c|c|c|c|}
-\hline
-\multirow{2}{*}{\textbf{Gas Metrics}}                        							& \multicolumn{2}{c|}{\textbf{Linked List}}           						& \multicolumn{2}{c|}{\textbf{Linked List with Mapping}}     					\\ \cline{2-5}
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = %
-                                                                								& with \texttt{SELFDESTRUCT} 		& without \texttt{SELFDESTRUCT}                	& with \texttt{DELETE} 		& without \texttt{DELETE}              		\\ \hline                                                                                                                                                                                                                                                          % = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = %
-                  \textbf{\thead{Net Cost in Gas\\(\texttt{gasUsed})}}                    & 557,085                    			& 721,370                     			& 731,514                     		& 334,689                      				\\ \hline
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = %
- \textbf{\thead{Gas Refund \\from Deleting a Storage}}            			& \full                 					& $\times$                 					& \full                    		& \prt                       				\\ \hline
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = %
-
-\end{tabular}
-\caption{\footnotesize{}
-\label{tab:LLvsLLMapping}}
-\end{table}
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
-
-Based on Table~\ref{tab:LLvsLLMapping}, the linked list with \texttt{SELFDESTRUCT} appears to be a good candidate for the call market implementation.
-However, as it can be seen in Figure~\ref{fig:random_insertion}, the associated cost for inserting elements into this priority queue is significantly greater than the linked list with mapping as insertion is identical to creating new contracts.
-Accordingly, we choose to implement the call market with the linked list with mapping that uses the  the \texttt{DELETE} method to clear up the chain every time the highest priority element is removed from the list.
-In overall this priority queue introduces a moderate gas cost for both insertion (\ie order submission) and removal (\ie matching the orders).
+ that uses the  the \texttt{DELETE} method to clear up the chain every time the highest priority element is removed from the list. In
 
@@
 
-\section{Experimentations}
+\section{Call Market Design}
+
+In this research work, we design and implement a call market on the Ethereum blockchain.
+We divide the trading day into frequent but discrete time intervals; every time the market opens traders submit their ask and bid order messages.
+These orders are accumulated in a sorted data structure and when the trading period is over, orders are matched against each other.
+Our proposed decentralized exchange is both data structure and token agnostic (traders can trade ERC20 standard compliant token).
+The upcoming orders are not stored in the call market contract, instead they are stored in a priority queue where each element is associated with a priority and is served according to its priority.
 

### 2020-09-08 LaTeX/sections/paper.tex
Edits on the figure references - Added the cost in eth and USD (conversions included)
Preliminaries - to be completed

@@
 
-* transparency, front-running
-* slow but is becoming more efficient over time, expensive
+\begin{itemize}
+
+% transparency, front-running:
+\item \textbf{Transparency and Front-running.} Blockchains (in general)  are transparent --- transactions are first relay around the network before being selected by a miner, validated, and included in a block.
+This allows malicious nodes/miners observe and front-run the transactions by dropping them or attempting to insert their own transactions before the observed transactions~\cite{eskandari2019sok}.
+In context of a decentralized exchange, front-running attacks enable the malicious nodes to have their orders executed before others and benefit from it.
+
+% slow but is becoming more efficient over time, expensive
+\item \textbf{Speed.} Blockchains are not fast architectures --- speed is one of the factors that diminishes the real world potential of blockchains.
+Blockchains are slow-moving as it takes block interval (\ie time it takes to mine a block) for transactions to be confirmed and included in valid blocks.
+So it is difficult to push a stock market on the blockchain as stock markets move extremely fast.
+High-frequency trading (HFT) is a trading method example that uses active computers to process a large number of trades in fractions of a second.
+Currently in Ethereum 1.0 blocks are produced at intervals every 10 to19 seconds, note that this is not yet suitable for time sensitive transactions.
+However, capabilities of blockchains will be further enhanced ad they will become more efficient over time; Ethereum 2.0 has a shorter block time of 12 seconds.
+
+% Gas model: gas limit, how much, per transaction vs per block, Solidity/EVM quirks: gas refunds
+\item \textbf{Gas Parameter in Ethereum Transactions.}
+
+Gas is the Ethereum's pseudo-currency and a key variable for the execution of smart contracts.
+DApps written in high-level programming languages are compiled and translated into a compact representation (called ‘bytecode’) to be further executed on the Ethereum virtual machine or EVM.
+Each of these opcodes has a fixed amount of gas assigned and is a measure of computational effort.
+Separating ether from gas prevents transactions cost from being too expensive as they are less impacted by ETH price fluctuations.
+Gas unit does not a have a monetary value and as mentioned it only  measures the computational work undertaken by miners.
+To pay miners, Ethereum introduces a \texttt{gas price} --- small denomination of ether called \textbf{Gwei} attached to each gas unit.
+Essentially, gas price indicates how much users are willing to pay per unit of gas, clearly the higher gas price leads to the faster execution of a transaction.
+Miners also need to know the total amount of computational work a user is requesting, called the \texttt{gas limit}.
+\texttt{Gas limit} is a parameter that limits the amount of gas users would spend in a transaction.
+It protects users from spending unlimited ETH on their transactions and must be set carefully.
+If the \texttt{gas limit} is too low, the transaction will exceed the limit, all changes will be reversed but the users must still pay for the computational work performed by the miner.
+
+gas is what makes ethereum furnctiom,  it safegaurds the network from overload and incentivises people too keep ethereum running.
+By seperating eth from gas, txs cost are less influneced by chning price of Eth so keeping txs from being too expensive
+
+gas price: how much you pay per gas unit
+gas limit: how much work you are requesting
+
+gas cost (Ether) = gasPrice * gasCost(gas)
+
+gas limit: is a parameter that limits the amount of gas you spend in a transaction (how to estimate? using estimateGas)
+gas price how to estimate: using ethgassation 
+by defaluth the gas minimum gas limit for ethereum txs is 21000 gas
+
+a block also has a gas limit field, it defines a maximum amount of gas all txs in th eblock combined are allowed to consume.
+this block gas limit determines the maximum number of transactions within the block.
+this block gas limt is not fixed and set by miners
+
 * Gas model: gas limit, how much, per transaction vs per block, Solidity/EVM quirks: gas refunds
@@
 We propose a different method of implementing a fully decentralized exchange using an alternative data structure known as \textit{a call market} or \textit{frequent batch auction} instead of a time-sensitive order book~\cite{clark2014decentralizing}.
+
+\end{itemize}
 
@@
 
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
+%  = = = = = = Table 2 (dequeue) Conversions = = = = = = %
+%
+%As of July 2020,  $1 gas = 56\times10^{-9} ether$\footnote{https://ethstats.net/} and 1 ether = \$238.33\footnote{https://coinmarketcap.com/}.
+%
+%$Transaction cost (eth) = GasUsed (unit) \times Gas Price (eth)$ 
+%
+%%  = = = = = = Transaction Costs in eth = = = = = = %
+%
+%Heap with Dynamic Array:    		$2,518,131 \times 56\times10^{-9} = 141,015,336\times 10^{-9}$
+%Heap with Dynamic Array:     		$1,385,307 \times 56\times10^{-9} = 77,577,192\times 10^{-9}$
+%Heap with Mapping:              		$2,781,684 \times 56\times10^{-9} = 155,774,304\times 10^{-9}$
+%Linked List:						$557,085 \times 56\times10^{-9} = 	31,196,760\times 10^{-9}$
+%Linked List with Mapping:			$731,514 \times 56\times10^{-9} = 	40,964,784\times 10^{-9}$
+%
+%%  = = = = = = Transaction Costs in USD = = = = = = %
+%
+%Heap with Dynamic Array:    		$141,015,336\times 10^{-9} \times 238.33 = \$33.60$
+%Heap with Dynamic Array:     		$77,577,192\times 10^{-9} \times 238.33 = \$18.48$
+%Heap with Mapping:              		$155,774,304\times 10^{-9} \times 238.33 = \$37.12$
+%Linked List:						$31,196,760\times 10^{-9} \times 238.33 = \$7.43$
+%Linked List with Mapping:			$40,964,784\times 10^{-9} \times 238.33 = \$9.76$
+%
 % = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
@@
 %---------+++++++++++++++++++-----------------
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
+
+%  = = = = = = Table 3 (cleaning.tex) Conversions = = = = = = %
+
+%As of July 2020,  $1 gas = 56\times10^{-9} ether$\footnote{https://ethstats.net/} and 1 ether = \$238.33\footnote{https://coinmarketcap.com/}.
+%
+%$Transaction cost (eth) = GasUsed (unit) \times Gas Price (eth)$ 
+%
+%%  = = = = = = Transaction Costs in eth = = = = = = %
+%
+%Linked List with \texttt{SELFDESTRUCT}:     				$557,085 \times 56\times10^{-9} =  31,196,760\times 10^{-9}$  
+%Linked List w/o \texttt{SELFDESTRUCT}:     				$721,370 \times 56\times10^{-9} =  40,396,720\times 10^{-9}$ 
+%Linked List with Mapping and \texttt{DELETE}:    			$731,514 \times 56\times10^{-9} =  40,964,784\times 10^{-9}$ 
+%Linked List with Mapping and w/o \texttt{DELETE}: 		$334,689 \times 56\times10^{-9} =  18,742,584\times 10^{-9}$ 
+%
+%%  = = = = = = Transaction Costs in USD = = = = = = %
+%
+%Linked List with \texttt{SELFDESTRUCT}:     				$31,196,760\times 10^{-9}  \times 238.33 = \$7.43$
+%Linked List w/o \texttt{SELFDESTRUCT}:     				$40,396,720\times 10^{-9} \times 238.33 = \$9.62$
+%Linked List with Mapping and \texttt{DELETE}:    			$40,964,784\times 10^{-9}  \times 238.33 = \$9.76$
+%Linked List with Mapping and w/o \texttt{DELETE}: 		$18,742,584\times 10^{-9} \times 238.33 = \$4.46$
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
 

### 2020-09-08 LaTeX/sections/paper.tex
Blockchain (Preliminaries) Completed

@@
 \item \textbf{Transparency and Front-running.} Blockchains (in general)  are transparent --- transactions are first relay around the network before being selected by a miner, validated, and included in a block.
-This allows malicious nodes/miners observe and front-run the transactions by dropping them or attempting to insert their own transactions before the observed transactions~\cite{eskandari2019sok}.
-In context of a decentralized exchange, front-running attacks enable the malicious nodes to have their orders executed before others and benefit from it.
+This allows malicious nodes/miners to observe and front-run the transactions by dropping them or attempting to insert their own transactions before the observed transactions~\cite{eskandari2019sok}.
+In the context of a DEX, front-running attacks enable malicious nodes to have their orders executed before others and benefit from it.
 
@@
 High-frequency trading (HFT) is a trading method example that uses active computers to process a large number of trades in fractions of a second.
-Currently in Ethereum 1.0 blocks are produced at intervals every 10 to19 seconds, note that this is not yet suitable for time sensitive transactions.
+In Ethereum 1.0 blocks are produced at intervals every 10 to19 seconds, note that this is not yet suitable for time sensitive transactions.
 However, capabilities of blockchains will be further enhanced ad they will become more efficient over time; Ethereum 2.0 has a shorter block time of 12 seconds.
@@
 Each of these opcodes has a fixed amount of gas assigned and is a measure of computational effort.
-Separating ether from gas prevents transactions cost from being too expensive as they are less impacted by ETH price fluctuations.
-Gas unit does not a have a monetary value and as mentioned it only  measures the computational work undertaken by miners.
+Separating ETH from gas prevents transactions cost from being too expensive as they are less impacted by ETH price fluctuations.
+Gas unit does not a have a monetary value and as mentioned, it only  measures the computational work undertaken by miners.
 To pay miners, Ethereum introduces a \texttt{gas price} --- small denomination of ether called \textbf{Gwei} attached to each gas unit.
@@
 It protects users from spending unlimited ETH on their transactions and must be set carefully.
-If the \texttt{gas limit} is too low, the transaction will exceed the limit, all changes will be reversed but the users must still pay for the computational work performed by the miner.
+If the \texttt{gas limit} is too low, the transaction will exceed the limit, all operations will be reverted while the user must pay for the computational work performed by the miner.
+By default the gas limit for an Ethereum transaction is 21,000 gas.
+An Ethereum block also has a \texttt{block gas limit} field which is set by the Ethereum miners and indicates the maximum amount of gas all the transactions in that block are allowed to consume, the Ethereum \texttt{block gas limit} is currently 11,741,495.
+\footnote{\[July 2020:\] https://ethstats.net/}
 
-gas is what makes ethereum furnctiom,  it safegaurds the network from overload and incentivises people too keep ethereum running.
-By seperating eth from gas, txs cost are less influneced by chning price of Eth so keeping txs from being too expensive
+\subsection*{Gas Refunds.}There are two particular EVM operations with negative gas --- certain amount of gas is refunded to the sender at the end of the transaction. These operation include:
 
-gas price: how much you pay per gas unit
-gas limit: how much work you are requesting
+\paragraph{\texttt{SELFDESTRUCT}.}This operation destroys and deletes the originating contract and refunds its balance (if any) to a designated receiver address.
+Note that the Ethereum storage is implemented in the form of a has map and EVM is not statistically aware of which storage slots are held by the contract.
+Because of this the \texttt{SELFDESTRUCT} operation does not remove the initial byte code of the contract from the chain, but it frees up the state storage and has a refund of 24,000 gas.
 
-gas cost (Ether) = gasPrice * gasCost(gas)
+\paragraph{\texttt{SSTORE}.} This operation clears the Ethereum storage and has15,000 gas refunds.
 
-gas limit: is a parameter that limits the amount of gas you spend in a transaction (how to estimate? using estimateGas)
-gas price how to estimate: using ethgassation 
-by defaluth the gas minimum gas limit for ethereum txs is 21000 gas
+Note that in order to urge miners to process smart contracts with refunds, the accumulated gas refund can never exceed half the gas used up during computation~\cite{wood2014ethereum}.
+So at the end of a successful transaction, the amount of gas in the refund counter (capped at half the net gas used) is returned to the caller.
+At the time of this writing, Ethereum transaction receipts only account for the \texttt{gasUsed}, which is the total amount of gas units spent during a transaction, and we are not able to obtain the value of the EVM's refund counter from inside the EVM~\cite{signer2018gas}.
+So in order to account for refunds, we decide to calculate them manually; first we figure out exactly how much storage is being cleared or how many smart contracts are being destroyed, then we multiply these numbers by 24,000 and 15,000 respectively.
 
-a block also has a gas limit field, it defines a maximum amount of gas all txs in th eblock combined are allowed to consume.
+%gas price: how much you pay per gas unit
+%gas limit: how much work you are requesting 
+%gas cost (Ether) = gasPrice * gasCost(gas)
+%gas limit: is a parameter that limits the amount of gas you spend in a transaction (how to estimate? using estimateGas)
+%gas price how to estimate: using ethgassation 
+%by defaluth the gas minimum gas limit for ethereum txs is 21000 gas
+%a block also has a gas limit field, it defines a maximum amount of gas all txs in th eblock combined are allowed to consume.
 this block gas limit determines the maximum number of transactions within the block.
 this block gas limt is not fixed and set by miners
-
-* Gas model: gas limit, how much, per transaction vs per block, Solidity/EVM quirks: gas refunds
-
-At the time of this writing, Ethereum transaction receipts only contain the net gas consumption (\texttt{gasUsed}) and we cannot obtain the value of the EVM's refund counter from inside the EVM~\cite{signer2018gas}.
-So in order to account for refunds inside each priority queue smart contract we calculate them manually; first we figure out exactly how much storage is being cleared when dequeuing the highest priority elements (\texttt{SSTORE} instruction) and then we multiply the number of storage slots cleared by 15,000 (see the last column of Table~\ref{tab:PQUnitTests}).
-
-Note that in order to urge miners to process smart contracts with refunds, the accumulated gas refund can never exceed half the gas used up during computation~\cite{wood2014ethereum}.
+%
+%ers to process smart contracts with refunds, the accumulated gas refund can never exceed half the gas used up during computation~\cite{wood2014ethereum}.
 So at the end of a successful transaction, the amount of gas in the refund counter (capped at half the net gas used) is returned to the caller.
@@
 
-\subsubsection{Decision.} Based on enqueing, the heap variants are the cheapest in terms of gas, while based on dequeuing, the link list variants are cheapest.
+\subsubsection{Decision.} Based on enqueuing, the heap variants are the cheapest in terms of gas, while based on dequeuing, the link list variants are cheapest.
 This is in accordance with the theoretical worst-case time complexity for each.

### 2020-09-09 LaTeX/sections/paper.tex
Edits

@@
 \subsection*{Contributions.}
+Our design \cm is intended as a simple module that developers can modify as they choose.
+By adding \cm to an ERC20 (or similar) token contract, everything that is needed for buying/selling tokens is immediately available on chain without involving any third party exchanges.
+The main advantage of blockchain is low barriers of entry and this further lowers the barrier.
 
@@
 It most circumstances, the market closing algorithm does not have to consider any deeper bids/asks from the list when choosing whether the current best bid and ask can be fulfilled.
-The only exception is in the case of a tie on price, which we return to later.
+The only exceptions are in the case of a tie on price or a canceled order, both of which we return to later.
 For this reason, the ideal data structure for storing bids/asks is a \textit{priority queue} (see Table~\ref{tab:PQ_API}) where each order's priority is its price.
@@
 
-% With 50 selfdestructs
+%Although the \texttt{SELFDESTRUCT} operation does not remove the initial byte code of the contract from the chain, but it frees up the state storage and refunds 24000 gas to the caller.
 
-\subsubsection*{Linked List.} Removing the highest priority element from the list can be done in two ways.
-We can use the \texttt{SELFDESTRUCT} operation to destroy the head node of the list (\ie smart contract) from the Ethereum blockchain and transfer its funds (if any) to a payable address (\eg the current block miner or the call market contract).
-Although the \texttt{SELFDESTRUCT} operation does not remove the initial byte code of the contract from the chain, but it frees up the state storage and refunds 24000 gas to the caller.
-Another design perspective is to only update the head pointer of the linked list and leave the previous head (\ie smart contract) on Ethereum blockchain when removing the highest priority element from the list.
-Although the first technique is a bit more costly (because it adds an extra operation \texttt{SELFDESTRUCT} to the \texttt{dequeue()} function), it results in the less final net cost due to the 24000 gas refunds.
-Also, it is best to avoid storing unnecessary storage variables on chain.
-Table~\ref{tab:LLvsLLMapping} outlines different gas metrics for iteratively dequeuing highest priority elements in the two implementations of sorted linked lists that contain 50 unsigned integers.
+One consequence of a linked list is that a new contract is created for every node in the list.
+Beyond being expensive for adding new nodes (a cost that will be bared by the trader in a call market), it also leaves a large footprint on the Ethereum blockchain, especially if we leave the nodes on the blockchain in perpetuity (\ie we just update the head node of the list and leave the previous head `dangling.').
+However in a PQ, nodes are only removed from the head of the list; thus the node contracts could be `destroyed' one by one using an extra operation, \texttt{SELFDESTRUCT}, in the \texttt{dequeue()} function.
+As shown in Table~\ref{tab:cleaning}, the refund from doing this outweighs to the cost of the extra computation: gas costs are reduced from 721K to 557K.
+This suggests a general principle: cleaning up after yourself will pay for itself in gas refunds.
+Unfortunately, this is not universally true as shown by applying the same principle to the Linked List with Mapping.
 
-%---------+++++++++++++++++++-----------------
+Dequeuing in a linked list with mapping can be implemented in two ways.
+The simplest approach is process a node, update the head pointer, and leave the `removed' node's data behind in the mapping untouched (where it will never be referenced again).
+Alternatively we can call \texttt{DELETE} on each mapping entry once we are done with a node in the PQ.
+Deleting a storage variable is identical to setting a non-zero variable to zero (\texttt{SSTORE} 0) that costs 20,000 gas but with 15,000 refunded---a net positive gas cost~\cite{wood2014ethereum}.
+As it can be seen in the last two rows of Table~\ref{tab:cleaning}, leaving the data on chain is cheaper then cleaning it up.
 
-\subsubsection*{Linked List with Mapping.} Similarly, linked list with mapping can be implemented in two ways.
-For dequeuing items from this priority queue we can use the \texttt{DELETE} method and remove the mapping element that contains the highest priority item from storage completely  \textbf{and} update the head and tail pointers of the list.
-Deleting a storage variable is identical to setting a non-zero variable to zero (\texttt{SSTORE} 0) that costs 20,000 gas but with 15,000 refunded~\cite{wood2014ethereum}.
-So although the \texttt{DELETE} method refunds in 15000 gas, it is yet a gas-costly operation  as it increases the overall gas cost of the transaction.
-In another technique, we can only update the head and tail pointers of the linked list when dequeueing the highest priority item and not delete the mapping element associated with the previous pointers.
-As it can be seen in the last two columns of Table~\ref{tab:LLvsLLMapping}, this scheme consumes less gas for dequeuing 50 unsigned integers compared to the previous technique where we clear up the chain, however, leaving unnecessary storage data on chain is not a proper design practice.
+The lesson here is that gas refunds incentivize developers to clean up storage variables they will not use again, but it is highly contextual as to whether it will pay for itself.
+Further the cap on the maximum refund means that refunds are not fully received for large cleanup operations (however removing the cap impacts the miners' incentives to include the transaction).
+This is a complicated and under-explored area of Ethereum in the research literature.
+For our own work, we strive to be good citizens of Ethereum and cleanup to the extent that we can---thus all PQs in Table~\ref{tab:PQUnitTests} implement some cleanup and we select Linked List with Mapping and \texttt{DELETE} for \cm.
 
- that uses the  the \texttt{DELETE} method to clear up the chain every time the highest priority element is removed from the list. In
-
-% = = = = = = = = = = = = = Experimentations = = = = = = = = = = = = = = = = = = =  %
+% = = = = = = = = = = = = = Implementatiion = = = = = = = = = = = = = = = = = = =  %
 
@@
 
-In this research work, we design and implement a call market on the Ethereum blockchain.
-We divide the trading day into frequent but discrete time intervals; every time the market opens traders submit their ask and bid order messages.
-These orders are accumulated in a sorted data structure and when the trading period is over, orders are matched against each other.
-Our proposed decentralized exchange is both data structure and token agnostic (traders can trade ERC20 standard compliant token).
-The upcoming orders are not stored in the call market contract, instead they are stored in a priority queue where each element is associated with a priority and is served according to its priority.
-
-As mentioned in~\ref{sec:callmarket}, Our system treats the time as discrete and not continuous; upcoming orders are accumulated over predetermined time intervals and are processed in batch instead of serially in order of receipt.
-The trading day is divided into frequent but discrete time intervals; every time the market opens traders submit their ask and bid order messages.
-These orders are accumulated in a linked list with mapping priority queue and when the trading period is over, orders are matched against each other.
-The call market smart contract is written in 268 lines of Solidity, a high level programming language that is syntactically similar to Java~\cite{Ethereum41:online}, using the Truffle development framework and deployed on Ganache-CLI, Table~\ref{tab:callmarket_functions} represents the call market's primary operations.
-
 %GitHub repo:  \footnote{\CallMarketRepo}
 % = = = = = = = = = = = = = = = = = = = = =Call market operations Table = = = = = = = = = = = =  = = = = = =  %
-\begin{table}[]
+\begin{table}[t]
 \begin{tabular}{|l|l|}
@@
 
-To facilitate a safe exchange among buyers and sellers, we implement the Call Market smart contract in the form of a \textit{collateralized}; for market participants to be able to send bid and/or ask orders, they have to first supply tokens (depending on what ERC20 tokens they aim to trade) as collaterals by calling any of the  \texttt{DepositToken()} or \texttt{DepositEther()} methods.
-The collateralized call market acts as a payment guarantee so traders cannot default on payment or delivery of their assets.
+Our design \cm is intended as a module that developers can modify as they choose---thus we tried to simplify the design at every step to make it highly extensible but still functional without any extensions.
+A call market will open for a specified period of time during which it will accept orders.
+Orders are added to a PQ.
+Our vision (discussed below) is the market would be open for a very short period of time, close, and then reopen immediately (\eg every other block).
+This is akin to how a crossing network operates in traditional finance (\ie \textblue{some explanation}).
+We keep the design simple by not allowing cancellations.
+Because markets are relatively short-lived, cancelations require a second transaction (and front-running attacks apply to cancellation orders~\cite{eskandari2019sok}), orders simply expire when the market call period ends.
 
-Followings outline results of the experiments we performed using Javascript and leveraging Mocha testing framework.
+Another simplifying assumption was to implement a \textit{collateralized} call market.
+We assume all trades are between ETH and an ERC20 token, all orders are pre-funded in the contract with ETH (for bids) and tokens (for asks), and once ETH or tokens are committed to an order, they cannot be withdrawn until the market closes.
+We revisit alternatives to this design below.
+This ensures all executed orders clear and settle (\ie no defaults on payment or delivery).
 
-%============= Worst_Case_Matching_test.js Tables=================== %
+% Volume of 1
+% Ties?
 
- \subsection{Experiments}
+\cm is written in 225 lines (SLOC) of Solidity (including 3 external libraries),\footnote{Github: linked removed for anonymity} a high level programming language that is syntactically similar to Java~\cite{Ethereum41:online}.
+We tested it with the Mocha testing framework (tests included in the codebase), as deployed using Truffle on Ganache-CLI to obtain our performance metrics.
+Table~\ref{tab:callmarket_functions} represents the call market's primary operations.
 
-Table~\ref{tab:worst_case_matching} outlines the \texttt{Match()} function's computational costs and performance for three different implementations of the call market.
-We used three different designs of the linked list with mapping priority queue.
-(1) Every time a trade happens, we use the \texttt{DELETE} method to remove the mapping elements that contains best bid and ask orders from storage completely \textbf{and} update the head and tail pointers of the list.
-(2) We only update the pointers of the priority queue and do not remove the best bid and ask orders during the entire matching process.
-Instead we destroy the priority queue smart contract~\footnote{We execute a public function defined in the priority queue smart contract which itself calls the \texttt{self-destruct()} operation and transfers its funds (if any) to the call market contract.} once the matching is completed.
-(3) In the last implementation, we allow the matching process to be completed and do not clear any on chain data.
-As it can be seen in Table~\ref{tab:worst_case_matching}, the \texttt{Match()} operation shows a better performance when killing the priority contract and/or not clearing data from the chain.
-However, leaving unnecessary storage data on chain is not a proper design practice (note that as mentioned in Section~\ref{sec:LLvsLLMapping}, destroying a smart contract does not remove the initial byte code of the contract from the chain but it frees up the state storage and refunds 24000 gas to the caller.)
-The last column of Table~\ref{tab:worst_case_matching} reflects the gas cost for matching 1000 pairs of bids and asks for which we set the block gas limit to the maximum of  $2^{53}$ (the Javascript's max safe integer).
+%============= Performance =================== %
 
-Note that this is a \textit{worst case matching} test where all bids and asks are submitted as marketable limit orders with specified prices that would be filled undoubtedly, performed using the current Ethereum gas metrics (block gas limit $=$11,741,495 and 1 gas $=$ 56 gwei)~\footnote{https://ethstats.net/}.
+ \subsection{Performance}
 
-%Although deleting the priority queue contract adds an extra external call to the \texttt{Match()} function and should technically increase the gas cost, the 24000 gas refunds from \texttt{SELFDESTRUCT} would compensate the cost.
-So it can still match as same number of orders (before running out of gas) as in the no on chain clearing implementation.
+ \input{tables/performance.tex}
 
-% = = = = = = = = = = = =Worst Case Matching on Linkedlist With Mapping Table = = = = = = = = = = = = =  %
+The main research question is how many orders can be processed in a single Ethereum transaction when the closing the call market, \textblue{using Ethereum today}.
+As our previous experiments indicated, the choice of priority queue (PQ) implementation is the main influence on performance (see Table~\ref{tab:worst_case_matching}).
+We implemented a generic call market that interfaces with a generic PQ (at its own contract address) and ran experiments for each PQ implementation.
+We looked at the \textit{worst-case} for performance which is when every submitted bid and ask is marketable (\ie will require fulfillment).
+In the first two columns, we determined the highest number of orders that can be processed in a single call to \texttt{CloseMarket()} and not exceed the the current Ethereum block gas limit of 11,741,495.
+Since Ethereum will become more efficient over time, we also were interested in how much gas it would cost to execute 1000 pairs of orders which is given in the third column.
+The fourth column indicates the cost to the trader of submitting a bid or ask --- since this costs will vary depending on how many orders are already submitted (recall Figure~\ref{fig:random_insertion}), we average the cost of 200 order submissions.
 
-\begin{table}[]
-\centering
-\begin{tabular}{|c|c|c|c|}
-\hline
+As expected, the numbers closely track the performance of the PQ itself suggesting the PQ is indeed the main influence on performance.
+In Ethereum today, call markets appear to be limited to processing about a hundred orders per transaction.
+If markets open on every other block and the call market could monopolize an entire block to close, a few hundred orders per minute (worst-case) can be processed.
+The main takeaway is that the transparency, front-running resistance, and low barrier to entry of Ethereum comes with an enormous cost (\ie an institutional exchange like NASDAQ can process 100K trades per second).
+That said, many exchanges trade the same assets under different trading rules (\ie market fragmentation) because traders have different preferences.
+\cm can work today in some circumstances like very low liquidity tokens, or markets with high volumes and a small number of traders (\eg liquidation auctions).
 
-\textbf{\thead{Linked List with Mapping}}    & \textbf{\thead{Maximum Number \\ of \\ Matched Orders}}      & \textbf{\thead{Net Cost\\in Gas}}          & \textbf{\thead{Net Cost in Gas\\ for \\ 1000 Pairs \\ of Orders}}    \\ \hline
+\textblue{Optimize for closing market, even at cost of higher submission.}
 
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  = = = = = = = = = = = %
-	\textbf{\thead{Clearing the Mapping Elements}}         			& 86 pairs                					& 5,433,259                   				& 62,774,170                      \\ \hline
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  = = = = = = = = = = = %
-	\textbf{\thead{Destroying the Priority Queue Contract}}           	& 210 pairs	                     				& 5,304,211 							& 25,099,713				\\ \hline
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  = = = = = = = = = = = %
-	\textbf{\thead{No On-chain Clearing}} 		                       	& 210 pairs							& 5,299,877							& 25,095,370				\\ \hline
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  = = = = = = = = = = = %
-
-\end{tabular}
-\caption{\footnotesize{}
-\label{tab:LLMApping_worst_case_matching}}
-\end{table}
-
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
-
-% = = = = = = = = = = = =Worst_Case_Matching Table = = = = = = = = = = = = =  %
-
-\begin{table}[]
-\centering
-\begin{tabular}{|c|c|c|c|}
-\hline
-
-\textbf{\thead{Priority Queue}}    & \textbf{\thead{Maximum Number \\ of \\ Matched Orders}}      & \textbf{\thead{Net Cost\\in Gas}}          & \textbf{\thead{Net Cost in Gas\\ for \\ 1000 Pairs \\ of Orders}} \\ \hline
-
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
-	\textbf{\thead{Heap with \\ Dynamic Array}}         				& 38 pairs                & 5,372,679                   	& 457,326,935                      \\ \hline
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
-	\textbf{\thead{Heap with \\ Static Array}}           				& 42 pairs                & 5,247,636                  	& 333,656,805                       \\ \hline
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
-	\textbf{\thead{Mapping with \\ keys stored \\ in Heap}} 		& 46 pairs                & 5,285,275                     & 226,499,722                        \\ \hline
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
-	\textbf{Linkedlist}                       							& 152 pairs                & 5,495,265                     & 35,823,601                        \\ \hline
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
-	\textbf{\thead{Linkedlist with \\ Mapping}}          				& 86 pairs                 & 5,433,259                     & 62,774,170                        \\ \hline
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
-
-\end{tabular}
-\caption{\footnotesize{}
-\label{tab:worst_case_matching}}
-\end{table}
+% = = = = = = = = = = = =Clearing Mappings = = = = = = = = = = = = =  %
 
 \section{Call Market Different Design and Implementation Details }
-
-% = = = = = = = = = = = =Clearing Mappings = = = = = = = = = = = = =  %
 
@@
 
+% Cancelations
+% How quick we open and close
+%
+
 % = = = = = = = = = = = =meta_tx Figure = = = = = = = = = = = = =  %
@@
 
+% Safely returning collateral 
+% Options for non-collaterialized markets
+
 % = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
@@
 
-% = = = = = = = = = = = =Gas costs and refunds for Dequeueing 50 integers from each PQ  = = = = = = = = = = = = =  %
-
-\begin{table}[]
-\centering
-\begin{tabular}{|c|c|c|c|c|}
-\hline
-
-\textbf{\thead{Priority Queue}}    & \textbf{\thead{Net Cost\\in Gas}}      & \textbf{\thead{Total Cost\\in Gas\\(From \texttt{estimateGas})}}      & \textbf{The Difference}    & \textbf{\thead{Gas Refund \\(Manually Calculated)}} \\ \hline
-
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
-	\textbf{\thead{Heap with \\ Dynamic Array}}         				& 2,518,131               & 3,283,480		& 765,349             & 750,000                       \\ \hline
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
-	\textbf{\thead{Heap with \\ Static Array}}           				& 1,385,307                & 2,150,625     	& 765,318             & 750,000                      \\ \hline
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
-	\textbf{\thead{Mapping with \\ keys stored \\ in Heap}} 		& 2,781,684                & 4,316,229       	& 1,534,545           & 1,500,000                     \\ \hline
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
-	\textbf{Linked List}                       							& 557,085               	& 1,772,085      	& 1,215,000           & 1,200,000                      \\ \hline
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
-	\textbf{\thead{Linked List with \\ Mapping}}          				& 731,514              	& 3,731,514       	& 3,000,000     	  &  3,765,000                       \\ \hline
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
-
-\end{tabular}
-\caption{\footnotesize{The gas metrics associated with dequeuing 50 items from five priority queues.}
-\label{tab:PQUnitTests}}
-\end{table}
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
-
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
-\begin{table}[]
-\begin{tabular}{|c|c|c|c|c|}
-\hline
-\multirow{2}{*}{Gas Metrics}                        							& \multicolumn{2}{c|}{Linked List}           						& \multicolumn{2}{c|}{Linked List with Mapping}     					\\ \cline{2-5} 
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = %
-                                                                						& with \texttt{SELFDESTRUCT} 		& without \texttt{SELFDESTRUCT}                	& with \texttt{delete} 		& without \texttt{delete}              		\\ \hline                                                                                                                                                                                                                                                          % = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = %
-                   Net Cost in Gas                          					& 557,085                    			& 721,370                     				& 731,514                     	& 334,689                      				\\ \hline
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = %
-\thead{Total Cost in Gas \\ (from \texttt{estimateGas})} 		& 1,772,085                  			& 736,370                  					& 3,731,514                     	& 1,099,689                       				\\ \hline
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = %
-		    The Difference                                             		& 1,215,000                  			& 15,000                      				& 3,000,000                    	& 765,000                       				\\ \hline
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = %
-
-\end{tabular}
-\caption{\footnotesize{}
-\label{tab:LLvsLLMapping}}
-\end{table}
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
+%
+%% = = = = = = = = = = = =Gas costs and refunds for Dequeueing 50 integers from each PQ  = = = = = = = = = = = = =  %
+%
+%\begin{table}[]
+%\centering
+%\begin{tabular}{|c|c|c|c|c|}
+%\hline
+%
+%\textbf{\thead{Priority Queue}}    & \textbf{\thead{Net Cost\\in Gas}}      & \textbf{\thead{Total Cost\\in Gas\\(From \texttt{estimateGas})}}      & \textbf{The Difference}    & \textbf{\thead{Gas Refund \\(Manually Calculated)}} \\ \hline
+%
+%% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
+%	\textbf{\thead{Heap with \\ Dynamic Array}}         				& 2,518,131               & 3,283,480		& 765,349             & 750,000                       \\ \hline
+%% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
+%	\textbf{\thead{Heap with \\ Static Array}}           				& 1,385,307                & 2,150,625     	& 765,318             & 750,000                      \\ \hline
+%% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
+%	\textbf{\thead{Mapping with \\ keys stored \\ in Heap}} 		& 2,781,684                & 4,316,229       	& 1,534,545           & 1,500,000                     \\ \hline
+%% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
+%	\textbf{Linked List}                       							& 557,085               	& 1,772,085      	& 1,215,000           & 1,200,000                      \\ \hline
+%% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
+%	\textbf{\thead{Linked List with \\ Mapping}}          				& 731,514              	& 3,731,514       	& 3,000,000     	  &  3,765,000                       \\ \hline
+%% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
+%
+%\end{tabular}
+%\caption{\footnotesize{The gas metrics associated with dequeuing 50 items from five priority queues.}
+%\label{tab:PQUnitTests}}
+%\end{table}
+%% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
+%
+%% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
+%\begin{table}[]
+%\begin{tabular}{|c|c|c|c|c|}
+%\hline
+%\multirow{2}{*}{Gas Metrics}                        							& \multicolumn{2}{c|}{Linked List}           						& \multicolumn{2}{c|}{Linked List with Mapping}     					\\ \cline{2-5} 
+%% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = %
+%                                                                						& with \texttt{SELFDESTRUCT} 		& without \texttt{SELFDESTRUCT}                	& with \texttt{delete} 		& without \texttt{delete}              		\\ \hline                                                                                                                                                                                                                                                          % = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = %
+%                   Net Cost in Gas                          					& 557,085                    			& 721,370                     				& 731,514                     	& 334,689                      				\\ \hline
+%% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = %
+%\thead{Total Cost in Gas \\ (from \texttt{estimateGas})} 		& 1,772,085                  			& 736,370                  					& 3,731,514                     	& 1,099,689                       				\\ \hline
+%% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = %
+%		    The Difference                                             		& 1,215,000                  			& 15,000                      				& 3,000,000                    	& 765,000                       				\\ \hline
+%% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = %
+%
+%\end{tabular}
+%\caption{\footnotesize{}
+%\label{tab:LLvsLLMapping}}
+%\end{table}
+%% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
 

### 2020-09-14 LaTeX/sections/paper.tex
DEX eval
Added the text for static analysis

@@
 % !TEX root = ../main.tex
+
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
+\input{tables/eval.tex}
+
+\subsection*{Static Analysis of \cm}
+We used \textit{Slither}~\footnote{https://github.com/crytic/slither} and \textit{SmartCheck}~\footnote{https://tool.smartdec.net} security audit tools on the \cm to check the code  for vulnerabilities and bad practices.
+We received 100\% success rate in a total of 67 audits performed by considering 'Informational' checks as 'Passed'.
 

### 2020-09-14 LaTeX/sections/abstract.tex
front-end of paper

@@
 
-Abstract goes here
+In the early days of Ethereum, developers experimented with exchange services (for digital assets) that operated fully on the blockchain.
+However for performance reasons, this idea has been abandoned for years in favour of a hybrid model where some functionality is done on-chain (\eg loading accounts, order cancelation) and some functionality (\eg matching orders) is done off-chain.
+As blockchain performance continues to improve (both in research and in practice), it is an ideal time to revisit the idea of a fully on-chain exchange---which has a superior security threat model---to benchmark what is possible performance-wise.
+We design and optimize a call market exchange, \cm, on Ethereum, and conduct a variety of experiments to show the current benchmark is around one hundred trade executions per block.
+We also explore numerous extensions for further improvements.
 

### 2020-09-14 LaTeX/sections/appendix.tex
front-end of paper

--- 2020-09-09 LaTeX/sections/paper.tex
@@
 
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
-\section{Introductory Remarks}
-
-Blockchain is a type of distributed database (or ledger) that is open to anyone who wants to participate, robust against a wide range of faulty and malicious behaviours, and runs without anyone in charge.
-When a participant looks at her local copy of the ledger, she is assured that (i) anyone has the exact same records and (ii) each record was validated by the "majority" (technically, a computational majority) of participants before it was written into the ledger.
-Blockchain technology has rapidly gained global interest and become one of the most significant technologies in recent years.
-It was first introduced in 2008 by Satoshi Nakamoto as an underlying technology of Bitcoin, a peer to peer electronic cash system~\cite{nakamoto2019bitcoin}, whose currency reached a market capitalization of \$137 billion as of January 2020.
-In 2014, a new blockchain based application known as Ethereum was introduced by Buterin~\cite{buterin2014next}.
-By implementing a decentralized virtual machine, Ethereum virtual machine (EVM), Ethereum allows network users to execute programmable smart contracts on it.
-So developers are now able to build decentralized applications (DApps) that are executed correctly according to the consensus rules of the Ethereum network.
-
-% = = = = = = = = = = = = = = = = =
-\subsection*{Contributions.}
-Our design \cm is intended as a simple module that developers can modify as they choose.
-By adding \cm to an ERC20 (or similar) token contract, everything that is needed for buying/selling tokens is immediately available on chain without involving any third party exchanges.
-The main advantage of blockchain is low barriers of entry and this further lowers the barrier.
-
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
-\section{Preliminaries}
-
-Strong interest in blockchain and distributed ledger technologies has led into the high trading volume of digital assets and emergence of fast growing cryptocurrency exchanges all over the world.
-These crypto exchanges are similar to stock exchanges but, as the name suggests, facilitate the trading process of different cryptocurrency tokens.
-Basically, such exchanges provide a trading venue where market participants can buy and/or sell cryptocurrency assets among one another.
-In this section, we describe two types of crypto exchanges.
-
-\subsection{Blockchain}
-
-\begin{itemize}
-
-% transparency, front-running:
-\item \textbf{Transparency and Front-running.} Blockchains (in general)  are transparent --- transactions are first relay around the network before being selected by a miner, validated, and included in a block.
-This allows malicious nodes/miners to observe and front-run the transactions by dropping them or attempting to insert their own transactions before the observed transactions~\cite{eskandari2019sok}.
-In the context of a DEX, front-running attacks enable malicious nodes to have their orders executed before others and benefit from it.
-
-% slow but is becoming more efficient over time, expensive
-\item \textbf{Speed.} Blockchains are not fast architectures --- speed is one of the factors that diminishes the real world potential of blockchains.
-Blockchains are slow-moving as it takes block interval (\ie time it takes to mine a block) for transactions to be confirmed and included in valid blocks.
-So it is difficult to push a stock market on the blockchain as stock markets move extremely fast.
-High-frequency trading (HFT) is a trading method example that uses active computers to process a large number of trades in fractions of a second.
-In Ethereum 1.0 blocks are produced at intervals every 10 to19 seconds, note that this is not yet suitable for time sensitive transactions.
-However, capabilities of blockchains will be further enhanced ad they will become more efficient over time; Ethereum 2.0 has a shorter block time of 12 seconds.
-
-% Gas model: gas limit, how much, per transaction vs per block, Solidity/EVM quirks: gas refunds
-\item \textbf{Gas Parameter in Ethereum Transactions.}
+\section{Ethereum's Gas Model}
 
@@
 So at the end of a successful transaction, the amount of gas in the refund counter (capped at half the net gas used) is returned to the caller.
-
-Based on these issues blockchains cannot solve this particular problem.
-Many stock exchanges that currently operate on blockchains tackle this issue by using a private network (where not every network participant can be a node or miner) together with a central time-server that establishes the time priority.
-We propose a different method of implementing a fully decentralized exchange using an alternative data structure known as \textit{a call market} or \textit{frequent batch auction} instead of a time-sensitive order book~\cite{clark2014decentralizing}.
-
-\end{itemize}
-
-\subsection{Exchanges}
-
-% = = = = = = = = = = = = = = = = =
-\subsubsection{Centralized Exchanges (CEX)}\label{sec:CEX}
-
-This group of exchanges operate in a traditional manner by providing a centralized platform controlled by exchange operators.
-Essentially, the exchange acts as a trusted party whom the market participants must trust to handle their assets.
-Traders transfer the ownership of their assets to the exchange who safeguards customer funds using different methods.
-Centralized exchanges ease trading process of digital assets as they do not place the burden of safeguarding of the assets onto individualst, however, traders must fully trust the exchange operator in taking custody of their assets (\eg Coinbase).~\footnote{https://www.coinbase.com} Similar to any centralized platform these exchanges are not completely immune to malicious activities.
-For example in February 2014, a famous centralized Tokyo-based Bitcoin exchange called MtGox was hacked which led to loss of 650,000 Bitcoins~\cite{TheHisto45:online}.
-Also, a malicious exchange operator can simply steal users' funds; in February 2019, QuadrigaCX, Canada’s well-known centralized cryptocurrency exchange, claimed that it cannot access to \$190-million worth of customers’ funds~\cite{SEBIOrde83:online}.
-
-% = = = = = = = = = = = = = = = = =
-\subsubsection{Decentralized Exchanges (DEX)}
-
-Unlike centralized exchanges, DEXes facilitate a secure automated peer-to-peer trading process on blockchains (\eg Ethereum) for market participants with no third parties involved, hence solving the issues that are inherent in centralized exchanges.
-This group of exchanges provide a better security and privacy by enabling traders to remain fully authoritative over their funds and personal data.
-With rising of Decentralized Finance (DeFi) or Open Finance movements, the number of DEX platforms on Ethereum have recently exploded and large volume of trading now occurs on DeFi exchanges (\eg Uniswap).~\footnote{https://uniswap.org}
-
-However due to the high cost and technical limitations introduced by blockchain technologies, building a fully decentralized exchange has remained a major challenge.
-In the following section, we explore the idea of building a decentralized exchange on Ethereum.
-
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
-
-\subsection{Order Books}
-
-Order books are electronic data structures that maintain lists of bid and ask orders for various assets (\eg currencies, stocks, bonds \etc) in specific markets.
-The most common version of order books is a \textit{double auction}, where market participants submit their bid and ask orders and the market clearing price will be calculated as the average between the best bid and ask prices.
-Order books often sort orders based on their price and submission time, this order allocation technique is called price-time priority~\cite{preis2011price} where orders are prioritized from highest price to lowest and given any two orders with the same price, they will be sorted based on their submission timestamps.
-
-Looking more closely, order books are rather electronic ledgers that get updated over time.
-Given the definition of the Ethereum blockchain, that is a distributed ledger, the idea of implementing an order book in the form of a smart contract will seemingly resolve the existing issues with centralized exchanges (see Section~\ref{sec:CEX}).
-However, this design is not feasible due to some technical limitations that exist within blockchains:
-
-% = = = = = = = = = = = = = = = = =
-\begin{itemize}
-%---------+++++++++++++++++++-----------------
-
-\item \textbf{Speed.} All blockchains are slow-moving as it takes block intervals for transactions to get confirmed.
-On the other hand stock markets move very fast;  high-frequency trading (HFT) is a trading method example that uses active computers to process a large number of trades in fractions of a second.
-
-%---------+++++++++++++++++++-----------------
-
-\item \textbf{Front-running and Censorship.} Traders must broadcast their order messages to the network before they can be placed in the block (\ie order book).
-In such scenario, privileged nodes and miners can front-run transactions or completely drop (censor) those that are competing with their own~\cite{eskandari2019sok}.
-Also, miners could almost control how the order book gets updated by inserting their own order messages after viewing all other orders and before mining the block .
-
-%---------+++++++++++++++++++-----------------
-
-\item \textbf{Enforcing Time.} There is no notion of time on blockchains.I if two orders arrive at the same price, in the normal world whoever is the first wins.
-However, we cannot enforce the priority of orders in the blockchain space; if Alice is more well-connected to the network her order gets broadcast better and executed first although she sends it after Bob.
-
-%---------+++++++++++++++++++-----------------
-\end{itemize}
-% = = = = = = = = = = = = = = = = =
-
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
-
-\section{Priority Queue}\label{sec:pq}
-
-% = = = = = = = = = = = =Operations for a generic Priority Queue Table = = =  = = = = = = = = = = = %
-\begin{table}[t]
-\centering
-\begin{tabular}{|c|c|}
-\hline
-
-\textbf{Operation}   & \textbf{Description}    \\ \hline
-
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
-	\textbf{Enqueue()}       	& inserts an element into the priority queue                        \\ \hline
-	\textbf{Dequeue()}		& removes and returns the highest priority element 		\\ \hline
-	\textbf{isEmpty()}			& checks if the priority queue is empty 					\\ \hline
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
-
-\end{tabular}
-\caption{\footnotesize{Operations for a generic Priority Queue.}
-\label{tab:PQ_API}}
-\end{table}
-% = = = = = = = = = = = = = = = = = = = = =  = = = = = = = = = = =  = = = = = = = = = == = = =  = =%
-
-In designing \cm, performance within Ethereum's limited gas model became the main bottleneck.
-Within a call market, recording trades and accessing them to close the market is the most time consuming step.
-For this reason, we decided to do a deep study of the best data-structure for this specific task.
-While data structures are well studied for many languages, Solidity/EVM have their own quirks (\eg gas refunds, a relatively cheap mapping data structure, and no actual support for object oriented programming) that make them difficult to assess which will perform best without actually deploying and evaluating each variant.
-
-When closing a call market, the orders are examined in order: highest to lowest price for bids, and lowest to highest price for asks.
-It most circumstances, the market closing algorithm does not have to consider any deeper bids/asks from the list when choosing whether the current best bid and ask can be fulfilled.
-The only exceptions are in the case of a tie on price or a canceled order, both of which we return to later.
-For this reason, the ideal data structure for storing bids/asks is a \textit{priority queue} (see Table~\ref{tab:PQ_API}) where each order's priority is its price.
-Specifically, we use two PQs---one for bids where the highest price is the highest priority, and one for asks where the lowest price is the highest priority.
-
-There are numerous ways of implementing a PQ.
-A PQ has an underlying list---common options include a static array, dynamic array, and linked list.
-The most expensive operation is keeping the data sorted---common options include (i) sorting during each enqueue, (ii) sorting for each dequeue, or (iii) splitting the difference by using a heap as the underlying data structure.
-Respectively, the time complexities are (i) linear enqueue and constant dequeue, (ii) constant enqueue and linear dequeue, and (iii) logarithmic enqueue and logarithmic dequeue.
-This said, Solidity/EVM has its own specific considerations to take into account.
-As closing the market is very expensive with any PQ, we rule out using (ii) as fully sorting while dequeuing would be prohibitive.
-We experiment with the following 5 options for (i) and (iii):
-
-% = = = = = = = = = = = = = = = = =
-\begin{enumerate}
-
-%---------+++++++++++++++++++-----------------
-
-\item\textbf{{Heap with Dynamic Array.}} A heap is a type of binary tree data structure that comes in two forms of a (i) Max-Heap and (ii) Min-Heap.
-All the nodes of tree are in a specific order and the root of the tree always represents the highest priority item of the data structure (the largest and smallest values in the Max-Heap and Min-Heap respectively).
-We implemented a priority queue with a heap that stores its data in a dynamically-sized array.
-
-%---------+++++++++++++++++++-----------------
-
-\item\textbf{{Heap with Static Array.}} A heap can be also represented by a Solidity storage array in which the storage is statically allocated.
-To do this, we pass the required size of the array as a constructor parameter to the priority queue smart contract.
-
-%---------+++++++++++++++++++-----------------
-
-\item\textbf{{Heap with Mapping.}} In the above implementations, the heap stores the entire order (as a struct) in the heap.
-In this variant, we store the order struct in a Solidity mapping and store the mapping's key in the heap.
-
-%---------+++++++++++++++++++-----------------
-
-\item\textbf{{Linked List.}} In this variant, we insert a new element into its correct position (based on its price) when running enqueue.
-The PQ itself stores elements in a linked list (enabling us to efficiently insert a new element between two existing elements).
-Solidity is described as object-oriented but the equivalent of an object is an entire smart contract.
-Therefore an object-oriented linked list must either (i) create each node in the list as a struct---but this is not possible as Solidity does not support recursive structs---or (ii) make every node in the list its own contract.
-The latter option seems wasteful and unusual, but we try it out anyways.
-Thus each node is its own contract and contains the order data and a pointer to the address of the next contract in the list.
-
-%---------+++++++++++++++++++-----------------
-
-\item\textbf{{Linked List with Mapping.}} Finally, we try a variant of a linked list using a Solidity mapping.
-The value of the mapping is a struct with order data and the key of the next (and previous) node in the list.
-The contract stores the key of the first node (head) in the list.
-
-%---------+++++++++++++++++++-----------------
-
-\end{enumerate}
-% = = = = = = = = = = = = = = = = =
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
-
-\subsection{Priority Queue Evaluation}
-
-\subsubsection{Enqueue performance.} We implemented, deployed, and tested each priority queue using Truffle and Ganache.\footnote{Github: Link removed for anonymity.} We tried a variety of tests (including testing the full call market with each varient) with consistent results in performance.
-A simple test to showcase the performance profile is shown in Figure~\ref{fig:random_insertion}.
-We simply enqueue 50 integers chosen at random from a fixed interval in each PQ variant.
-The bigger the PQ gets, the longer enqueue takes---a linear increase for the linked list variants, and logarithmic for the heap variants.
-
-% = = = = = = = = = = = =random_insertion Figure = = = = = = = = = = = = =  %
-
-\begin{figure}[t]
-\centering
-\includegraphics[width=0.8\textwidth]{fig/random_insertion.png}
-\caption{\footnotesize{Gas costs for enqueuing random items into five different priority queue variants.
-For the x-axis, a value of 10 indicates it is the 10th number entered in the priority queue.
-The y-axis is the cost of enqueue in gas.}  \label{fig:random_insertion}}
-\end{figure}
-
-\input{tables/dequeue.tex}
-
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
-
-\subsubsection{Dequeue performance.} For each PQ variant storing 50 random integers, the \texttt{Dequeue()} function is iterated until the data structure is empty.
-The total gas cost for fully dequeuing the priority queue variants is outlined in Table~\ref{tab:PQUnitTests}.
-These tests are performed using the following Ethereum gas metrics: block gas limit $=$11,741,495 and 1 gas $=$ 56 gwei.\footnote{\[July 2020:\] https://ethstats.net/} Dequeuing removes data from the contract's storage.
-Recall this results in a gas refund.
-Based on our manual estimates (EVM does not expose the refund counter), every variant receives the maximum gas refund possible (\ie half the total cost of the transaction).
-In other words, each of them actually consumes twice the \texttt{gasUsed} amount in gas before the refund, however none of them are better or worst based on how much of a refund they generate.
-
-\subsubsection{Decision.} Based on enqueuing, the heap variants are the cheapest in terms of gas, while based on dequeuing, the link list variants are cheapest.
-This is in accordance with the theoretical worst-case time complexity for each.
-However, (i) the linked list variants are materially cheaper than the heap variants at dequeuing, and (ii) dequeuing in a call market must be done as a batch, whereas enqueuing is paid for one at a time by the trader submitting the order, and (iii) Ethereum will not permit more than hundreds of orders so the asymptotic behaviour is not a significant factor.
-For these reasons, we suggest using a linked list variant for this specific application.
-As it can be seen in Figure~\ref{fig:random_insertion}, the associated cost for inserting elements into a linked list PQ is significantly greater than the linked list with mapping, as each insertion cause the creation of a new contracts.
-Accordingly, we choose to implement the call market with the linked list with mapping.
-Overall this PQ balances a moderate gas cost for insertion (\ie order submission) with one for removal (\ie matching the orders).
-
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
-%  = = = = = = Table 2 (dequeue) Conversions = = = = = = %
-%
-%As of July 2020,  $1 gas = 56\times10^{-9} ether$\footnote{https://ethstats.net/} and 1 ether = \$238.33\footnote{https://coinmarketcap.com/}.
-%
-%$Transaction cost (eth) = GasUsed (unit) \times Gas Price (eth)$ 
-%
-%%  = = = = = = Transaction Costs in eth = = = = = = %
-%
-%Heap with Dynamic Array:    		$2,518,131 \times 56\times10^{-9} = 141,015,336\times 10^{-9}$
-%Heap with Dynamic Array:     		$1,385,307 \times 56\times10^{-9} = 77,577,192\times 10^{-9}$
-%Heap with Mapping:              		$2,781,684 \times 56\times10^{-9} = 155,774,304\times 10^{-9}$
-%Linked List:						$557,085 \times 56\times10^{-9} = 	31,196,760\times 10^{-9}$
-%Linked List with Mapping:			$731,514 \times 56\times10^{-9} = 	40,964,784\times 10^{-9}$
-%
-%%  = = = = = = Transaction Costs in USD = = = = = = %
-%
-%Heap with Dynamic Array:    		$141,015,336\times 10^{-9} \times 238.33 = \$33.60$
-%Heap with Dynamic Array:     		$77,577,192\times 10^{-9} \times 238.33 = \$18.48$
-%Heap with Mapping:              		$155,774,304\times 10^{-9} \times 238.33 = \$37.12$
-%Linked List:						$31,196,760\times 10^{-9} \times 238.33 = \$7.43$
-%Linked List with Mapping:			$40,964,784\times 10^{-9} \times 238.33 = \$9.76$
-%
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
-
-\subsection{Cost/Benefit of cleaning up after yourself}
-\label{sec:LLvsLLMapping}
-\label{sec:gasrefund}
-
-\input{tables/cleaning.tex}
-
-%---------+++++++++++++++++++-----------------
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
-
-%  = = = = = = Table 3 (cleaning.tex) Conversions = = = = = = %
-
-%As of July 2020,  $1 gas = 56\times10^{-9} ether$\footnote{https://ethstats.net/} and 1 ether = \$238.33\footnote{https://coinmarketcap.com/}.
-%
-%$Transaction cost (eth) = GasUsed (unit) \times Gas Price (eth)$ 
-%
-%%  = = = = = = Transaction Costs in eth = = = = = = %
-%
-%Linked List with \texttt{SELFDESTRUCT}:     				$557,085 \times 56\times10^{-9} =  31,196,760\times 10^{-9}$  
-%Linked List w/o \texttt{SELFDESTRUCT}:     				$721,370 \times 56\times10^{-9} =  40,396,720\times 10^{-9}$ 
-%Linked List with Mapping and \texttt{DELETE}:    			$731,514 \times 56\times10^{-9} =  40,964,784\times 10^{-9}$ 
-%Linked List with Mapping and w/o \texttt{DELETE}: 		$334,689 \times 56\times10^{-9} =  18,742,584\times 10^{-9}$ 
-%
-%%  = = = = = = Transaction Costs in USD = = = = = = %
-%
-%Linked List with \texttt{SELFDESTRUCT}:     				$31,196,760\times 10^{-9}  \times 238.33 = \$7.43$
-%Linked List w/o \texttt{SELFDESTRUCT}:     				$40,396,720\times 10^{-9} \times 238.33 = \$9.62$
-%Linked List with Mapping and \texttt{DELETE}:    			$40,964,784\times 10^{-9}  \times 238.33 = \$9.76$
-%Linked List with Mapping and w/o \texttt{DELETE}: 		$18,742,584\times 10^{-9} \times 238.33 = \$4.46$
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
-
-%Although the \texttt{SELFDESTRUCT} operation does not remove the initial byte code of the contract from the chain, but it frees up the state storage and refunds 24000 gas to the caller.
-
-One consequence of a linked list is that a new contract is created for every node in the list.
-Beyond being expensive for adding new nodes (a cost that will be bared by the trader in a call market), it also leaves a large footprint on the Ethereum blockchain, especially if we leave the nodes on the blockchain in perpetuity (\ie we just update the head node of the list and leave the previous head `dangling.').
-However in a PQ, nodes are only removed from the head of the list; thus the node contracts could be `destroyed' one by one using an extra operation, \texttt{SELFDESTRUCT}, in the \texttt{dequeue()} function.
-As shown in Table~\ref{tab:cleaning}, the refund from doing this outweighs to the cost of the extra computation: gas costs are reduced from 721K to 557K.
-This suggests a general principle: cleaning up after yourself will pay for itself in gas refunds.
-Unfortunately, this is not universally true as shown by applying the same principle to the Linked List with Mapping.
-
-Dequeuing in a linked list with mapping can be implemented in two ways.
-The simplest approach is process a node, update the head pointer, and leave the `removed' node's data behind in the mapping untouched (where it will never be referenced again).
-Alternatively we can call \texttt{DELETE} on each mapping entry once we are done with a node in the PQ.
-Deleting a storage variable is identical to setting a non-zero variable to zero (\texttt{SSTORE} 0) that costs 20,000 gas but with 15,000 refunded---a net positive gas cost~\cite{wood2014ethereum}.
-As it can be seen in the last two rows of Table~\ref{tab:cleaning}, leaving the data on chain is cheaper then cleaning it up.
-
-The lesson here is that gas refunds incentivize developers to clean up storage variables they will not use again, but it is highly contextual as to whether it will pay for itself.
-Further the cap on the maximum refund means that refunds are not fully received for large cleanup operations (however removing the cap impacts the miners' incentives to include the transaction).
-This is a complicated and under-explored area of Ethereum in the research literature.
-For our own work, we strive to be good citizens of Ethereum and cleanup to the extent that we can---thus all PQs in Table~\ref{tab:PQUnitTests} implement some cleanup and we select Linked List with Mapping and \texttt{DELETE} for \cm.
-
-% = = = = = = = = = = = = = Implementatiion = = = = = = = = = = = = = = = = = = =  %
-
-\section{Call Market Design}
-
-%GitHub repo:  \footnote{\CallMarketRepo}
-% = = = = = = = = = = = = = = = = = = = = =Call market operations Table = = = = = = = = = = = =  = = = = = =  %
-\begin{table}[t]
-\begin{tabular}{|l|l|}
-\hline
-\multicolumn{1}{|c|}{\textbf{Operation}} & \multicolumn{1}{c|}{\textbf{Description}}                            			\\ \hline
-
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
-	DepositToken()                           & Deposits ERC20 standard compliant tokens in the call market contract \\ \hline
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
-	DepositEther()                           	& Deposits Ethers in the call market contract                         			 \\ \hline
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
-	OpenMarket()                             & Opens the market                                                    					 \\ \hline
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
-	CloseMarket()                            & Closes the market                                                    					\\ \hline
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
-	SubmitBid()                              & Inserts the upcoming bid order messages inside the priority queue    \\ \hline
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
-	SubmitAsk()                              & Inserts the upcoming ask order messages inside the priority queue    \\ \hline
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
-	MatchOrders()                           & Matches the orders against each other                                			\\ \hline
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
-	ClaimTokens()                           & Transfers collateral tokens back to the trader                       			\\ \hline
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
-	ClaimEther()                             & Transfers collateral Ethers back to the trader                       			\\ \hline
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
-\end{tabular}
-\caption{\footnotesize{Primary operations of the call market smart contract.}
-\label{tab:callmarket_functions}}
-\end{table}
-
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
-
-Our design \cm is intended as a module that developers can modify as they choose---thus we tried to simplify the design at every step to make it highly extensible but still functional without any extensions.
-A call market will open for a specified period of time during which it will accept orders.
-Orders are added to a PQ.
-Our vision (discussed below) is the market would be open for a very short period of time, close, and then reopen immediately (\eg every other block).
-This is akin to how a crossing network operates in traditional finance (\ie \textblue{some explanation}).
-We keep the design simple by not allowing cancellations.
-Because markets are relatively short-lived, cancelations require a second transaction (and front-running attacks apply to cancellation orders~\cite{eskandari2019sok}), orders simply expire when the market call period ends.
-
-Another simplifying assumption was to implement a \textit{collateralized} call market.
-We assume all trades are between ETH and an ERC20 token, all orders are pre-funded in the contract with ETH (for bids) and tokens (for asks), and once ETH or tokens are committed to an order, they cannot be withdrawn until the market closes.
-We revisit alternatives to this design below.
-This ensures all executed orders clear and settle (\ie no defaults on payment or delivery).
-
-% Volume of 1
-% Ties?
-
-\cm is written in 225 lines (SLOC) of Solidity (including 3 external libraries),\footnote{Github: linked removed for anonymity} a high level programming language that is syntactically similar to Java~\cite{Ethereum41:online}.
-We tested it with the Mocha testing framework (tests included in the codebase), as deployed using Truffle on Ganache-CLI to obtain our performance metrics.
-Table~\ref{tab:callmarket_functions} represents the call market's primary operations.
-
-%============= Performance =================== %
-
- \subsection{Performance}
-
- \input{tables/performance.tex}
-
-The main research question is how many orders can be processed in a single Ethereum transaction when the closing the call market, \textblue{using Ethereum today}.
-As our previous experiments indicated, the choice of priority queue (PQ) implementation is the main influence on performance (see Table~\ref{tab:worst_case_matching}).
-We implemented a generic call market that interfaces with a generic PQ (at its own contract address) and ran experiments for each PQ implementation.
-We looked at the \textit{worst-case} for performance which is when every submitted bid and ask is marketable (\ie will require fulfillment).
-In the first two columns, we determined the highest number of orders that can be processed in a single call to \texttt{CloseMarket()} and not exceed the the current Ethereum block gas limit of 11,741,495.
-Since Ethereum will become more efficient over time, we also were interested in how much gas it would cost to execute 1000 pairs of orders which is given in the third column.
-The fourth column indicates the cost to the trader of submitting a bid or ask --- since this costs will vary depending on how many orders are already submitted (recall Figure~\ref{fig:random_insertion}), we average the cost of 200 order submissions.
-
-As expected, the numbers closely track the performance of the PQ itself suggesting the PQ is indeed the main influence on performance.
-In Ethereum today, call markets appear to be limited to processing about a hundred orders per transaction.
-If markets open on every other block and the call market could monopolize an entire block to close, a few hundred orders per minute (worst-case) can be processed.
-The main takeaway is that the transparency, front-running resistance, and low barrier to entry of Ethereum comes with an enormous cost (\ie an institutional exchange like NASDAQ can process 100K trades per second).
-That said, many exchanges trade the same assets under different trading rules (\ie market fragmentation) because traders have different preferences.
-\cm can work today in some circumstances like very low liquidity tokens, or markets with high volumes and a small number of traders (\eg liquidation auctions).
-
-\textblue{Optimize for closing market, even at cost of higher submission.}
-
-% = = = = = = = = = = = =Clearing Mappings = = = = = = = = = = = = =  %
-
-\section{Call Market Different Design and Implementation Details }
-
-\subsection{Clearing Mappings}
-
-To maintain the collateral balance of each market participant, we use two Solidity type one-to-one mappings that map Ethereum addresses to 256 bits unsigned integers; \texttt{TotalBalance} and \texttt{UnavailableBalance}.
-Once market closes and orders are matched, the \texttt{UnavailableBalance} needs to be cleared.
-However, since it is not possible to delete the entire mapping without knowing the keys~\footnote{https://solidity.readthedocs.io/en/v0.5.12/security-considerations.html}, clearing the \texttt{UnavailableBalance} mapping remains a challenging issue to solve.
-Here we provide a landscape of solutions for that.
-%only individual keys and what they map to can be deleted.
-
-\begin{itemize}
-
-%---------+++++++++++++++++++-----------------
-\item \textbf{Creating a New Mapping Every Time the Market Opens.} Instead of clearing the \texttt{UnavailableBalance} of traders at the end of a matching process, we could create a new mapping every time the market opens.
-Note that in this scheme traders can claim their funds back (using the \texttt{ClaimEther()} and/or \texttt{ClaimToken} methods) only when the market is closed (\ie the market is in the \texttt{Closed} state).
-
-%---------+++++++++++++++++++-----------------
-\item \textbf{Creating Custom Keys for the Mapping.} We can create custom keys for the mapping by defining a counter as a global variable inside the call market smart contract and increment it only once at the end of the matching process.
-So instead of clearing the mapping, we only use another portion of it every time the market opens.
-
-%---------+++++++++++++++++++-----------------
-\item \textbf{Storing the Mapping in a Data-Contract.} Another design proposal is to create a new smart contract every time the market opens, this data contract only stores the \texttt{UnavailableBalance} mapping and will be destroyed (using the \texttt{SELFDESTRUCT} operation) at the end of the matching process.
-
-%---------+++++++++++++++++++-----------------
-\item \textbf{Storing the Mapping keys in an additional Array.} Another common pattern is to create an additional array on top of the mapping and iterate over that.
-This array (\eg address[]) stores the traders' addresses and enables us to iterate over the mapping and delete individual keys and what they map to at the end of the matching process.
-Note that this is a gas-costly design pattern as we would need to maintain a secondary data structure.
-
-%---------+++++++++++++++++++-----------------
-\end{itemize}
-
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
-
-% = = = = = = = = = = = =Closing and Reopening the Market = = = = = = = = = = = = =  %
-
-\subsection{Closing and Reopening the Market}
-
-% We use one-shot market for the sake of our performance tests on different data structures. and once we have all the numbers we can think about iterated market.
-
-At the end of the trading period, the market needs to be closed and reopened.
-However, there is no automatic process to called an Ethereum function and contracts can only run when a function is called.
-
-%when to close the market?
-%What time period?
-
-\begin{itemize}
-% = = = = = = = = = = = =How to enforce time on on the Ethereum blockchain? = = = = = = = = = = = = =  %
-
-\item\textbf{{Enforcing Time on the Blockchain.}}
-
-% We want the market to run on a periodic schedule => it is difficult for market participants to call the \texttt{Close()} function periodically.
-
-% However there are incentives for them to do so: (i) they get paid and refunded (financial incentives), and (ii) Closing the market allow market participants to open it again and start their trading activities
-
-% Another solution pattern to enforce the time is to use the Ethereum Alarm Clock
-
-% = = = = = = = = = = = =Who Pays the Cost for Closing and Reopening the Market?= = = = = = = = = = = = =  %
-
-\item\textbf{{Who Pays the Cost for Closing and Reopening the Market?}}
-
-We think it is useful to explore the landscape of possible designs for closing the market.
-
-\begin{itemize}
-
-%= = = = = = Miners Close the Market = = = = = = =%
-\item \textbf {Miners Close and Reopen the Market.} The difference between the best bid and ask prices is called the \textit{bid-ask spread}.
-In our design, when the trade occurs between the the highest bid (the highest amount a buyer is willing to pay for an asset) and lowest ask (the lowest amount a seller is willing to accept for an asset) orders, the bid-ask spread is paid to the miner.
-There are possibilities that (i) no trade occurs or (ii) the bid-ask spread is zero (\ie the best bid and best ask prices are identical).
-So there is enough economic incentive for the the miner to execute the \texttt{CloseMarket()} function and get refunded as the refund amount could be potentially higher than the bid-ask spread.
-% = = = = = = = = = =Processing Orders in Groups= = = = = = = = = = = = = = = %
-
-\item \textbf{Processing Orders in Groups.} Another solution pattern is to process certain number of bid and ask orders upon every execution of the \texttt{CloseMarket()} function rather than treating them as one substantial transaction.
-A market participant $P_i$ would process $n$ orders from the previous market (\texttt{CloseMarket(n)}) when sending new orders to the current market.
-This process continues until all the orders in the previous markets are processed.
-% incentive?
-=> contribution to the community!?
-%= = = = = =  = =  =  Meta txs =  = = = = = = = = =%
-
-\item \textbf {Using the Meta Transactions.} Meta transactions enable users to execute Ethereum functions without paying the gas.
-Rather than spending gas, users sign their intended action using their private keys and broadcast it to the network with no cost.
-A third party process (\textit{a relayer}) then crafts the actual transaction on user's behalf, sends the transaction to the Ethereum blockchain, and charges the base contract with the associated fees (see Figure~\ref{fig:meta_tx}).
-The required gas to pay for the \texttt{Match()} function could be collected as fees.
-So market participants are charged with certain amounts of fees every time they submit an order, these fees are accumulated in the CallMarket contract and will be used to pay for executing the \texttt{CloseMarket()} function.
-
-% Cancelations
-% How quick we open and close
-%
-
-% = = = = = = = = = = = =meta_tx Figure = = = = = = = = = = = = =  %
-
-\begin{figure}[htb!p]
-\centering
-\includegraphics[width=0.8\textwidth]{fig/meta_tx.png}
-\caption{\footnotesize{}  \label{fig:meta_tx}}
-\end{figure}
-
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
-
-%= = = = = =  = =  =  Users close and get refunded with the contract funds (collected as fees during order submissions) =  = = = = = = = = =%
-
-\item \textbf{Using the "Contract Pays" Model.} An alternative solution is to design the market such that the last person to submit an order calls the \texttt{CloseMarket()} function, but in contrast to a normal transaction (where the person initiating the transaction must pay the fee), here the CallMarket contract pays the cost for closing the market and matching the orders respectively.
-To enforce this design we can use Solidity function modifiers; every time a new order is submitted, a function modifier checks whether (i) the auction period has to end and/or (ii) the maximum number of total orders has reached.
-If any of these two conditions are met, the \texttt{CloseMarket()} will be called.
-Again, market participants are charged with certain amounts of fees every time they submit an order, these fees are accumulated in the CallMarket.
-Once the \texttt{CloseMarket()} is successfully executed and orders are matched, the contract transfers its funds to that person.
-Note that here the person must still have enough gas to cover the execution of the transaction as the funds will be only transferred after the transaction is fully executed.
-However, market participants are incentivized to do so as they may receive more ethers than they have spent.
-
-%= = = = = =  = =  =  Rollups=  = = = = = = = = =%
-
-\item \textbf{Using Rollups.} Rollup is a scaling method that moves the storage and computation of the smart contracts off-chain while maintaining the transaction data on the main chain as call-data.
-In this technique, any Ethereum user can act as a validator; they can execute the \texttt{CloseMarket()}function and only post the new state of the contract (the updated balance of traders) in the form of \textit{assertions} to the main chain.
-Rollups improve scalability, provide faster and cheaper execution of the contracts, and eliminate the gas limit as the contract is no longer executed on-chain.
-In the followings we briefly discuss different rollup proposals and techniques. Each approach uses a different method to ensure correction of assertions:
-
-\begin{itemize}
-
-\item \textbf{{Non-interactive Rollups.}} In this rollup technique, assertions are posted together with a validity proof that would be later used by validators to check if the \texttt{CloseMarket()} function has been executed correctly.
-ZK-Rollup scheme is one of the solutions that uses ZK-SNARKs to prove the validity of the assertions in zero-knowledge.
-ZK proofs are quick and cheap to verify but they are expensive and time consuming to generate.
-These proofs could be generated (i) for free or (ii) the CallMarket contract could collect proportional fees for every trade that is successfully executed.
-
-\item \textbf{{Optimistic Rollups.}} In this scheme, assertions are assumed to be valid if there is no dispute posted about them with a certain window of time (a.k.a.
-"the challenge period').
-Here, dispute resolution is a gas-costly method as the CallMarket contract would have to emulate the transaction on-chain to ensure the correctness the assertion.
-This scheme introduces a tradeoff between privacy and performance as all the assertions are publicly available and accessible.
-However, here the new state only reflects the updated balances of traders and no secret is involved.
-
-\item \textbf {{Multi-round Interactive Rollups.}} In this design paradigm, \textit{pending assertions} are posted on-chain and they are open to dispute.
-Once the challenge period is over and no challenge is submitted, the assertion is confirmed and the CallMarket contract transitions to the new state (\ie updates traders' balances).
-This scheme takes the overhead for the CallMarket contract to execute the \texttt{Close()} on-chain by using rounds to the dispute resolutions.
-The two parties (asserter and challenger) must run an interactive protocol and the CallMarket smart contract would have to act as a referee and decides which party's claim is true.
-Arbitrum is an example of multi-round interactive rollups that uses an efficient challenge-based protocol to penalize the dishonest parties~\cite{kalodner2018arbitrum}.
-
-\end{itemize}
-
-%= = = = = =  = =  =  SGX=  = = = = = = = = =%
-
-\item \textbf{{Using Trusted Execution Environments.}} Another way of achieving execution of the \texttt{CloseMarket()} function is incorporating the Ethereum blockchain into the Trusted Execution Environments (TEEs) and decoupling the contract execution from consensus mechanism.
-TEEs enable secure execution of applications in an isolated processing environment called the \textit{enclave}.
-Here, the enclave could execute the \texttt{CloseMarket()} function off-chain in TEEs and publish an on-chain attestation Quote to the CallMarket contract.
-The contract then verifies the correctness of the Quote and if validated correctly, it transitions to the new state.
-Ekiden is an example that uses Intel SGX to solve the scalability and confidentiality issues with the smart contract execution~\cite{cheng2019ekiden}.
-A drawback of this scheme is in order to achieve confidentiality-preserving smart contracts we have to trust a trusted party in the form of the hardware manufacturer (\eg Intel).
-
-\end{itemize}
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
-\end{itemize}
-
-% = = = = = = = = = = = =Transferring the Collateral back to the traders = = = = = = = = = = = = =  %
-\subsection{Transferring the Collateral back to Traders.}
-
-% Safely returning collateral 
-% Options for non-collaterialized markets
-
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
-
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
-
-% = = = = = = = = = = = =Notes Discussed in Meetings = = = = = = = = = = = = =  %
-
-% Our two competitors are Uinswap and Loopring (that uses ZK roll ups):
-% 	1- Uniswap: we can argue that in traditional markets we have various traditional exchanges. Each of these exchanges have different trading rules and designs which work for different traders.
-%	2- Loopring:
-%		2-1: Barrier to entry: In order for a trader to trade specific ERC20 on Loopring, Loopring has to agree to support that token.
-It might not be difficult and they probably approve the token as long as it is standard compliant.
-%		2-2: ZK proofs are quick and cheap to verify but they are expensive and time consuming to generate: (1) now they are generating these proofs for free but later they charge traders for doing that.
-(2) Looping does not probably generate these proofs per every block so the settlement and 				clearing is not happening per block.
-So we have faster clearing and settlement as we clear everything per block.
-% 		2-3: Loopring is non-custodial, meaning that the money moves only when the proofs come, so there is a latency in transferring funds to the traders.
-
-% The heap with dynamic array can do 26 pairs of matches at worst case matching whereas Linkedliat does 90 pairs.
-So if we want to cap the orders over 4 PQs, we’re basically increasing the heap size which makes match more expensive for nothing (every time a match happens and the root is deleted the whole heap is reheapified)
-
-% There will be no ties as we use 2 counters for buy and sell orders. These counters are concatenated them with the price. So we somehow enforce time priority
-
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
-
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
-%The tables I changed after estimateGas, Not sure which ones to keep. Should talk to Jeremy
-
-%
-%% = = = = = = = = = = = =Gas costs and refunds for Dequeueing 50 integers from each PQ  = = = = = = = = = = = = =  %
-%
-%\begin{table}[]
-%\centering
-%\begin{tabular}{|c|c|c|c|c|}
-%\hline
-%
-%\textbf{\thead{Priority Queue}}    & \textbf{\thead{Net Cost\\in Gas}}      & \textbf{\thead{Total Cost\\in Gas\\(From \texttt{estimateGas})}}      & \textbf{The Difference}    & \textbf{\thead{Gas Refund \\(Manually Calculated)}} \\ \hline
-%
-%% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
-%	\textbf{\thead{Heap with \\ Dynamic Array}}         				& 2,518,131               & 3,283,480		& 765,349             & 750,000                       \\ \hline
-%% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
-%	\textbf{\thead{Heap with \\ Static Array}}           				& 1,385,307                & 2,150,625     	& 765,318             & 750,000                      \\ \hline
-%% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
-%	\textbf{\thead{Mapping with \\ keys stored \\ in Heap}} 		& 2,781,684                & 4,316,229       	& 1,534,545           & 1,500,000                     \\ \hline
-%% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
-%	\textbf{Linked List}                       							& 557,085               	& 1,772,085      	& 1,215,000           & 1,200,000                      \\ \hline
-%% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
-%	\textbf{\thead{Linked List with \\ Mapping}}          				& 731,514              	& 3,731,514       	& 3,000,000     	  &  3,765,000                       \\ \hline
-%% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
-%
-%\end{tabular}
-%\caption{\footnotesize{The gas metrics associated with dequeuing 50 items from five priority queues.}
-%\label{tab:PQUnitTests}}
-%\end{table}
-%% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
-%
-%% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
-%\begin{table}[]
-%\begin{tabular}{|c|c|c|c|c|}
-%\hline
-%\multirow{2}{*}{Gas Metrics}                        							& \multicolumn{2}{c|}{Linked List}           						& \multicolumn{2}{c|}{Linked List with Mapping}     					\\ \cline{2-5} 
-%% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = %
-%                                                                						& with \texttt{SELFDESTRUCT} 		& without \texttt{SELFDESTRUCT}                	& with \texttt{delete} 		& without \texttt{delete}              		\\ \hline                                                                                                                                                                                                                                                          % = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = %
-%                   Net Cost in Gas                          					& 557,085                    			& 721,370                     				& 731,514                     	& 334,689                      				\\ \hline
-%% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = %
-%\thead{Total Cost in Gas \\ (from \texttt{estimateGas})} 		& 1,772,085                  			& 736,370                  					& 3,731,514                     	& 1,099,689                       				\\ \hline
-%% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = %
-%		    The Difference                                             		& 1,215,000                  			& 15,000                      				& 3,000,000                    	& 765,000                       				\\ \hline
-%% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = %
-%
-%\end{tabular}
-%\caption{\footnotesize{}
-%\label{tab:LLvsLLMapping}}
-%\end{table}
-%% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
-
-%======================================== %
-
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
-
-\section{Concluding Remarks}
-
-%\subsubsection*{Acknowledgements.} J. Clark thanks ...

### 2020-09-14 LaTeX/sections/paper.tex
front-end of paper

--- 2020-09-09 LaTeX/sections/paper.tex
@@
 % = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
+
 \section{Introductory Remarks}
 
-Blockchain is a type of distributed database (or ledger) that is open to anyone who wants to participate, robust against a wide range of faulty and malicious behaviours, and runs without anyone in charge.
-When a participant looks at her local copy of the ledger, she is assured that (i) anyone has the exact same records and (ii) each record was validated by the "majority" (technically, a computational majority) of participants before it was written into the ledger.
-Blockchain technology has rapidly gained global interest and become one of the most significant technologies in recent years.
-It was first introduced in 2008 by Satoshi Nakamoto as an underlying technology of Bitcoin, a peer to peer electronic cash system~\cite{nakamoto2019bitcoin}, whose currency reached a market capitalization of \$137 billion as of January 2020.
-In 2014, a new blockchain based application known as Ethereum was introduced by Buterin~\cite{buterin2014next}.
-By implementing a decentralized virtual machine, Ethereum virtual machine (EVM), Ethereum allows network users to execute programmable smart contracts on it.
-So developers are now able to build decentralized applications (DApps) that are executed correctly according to the consensus rules of the Ethereum network.
+For better or worst, blockchain technologies like Ethereum have dramatically lowered the barrier to entry for developing and deploying financial technology.
+New tokens have been launched with a few clicks of a user interface, and large investment infrastructures have been developed and deployed with little regulatory oversight.
+Blockchain exchange services allow order-based trading of digital currencies, tokens, and other digital assets.
+Such exchanges are a key component to blockchain-based economic activity.
+
+For years, exchanges have operated either entirely off-chain by trusted operators or partially on-chain by semi-trusted operators.
+A fully on-chain exchange is feasible but considered too slow, at least for a public blockchain like Ethereum.
+We believe it is a very good time to do a deep dive into understanding precisely \textit{how slow} for the following reasons: (1) public blockchains are becoming faster (both in theory and slowly in practice) and the efficiency of an on-chain exchange will increase in time, (2) demand for on-chain trading is exemplified by the recent popularity of dealer-based (or quote-based) trading like Uniswap and Curve Finance, and (3) stablecoins have become a popular and allow on-chain trading with pricing in USD (or other government currency).
 
 % = = = = = = = = = = = = = = = = =
-\subsection*{Contributions.}
-Our design \cm is intended as a simple module that developers can modify as they choose.
+
+\paragraph{Contributions.}
+
+We design and implement \cm, a fully on-chain call market in Solidity---a high-level programming language for Ethereum.
+We choose Ethereum as a `hostile' environment for an orderbook: Ethereum is public (strongest adversary) and slow (lower-bound benchmark) relative to more scalable blockchains, including the anticipated Ethereum 2.0.
+\cm is intended as a simple module that developers can modify as they choose.
 By adding \cm to an ERC20 (or similar) token contract, everything that is needed for buying/selling tokens is immediately available on chain without involving any third party exchanges.
-The main advantage of blockchain is low barriers of entry and this further lowers the barrier.
+\cm is non-custodial, transparent, and mitigates front-running attacks that are generally possible on-chain.
 
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
-\section{Preliminaries}
-
-Strong interest in blockchain and distributed ledger technologies has led into the high trading volume of digital assets and emergence of fast growing cryptocurrency exchanges all over the world.
-These crypto exchanges are similar to stock exchanges but, as the name suggests, facilitate the trading process of different cryptocurrency tokens.
-Basically, such exchanges provide a trading venue where market participants can buy and/or sell cryptocurrency assets among one another.
-In this section, we describe two types of crypto exchanges.
-
-\subsection{Blockchain}
-
-\begin{itemize}
-
-% transparency, front-running:
-\item \textbf{Transparency and Front-running.} Blockchains (in general)  are transparent --- transactions are first relay around the network before being selected by a miner, validated, and included in a block.
-This allows malicious nodes/miners to observe and front-run the transactions by dropping them or attempting to insert their own transactions before the observed transactions~\cite{eskandari2019sok}.
-In the context of a DEX, front-running attacks enable malicious nodes to have their orders executed before others and benefit from it.
-
-% slow but is becoming more efficient over time, expensive
-\item \textbf{Speed.} Blockchains are not fast architectures --- speed is one of the factors that diminishes the real world potential of blockchains.
-Blockchains are slow-moving as it takes block interval (\ie time it takes to mine a block) for transactions to be confirmed and included in valid blocks.
-So it is difficult to push a stock market on the blockchain as stock markets move extremely fast.
-High-frequency trading (HFT) is a trading method example that uses active computers to process a large number of trades in fractions of a second.
-In Ethereum 1.0 blocks are produced at intervals every 10 to19 seconds, note that this is not yet suitable for time sensitive transactions.
-However, capabilities of blockchains will be further enhanced ad they will become more efficient over time; Ethereum 2.0 has a shorter block time of 12 seconds.
-
-% Gas model: gas limit, how much, per transaction vs per block, Solidity/EVM quirks: gas refunds
-\item \textbf{Gas Parameter in Ethereum Transactions.}
-
-Gas is the Ethereum's pseudo-currency and a key variable for the execution of smart contracts.
-DApps written in high-level programming languages are compiled and translated into a compact representation (called ‘bytecode’) to be further executed on the Ethereum virtual machine or EVM.
-Each of these opcodes has a fixed amount of gas assigned and is a measure of computational effort.
-Separating ETH from gas prevents transactions cost from being too expensive as they are less impacted by ETH price fluctuations.
-Gas unit does not a have a monetary value and as mentioned, it only  measures the computational work undertaken by miners.
-To pay miners, Ethereum introduces a \texttt{gas price} --- small denomination of ether called \textbf{Gwei} attached to each gas unit.
-Essentially, gas price indicates how much users are willing to pay per unit of gas, clearly the higher gas price leads to the faster execution of a transaction.
-Miners also need to know the total amount of computational work a user is requesting, called the \texttt{gas limit}.
-\texttt{Gas limit} is a parameter that limits the amount of gas users would spend in a transaction.
-It protects users from spending unlimited ETH on their transactions and must be set carefully.
-If the \texttt{gas limit} is too low, the transaction will exceed the limit, all operations will be reverted while the user must pay for the computational work performed by the miner.
-By default the gas limit for an Ethereum transaction is 21,000 gas.
-An Ethereum block also has a \texttt{block gas limit} field which is set by the Ethereum miners and indicates the maximum amount of gas all the transactions in that block are allowed to consume, the Ethereum \texttt{block gas limit} is currently 11,741,495.
-\footnote{\[July 2020:\] https://ethstats.net/}
-
-\subsection*{Gas Refunds.}There are two particular EVM operations with negative gas --- certain amount of gas is refunded to the sender at the end of the transaction. These operation include:
-
-\paragraph{\texttt{SELFDESTRUCT}.}This operation destroys and deletes the originating contract and refunds its balance (if any) to a designated receiver address.
-Note that the Ethereum storage is implemented in the form of a has map and EVM is not statistically aware of which storage slots are held by the contract.
-Because of this the \texttt{SELFDESTRUCT} operation does not remove the initial byte code of the contract from the chain, but it frees up the state storage and has a refund of 24,000 gas.
-
-\paragraph{\texttt{SSTORE}.} This operation clears the Ethereum storage and has15,000 gas refunds.
-
-Note that in order to urge miners to process smart contracts with refunds, the accumulated gas refund can never exceed half the gas used up during computation~\cite{wood2014ethereum}.
-So at the end of a successful transaction, the amount of gas in the refund counter (capped at half the net gas used) is returned to the caller.
-At the time of this writing, Ethereum transaction receipts only account for the \texttt{gasUsed}, which is the total amount of gas units spent during a transaction, and we are not able to obtain the value of the EVM's refund counter from inside the EVM~\cite{signer2018gas}.
-So in order to account for refunds, we decide to calculate them manually; first we figure out exactly how much storage is being cleared or how many smart contracts are being destroyed, then we multiply these numbers by 24,000 and 15,000 respectively.
-
-%gas price: how much you pay per gas unit
-%gas limit: how much work you are requesting 
-%gas cost (Ether) = gasPrice * gasCost(gas)
-%gas limit: is a parameter that limits the amount of gas you spend in a transaction (how to estimate? using estimateGas)
-%gas price how to estimate: using ethgassation 
-%by defaluth the gas minimum gas limit for ethereum txs is 21000 gas
-%a block also has a gas limit field, it defines a maximum amount of gas all txs in th eblock combined are allowed to consume.
-this block gas limit determines the maximum number of transactions within the block.
-this block gas limt is not fixed and set by miners
-%
-%ers to process smart contracts with refunds, the accumulated gas refund can never exceed half the gas used up during computation~\cite{wood2014ethereum}.
-So at the end of a successful transaction, the amount of gas in the refund counter (capped at half the net gas used) is returned to the caller.
-
-Based on these issues blockchains cannot solve this particular problem.
-Many stock exchanges that currently operate on blockchains tackle this issue by using a private network (where not every network participant can be a node or miner) together with a central time-server that establishes the time priority.
-We propose a different method of implementing a fully decentralized exchange using an alternative data structure known as \textit{a call market} or \textit{frequent batch auction} instead of a time-sensitive order book~\cite{clark2014decentralizing}.
-
-\end{itemize}
-
-\subsection{Exchanges}
-
-% = = = = = = = = = = = = = = = = =
-\subsubsection{Centralized Exchanges (CEX)}\label{sec:CEX}
-
-This group of exchanges operate in a traditional manner by providing a centralized platform controlled by exchange operators.
-Essentially, the exchange acts as a trusted party whom the market participants must trust to handle their assets.
-Traders transfer the ownership of their assets to the exchange who safeguards customer funds using different methods.
-Centralized exchanges ease trading process of digital assets as they do not place the burden of safeguarding of the assets onto individualst, however, traders must fully trust the exchange operator in taking custody of their assets (\eg Coinbase).~\footnote{https://www.coinbase.com} Similar to any centralized platform these exchanges are not completely immune to malicious activities.
-For example in February 2014, a famous centralized Tokyo-based Bitcoin exchange called MtGox was hacked which led to loss of 650,000 Bitcoins~\cite{TheHisto45:online}.
-Also, a malicious exchange operator can simply steal users' funds; in February 2019, QuadrigaCX, Canada’s well-known centralized cryptocurrency exchange, claimed that it cannot access to \$190-million worth of customers’ funds~\cite{SEBIOrde83:online}.
-
-% = = = = = = = = = = = = = = = = =
-\subsubsection{Decentralized Exchanges (DEX)}
-
-Unlike centralized exchanges, DEXes facilitate a secure automated peer-to-peer trading process on blockchains (\eg Ethereum) for market participants with no third parties involved, hence solving the issues that are inherent in centralized exchanges.
-This group of exchanges provide a better security and privacy by enabling traders to remain fully authoritative over their funds and personal data.
-With rising of Decentralized Finance (DeFi) or Open Finance movements, the number of DEX platforms on Ethereum have recently exploded and large volume of trading now occurs on DeFi exchanges (\eg Uniswap).~\footnote{https://uniswap.org}
-
-However due to the high cost and technical limitations introduced by blockchain technologies, building a fully decentralized exchange has remained a major challenge.
-In the following section, we explore the idea of building a decentralized exchange on Ethereum.
+While Solidity and EVM are like many common programming languages, they also have quirks that require experimentation to best optimize performance (\eg factoring in the gas costs of operations, gas refunds, limits to Solidity's object oriented design, clearing mappings).
+We test five priority queues---the core data structure of the call market---and various options for cleaning up our data once finished with it.
+The bottom line is that the current benchmark for a \cm-esque design is in the low hundreds of trade executions per block on Ethereum today.
+This positions \cm as a feasible design for certain types of markets today (low liquidity, small number of traders) but also as an early study on technology that is likely to improve vastly in the coming years.
 
@@
 
-\subsection{Order Books}
+\section{Preliminaries}
 
-Order books are electronic data structures that maintain lists of bid and ask orders for various assets (\eg currencies, stocks, bonds \etc) in specific markets.
-The most common version of order books is a \textit{double auction}, where market participants submit their bid and ask orders and the market clearing price will be calculated as the average between the best bid and ask prices.
-Order books often sort orders based on their price and submission time, this order allocation technique is called price-time priority~\cite{preis2011price} where orders are prioritized from highest price to lowest and given any two orders with the same price, they will be sorted based on their submission timestamps.
+\subsection{Market Structure}
 
-Looking more closely, order books are rather electronic ledgers that get updated over time.
-Given the definition of the Ethereum blockchain, that is a distributed ledger, the idea of implementing an order book in the form of a smart contract will seemingly resolve the existing issues with centralized exchanges (see Section~\ref{sec:CEX}).
-However, this design is not feasible due to some technical limitations that exist within blockchains:
+\paragraph{Execution systems.} There are three main approaches to arranging a trade.
+In a \emph{quote-driven} market, a dealer uses their own inventory to offer a price for buying or selling an asset.
+In a \emph{brokered exchange}, a broker finds a buyer and seller.
+In an \emph{order-driven} market, offers to buy (\emph{bids}) and sell (\emph{offers}/\emph{asks}) from many traders are placed as orders in an orderbook.
+Order-driven markets can be \emph{continuous}, with buyers/sellers at any time adding orders to the orderbook (\emph{makers}) or executing against an existing order (\emph{takers}); or they can be \emph{called}, where all traders submit orders within a window of time and orders are matched in a batch like an auction.
 
-% = = = = = = = = = = = = = = = = =
-\begin{itemize}
-%---------+++++++++++++++++++-----------------
+\subsection{Decentralized Order Matching}
 
-\item \textbf{Speed.} All blockchains are slow-moving as it takes block intervals for transactions to get confirmed.
-On the other hand stock markets move very fast;  high-frequency trading (HFT) is a trading method example that uses active computers to process a large number of trades in fractions of a second.
+\paragraph{Central exchanges (CEX).} Traditional financial markets (\eg NYSE and NASDAQ) use order-matching systems to arrange trades.
+An exchange will list one or more assets (stocks, bonds, derivatives, or more exotic securities) to be traded with each given its own orderbook priced in a currency (\eg USD).
+Exchanges for blockchain-based assets (also called cryptoassets by enthusiasts) can operate the same way, using a centralized exchange (CEX) design where a firm operates the platform as a trusted third party in every aspect: custodianship over assets/currency being traded, exchanging assets fairly, and offering the best possible price execution.
+Security breaches and fraud (\eg MtGox~\cite{TheHisto45:online}, QuadrigaCX~\cite{SEBIOrde83:online}, and many others) in centralized exchanges have become a common source of lost funds for users, while accusations of unfair trade execution have been levelled but are difficult to prove.
 
-%---------+++++++++++++++++++-----------------
+\paragraph{On-chain orderbooks.} For trades between two blockchain-based assets (\eg a digital asset priced with a cryptocurrency, stablecoin, or second digital asset), order matching can be performed `on-chain' by deploying the order-matching system either on a dedicated blockchain or inside a decentralized application (DApp; \textit{a.k.a.} smart contract).
+In this model, traders entrust their assets to an autonomously operating DApp with known source code instead of a third party custodian that can abscond with or lose the funds.
+The trading rules will operate as coded, clearing and settling can be guaranteed, and order submission is handled by the blockchain---a reasonably fair and transparent system (but see front-running below).
+Finally, anyone can create an on-chain orderbook for any asset (on the same chain) at any time.
+While they sound ideal, performance is a substantial issue and the main subject of this paper.
 
-\item \textbf{Front-running and Censorship.} Traders must broadcast their order messages to the network before they can be placed in the block (\ie order book).
-In such scenario, privileged nodes and miners can front-run transactions or completely drop (censor) those that are competing with their own~\cite{eskandari2019sok}.
-Also, miners could almost control how the order book gets updated by inserting their own order messages after viewing all other orders and before mining the block .
+In this paper, we focus on benchmarking an orderbook for a public blockchain (\eg Ethereum).
+Ethereum is widely-used and we stand to learn the most from working in a performance-hostile environment (\ie Ethereum is good lower-bound).
+Exchanges could be given their own dedicated blockchain, where trade execution logic can be moved at the consensus level.
+Permissioned blockchains (\eg NASDAQ Linq, tZero) can also increase execution time and throughput, possibly with some reduction in transparency and trust.
 
-%---------+++++++++++++++++++-----------------
+\paragraph{On-chain dealers.} Another on-chain advantage is that other smart contracts, not just human users, can initiate trades, enabling broader decentralized finance (DeFi) applications.
+This has fuelled a resurgence in on-chain exchange but through a quote-driven design rather than an order-driven one.
+Automated market makers  (\eg Uniswap) have all the trust advantages of an on-chain orderbook, plus they are very efficient relative to an on-chain orderbook.
+The trade-off is that they operate as a dealer---the DApp exchanges assets from its own inventory.
+This inventory is loaded into the DApp by an investor who will not make money on the trades themselves, but hope for long term profit through trading fees.
+By contrast, an orderbook requires no upfront inventory and does not have to charge trading fees (but can).
+Finally, there is a complicated difference in their price dynamics (\eg market impact of a trade, slippage between the best bid/offer and actual average execution price, \etc)---deserving of an entire research paper to precisely define.
+We leave it as an assertion that with equal liquidity, orderbooks have more favourable price dynamics for traders.
 
-\item \textbf{Enforcing Time.} There is no notion of time on blockchains.I if two orders arrive at the same price, in the normal world whoever is the first wins.
-However, we cannot enforce the priority of orders in the blockchain space; if Alice is more well-connected to the network her order gets broadcast better and executed first although she sends it after Bob.
+\paragraph{Hybrid designs.} Before on-chain dealers became prominent in the late 2010s, the most popular design was hybrid order-driven exchanges with some trusted off-chain components and some on-chain functionality.
+Some (\eg EtherDelta) were envisioned as operating fully on-chain, but performance limitations drove developers to move key components, such as the order matching system, off-chain to a centralized database.
+A landscape of DEX designs exist: many avoiding taking custodianship of assets off-chain, and virtually all (for order-driven markets) operate the orderbook itself off-chain.
+A non-custodial DEX solves the big issue of a CEX---the operator stealing the funds---however trade execution is still not provably fair.
+A mitigation is to issue a proof of correct execution to the DApp (\eg Loopring) but these proofs have blindspots (discussed in section~\ref{sec:rollups}).
+\cm offers key advantages in this model.
 
-%---------+++++++++++++++++++-----------------
-\end{itemize}
-% = = = = = = = = = = = = = = = = =
+\subsection{Related Work}
+
+\paragraph{Blockchain limitations and solution.} While an orderbook is a ledger and blockchains provide a distributed ledger, it is not straightforward to drop a continuous-time orderbook onto a blockchain.
+An older 2014 paper~\cite{clark2014decentralizing} on the `Princeton prediction market'~\cite{Bra13} motivates our work.
+The authors observe the following limitations of on-chain continous orderbooks: block intervals are slow and not continuous, there is no support for accurate time-stamping, transactions can be dropped or reordered by miners, fast traders can react to submitted orders/cancelations when broadcast to network but not in a block and have their orders appear first (as examined in later work on front-running: \cite{eskandari2019sok,daian2019flash}).
+
+\paragraph{Call markets.} The researchers propose using a call market instead of a continuous-time market~\cite{clark2014decentralizing}.
+Orders are collected and placed into the orderbook over a window of time (\eg 1 or more blocks), then the market is closed and the orders are processed in batch: the best bids are matched to the best asks in order.
+If the prices overlap, the miner keeps the difference (which they could extract anyways through front-running).
+Call markets largely side-step front-running attacks from other traders because reordering trades has no impact (discussed more in section~\ref{sec:front}).
+The paper does not include an implementation and was envisioned as an alt-coin (Ethereum was still in development in 2014) with market closing being done by the miners themselves as part of the blockchain logic.
+
+Large exchanges, like the NYSE and NASDAQ, use a two minute call market every day at opening and closing time (in between, the exchange runs as a continuous time market).
+Other exchanges, called crossing networks, also operate as a call market at various times throughout the trading day.\footnote{A crossing network uses a secondary market for determining the closing price.
+Many prominent crossing networks are operated internally within a brokerage for its clients, and often as a `	dark pool' with an unpublished orderbook.} Call market are studied widely in finance~\cite{Har03}.
+Time-sensitive traders submit orders early, especially in crossing networks that close at a randomly determined time (traders risk missing the call if they wait too long).
+A blockchain happens to provide this function naturally, as blocks are published unpredictably.
+Price-sensitive traders wait to base their pricing off the already submitted orders and do not mind missing a call if it obtains them a better price.
 
 % = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
 
-\section{Priority Queue}\label{sec:pq}
+\section{Priority Queues}\label{sec:pq}
 
-% = = = = = = = = = = = =Operations for a generic Priority Queue Table = = =  = = = = = = = = = = = %
-\begin{table}[t]
-\centering
-\begin{tabular}{|c|c|}
-\hline
+\input{tables/pq.tex}
 
-\textbf{Operation}   & \textbf{Description}    \\ \hline
-
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
-	\textbf{Enqueue()}       	& inserts an element into the priority queue                        \\ \hline
-	\textbf{Dequeue()}		& removes and returns the highest priority element 		\\ \hline
-	\textbf{isEmpty()}			& checks if the priority queue is empty 					\\ \hline
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
-
-\end{tabular}
-\caption{\footnotesize{Operations for a generic Priority Queue.}
-\label{tab:PQ_API}}
-\end{table}
-% = = = = = = = = = = = = = = = = = = = = =  = = = = = = = = = = =  = = = = = = = = = == = = =  = =%
-
-In designing \cm, performance within Ethereum's limited gas model became the main bottleneck.
-Within a call market, recording trades and accessing them to close the market is the most time consuming step.
-For this reason, we decided to do a deep study of the best data-structure for this specific task.
-While data structures are well studied for many languages, Solidity/EVM have their own quirks (\eg gas refunds, a relatively cheap mapping data structure, and no actual support for object oriented programming) that make them difficult to assess which will perform best without actually deploying and evaluating each variant.
+In designing \cm within Ethereum's gas model, performance is the main bottleneck.
+For a call market, processing all the trades and closing the market is the most time consuming step.
+The most critical design decision is the data structure for holding orders.
+While data structures are well studied for many languages, Solidity/EVM has its own unique aspects (\eg gas refunds, a relatively cheap mapping data structure, only partial support for object oriented programming) that creates difficulties in assessing which will perform best without actually deploying and evaluating each variant.
 
@@
 Respectively, the time complexities are (i) linear enqueue and constant dequeue, (ii) constant enqueue and linear dequeue, and (iii) logarithmic enqueue and logarithmic dequeue.
-This said, Solidity/EVM has its own specific considerations to take into account.
 As closing the market is very expensive with any PQ, we rule out using (ii) as fully sorting while dequeuing would be prohibitive.
@@
 The total gas cost for fully dequeuing the priority queue variants is outlined in Table~\ref{tab:PQUnitTests}.
-These tests are performed using the following Ethereum gas metrics: block gas limit $=$11,741,495 and 1 gas $=$ 56 gwei.\footnote{\[July 2020:\] https://ethstats.net/} Dequeuing removes data from the contract's storage.
+These tests are performed using the following Ethereum gas metrics: block gas limit $=$11,741,495 and 1 gas $=$ 56 gwei.\footnote{EthStats (July 2020): \url{https://ethstats.net/}} Dequeuing removes data from the contract's storage.
 Recall this results in a gas refund.
@@
 
-\subsubsection{Decision.} Based on enqueuing, the heap variants are the cheapest in terms of gas, while based on dequeuing, the link list variants are cheapest.
+\subsubsection{Discussion.} Based on enqueuing, the heap variants are the cheapest in terms of gas, while based on dequeuing, the link list variants are cheapest.
 This is in accordance with the theoretical worst-case time complexity for each.
@@
 
+\subsection{Front-running} \label{sec:front}
+% Front running -> drop trades, move to next block, can't front-run
+% Take 1000 trades over a window of time -> shuffle -> what is different between A and B?u
+% No price improvement changes people waiting to trade?
+
 \subsection{Clearing Mappings}
@@
 
+\label{sec:rollups}
 \item \textbf{Using Rollups.} Rollup is a scaling method that moves the storage and computation of the smart contracts off-chain while maintaining the transaction data on the main chain as call-data.

### 2020-09-14 LaTeX/tables/pq.tex
front-end of paper

% = = = = = = = = = = = =Operations for a generic Priority Queue Table = = =  = = = = = = = = = = = %
\begin{table}[t]
\centering
\begin{tabular}{|c|c|}
\hline

\textbf{Operation}   & \textbf{Description}    \\ \hline

% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
	\textbf{Enqueue()}       	& inserts an element into the priority queue                        \\ \hline
	\textbf{Dequeue()}		& removes and returns the highest priority element 		\\ \hline
	\textbf{isEmpty()}			& checks if the priority queue is empty 					\\ \hline
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %

\end{tabular}
\caption{\footnotesize{Operations for a generic Priority Queue.}
\label{tab:PQ_API}}
\end{table}
% = = = = = = = = = = = = = = = = = = = = =  = = = = = = = = = = =  = = = = = = = = = == = = =  = =%

### 2020-09-14 LaTeX/sections/paper.tex

@@
 % !TEX root = ../main.tex
-
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
 
@@
 
+\subsection*{Static Analysis of \cm}
+We used \textit{Slither}~\footnote{https://github.com/crytic/slither} and \textit{SmartCheck}~\footnote{https://tool.smartdec.net} security audit tools on the \cm to check the code  for vulnerabilities and bad practices.
+We received 100\% success rate in a total of 67 audits performed by considering 'Informational' checks as 'Passed'.
+
 % = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %

### 2020-09-14 LaTeX/tables/eval.tex

% !TEX root = ../main.tex

\begin{table}[t]
\centering
\begin{tabular}{|l|c|p{0.4cm}|p{0.4cm}|p{0.4cm}|p{0.4cm}|p{0.4cm}|p{0.4cm}|p{0.4cm}|p{0.4cm}|p{0.4cm}|p{0.4cm}|p{0.4cm}|}

\multicolumn{1}{c}{\textbf{Exchange Platform}} & 
\multicolumn{1}{c}{\textbf{Examples}} & 
\headrow{Less Censorable} & 
\headrow{Minimum/ No  Trust} & 
\headrow{Fast Updates (No Latency)} & 
\headrow{High Performance} &
\headrow{Low Cost} &
\headrow{All ERC20 Compatible} &
\headrow{No Custody of Order Book} &
\headrow{No Custody of Funds} &
\headrow{Accurate Price Discovery} &
\headrow{High Transparency} &
\headrow{Automatic Matching} \\

\hline

% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = == = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
\multirow{2}{*}{DEX w/ On-chain Order Book }      	& Bitshares		&\multirow{2}{*}{\full }		&\multirow{2}{*}{\full }		&\multirow{2}{*}{\prt }		&\multirow{2}{*}{half }		&\multirow{2}{*}{half }		&\multirow{2}{*}{half } 		&\multirow{2}{*}{\full }		&\multirow{2}{*}{\full }		&\multirow{2}{*}{\full }		&\multirow{2}{*}{\full }		&\multirow{2}{*}{\full } 		\\ 													
											&Stellar			& 						&						&						&						&						&						&						&						&						& 						&						\\  \hline						
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = == = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
\multirow{3}{*}{DEX w/ Off-chain Order Book}        &0x				&\multirow{3}{*}{half}		&\multirow{3}{*}{half }		&\multirow{3}{*}{\full }		&\multirow{3}{*}{\full }		&\multirow{3}{*}{\full }		&\multirow{3}{*}{\full } 		&\multirow{3}{*}{\prt }		&\multirow{3}{*}{\full }		&\multirow{3}{*}{\full }		&\multirow{3}{*}{\prt }		&\multirow{3}{*}{half } 		\\ 
							                      	&EtherDelta		& 						&						&						&						&						&						&						&						&						& 						&						\\
										       &IDEX     		& 						&						&						&						&						&						&						&						&						& 						&						\\ \hline
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = == = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
\multirow{3}{*}{Automated Market Making DEX}    &UniSwap		&\multirow{3}{*}{\full}		&\multirow{3}{*}{half }		&\multirow{3}{*}{ DN}		&\multirow{3}{*}{half}		&\multirow{3}{*}{ half}		&\multirow{3}{*}{half} 		&\multirow{3}{*}{ \full}		&\multirow{3}{*}{ \prt}		&\multirow{3}{*}{\full }		&\multirow{3}{*}{ \full}		&\multirow{3}{*}{ DN} 		\\ 
							                      	&Bancor			& 						&						&						&						&						&						&						&						&						& 						&						\\
										       &Curve     		& 						&						&						&						&						&						&						&						&						& 						&						\\ \hline			
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = == = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
\multirow{3}{*}{CEX}    							&Binance		&\multirow{3}{*}{\prt}		&\multirow{3}{*}{\prt}		&\multirow{3}{*}{\full}		&\multirow{3}{*}{\full}		&\multirow{3}{*}{\full}		&\multirow{3}{*}{\full} 		&\multirow{3}{*}{\full}		&\multirow{3}{*}{\prt}		&\multirow{3}{*}{\prt}		&\multirow{3}{*}{\prt }		&\multirow{3}{*}{\full } 		\\ 
							                      	&Coinbase		& 						&						&						&						&						&						&						&						&						& 						&						\\
										       &Bitfinex     		& 						&						&						&						&						&						&						&						&						& 						&						\\ \hline	
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = == = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
\multicolumn{2}{|c|}{Auction Based Model (us)}       & 						&						&						&						&						&						&						&						&						& 						&						\\ \hline
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = == = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %

\end{tabular}
\caption{\footnotesize{Comparative evaluation of different types of exchange platforms: {\full} indicates the properties (columns) are fulfilled by the corresponding mechanism (rows) within reason, {\prt} means the property is not fulfilled, \textblue{say sth about half dot when you figure out how to generate it}}
\label{tab:eval}}
\end{table}

### 2020-09-14 LaTeX/sections/abstract.tex
more edits

--- 2020-04-30 LaTeX/sections/abstract.tex
@@
 \begin{abstract}
-
-Abstract goes here
-
+Order-driven exchanges on Ethereum tend to operate in a fully centralized fashion, or with some functionality performed on-chain (\eg loading accounts, order cancelation) and some off-chain functionality (\eg matching orders).
+Fully on-chain solutions have a superior threat model and were experimented with in the early days of Ethereum, but they have been largely abandoned for performance reasons.
+As blockchain performance continues to improve (both in research and in practice) and on-chain dealer-based exchanges like Uniswap (an alternative to order-based exchanges) rise in popularity, it seems to be an ideal time to revisit the idea of a fully on-chain order-driven exchange and benchmark what is possible performance-wise.
+We design and optimize an Ethereum-based call market exchange, \cm, and conduct a variety of experiments to show the current benchmark is around one hundred trade executions per block.
+We also explore numerous extensions for further improvements.
 \end{abstract}

### 2020-09-14 LaTeX/sections/paper.tex
more edits

--- 2020-09-14 LaTeX/sections/paper.tex
@@
 
-% = = = = = = = = = = = = = = = = =
-
-\paragraph{Contributions.}
-
-We design and implement \cm, a fully on-chain call market in Solidity---a high-level programming language for Ethereum.
+\paragraph{Contributions.} We design and implement \cm, a fully on-chain call market in Solidity---a high-level programming language for Ethereum.
 We choose Ethereum as a `hostile' environment for an orderbook: Ethereum is public (strongest adversary) and slow (lower-bound benchmark) relative to more scalable blockchains, including the anticipated Ethereum 2.0.
@@
 % = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
 
@@
 
-\paragraph{Execution systems.} There are three main approaches to arranging a trade.
+\paragraph{Execution systems.} There are three main approaches to arranging a trade~\cite{Har03}.
 In a \emph{quote-driven} market, a dealer uses their own inventory to offer a price for buying or selling an asset.
@@
 
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
+\paragraph{Other Literature.}
+% Madiba -> pulp.bib
+% Velocity, 
+% FuturesMex~\cite{massacci2018futuresmex}
+% Findel 
+% Libra~\cite{mavroudis2019libra}
+% Arwen
+% Tesseract (SGX-exchange)~\cite{bentov2017tesseract}
+% Christopher Thorpe
+
 % = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
@@
 
-% = = = = = = = = = = = = = = = = =
 \begin{enumerate}
 
-%---------+++++++++++++++++++-----------------
-
-\item\textbf{{Heap with Dynamic Array.}} A heap is a type of binary tree data structure that comes in two forms of a (i) Max-Heap and (ii) Min-Heap.
+\item \textbf{Heap with Dynamic Array.} A heap is a type of binary tree data structure that comes in two forms of a (i) Max-Heap and (ii) Min-Heap.
 All the nodes of tree are in a specific order and the root of the tree always represents the highest priority item of the data structure (the largest and smallest values in the Max-Heap and Min-Heap respectively).
@@
 
-%---------+++++++++++++++++++-----------------
-
-\item\textbf{{Heap with Static Array.}} A heap can be also represented by a Solidity storage array in which the storage is statically allocated.
+\item \textbf{Heap with Static Array.} A heap can be also represented by a Solidity storage array in which the storage is statically allocated.
 To do this, we pass the required size of the array as a constructor parameter to the priority queue smart contract.
 
-%---------+++++++++++++++++++-----------------
-
-\item\textbf{{Heap with Mapping.}} In the above implementations, the heap stores the entire order (as a struct) in the heap.
+\item \textbf{Heap with Mapping.} In the above implementations, the heap stores the entire order (as a struct) in the heap.
 In this variant, we store the order struct in a Solidity mapping and store the mapping's key in the heap.
 
-%---------+++++++++++++++++++-----------------
-
-\item\textbf{{Linked List.}} In this variant, we insert a new element into its correct position (based on its price) when running enqueue.
+\item \textbf{Linked List.} In this variant, we insert a new element into its correct position (based on its price) when running enqueue.
 The PQ itself stores elements in a linked list (enabling us to efficiently insert a new element between two existing elements).
@@
 
-%---------+++++++++++++++++++-----------------
-
-\item\textbf{{Linked List with Mapping.}} Finally, we try a variant of a linked list using a Solidity mapping.
+\item \textbf{Linked List with Mapping.} Finally, we try a variant of a linked list using a Solidity mapping.
 The value of the mapping is a struct with order data and the key of the next (and previous) node in the list.
@@
 
-%---------+++++++++++++++++++-----------------
+\end{enumerate}
 
-\end{enumerate}
-% = = = = = = = = = = = = = = = = =
 % = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
@@
 
-% = = = = = = = = = = = =random_insertion Figure = = = = = = = = = = = = =  %
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
 
@@
 \end{figure}
+
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
 
@@
 % = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
-%  = = = = = = Table 2 (dequeue) Conversions = = = = = = %
-%
-%As of July 2020,  $1 gas = 56\times10^{-9} ether$\footnote{https://ethstats.net/} and 1 ether = \$238.33\footnote{https://coinmarketcap.com/}.
-%
-%$Transaction cost (eth) = GasUsed (unit) \times Gas Price (eth)$ 
-%
-%%  = = = = = = Transaction Costs in eth = = = = = = %
-%
-%Heap with Dynamic Array:    		$2,518,131 \times 56\times10^{-9} = 141,015,336\times 10^{-9}$
-%Heap with Dynamic Array:     		$1,385,307 \times 56\times10^{-9} = 77,577,192\times 10^{-9}$
-%Heap with Mapping:              		$2,781,684 \times 56\times10^{-9} = 155,774,304\times 10^{-9}$
-%Linked List:						$557,085 \times 56\times10^{-9} = 	31,196,760\times 10^{-9}$
-%Linked List with Mapping:			$731,514 \times 56\times10^{-9} = 	40,964,784\times 10^{-9}$
-%
-%%  = = = = = = Transaction Costs in USD = = = = = = %
-%
-%Heap with Dynamic Array:    		$141,015,336\times 10^{-9} \times 238.33 = \$33.60$
-%Heap with Dynamic Array:     		$77,577,192\times 10^{-9} \times 238.33 = \$18.48$
-%Heap with Mapping:              		$155,774,304\times 10^{-9} \times 238.33 = \$37.12$
-%Linked List:						$31,196,760\times 10^{-9} \times 238.33 = \$7.43$
-%Linked List with Mapping:			$40,964,784\times 10^{-9} \times 238.33 = \$9.76$
-%
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
 
@@
 \input{tables/cleaning.tex}
-
-%---------+++++++++++++++++++-----------------
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
-
-%  = = = = = = Table 3 (cleaning.tex) Conversions = = = = = = %
-
-%As of July 2020,  $1 gas = 56\times10^{-9} ether$\footnote{https://ethstats.net/} and 1 ether = \$238.33\footnote{https://coinmarketcap.com/}.
-%
-%$Transaction cost (eth) = GasUsed (unit) \times Gas Price (eth)$ 
-%
-%%  = = = = = = Transaction Costs in eth = = = = = = %
-%
-%Linked List with \texttt{SELFDESTRUCT}:     				$557,085 \times 56\times10^{-9} =  31,196,760\times 10^{-9}$  
-%Linked List w/o \texttt{SELFDESTRUCT}:     				$721,370 \times 56\times10^{-9} =  40,396,720\times 10^{-9}$ 
-%Linked List with Mapping and \texttt{DELETE}:    			$731,514 \times 56\times10^{-9} =  40,964,784\times 10^{-9}$ 
-%Linked List with Mapping and w/o \texttt{DELETE}: 		$334,689 \times 56\times10^{-9} =  18,742,584\times 10^{-9}$ 
-%
-%%  = = = = = = Transaction Costs in USD = = = = = = %
-%
-%Linked List with \texttt{SELFDESTRUCT}:     				$31,196,760\times 10^{-9}  \times 238.33 = \$7.43$
-%Linked List w/o \texttt{SELFDESTRUCT}:     				$40,396,720\times 10^{-9} \times 238.33 = \$9.62$
-%Linked List with Mapping and \texttt{DELETE}:    			$40,964,784\times 10^{-9}  \times 238.33 = \$9.76$
-%Linked List with Mapping and w/o \texttt{DELETE}: 		$18,742,584\times 10^{-9} \times 238.33 = \$4.46$
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
-
-%Although the \texttt{SELFDESTRUCT} operation does not remove the initial byte code of the contract from the chain, but it frees up the state storage and refunds 24000 gas to the caller.
 
@@
 
-% = = = = = = = = = = = = = Implementatiion = = = = = = = = = = = = = = = = = = =  %
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
 
@@
 %GitHub repo:  \footnote{\CallMarketRepo}
-% = = = = = = = = = = = = = = = = = = = = =Call market operations Table = = = = = = = = = = = =  = = = = = =  %
-\begin{table}[t]
-\begin{tabular}{|l|l|}
-\hline
-\multicolumn{1}{|c|}{\textbf{Operation}} & \multicolumn{1}{c|}{\textbf{Description}}                            			\\ \hline
 
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
-	DepositToken()                           & Deposits ERC20 standard compliant tokens in the call market contract \\ \hline
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
-	DepositEther()                           	& Deposits Ethers in the call market contract                         			 \\ \hline
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
-	OpenMarket()                             & Opens the market                                                    					 \\ \hline
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
-	CloseMarket()                            & Closes the market                                                    					\\ \hline
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
-	SubmitBid()                              & Inserts the upcoming bid order messages inside the priority queue    \\ \hline
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
-	SubmitAsk()                              & Inserts the upcoming ask order messages inside the priority queue    \\ \hline
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
-	MatchOrders()                           & Matches the orders against each other                                			\\ \hline
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
-	ClaimTokens()                           & Transfers collateral tokens back to the trader                       			\\ \hline
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
-	ClaimEther()                             & Transfers collateral Ethers back to the trader                       			\\ \hline
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
-\end{tabular}
-\caption{\footnotesize{Primary operations of the call market smart contract.}
-\label{tab:callmarket_functions}}
-\end{table}
+\input{tables/functions.tex}
 
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
-
-Our design \cm is intended as a module that developers can modify as they choose---thus we tried to simplify the design at every step to make it highly extensible but still functional without any extensions.
+\cm is intended as a module that developers can modify as they choose---thus we tried to simplify the design at every step to make it highly extensible but still functional without any extensions.
 A call market will open for a specified period of time during which it will accept orders.
@@
 Our vision (discussed below) is the market would be open for a very short period of time, close, and then reopen immediately (\eg every other block).
-This is akin to how a crossing network operates in traditional finance (\ie \textblue{some explanation}).
 We keep the design simple by not allowing cancellations.
-Because markets are relatively short-lived, cancelations require a second transaction (and front-running attacks apply to cancellation orders~\cite{eskandari2019sok}), orders simply expire when the market call period ends.
+Because markets are relatively short-lived, cancelations require a second transaction, and front-running attacks apply to cancellation orders~\cite{eskandari2019sok}, orders simply expire when the market call period ends.
 
@@
 
- \subsection{Performance}
+ \subsection{Measurements}
 
@@
 
-\textblue{Optimize for closing market, even at cost of higher submission.}
+\subsection{Security Analysis} \label{sec:front}
+
+\paragraph{Front-running.} 
+% Front running -> drop trades, move to next block, can't front-run
+% Take 1000 trades over a window of time -> shuffle -> what is different between A and B?u
+% No price improvement changes people waiting to trade?
+
+\paragraph{Contract Security.} We used two security audit tools, \textit{Slither}\footnote{https://github.com/crytic/slither} and \textit{SmartCheck},\footnote{https://tool.smartdec.net}, on \cm to find vulnerabilities and bad practices.
+We received 100\% success rate in a total of 67 audits performed by considering 'Informational' checks as 'passed'.
 
@@
 
-\section{Call Market Different Design and Implementation Details }
+\section{Design alternatives and extensions}
 
-\subsection{Front-running} \label{sec:front}
-% Front running -> drop trades, move to next block, can't front-run
-% Take 1000 trades over a window of time -> shuffle -> what is different between A and B?u
-% No price improvement changes people waiting to trade?
+\subsection{Resolving ties}
+
+\subsection{Price level / volume level}
 

### 2020-09-14 LaTeX/tables/functions.tex
more edits

% !TEX root = ../main.tex

% = = = = = = = = = = = = = = = = = = = = =Call market operations Table = = = = = = = = = = = =  = = = = = =  %
\begin{table}[t]
\begin{tabular}{|l|l|}
\hline
\multicolumn{1}{|c|}{\textbf{Operation}} & \multicolumn{1}{c|}{\textbf{Description}}                            			\\ \hline

% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
	DepositToken()                           & Deposits ERC20 standard compliant tokens in the call market contract \\ \hline
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
	DepositEther()                           	& Deposits ETH in the call market contract                         			 \\ \hline
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
	OpenMarket()                             & Opens the market                                                    					 \\ \hline
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
	CloseMarket()                            & Closes the market                                                    					\\ \hline
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
	SubmitBid()                              & Inserts the upcoming bid order messages inside the priority queue    \\ \hline
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
	SubmitAsk()                              & Inserts the upcoming ask order messages inside the priority queue    \\ \hline
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
	MatchOrders()                           & Matches the orders against each other                                			\\ \hline
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
	ClaimTokens()                           & Transfers collateralized tokens back to the trader                       			\\ \hline
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
	ClaimEther()                             & Transfers collateralized ETH back to the trader                       			\\ \hline
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
\end{tabular}
\caption{\footnotesize{Primary operations of the call market smart contract.}
\label{tab:callmarket_functions}}
\end{table}

% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %

### 2020-09-14 LaTeX/sections/paper.tex
more edits

@@
 
-\paragraph{Front-running.} 
-% Front running -> drop trades, move to next block, can't front-run
-% Take 1000 trades over a window of time -> shuffle -> what is different between A and B?u
-% No price improvement changes people waiting to trade?
+\paragraph{Code Security.} We used two security audit tools, \textit{Slither}\footnote{https://github.com/crytic/slither} and \textit{SmartCheck},\footnote{https://tool.smartdec.net} on \cm to find vulnerabilities and bad practices across 67 tests.
+\cm passes all test except some `informational' warnings (\eg a costly loop) that are intentional design choices.
 
-\paragraph{Contract Security.} We used two security audit tools, \textit{Slither}\footnote{https://github.com/crytic/slither} and \textit{SmartCheck},\footnote{https://tool.smartdec.net}, on \cm to find vulnerabilities and bad practices.
-We received 100\% success rate in a total of 67 audits performed by considering 'Informational' checks as 'passed'.
+\paragraph{Front-running.} The primary motivation for using a call market, as opposed to a continuous time orderbook, is to mitigate front-running attacks~\cite{clark2014decentralizing,eskandari2019sok,daian2019flash}.
+Consider a sequence of 100 orders submitted within a window of time to market A, and the same sequence randomly shuffled and submitted to market B.
+If A and B are continuous, the orders that are executed in A could be quite different from B.
+In a call market, the outcome of A and B will be exactly equivalent.
+For this reason, there is no threat from miners reordering transactions or users offering higher gas rates to have their orders executed before other orders already broadcast to the network.
+
+In a traditional call market, a market clearing price is chosen and all trades are executed at this price.
+All bids made at a higher price will receive the assets for the lower clearing price (and conversely for lower ask prices): this is called a price improvement.
+A miner about to mine on a set of transactions, including orders, could insert its own orders that make arbitrage profit by lowering the other traders' price improvements.
+For this reason, in \cm, all price improvements are given to the miner (using \texttt{block.coinbase.transfer()}).
+This does not actively hurt traders---they always receive the same price from their order---and it removes any incentive to front-run these profits.
+
+Potential for front-running still exists around ties on price and cancelations (see below).
+Finally, \textit{displacement attacks}~\cite{eskandari2019sok} are possible where competitive orders are delayed long enough for the market to close without them.
+For all these reasons, we say \cm reduces front-running attacks but stop short of saying it is completely solved by \cm.
 
@@
 
-\subsection{Resolving ties}
+As a module, we try to keep \cm as simple as possible, and allow customization and extensions as appropriate. We discuss potential modifications here.
 
-\subsection{Price level / volume level}
+\subsection{Token Divisibility and Volumes}
 
-\subsection{Clearing Mappings}
+We implement a very simple market where orders all have the same volume: 1 token.
+Traders submit multiple orders to increase volume.
+To extend orders with a volume field, it must first be determined if the token are non-divisible or divisible (and to what precision).
+In this case, \texttt{MarketClose()} needs look at multiple bids to fulfill a single ask (and vice-versa) and declare its trading rules on partial fills.
+We also simplify the market rules around ties on price: we execut them FIFO (breaking front-running resistance for ties on prices).
+A common trading rule (that does resist front-running) is to fill ties in proportion to their volume (\ie \textit{pro rata} allocation)\footnote{If Alice and Bob bid the same price for 100 tokens and 20 tokens respectively, and there are only 60 tokens left in marketable asks, Alice receives 50 and Bob 10.} however this approach is also contingent on the divisibility of tokens.
+Consider the following corner-case: 3 equally priced bids of 1 non-divisible token and 1 ask at the same price.
+There is not good option: (1) the bids could all be dropped (fair but not market efficient), (2) bids could be prioritized based on time as in \cm (front-running is viable, but in this corner case only), or (3) the bid could be randomly chosen (\cf~\cite{mavroudis2019libra}; blockchain `randomness' is generally deterministic and manipulatable by miners~\cite{bonneau2015random,buenz2017proofs} and counter-measures could take a few blocks to select~\cite{boneh2018verifiable}).
 
-To maintain the collateral balance of each market participant, we use two Solidity type one-to-one mappings that map Ethereum addresses to 256 bits unsigned integers; \texttt{TotalBalance} and \texttt{UnavailableBalance}.
-Once market closes and orders are matched, the \texttt{UnavailableBalance} needs to be cleared.
-However, since it is not possible to delete the entire mapping without knowing the keys~\footnote{https://solidity.readthedocs.io/en/v0.5.12/security-considerations.html}, clearing the \texttt{UnavailableBalance} mapping remains a challenging issue to solve.
-Here we provide a landscape of solutions for that.
-%only individual keys and what they map to can be deleted.
+\subsection{Cancelations}
 
-\begin{itemize}
-
-%---------+++++++++++++++++++-----------------
-\item \textbf{Creating a New Mapping Every Time the Market Opens.} Instead of clearing the \texttt{UnavailableBalance} of traders at the end of a matching process, we could create a new mapping every time the market opens.
-Note that in this scheme traders can claim their funds back (using the \texttt{ClaimEther()} and/or \texttt{ClaimToken} methods) only when the market is closed (\ie the market is in the \texttt{Closed} state).
-
-%---------+++++++++++++++++++-----------------
-\item \textbf{Creating Custom Keys for the Mapping.} We can create custom keys for the mapping by defining a counter as a global variable inside the call market smart contract and increment it only once at the end of the matching process.
-So instead of clearing the mapping, we only use another portion of it every time the market opens.
-
-%---------+++++++++++++++++++-----------------
-\item \textbf{Storing the Mapping in a Data-Contract.} Another design proposal is to create a new smart contract every time the market opens, this data contract only stores the \texttt{UnavailableBalance} mapping and will be destroyed (using the \texttt{SELFDESTRUCT} operation) at the end of the matching process.
-
-%---------+++++++++++++++++++-----------------
-\item \textbf{Storing the Mapping keys in an additional Array.} Another common pattern is to create an additional array on top of the mapping and iterate over that.
-This array (\eg address[]) stores the traders' addresses and enables us to iterate over the mapping and delete individual keys and what they map to at the end of the matching process.
-Note that this is a gas-costly design pattern as we would need to maintain a secondary data structure.
-
-%---------+++++++++++++++++++-----------------
-\end{itemize}
-
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
+\subsection{Market clearing price -> informational only}
 
@@
 
-\begin{figure}[htb!p]
-\centering
-\includegraphics[width=0.8\textwidth]{fig/meta_tx.png}
-\caption{\footnotesize{}  \label{fig:meta_tx}}
-\end{figure}
+%\begin{figure}[htb!p]
+%\centering
+%\includegraphics[width=0.8\textwidth]{fig/meta_tx.png}
+%\caption{\footnotesize{}  \label{fig:meta_tx}}
+%\end{figure}
 
@@
 % Options for non-collaterialized markets
+
+\subsection{Clearing Mappings}
+
+To maintain the collateral balance of each market participant, we use two Solidity type one-to-one mappings that map Ethereum addresses to 256 bits unsigned integers; \texttt{TotalBalance} and \texttt{UnavailableBalance}.
+Once market closes and orders are matched, the \texttt{UnavailableBalance} needs to be cleared.
+However, since it is not possible to delete the entire mapping without knowing the keys~\footnote{https://solidity.readthedocs.io/en/v0.5.12/security-considerations.html}, clearing the \texttt{UnavailableBalance} mapping remains a challenging issue to solve.
+Here we provide a landscape of solutions for that.
+%only individual keys and what they map to can be deleted.
+
+\begin{itemize}
+
+%---------+++++++++++++++++++-----------------
+\item \textbf{Creating a New Mapping Every Time the Market Opens.} Instead of clearing the \texttt{UnavailableBalance} of traders at the end of a matching process, we could create a new mapping every time the market opens.
+Note that in this scheme traders can claim their funds back (using the \texttt{ClaimEther()} and/or \texttt{ClaimToken} methods) only when the market is closed (\ie the market is in the \texttt{Closed} state).
+
+%---------+++++++++++++++++++-----------------
+\item \textbf{Creating Custom Keys for the Mapping.} We can create custom keys for the mapping by defining a counter as a global variable inside the call market smart contract and increment it only once at the end of the matching process.
+So instead of clearing the mapping, we only use another portion of it every time the market opens.
+
+%---------+++++++++++++++++++-----------------
+\item \textbf{Storing the Mapping in a Data-Contract.} Another design proposal is to create a new smart contract every time the market opens, this data contract only stores the \texttt{UnavailableBalance} mapping and will be destroyed (using the \texttt{SELFDESTRUCT} operation) at the end of the matching process.
+
+%---------+++++++++++++++++++-----------------
+\item \textbf{Storing the Mapping keys in an additional Array.} Another common pattern is to create an additional array on top of the mapping and iterate over that.
+This array (\eg address[]) stores the traders' addresses and enables us to iterate over the mapping and delete individual keys and what they map to at the end of the matching process.
+Note that this is a gas-costly design pattern as we would need to maintain a secondary data structure.
+
+%---------+++++++++++++++++++-----------------
+\end{itemize}
+
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
 

### 2020-09-15 LaTeX/sections/paper.tex
some more edits

@@
 In a call market, the outcome of A and B will be exactly equivalent.
-For this reason, there is no threat from miners reordering transactions or users offering higher gas rates to have their orders executed before other orders already broadcast to the network.
-
-In a traditional call market, a market clearing price is chosen and all trades are executed at this price.
-All bids made at a higher price will receive the assets for the lower clearing price (and conversely for lower ask prices): this is called a price improvement.
-A miner about to mine on a set of transactions, including orders, could insert its own orders that make arbitrage profit by lowering the other traders' price improvements.
-For this reason, in \cm, all price improvements are given to the miner (using \texttt{block.coinbase.transfer()}).
-This does not actively hurt traders---they always receive the same price from their order---and it removes any incentive to front-run these profits.
+For this reason, there is no threat from miners reordering transactions or users offering higher gas rates to have their orders executed before other orders already broadcasted.
 
@@
 Finally, \textit{displacement attacks}~\cite{eskandari2019sok} are possible where competitive orders are delayed long enough for the market to close without them.
+In a traditional call market, a market clearing price is chosen and all trades are executed at this price.
+All bids made at a higher price will receive the assets for the lower clearing price (and conversely for lower ask prices): this is called a price improvement.
+A miner about to mine on a set of transactions, including its own orders, could drop other traders' orders to maximize its own price improvement.
+For this reason, in \cm, all price improvements are given to the miner (using \texttt{block.coinbase.transfer()}).
+This does not actively hurt traders---they always receive the same price from their order---and it removes any incentive to front-run these profits.
 For all these reasons, we say \cm reduces front-running attacks but stop short of saying it is completely solved by \cm.
@@
 
-\begin{itemize}
-% = = = = = = = = = = = =How to enforce time on on the Ethereum blockchain? = = = = = = = = = = = = =  %
-
-\item\textbf{{Enforcing Time on the Blockchain.}}
-
 % We want the market to run on a periodic schedule => it is difficult for market participants to call the \texttt{Close()} function periodically.
@@
 
-\item\textbf{{Who Pays the Cost for Closing and Reopening the Market?}}
+\subsection{Who Pays the Cost for Closing and Reopening the Market?}
 
@@
 
-\begin{itemize}
-
 %= = = = = = Miners Close the Market = = = = = = =%
-\item \textbf {Miners Close and Reopen the Market.} The difference between the best bid and ask prices is called the \textit{bid-ask spread}.
+\paragraph{Miners Close and Reopen the Market.} The difference between the best bid and ask prices is called the \textit{bid-ask spread}.
 In our design, when the trade occurs between the the highest bid (the highest amount a buyer is willing to pay for an asset) and lowest ask (the lowest amount a seller is willing to accept for an asset) orders, the bid-ask spread is paid to the miner.
@@
 
-\item \textbf{Processing Orders in Groups.} Another solution pattern is to process certain number of bid and ask orders upon every execution of the \texttt{CloseMarket()} function rather than treating them as one substantial transaction.
+\paragraph{Processing Orders in Groups.} Another solution pattern is to process certain number of bid and ask orders upon every execution of the \texttt{CloseMarket()} function rather than treating them as one substantial transaction.
 A market participant $P_i$ would process $n$ orders from the previous market (\texttt{CloseMarket(n)}) when sending new orders to the current market.
@@
 
-\item \textbf {Using the Meta Transactions.} Meta transactions enable users to execute Ethereum functions without paying the gas.
+\paragraph{Using the Meta Transactions.} Meta transactions enable users to execute Ethereum functions without paying the gas.
 Rather than spending gas, users sign their intended action using their private keys and broadcast it to the network with no cost.
@@
 
-\item \textbf{Using the "Contract Pays" Model.} An alternative solution is to design the market such that the last person to submit an order calls the \texttt{CloseMarket()} function, but in contrast to a normal transaction (where the person initiating the transaction must pay the fee), here the CallMarket contract pays the cost for closing the market and matching the orders respectively.
+\paragraph{Using the "Contract Pays" Model.} An alternative solution is to design the market such that the last person to submit an order calls the \texttt{CloseMarket()} function, but in contrast to a normal transaction (where the person initiating the transaction must pay the fee), here the CallMarket contract pays the cost for closing the market and matching the orders respectively.
 To enforce this design we can use Solidity function modifiers; every time a new order is submitted, a function modifier checks whether (i) the auction period has to end and/or (ii) the maximum number of total orders has reached.
@@
 
+\subsection{Off-Chain Closing}
 \label{sec:rollups}
-\item \textbf{Using Rollups.} Rollup is a scaling method that moves the storage and computation of the smart contracts off-chain while maintaining the transaction data on the main chain as call-data.
+
+\paragraph{Using Rollups.} Rollup is a scaling method that moves the storage and computation of the smart contracts off-chain while maintaining the transaction data on the main chain as call-data.
 In this technique, any Ethereum user can act as a validator; they can execute the \texttt{CloseMarket()}function and only post the new state of the contract (the updated balance of traders) in the form of \textit{assertions} to the main chain.
@@
 
-\begin{itemize}
-
-\item \textbf{{Non-interactive Rollups.}} In this rollup technique, assertions are posted together with a validity proof that would be later used by validators to check if the \texttt{CloseMarket()} function has been executed correctly.
+\paragraph{Non-interactive Rollups.} In this rollup technique, assertions are posted together with a validity proof that would be later used by validators to check if the \texttt{CloseMarket()} function has been executed correctly.
 ZK-Rollup scheme is one of the solutions that uses ZK-SNARKs to prove the validity of the assertions in zero-knowledge.
@@
 
-\item \textbf{{Optimistic Rollups.}} In this scheme, assertions are assumed to be valid if there is no dispute posted about them with a certain window of time (a.k.a.
+\paragraph{Optimistic Rollups.} In this scheme, assertions are assumed to be valid if there is no dispute posted about them with a certain window of time (a.k.a.
 "the challenge period').
@@
 
-\item \textbf {{Multi-round Interactive Rollups.}} In this design paradigm, \textit{pending assertions} are posted on-chain and they are open to dispute.
+\paragraph{{Multi-round Interactive Rollups.}} In this design paradigm, \textit{pending assertions} are posted on-chain and they are open to dispute.
 Once the challenge period is over and no challenge is submitted, the assertion is confirmed and the CallMarket contract transitions to the new state (\ie updates traders' balances).
@@
 
-\end{itemize}
-
 %= = = = = =  = =  =  SGX=  = = = = = = = = =%
 
-\item \textbf{{Using Trusted Execution Environments.}} Another way of achieving execution of the \texttt{CloseMarket()} function is incorporating the Ethereum blockchain into the Trusted Execution Environments (TEEs) and decoupling the contract execution from consensus mechanism.
+\paragraph{{Using Trusted Execution Environments.}} Another way of achieving execution of the \texttt{CloseMarket()} function is incorporating the Ethereum blockchain into the Trusted Execution Environments (TEEs) and decoupling the contract execution from consensus mechanism.
 TEEs enable secure execution of applications in an isolated processing environment called the \textit{enclave}.
@@
 A drawback of this scheme is in order to achieve confidentiality-preserving smart contracts we have to trust a trusted party in the form of the hardware manufacturer (\eg Intel).
-
-\end{itemize}
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
-\end{itemize}
 
@@
 
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
-
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
-
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
-
-% = = = = = = = = = = = =Notes Discussed in Meetings = = = = = = = = = = = = =  %
-
-% Our two competitors are Uinswap and Loopring (that uses ZK roll ups):
-% 	1- Uniswap: we can argue that in traditional markets we have various traditional exchanges. Each of these exchanges have different trading rules and designs which work for different traders.
-%	2- Loopring:
-%		2-1: Barrier to entry: In order for a trader to trade specific ERC20 on Loopring, Loopring has to agree to support that token.
-It might not be difficult and they probably approve the token as long as it is standard compliant.
-%		2-2: ZK proofs are quick and cheap to verify but they are expensive and time consuming to generate: (1) now they are generating these proofs for free but later they charge traders for doing that.
-(2) Looping does not probably generate these proofs per every block so the settlement and 				clearing is not happening per block.
-So we have faster clearing and settlement as we clear everything per block.
-% 		2-3: Loopring is non-custodial, meaning that the money moves only when the proofs come, so there is a latency in transferring funds to the traders.
-
-% The heap with dynamic array can do 26 pairs of matches at worst case matching whereas Linkedliat does 90 pairs.
-So if we want to cap the orders over 4 PQs, we’re basically increasing the heap size which makes match more expensive for nothing (every time a match happens and the root is deleted the whole heap is reheapified)
-
-% There will be no ties as we use 2 counters for buy and sell orders. These counters are concatenated them with the price. So we somehow enforce time priority
-
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
-
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
-%The tables I changed after estimateGas, Not sure which ones to keep. Should talk to Jeremy
-
-%
-%% = = = = = = = = = = = =Gas costs and refunds for Dequeueing 50 integers from each PQ  = = = = = = = = = = = = =  %
-%
-%\begin{table}[]
-%\centering
-%\begin{tabular}{|c|c|c|c|c|}
-%\hline
-%
-%\textbf{\thead{Priority Queue}}    & \textbf{\thead{Net Cost\\in Gas}}      & \textbf{\thead{Total Cost\\in Gas\\(From \texttt{estimateGas})}}      & \textbf{The Difference}    & \textbf{\thead{Gas Refund \\(Manually Calculated)}} \\ \hline
-%
-%% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
-%	\textbf{\thead{Heap with \\ Dynamic Array}}         				& 2,518,131               & 3,283,480		& 765,349             & 750,000                       \\ \hline
-%% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
-%	\textbf{\thead{Heap with \\ Static Array}}           				& 1,385,307                & 2,150,625     	& 765,318             & 750,000                      \\ \hline
-%% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
-%	\textbf{\thead{Mapping with \\ keys stored \\ in Heap}} 		& 2,781,684                & 4,316,229       	& 1,534,545           & 1,500,000                     \\ \hline
-%% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
-%	\textbf{Linked List}                       							& 557,085               	& 1,772,085      	& 1,215,000           & 1,200,000                      \\ \hline
-%% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
-%	\textbf{\thead{Linked List with \\ Mapping}}          				& 731,514              	& 3,731,514       	& 3,000,000     	  &  3,765,000                       \\ \hline
-%% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
-%
-%\end{tabular}
-%\caption{\footnotesize{The gas metrics associated with dequeuing 50 items from five priority queues.}
-%\label{tab:PQUnitTests}}
-%\end{table}
-%% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
-%
-%% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
-%\begin{table}[]
-%\begin{tabular}{|c|c|c|c|c|}
-%\hline
-%\multirow{2}{*}{Gas Metrics}                        							& \multicolumn{2}{c|}{Linked List}           						& \multicolumn{2}{c|}{Linked List with Mapping}     					\\ \cline{2-5} 
-%% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = %
-%                                                                						& with \texttt{SELFDESTRUCT} 		& without \texttt{SELFDESTRUCT}                	& with \texttt{delete} 		& without \texttt{delete}              		\\ \hline                                                                                                                                                                                                                                                          % = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = %
-%                   Net Cost in Gas                          					& 557,085                    			& 721,370                     				& 731,514                     	& 334,689                      				\\ \hline
-%% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = %
-%\thead{Total Cost in Gas \\ (from \texttt{estimateGas})} 		& 1,772,085                  			& 736,370                  					& 3,731,514                     	& 1,099,689                       				\\ \hline
-%% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = %
-%		    The Difference                                             		& 1,215,000                  			& 15,000                      				& 3,000,000                    	& 765,000                       				\\ \hline
-%% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = %
-%
-%\end{tabular}
-%\caption{\footnotesize{}
-%\label{tab:LLvsLLMapping}}
-%\end{table}
-%% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
-
-%======================================== %
-
 % = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
@@
 
+Imagine you have just launched an ERC20 token on Ethereum.
+Now want your holders to be able to trade it.
+While the barrier to entry for exchange services is low, it still exists.
+For a centralized or decentralized exchange, you have to convince the operators to list your token and you will be delayed while they process your request.
+For an automated market maker, you will have to lock up a large amount of ETH into the DApp, along with your tokens.
+For rollups, you will have to list your token, host your own servers, and/or enlist arbitrators.
+By contrast to all of these, with \cm you just deploy the code alongside your token and trading is immediately supported.
+Even if \cm is a fallback solution today, we believe it is helpful for every token to be accompanied by on-chain trade execution.
+And with future improvements to blockchain scalability, it could become the defacto trading method.
+
 %\subsubsection*{Acknowledgements.} J. Clark thanks ...

### 2020-09-17 LaTeX/sections/appendix.tex
more edits
point form sections

@@
 % !TEX root = ../main.tex
+
+% Extended discussion on cleaning up data structures in Ethereum
 
@@
 An Ethereum block also has a \texttt{block gas limit} field which is set by the Ethereum miners and indicates the maximum amount of gas all the transactions in that block are allowed to consume, the Ethereum \texttt{block gas limit} is currently 11,741,495.
-\footnote{\[July 2020:\] https://ethstats.net/}
+\footnote{July 2020: https://ethstats.net/}
 
@@
 
+\subsection{Clearing Mappings}
+
+To maintain the collateral balance of each market participant, we use two Solidity type one-to-one mappings that map Ethereum addresses to 256 bits unsigned integers; \texttt{TotalBalance} and \texttt{UnavailableBalance}.
+Once market closes and orders are matched, the \texttt{UnavailableBalance} needs to be cleared.
+However, since it is not possible to delete the entire mapping without knowing the keys~\footnote{https://solidity.readthedocs.io/en/v0.5.12/security-considerations.html}, clearing the \texttt{UnavailableBalance} mapping remains a challenging issue to solve.
+Here we provide a landscape of solutions for that.
+%only individual keys and what they map to can be deleted.
+
+\begin{itemize}
+
+%---------+++++++++++++++++++-----------------
+\item \textbf{Creating a New Mapping Every Time the Market Opens.} Instead of clearing the \texttt{UnavailableBalance} of traders at the end of a matching process, we could create a new mapping every time the market opens.
+Note that in this scheme traders can claim their funds back (using the \texttt{ClaimEther()} and/or \texttt{ClaimToken} methods) only when the market is closed (\ie the market is in the \texttt{Closed} state).
+
+%---------+++++++++++++++++++-----------------
+\item \textbf{Creating Custom Keys for the Mapping.} We can create custom keys for the mapping by defining a counter as a global variable inside the call market smart contract and increment it only once at the end of the matching process.
+So instead of clearing the mapping, we only use another portion of it every time the market opens.
+
+%---------+++++++++++++++++++-----------------
+\item \textbf{Storing the Mapping in a Data-Contract.} Another design proposal is to create a new smart contract every time the market opens, this data contract only stores the \texttt{UnavailableBalance} mapping and will be destroyed (using the \texttt{SELFDESTRUCT} operation) at the end of the matching process.
+
+%---------+++++++++++++++++++-----------------
+\item \textbf{Storing the Mapping keys in an additional Array.} Another common pattern is to create an additional array on top of the mapping and iterate over that.
+This array (\eg address[]) stores the traders' addresses and enables us to iterate over the mapping and delete individual keys and what they map to at the end of the matching process.
+Note that this is a gas-costly design pattern as we would need to maintain a secondary data structure.
+
+%---------+++++++++++++++++++-----------------
+\end{itemize}
+
 %gas price: how much you pay per gas unit
@@
 So at the end of a successful transaction, the amount of gas in the refund counter (capped at half the net gas used) is returned to the caller.
+
+% \input{tables/eval.tex}
+
+%\section{Rollups}
+%
+%\subsection{Using Rollups.} Rollup is a scaling method that moves the storage and computation of the smart contracts off-chain while maintaining the transaction data on the main chain as call-data.
+In this technique, any Ethereum user can act as a validator; they can execute the \texttt{CloseMarket()}function and only post the new state of the contract (the updated balance of traders) in the form of \textit{assertions} to the main chain.
+Rollups improve scalability, provide faster and cheaper execution of the contracts, and eliminate the gas limit as the contract is no longer executed on-chain.
+%
+%In the followings we briefly discuss different rollup proposals and techniques. Each approach uses a different method to ensure correction of assertions:
+%
+%\paragraph{Non-interactive Rollups.} In this rollup technique, assertions are posted together with a validity proof that would be later used by validators to check if the \texttt{CloseMarket()} function has been executed correctly.
+ZK-Rollup scheme is one of the solutions that uses ZK-SNARKs to prove the validity of the assertions in zero-knowledge.
+ZK proofs are quick and cheap to verify but they are expensive and time consuming to generate.
+These proofs could be generated (i) for free or (ii) the CallMarket contract could collect proportional fees for every trade that is successfully executed.
+%
+%\paragraph{Optimistic Rollups.} In this scheme, assertions are assumed to be valid if there is no dispute posted about them with a certain window of time (a.k.a.
+"the challenge period').
+Here, dispute resolution is a gas-costly method as the CallMarket contract would have to emulate the transaction on-chain to ensure the correctness the assertion.
+This scheme introduces a tradeoff between privacy and performance as all the assertions are publicly available and accessible.
+However, here the new state only reflects the updated balances of traders and no secret is involved.
+%
+%\paragraph{{Multi-round Interactive Rollups.}} In this design paradigm, \textit{pending assertions} are posted on-chain and they are open to dispute.
+Once the challenge period is over and no challenge is submitted, the assertion is confirmed and the CallMarket contract transitions to the new state (\ie updates traders' balances).
+This scheme takes the overhead for the CallMarket contract to execute the \texttt{Close()} on-chain by using rounds to the dispute resolutions.
+The two parties (asserter and challenger) must run an interactive protocol and the CallMarket smart contract would have to act as a referee and decides which party's claim is true.
+Arbitrum is an example of multi-round interactive rollups that uses an efficient challenge-based protocol to penalize the dishonest parties~\cite{kalodner2018arbitrum}.
+%
+%%= = = = = =  = =  =  SGX=  = = = = = = = = =%
+%
+%\paragraph{{Using Trusted Execution Environments.}} Another way of achieving execution of the \texttt{CloseMarket()} function is incorporating the Ethereum blockchain into the Trusted Execution Environments (TEEs) and decoupling the contract execution from consensus mechanism.
+TEEs enable secure execution of applications in an isolated processing environment called the \textit{enclave}.
+Here, the enclave could execute the \texttt{CloseMarket()} function off-chain in TEEs and publish an on-chain attestation Quote to the CallMarket contract.
+The contract then verifies the correctness of the Quote and if validated correctly, it transitions to the new state.
+Ekiden is an example that uses Intel SGX to solve the scalability and confidentiality issues with the smart contract execution~\cite{cheng2019ekiden}.
+A drawback of this scheme is in order to achieve confidentiality-preserving smart contracts we have to trust a trusted party in the form of the hardware manufacturer (\eg Intel).

### 2020-09-17 LaTeX/sections/paper.tex
Bib added
edits
point form sections

@@
 
-\paragraph{Other Literature.}
-% Madiba -> pulp.bib
-% Velocity, 
-% FuturesMex~\cite{massacci2018futuresmex}
-% Findel 
-% Libra~\cite{mavroudis2019libra}
-% Arwen
-% Tesseract (SGX-exchange)~\cite{bentov2017tesseract}
-% Christopher Thorpe
+\paragraph{Other Academic Literature.} There are numerous industry projects on blockchain-based exchanges and orderbooks but most of the academic literature is on topics that are related but tangential to the mechanics of trade execution.
+Early literature considered trade execution under encryption (\ie dark markets)~\cite{TP07,YSLT10,TW12}.
+A number of projects consider structuring futures and derivatives in smart contracts---Velocity ~\cite{eskandari2017feasibility}, Findel ~\cite{biryukov2017findel}, FuturesMex~\cite{massacci2018futuresmex}---but once issued, the derivative can be traded using exchanges.
+Atomic swaps (\ie payment vs delivery) are necessary for settling trades and some general approaches include Arwen~\cite{heilman2020arwen} and Tesseract~\cite{bentov2017tesseract}.
 
@@
 
-\subsection{Market clearing price -> informational only}
+We don't cancel
+Front-running is a problem
+Market is so short-lived
+Find an order to cancel in the data structure -> stronger than a PQ like binary search or a binary search tree. (Also have the trader find their own order and tell us where it is), or use a list.
+
+\subsection{Market clearing price}
+
+Uniswap - 
+MCP -> no really reliable, could in theory be used as an oracle but probably shouldn't be 
+At best, part of a distributed oracle
 
@@
 
-% We use one-shot market for the sake of our performance tests on different data structures. and once we have all the numbers we can think about iterated market.
+We use one-shot market for the sake of our performance tests on different data structures. and once we have all the numbers we can think about iterated market.
 
-At the end of the trading period, the market needs to be closed and reopened.
+ We want the market to run on a periodic schedule => it is difficult for market participants to call the \texttt{Close()} function periodically.
+
+ PM paper -> close every block, close run a beginning of block. 
+ Every other block (modifiers only open for block) -> schedule running close (which could reopen when it is done) -> it won't run itself -> Ethereum Alarm Clock, traders will want to trade so could trigger it.
+Why won't they ?
+Costs a lot.
+
+ %At the end of the trading period, the market needs to be closed and reopened.
 However, there is no automatic process to called an Ethereum function and contracts can only run when a function is called.
-
-%when to close the market?
-%What time period?
-
-% We want the market to run on a periodic schedule => it is difficult for market participants to call the \texttt{Close()} function periodically.
-
-% However there are incentives for them to do so: (i) they get paid and refunded (financial incentives), and (ii) Closing the market allow market participants to open it again and start their trading activities
-
-% Another solution pattern to enforce the time is to use the Ethereum Alarm Clock
 
@@
 %= = = = = = Miners Close the Market = = = = = = =%
-\paragraph{Miners Close and Reopen the Market.} The difference between the best bid and ask prices is called the \textit{bid-ask spread}.
+\paragraph{Miners.} The difference between the best bid and ask prices is called the \textit{bid-ask spread}.
 In our design, when the trade occurs between the the highest bid (the highest amount a buyer is willing to pay for an asset) and lowest ask (the lowest amount a seller is willing to accept for an asset) orders, the bid-ask spread is paid to the miner.
@@
 So there is enough economic incentive for the the miner to execute the \texttt{CloseMarket()} function and get refunded as the refund amount could be potentially higher than the bid-ask spread.
+% Miners will compete for it
+
 % = = = = = = = = = =Processing Orders in Groups= = = = = = = = = = = = = = = %
 
-\paragraph{Processing Orders in Groups.} Another solution pattern is to process certain number of bid and ask orders upon every execution of the \texttt{CloseMarket()} function rather than treating them as one substantial transaction.
+\paragraph{Next Traders.} Another solution pattern is to process certain number of bid and ask orders upon every execution of the \texttt{CloseMarket()} function rather than treating them as one substantial transaction.
 A market participant $P_i$ would process $n$ orders from the previous market (\texttt{CloseMarket(n)}) when sending new orders to the current market.
@@
 => contribution to the community!?
-%= = = = = =  = =  =  Meta txs =  = = = = = = = = =%
-
-\paragraph{Using the Meta Transactions.} Meta transactions enable users to execute Ethereum functions without paying the gas.
-Rather than spending gas, users sign their intended action using their private keys and broadcast it to the network with no cost.
-A third party process (\textit{a relayer}) then crafts the actual transaction on user's behalf, sends the transaction to the Ethereum blockchain, and charges the base contract with the associated fees (see Figure~\ref{fig:meta_tx}).
-The required gas to pay for the \texttt{Match()} function could be collected as fees.
-So market participants are charged with certain amounts of fees every time they submit an order, these fees are accumulated in the CallMarket contract and will be used to pay for executing the \texttt{CloseMarket()} function.
-
-% Cancelations
-% How quick we open and close
-%
-
-% = = = = = = = = = = = =meta_tx Figure = = = = = = = = = = = = =  %
-
-%\begin{figure}[htb!p]
-%\centering
-%\includegraphics[width=0.8\textwidth]{fig/meta_tx.png}
-%\caption{\footnotesize{}  \label{fig:meta_tx}}
-%\end{figure}
-
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
+% Chop it smaller, pushes it around -> could have orders in next market pay to close previous market -> not enough orders come in -> fall back to traditional close -> progressive close
 
@@
 
-\paragraph{Using the "Contract Pays" Model.} An alternative solution is to design the market such that the last person to submit an order calls the \texttt{CloseMarket()} function, but in contrast to a normal transaction (where the person initiating the transaction must pay the fee), here the CallMarket contract pays the cost for closing the market and matching the orders respectively.
+\paragraph{Contract Pays.} An alternative solution is to design the market such that the last person to submit an order calls the \texttt{CloseMarket()} function, but in contrast to a normal transaction (where the person initiating the transaction must pay the fee), here the CallMarket contract pays the cost for closing the market and matching the orders respectively.
 To enforce this design we can use Solidity function modifiers; every time a new order is submitted, a function modifier checks whether (i) the auction period has to end and/or (ii) the maximum number of total orders has reached.
@@
 
+%= = = = = =  = =  =  Meta txs =  = = = = = = = = =%
+
+\paragraph{A Relayer.} Meta transactions enable users to execute Ethereum functions without paying the gas.
+Rather than spending gas, users sign their intended action using their private keys and broadcast it to the network with no cost.
+A third party process (\textit{a relayer}) then crafts the actual transaction on user's behalf, sends the transaction to the Ethereum blockchain, and charges the base contract with the associated fees (see Figure~\ref{fig:meta_tx}).
+The required gas to pay for the \texttt{Match()} function could be collected as fees.
+So market participants are charged with certain amounts of fees every time they submit an order, these fees are accumulated in the CallMarket contract and will be used to pay for executing the \texttt{CloseMarket()} function.
+
 %= = = = = =  = =  =  Rollups=  = = = = = = = = =%
@@
 
-\paragraph{Using Rollups.} Rollup is a scaling method that moves the storage and computation of the smart contracts off-chain while maintaining the transaction data on the main chain as call-data.
-In this technique, any Ethereum user can act as a validator; they can execute the \texttt{CloseMarket()}function and only post the new state of the contract (the updated balance of traders) in the form of \textit{assertions} to the main chain.
-Rollups improve scalability, provide faster and cheaper execution of the contracts, and eliminate the gas limit as the contract is no longer executed on-chain.
-In the followings we briefly discuss different rollup proposals and techniques. Each approach uses a different method to ensure correction of assertions:
-
-\paragraph{Non-interactive Rollups.} In this rollup technique, assertions are posted together with a validity proof that would be later used by validators to check if the \texttt{CloseMarket()} function has been executed correctly.
-ZK-Rollup scheme is one of the solutions that uses ZK-SNARKs to prove the validity of the assertions in zero-knowledge.
-ZK proofs are quick and cheap to verify but they are expensive and time consuming to generate.
-These proofs could be generated (i) for free or (ii) the CallMarket contract could collect proportional fees for every trade that is successfully executed.
-
-\paragraph{Optimistic Rollups.} In this scheme, assertions are assumed to be valid if there is no dispute posted about them with a certain window of time (a.k.a.
-"the challenge period').
-Here, dispute resolution is a gas-costly method as the CallMarket contract would have to emulate the transaction on-chain to ensure the correctness the assertion.
-This scheme introduces a tradeoff between privacy and performance as all the assertions are publicly available and accessible.
-However, here the new state only reflects the updated balances of traders and no secret is involved.
-
-\paragraph{{Multi-round Interactive Rollups.}} In this design paradigm, \textit{pending assertions} are posted on-chain and they are open to dispute.
-Once the challenge period is over and no challenge is submitted, the assertion is confirmed and the CallMarket contract transitions to the new state (\ie updates traders' balances).
-This scheme takes the overhead for the CallMarket contract to execute the \texttt{Close()} on-chain by using rounds to the dispute resolutions.
-The two parties (asserter and challenger) must run an interactive protocol and the CallMarket smart contract would have to act as a referee and decides which party's claim is true.
-Arbitrum is an example of multi-round interactive rollups that uses an efficient challenge-based protocol to penalize the dishonest parties~\cite{kalodner2018arbitrum}.
-
-%= = = = = =  = =  =  SGX=  = = = = = = = = =%
-
-\paragraph{{Using Trusted Execution Environments.}} Another way of achieving execution of the \texttt{CloseMarket()} function is incorporating the Ethereum blockchain into the Trusted Execution Environments (TEEs) and decoupling the contract execution from consensus mechanism.
-TEEs enable secure execution of applications in an isolated processing environment called the \textit{enclave}.
-Here, the enclave could execute the \texttt{CloseMarket()} function off-chain in TEEs and publish an on-chain attestation Quote to the CallMarket contract.
-The contract then verifies the correctness of the Quote and if validated correctly, it transitions to the new state.
-Ekiden is an example that uses Intel SGX to solve the scalability and confidentiality issues with the smart contract execution~\cite{cheng2019ekiden}.
-A drawback of this scheme is in order to achieve confidentiality-preserving smart contracts we have to trust a trusted party in the form of the hardware manufacturer (\eg Intel).
+Someone does it off-chain and (a) Ethereum checks that it was done right with a proof (SNARK)~\cite{}, (b) Ethereum checks that it was done right with an attestation from a trusted execution environment (\eg Intel SGX or Intel TXT) (SGX is broken but TXT is still fine)~\cite{cheng2019ekiden}, and (c) we assume it was done right but Ethereum will resolve a dispute about where specifically the computation went wrong.~\cite{kalodner2018arbitrum}.
+Why not use SGX for everything?
 
 % = = = = = = = = = = = =Transferring the Collateral back to the traders = = = = = = = = = = = = =  %
-\subsection{Transferring the Collateral back to Traders.}
+\subsection{Collateralization.}
 
-% Safely returning collateral 
-% Options for non-collaterialized markets
-
-\subsection{Clearing Mappings}
-
-To maintain the collateral balance of each market participant, we use two Solidity type one-to-one mappings that map Ethereum addresses to 256 bits unsigned integers; \texttt{TotalBalance} and \texttt{UnavailableBalance}.
-Once market closes and orders are matched, the \texttt{UnavailableBalance} needs to be cleared.
-However, since it is not possible to delete the entire mapping without knowing the keys~\footnote{https://solidity.readthedocs.io/en/v0.5.12/security-considerations.html}, clearing the \texttt{UnavailableBalance} mapping remains a challenging issue to solve.
-Here we provide a landscape of solutions for that.
-%only individual keys and what they map to can be deleted.
-
-\begin{itemize}
-
-%---------+++++++++++++++++++-----------------
-\item \textbf{Creating a New Mapping Every Time the Market Opens.} Instead of clearing the \texttt{UnavailableBalance} of traders at the end of a matching process, we could create a new mapping every time the market opens.
-Note that in this scheme traders can claim their funds back (using the \texttt{ClaimEther()} and/or \texttt{ClaimToken} methods) only when the market is closed (\ie the market is in the \texttt{Closed} state).
-
-%---------+++++++++++++++++++-----------------
-\item \textbf{Creating Custom Keys for the Mapping.} We can create custom keys for the mapping by defining a counter as a global variable inside the call market smart contract and increment it only once at the end of the matching process.
-So instead of clearing the mapping, we only use another portion of it every time the market opens.
-
-%---------+++++++++++++++++++-----------------
-\item \textbf{Storing the Mapping in a Data-Contract.} Another design proposal is to create a new smart contract every time the market opens, this data contract only stores the \texttt{UnavailableBalance} mapping and will be destroyed (using the \texttt{SELFDESTRUCT} operation) at the end of the matching process.
-
-%---------+++++++++++++++++++-----------------
-\item \textbf{Storing the Mapping keys in an additional Array.} Another common pattern is to create an additional array on top of the mapping and iterate over that.
-This array (\eg address[]) stores the traders' addresses and enables us to iterate over the mapping and delete individual keys and what they map to at the end of the matching process.
-Note that this is a gas-costly design pattern as we would need to maintain a secondary data structure.
-
-%---------+++++++++++++++++++-----------------
-\end{itemize}
+Options for non-collateralized markets
+ERC20 to ERC20 -> extra transaction
 

### 2020-09-21 LaTeX/sections/appendix.tex
Appendix added

@@
 
-% Extended discussion on cleaning up data structures in Ethereum
+\section{Extended Discussion on Cleaning up Data Structures on Ethereum}
 
-\section{Ethereum's Gas Model}
+As discussed in Section~\ref{sec:gasrefund}, whether to clean up storage variables or not remains a vital challenge for developers when developing DApps on the Ethereum blockchain--- this is even more crucial for implementation of \cm, as we needed  to choose the best middle ground design model which gives us a satisfactory performance and cost results.
+For this reason, we believe it it is helpful (both for researchers and developers) to extend our discussion on this topic.
+First, we discuss the Ethereum's gas model--- (i) what are different gas parameters one needs to take into account when sending a transaction on the Ethereum blockchain, (ii) what is the gas refund, and (iii) and how it is calculated.
+Next, we discuss one major challenge, \textit{clearing mappings}, that we faced when implementing \cm on the Ethereum.
+
+\subsection{Ethereum's Gas Model}
 
@@
 Each of these opcodes has a fixed amount of gas assigned and is a measure of computational effort.
-Separating ETH from gas prevents transactions cost from being too expensive as they are less impacted by ETH price fluctuations.
+Separating ETH from gas prevents transaction costs from being too expensive as they are less impacted by ETH price fluctuations.
 Gas unit does not a have a monetary value and as mentioned, it only  measures the computational work undertaken by miners.
 To pay miners, Ethereum introduces a \texttt{gas price} --- small denomination of ether called \textbf{Gwei} attached to each gas unit.
-Essentially, gas price indicates how much users are willing to pay per unit of gas, clearly the higher gas price leads to the faster execution of a transaction.
+Essentially, gas price indicates how much users are willing to pay per unit of gas--- clearly a higher gas price leads to the faster execution of a transaction.
 Miners also need to know the total amount of computational work a user is requesting, called the \texttt{gas limit}.
-\texttt{Gas limit} is a parameter that limits the amount of gas users would spend in a transaction.
-It protects users from spending unlimited ETH on their transactions and must be set carefully.
-If the \texttt{gas limit} is too low, the transaction will exceed the limit, all operations will be reverted while the user must pay for the computational work performed by the miner.
+\texttt{Gas limit} is a parameter that limits the amount of gas users would spend in a transaction, it protects users from spending unlimited ETH on their transactions and must be set carefully.
+If the \texttt{gas limit} is too low, the transaction will exceed the limit and all operations will be reverted while the user must pay for the computational work performed by the miner.
 By default the gas limit for an Ethereum transaction is 21,000 gas.
@@
 
-\subsection*{Gas Refunds.}There are two particular EVM operations with negative gas --- certain amount of gas is refunded to the sender at the end of the transaction. These operation include:
+\subsubsection*{Gas Refunds.}There are two particular EVM operations with negative gas--- certain amount of gas is refunded to the sender at the end of the transaction. These operations include:
 
-\paragraph{\texttt{SELFDESTRUCT}.}This operation destroys and deletes the originating contract and refunds its balance (if any) to a designated receiver address.
+\paragraph{\texttt{SELFDESTRUCT}.}This operation destroys the originating contract and refunds its balance (if any) to a designated receiver address.
 Note that the Ethereum storage is implemented in the form of a has map and EVM is not statistically aware of which storage slots are held by the contract.
-Because of this the \texttt{SELFDESTRUCT} operation does not remove the initial byte code of the contract from the chain, but it frees up the state storage and has a refund of 24,000 gas.
+So the \texttt{SELFDESTRUCT} operation does not remove the initial byte code of the contract from the chain, but it frees up the state storage and has a refund of 24,000 gas.
 
@@
 So at the end of a successful transaction, the amount of gas in the refund counter (capped at half the net gas used) is returned to the caller.
-At the time of this writing, Ethereum transaction receipts only account for the \texttt{gasUsed}, which is the total amount of gas units spent during a transaction, and we are not able to obtain the value of the EVM's refund counter from inside the EVM~\cite{signer2018gas}.
-So in order to account for refunds, we decide to calculate them manually; first we figure out exactly how much storage is being cleared or how many smart contracts are being destroyed, then we multiply these numbers by 24,000 and 15,000 respectively.
+At the time of this writing, Ethereum transaction receipts only account for the \texttt{gasUsed}, which is the total amount of gas units spent during a transaction, and users are not able to obtain the value of the EVM's refund counter from inside the EVM~\cite{signer2018gas}.
+So in order to account for refunds, we can only calculate them manually; first we need to figure out exactly how much storage is being cleared or how many smart contracts are being destroyed, then we multiply these numbers by 24,000 and 15,000 respectively.
 
@@
 
-To maintain the collateral balance of each market participant, we use two Solidity type one-to-one mappings that map Ethereum addresses to 256 bits unsigned integers; \texttt{TotalBalance} and \texttt{UnavailableBalance}.
-Once market closes and orders are matched, the \texttt{UnavailableBalance} needs to be cleared.
-However, since it is not possible to delete the entire mapping without knowing the keys~\footnote{https://solidity.readthedocs.io/en/v0.5.12/security-considerations.html}, clearing the \texttt{UnavailableBalance} mapping remains a challenging issue to solve.
-Here we provide a landscape of solutions for that.
-%only individual keys and what they map to can be deleted.
+To maintain the ETH and ERC20 tokens balances of each trader in \cm, we use one-to-one mappings, \texttt{totalBalance} and \texttt{unavailableBalance}, that map Ethereum addresses to unsigned integers.
+Note that we need to clear up the entire  \texttt{unavailableBalance} mapping during the orders settlement and clearing phase.
+However in Solidity, it is not possible to delete the entire mapping without knowing the keys~\footnote{In a Solidity mapping, only individual keys and what they map to can be deleted: https://solidity.readthedocs.io/en/v0.5.12/security-considerations.html}.
+Here we propose and discuss the landscape of various solutions together with how each method affects the total amounts of gas costs for clearing orders in \cm.
 
-\begin{itemize}
+\begin{enumerate}
 
 %---------+++++++++++++++++++-----------------
-\item \textbf{Creating a New Mapping Every Time the Market Opens.} Instead of clearing the \texttt{UnavailableBalance} of traders at the end of a matching process, we could create a new mapping every time the market opens.
-Note that in this scheme traders can claim their funds back (using the \texttt{ClaimEther()} and/or \texttt{ClaimToken} methods) only when the market is closed (\ie the market is in the \texttt{Closed} state).
+\item \textbf{Storing mapping keys in additional array.} This is a common design pattern used by DApp developers--- to delete the mapping, one needs to create an additional array on top of it and iterate over that array.
+For example in \cm, we can create \texttt{address[] helperArray} that stores traders' addresses.
+Knowing traders addresses (\ie mapping keys), we can now iterate over the mapping and delete these individual keys and what they map to at the end of the matching/clearing process.
+Despite being a common design pattern, this solution
+significantly increases the total cost of matching the orders as Solidity loops are costly operations.
 
 %---------+++++++++++++++++++-----------------
-\item \textbf{Creating Custom Keys for the Mapping.} We can create custom keys for the mapping by defining a counter as a global variable inside the call market smart contract and increment it only once at the end of the matching process.
-So instead of clearing the mapping, we only use another portion of it every time the market opens.
+\item \textbf{Storing the mapping in a separate smart contract.} Another design proposal is to create a new smart contract every time the market opens.
+This contract \textit{only} stores the \texttt{unavailableBalance} mappings and will be destroyed (using the \texttt{SELFDESTRUCT} operation) at the end of the matching process.
+This solution assigns overhead costs to the \texttt{matchOrders()} function as it involves an external call to another smart contract (\ie destroy the contract containing the mappings).
 
 %---------+++++++++++++++++++-----------------
-\item \textbf{Storing the Mapping in a Data-Contract.} Another design proposal is to create a new smart contract every time the market opens, this data contract only stores the \texttt{UnavailableBalance} mapping and will be destroyed (using the \texttt{SELFDESTRUCT} operation) at the end of the matching process.
+\item \textbf{Generating custom mapping keys.} We can also define a global counter variable and use it as a custom key for the mappings.
+This counter is incremented \textit{only once} at the end of the matching process.
+So we only use a new portion of the mapping (and leave the used portion on the Ethereum blockchain) every time the market opens.
+This solution removes the burden of the gas cost from the \texttt{matchOrders()} function (as discussed in Section~\ref{sec:gasrefund}, leaving the data on chain is cheaper then cleaning it up), however DApp developers are advised to be good citizens of Ethereum and cleanup on-chain data they no longer need.
 
 %---------+++++++++++++++++++-----------------
-\item \textbf{Storing the Mapping keys in an additional Array.} Another common pattern is to create an additional array on top of the mapping and iterate over that.
-This array (\eg address[]) stores the traders' addresses and enables us to iterate over the mapping and delete individual keys and what they map to at the end of the matching process.
-Note that this is a gas-costly design pattern as we would need to maintain a secondary data structure.
+\item \textbf{Creating a new mapping every time the market opens.} Similar to the previous proposal, we can skip deleting mappings and instead create a new mapping every time the market opens.
+Again, although this method does not increase the cost of matching the orders in \cm, it leaves unused data on the Ethereum blockchain.
 
 %---------+++++++++++++++++++-----------------
-\end{itemize}
+\end{enumerate}
 

### 2020-09-21 LaTeX/sections/abstract.tex
full round edit (#1)

@@
 As blockchain performance continues to improve (both in research and in practice) and on-chain dealer-based exchanges like Uniswap (an alternative to order-based exchanges) rise in popularity, it seems to be an ideal time to revisit the idea of a fully on-chain order-driven exchange and benchmark what is possible performance-wise.
-We design and optimize an Ethereum-based call market exchange, \cm, and conduct a variety of experiments to show the current benchmark is around one hundred trade executions per block.
+We design and optimize an Ethereum-based call market exchange, \cm, and conduct a variety of experiments to show \textblue{the current benchmark is around one hundred trade executions per block}.
 We also explore numerous extensions for further improvements.

### 2020-09-21 LaTeX/sections/appendix.tex
full round edit (#1)

@@
 
-As discussed in Section~\ref{sec:gasrefund}, whether to clean up storage variables or not remains a vital challenge for developers when developing DApps on the Ethereum blockchain--- this is even more crucial for implementation of \cm, as we needed  to choose the best middle ground design model which gives us a satisfactory performance and cost results.
+As discussed in Section~\ref{sec:gasrefund}, whether to clean up storage variables or not remains a vital challenge for developers when developing DApps on the Ethereum blockchain--- this is even more crucial for implementation of \cm, as we need to choose the best middle ground design model which gives us optimized performance and cost results.
 For this reason, we believe it it is helpful (both for researchers and developers) to extend our discussion on this topic.
@@
 
-To maintain the ETH and ERC20 tokens balances of each trader in \cm, we use one-to-one mappings, \texttt{totalBalance} and \texttt{unavailableBalance}, that map Ethereum addresses to unsigned integers.
+To maintain the ETH and token balances of each trader in \cm, we use one-to-one mappings, \texttt{totalBalance} and \texttt{unavailableBalance}, that map Ethereum addresses to unsigned integers.
 Note that we need to clear up the entire  \texttt{unavailableBalance} mapping during the orders settlement and clearing phase.
@@
 So we only use a new portion of the mapping (and leave the used portion on the Ethereum blockchain) every time the market opens.
-This solution removes the burden of the gas cost from the \texttt{matchOrders()} function (as discussed in Section~\ref{sec:gasrefund}, leaving the data on chain is cheaper then cleaning it up), however DApp developers are advised to be good citizens of Ethereum and cleanup on-chain data they no longer need.
+This solution removes the burden of the gas cost from the \texttt{matchOrders()} function (as discussed in Section~\ref{sec:gasrefund}, leaving the data on chain is cheaper than cleaning it up), however DApp developers are advised to be good citizens of Ethereum and cleanup on-chain data they no longer need.
 

### 2020-09-21 LaTeX/tables/functions.tex
full round edit (#1)

@@
 % = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
-	DepositToken()                           & Deposits ERC20 standard compliant tokens in the call market contract \\ \hline
+	depositToken()                           & Deposits ERC20 standard compliant tokens in \cm smart contract \\ \hline
 % = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
-	DepositEther()                           	& Deposits ETH in the call market contract                         			 \\ \hline
+	depositEther()                           	& Deposits ETH in \cm smart contract                        			 \\ \hline
 % = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
-	OpenMarket()                             & Opens the market                                                    					 \\ \hline
+	openMarket()                             & Opens the market                                                    					 \\ \hline
 % = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
-	CloseMarket()                            & Closes the market                                                    					\\ \hline
+	closeMarket()                            & Closes the market                                                    					\\ \hline
 % = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
-	SubmitBid()                              & Inserts the upcoming bid order messages inside the priority queue    \\ \hline
+	submitBid()                              & Inserts the upcoming bid order messages inside the priority queue    \\ \hline
 % = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
-	SubmitAsk()                              & Inserts the upcoming ask order messages inside the priority queue    \\ \hline
+	submitAsk()                              & Inserts the upcoming ask order messages inside the priority queue    \\ \hline
 % = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
-	MatchOrders()                           & Matches the orders against each other                                			\\ \hline
+	matchOrders()                           & Matches the orders against each other                                			\\ \hline
 % = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
-	ClaimTokens()                           & Transfers collateralized tokens back to the trader                       			\\ \hline
+	claimTokens()                           & Transfers collateralized tokens back to the trader                       			\\ \hline
 % = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
-	ClaimEther()                             & Transfers collateralized ETH back to the trader                       			\\ \hline
+	claimEther()                             & Transfers collateralized ETH back to the trader                       			\\ \hline
 % = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
 \end{tabular}
-\caption{\footnotesize{Primary operations of the call market smart contract.}
-\label{tab:callmarket_functions}}
+\caption{\footnotesize{Primary operations of \cm smart contract.}
+\label{tab:cm_functions}}
 \end{table}

### 2020-09-22 LaTeX/sections/paper.tex
resolved th text blues + added the numbers for arbitrum

@@
 
-For better or worst, blockchain technologies like Ethereum have dramatically lowered the barrier to entry for developing and deploying financial technology.
+For better or worse, blockchain technologies like Ethereum have dramatically lowered the barrier to entry for developing and deploying financial technology.
 New tokens have been launched with a few clicks of a user interface, and large investment infrastructures have been developed and deployed with little regulatory oversight.
@@
 A fully on-chain exchange is feasible but considered too slow, at least for a public blockchain like Ethereum.
-We believe it is a very good time to do a deep dive into understanding precisely \textit{how slow} for the following reasons: (1) public blockchains are becoming faster (both in theory and slowly in practice) and the efficiency of an on-chain exchange will increase in time, (2) demand for on-chain trading is exemplified by the recent popularity of dealer-based (or quote-based) trading like Uniswap and Curve Finance, and (3) stablecoins have become a popular and allow on-chain trading with pricing in USD (or other government currency).
+We believe it is a very good time to do a deep dive into understanding precisely \textit{how slow} for the following reasons: (1) public blockchains are becoming faster (both in theory and slowly in practice) and the efficiency of an on-chain exchange will increase in time, (2) demand for on-chain trading is exemplified by the recent popularity of dealer-based (or quote-based) trading like Uniswap and Curve Finance, and (3) stablecoins have become popular and allow on-chain trading with pricing in USD (or other government currency).
 
@@
 
-\paragraph{Central exchanges (CEX).} Traditional financial markets (\eg NYSE and NASDAQ) use order-matching systems to arrange trades.
+\paragraph{Central Exchanges (CEX).} Traditional financial markets (\eg NYSE and NASDAQ) use order-matching systems to arrange trades.
 An exchange will list one or more assets (stocks, bonds, derivatives, or more exotic securities) to be traded with each given its own orderbook priced in a currency (\eg USD).
-Exchanges for blockchain-based assets (also called cryptoassets by enthusiasts) can operate the same way, using a centralized exchange (CEX) design where a firm operates the platform as a trusted third party in every aspect: custodianship over assets/currency being traded, exchanging assets fairly, and offering the best possible price execution.
+Exchanges for blockchain-based assets (also called crypto assets by enthusiasts) can operate the same way, using a centralized exchange (CEX) design where a firm operates the platform as a trusted third party in every aspect: custodianship over assets/currency being traded, exchanging assets fairly, and offering the best possible price execution.
 Security breaches and fraud (\eg MtGox~\cite{TheHisto45:online}, QuadrigaCX~\cite{SEBIOrde83:online}, and many others) in centralized exchanges have become a common source of lost funds for users, while accusations of unfair trade execution have been levelled but are difficult to prove.
 
-\paragraph{On-chain orderbooks.} For trades between two blockchain-based assets (\eg a digital asset priced with a cryptocurrency, stablecoin, or second digital asset), order matching can be performed `on-chain' by deploying the order-matching system either on a dedicated blockchain or inside a decentralized application (DApp; \textit{a.k.a.} smart contract).
+\paragraph{On-chain Orderbooks.} For trades between two blockchain-based assets (\eg a digital asset priced with a cryptocurrency, stablecoin, or second digital asset), order matching can be performed `on-chain' by deploying the order-matching system either on a dedicated blockchain or inside a decentralized application (DApp; \textit{a.k.a.} smart contract).
 In this model, traders entrust their assets to an autonomously operating DApp with known source code instead of a third party custodian that can abscond with or lose the funds.
@@
 
-\paragraph{On-chain dealers.} Another on-chain advantage is that other smart contracts, not just human users, can initiate trades, enabling broader decentralized finance (DeFi) applications.
+\paragraph{On-chain Dealers.} Another on-chain advantage is that other smart contracts, not just human users, can initiate trades, enabling broader decentralized finance (DeFi) applications.
 This has fuelled a resurgence in on-chain exchange but through a quote-driven design rather than an order-driven one.
@@
 By contrast, an orderbook requires no upfront inventory and does not have to charge trading fees (but can).
-Finally, there is a complicated difference in their price dynamics (\eg market impact of a trade, slippage between the best bid/offer and actual average execution price, \etc)---deserving of an entire research paper to precisely define.
+Finally, there is a complicated difference in their price dynamics (\eg market impact of a trade, slippage between the best bid/ask and actual average execution price, \etc)---deserving of an entire research paper to precisely define.
 We leave it as an assertion that with equal liquidity, orderbooks have more favourable price dynamics for traders.
 
-\paragraph{Hybrid designs.} Before on-chain dealers became prominent in the late 2010s, the most popular design was hybrid order-driven exchanges with some trusted off-chain components and some on-chain functionality.
+\paragraph{Hybrid Designs.} Before on-chain dealers became prominent in the late 2010s, the most popular design was hybrid order-driven exchanges with some trusted off-chain components and some on-chain functionality.
 Some (\eg EtherDelta) were envisioned as operating fully on-chain, but performance limitations drove developers to move key components, such as the order matching system, off-chain to a centralized database.
@@
 
-\paragraph{Blockchain limitations and solution.} While an orderbook is a ledger and blockchains provide a distributed ledger, it is not straightforward to drop a continuous-time orderbook onto a blockchain.
+\paragraph{Blockchain Limitations and Solution.} While an orderbook is a ledger and blockchains provide a distributed ledger, it is not straightforward to drop a continuous-time orderbook onto a blockchain.
 An older 2014 paper~\cite{clark2014decentralizing} on the `Princeton prediction market'~\cite{Bra13} motivates our work.
@@
 
-\paragraph{Call markets.} The researchers propose using a call market instead of a continuous-time market~\cite{clark2014decentralizing}.
+\paragraph{Call Markets.} The researchers propose using a call market instead of a continuous-time market~\cite{clark2014decentralizing}.
 Orders are collected and placed into the orderbook over a window of time (\eg 1 or more blocks), then the market is closed and the orders are processed in batch: the best bids are matched to the best asks in order.
@@
 The most critical design decision is the data structure for holding orders.
-While data structures are well studied for many languages, Solidity/EVM has its own unique aspects (\eg gas refunds, a relatively cheap mapping data structure, only partial support for object oriented programming) that creates difficulties in assessing which will perform best without actually deploying and evaluating each variant.
+While data structures are well studied for many languages, Solidity/EVM has its own unique aspects (\eg gas refunds, a relatively cheap mapping data structure, only partial support for object oriented programming) that create difficulties in assessing which will perform best without actually deploying and evaluating each variant.
 
 When closing a call market, the orders are examined in order: highest to lowest price for bids, and lowest to highest price for asks.
-It most circumstances, the market closing algorithm does not have to consider any deeper bids/asks from the list when choosing whether the current best bid and ask can be fulfilled.
+In most circumstances, the market closing algorithm does not have to consider any deeper bids/asks from the list when choosing whether the current best bid and ask can be fulfilled.
 The only exceptions are in the case of a tie on price or a canceled order, both of which we return to later.
@@
 \item \textbf{Heap with Dynamic Array.} A heap is a type of binary tree data structure that comes in two forms of a (i) Max-Heap and (ii) Min-Heap.
-All the nodes of tree are in a specific order and the root of the tree always represents the highest priority item of the data structure (the largest and smallest values in the Max-Heap and Min-Heap respectively).
+All the nodes of the tree are in a specific order and the root always represents the highest priority item of the data structure (the largest and smallest values in the Max-Heap and Min-Heap respectively).
 We implemented a priority queue with a heap that stores its data in a dynamically-sized array.
@@
 
-\item \textbf{Heap with Mapping.} In the above implementations, the heap stores the entire order (as a struct) in the heap.
-In this variant, we store the order struct in a Solidity mapping and store the mapping's key in the heap.
+\item \textbf{Heap with Mapping.} In the above implementations, the entire order is stored (as a struct) in the heap.
+In this variant, we store the order struct in a Solidity mapping and store the mapping keys in the heap.
 
@@
 The value of the mapping is a struct with order data and the key of the next (and previous) node in the list.
-The contract stores the key of the first node (head) in the list.
+The contract stores the key of the first node (head) and last node (tail) in the list.
 
@@
 \centering
-\includegraphics[width=0.8\textwidth]{fig/random_insertion.png}
-\caption{\footnotesize{Gas costs for enqueuing random items into five different priority queue variants.
+\includegraphics[width=0.8\textwidth]{fig/random_insertion2.png}
+\caption{\footnotesize{Gas costs for enqueuing random numbers into five priority queue variants.
 For the x-axis, a value of 10 indicates it is the 10th number entered in the priority queue.
@@
 
-\subsubsection{Dequeue performance.} For each PQ variant storing 50 random integers, the \texttt{Dequeue()} function is iterated until the data structure is empty.
+\subsubsection{Dequeue Performance.} For each PQ variant storing 50 random integers, the \texttt{Dequeue()} function is iterated until the data structure is empty.
 The total gas cost for fully dequeuing the priority queue variants is outlined in Table~\ref{tab:PQUnitTests}.
@@
 Based on our manual estimates (EVM does not expose the refund counter), every variant receives the maximum gas refund possible (\ie half the total cost of the transaction).
-In other words, each of them actually consumes twice the \texttt{gasUsed} amount in gas before the refund, however none of them are better or worst based on how much of a refund they generate.
+In other words, each of them actually consumes twice the \texttt{gasUsed} amount in gas before the refund, however none of them are better or worse based on how much of a refund they generate.
 
@@
 For these reasons, we suggest using a linked list variant for this specific application.
-As it can be seen in Figure~\ref{fig:random_insertion}, the associated cost for inserting elements into a linked list PQ is significantly greater than the linked list with mapping, as each insertion cause the creation of a new contracts.
+As it can be seen in Figure~\ref{fig:random_insertion}, the associated cost for inserting elements into a linked list PQ is significantly greater than the linked list with mapping, as each insertion causes the creation of a new contract.
 Accordingly, we choose to implement the call market with the linked list with mapping.
@@
 
-\subsection{Cost/Benefit of cleaning up after yourself}
-\label{sec:LLvsLLMapping}
+\subsection{Cost/Benefit of Cleaning up After Yourself}
 \label{sec:gasrefund}
@@
 This suggests a general principle: cleaning up after yourself will pay for itself in gas refunds.
-Unfortunately, this is not universally true as shown by applying the same principle to the Linked List with Mapping.
+Unfortunately, this is not universally true as shown by applying the same principle to the linked list with mapping.
 
 Dequeuing in a linked list with mapping can be implemented in two ways.
-The simplest approach is process a node, update the head pointer, and leave the `removed' node's data behind in the mapping untouched (where it will never be referenced again).
+The simplest approach is to process a node, update the head pointer, and leave the `removed' node's data behind in the mapping untouched (where it will never be referenced again).
 Alternatively we can call \texttt{DELETE} on each mapping entry once we are done with a node in the PQ.
 Deleting a storage variable is identical to setting a non-zero variable to zero (\texttt{SSTORE} 0) that costs 20,000 gas but with 15,000 refunded---a net positive gas cost~\cite{wood2014ethereum}.
-As it can be seen in the last two rows of Table~\ref{tab:cleaning}, leaving the data on chain is cheaper then cleaning it up.
+As it can be seen in the last two rows of Table~\ref{tab:cleaning}, leaving the data on chain is cheaper than cleaning it up.
 
@@
 This is a complicated and under-explored area of Ethereum in the research literature.
-For our own work, we strive to be good citizens of Ethereum and cleanup to the extent that we can---thus all PQs in Table~\ref{tab:PQUnitTests} implement some cleanup and we select Linked List with Mapping and \texttt{DELETE} for \cm.
+For our own work, we strive to be good citizens of Ethereum and clean up to the extent that we can---thus all PQs in Table~\ref{tab:PQUnitTests} implement some clean up and we select linked list with mapping and \texttt{DELETE} for \cm.
 
@@
 We assume all trades are between ETH and an ERC20 token, all orders are pre-funded in the contract with ETH (for bids) and tokens (for asks), and once ETH or tokens are committed to an order, they cannot be withdrawn until the market closes.
-We revisit alternatives to this design below.
+\textblue{We revisit alternatives to this design below}.
 This ensures all executed orders clear and settle (\ie no defaults on payment or delivery).
@@
 
-\cm is written in 225 lines (SLOC) of Solidity (including 3 external libraries),\footnote{Github: linked removed for anonymity} a high level programming language that is syntactically similar to Java~\cite{Ethereum41:online}.
+\cm is written in 324 lines (SLOC) of Solidity~\footnote{Github: linked removed for anonymity}, a high level programming language that is syntactically similar to Java~\cite{Ethereum41:online}.
 We tested it with the Mocha testing framework (tests included in the codebase), as deployed using Truffle on Ganache-CLI to obtain our performance metrics.
-Table~\ref{tab:callmarket_functions} represents the call market's primary operations.
+Table~\ref{tab:cm_functions} represents \cm's primary operations.
 
@@
 
-The main research question is how many orders can be processed in a single Ethereum transaction when the closing the call market, \textblue{using Ethereum today}.
+The main research question is how many orders can be processed in a single Ethereum transaction when the closing the call market, using Ethereum today.
 As our previous experiments indicated, the choice of priority queue (PQ) implementation is the main influence on performance (see Table~\ref{tab:worst_case_matching}).
@@
 We looked at the \textit{worst-case} for performance which is when every submitted bid and ask is marketable (\ie will require fulfillment).
-In the first two columns, we determined the highest number of orders that can be processed in a single call to \texttt{CloseMarket()} and not exceed the the current Ethereum block gas limit of 11,741,495.
+In the first two columns, we determined the highest number of orders that can be processed in a single call to the \texttt{closeMarket()} and not exceed the the current Ethereum block gas limit of 11,741,495.
 Since Ethereum will become more efficient over time, we also were interested in how much gas it would cost to execute 1000 pairs of orders which is given in the third column.
@@
 To extend orders with a volume field, it must first be determined if the token are non-divisible or divisible (and to what precision).
-In this case, \texttt{MarketClose()} needs look at multiple bids to fulfill a single ask (and vice-versa) and declare its trading rules on partial fills.
-We also simplify the market rules around ties on price: we execut them FIFO (breaking front-running resistance for ties on prices).
+In this case, \texttt{closeMarket()} needs to look at multiple bids to fulfill a single ask (and vice-versa) and declare its trading rules on partial fills.
+We also simplify the market rules around ties on price: we execute them FIFO (breaking front-running resistance for ties on prices).
 A common trading rule (that does resist front-running) is to fill ties in proportion to their volume (\ie \textit{pro rata} allocation)\footnote{If Alice and Bob bid the same price for 100 tokens and 20 tokens respectively, and there are only 60 tokens left in marketable asks, Alice receives 50 and Bob 10.} however this approach is also contingent on the divisibility of tokens.
@@
 
- We want the market to run on a periodic schedule => it is difficult for market participants to call the \texttt{Close()} function periodically.
+ We want the market to run on a periodic schedule => it is difficult for market participants to call the \texttt{closeMarket()} function periodically.
 
@@
 There are possibilities that (i) no trade occurs or (ii) the bid-ask spread is zero (\ie the best bid and best ask prices are identical).
-So there is enough economic incentive for the the miner to execute the \texttt{CloseMarket()} function and get refunded as the refund amount could be potentially higher than the bid-ask spread.
+So there is enough economic incentive for the the miner to execute the \texttt{closeMarket()} function and get refunded as the refund amount could be potentially higher than the bid-ask spread.
 % Miners will compete for it
@@
 
-\paragraph{Next Traders.} Another solution pattern is to process certain number of bid and ask orders upon every execution of the \texttt{CloseMarket()} function rather than treating them as one substantial transaction.
-A market participant $P_i$ would process $n$ orders from the previous market (\texttt{CloseMarket(n)}) when sending new orders to the current market.
+\paragraph{Next Traders.} Another solution pattern is to process certain number of bid and ask orders upon every execution of the \texttt{closeMarket()} function rather than treating them as one substantial transaction.
+A market participant $P_i$ would process $n$ orders from the previous market (\texttt{closeMarket(n)}) when sending new orders to the current market.
 This process continues until all the orders in the previous markets are processed.
@@
 
-\paragraph{Contract Pays.} An alternative solution is to design the market such that the last person to submit an order calls the \texttt{CloseMarket()} function, but in contrast to a normal transaction (where the person initiating the transaction must pay the fee), here the CallMarket contract pays the cost for closing the market and matching the orders respectively.
+\paragraph{Contract Pays.} An alternative solution is to design the market such that the last person to submit an order calls the \texttt{closeMarket()}function, but in contrast to a normal transaction (where the person initiating the transaction must pay the fee), here the CallMarket contract pays the cost for closing the market and matching the orders respectively.
 To enforce this design we can use Solidity function modifiers; every time a new order is submitted, a function modifier checks whether (i) the auction period has to end and/or (ii) the maximum number of total orders has reached.
-If any of these two conditions are met, the \texttt{CloseMarket()} will be called.
+If any of these two conditions are met, \texttt{closeMarket()} will be called.
 Again, market participants are charged with certain amounts of fees every time they submit an order, these fees are accumulated in the CallMarket.
-Once the \texttt{CloseMarket()} is successfully executed and orders are matched, the contract transfers its funds to that person.
+Once the  \texttt{closeMarket()} is successfully executed and orders are matched, the contract transfers its funds to that person.
 Note that here the person must still have enough gas to cover the execution of the transaction as the funds will be only transferred after the transaction is fully executed.
@@
 Rather than spending gas, users sign their intended action using their private keys and broadcast it to the network with no cost.
-A third party process (\textit{a relayer}) then crafts the actual transaction on user's behalf, sends the transaction to the Ethereum blockchain, and charges the base contract with the associated fees (see Figure~\ref{fig:meta_tx}).
-The required gas to pay for the \texttt{Match()} function could be collected as fees.
-So market participants are charged with certain amounts of fees every time they submit an order, these fees are accumulated in the CallMarket contract and will be used to pay for executing the \texttt{CloseMarket()} function.
+A third party process (\textit{a relayer}) then crafts the actual transaction on user's behalf, sends the transaction to the Ethereum blockchain, and charges the base contract with the associated fees.
+The required gas to pay for the \texttt{matchOrders()} function could be collected as fees.
+So market participants are charged with certain amounts of fees every time they submit an order, these fees are accumulated in the CallMarket contract and will be used to pay for executing the \texttt{closeMarket()}function.
 
@@
 
+%Arbitrum numbers: 
+% Heap w/ dynamic array: matching 38 pairs, cost: 38,863
+% Heap w/ dynamic array: matching 1000 pairs, cost: 38,851
+% Heap w/ dynamic array: 2000 average submission: cost (averaged): 39,169 (we have the plot too, if needed)
+
 % = = = = = = = = = = = =Transferring the Collateral back to the traders = = = = = = = = = = = = =  %
-\subsection{Collateralization.}
+\subsection{Collateralization}
 

### 2020-09-22 LaTeX/sections/paper.tex
edits on tables
more notes on arbitrum: costs, censorship, tx finality

@@
 \includegraphics[width=0.8\textwidth]{fig/random_insertion2.png}
-\caption{\footnotesize{Gas costs for enqueuing random numbers into five priority queue variants.
+\caption{\footnotesize{Gas costs for enqueuing random integers into five priority queue variants.
 For the x-axis, a value of 10 indicates it is the 10th number entered in the priority queue.
@@
 %Arbitrum numbers: 
-% Heap w/ dynamic array: matching 38 pairs, cost: 38,863
+% Heap w/ dynamic array: matching 38 pairs, cost: 38,863 (this is the cost of posting transactions as calldata on the L1 chain, as well as the overhead associated with each batch of transactions, and the L1 cost of settling transactions in the Arbitrum protocol)
 % Heap w/ dynamic array: matching 1000 pairs, cost: 38,851
 % Heap w/ dynamic array: 2000 average submission: cost (averaged): 39,169 (we have the plot too, if needed)
+
+Costs in arbitrum include:
+
+--- Level 1 (Ethereum here) gas costs: This is the cost of posting transactions as calldata on the L1 chain, as well as the overhead associated with each batch of transactions, and the L1 cost of settling transactions in the Arbitrum protocol.
+
+---Validator’s staking costs: In normal operation, one validator will need to be staked.
+(putting their money behind the claim that this state is correct), if that state eventually gets confirmed they get their stake back, if not they'll lose it (half of it burns half of it goes back to the honest validator)
+
+---Validator computation and storage: Every validator must do computation to track the chain’s processing of transactions, and must maintain storage to keep track of the contracts’ EVM storage.
+
+More about Arbitrum:
+
+>> performance: Arbitrum software currently supports 453 transactions-per-second for basic transactions . more optimization on the way
+
+>> low cost: The cost of running Arbitrum Rollup is quite low compared to level 1 Ethereum and other scaling solutions such as those based on zero-knowledge proofs.
+Layer 2 (arbitrum roll up chain) fees are low, fixed, and predictable and should not be overly burdensome.
+Nobody needs to use special equipment or high-end machines.
+Arbitrum requires validators, which is a permissionless role that can be run on any reasonable on-line machine.
+Although anybody can act as a validator, in order to protect against a “tragedy of the commons” and make sure reputable validators are participating, we support a notion of “invited validators” that are compensated for their costs.
+
+>> Fast finality: txs complete with the same finality time as Ethereum L1
+
+>> Censorship Resistant: validators are not in a position to censor or front-run txs, when a tx arrives to the roll up chain, it is ordered and timestamped based on the Ethereum block number it is included in.
+So validators cannot reorder (MORE: a user would directly send txs to her contract on the Ethereum chain and then the call will be sent to the Arbitrum inbox contract which is responsible for incoming txs.
+All the incoming calls to this contract are ordered and time-stamped using the Ethereum block number.
+So front-running may/or may not still happen on the Ethereum chain, but validators are not in position to front-run, they will execute the txs in the order that they were put in the inbox contract.
+The team emphasizes on the fact that the main reason for having a separate contract on the Arbitrum chain to receive the incoming calls is to prevent censorship and front-running.)
 

### 2020-09-22 LaTeX/tables/pq.tex
edits on tables
more notes on arbitrum: costs, censorship, tx finality

@@
 % = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
-	\textbf{Enqueue()}       	& inserts an element into the priority queue                        \\ \hline
-	\textbf{Dequeue()}		& removes and returns the highest priority element 		\\ \hline
-	\textbf{isEmpty()}			& checks if the priority queue is empty 					\\ \hline
+	\textbf{Enqueue()}       	& Inserts an element into the priority queue                        \\ \hline
+	\textbf{Dequeue()}		& Removes and returns the highest priority element 		\\ \hline
+	\textbf{isEmpty()}			& Checks if the priority queue is empty 					\\ \hline
 % = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
@@
 \end{tabular}
-\caption{\footnotesize{Operations for a generic Priority Queue.}
+\caption{\footnotesize{Operations for a generic priority queue.}
 \label{tab:PQ_API}}

### 2020-09-22 LaTeX/sections/paper.tex
More edits

@@
 \paragraph{Contributions.} We design and implement \cm, a fully on-chain call market in Solidity---a high-level programming language for Ethereum.
-We choose Ethereum as a `hostile' environment for an orderbook: Ethereum is public (strongest adversary) and slow (lower-bound benchmark) relative to more scalable blockchains, including the anticipated Ethereum 2.0.
+We choose Ethereum as a `hostile' environment for an order book: Ethereum is public (strongest adversary) and slow (lower-bound benchmark) relative to more scalable blockchains, including the anticipated Ethereum 2.0.
 \cm is intended as a simple module that developers can modify as they choose.
@@
 In a \emph{brokered exchange}, a broker finds a buyer and seller.
-In an \emph{order-driven} market, offers to buy (\emph{bids}) and sell (\emph{offers}/\emph{asks}) from many traders are placed as orders in an orderbook.
-Order-driven markets can be \emph{continuous}, with buyers/sellers at any time adding orders to the orderbook (\emph{makers}) or executing against an existing order (\emph{takers}); or they can be \emph{called}, where all traders submit orders within a window of time and orders are matched in a batch like an auction.
+In an \emph{order-driven} market, offers to buy (\emph{bids}) and sell (\emph{offers}/\emph{asks}) from many traders are placed as orders in an order book.
+Order-driven markets can be \emph{continuous}, with buyers/sellers at any time adding orders to the order book (\emph{makers}) or executing against an existing order (\emph{takers}); or they can be \emph{called}, where all traders submit orders within a window of time and orders are matched in a batch like an auction.
 
@@
 \paragraph{Central Exchanges (CEX).} Traditional financial markets (\eg NYSE and NASDAQ) use order-matching systems to arrange trades.
-An exchange will list one or more assets (stocks, bonds, derivatives, or more exotic securities) to be traded with each given its own orderbook priced in a currency (\eg USD).
+An exchange will list one or more assets (stocks, bonds, derivatives, or more exotic securities) to be traded with each given its own order book priced in a currency (\eg USD).
 Exchanges for blockchain-based assets (also called crypto assets by enthusiasts) can operate the same way, using a centralized exchange (CEX) design where a firm operates the platform as a trusted third party in every aspect: custodianship over assets/currency being traded, exchanging assets fairly, and offering the best possible price execution.
@@
 
-\paragraph{On-chain Orderbooks.} For trades between two blockchain-based assets (\eg a digital asset priced with a cryptocurrency, stablecoin, or second digital asset), order matching can be performed `on-chain' by deploying the order-matching system either on a dedicated blockchain or inside a decentralized application (DApp; \textit{a.k.a.} smart contract).
+\paragraph{On-chain Order Books.} For trades between two blockchain-based assets (\eg a digital asset priced with a cryptocurrency, stablecoin, or second digital asset), order matching can be performed `on-chain' by deploying the order-matching system either on a dedicated blockchain or inside a decentralized application (DApp; \textit{a.k.a.} smart contract).
 In this model, traders entrust their assets to an autonomously operating DApp with known source code instead of a third party custodian that can abscond with or lose the funds.
 The trading rules will operate as coded, clearing and settling can be guaranteed, and order submission is handled by the blockchain---a reasonably fair and transparent system (but see front-running below).
-Finally, anyone can create an on-chain orderbook for any asset (on the same chain) at any time.
+Finally, anyone can create an on-chain order book for any asset (on the same chain) at any time.
 While they sound ideal, performance is a substantial issue and the main subject of this paper.
 
-In this paper, we focus on benchmarking an orderbook for a public blockchain (\eg Ethereum).
+In this paper, we focus on benchmarking an order book for a public blockchain (\eg Ethereum).
 Ethereum is widely-used and we stand to learn the most from working in a performance-hostile environment (\ie Ethereum is good lower-bound).
@@
 This has fuelled a resurgence in on-chain exchange but through a quote-driven design rather than an order-driven one.
-Automated market makers  (\eg Uniswap) have all the trust advantages of an on-chain orderbook, plus they are very efficient relative to an on-chain orderbook.
+Automated market makers  (\eg Uniswap) have all the trust advantages of an on-chain order book, plus they are very efficient relative to an on-chain order book.
 The trade-off is that they operate as a dealer---the DApp exchanges assets from its own inventory.
 This inventory is loaded into the DApp by an investor who will not make money on the trades themselves, but hope for long term profit through trading fees.
-By contrast, an orderbook requires no upfront inventory and does not have to charge trading fees (but can).
+By contrast, an order book requires no upfront inventory and does not have to charge trading fees (but can).
 Finally, there is a complicated difference in their price dynamics (\eg market impact of a trade, slippage between the best bid/ask and actual average execution price, \etc)---deserving of an entire research paper to precisely define.
-We leave it as an assertion that with equal liquidity, orderbooks have more favourable price dynamics for traders.
+We leave it as an assertion that with equal liquidity, order books have more favourable price dynamics for traders.
 
@@
 Some (\eg EtherDelta) were envisioned as operating fully on-chain, but performance limitations drove developers to move key components, such as the order matching system, off-chain to a centralized database.
-A landscape of DEX designs exist: many avoiding taking custodianship of assets off-chain, and virtually all (for order-driven markets) operate the orderbook itself off-chain.
+A landscape of DEX designs exist: many avoiding taking custodianship of assets off-chain, and virtually all (for order-driven markets) operate the order book itself off-chain.
 A non-custodial DEX solves the big issue of a CEX---the operator stealing the funds---however trade execution is still not provably fair.
@@
 
-\subsection{Related Work}
+\subsection{Related Works}
 
-\paragraph{Blockchain Limitations and Solution.} While an orderbook is a ledger and blockchains provide a distributed ledger, it is not straightforward to drop a continuous-time orderbook onto a blockchain.
+\paragraph{Blockchain Limitations and Solution.} While an order book is a ledger and blockchains provide a distributed ledger, it is not straightforward to drop a continuous-time order book onto a blockchain.
 An older 2014 paper~\cite{clark2014decentralizing} on the `Princeton prediction market'~\cite{Bra13} motivates our work.
-The authors observe the following limitations of on-chain continous orderbooks: block intervals are slow and not continuous, there is no support for accurate time-stamping, transactions can be dropped or reordered by miners, fast traders can react to submitted orders/cancelations when broadcast to network but not in a block and have their orders appear first (as examined in later work on front-running: \cite{eskandari2019sok,daian2019flash}).
+The authors observe the following limitations of on-chain continuous order books: block intervals are slow and not continuous, there is no support for accurate time-stamping, transactions can be dropped or reordered by miners, fast traders can react to submitted orders/cancelations when broadcast to network but not in a block and have their orders appear first (as examined in later work on front-running: \cite{eskandari2019sok,daian2019flash}).
 
 \paragraph{Call Markets.} The researchers propose using a call market instead of a continuous-time market~\cite{clark2014decentralizing}.
-Orders are collected and placed into the orderbook over a window of time (\eg 1 or more blocks), then the market is closed and the orders are processed in batch: the best bids are matched to the best asks in order.
+Orders are collected and placed into the order book over a window of time (\eg 1 or more blocks), then the market is closed and the orders are processed in batch: the best bids are matched to the best asks in order.
 If the prices overlap, the miner keeps the difference (which they could extract anyways through front-running).
@@
 Other exchanges, called crossing networks, also operate as a call market at various times throughout the trading day.\footnote{A crossing network uses a secondary market for determining the closing price.
-Many prominent crossing networks are operated internally within a brokerage for its clients, and often as a `	dark pool' with an unpublished orderbook.} Call market are studied widely in finance~\cite{Har03}.
+Many prominent crossing networks are operated internally within a brokerage for its clients, and often as a `	dark pool' with an unpublished order book.} Call market are studied widely in finance~\cite{Har03}.
 Time-sensitive traders submit orders early, especially in crossing networks that close at a randomly determined time (traders risk missing the call if they wait too long).
@@
 
-\paragraph{Other Academic Literature.} There are numerous industry projects on blockchain-based exchanges and orderbooks but most of the academic literature is on topics that are related but tangential to the mechanics of trade execution.
+\paragraph{Other Academic Literature.} There are numerous industry projects on blockchain-based exchanges and order books but most of the academic literature is on topics that are related but tangential to the mechanics of trade execution.
 Early literature considered trade execution under encryption (\ie dark markets)~\cite{TP07,YSLT10,TW12}.
@@
 
-\subsubsection{Enqueue performance.} We implemented, deployed, and tested each priority queue using Truffle and Ganache.\footnote{Github: Link removed for anonymity.} We tried a variety of tests (including testing the full call market with each varient) with consistent results in performance.
+\subsubsection{Enqueue performance.} We implemented, deployed, and tested each priority queue using Truffle and Ganache.\footnote{Github: Link removed for anonymity.} We tried a variety of tests (including testing the full call market with each variant) with consistent results in performance.
 A simple test to showcase the performance profile is shown in Figure~\ref{fig:random_insertion}.
@@
 The total gas cost for fully dequeuing the priority queue variants is outlined in Table~\ref{tab:PQUnitTests}.
-These tests are performed using the following Ethereum gas metrics: block gas limit $=$11,741,495 and 1 gas $=$ 56 gwei.\footnote{EthStats (July 2020): \url{https://ethstats.net/}} Dequeuing removes data from the contract's storage.
+These tests are performed using the following Ethereum gas metrics: block gas limit $=$11,741,495 and 1 gas $=$ 56 Gwei.\footnote{EthStats (July 2020): \url{https://ethstats.net/}} Dequeuing removes data from the contract's storage.
 Recall this results in a gas refund.
@@
 Beyond being expensive for adding new nodes (a cost that will be bared by the trader in a call market), it also leaves a large footprint on the Ethereum blockchain, especially if we leave the nodes on the blockchain in perpetuity (\ie we just update the head node of the list and leave the previous head `dangling.').
-However in a PQ, nodes are only removed from the head of the list; thus the node contracts could be `destroyed' one by one using an extra operation, \texttt{SELFDESTRUCT}, in the \texttt{dequeue()} function.
+However in a PQ, nodes are only removed from the head of the list; thus the node contracts could be `destroyed' one by one using an extra operation, \texttt{SELFDESTRUCT}, in the \texttt{Dequeue()} function.
 As shown in Table~\ref{tab:cleaning}, the refund from doing this outweighs to the cost of the extra computation: gas costs are reduced from 721K to 557K.
@@
 
-\paragraph{Front-running.} The primary motivation for using a call market, as opposed to a continuous time orderbook, is to mitigate front-running attacks~\cite{clark2014decentralizing,eskandari2019sok,daian2019flash}.
+\paragraph{Front-running.} The primary motivation for using a call market, as opposed to a continuous time order book, is to mitigate front-running attacks~\cite{clark2014decentralizing,eskandari2019sok,daian2019flash}.
 Consider a sequence of 100 orders submitted within a window of time to market A, and the same sequence randomly shuffled and submitted to market B.

### 2020-09-23 LaTeX/sections/paper.tex
finished (collateral didn't fit)

@@
 A mitigation is to issue a proof of correct execution to the DApp (\eg Loopring) but these proofs have blindspots (discussed in section~\ref{sec:rollups}).
-\cm offers key advantages in this model.
+\cm offers key advantages in this model as well.
 
@@
 We assume all trades are between ETH and an ERC20 token, all orders are pre-funded in the contract with ETH (for bids) and tokens (for asks), and once ETH or tokens are committed to an order, they cannot be withdrawn until the market closes.
-\textblue{We revisit alternatives to this design below}.
 This ensures all executed orders clear and settle (\ie no defaults on payment or delivery).
@@
 
-\cm is written in 324 lines (SLOC) of Solidity~\footnote{Github: linked removed for anonymity}, a high level programming language that is syntactically similar to Java~\cite{Ethereum41:online}.
+\cm is written in 324 lines (SLOC) of Solidity,~\footnote{Github: linked removed for anonymity} a high level programming language that is syntactically similar to Java~\cite{Ethereum41:online}.
 We tested it with the Mocha testing framework (tests included in the codebase), as deployed using Truffle on Ganache-CLI to obtain our performance metrics.
@@
 \paragraph{Front-running.} The primary motivation for using a call market, as opposed to a continuous time order book, is to mitigate front-running attacks~\cite{clark2014decentralizing,eskandari2019sok,daian2019flash}.
-Consider a sequence of 100 orders submitted within a window of time to market A, and the same sequence randomly shuffled and submitted to market B.
+Consider a sequence of 100 orders submitted within a window of time to market A, and the same sequence is randomly shuffled and submitted to market B.
 If A and B are continuous, the orders that are executed in A could be quite different from B.
 In a call market, the outcome of A and B will be exactly equivalent.
-For this reason, there is no threat from miners reordering transactions or users offering higher gas rates to have their orders executed before other orders already broadcasted.
+There is no threat from miners reordering transactions or traders offering higher gas rates to have their orders executed before other orders already broadcasted.
 
@@
 
-% = = = = = = = = = = = =Clearing Mappings = = = = = = = = = = = = =  %
+% = = = = = = = = = = = = = = = = = = = = = = = = =  %
 
@@
 Consider the following corner-case: 3 equally priced bids of 1 non-divisible token and 1 ask at the same price.
-There is not good option: (1) the bids could all be dropped (fair but not market efficient), (2) bids could be prioritized based on time as in \cm (front-running is viable, but in this corner case only), or (3) the bid could be randomly chosen (\cf~\cite{mavroudis2019libra}; blockchain `randomness' is generally deterministic and manipulatable by miners~\cite{bonneau2015random,buenz2017proofs} and counter-measures could take a few blocks to select~\cite{boneh2018verifiable}).
+There is not good option: (1) the bids could all be dropped (fair but not market efficient), (2) bids could be prioritized based on time as in \cm (front-running is viable, but in this corner case only), or (3) the bid could be randomly chosen (\cf Libra~\cite{mavroudis2019libra}); blockchain `randomness' is generally deterministic and manipulatable by miners~\cite{bonneau2015random,buenz2017proofs} and counter-measures could take a few blocks to select~\cite{boneh2018verifiable}).
 
@@
 
-We don't cancel
-Front-running is a problem
-Market is so short-lived
-Find an order to cancel in the data structure -> stronger than a PQ like binary search or a binary search tree. (Also have the trader find their own order and tell us where it is), or use a list.
+\cm does not support trade cancelations.
+We intend to open and close markets quickly (on the order of blocks), so orders are relatively short-lived.
+Support for cancelation also opens the market to new front-running issues where other traders (or miners) can displace cancelations until after the market closes (however one benefit of a call market is that beating a cancelation with a new order has no effect, assuming the cancelation is run any time before the market closes).
+Finally, cancelations have a performance impact.
+Canceled orders can be removed from the underlying data structure   or accumulated in a list that is cross-checked when closing the market.
+Removing orders requires a more verbose structure than a priority queue (\eg a binary search tree instead of a heap; or methods to traverse a linked list rather than only pulling from the head).
+While client software could help point out where the trade is in the data structure, the orderbook can change between submitting the cancelation request and running the method.
+A linked list with mapping that returns the key for each submitted order seems to be the most tenable data structure.
 
@@
 
-Uniswap - 
-MCP -> no really reliable, could in theory be used as an oracle but probably shouldn't be 
-At best, part of a distributed oracle
+Call markets are heralded for fair price discovery.
+This is why many exchanges use a call market at the end of the day to determine the closing price of an asset, which is an important price both optically (it is well-published) and operationally (many derivates settle based on the closing price).
+We purposely do not compute a `market clearing price' with \cm because miners can easily manipulate the price (\ie include a single wash trade at the price they want fixed), although they forgo profit for doing so.
+This is not merely hypothetical---Uniswap (the prominant quote-drive, on-chain exchange) prices have been manipulated to exploit other DeFi applications relying on them.
+Countermeasures to protect Uniswap price integrity could also apply to \cm: (1) taking a rolling mediant of prices over time, and (2) using it alongside other sources for the same price and forming a consensus.
+While \cm does not emit a market clearing price, it can be computed by a webapp examining the orderbook at market close.
 
-% = = = = = = = = = = = =Closing and Reopening the Market = = = = = = = = = = = = =  %
+\subsection{Scheduling events}
 
-\subsection{Closing and Reopening the Market}
+As a simple module, \cm is a one-shot market.
+However it can be extended to re-open with a clean orderbook after \texttt{closeMarket()} is run.
+Modifiers can enforce when the market operates openly (collecting orders) and when close can be run.
+In the Princeton paper~\cite{clark2014decentralizing}, the call market is envisioned to run as an alt-coin, where orders accumulate within a block and a miner closes the market as part of the logic of producing a new block (\ie within the same portion of code as computing their coinbase transaction in Bitcoin or Gas Used in Ethereum).
 
-We use one-shot market for the sake of our performance tests on different data structures. and once we have all the numbers we can think about iterated market.
+If the call market runs as a DApp on Ethereum, it seems difficult to open and close the market every block.
+Someone needs to call \texttt{closeMarket()} for every block (we return to who this is next) but the market will only work as intended if miners execute this function after every \texttt{submitBid()} and \texttt{submitAsk()} invocation.
+Since price improvements are paid to the miners, the miner is incentivized to run \texttt{closeMarket()} last to make the most profit.
+Perhaps in a world where these markets became immensely popular, miners would actually do this, but as it stands, miners do not generally search for the transaction ordering that nets them the most profit.
 
- We want the market to run on a periodic schedule => it is difficult for market participants to call the \texttt{closeMarket()} function periodically.
+A close alternative is to allow markets to open and close on different blocks.
+Specifically, the \texttt{closeMarket()} function calls \texttt{openMarket()} as a subroutine and sets two modifiers: orders are only accepted in the block immediately after the current block (\ie the block that executes \texttt{closeMarket()}) and \texttt{closeMarket()} cannot be run again until two blocks after the current block.
 
- PM paper -> close every block, close run a beginning of block. 
- Every other block (modifiers only open for block) -> schedule running close (which could reopen when it is done) -> it won't run itself -> Ethereum Alarm Clock, traders will want to trade so could trigger it.
-Why won't they ?
-Costs a lot.
-
- %At the end of the trading period, the market needs to be closed and reopened.
-However, there is no automatic process to called an Ethereum function and contracts can only run when a function is called.
+The final issue is who invokes \texttt{closeMarket()} every other block?
+There are actually two issues here: the issue of scheduling the function call and the issue of paying for it.
+For scheduling the function call, we can do one of the following: rely on market participants who are eager to trade to reopen the market, offer a bounty to reopen the market, or use an external service like Ethereum Alarm Clock.\footnote{\url{https://ethereum-alarm-clock-service.readthedocs.io/}} Next we consider the second issue of who pays to close the market.
 
@@
 
-\subsection{Who Pays the Cost for Closing and Reopening the Market?}
+\subsection{Who pays to close/reopen the market?}
 
-We think it is useful to explore the landscape of possible designs for closing the market.
+It is unlikely that a mining software will become aware of specific DApps, but miners are paid all price improvements in the market and so it is possible that running \texttt{closeMarket()} would pay for itself.
+However we consider two other (more realistic) scenarios.
+One solution requires a modified closing function, \texttt{closeMarket(n)}, that only processes $n$ orders at a time (until the order book is empty).
+Once the time window for submitting orders is past, a new market is created (without settling the previous market).
+Every orders to the new market is also requires to run, say, \texttt{closeMarket(10)} on the older market, thus progressively closing the previous market while accepting orders to the new market.
+This solution pattern has two issues: first, amortizing the cost of closing the market amongst the early traders of the new market is an added incentive to not submit orders early to the market; the second related issue is if not enough traders submit orders in the new market, the old market never closes (resulting in a backlog of old markets waiting to close).
 
-%= = = = = = Miners Close the Market = = = = = = =%
-\paragraph{Miners.} The difference between the best bid and ask prices is called the \textit{bid-ask spread}.
-In our design, when the trade occurs between the the highest bid (the highest amount a buyer is willing to pay for an asset) and lowest ask (the lowest amount a seller is willing to accept for an asset) orders, the bid-ask spread is paid to the miner.
-There are possibilities that (i) no trade occurs or (ii) the bid-ask spread is zero (\ie the best bid and best ask prices are identical).
-So there is enough economic incentive for the the miner to execute the \texttt{closeMarket()} function and get refunded as the refund amount could be potentially higher than the bid-ask spread.
-% Miners will compete for it
-
-% = = = = = = = = = =Processing Orders in Groups= = = = = = = = = = = = = = = %
-
-\paragraph{Next Traders.} Another solution pattern is to process certain number of bid and ask orders upon every execution of the \texttt{closeMarket()} function rather than treating them as one substantial transaction.
-A market participant $P_i$ would process $n$ orders from the previous market (\texttt{closeMarket(n)}) when sending new orders to the current market.
-This process continues until all the orders in the previous markets are processed.
-% incentive?
-=> contribution to the community!?
-% Chop it smaller, pushes it around -> could have orders in next market pay to close previous market -> not enough orders come in -> fall back to traditional close -> progressive close
-
-%= = = = = =  = =  =  Users close and get refunded with the contract funds (collected as fees during order submissions) =  = = = = = = = = =%
-
-\paragraph{Contract Pays.} An alternative solution is to design the market such that the last person to submit an order calls the \texttt{closeMarket()}function, but in contrast to a normal transaction (where the person initiating the transaction must pay the fee), here the CallMarket contract pays the cost for closing the market and matching the orders respectively.
-To enforce this design we can use Solidity function modifiers; every time a new order is submitted, a function modifier checks whether (i) the auction period has to end and/or (ii) the maximum number of total orders has reached.
-If any of these two conditions are met, \texttt{closeMarket()} will be called.
-Again, market participants are charged with certain amounts of fees every time they submit an order, these fees are accumulated in the CallMarket.
-Once the  \texttt{closeMarket()} is successfully executed and orders are matched, the contract transfers its funds to that person.
-Note that here the person must still have enough gas to cover the execution of the transaction as the funds will be only transferred after the transaction is fully executed.
-However, market participants are incentivized to do so as they may receive more ethers than they have spent.
-
-%= = = = = =  = =  =  Meta txs =  = = = = = = = = =%
-
-\paragraph{A Relayer.} Meta transactions enable users to execute Ethereum functions without paying the gas.
-Rather than spending gas, users sign their intended action using their private keys and broadcast it to the network with no cost.
-A third party process (\textit{a relayer}) then crafts the actual transaction on user's behalf, sends the transaction to the Ethereum blockchain, and charges the base contract with the associated fees.
-The required gas to pay for the \texttt{matchOrders()} function could be collected as fees.
-So market participants are charged with certain amounts of fees every time they submit an order, these fees are accumulated in the CallMarket contract and will be used to pay for executing the \texttt{closeMarket()}function.
+The second solution is to levy a carefully computed fee against the traders for every new order they submit.
+The fees are accumulated by the DApp to use as a bounty.
+When the time window for the open market elapses, the user who calls \texttt{closeMarket()} receives the bounty.
+This is a better solution, although not perfect: \texttt{closeMarket()} cost does not follow a tight linear increase with the number of orders, and gas prices vary over time which could render the bounty insufficient for offsetting the \texttt{closeMarket()} cost.
+However an interest third party (such as the token issuer for a given market) might bailout the market when it halts on \texttt{closeMarket()} to facilitate further trading.
+If the contract can pay for its own functions, an interested party can also arrange for a commercial service (\eg any.sender\footnote{\url{https://github.com/PISAresearch/docs.any.sender}}) to relay the \texttt{closeMarket()} function call on Ethereum (an approach called \textit{meta-transactions}).
 
@@
 
-\subsection{Off-Chain Closing}
+\subsection{Off-chain closing}
 \label{sec:rollups}
 
-Someone does it off-chain and (a) Ethereum checks that it was done right with a proof (SNARK)~\cite{}, (b) Ethereum checks that it was done right with an attestation from a trusted execution environment (\eg Intel SGX or Intel TXT) (SGX is broken but TXT is still fine)~\cite{cheng2019ekiden}, and (c) we assume it was done right but Ethereum will resolve a dispute about where specifically the computation went wrong.~\cite{kalodner2018arbitrum}.
-Why not use SGX for everything?
+We have two main motivations for designing an \textit{on-chain} order book: (1) the trust model is superior to partially/fully centralized solutions, and (2) \cm can be deployed without any delay or other arrangements.
+We have relaxed (2) already by considering services like Ethereum Alarm Clock and any.sender to facilitate easy market closings.
+In this section, we present a variant that only provides (1) (however one that can be deployed without any other market stakeholders).
 
-%Arbitrum numbers: 
-% Heap w/ dynamic array: matching 38 pairs, cost: 38,863 (this is the cost of posting transactions as calldata on the L1 chain, as well as the overhead associated with each batch of transactions, and the L1 cost of settling transactions in the Arbitrum protocol)
-% Heap w/ dynamic array: matching 1000 pairs, cost: 38,851
-% Heap w/ dynamic array: 2000 average submission: cost (averaged): 39,169 (we have the plot too, if needed)
+A function can be computed off-chain and the new state of the DApp, called a \textit{rollup}, is written back to the blockchain, accompanied by either (1) a proof that the function was executed correctly, or (2) a dispute resolution process that can resolve, on-chain, functions that are not executed correctly (\eg Arbitrum~\cite{kalodner2018arbitrum}).
+In the case of (1), validating the proof must be cheaper than running the function itself.
+There are two main approaches to (1): the first is to use cryptographic proof techniques (\eg SNARKS~\cite{BCGTV13,GGPR13} and variants~\cite{BBHR19}), and the second is to execute the function in a trusted execution environment (TEE; \eg Intel SGX) and validate the TEE's quote on-chain (\eg Ekiden~\cite{cheng2019ekiden}).\footnote{The TEE-based approach is mired by recent attacks on SGX~\cite{SGX1,SGX2,SGX3,SGX4}, however these attacks do not necessarily apply to the specifics of how SGX is used here, and safer TEE technologies like Intel TXT (\cf~\cite{ZBC+19}) can be substituted.}
 
-Costs in arbitrum include:
+We implement a variant of \cm using rollups on Arbitrum.\footnote{\url{https://offchainlabs.com} for more current details than the 2018 \textit{USENIX Security} paper~\cite{kalodner2018arbitrum}.} In this model, the token issuer (or other interested party) will run a dedicated server to watch Ethereum for function invocations submitted and sequenced on-chain, perform the function call off-chain, and write the resultant state on-chain.
+Anyone capable of running EVM code can verify the result.
+If it is incorrect, a dispute can be filed (with the correct state) and an on-chain correction will be made.
+With or without disputes, participants that validate the function calls for themselves can proceed knowing that the correct state will eventually be finalized.
 
---- Level 1 (Ethereum here) gas costs: This is the cost of posting transactions as calldata on the L1 chain, as well as the overhead associated with each batch of transactions, and the L1 cost of settling transactions in the Arbitrum protocol.
+In our \cm variant with rollups, the token issuer is does all the computation (both enqueuing and dequeuing).
+Thus we switch the priority queue to use a heap with dynamic array, which balances the expense of both operations (instead of optimizing for dequeuing in \texttt{closeMarket()}).
+Recall that on-chain, such a priory queue can only match 38 pairs at a cost of 5,372,679 gas.
+With roll-ups, 38 pairs cost 38,863 gas.
+As the pairs increase, the cost is essentially constant (\eg 1000 pairs cost 38,851 as opposed to 457,326,935 on-chain).
+Submitting an order costs 39,169 gas on average as opposed to 207,932 on-chain.
 
----Validator’s staking costs: In normal operation, one validator will need to be staked.
-(putting their money behind the claim that this state is correct), if that state eventually gets confirmed they get their stake back, if not they'll lose it (half of it burns half of it goes back to the honest validator)
+Our \cm variant is not the first rollup-based order book.
+Loopring 3.0\footnote{\url{https://loopring.org}} offers a continuous time order book.
+The primary difference is that orders in Loopring 3.0 are submitted off-chain to the operator directly, whereas our variant requires on-chain submission.
+While on-chain submission is hampered by Ethereum's block limits, the threat model of reordering transactions is well-understood and our call market design mitigates most front-running attacks.
+In Loopring 3.0, the rollup proof does not ensure that the exchange did not reorder transactions, which is particularly problematic in a continuous time order book.
+In short, we provide better protection against a malicious exchange while Loopring 3.0 provides even better performance.
 
----Validator computation and storage: Every validator must do computation to track the chain’s processing of transactions, and must maintain storage to keep track of the contracts’ EVM storage.
-
-More about Arbitrum:
-
->> performance: Arbitrum software currently supports 453 transactions-per-second for basic transactions . more optimization on the way
-
->> low cost: The cost of running Arbitrum Rollup is quite low compared to level 1 Ethereum and other scaling solutions such as those based on zero-knowledge proofs.
-Layer 2 (arbitrum roll up chain) fees are low, fixed, and predictable and should not be overly burdensome.
-Nobody needs to use special equipment or high-end machines.
-Arbitrum requires validators, which is a permissionless role that can be run on any reasonable on-line machine.
-Although anybody can act as a validator, in order to protect against a “tragedy of the commons” and make sure reputable validators are participating, we support a notion of “invited validators” that are compensated for their costs.
-
->> Fast finality: txs complete with the same finality time as Ethereum L1
-
->> Censorship Resistant: validators are not in a position to censor or front-run txs, when a tx arrives to the roll up chain, it is ordered and timestamped based on the Ethereum block number it is included in.
-So validators cannot reorder (MORE: a user would directly send txs to her contract on the Ethereum chain and then the call will be sent to the Arbitrum inbox contract which is responsible for incoming txs.
-All the incoming calls to this contract are ordered and time-stamped using the Ethereum block number.
-So front-running may/or may not still happen on the Ethereum chain, but validators are not in position to front-run, they will execute the txs in the order that they were put in the inbox contract.
-The team emphasizes on the fact that the main reason for having a separate contract on the Arbitrum chain to receive the incoming calls is to prevent censorship and front-running.)
-
-% = = = = = = = = = = = =Transferring the Collateral back to the traders = = = = = = = = = = = = =  %
-\subsection{Collateralization}
-
-Options for non-collateralized markets
-ERC20 to ERC20 -> extra transaction
+%% = = = = = = = = = = = =Transferring the Collateral back to the traders = = = = = = = = = = = = =  %
+%\subsection{Collateralization}
+%
+%Options for non-collateralized markets
+%ERC20 to ERC20 -> extra transaction
+%
 
@@
 For an automated market maker, you will have to lock up a large amount of ETH into the DApp, along with your tokens.
-For rollups, you will have to list your token, host your own servers, and/or enlist arbitrators.
+For rollups, you will have to host your own servers or list it with an exchange.
 By contrast to all of these, with \cm you just deploy the code alongside your token and trading is immediately supported.
 Even if \cm is a fallback solution today, we believe it is helpful for every token to be accompanied by on-chain trade execution.
-And with future improvements to blockchain scalability, it could become the defacto trading method.
+With future improvements to blockchain scalability, it could become the defacto trading method.
 

### 2020-09-23 LaTeX/sections/abstract.tex
finished (collateral didn't fit)
appendix edits

--- 2020-09-14 LaTeX/sections/abstract.tex
@@
 Fully on-chain solutions have a superior threat model and were experimented with in the early days of Ethereum, but they have been largely abandoned for performance reasons.
-As blockchain performance continues to improve (both in research and in practice) and on-chain dealer-based exchanges like Uniswap (an alternative to order-based exchanges) rise in popularity, it seems to be an ideal time to revisit the idea of a fully on-chain order-driven exchange and benchmark what is possible performance-wise.
+As block\-chain performance continues to improve (both in research and in practice) and on-chain dealer-based exchanges like Uniswap (an alternative to order-based exchanges) rise in popularity, it seems to be an ideal time to revisit the idea of a fully on-chain order-driven exchange and benchmark what is possible performance-wise.
 We design and optimize an Ethereum-based call market exchange, \cm, and conduct a variety of experiments to show the current benchmark is around one hundred trade executions per block.
-We also explore numerous extensions for further improvements.
+We also explore numerous extensions for further improvements, including a variant using off-chain execution (`rollups').
 \end{abstract}

### 2020-09-23 LaTeX/sections/paper.tex
appendix edits

@@
 
-\subsection{Cost/Benefit of Cleaning up After Yourself}
+\subsection{Cost/Benefit of cleaning up after yourself}
 \label{sec:gasrefund}
@@
 One consequence of a linked list is that a new contract is created for every node in the list.
-Beyond being expensive for adding new nodes (a cost that will be bared by the trader in a call market), it also leaves a large footprint on the Ethereum blockchain, especially if we leave the nodes on the blockchain in perpetuity (\ie we just update the head node of the list and leave the previous head `dangling.').
+Beyond being expensive for adding new nodes (a cost that will be bared by the trader in a call market), it also leaves a large footprint in the active Ethereum state, especially if we leave the nodes on the blockchain in perpetuity (\ie we just update the head node of the list and leave the previous head `dangling.').
 However in a PQ, nodes are only removed from the head of the list; thus the node contracts could be `destroyed' one by one using an extra operation, \texttt{SELFDESTRUCT}, in the \texttt{Dequeue()} function.
@@
 For an automated market maker, you will have to lock up a large amount of ETH into the DApp, along with your tokens.
-For rollups, you will have to host your own servers or list it with an exchange.
+For rollups, you will have to host your own servers.
 By contrast to all of these, with \cm you just deploy the code alongside your token and trading is immediately supported.

### 2020-09-23 LaTeX/sections/paper.tex
edits on the last part

--- 2020-09-23 LaTeX/sections/paper.tex
@@
 
-\section{Design alternatives and extensions}
+\section{Design Alternatives and Extensions}
 
@@
 Traders submit multiple orders to increase volume.
-To extend orders with a volume field, it must first be determined if the token are non-divisible or divisible (and to what precision).
+To extend orders with a volume field, it must first be determined if the token is non-divisible or divisible (and to what precision).
 In this case, \texttt{closeMarket()} needs to look at multiple bids to fulfill a single ask (and vice-versa) and declare its trading rules on partial fills.
-We also simplify the market rules around ties on price: we execute them FIFO (breaking front-running resistance for ties on prices).
+We also simplify the market rules around ties on price: we execute them in a FIFO manner (breaking front-running resistance for ties on prices).
 A common trading rule (that does resist front-running) is to fill ties in proportion to their volume (\ie \textit{pro rata} allocation)\footnote{If Alice and Bob bid the same price for 100 tokens and 20 tokens respectively, and there are only 60 tokens left in marketable asks, Alice receives 50 and Bob 10.} however this approach is also contingent on the divisibility of tokens.
 Consider the following corner-case: 3 equally priced bids of 1 non-divisible token and 1 ask at the same price.
-There is not good option: (1) the bids could all be dropped (fair but not market efficient), (2) bids could be prioritized based on time as in \cm (front-running is viable, but in this corner case only), or (3) the bid could be randomly chosen (\cf Libra~\cite{mavroudis2019libra}); blockchain `randomness' is generally deterministic and manipulatable by miners~\cite{bonneau2015random,buenz2017proofs} and counter-measures could take a few blocks to select~\cite{boneh2018verifiable}).
+There is no good option: (1) the bids could all be dropped (fair but not market efficient), (2) bids could be prioritized based on time as in \cm (front-running is viable, but in this corner case only), or (3) the bid could be randomly chosen (\cf Libra~\cite{mavroudis2019libra}); blockchain `randomness' is generally deterministic and manipulatable by miners~\cite{bonneau2015random,buenz2017proofs} and counter-measures could take a few blocks to select~\cite{boneh2018verifiable}).
 
-\subsection{Cancelations}
+\subsection{Cancellations}
 
-\cm does not support trade cancelations.
+\cm does not support order cancelations.
 We intend to open and close markets quickly (on the order of blocks), so orders are relatively short-lived.
-Support for cancelation also opens the market to new front-running issues where other traders (or miners) can displace cancelations until after the market closes (however one benefit of a call market is that beating a cancelation with a new order has no effect, assuming the cancelation is run any time before the market closes).
-Finally, cancelations have a performance impact.
-Canceled orders can be removed from the underlying data structure   or accumulated in a list that is cross-checked when closing the market.
+Support for cancellation also opens the market to new front-running issues where other traders (or miners) can displace cancellations until after the market closes (however one benefit of a call market is that beating a cancellation with a new order has no effect, assuming the cancellation is run any time before the market closes).
+Finally, cancellations have a performance impact.
+Cancelled orders can be removed from the underlying data structure   or accumulated in a list that is cross-checked when closing the market.
 Removing orders requires a more verbose structure than a priority queue (\eg a binary search tree instead of a heap; or methods to traverse a linked list rather than only pulling from the head).
-While client software could help point out where the trade is in the data structure, the orderbook can change between submitting the cancelation request and running the method.
+While client software could help point out where the order is in the data structure, the order book can change between submitting the cancellation request and running the method.
 A linked list with mapping that returns the key for each submitted order seems to be the most tenable data structure.
 
-\subsection{Market clearing price}
+\subsection{Market Clearing Price}
 
@@
 We purposely do not compute a `market clearing price' with \cm because miners can easily manipulate the price (\ie include a single wash trade at the price they want fixed), although they forgo profit for doing so.
-This is not merely hypothetical---Uniswap (the prominant quote-drive, on-chain exchange) prices have been manipulated to exploit other DeFi applications relying on them.
+This is not merely hypothetical---Uniswap (the prominent quote-drive, on-chain exchange) prices have been manipulated to exploit other DeFi applications relying on them.
 Countermeasures to protect Uniswap price integrity could also apply to \cm: (1) taking a rolling mediant of prices over time, and (2) using it alongside other sources for the same price and forming a consensus.
-While \cm does not emit a market clearing price, it can be computed by a webapp examining the orderbook at market close.
+While \cm does not emit a market clearing price, it can be computed by a web application examining the order book at market close.
 
-\subsection{Scheduling events}
+\subsection{Scheduling Events}
 
 As a simple module, \cm is a one-shot market.
-However it can be extended to re-open with a clean orderbook after \texttt{closeMarket()} is run.
+However it can be extended to re-open with a clean order book after \texttt{closeMarket()} is run.
 Modifiers can enforce when the market operates openly (collecting orders) and when close can be run.
-In the Princeton paper~\cite{clark2014decentralizing}, the call market is envisioned to run as an alt-coin, where orders accumulate within a block and a miner closes the market as part of the logic of producing a new block (\ie within the same portion of code as computing their coinbase transaction in Bitcoin or Gas Used in Ethereum).
+In the Princeton paper~\cite{clark2014decentralizing}, the call market is envisioned to run as an alt-coin, where orders accumulate within a block and a miner closes the market as part of the logic of producing a new block (\ie within the same portion of code as computing their coinbase transaction in Bitcoin or gasUsed in Ethereum).
 
@@
 
-\subsection{Who pays to close/reopen the market?}
+\subsection{Who Pays to Close/Reopen the Market?}
 
@@
 Once the time window for submitting orders is past, a new market is created (without settling the previous market).
-Every orders to the new market is also requires to run, say, \texttt{closeMarket(10)} on the older market, thus progressively closing the previous market while accepting orders to the new market.
+Every order submission on the new market also requires to run, say, \texttt{closeMarket(10)} on the older market, thus progressively closing the previous market while accepting orders to the new market.
 This solution pattern has two issues: first, amortizing the cost of closing the market amongst the early traders of the new market is an added incentive to not submit orders early to the market; the second related issue is if not enough traders submit orders in the new market, the old market never closes (resulting in a backlog of old markets waiting to close).
@@
 This is a better solution, although not perfect: \texttt{closeMarket()} cost does not follow a tight linear increase with the number of orders, and gas prices vary over time which could render the bounty insufficient for offsetting the \texttt{closeMarket()} cost.
-However an interest third party (such as the token issuer for a given market) might bailout the market when it halts on \texttt{closeMarket()} to facilitate further trading.
+However an interested third party (such as the token issuer for a given market) might bailout the market when it halts on \texttt{closeMarket()} to facilitate further trading.
 If the contract can pay for its own functions, an interested party can also arrange for a commercial service (\eg any.sender\footnote{\url{https://github.com/PISAresearch/docs.any.sender}}) to relay the \texttt{closeMarket()} function call on Ethereum (an approach called \textit{meta-transactions}).
@@
 
-\subsection{Off-chain closing}
+\subsection{Off-chain Closing}
 \label{sec:rollups}
@@
 
-In our \cm variant with rollups, the token issuer is does all the computation (both enqueuing and dequeuing).
+In our \cm variant with rollups, the token issuer does all the computation (both enqueuing and dequeuing).
 Thus we switch the priority queue to use a heap with dynamic array, which balances the expense of both operations (instead of optimizing for dequeuing in \texttt{closeMarket()}).
-Recall that on-chain, such a priory queue can only match 38 pairs at a cost of 5,372,679 gas.
+Recall that on-chain, such a priority queue can only match 38 pairs at a cost of 5,372,679 gas.
 With roll-ups, 38 pairs cost 38,863 gas.

### 2020-09-23 LaTeX/sections/appendix.tex

--- 2020-09-17 LaTeX/sections/appendix.tex
@@
 
-% Extended discussion on cleaning up data structures in Ethereum
+\section{Extended discussion on cleaning up data structures}
 
-\section{Ethereum's Gas Model}
+For space considerations, we kept the discussion in Section~\ref{sec:gasrefund} brief but the subject could use more explanation.
+First, we discuss the Ethereum's gas model--- (i) what are different gas parameters one needs to take into account when sending a transaction on the Ethereum blockchain, (ii) what is the gas refund, and (iii) and how it is calculated.
+Next, we discuss one challenge in \cm, \textit{clearing mappings}, that turns out to be more difficult than we initially expected.
 
-Gas is the Ethereum's pseudo-currency and a key variable for the execution of smart contracts.
-DApps written in high-level programming languages are compiled and translated into a compact representation (called ‘bytecode’) to be further executed on the Ethereum virtual machine or EVM.
-Each of these opcodes has a fixed amount of gas assigned and is a measure of computational effort.
-Separating ETH from gas prevents transactions cost from being too expensive as they are less impacted by ETH price fluctuations.
-Gas unit does not a have a monetary value and as mentioned, it only  measures the computational work undertaken by miners.
-To pay miners, Ethereum introduces a \texttt{gas price} --- small denomination of ether called \textbf{Gwei} attached to each gas unit.
-Essentially, gas price indicates how much users are willing to pay per unit of gas, clearly the higher gas price leads to the faster execution of a transaction.
-Miners also need to know the total amount of computational work a user is requesting, called the \texttt{gas limit}.
-\texttt{Gas limit} is a parameter that limits the amount of gas users would spend in a transaction.
-It protects users from spending unlimited ETH on their transactions and must be set carefully.
-If the \texttt{gas limit} is too low, the transaction will exceed the limit, all operations will be reverted while the user must pay for the computational work performed by the miner.
-By default the gas limit for an Ethereum transaction is 21,000 gas.
-An Ethereum block also has a \texttt{block gas limit} field which is set by the Ethereum miners and indicates the maximum amount of gas all the transactions in that block are allowed to consume, the Ethereum \texttt{block gas limit} is currently 11,741,495.
-\footnote{July 2020: https://ethstats.net/}
+\subsection{Ethereum's gas model}
 
-\subsection*{Gas Refunds.}There are two particular EVM operations with negative gas --- certain amount of gas is refunded to the sender at the end of the transaction. These operation include:
+DApps written in high-level programming languages are compiled and translated into a compact representation (called ‘bytecode’) to be further executed on the Ethereum virtual machine (EVM).
+When a transaction is executed, each opcode in the execution path accrues a fixed, pre-specified amount of gas.
+The function caller will pledge to pay a certain amount of ETH (typically quoted in units of \textbf{Gwei}, where \textit{wei} is the smallest transactional unit of ETH) per gas, and miners are free to chose to execute it or ignore it.
+The function caller is charged for exactly the amount the transaction costs and they cap the maximum they are willing to be charged (\textit{gas limit})---if the cap is too low to complete the execution, the miner keeps the gwei and reverts the state of the DApp (as if the function never ran).
 
-\paragraph{\texttt{SELFDESTRUCT}.}This operation destroys and deletes the originating contract and refunds its balance (if any) to a designated receiver address.
-Note that the Ethereum storage is implemented in the form of a has map and EVM is not statistically aware of which storage slots are held by the contract.
-Because of this the \texttt{SELFDESTRUCT} operation does not remove the initial byte code of the contract from the chain, but it frees up the state storage and has a refund of 24,000 gas.
+In Ethereum, transactions are bundled into blocks.
+A miner can include as many transactions (typically preferring transactions that bid the highest for gas) that can fit under a pre-specified \texttt{block gas limit}, which is algorithmically adjusted for every block.
+As of the time of writting, the limit is around 11M gas.
 
-\paragraph{\texttt{SSTORE}.} This operation clears the Ethereum storage and has15,000 gas refunds.
+\subsubsection{Gas refunds.} In order to reconstruct the current state of Ethereum's EVM, a node must obtain a copy of every variable change since the genesis block (or a more recent `checkpoint' that is universally agreed to).
+For this reason, stored variables persist for a long time and, at first glance, it seems pointless to free up variable storage (and unclear what `free up' even means).
+Once the current state of the EVM is established by a node, it can forget about every historical variable changes and only concern itself with the variables that have non-zero value (as a byte-string for non-integers) in the current state (uninitialized variables in Ethereum have the value zero by default).
+Therefore, freeing up variables will reduce the amount of state Ethereum nodes need to maintain going forward.
 
-Note that in order to urge miners to process smart contracts with refunds, the accumulated gas refund can never exceed half the gas used up during computation~\cite{wood2014ethereum}.
-So at the end of a successful transaction, the amount of gas in the refund counter (capped at half the net gas used) is returned to the caller.
-At the time of this writing, Ethereum transaction receipts only account for the \texttt{gasUsed}, which is the total amount of gas units spent during a transaction, and we are not able to obtain the value of the EVM's refund counter from inside the EVM~\cite{signer2018gas}.
-So in order to account for refunds, we decide to calculate them manually; first we figure out exactly how much storage is being cleared or how many smart contracts are being destroyed, then we multiply these numbers by 24,000 and 15,000 respectively.
+For this reason, some EVM operations cost a negative amount of gas.
+That is, the gas is refunded to the sender at the end of the transaction, however (1) the refund is capped at 50\% of the total gas cost of the transaction, and (2) the block gas limit applies to the pre-refunded amount (\ie a transaction receiving a full refund can cost up to 5.5M gas with a 11M limit).
+Negative gas operations include:
+
+\begin{itemize}
+
+\item \texttt{SELFDESTRUCT}.
+This operation destroys the contract that calls it and refunds its balance (if any) to a designated receiver address.
+\texttt{SELFDESTRUCT} operation does not remove the initial byte code of the contract from the chain.
+It always refunds 24,000 gas.
+For example, if a contract A stores a single non-zero integer and contract B stores 100 non-zero integers, the \texttt{SELFDESTRUCT} refund for both is the same (24,000 gas).
+
+\item \texttt{SSTORE}.
+This operation loads a storage slot with a value.
+Using \texttt{SSTORE} to load a zero into a storage slot means the nodes can start ignoring it (recall that all variables, even if uninitialized, have zero by default).
+Doing this refunds 15,000 gas per slot.
+
+\end{itemize}
+
+At the time of this writing, Ethereum transaction receipts only account for the \texttt{gasUsed}, which is the total amount of gas units spent during a transaction, and users are not able to obtain the value of the EVM's refund counter from inside the EVM~\cite{signer2018gas}.
+So in order to account for refunds in Tables~\ref{tab:PQUnitTests}, we calculate them manually.
+First we need to figure out exactly how much storage is being cleared or how many smart contracts are being destroyed, then we multiply these numbers by 24,000 and 15,000 respectively.
 
@@
 
-To maintain the collateral balance of each market participant, we use two Solidity type one-to-one mappings that map Ethereum addresses to 256 bits unsigned integers; \texttt{TotalBalance} and \texttt{UnavailableBalance}.
-Once market closes and orders are matched, the \texttt{UnavailableBalance} needs to be cleared.
-However, since it is not possible to delete the entire mapping without knowing the keys~\footnote{https://solidity.readthedocs.io/en/v0.5.12/security-considerations.html}, clearing the \texttt{UnavailableBalance} mapping remains a challenging issue to solve.
-Here we provide a landscape of solutions for that.
-%only individual keys and what they map to can be deleted.
+Now let us put this theory into practice.
+In \cm, traders preload their account with ERC-20 tokens and/or ETH.
+\cm tracks what they are owed using a mapping called \texttt{totalBalance} and allow traders to withdraw their tokens at any time.
+However if a trader submits an order (\ie ask for their tokens), the tokens are committed and no available for withdrawal until the market closes (after which, the tokens are either transferred to the buyer or, if the trade is not executed, returned to the trader).
+Committed tokens are also tracked in a mapping called \texttt{unavailableBalance}.
+A buyer can request a token withdrawal up to their total balance subtracted by their unavailable balance.
 
-\begin{itemize}
+As the DApp runs \texttt{closeMarket()}, it starts matching the best bids and to the best asks.
+As orders execute, \texttt{totalBalance} and \texttt{unavailableBalance} are updated.
+At a certain point, the bids and asks will stop matching in price.
+At this point, every order left in the order book cannot execute (because the priority queue sorts orders by price, and so orders deeper in the queue have worst prices than the order at the head of the queue).
+Therefore all remaining entries in \texttt{unavailableBalance} can be cleared.
 
-%---------+++++++++++++++++++-----------------
-\item \textbf{Creating a New Mapping Every Time the Market Opens.} Instead of clearing the \texttt{UnavailableBalance} of traders at the end of a matching process, we could create a new mapping every time the market opens.
-Note that in this scheme traders can claim their funds back (using the \texttt{ClaimEther()} and/or \texttt{ClaimToken} methods) only when the market is closed (\ie the market is in the \texttt{Closed} state).
+In Solidity, it is not possible to delete an entire mapping without individually zero-ing out each entry key-by-key.
+At the same time, it is wasteful to let an entire mapping sit in the EVM when it will never be referenced again.
+The following are some options for addressing this conflict.
 
-%---------+++++++++++++++++++-----------------
-\item \textbf{Creating Custom Keys for the Mapping.} We can create custom keys for the mapping by defining a counter as a global variable inside the call market smart contract and increment it only once at the end of the matching process.
-So instead of clearing the mapping, we only use another portion of it every time the market opens.
+\begin{enumerate}
 
-%---------+++++++++++++++++++-----------------
-\item \textbf{Storing the Mapping in a Data-Contract.} Another design proposal is to create a new smart contract every time the market opens, this data contract only stores the \texttt{UnavailableBalance} mapping and will be destroyed (using the \texttt{SELFDESTRUCT} operation) at the end of the matching process.
+\item \textbf{Manually clearing the mapping.} Since mappings cannot be iterated, a common design pattern used by DApp developers is to store keys in an array and iterate over the array to zero out each mapping and array entry.
+Clearing a mapping this way costs substantially more to clear than what is refunded (15,000 for each element).
 
-%---------+++++++++++++++++++-----------------
-\item \textbf{Storing the Mapping keys in an additional Array.} Another common pattern is to create an additional array on top of the mapping and iterate over that.
-This array (\eg address[]) stores the traders' addresses and enables us to iterate over the mapping and delete individual keys and what they map to at the end of the matching process.
-Note that this is a gas-costly design pattern as we would need to maintain a secondary data structure.
+\item \textbf{Store the mapping in a separate DApp.} We could wrap the mapping inside its own DApp and when we are done with the mapping, we can run \texttt{SELFDESTRUCT} on the contract.
+This refunds us 24,000 gas which is less than the cost of deploying the extra contract.
+Additionally, every call to the mapping is more expensive because (1) it is an external function call, and (2) function calls  to be evaluated to ensure they only come from the market contract (if a mapping is a local variable, you get private access for free).
 
-%---------+++++++++++++++++++-----------------
-\end{itemize}
+\item \textbf{Leave and ignore the mapping.} The final option is to not clear the mapping and just create a new one (or create a new prefix for all mapping keys to reflect the new version of the mapping).
+Unfortunately, this is the most economical option for DApp developers even if it is the worst option for Ethereum nodes.
 
-%gas price: how much you pay per gas unit
-%gas limit: how much work you are requesting 
-%gas cost (Ether) = gasPrice * gasCost(gas)
-%gas limit: is a parameter that limits the amount of gas you spend in a transaction (how to estimate? using estimateGas)
-%gas price how to estimate: using ethgassation 
-%by defaluth the gas minimum gas limit for ethereum txs is 21000 gas
-%a block also has a gas limit field, it defines a maximum amount of gas all txs in th eblock combined are allowed to consume.
-this block gas limit determines the maximum number of transactions within the block.
-this block gas limt is not fixed and set by miners
-%
-%ers to process smart contracts with refunds, the accumulated gas refund can never exceed half the gas used up during computation~\cite{wood2014ethereum}.
-So at the end of a successful transaction, the amount of gas in the refund counter (capped at half the net gas used) is returned to the caller.
+\end{enumerate}
 
-% \input{tables/eval.tex}
-
-%\section{Rollups}
-%
-%\subsection{Using Rollups.} Rollup is a scaling method that moves the storage and computation of the smart contracts off-chain while maintaining the transaction data on the main chain as call-data.
-In this technique, any Ethereum user can act as a validator; they can execute the \texttt{CloseMarket()}function and only post the new state of the contract (the updated balance of traders) in the form of \textit{assertions} to the main chain.
-Rollups improve scalability, provide faster and cheaper execution of the contracts, and eliminate the gas limit as the contract is no longer executed on-chain.
-%
-%In the followings we briefly discuss different rollup proposals and techniques. Each approach uses a different method to ensure correction of assertions:
-%
-%\paragraph{Non-interactive Rollups.} In this rollup technique, assertions are posted together with a validity proof that would be later used by validators to check if the \texttt{CloseMarket()} function has been executed correctly.
-ZK-Rollup scheme is one of the solutions that uses ZK-SNARKs to prove the validity of the assertions in zero-knowledge.
-ZK proofs are quick and cheap to verify but they are expensive and time consuming to generate.
-These proofs could be generated (i) for free or (ii) the CallMarket contract could collect proportional fees for every trade that is successfully executed.
-%
-%\paragraph{Optimistic Rollups.} In this scheme, assertions are assumed to be valid if there is no dispute posted about them with a certain window of time (a.k.a.
-"the challenge period').
-Here, dispute resolution is a gas-costly method as the CallMarket contract would have to emulate the transaction on-chain to ensure the correctness the assertion.
-This scheme introduces a tradeoff between privacy and performance as all the assertions are publicly available and accessible.
-However, here the new state only reflects the updated balances of traders and no secret is involved.
-%
-%\paragraph{{Multi-round Interactive Rollups.}} In this design paradigm, \textit{pending assertions} are posted on-chain and they are open to dispute.
-Once the challenge period is over and no challenge is submitted, the assertion is confirmed and the CallMarket contract transitions to the new state (\ie updates traders' balances).
-This scheme takes the overhead for the CallMarket contract to execute the \texttt{Close()} on-chain by using rounds to the dispute resolutions.
-The two parties (asserter and challenger) must run an interactive protocol and the CallMarket smart contract would have to act as a referee and decides which party's claim is true.
-Arbitrum is an example of multi-round interactive rollups that uses an efficient challenge-based protocol to penalize the dishonest parties~\cite{kalodner2018arbitrum}.
-%
-%%= = = = = =  = =  =  SGX=  = = = = = = = = =%
-%
-%\paragraph{{Using Trusted Execution Environments.}} Another way of achieving execution of the \texttt{CloseMarket()} function is incorporating the Ethereum blockchain into the Trusted Execution Environments (TEEs) and decoupling the contract execution from consensus mechanism.
-TEEs enable secure execution of applications in an isolated processing environment called the \textit{enclave}.
-Here, the enclave could execute the \texttt{CloseMarket()} function off-chain in TEEs and publish an on-chain attestation Quote to the CallMarket contract.
-The contract then verifies the correctness of the Quote and if validated correctly, it transitions to the new state.
-Ekiden is an example that uses Intel SGX to solve the scalability and confidentiality issues with the smart contract execution~\cite{cheng2019ekiden}.
-A drawback of this scheme is in order to achieve confidentiality-preserving smart contracts we have to trust a trusted party in the form of the hardware manufacturer (\eg Intel).
+Clearing storage is important for reducing EVM bloat.
+The Ethereum refund model should be considered further by Ethereum developers to better incentivize developers to be less wasteful in using storage.

### 2020-09-23 LaTeX/sections/appendix.tex
appendix

@@
 
-\section{Extended discussion on cleaning up data structures}
+\section{Clearing storage (extended discussion)}
 
@@
 The Ethereum refund model should be considered further by Ethereum developers to better incentivize developers to be less wasteful in using storage.
+
+\section{Collateralization options}
+
+In \cm, both the tokens and ETH that a trader want to potentially use in the order book are pre-loaded into the contract.
+Consider Alice who holds a token and decides she wants to trade it for ETH.
+In this model, she must first transfer the tokens to the contract and then submit an ask order.
+If she does this within the same block, there is a chance that a miner will execute the ask before the transfer and the ask will revert.
+If she waits for confirmation, this introduces a delay.
+This delay seems reasonable but we point out a few ways it could be addressed:
+
+\begin{enumerate}
+
+\item \textbf{Use \texttt{msg.value}.} For the ETH side of a trade (\ie for bids), ETH could be sent with the function call to \texttt{submitBid()} to remove the need for \texttt{depositEther()}.
+
+\item \textbf{asdf} \cm could
+
+\item \textbf{asdf} \cm could
+
+\item \textbf{asdf} \cm could
+
+\item \textbf{asdf} \cm could
+
+\end{enumerate}
+
+%% = = = = = = = = = = = =Transferring the Collateral back to the traders = = = = = = = = = = = = =  %
+%\subsection{Collateralization}
+%
+%Options for non-collateralized markets
+%ERC20 to ERC20 -> extra transaction
+%

### 2020-09-23 LaTeX/sections/appendix.tex
edits on appendix

--- 2020-09-23 LaTeX/sections/appendix.tex
@@
 
-\section{Extended discussion on cleaning up data structures}
+\section{Extended Discussion on Cleaning up Data Structures}
 
@@
 
-\subsection{Ethereum's gas model}
+\subsection{Ethereum's Gas Model}
 
@@
 When a transaction is executed, each opcode in the execution path accrues a fixed, pre-specified amount of gas.
-The function caller will pledge to pay a certain amount of ETH (typically quoted in units of \textbf{Gwei}, where \textit{wei} is the smallest transactional unit of ETH) per gas, and miners are free to chose to execute it or ignore it.
-The function caller is charged for exactly the amount the transaction costs and they cap the maximum they are willing to be charged (\textit{gas limit})---if the cap is too low to complete the execution, the miner keeps the gwei and reverts the state of the DApp (as if the function never ran).
+The function caller will pledge to pay a certain amount of ETH (typically quoted in units of \textbf{Gwei}, where \textit{wei} is the smallest transactional unit of ETH) per gas, and miners are free to choose to execute that transaction or ignore it.
+The function caller is charged for exactly the amount the transaction costs and they cap the maximum they are willing to be charged (\textit{gas limit})---if the cap is too low to complete the execution, the miner keeps the Gwei and reverts the state of the DApp (as if the function never ran).
 
@@
 A miner can include as many transactions (typically preferring transactions that bid the highest for gas) that can fit under a pre-specified \texttt{block gas limit}, which is algorithmically adjusted for every block.
-As of the time of writting, the limit is around 11M gas.
+As of the time of writing, the limit is around 11M gas.
 
-\subsubsection{Gas refunds.} In order to reconstruct the current state of Ethereum's EVM, a node must obtain a copy of every variable change since the genesis block (or a more recent `checkpoint' that is universally agreed to).
+\subsubsection{Gas Refunds.} In order to reconstruct the current state of Ethereum's EVM, a node must obtain a copy of every variable change since the genesis block (or a more recent `checkpoint' that is universally agreed to).
 For this reason, stored variables persist for a long time and, at first glance, it seems pointless to free up variable storage (and unclear what `free up' even means).
@@
 In \cm, traders preload their account with ERC-20 tokens and/or ETH.
-\cm tracks what they are owed using a mapping called \texttt{totalBalance} and allow traders to withdraw their tokens at any time.
-However if a trader submits an order (\ie ask for their tokens), the tokens are committed and no available for withdrawal until the market closes (after which, the tokens are either transferred to the buyer or, if the trade is not executed, returned to the trader).
+\cm tracks what they are owed using a mapping called \texttt{totalBalance} and allows traders to withdraw their tokens at any time.
+However if a trader submits an order (\ie ask for their tokens), the tokens are committed and not available for withdrawal until the market closes (after which, the tokens are either transferred to the buyer or, if the trade is not executed, returned to the trader).
 Committed tokens are also tracked in a mapping called \texttt{unavailableBalance}.
-A buyer can request a token withdrawal up to their total balance subtracted by their unavailable balance.
+Sellers can request a token withdrawal up to their total balance subtracted by their unavailable balance.
 
-As the DApp runs \texttt{closeMarket()}, it starts matching the best bids and to the best asks.
+\textblue{As the DApp runs \texttt{closeMarket()}, it starts matching the best bids to the best asks.
 As orders execute, \texttt{totalBalance} and \texttt{unavailableBalance} are updated.
@@
 At this point, every order left in the order book cannot execute (because the priority queue sorts orders by price, and so orders deeper in the queue have worst prices than the order at the head of the queue).
-Therefore all remaining entries in \texttt{unavailableBalance} can be cleared.
+Therefore all remaining entries in \texttt{unavailableBalance} can be cleared.}
 

### 2020-09-23 LaTeX/sections/appendix.tex
collateralization

--- 2020-09-23 LaTeX/sections/appendix.tex
@@
 \item \textbf{Use \texttt{msg.value}.} For the ETH side of a trade (\ie for bids), ETH could be sent with the function call to \texttt{submitBid()} to remove the need for \texttt{depositEther()}.
+This works for markets that trade ERC-20 tokens for ETH, but would not work for ERC-20 to ERC-20 exchanges.
 
-\item \textbf{asdf} \cm could
+\item \textbf{Merge deposits with bids/asks.} \cm could have an additional function that atomicly runs the functionality of \texttt{depositToken()} followed by the functionality of \texttt{submitAsk()}.
+This removes the chance that the deposit and order submission are ordered incorrectly.
 
-\item \textbf{asdf} \cm could
+\item \textbf{Use ERC-20 approval.} Instead of \cm taking custody of the tokens, the token holder could simply approve \cm to transfer tokens on her behalf.
+If \cm is coded securely, it is unconcerning to allow the approval to stand long-term and the trader never has to lock up their tokens in the DApp.
+The issue is that there is no guarantee that the tokens are actually available when the market closes (\ie Alice can approve a DApp to spend 100 tokens even if she only has 5 tokens, or no tokens).
+In this case, \cm would optimistically try to transfer the tokens and if it fails, move onto the next order.
+This is also gives Alice an indirect way to cancel an order, by removing the tokens backing the order---this could be a feature or it could be considered an abuse.
 
-\item \textbf{asdf} \cm could
-
-\item \textbf{asdf} \cm could
+\item \textbf{Use a fidelity bond.} Traders could post some amount of tokens as a fidelity bond, and be allowed to submit orders up to 100x this value using approve.
+If a trade fails because the pledged tokens are not available, the fidelity bond is slashed as punishment.
+This lets traders side-step time-consuming transfers to and from \cm while still incentivizing them to ensure that submitted trades can actually be executed.
+The tradeoff is that \cm needs to update balances with external calls to the ERC-20 contract instead of simply updating its internal ledger.
 

### 2020-09-23 LaTeX/sections/appendix.tex

@@
 In \cm, traders preload their account with ERC-20 tokens and/or ETH.
-\cm tracks what they are owed using a mapping called \texttt{totalBalance} and allow traders to withdraw their tokens at any time.
-However if a trader submits an order (\ie ask for their tokens), the tokens are committed and no available for withdrawal until the market closes (after which, the tokens are either transferred to the buyer or, if the trade is not executed, returned to the trader).
+\cm tracks what they are owed using a mapping called \texttt{totalBalance} and allows traders to withdraw their tokens at any time.
+However if a trader submits an order (\ie ask for their tokens), the tokens are committed and not available for withdrawal until the market closes (after which, the tokens are either transferred to the buyer or, if the trade is not executed, returned to the trader).
 Committed tokens are also tracked in a mapping called \texttt{unavailableBalance}.
-A buyer can request a token withdrawal up to their total balance subtracted by their unavailable balance.
+Sellers can request a token withdrawal up to their total balance subtracted by their unavailable balance.
 
-As the DApp runs \texttt{closeMarket()}, it starts matching the best bids and to the best asks.
+As the DApp runs \texttt{closeMarket()}, it starts matching the best bids to the best asks.
 As orders execute, \texttt{totalBalance} and \texttt{unavailableBalance} are updated.

### 2020-09-23 LaTeX/sections/appendix.tex
full round edit (#2)

@@
 
-\section{Collateralization options}
+\section{Collateralization Options}
 
@@
 
-\item \textbf{Merge deposits with bids/asks.} \cm could have an additional function that atomicly runs the functionality of \texttt{depositToken()} followed by the functionality of \texttt{submitAsk()}.
+\item \textbf{Merge deposits with bids/asks.} \cm could have an additional function that atomically runs the functionality of \texttt{depositToken()} followed by the functionality of \texttt{submitAsk()}.
 This removes the chance that the deposit and order submission are ordered incorrectly.
@@
 In this case, \cm would optimistically try to transfer the tokens and if it fails, move onto the next order.
-This is also gives Alice an indirect way to cancel an order, by removing the tokens backing the order---this could be a feature or it could be considered an abuse.
+This also gives Alice an indirect way to cancel an order, by removing the tokens backing the order---this could be a feature or it could be considered an abuse.
 
@@
 If a trade fails because the pledged tokens are not available, the fidelity bond is slashed as punishment.
-This lets traders side-step time-consuming transfers to and from \cm while still incentivizing them to ensure that submitted trades can actually be executed.
+This lets traders side-step time-consuming transfers to and from \cm while still incentivizing them to ensure that submitted orders can actually be executed.
 The tradeoff is that \cm needs to update balances with external calls to the ERC-20 contract instead of simply updating its internal ledger.

### 2020-09-23 LaTeX/sections/paper.tex
appendix
full round edit (#2)

@@
 
-\paragraph{Execution systems.} There are three main approaches to arranging a trade~\cite{Har03}.
-In a \emph{quote-driven} market, a dealer uses their own inventory to offer a price for buying or selling an asset.
+\paragraph{Execution Systems.} There are three main approaches to arranging a trade~\cite{Har03}.
+In a \emph{quote-driven} market, a dealer uses its own inventory to offer a price for buying or selling an asset.
 In a \emph{brokered exchange}, a broker finds a buyer and seller.
@@
 \paragraph{Central Exchanges (CEX).} Traditional financial markets (\eg NYSE and NASDAQ) use order-matching systems to arrange trades.
-An exchange will list one or more assets (stocks, bonds, derivatives, or more exotic securities) to be traded with each given its own order book priced in a currency (\eg USD).
+An exchange will list one or more assets (stocks, bonds, derivatives, or more exotic securities) to be traded with each other, given its own order book priced in a currency (\eg USD).
 Exchanges for blockchain-based assets (also called crypto assets by enthusiasts) can operate the same way, using a centralized exchange (CEX) design where a firm operates the platform as a trusted third party in every aspect: custodianship over assets/currency being traded, exchanging assets fairly, and offering the best possible price execution.
@@
 In this paper, we focus on benchmarking an order book for a public blockchain (\eg Ethereum).
-Ethereum is widely-used and we stand to learn the most from working in a performance-hostile environment (\ie Ethereum is good lower-bound).
+Ethereum is widely-used and we stand to learn the most from working in a performance-hostile environment (\ie Ethereum is a good lower-bound).
 Exchanges could be given their own dedicated blockchain, where trade execution logic can be moved at the consensus level.
@@
 The trade-off is that they operate as a dealer---the DApp exchanges assets from its own inventory.
-This inventory is loaded into the DApp by an investor who will not make money on the trades themselves, but hope for long term profit through trading fees.
+This inventory is loaded into the DApp by an investor who will not make money on the trades themselves, but hope for long-term profit through trading fees.
 By contrast, an order book requires no upfront inventory and does not have to charge trading fees (but can).
@@
 Some (\eg EtherDelta) were envisioned as operating fully on-chain, but performance limitations drove developers to move key components, such as the order matching system, off-chain to a centralized database.
-A landscape of DEX designs exist: many avoiding taking custodianship of assets off-chain, and virtually all (for order-driven markets) operate the order book itself off-chain.
+A landscape of DEX designs exist: many avoid taking custodianship of assets off-chain, and virtually all (for order-driven markets) operate the order book itself off-chain.
 A non-custodial DEX solves the big issue of a CEX---the operator stealing the funds---however trade execution is still not provably fair.
@@
 An older 2014 paper~\cite{clark2014decentralizing} on the `Princeton prediction market'~\cite{Bra13} motivates our work.
-The authors observe the following limitations of on-chain continuous order books: block intervals are slow and not continuous, there is no support for accurate time-stamping, transactions can be dropped or reordered by miners, fast traders can react to submitted orders/cancelations when broadcast to network but not in a block and have their orders appear first (as examined in later work on front-running: \cite{eskandari2019sok,daian2019flash}).
+The authors observe the following limitations of on-chain continuous order books: block intervals are slow and not continuous, there is no support for accurate time-stamping, transactions can be dropped or reordered by miners, fast traders can react to submitted orders/cancellations when broadcast to network but not in a block and have their orders appear first (as examined in later work on front-running: \cite{eskandari2019sok,daian2019flash}).
 
@@
 
-Large exchanges, like the NYSE and NASDAQ, use a two minute call market every day at opening and closing time (in between, the exchange runs as a continuous time market).
+Large exchanges, like the NYSE and NASDAQ, use a two minute call market every day at opening and closing time (in between, the exchange runs as a continuous-time market).
 Other exchanges, called crossing networks, also operate as a call market at various times throughout the trading day.\footnote{A crossing network uses a secondary market for determining the closing price.
-Many prominent crossing networks are operated internally within a brokerage for its clients, and often as a `	dark pool' with an unpublished order book.} Call market are studied widely in finance~\cite{Har03}.
+Many prominent crossing networks are operated internally within a brokerage for its clients, and often as a `dark pool' with an unpublished order book.} Call market are studied widely in finance~\cite{Har03}.
 Time-sensitive traders submit orders early, especially in crossing networks that close at a randomly determined time (traders risk missing the call if they wait too long).
@@
 In most circumstances, the market closing algorithm does not have to consider any deeper bids/asks from the list when choosing whether the current best bid and ask can be fulfilled.
-The only exceptions are in the case of a tie on price or a canceled order, both of which we return to later.
+The only exceptions are in the case of a tie on price or a cancelled order, both of which we return to later.
 For this reason, the ideal data structure for storing bids/asks is a \textit{priority queue} (see Table~\ref{tab:PQ_API}) where each order's priority is its price.
@@
 All the nodes of the tree are in a specific order and the root always represents the highest priority item of the data structure (the largest and smallest values in the Max-Heap and Min-Heap respectively).
-We implemented a priority queue with a heap that stores its data in a dynamically-sized array.
+We implement a priority queue with a heap that stores its data in a dynamically-sized array.
 
@@
 
-\subsubsection{Enqueue performance.} We implemented, deployed, and tested each priority queue using Truffle and Ganache.\footnote{Github: Link removed for anonymity.} We tried a variety of tests (including testing the full call market with each variant) with consistent results in performance.
+\subsubsection{Enqueue Performance.} We implemented, deployed, and tested each priority queue using Truffle and Ganache.\footnote{Github: Link removed for anonymity.} We tried a variety of tests (including testing the full call market with each variant) with consistent results in performance.
 A simple test to showcase the performance profile is shown in Figure~\ref{fig:random_insertion}.
@@
 \includegraphics[width=0.8\textwidth]{fig/random_insertion2.png}
-\caption{\footnotesize{Gas costs for enqueuing random integers into five priority queue variants.
-For the x-axis, a value of 10 indicates it is the 10th number entered in the priority queue.
-The y-axis is the cost of enqueue in gas.}  \label{fig:random_insertion}}
+\caption{\footnotesize{Gas costs for enqueuing 50 random integers into five priority queue variants.
+For the x-axis, a value of 9 indicates it is the 9th number entered in the priority queue.
+The y-axis is the cost of enqueuing in gas.}  \label{fig:random_insertion}}
 \end{figure}
@@
 
-\subsubsection{Discussion.} Based on enqueuing, the heap variants are the cheapest in terms of gas, while based on dequeuing, the link list variants are cheapest.
+\subsubsection{Discussion.} Based on enqueuing, the heap variants are the cheapest in terms of gas, while based on dequeuing, the link list variants are the cheapest.
 This is in accordance with the theoretical worst-case time complexity for each.
@@
 
-\subsection{Cost/Benefit of cleaning up after yourself}
+\subsection{Cost/Benefit of Cleaning up After Yourself}
 \label{sec:gasrefund}
@@
 One consequence of a linked list is that a new contract is created for every node in the list.
-Beyond being expensive for adding new nodes (a cost that will be bared by the trader in a call market), it also leaves a large footprint in the active Ethereum state, especially if we leave the nodes on the blockchain in perpetuity (\ie we just update the head node of the list and leave the previous head `dangling.').
+Beyond being expensive for adding new nodes (a cost that will be bared by the trader in a call market), it also leaves a large footprint in the active Ethereum state, especially if we leave the nodes on the blockchain in perpetuity (\ie we just update the head node of the list and leave the previous head `dangling').
 However in a PQ, nodes are only removed from the head of the list; thus the node contracts could be `destroyed' one by one using an extra operation, \texttt{SELFDESTRUCT}, in the \texttt{Dequeue()} function.
@@
 The simplest approach is to process a node, update the head pointer, and leave the `removed' node's data behind in the mapping untouched (where it will never be referenced again).
-Alternatively we can call \texttt{DELETE} on each mapping entry once we are done with a node in the PQ.
+Alternatively, we can call \texttt{DELETE} on each mapping entry once we are done processing a node in the PQ.
 Deleting a storage variable is identical to setting a non-zero variable to zero (\texttt{SSTORE} 0) that costs 20,000 gas but with 15,000 refunded---a net positive gas cost~\cite{wood2014ethereum}.
@@
 This is a complicated and under-explored area of Ethereum in the research literature.
-For our own work, we strive to be good citizens of Ethereum and clean up to the extent that we can---thus all PQs in Table~\ref{tab:PQUnitTests} implement some clean up and we select linked list with mapping and \texttt{DELETE} for \cm.
+For our own work, we strive to be good citizens of Ethereum and clean up to the extent that we can---thus all PQs in Table~\ref{tab:PQUnitTests} implement some cleanup and we select linked list with mapping and \texttt{DELETE} for \cm.
 
@@
 \cm is intended as a module that developers can modify as they choose---thus we tried to simplify the design at every step to make it highly extensible but still functional without any extensions.
-A call market will open for a specified period of time during which it will accept orders.
-Orders are added to a PQ.
+A call market will open for a specified period of time during which it will accept orders, and these orders are added to a PQ.
 Our vision (discussed below) is the market would be open for a very short period of time, close, and then reopen immediately (\eg every other block).
 We keep the design simple by not allowing cancellations.
-Because markets are relatively short-lived, cancelations require a second transaction, and front-running attacks apply to cancellation orders~\cite{eskandari2019sok}, orders simply expire when the market call period ends.
+Because cancellations require a second transaction, and front-running attacks apply to cancellation orders~\cite{eskandari2019sok}.Also, markets are relatively short-lived and orders simply expire when the market call period ends.
 
@@
 
-The main research question is how many orders can be processed in a single Ethereum transaction when the closing the call market, using Ethereum today.
+The main research question is how many orders can be processed in a single Ethereum transaction when closing the call market, using Ethereum today.
 As our previous experiments indicated, the choice of priority queue (PQ) implementation is the main influence on performance (see Table~\ref{tab:worst_case_matching}).
@@
 Since Ethereum will become more efficient over time, we also were interested in how much gas it would cost to execute 1000 pairs of orders which is given in the third column.
-The fourth column indicates the cost to the trader of submitting a bid or ask --- since this costs will vary depending on how many orders are already submitted (recall Figure~\ref{fig:random_insertion}), we average the cost of 200 order submissions.
+The fourth column indicates the cost of submitting a bid or ask --- since this costs will vary depending on how many orders are already submitted (recall Figure~\ref{fig:random_insertion}), we average the cost of 200 order submissions.
 
@@
 \paragraph{Code Security.} We used two security audit tools, \textit{Slither}\footnote{https://github.com/crytic/slither} and \textit{SmartCheck},\footnote{https://tool.smartdec.net} on \cm to find vulnerabilities and bad practices across 67 tests.
-\cm passes all test except some `informational' warnings (\eg a costly loop) that are intentional design choices.
+\cm passes all tests except some `informational' warnings (\eg a costly loop) that are intentional design choices.
 
-\paragraph{Front-running.} The primary motivation for using a call market, as opposed to a continuous time order book, is to mitigate front-running attacks~\cite{clark2014decentralizing,eskandari2019sok,daian2019flash}.
+\paragraph{Front-running.} The primary motivation for using a call market, as opposed to a continuous-time order book, is to mitigate front-running attacks~\cite{clark2014decentralizing,eskandari2019sok,daian2019flash}.
 Consider a sequence of 100 orders submitted within a window of time to market A, and the same sequence is randomly shuffled and submitted to market B.
@@
 
-Potential for front-running still exists around ties on price and cancelations (see below).
+Potential for front-running still exists around ties on price and order cancellations (see below).
 Finally, \textit{displacement attacks}~\cite{eskandari2019sok} are possible where competitive orders are delayed long enough for the market to close without them.
@@
 For this reason, in \cm, all price improvements are given to the miner (using \texttt{block.coinbase.transfer()}).
-This does not actively hurt traders---they always receive the same price from their order---and it removes any incentive to front-run these profits.
-For all these reasons, we say \cm reduces front-running attacks but stop short of saying it is completely solved by \cm.
+This does not actively hurt traders---they always receive the same price from their orders---and it removes any incentive to front-run these profits.
+For all these reasons, we say \cm reduces front-running attacks but stop short of saying this issue is completely solved by \cm.
 
@@
 
-As a module, we try to keep \cm as simple as possible, and allow customization and extensions as appropriate. We discuss potential modifications here.
+As a module, we try to keep \cm as simple as possible, and allow customizations and extensions as appropriate. We discuss potential modifications here.
 
@@
 
-\subsection{Cancellations}
+\subsection{Order Cancellations}
 
-\cm does not support order cancelations.
+\cm does not support order cancellations.
 We intend to open and close markets quickly (on the order of blocks), so orders are relatively short-lived.
@@
 A close alternative is to allow markets to open and close on different blocks.
-Specifically, the \texttt{closeMarket()} function calls \texttt{openMarket()} as a subroutine and sets two modifiers: orders are only accepted in the block immediately after the current block (\ie the block that executes \texttt{closeMarket()}) and \texttt{closeMarket()} cannot be run again until two blocks after the current block.
+Specifically, the \texttt{closeMarket()} function calls \texttt{openMarket()} as a subroutine and sets two modifiers: orders are only accepted in the block immediately after the current block (\ie the block that executes the \texttt{closeMarket()}) and \texttt{closeMarket()} cannot be run again until two blocks after the current block.
 
@@
 However we consider two other (more realistic) scenarios.
-One solution requires a modified closing function, \texttt{closeMarket(n)}, that only processes $n$ orders at a time (until the order book is empty).
+One solution requires a modified closing function, \texttt{closeMarket(n)}, that only processes $n$ orders at a time (until there is no orders left in the list).
 Once the time window for submitting orders is past, a new market is created (without settling the previous market).
@@
 The second solution is to levy a carefully computed fee against the traders for every new order they submit.
-The fees are accumulated by the DApp to use as a bounty.
+These fees are accumulated by the DApp to use as a bounty.
 When the time window for the open market elapses, the user who calls \texttt{closeMarket()} receives the bounty.
@@
 
-We implement a variant of \cm using rollups on Arbitrum.\footnote{\url{https://offchainlabs.com} for more current details than the 2018 \textit{USENIX Security} paper~\cite{kalodner2018arbitrum}.} In this model, the token issuer (or other interested party) will run a dedicated server to watch Ethereum for function invocations submitted and sequenced on-chain, perform the function call off-chain, and write the resultant state on-chain.
+We implemented a variant of \cm using rollups on Arbitrum.\footnote{\url{https://offchainlabs.com} for more current details than the 2018 \textit{USENIX Security} paper~\cite{kalodner2018arbitrum}.} In this model, the token issuer (or other interested party) will run a dedicated server to watch Ethereum for function invocations submitted and sequenced on-chain, perform the function call off-chain, and write the resultant state on-chain.
 Anyone capable of running EVM code can verify the result.
@@
 Our \cm variant is not the first rollup-based order book.
-Loopring 3.0\footnote{\url{https://loopring.org}} offers a continuous time order book.
+Loopring 3.0\footnote{\url{https://loopring.org}} offers a continuous-time order book.
 The primary difference is that orders in Loopring 3.0 are submitted off-chain to the operator directly, whereas our variant requires on-chain submission.
 While on-chain submission is hampered by Ethereum's block limits, the threat model of reordering transactions is well-understood and our call market design mitigates most front-running attacks.
-In Loopring 3.0, the rollup proof does not ensure that the exchange did not reorder transactions, which is particularly problematic in a continuous time order book.
+In Loopring 3.0, the rollup proof does not ensure that the exchange did not reorder transactions, which is particularly problematic in a continuous-time order book.
 In short, we provide better protection against a malicious exchange while Loopring 3.0 provides even better performance.
-
-%% = = = = = = = = = = = =Transferring the Collateral back to the traders = = = = = = = = = = = = =  %
-%\subsection{Collateralization}
-%
-%Options for non-collateralized markets
-%ERC20 to ERC20 -> extra transaction
-%
 

### 2020-09-24 LaTeX/sections/abstract.tex
final edits

@@
 \begin{abstract}
-Order-driven exchanges on Ethereum tend to operate in a fully centralized fashion, or with some functionality performed on-chain (\eg loading accounts, order cancelation) and some off-chain functionality (\eg matching orders).
+Order-driven exchanges on Ethereum tend to operate in a fully centralized fashion, or with some functionality performed on-chain (\eg loading accounts, order cancellation) and some off-chain functionality (\eg matching orders).
 Fully on-chain solutions have a superior threat model and were experimented with in the early days of Ethereum, but they have been largely abandoned for performance reasons.

### 2020-09-24 LaTeX/sections/paper.tex
final edits

@@
 In designing \cm within Ethereum's gas model, performance is the main bottleneck.
-For a call market, processing all the trades and closing the market is the most time consuming step.
+For a call market, closing the market and processing all the orders is the most time consuming step.
 The most critical design decision is the data structure for holding orders.
@@
 \caption{\footnotesize{Gas costs for enqueuing 50 random integers into five priority queue variants.
-For the x-axis, a value of 9 indicates it is the 9th number entered in the priority queue.
+For the x-axis, a value of 9 indicates it is the 9th integer entered in the priority queue.
 The y-axis is the cost of enqueuing in gas.}  \label{fig:random_insertion}}
@@
 We looked at the \textit{worst-case} for performance which is when every submitted bid and ask is marketable (\ie will require fulfillment).
-In the first two columns, we determined the highest number of orders that can be processed in a single call to the \texttt{closeMarket()} and not exceed the the current Ethereum block gas limit of 11,741,495.
+In the first two columns, we determine the highest number of orders that can be processed in a single call to the \texttt{closeMarket()} and not exceed the the current Ethereum block gas limit of 11,741,495.
 Since Ethereum will become more efficient over time, we also were interested in how much gas it would cost to execute 1000 pairs of orders which is given in the third column.
@@
 If markets open on every other block and the call market could monopolize an entire block to close, a few hundred orders per minute (worst-case) can be processed.
-The main takeaway is that the transparency, front-running resistance, and low barrier to entry of Ethereum comes with an enormous cost (\ie an institutional exchange like NASDAQ can process 100K trades per second).
+The main takeaway is that the transparency, front-running resistance, and low barrier to entry of Ethereum come with an enormous cost (\ie an institutional exchange like NASDAQ can process 100K trades per second).
 That said, many exchanges trade the same assets under different trading rules (\ie market fragmentation) because traders have different preferences.
@@
 
-As a module, we try to keep \cm as simple as possible, and allow customizations and extensions as appropriate. We discuss potential modifications here.
+As a module, we tried to keep \cm as simple as possible, and allow customizations and extensions as appropriate. We discuss potential modifications here.
 
@@
 
-We implement a very simple market where orders all have the same volume: 1 token.
+We implemented a very simple market where orders all have the same volume: 1 token.
 Traders submit multiple orders to increase volume.
@@
 If the call market runs as a DApp on Ethereum, it seems difficult to open and close the market every block.
-Someone needs to call \texttt{closeMarket()} for every block (we return to who this is next) but the market will only work as intended if miners execute this function after every \texttt{submitBid()} and \texttt{submitAsk()} invocation.
+Someone needs to call the \texttt{closeMarket()} for every block (we return to who this is next) but the market will only work as intended if miners execute this function after every \texttt{submitBid()} and \texttt{submitAsk()} invocation.
 Since price improvements are paid to the miners, the miner is incentivized to run \texttt{closeMarket()} last to make the most profit.
@@
 There are actually two issues here: the issue of scheduling the function call and the issue of paying for it.
-For scheduling the function call, we can do one of the following: rely on market participants who are eager to trade to reopen the market, offer a bounty to reopen the market, or use an external service like Ethereum Alarm Clock.\footnote{\url{https://ethereum-alarm-clock-service.readthedocs.io/}} Next we consider the second issue of who pays to close the market.
+For scheduling the function call, we can do one of the following: rely on market participants, who are eager to trade, to reopen the market, offer a bounty to reopen the market, or use an external service like Ethereum Alarm Clock.\footnote{\url{https://ethereum-alarm-clock-service.readthedocs.io/}} Next we consider the second issue of who pays to close the market.
 
@@
 However we consider two other (more realistic) scenarios.
-One solution requires a modified closing function, \texttt{closeMarket(n)}, that only processes $n$ orders at a time (until there is no orders left in the list).
+One solution requires a modified closing function, \texttt{closeMarket(n)}, that only processes $n$ orders at a time (until the order book is empty).
 Once the time window for submitting orders is past, a new market is created (without settling the previous market).

### 2020-09-24 LaTeX/tables/functions.tex
full round edit (#2)
final edits

@@
 % = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
-	closeMarket()                            & Closes the market                                                    					\\ \hline
+	closeMarket()                            & Closes the market and processes the orders       \\ \hline
 % = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
@@
 % = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
-	matchOrders()                           & Matches the orders against each other                                			\\ \hline
+	claimTokens()                           & Transfers tokens to the traders                       			\\ \hline
 % = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
-	claimTokens()                           & Transfers collateralized tokens back to the trader                       			\\ \hline
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
-	claimEther()                             & Transfers collateralized ETH back to the trader                       			\\ \hline
+	claimEther()                             & Transfers ETH to the traders                       			\\ \hline
 % = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %

### 2020-09-24 LaTeX/sections/paper.tex
DONE!

@@
 \paragraph{Other Academic Literature.} There are numerous industry projects on blockchain-based exchanges and order books but most of the academic literature is on topics that are related but tangential to the mechanics of trade execution.
-Early literature considered trade execution under encryption (\ie dark markets)~\cite{TP07,YSLT10,TW12}.
-A number of projects consider structuring futures and derivatives in smart contracts---Velocity ~\cite{eskandari2017feasibility}, Findel ~\cite{biryukov2017findel}, FuturesMex~\cite{massacci2018futuresmex}---but once issued, the derivative can be traded using exchanges.
+Early (and some recent) literature consider trade execution under encryption (\ie dark markets) for securities~\cite{TP07,YSLT10,TW12,cartlidge2019mpc} and futures~\cite{massacci2018futuresmex}.
+A number of projects consider structuring derivatives in smart contracts---Velocity ~\cite{eskandari2017feasibility}, Findel ~\cite{biryukov2017findel}---but once issued, the derivative can be traded using exchanges.
 Atomic swaps (\ie payment vs delivery) are necessary for settling trades and some general approaches include Arwen~\cite{heilman2020arwen} and Tesseract~\cite{bentov2017tesseract}.

### 2020-11-10 Code/New-Truffle/migrations/2_deploy_DappToken.js
CodeUpdates

@@ -1,8 +1,8 @@
 var DappToken = artifacts.require("./DappToken.sol"); 
 module.exports = function (deployer) {
+    //deployer.deploy(DappToken, 10000000, {overwrite: false});
     deployer.deploy(DappToken, 10000000);
-    
-    console.log("I was deployed!");
+    console.log("DappToken was deployed!");
     
 
 };

### 2020-11-10 Code/New-Truffle/migrations/3_deploy_CallMarket.js

@@ -1,11 +1,11 @@
 var CallMarket = artifacts.require("./CallMarket.sol"); 
-var PQ1 = artifacts.require("./HeapDynamicArray.sol"); 
-var PQ2 = artifacts.require("./HeapStaticArray.sol"); 
-var PQ3 = artifacts.require("./HeapMapping.sol");
-var PQ4 = artifacts.require("./LinkedList.sol");
-var PQ5 = artifacts.require("./LinkedListMapping.sol");
-var MP = artifacts.require("./Mapping.sol");
-var PQaddress;
+// var PQ1 = artifacts.require("./HeapDynamicArray.sol"); 
+// var PQ2 = artifacts.require("./HeapStaticArray.sol"); 
+// var PQ3 = artifacts.require("./HeapMapping.sol");
+// var PQ4 = artifacts.require("./LinkedList.sol");
+// var PQ5 = artifacts.require("./LinkedListMapping.sol");
+// var MP = artifacts.require("./Mapping.sol");
+// var PQaddress;
 
 //const BN = require('bn.js');
 
@@ -52,8 +52,9 @@ var PQaddress;
 
 module.exports =  function (deployer) {
     
-    deployer.deploy(CallMarket)
-    console.log("I was deployed!");
+    //deployer.deploy(CallMarket,{overwrite: false});
+    deployer.deploy(CallMarket);
+    console.log("CallMarket was deployed!");
 
 
 };

### 2020-11-10 Code/New-Truffle/test/17_Worst_Case_Matching_test.js

@@ -29,9 +29,14 @@ contract('DappToken', function(accounts) {
     it('should approve transfer of 100 tokens from account[0] to the CallMarket contract ', async ()=> {
         const DappTokenInstance = await DappToken.deployed();
         tokenaddress = DappTokenInstance.address;
+        //accounts = await web3.eth.getAccounts();
+        //console.log(accounts[0].address);
+        const balance = await DappTokenInstance.balanceOf(accounts[0]);
         const receipt = await DappTokenInstance.approve (CallMarketaddress, 15000, {from: accounts[0]});
-        const result = await DappTokenInstance.allowance(accounts[0],CallMarketaddress);
-        console.log('Account[0] allowes the CallMarket contract to spend:',result.toNumber());
+        //const result = await DappTokenInstance.allowance(accounts[0],CallMarketaddress);
+        //console.log('Account[0] allowes the CallMarket contract to spend:',result.toNumber());
+        console.log('********************************************');
+        console.log('account[0] DappToken balance is:',balance.toNumber());
         console.log('********************************************');
     
     });   
@@ -41,39 +46,60 @@ contract('DappToken', function(accounts) {
 //*******************New test Block for the already deployed CallMarket contract *************************
 describe('CallMarket', function(accounts) {
     this.timeout(0);
-   
+    
     //*******************Test 1*************************
+    it('should show the Ether balances of traders before the trade', async() => {
+        const CallMarketInstance = await CallMarket.deployed(); 
+        accounts = await web3.eth.getAccounts();
+        
+        const AliceEtherBalance = await web3.eth.getBalance(accounts[1]);
+        const BobEtherBalance = await web3.eth.getBalance(accounts[0]);
+
+        console.log('The Ether balance of account[1] (Alice) before the trade is:', AliceEtherBalance); 
+        console.log('The Ether balance of account[0] (Bob) before the trade  is:', BobEtherBalance); 
+        console.log('********************************************');
+    });
+
+    //*******************Test 2*************************
     it('should deposit tokens from accounst[0] to the CallMarket contract', async() => {
         
         const CallMarketInstance = await CallMarket.deployed(); 
-
+        var add = CallMarketInstance.address;
+        console.log(add);
+        
         accounts = await web3.eth.getAccounts();
        
         const receipt = await CallMarketInstance.depositToken (tokenaddress, 15000, {from: accounts[0]});
-        
-        const totalbalance = await CallMarketInstance.totalTokenBalance(accounts[0]);
-        
[…]

### 2020-11-10 Code/New-Truffle/test/20_Average_Case_Submission.js

@@ -95,8 +95,9 @@ describe('CallMarket', function(accounts) {
             receipt = await CallMarketInstance.submitAsk (randomnumber, 1, {from: accounts[0]});
             const gasUsed = receipt.receipt.gasUsed;
             //console.log(`GasUsed for a submitAsk tx is: ${receipt.receipt.gasUsed}`);
-            console.log(`${receipt.receipt.gasUsed}`);
+            //console.log(`${receipt.receipt.gasUsed}`);
             array.push(j);
+            console.log(randomnumber);
         } 
         console.log(array.length,'asks have been succsessfully submitted');
          

### 2020-11-10 Code/New-Truffle/truffle-config.js

@@ -25,101 +25,104 @@
 // const mnemonic = fs.readFileSync(".secret").toString().trim();
 
 module.exports = {
-  /**
-   * Networks define how you connect to your ethereum client and let you set the
-   * defaults web3 uses to send transactions. If you don't specify one truffle
-   * will spin up a development blockchain for you on port 9545 when you
-   * run `develop` or `test`. You can ask a truffle command to use a specific
-   * network from the command line, e.g
-   *
-   * $ truffle test --network <network-name>
-   */
-  mocha: {
-    enableTimeouts: false,
-    //before_timeout: 120000 // Here is 2min but can be whatever timeout is suitable for you.
-    //before_timeout: 300000 // Here is 5min but can be whatever timeout is suitable for you.
-
-  },
-
-  networks: {
-    // Useful for testing. The `development` name is special - truffle uses it by default
-    // if it's defined here and no other network is specified at the command line.
-    // You should run a client (like ganache-cli, geth or parity) in a separate terminal
-    // tab if you use this network and you must also set the `host`, `port` and `network_id`
-    // options below to some value.
-    //
-    
-    development: {
-        host: "127.0.0.1",     // Localhost (default: none)
-        port: 8545,            // Standard Ethereum port (default: none)
-        network_id: "*",       // Any network (default: none)
-    
-    //Using the Ethereum current block gas limit and gas price (ganache-cli --gasLimit=0xB32937 --gasPrice=56000000000)
-        gasLimit: 11741495, 
-        gasPrice: 56000000000,        // 56 gwei (in wei), Ganache default is 20000000000 (20gwei)
-        gas: 11000000,                  // Gas sent with each transaction (default: ~6700000)
-        
-    
-    //For 1000 orders (ganache-cli --gasLimit=0x1fffffffffffff --gasPrice=1)
-        //gasLimit: 9007199254740991,
-        //gasPrice:1,
-        //gas:900000000000000,  //dynamic array with ".timeout(90000);" at the end of match test in worst case testing
-
+    /**
+     * Networks define how you connect to your ethereum client and let you set the
+     * defaults web3 uses to send transactions. If you don't specify one truffle
+     * will spin up a development blockchain for you on port 9545 when you
+     * run `develop` or `test`. You can ask a truffle command to use a specific
+     * network from the command line, e.g
+     *
+     * $ truffle test --network <network-name>
+     */
+    mocha: {
+      enableTimeouts: false,
[…]

### 2020-11-10 LaTeX/sections/appendix.tex

@@
 
-\item \textbf{Manually clearing the mapping.} Since mappings cannot be iterated, a common design pattern used by DApp developers is to store keys in an array and iterate over the array to zero out each mapping and array entry.
+\item \textbf{Manually Clearing the Mapping.} Since mappings cannot be iterated, a common design pattern used by DApp developers is to store keys in an array and iterate over the array to zero out each mapping and array entry.
 Clearing a mapping this way costs substantially more to clear than what is refunded (15,000 for each element).
@@
 
-\item \textbf{Leave and ignore the mapping.} The final option is to not clear the mapping and just create a new one (or create a new prefix for all mapping keys to reflect the new version of the mapping).
+\item \textbf{Leave and Ignore the Mapping.} The final option is to not clear the mapping and just create a new one (or create a new prefix for all mapping keys to reflect the new version of the mapping).
 Unfortunately, this is the most economical option for DApp developers even if it is the worst option for Ethereum nodes.
@@
 
-\item \textbf{Merge deposits with bids/asks.} \cm could have an additional function that atomically runs the functionality of \texttt{depositToken()} followed by the functionality of \texttt{submitAsk()}.
+\item \textbf{Merge Deposits with Bids/Asks.} \cm could have an additional function that atomically runs the functionality of \texttt{depositToken()} followed by the functionality of \texttt{submitAsk()}.
 This removes the chance that the deposit and order submission are ordered incorrectly.
 
-\item \textbf{Use ERC-20 approval.} Instead of \cm taking custody of the tokens, the token holder could simply approve \cm to transfer tokens on her behalf.
+\item \textbf{Use ERC-20 Approval.} Instead of \cm taking custody of the tokens, the token holder could simply approve \cm to transfer tokens on her behalf.
 If \cm is coded securely, it is unconcerning to allow the approval to stand long-term and the trader never has to lock up their tokens in the DApp.
@@
 
-\item \textbf{Use a fidelity bond.} Traders could post some amount of tokens as a fidelity bond, and be allowed to submit orders up to 100x this value using approve.
+\item \textbf{Use a Fidelity Bond.} Traders could post some amount of tokens as a fidelity bond, and be allowed to submit orders up to 100x this value using approve.
 If a trade fails because the pledged tokens are not available, the fidelity bond is slashed as punishment.
 This lets traders side-step time-consuming transfers to and from \cm while still incentivizing them to ensure that submitted orders can actually be executed.
-The tradeoff is that \cm needs to update balances with external calls to the ERC-20 contract instead of simply updating its internal ledger.
+The trade-off  is that \cm needs to update balances with external calls to the ERC-20 contract instead of simply updating its internal ledger.
 

### 2020-12-09 LaTeX-USENIX/setup/packages.tex
Edits

% !TEX root = ../main.tex

%------------------------USENIX----------------------%

\usepackage{usenix2019_v3}

%------------------------Packages----------------------%

% = = = Graphics
\usepackage[pdftex]{graphicx}
\graphicspath{{figures/}}
\DeclareGraphicsExtensions{.jpg,.png}

% = = = Subfig (note not subfigure)
\usepackage[caption=false,font=footnotesize]{subfig}

% = = = Math Symbols
\usepackage{amsmath}
%\usepackage{amstext,amssymb,amsthm}
\usepackage{bbm}
\usepackage{stmaryrd}

% = = = Other
\usepackage{array}
%\usepackage[hyphens]{url}
%\usepackage[pdftitle=Title,pdfauthor=Anonymous]{hyperref}
\usepackage{adjustbox}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{rotating}
\usepackage{makecell}
\usepackage{hhline}
\usepackage{lscape}
\usepackage{tabu}
\usepackage{tikz}
\usepackage{textcomp} %Using tilde
\usetikzlibrary{shapes,backgrounds} %Venn diagram
\usepackage[justification=centering]{caption} % to add caption in tabular environment using the command \captionof{table}{Your caption here} 
\usepackage{colortbl}

\usepackage{blindtext}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{tabularx}
\usepackage{blindtext}
\usepackage{booktabs}
\usepackage{makecell}

\usepackage{cellspace}

\usepackage{longtable}

%---------------------------------------------------%
\usepackage{listings, xcolor}
\renewcommand{\lstlistingname}{Code}
\definecolor{verylightgray}{rgb}{.97,.97,.97}
\lstdefinelanguage{Solidity}{
keywords=[1]{anonymous, assembly, assert, balance, break, call, callcode, case, catch, class, constant, continue, contract, debugger, default, delegatecall, delete, do, else, event, export, external, false, finally, for, function, gas, if, implements, import, in, indexed, instanceof, interface, internal, is, length, library, log0, log1, log2, log3, log4, memory, modifier, new, payable, pragma, private, protected, public, pure, push, require, return, returns, revert, selfdestruct, send, storage, struct, suicide, super, switch, then, this, throw, transfer, true, try, typeof, using, value, view, while, with, addmod, ecrecover, keccak256, mulmod, ripemd160, sha256, sha3}, % generic keywords including crypto operations
	keywordstyle=[1]\color{blue}\bfseries,
	keywords=[2]{Stages,States, address, bool, byte, bytes, bytes1, bytes2, bytes3, bytes4, bytes5, bytes6, bytes7, bytes8, bytes9, bytes10, bytes11, bytes12, bytes13, bytes14, bytes15, bytes16, bytes17, bytes18, bytes19, bytes20, bytes21, bytes22, bytes23, bytes24, bytes25, bytes26, bytes27, bytes28, bytes29, bytes30, bytes31, bytes32, enum, int, int8, int16, int24, int32, int40, int48, int56, int64, int72, int80, int88, int96, int104, int112, int120, int128, int136, int144, int152, int160, int168, int176, int184, int192, int200, int208, int216, int224, int232, int240, int248, int256, mapping, string, uint, uint8, uint16, uint24, uint32, uint40, uint48, uint56, uint64, uint72, uint80, uint88, uint96, uint104, uint112, uint120, uint128, uint136, uint144, uint152, uint160, uint168, uint176, uint184, uint192, uint200, uint208, uint216, uint224, uint232, uint240, uint248, uint256, var, void, ether, finney, szabo, wei, days, hours, minutes, seconds, weeks, years},	% types; money and time units
	keywordstyle=[2]\color{teal}\bfseries,
	keywords=[3]{block, blockhash, coinbase, difficulty, gaslimit, number, timestamp, msg, data, gas, sender, sig, value, now, tx, gasprice, origin},	% environment variables
	keywordstyle=[3]\color{violet}\bfseries,
	identifierstyle=\color{black},
	sensitive=false,
	comment=[l]{//},
	morecomment=[s]{/*}{*/},
	commentstyle=\color{gray}\ttfamily,
	stringstyle=\color{red}\ttfamily,
	morestring=[b]',
	morestring=[b]"
}

\lstset{
	language=Solidity,
	backgroundcolor=\color{verylightgray},
	extendedchars=true,
	basicstyle=\footnotesize\ttfamily,
	showstringspaces=false,
	showspaces=false,
	numbers=left,
	numberstyle=\footnotesize,
	numbersep=9pt,
	tabsize=2,
	breaklines=true,
	showtabs=false,
	captionpos=b,
      escapeinside={<@}{@>},
}

%------------------------END----------------------%

### 2020-12-16 LaTeX-USENIX/sections/paper.tex
Edits
some edits

--- 2020-09-24 LaTeX/sections/paper.tex
@@
 \subsection{Market Structure}
+
+\input{tables/eval.tex}
 
@@
 \centering
-\includegraphics[width=0.8\textwidth]{fig/random_insertion2.png}
+\includegraphics[width=0.5\textwidth]{fig/random_insertion2.png}
 \caption{\footnotesize{Gas costs for enqueuing 50 random integers into five priority queue variants.
@@
 Table~\ref{tab:cm_functions} represents \cm's primary operations.
+\textblue{Mahsa: \cm's size of bytecode in bytes: 17212,  \cm's size of deployed in bytes: 10812, initialization and constructor code in bytes: 6400}
 
@@
 \subsection{Token Divisibility and Volumes}
+
+\textblue{Mahsa: Partial Filling: we ran the worst case matching test with random volumes between 1 and 10 on linked list with mapping (which handles maximum pairs of 80 orders with single volumes).
+With partial filling, it can clear the book that contains 70 pairs at max (which on average ends up being ~118 trades).
+SO it is moderately more expensive}
 
@@
 %\subsubsection*{Acknowledgements.} J. Clark thanks ...
+
+\subsubsection*{Availability} 
+\textblue{USENIX program committees give extra points to submissions that are backed by artifacts that are publicly available.
+If you made your code or data available, it’s worth mentioning this fact in a dedicated section.}

### 2020-12-16 LaTeX-USENIX/tables/functions.tex
some edits

--- 2020-09-24 LaTeX/tables/functions.tex
@@
 \begin{table}[t]
-\begin{tabular}{|l|l|}
+\setlength{\tabcolsep}{0.7\tabcolsep}% Shrink \tabcolsep
+\begin{tabular}{|c|c|}
 \hline
@@
 % = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
-	depositToken()                           & Deposits ERC20 standard compliant tokens in \cm smart contract \\ \hline
+	depositToken()                           & \shortstack{Deposits ERC20 standard compliant \\ tokens in \cm smart contract} \\ \hline
 % = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
@@
 % = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
-	submitBid()                              & Inserts the upcoming bid order messages inside the priority queue    \\ \hline
+	submitBid()                              & \shortstack{Inserts the upcoming bid order \\ messages inside the priority queue}    \\ \hline
 % = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
-	submitAsk()                              & Inserts the upcoming ask order messages inside the priority queue    \\ \hline
+	submitAsk()                              & \shortstack{ Inserts the upcoming ask order \\ messages inside the priority queue}    \\ \hline
 % = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %

### 2020-12-18 LaTeX-USENIX/sections/abstract.tex
eval frameworks edits

--- 2020-09-24 LaTeX/sections/abstract.tex
@@
 As block\-chain performance continues to improve (both in research and in practice) and on-chain dealer-based exchanges like Uniswap (an alternative to order-based exchanges) rise in popularity, it seems to be an ideal time to revisit the idea of a fully on-chain order-driven exchange and benchmark what is possible performance-wise.
-We design and optimize an Ethereum-based call market exchange, \cm, and conduct a variety of experiments to show the current benchmark is around one hundred trade executions per block.
+We design and optimize an Ethereum-based call market (or batch auction) exchange, \cm, and conduct a variety of experiments to show the current benchmark is around one hundred trade executions per block.
 We also explore numerous extensions for further improvements, including a variant using off-chain execution (`rollups').

### 2020-12-21 LaTeX-USENIX/sections/paper.tex
PQ insertion figure added
edits

@@
 \centering
-\includegraphics[width=0.5\textwidth]{fig/random_insertion2.png}
+\includegraphics[width=0.5\textwidth]{fig/random_insertion3.png}
 \caption{\footnotesize{Gas costs for enqueuing 50 random integers into five priority queue variants.
@@
 
+\textblue{Reviewer's comment: DDOS against submitbid and submitask functions.
+Our answer: we put a cap on the number of orders submitted to the market so that we can always close.
+Also talk about bulk displacement attack (see reviewers comments)}
+
 %GitHub repo:  \footnote{\CallMarketRepo}
@@
 
-\paragraph{Front-running.} The primary motivation for using a call market, as opposed to a continuous-time order book, is to mitigate front-running attacks~\cite{clark2014decentralizing,eskandari2019sok,daian2019flash}.
+\paragraph{Front-running.} \textblue{we have to revisit this section: talk about our front-running paper: there are various ways to prevent frontrunning, one is through confidentiality..., then cite this paper: 'TEX – A Securely Scalable Trustless Exchange'~\cite{khalil2019tex} }The primary motivation for using a call market, as opposed to a continuous-time order book, is to mitigate front-running attacks~\cite{clark2014decentralizing,eskandari2019sok,daian2019flash}.
 Consider a sequence of 100 orders submitted within a window of time to market A, and the same sequence is randomly shuffled and submitted to market B.
@@
 \section{Design Alternatives and Extensions}
+
+ \textblue{ We need to find a home for this: another solution to reopen the market immediately after the closing call is to have many similar contracts for the market and  a factory contract to guide users to the correct address (from the reviewer's comment)}
 

### 2021-01-11 LaTeX-USENIX/sections/appendix.tex
new title, abstract and intro

--- 2020-11-10 LaTeX/sections/appendix.tex
@@
 
-\section{Collateralization Options}
-
-In \cm, both the tokens and ETH that a trader want to potentially use in the order book are pre-loaded into the contract.
-Consider Alice who holds a token and decides she wants to trade it for ETH.
-In this model, she must first transfer the tokens to the contract and then submit an ask order.
-If she does this within the same block, there is a chance that a miner will execute the ask before the transfer and the ask will revert.
-If she waits for confirmation, this introduces a delay.
-This delay seems reasonable but we point out a few ways it could be addressed:
-
-\begin{enumerate}
-
-\item \textbf{Use \texttt{msg.value}.} For the ETH side of a trade (\ie for bids), ETH could be sent with the function call to \texttt{submitBid()} to remove the need for    \texttt{depositEther()}.
-This works for markets that trade ERC-20 tokens for ETH, but would not work for ERC-20 to ERC-20 exchanges.
-
-\item \textbf{Merge Deposits with Bids/Asks.} \cm could have an additional function that atomically runs the functionality of \texttt{depositToken()} followed by the functionality of \texttt{submitAsk()}.
-This removes the chance that the deposit and order submission are ordered incorrectly.
-
-\item \textbf{Use ERC-20 Approval.} Instead of \cm taking custody of the tokens, the token holder could simply approve \cm to transfer tokens on her behalf.
-If \cm is coded securely, it is unconcerning to allow the approval to stand long-term and the trader never has to lock up their tokens in the DApp.
-The issue is that there is no guarantee that the tokens are actually available when the market closes (\ie Alice can approve a DApp to spend 100 tokens even if she only has 5 tokens, or no tokens).
-In this case, \cm would optimistically try to transfer the tokens and if it fails, move onto the next order.
-This also gives Alice an indirect way to cancel an order, by removing the tokens backing the order---this could be a feature or it could be considered an abuse.
-
-\item \textbf{Use a Fidelity Bond.} Traders could post some amount of tokens as a fidelity bond, and be allowed to submit orders up to 100x this value using approve.
-If a trade fails because the pledged tokens are not available, the fidelity bond is slashed as punishment.
-This lets traders side-step time-consuming transfers to and from \cm while still incentivizing them to ensure that submitted orders can actually be executed.
-The trade-off  is that \cm needs to update balances with external calls to the ERC-20 contract instead of simply updating its internal ledger.
-
-\end{enumerate}
-
 %% = = = = = = = = = = = =Transferring the Collateral back to the traders = = = = = = = = = = = = =  %

### 2021-01-11 LaTeX-USENIX/sections/paper.tex
edits on the eval + added the contract add
new title, abstract and intro

@@
 
-For years, exchanges have operated either entirely off-chain by trusted operators or partially on-chain by semi-trusted operators.
-A fully on-chain exchange is feasible but considered too slow, at least for a public blockchain like Ethereum.
-We believe it is a very good time to do a deep dive into understanding precisely \textit{how slow} for the following reasons: (1) public blockchains are becoming faster (both in theory and slowly in practice) and the efficiency of an on-chain exchange will increase in time, (2) demand for on-chain trading is exemplified by the recent popularity of dealer-based (or quote-based) trading like Uniswap and Curve Finance, and (3) stablecoins have become popular and allow on-chain trading with pricing in USD (or other government currency).
+Financial regulators seek to provide consumer protection during the issuing and trading of financial products and assets.
+They are concerned by their limited ability to intervene when trading is conducted on decentralized networks that, like Ethereum, run on the open internet.
+While order-driven exchange could theoretically happen `on-chain' and were experimented with in the early days of Ethereum, they have been largely abandoned for performance reasons in favour of running on centralized servers---or, at least, with core functionality performed off-chain (\eg matching orders) while other aspects (\eg loading accounts, order cancellation) might be performed on-chain.
+In this world, company names, employees, addresses, and publicly addressable servers all provide regulatory hooks.
 
-\paragraph{Contributions.} We design and implement \cm, a fully on-chain call market in Solidity---a high-level programming language for Ethereum.
-We choose Ethereum as a `hostile' environment for an order book: Ethereum is public (strongest adversary) and slow (lower-bound benchmark) relative to more scalable blockchains, including the anticipated Ethereum 2.0.
-\cm is intended as a simple module that developers can modify as they choose.
-By adding \cm to an ERC20 (or similar) token contract, everything that is needed for buying/selling tokens is immediately available on chain without involving any third party exchanges.
-\cm is non-custodial, transparent, and mitigates front-running attacks that are generally possible on-chain.
+Our research group has collaborated with our jurisdiction's financial regulator (name withheld for peer-review) to help them forecast how trading can be impacted by blockchain technology.
+This paper addresses their concerns about the feasibility of a `worst-case scenario' where a trading platform is anonymously deployed on a public blockchain, like Ethereum, and runs autonomously without any further intervention from an externally visible entity.
+Such a design appears feasible but is considered too slow.
+Together, we agreed it is a very good time to do a deep dive into understanding precisely \textit{how slow} for the following reasons: (1) public blockchains are becoming faster (both in theory and in practice) providing future efficiency gains for on-chain trading, (2) demand for on-chain trading is exemplified by the recent popularity of dealer quote-based trading like Uniswap and Curve Finance (reviewed below), and (3) stablecoins have become popular and allow on-chain trading with pricing in USD, alleviating another regulatory hook: the need for platforms to maintain traditional accounts for holding governmental currency and interface with the banking system.
+
+\paragraph{Contributions.} We study fully on-chain markets through design and implementation with Solidity---a high-level programming language for Ethereum.
+We choose Ethereum as a hostile environment for an order book: Ethereum runs on the internet open to anyone for networks participation (strongest adversarial model and hardest to regulate).
+As a result, it is slow which gives us a lower-bound benchmark relative to more scalable blockchains, including the anticipated Ethereum 2.0 and permissioned systems (\eg Hyperledger) operated by authorized nodes (a regulatory hook).
+Our design, \cm, is a proof-of-concept base class suitable for experiments and is extensible in several ways we describe.
+\cm is designed from a security perspective: users only trust their assets to \cm's auditable code (non-custodial) and not to a third party, all operations are transparent, and we nearly eliminate the ability for adversarial network nodes to profit from front-running orders.
+In fact, we believe we are the first to design a decentralized application that actually leverages front-running (\ie miner extractable value~\cite{daian2019flash}) for the benefit of the system (see Section~\ref{sec:close}).
 
@@
 The bottom line is that the current benchmark for a \cm-esque design is in the low hundreds of trade executions per block on Ethereum today.
-This positions \cm as a feasible design for certain types of markets today (low liquidity, small number of traders) but also as an early study on technology that is likely to improve vastly in the coming years.
+This positions \cm as a feasible design for only a narrow set of markets today (low liquidity, small number of traders) which is good news for regulators.
+However we caution that the technology is likely to improve vastly in the coming years and we demonstrate one avenue for improvement through `roll-ups'~\cite{kalodner2018arbitrum}.
+While roll-ups use central servers, in our architecture, these servers only interface with Ethereum and never directly with users which side-steps the regulatory hook that is present in many other server-augmented trading platforms.
 
@@
 
+\textblue{\cm is deployed on the Rinkeby--- Ethereum testnet (or test network).
+The contract address is '0x40F3089C4C404dA9E9655AD230aDD2E493BE8e5c', more details can be found on \texttt{https://rinkeby.etherscan.io}}
+
 \cm is written in 324 lines (SLOC) of Solidity,~\footnote{Github: linked removed for anonymity} a high level programming language that is syntactically similar to Java~\cite{Ethereum41:online}.
@@
 \subsection{Who Pays to Close/Reopen the Market?}
+\label{sec:close}
 
@@
 
+\section{Collateralization Options}
+
+In \cm, both the tokens and ETH that a trader want to potentially use in the order book are pre-loaded into the contract.
+Consider Alice who holds a token and decides she wants to trade it for ETH.
+In this model, she must first transfer the tokens to the contract and then submit an ask order.
+If she does this within the same block, there is a chance that a miner will execute the ask before the transfer and the ask will revert.
+If she waits for confirmation, this introduces a delay.
+This delay seems reasonable but we point out a few ways it could be addressed:
+
+\begin{enumerate}
+
+\item \textbf{Use \texttt{msg.value}.} For the ETH side of a trade (\ie for bids), ETH could be sent with the function call to \texttt{submitBid()} to remove the need for    \texttt{depositEther()}.
+This works for markets that trade ERC-20 tokens for ETH, but would not work for ERC-20 to ERC-20 exchanges.
+
+\item \textbf{Merge Deposits with Bids/Asks.} \cm could have an additional function that atomically runs the functionality of \texttt{depositToken()} followed by the functionality of \texttt{submitAsk()}.
+This removes the chance that the deposit and order submission are ordered incorrectly.
+
+\item \textbf{Use ERC-20 Approval.} Instead of \cm taking custody of the tokens, the token holder could simply approve \cm to transfer tokens on her behalf.
+If \cm is coded securely, it is unconcerning to allow the approval to stand long-term and the trader never has to lock up their tokens in the DApp.
+The issue is that there is no guarantee that the tokens are actually available when the market closes (\ie Alice can approve a DApp to spend 100 tokens even if she only has 5 tokens, or no tokens).
+In this case, \cm would optimistically try to transfer the tokens and if it fails, move onto the next order.
+This also gives Alice an indirect way to cancel an order, by removing the tokens backing the order---this could be a feature or it could be considered an abuse.
+
+\item \textbf{Use a Fidelity Bond.} Traders could post some amount of tokens as a fidelity bond, and be allowed to submit orders up to 100x this value using approve.
+If a trade fails because the pledged tokens are not available, the fidelity bond is slashed as punishment.
+This lets traders side-step time-consuming transfers to and from \cm while still incentivizing them to ensure that submitted orders can actually be executed.
+The trade-off  is that \cm needs to update balances with external calls to the ERC-20 contract instead of simply updating its internal ledger.
+
+\end{enumerate}
+
 % = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =

### 2021-01-11 LaTeX-USENIX/sections/paper.tex
some progress

@@
 \paragraph{Contributions.} We study fully on-chain markets through design and implementation with Solidity---a high-level programming language for Ethereum.
-We choose Ethereum as a hostile environment for an order book: Ethereum runs on the internet open to anyone for networks participation (strongest adversarial model and hardest to regulate).
-As a result, it is slow which gives us a lower-bound benchmark relative to more scalable blockchains, including the anticipated Ethereum 2.0 and permissioned systems (\eg Hyperledger) operated by authorized nodes (a regulatory hook).
-Our design, \cm, is a proof-of-concept base class suitable for experiments and is extensible in several ways we describe.
-\cm is designed from a security perspective: users only trust their assets to \cm's auditable code (non-custodial) and not to a third party, all operations are transparent, and we nearly eliminate the ability for adversarial network nodes to profit from front-running orders.
+We choose Ethereum as a hostile environment for an order book: Ethereum is fully decentralized (hardest to regulate), network participation is open to anyone on the internet (strongest adversarial model), and, as a result, it is slow (a lower-bound benchmark).
+Generally if an application is feasible on Ethereum, it will also be feasible and only run faster on a private (or permissioned) blockchain (\eg Hyperledger), which is operated by authorized network nodes (a regulatory hook).
+
+Our proof-of-concept, \cm, is an extensible base class suitable for experiments.
+\cm is designed from a security perspective: users only trust their assets to \cm's auditable code (non-custodial) and not to a third party; all operations are transparent; and we nearly eliminate the ability for adversarial network nodes to profit from front-running orders.
 In fact, we believe we are the first to design a decentralized application that actually leverages front-running (\ie miner extractable value~\cite{daian2019flash}) for the benefit of the system (see Section~\ref{sec:close}).
@@
 However we caution that the technology is likely to improve vastly in the coming years and we demonstrate one avenue for improvement through `roll-ups'~\cite{kalodner2018arbitrum}.
-While roll-ups use central servers, in our architecture, these servers only interface with Ethereum and never directly with users which side-steps the regulatory hook that is present in many other server-augmented trading platforms.
+While roll-ups use centralized servers and are thus no fully on-chain, we consider an architecture where these servers only interface with Ethereum and never interface directly with users, which side-steps the regulatory hook that is present in many other server-augmented trading platforms (including both decentralized exchanges like 0x and EtherDelta, and roll-ups like Loopring, all described below).
 
@@
 
-\subsection{Market Structure}
+\subsection{Ethereum and Blockchain Technology}
 
-\input{tables/eval.tex}
+A public blockchain is an open peer-to-peer network that maintains a set of transactions without a single entity in charge.
+Transactions can concern payments.
+In Ethereum, they represent the bytecode of user-written decentralized applications (DApps) to be stored on the blockchain; and the functional calls made to the DApp.
+Every functional call is a validated by all honest, participating nodes to have been correctly executed; a property that is robust against a fraction of faulty and malicious network nodes (or more precisely, their accumulated computational power).
+Once transactions are agreed upon, all honest participants will have identical sets of transactions in the same order.
+For Ethereum, this is conceptualized as the current state of a large virtual machine (EVM) that is running many DApps.
 
-\paragraph{Execution Systems.} There are three main approaches to arranging a trade~\cite{Har03}.
+Transactions are broadcast by users to the blockchain network where they are propagated to all nodes.
+Nodes that choose to `mine' will collect transactions (in the order of their choosing) into a block, and will attempt to have the network reach a consensus that their block should be added to the set (or chain) of previous blocks.
+A transaction is considered finalized once consensus on its inclusion has held for several additional blocks.
+
+\textbf{Gas.} Every transaction results in the participating nodes having to execute bytecode.
+This is not free.
+When a transaction is executed, each opcode in the execution path accrues a fixed, pre-specified amount of gas.
+The function caller will pledge to pay a certain amount of Ethereum's internal currency ETH (typically quoted in units of Gwei which is one billionth of an ETH) per unit of gas, and miners are free to choose to execute that transaction or ignore it.
+The function caller is charged for exactly the amount the transaction costs and they cap the maximum they are willing to be charged (\textit{gas limit})---if the cap is too low to complete the execution, the miner keeps the Gwei and reverts the state of the EVM (as if the function never ran).
+
+A miner can include as many transactions (typically preferring transactions that bid the highest for gas) that can fit under a pre-specified \textit{block gas limit}, which is algorithmically adjusted for every block.
+As of the time of writing, the limit is approximately 11M gas.
+Essentially, our main research question is how many on-chain trades can be executed without exceeding that limit.
+Later we also discuss several opcodes that refund gas (or cost negative gas), which we heavily utilize in our optimizations.
+
+\subsection{Trade Execution Systems}
+
+ There are three main approaches to arranging a trade~\cite{Har03}.
 In a \emph{quote-driven} market, a dealer uses its own inventory to offer a price for buying or selling an asset.
@@
 In an \emph{order-driven} market, offers to buy (\emph{bids}) and sell (\emph{offers}/\emph{asks}) from many traders are placed as orders in an order book.
-Order-driven markets can be \emph{continuous}, with buyers/sellers at any time adding orders to the order book (\emph{makers}) or executing against an existing order (\emph{takers}); or they can be \emph{called}, where all traders submit orders within a window of time and orders are matched in a batch like an auction.
+Order-driven markets can be \emph{continuous}, with buyers/sellers at any time adding orders to the order book (\emph{makers}) or executing against an existing order (\emph{takers}); or they can be \emph{called}, where all traders submit orders within a window of time and orders are matched in a batch (like an auction).
 
-\subsection{Decentralized Order Matching}
+\subsection{Trading Blockchain-based Assets}
+
+%\input{tables/eval.tex}
 
@@
 An exchange will list one or more assets (stocks, bonds, derivatives, or more exotic securities) to be traded with each other, given its own order book priced in a currency (\eg USD).
-Exchanges for blockchain-based assets (also called crypto assets by enthusiasts) can operate the same way, using a centralized exchange (CEX) design where a firm operates the platform as a trusted third party in every aspect: custodianship over assets/currency being traded, exchanging assets fairly, and offering the best possible price execution.
-Security breaches and fraud (\eg MtGox~\cite{TheHisto45:online}, QuadrigaCX~\cite{SEBIOrde83:online}, and many others) in centralized exchanges have become a common source of lost funds for users, while accusations of unfair trade execution have been levelled but are difficult to prove.
+Exchanges for blockchain-based assets (also called crypto assets by enthusiasts) can operate the same way, using a centralized exchange (CEX) design where a firm (\eg Binance, Bitfinex, \etc) operates the platform as a trusted third party in every aspect: custodianship over assets/currency being traded, exchanging assets fairly, offering the best possible price execution.
+Security breaches and fraud in centralized exchanges  (\eg MtGox~\cite{TheHisto45:online}, QuadrigaCX~\cite{SEBIOrde83:online}, and many others) have become a common source of lost funds for users, while accusations of unfair trade execution have been levelled but are difficult to prove.
+Today, CEXes are often regulated as other money service businesses---this provides some ability for the government to conduct financial tracking but does little to provide consumer protection against fraud.
 
@@
 While they sound ideal, performance is a substantial issue and the main subject of this paper.
+Since it is an open system, there is no obvious regulatory hook (beyond the blockchain itself).
 
 In this paper, we focus on benchmarking an order book for a public blockchain (\eg Ethereum).
-Ethereum is widely-used and we stand to learn the most from working in a performance-hostile environment (\ie Ethereum is a good lower-bound).
-Exchanges could be given their own dedicated blockchain, where trade execution logic can be moved at the consensus level.
-Permissioned blockchains (\eg NASDAQ Linq, tZero) can also increase execution time and throughput, possibly with some reduction in transparency and trust.
+Ethereum is widely-used and we stand to learn the most from working in a performance-hostile environment.
+Exchanges could be given their own dedicated blockchain, where trade execution logic can be coded into the network protocol.
+Trading systems on permissioned blockchains (\eg NASDAQ Linq, tZero) can also increase execution time and throughput but reduce user transparency and trust.
+Since it is a closed system, regulators will concentrate on the operators.
 
@@
 The trade-off is that they operate as a dealer---the DApp exchanges assets from its own inventory.
-This inventory is loaded into the DApp by an investor who will not make money on the trades themselves, but hope for long-term profit through trading fees.
-By contrast, an order book requires no upfront inventory and does not have to charge trading fees (but can).
+This inventory is loaded into the DApp by an investor who cannot make money on the trades themselves but hopes their losses (termed `impermanent losses') are offset over the long-term by trading fees.
+By contrast, an order book requires no upfront inventory and trading fees are optional.
 Finally, there is a complicated difference in their price dynamics (\eg market impact of a trade, slippage between the best bid/ask and actual average execution price, \etc)---deserving of an entire research paper to precisely define.
@@
 Some (\eg EtherDelta) were envisioned as operating fully on-chain, but performance limitations drove developers to move key components, such as the order matching system, off-chain to a centralized database.
-A landscape of DEX designs exist: many avoid taking custodianship of assets off-chain, and virtually all (for order-driven markets) operate the order book itself off-chain.
-A non-custodial DEX solves the big issue of a CEX---the operator stealing the funds---however trade execution is still not provably fair.
+A landscape of DEX designs exist (\eg EtherDelta, 0x, IDEX, \etc): many avoid taking custodianship of assets off-chain, and virtually all (for order-driven markets) operate the order book itself off-chain (a regulatory hook).
+A non-custodial DEX solves the big issue of a CEX---the operator stealing the funds---however trade execution is still not provably fair and server downtime is a common frustration for traders.
 A mitigation is to issue a proof of correct execution to the DApp (\eg Loopring) but these proofs have blindspots (discussed in section~\ref{sec:rollups}).
-\cm offers key advantages in this model as well.
 
@@
 
-Large exchanges, like the NYSE and NASDAQ, use a two minute call market every day at opening and closing time (in between, the exchange runs as a continuous-time market).
+Large exchanges, like the NYSE and NASDAQ, run two call markets every trading day in parallel with a continuous-time market.
+One call market closes at market open to produce the opening price for each stock, while the other closes at the end of the day to produce the closing price.
 Other exchanges, called crossing networks, also operate as a call market at various times throughout the trading day.\footnote{A crossing network uses a secondary market for determining the closing price.
@@
 Alternatively, we can call \texttt{DELETE} on each mapping entry once we are done processing a node in the PQ.
-Deleting a storage variable is identical to setting a non-zero variable to zero (\texttt{SSTORE} 0) that costs 20,000 gas but with 15,000 refunded---a net positive gas cost~\cite{wood2014ethereum}.
-As it can be seen in the last two rows of Table~\ref{tab:cleaning}, leaving the data on chain is cheaper than cleaning it up.
+\textblue{Deleting a storage variable is identical to setting a non-zero variable to zero (\texttt{SSTORE} 0) that costs 20,000 gas but with 15,000 refunded---a net positive gas cost~\cite{wood2014ethereum}.} As it can be seen in the last two rows of Table~\ref{tab:cleaning}, leaving the data on chain is cheaper than cleaning it up.
 
@@
 % Ties?
-
-\textblue{\cm is deployed on the Rinkeby--- Ethereum testnet (or test network).
-The contract address is '0x40F3089C4C404dA9E9655AD230aDD2E493BE8e5c', more details can be found on \texttt{https://rinkeby.etherscan.io}}
 
@@
 
-\section{Collateralization Options}
+\subsection{Collateralization Options}
 
@@
 
-Imagine you have just launched an ERC20 token on Ethereum.
+Imagine you have just launched a standard token on Ethereum.
 Now want your holders to be able to trade it.
@@
 For rollups, you will have to host your own servers.
-By contrast to all of these, with \cm you just deploy the code alongside your token and trading is immediately supported.
-Even if \cm is a fallback solution today, we believe it is helpful for every token to be accompanied by on-chain trade execution.
+By contrast to all of these, with an on-chain orderbook, you just deploy the code alongside your token and trading is immediately supported.
+Even if it is too slow today, there is little reason for developers not to offer it as a fallback solution that accompanies every token.
 With future improvements to blockchain scalability, it could become the defacto trading method.
@@
 \subsubsection*{Availability} 
-\textblue{USENIX program committees give extra points to submissions that are backed by artifacts that are publicly available.
-If you made your code or data available, it’s worth mentioning this fact in a dedicated section.}
+The Solidity source code for \cm, Truffle test files, and Arbitrum dependencies are available in a GitHub repository (non-anonymous link omitted).
+We have also deployed \cm on Ethereum's testnet Rinkeby with flattened (single file) source code of just the \cm base class and priority queue implementations.
+It is visible and can be interacted with here: \href{https://rinkeby.etherscan.io/address/0xffcaae2a77254b4cd72356b27377408ab31155b4}{[etherscan.io]}; while the Arbitrum variant is here: \href{https://explorer.offchainlabs.com/#/tx/0x500bee14a58d6d602a697cb858b78b5f071320a1d544c44fbea00048124b1ea8}{[explorer.offchainlabs.com]} (both links are anonymized).

### 2021-01-11 LaTeX-USENIX/sections/appendix.tex
more random edits

@@
 % !TEX root = ../main.tex
-
-\section{Clearing storage (extended discussion)}
-
-For space considerations, we kept the discussion in Section~\ref{sec:gasrefund} brief but the subject could use more explanation.
-First, we discuss the Ethereum's gas model--- (i) what are different gas parameters one needs to take into account when sending a transaction on the Ethereum blockchain, (ii) what is the gas refund, and (iii) and how it is calculated.
-Next, we discuss one challenge in \cm, \textit{clearing mappings}, that turns out to be more difficult than we initially expected.
-
-\subsection{Ethereum's Gas Model}
-
-DApps written in high-level programming languages are compiled and translated into a compact representation (called ‘bytecode’) to be further executed on the Ethereum virtual machine (EVM).
-When a transaction is executed, each opcode in the execution path accrues a fixed, pre-specified amount of gas.
-The function caller will pledge to pay a certain amount of ETH (typically quoted in units of \textbf{Gwei}, where \textit{wei} is the smallest transactional unit of ETH) per gas, and miners are free to choose to execute that transaction or ignore it.
-The function caller is charged for exactly the amount the transaction costs and they cap the maximum they are willing to be charged (\textit{gas limit})---if the cap is too low to complete the execution, the miner keeps the Gwei and reverts the state of the DApp (as if the function never ran).
-
-In Ethereum, transactions are bundled into blocks.
-A miner can include as many transactions (typically preferring transactions that bid the highest for gas) that can fit under a pre-specified \texttt{block gas limit}, which is algorithmically adjusted for every block.
-As of the time of writing, the limit is around 11M gas.
-
-\subsubsection{Gas Refunds.} In order to reconstruct the current state of Ethereum's EVM, a node must obtain a copy of every variable change since the genesis block (or a more recent `checkpoint' that is universally agreed to).
-For this reason, stored variables persist for a long time and, at first glance, it seems pointless to free up variable storage (and unclear what `free up' even means).
-Once the current state of the EVM is established by a node, it can forget about every historical variable changes and only concern itself with the variables that have non-zero value (as a byte-string for non-integers) in the current state (uninitialized variables in Ethereum have the value zero by default).
-Therefore, freeing up variables will reduce the amount of state Ethereum nodes need to maintain going forward.
-
-For this reason, some EVM operations cost a negative amount of gas.
-That is, the gas is refunded to the sender at the end of the transaction, however (1) the refund is capped at 50\% of the total gas cost of the transaction, and (2) the block gas limit applies to the pre-refunded amount (\ie a transaction receiving a full refund can cost up to 5.5M gas with a 11M limit).
-Negative gas operations include:
-
-\begin{itemize}
-
-\item \texttt{SELFDESTRUCT}.
-This operation destroys the contract that calls it and refunds its balance (if any) to a designated receiver address.
-\texttt{SELFDESTRUCT} operation does not remove the initial byte code of the contract from the chain.
-It always refunds 24,000 gas.
-For example, if a contract A stores a single non-zero integer and contract B stores 100 non-zero integers, the \texttt{SELFDESTRUCT} refund for both is the same (24,000 gas).
-
-\item \texttt{SSTORE}.
-This operation loads a storage slot with a value.
-Using \texttt{SSTORE} to load a zero into a storage slot means the nodes can start ignoring it (recall that all variables, even if uninitialized, have zero by default).
-Doing this refunds 15,000 gas per slot.
-
-\end{itemize}
-
-At the time of this writing, Ethereum transaction receipts only account for the \texttt{gasUsed}, which is the total amount of gas units spent during a transaction, and users are not able to obtain the value of the EVM's refund counter from inside the EVM~\cite{signer2018gas}.
-So in order to account for refunds in Tables~\ref{tab:PQUnitTests}, we calculate them manually.
-First we need to figure out exactly how much storage is being cleared or how many smart contracts are being destroyed, then we multiply these numbers by 24,000 and 15,000 respectively.
-
-\subsection{Clearing Mappings}
-
-Now let us put this theory into practice.
-In \cm, traders preload their account with ERC-20 tokens and/or ETH.
-\cm tracks what they are owed using a mapping called \texttt{totalBalance} and allows traders to withdraw their tokens at any time.
-However if a trader submits an order (\ie ask for their tokens), the tokens are committed and not available for withdrawal until the market closes (after which, the tokens are either transferred to the buyer or, if the trade is not executed, returned to the trader).
-Committed tokens are also tracked in a mapping called \texttt{unavailableBalance}.
-Sellers can request a token withdrawal up to their total balance subtracted by their unavailable balance.
-
-As the DApp runs \texttt{closeMarket()}, it starts matching the best bids to the best asks.
-As orders execute, \texttt{totalBalance} and \texttt{unavailableBalance} are updated.
-At a certain point, the bids and asks will stop matching in price.
-At this point, every order left in the order book cannot execute (because the priority queue sorts orders by price, and so orders deeper in the queue have worst prices than the order at the head of the queue).
-Therefore all remaining entries in \texttt{unavailableBalance} can be cleared.
-
-In Solidity, it is not possible to delete an entire mapping without individually zero-ing out each entry key-by-key.
-At the same time, it is wasteful to let an entire mapping sit in the EVM when it will never be referenced again.
-The following are some options for addressing this conflict.
-
-\begin{enumerate}
-
-\item \textbf{Manually Clearing the Mapping.} Since mappings cannot be iterated, a common design pattern used by DApp developers is to store keys in an array and iterate over the array to zero out each mapping and array entry.
-Clearing a mapping this way costs substantially more to clear than what is refunded (15,000 for each element).
-
-\item \textbf{Store the mapping in a separate DApp.} We could wrap the mapping inside its own DApp and when we are done with the mapping, we can run \texttt{SELFDESTRUCT} on the contract.
-This refunds us 24,000 gas which is less than the cost of deploying the extra contract.
-Additionally, every call to the mapping is more expensive because (1) it is an external function call, and (2) function calls  to be evaluated to ensure they only come from the market contract (if a mapping is a local variable, you get private access for free).
-
-\item \textbf{Leave and Ignore the Mapping.} The final option is to not clear the mapping and just create a new one (or create a new prefix for all mapping keys to reflect the new version of the mapping).
-Unfortunately, this is the most economical option for DApp developers even if it is the worst option for Ethereum nodes.
-
-\end{enumerate}
-
-Clearing storage is important for reducing EVM bloat.
-The Ethereum refund model should be considered further by Ethereum developers to better incentivize developers to be less wasteful in using storage.
 

### 2021-01-11 LaTeX-USENIX/sections/paper.tex
more random edits

@@
 
-\paragraph{Contributions.} We study fully on-chain markets through design and implementation with Solidity---a high-level programming language for Ethereum.
+\paragraph{Contributions.} We study fully on-chain markets through design and implementation with Solidity---a high-level programming language for Ethereum that is syntactically similar to Java~\cite{Ethereum41:online}.
 We choose Ethereum as a hostile environment for an order book: Ethereum is fully decentralized (hardest to regulate), network participation is open to anyone on the internet (strongest adversarial model), and, as a result, it is slow (a lower-bound benchmark).
@@
 
+\textblue{The only other paper similar to ours is TEX~\cite{khalil2019tex}. }
+
 % = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
@@
 
-\subsubsection{Enqueue Performance.} We implemented, deployed, and tested each priority queue using Truffle and Ganache.\footnote{Github: Link removed for anonymity.} We tried a variety of tests (including testing the full call market with each variant) with consistent results in performance.
+\paragraph{Enqueue Performance.} We implemented, deployed, and tested each priority queue using Truffle and Ganache.
+We tried a variety of tests (including testing the full call market with each variant) with consistent results in performance.
 A simple test to showcase the performance profile is shown in Figure~\ref{fig:random_insertion}.
@@
 \includegraphics[width=0.5\textwidth]{fig/random_insertion3.png}
-\caption{\footnotesize{Gas costs for enqueuing 50 random integers into five priority queue variants.
+\caption{Gas costs for enqueuing 50 random integers into five priority queue variants.
 For the x-axis, a value of 9 indicates it is the 9th integer entered in the priority queue.
-The y-axis is the cost of enqueuing in gas.}  \label{fig:random_insertion}}
+The y-axis is the cost of enqueuing in gas.
+\label{fig:random_insertion}}
 \end{figure}
@@
 
-\subsubsection{Dequeue Performance.} For each PQ variant storing 50 random integers, the \texttt{Dequeue()} function is iterated until the data structure is empty.
+\paragraph{Dequeue Performance.} For each PQ variant storing 50 random integers, the \texttt{Dequeue()} function is iterated until the data structure is empty.
 The total gas cost for fully dequeuing the priority queue variants is outlined in Table~\ref{tab:PQUnitTests}.
@@
 
-\subsubsection{Discussion.} Based on enqueuing, the heap variants are the cheapest in terms of gas, while based on dequeuing, the link list variants are the cheapest.
+\paragraph{Discussion.} Based on enqueuing, the heap variants are the cheapest in terms of gas, while based on dequeuing, the link list variants are the cheapest.
 This is in accordance with the theoretical worst-case time complexity for each.
@@
 
+\paragraph{Gas Refunds.} In order to reconstruct the current state of Ethereum's EVM, a node must obtain a copy of every variable change since the genesis block (or a more recent `checkpoint' that is universally agreed to).
+For this reason, stored variables persist for a long time and, at first glance, it seems pointless to free up variable storage (and unclear what `free up' even means).
+Once the current state of the EVM is established by a node, it can forget about every historical variable changes and only concern itself with the variables that have non-zero value (as a byte-string for non-integers) in the current state (uninitialized variables in Ethereum have the value zero by default).
+Therefore, freeing up variables will reduce the amount of state Ethereum nodes need to maintain going forward.
+
+For this reason, some EVM operations cost a negative amount of gas.
+That is, the gas is refunded to the sender at the end of the transaction, however (1) the refund is capped at 50\% of the total gas cost of the transaction, and (2) the block gas limit applies to the pre-refunded amount (\ie a transaction receiving a full refund can cost up to 5.5M gas with a 11M limit).
+Negative gas operations include:
+
+\begin{itemize}
+
+\item \texttt{SELFDESTRUCT}.
+This operation destroys the contract that calls it and refunds its balance (if any) to a designated receiver address.
+\texttt{SELFDESTRUCT} operation does not remove the initial byte code of the contract from the chain.
+It always refunds 24,000 gas.
+For example, if a contract A stores a single non-zero integer and contract B stores 100 non-zero integers, the \texttt{SELFDESTRUCT} refund for both is the same (24,000 gas).
+
+\item \texttt{SSTORE}.
+This operation loads a storage slot with a value.
+Using \texttt{SSTORE} to load a zero into a storage slot means the nodes can start ignoring it (recall that all variables, even if uninitialized, have zero by default).
+Doing this refunds 15,000 gas per slot.
+
+\end{itemize}
+
+At the time of this writing, Ethereum transaction receipts only account for the \texttt{gasUsed}, which is the total amount of gas units spent during a transaction, and users are not able to obtain the value of the EVM's refund counter from inside the EVM~\cite{signer2018gas}.
+So in order to account for refunds in Tables~\ref{tab:PQUnitTests}, we calculate them manually.
+First we need to figure out exactly how much storage is being cleared or how many smart contracts are being destroyed, then we multiply these numbers by 24,000 and 15,000 respectively.
+
+\paragraph{Refunds and PQs}
+
 One consequence of a linked list is that a new contract is created for every node in the list.
@@
 Alternatively, we can call \texttt{DELETE} on each mapping entry once we are done processing a node in the PQ.
-\textblue{Deleting a storage variable is identical to setting a non-zero variable to zero (\texttt{SSTORE} 0) that costs 20,000 gas but with 15,000 refunded---a net positive gas cost~\cite{wood2014ethereum}.} As it can be seen in the last two rows of Table~\ref{tab:cleaning}, leaving the data on chain is cheaper than cleaning it up.
+As it can be seen in the last two rows of Table~\ref{tab:cleaning}, leaving the data on chain is cheaper than cleaning it up.
 
@@
 
-\textblue{Reviewer's comment: DDOS against submitbid and submitask functions.
-Our answer: we put a cap on the number of orders submitted to the market so that we can always close.
-Also talk about bulk displacement attack (see reviewers comments)}
-
-%GitHub repo:  \footnote{\CallMarketRepo}
-
 \input{tables/functions.tex}
 
-\cm is intended as a module that developers can modify as they choose---thus we tried to simplify the design at every step to make it highly extensible but still functional without any extensions.
-A call market will open for a specified period of time during which it will accept orders, and these orders are added to a PQ.
+\cm is proof of concept code.
+We try to simplify the design at every step to make it highly extensible but still functional without any extensions.
+A call market will open for a specified period of time during which it will accept a capped number of orders (parameterized so that all orders can be processed), and these orders are added to a PQ.
 Our vision (discussed below) is the market would be open for a very short period of time, close, and then reopen immediately (\eg every other block).
-We keep the design simple by not allowing cancellations.
-Because cancellations require a second transaction, and front-running attacks apply to cancellation orders~\cite{eskandari2019sok}.Also, markets are relatively short-lived and orders simply expire when the market call period ends.
+We keep the design simple by not allowing cancellations which require a second transaction and front-running attacks apply to cancellation orders~\cite{eskandari2019sok}.
+As markets are relatively short-lived, orders simply expire when the market call period ends.
 
-Another simplifying assumption was to implement a \textit{collateralized} call market.
+Another simplifying assumption is to implement a \textit{collateralized} call market.
 We assume all trades are between ETH and an ERC20 token, all orders are pre-funded in the contract with ETH (for bids) and tokens (for asks), and once ETH or tokens are committed to an order, they cannot be withdrawn until the market closes.
@@
 
-\cm is written in 324 lines (SLOC) of Solidity,~\footnote{Github: linked removed for anonymity} a high level programming language that is syntactically similar to Java~\cite{Ethereum41:online}.
-We tested it with the Mocha testing framework (tests included in the codebase), as deployed using Truffle on Ganache-CLI to obtain our performance metrics.
-Table~\ref{tab:cm_functions} represents \cm's primary operations.
-\textblue{Mahsa: \cm's size of bytecode in bytes: 17212,  \cm's size of deployed in bytes: 10812, initialization and constructor code in bytes: 6400}
+\cm is open source and written in 350 lines (SLOC) of Solidity plus the priority queue (\eg a heap with dynamic array is 282 SLOC).
+Refer to the availability section at the end of the paper.
+We tested it with the Mocha testing framework using Truffle on Ganache-CLI to obtain our performance metrics.
+Once deployed, the bytecode of \cm is 10812 bytes plus the constructor code (6400 bytes) which is not stored.
+We cross-checked for vulnerabilities with \textit{Slither}\footnote{https://github.com/crytic/slither} and \textit{SmartCheck}\footnote{https://tool.smartdec.net} (it only fails some `informational' warnings (\eg a costly loop) that are intentional design choices).
+Table~\ref{tab:cm_functions} summarizes \cm's primary operations.
 
@@
 
-\paragraph{Code Security.} We used two security audit tools, \textit{Slither}\footnote{https://github.com/crytic/slither} and \textit{SmartCheck},\footnote{https://tool.smartdec.net} on \cm to find vulnerabilities and bad practices across 67 tests.
-\cm passes all tests except some `informational' warnings (\eg a costly loop) that are intentional design choices.
+\paragraph{Front-running.}
 
-\paragraph{Front-running.} \textblue{we have to revisit this section: talk about our front-running paper: there are various ways to prevent frontrunning, one is through confidentiality..., then cite this paper: 'TEX – A Securely Scalable Trustless Exchange'~\cite{khalil2019tex} }The primary motivation for using a call market, as opposed to a continuous-time order book, is to mitigate front-running attacks~\cite{clark2014decentralizing,eskandari2019sok,daian2019flash}.
+The primary motivation for using a call market, as opposed to a continuous-time order book, is to mitigate front-running attacks~\cite{clark2014decentralizing,eskandari2019sok,daian2019flash}.
 Consider a sequence of 100 orders submitted within a window of time to market A, and the same sequence is randomly shuffled and submitted to market B.
@@
 
-Potential for front-running still exists around ties on price and order cancellations (see below).
-Finally, \textit{displacement attacks}~\cite{eskandari2019sok} are possible where competitive orders are delayed long enough for the market to close without them.
 In a traditional call market, a market clearing price is chosen and all trades are executed at this price.
@@
 This does not actively hurt traders---they always receive the same price from their orders---and it removes any incentive to front-run these profits.
+
+Potential for front-running still exists around ties on price and order cancellations (both discussed in the next section).
+Finally, \textit{displacement attacks}~\cite{eskandari2019sok} are possible where competitive orders are delayed long enough for the market to close without them or the adversary fills up the current market (which caps the number of orders) to ensure other orders cannot be added.
+Both are expensive attacks.
 For all these reasons, we say \cm reduces front-running attacks but stop short of saying this issue is completely solved by \cm.
+
+\subsection{Cleaning Up}
+
+In \cm, traders preload their account with ERC-20 tokens and/or ETH.
+\cm tracks what they are owed using a mapping called \texttt{totalBalance} and allows traders to withdraw their tokens at any time.
+However if a trader submits an order (\ie ask for their tokens), the tokens are committed and not available for withdrawal until the market closes (after which, the tokens are either transferred to the buyer or, if the trade is not executed, returned to the trader).
+Committed tokens are also tracked in a mapping called \texttt{unavailableBalance}.
+Sellers can request a token withdrawal up to their total balance subtracted by their unavailable balance.
+
+As the DApp runs \texttt{closeMarket()}, it starts matching the best bids to the best asks.
+As orders execute, \texttt{totalBalance} and \texttt{unavailableBalance} are updated.
+At a certain point, the bids and asks will stop matching in price.
+At this point, every order left in the order book cannot execute (because the priority queue sorts orders by price, and so orders deeper in the queue have worst prices than the order at the head of the queue).
+Therefore all remaining entries in \texttt{unavailableBalance} can be cleared.
+
+In Solidity, it is not possible to delete an entire mapping without individually zero-ing out each entry key-by-key.
+At the same time, it is wasteful to let an entire mapping sit in the EVM when it will never be referenced again.
+The following are some options for addressing this conflict.
+
+\begin{enumerate}
+
+\item \textbf{Manually Clearing the Mapping.} Since mappings cannot be iterated, a common design pattern used by DApp developers is to store keys in an array and iterate over the array to zero out each mapping and array entry.
+Clearing a mapping this way costs substantially more to clear than what is refunded (15,000 for each element).
+
+\item \textbf{Store the mapping in a separate DApp.} We could wrap the mapping inside its own DApp and when we are done with the mapping, we can run \texttt{SELFDESTRUCT} on the contract.
+This refunds us 24,000 gas which is less than the cost of deploying the extra contract.
+Additionally, every call to the mapping is more expensive because (1) it is an external function call, and (2) function calls  to be evaluated to ensure they only come from the market contract (if a mapping is a local variable, you get private access for free).
+
+\item \textbf{Leave and Ignore the Mapping.} The final option is to not clear the mapping and just create a new one (or create a new prefix for all mapping keys to reflect the new version of the mapping).
+Unfortunately, this is the most economical option for DApp developers even if it is the worst option for Ethereum nodes.
+
+\end{enumerate}
+
+Clearing storage is important for reducing EVM bloat.
+The Ethereum refund model should be considered further by Ethereum developers to better incentivize developers to be less wasteful in using storage.
 
@@
 It is visible and can be interacted with here: \href{https://rinkeby.etherscan.io/address/0xffcaae2a77254b4cd72356b27377408ab31155b4}{[etherscan.io]}; while the Arbitrum variant is here: \href{https://explorer.offchainlabs.com/#/tx/0x500bee14a58d6d602a697cb858b78b5f071320a1d544c44fbea00048124b1ea8}{[explorer.offchainlabs.com]} (both links are anonymized).
+
+%GitHub repo:  \footnote{\CallMarketRepo}

### 2021-01-12 LaTeX-USENIX/sections/paper.tex
edits

@@
 
-\textbf{Gas.} Every transaction results in the participating nodes having to execute bytecode.
+\textbf{Ethereum's Gas Model.} Every transaction results in the participating nodes having to execute bytecode.
 This is not free.
@@
 
-\paragraph{Refunds and PQs}
+\paragraph{Refunds and PQs.}
 
@@
 This is a complicated and under-explored area of Ethereum in the research literature.
-For our own work, we strive to be good citizens of Ethereum and clean up to the extent that we can---thus all PQs in Table~\ref{tab:PQUnitTests} implement some cleanup and we select linked list with mapping and \texttt{DELETE} for \cm.
+For our own work, we strive to be good citizens of Ethereum and clean up to the extent that we can---thus all PQs in Table~\ref{tab:PQUnitTests} implement some cleanup.
 
@@
 \cm is proof of concept code.
-We try to simplify the design at every step to make it highly extensible but still functional without any extensions.
-A call market will open for a specified period of time during which it will accept a capped number of orders (parameterized so that all orders can be processed), and these orders are added to a PQ.
+We try to simplify the design at every step to make it an extensible base class but still functional without any extensions.
+A call market will open for a specified period of time during which it will accept a capped number of orders (\eg 100 orders---parameterized so that all orders can be processed), and these orders are added to a PQ.
 Our vision (discussed below) is the market would be open for a very short period of time, close, and then reopen immediately (\eg every other block).
@@
 
-\subsection{Security Analysis} \label{sec:front}
-
-\paragraph{Front-running.}
+\subsection{Front-running} \label{sec:front}
 
@@
 
-\subsection{Cleaning Up}
+\subsection{Cleaning Up Revisted}
 
-In \cm, traders preload their account with ERC-20 tokens and/or ETH.
+Beyond the cleaning up issues with priority queues, \cm also uses mappings with each market.
+Traders preload their account with ERC-20 tokens and/or ETH.
 \cm tracks what they are owed using a mapping called \texttt{totalBalance} and allows traders to withdraw their tokens at any time.
@@
 
- \textblue{ We need to find a home for this: another solution to reopen the market immediately after the closing call is to have many similar contracts for the market and  a factory contract to guide users to the correct address (from the reviewer's comment)}
+%\textblue{ We need to find a home for this: another solution to reopen the market immediately after the closing call is to have many similar contracts for the market and  a factory contract to guide users to the correct address (from the reviewer's comment)}
 
-As a module, we tried to keep \cm as simple as possible, and allow customizations and extensions as appropriate. We discuss potential modifications here.
+\cm is designed as base class that can be extended and customized. We discuss potential modifications here.
 

### 2021-01-12 LaTeX-USENIX/sections/abstract.tex

--- 2020-09-23 LaTeX/sections/abstract.tex
@@
 \begin{abstract}
-Order-driven exchanges on Ethereum tend to operate in a fully centralized fashion, or with some functionality performed on-chain (\eg loading accounts, order cancelation) and some off-chain functionality (\eg matching orders).
-Fully on-chain solutions have a superior threat model and were experimented with in the early days of Ethereum, but they have been largely abandoned for performance reasons.
-As block\-chain performance continues to improve (both in research and in practice) and on-chain dealer-based exchanges like Uniswap (an alternative to order-based exchanges) rise in popularity, it seems to be an ideal time to revisit the idea of a fully on-chain order-driven exchange and benchmark what is possible performance-wise.
-We design and optimize an Ethereum-based call market exchange, \cm, and conduct a variety of experiments to show the current benchmark is around one hundred trade executions per block.
-We also explore numerous extensions for further improvements, including a variant using off-chain execution (`rollups').
+
+When consumers trade financial products, they typically use well-identified service providers that operate under government regulation.
+In theory, decentralized platforms like Ethereum can offer trading services `on-chain' without an obvious entry point for regulators.
+Fortunately for regulators, most trading volume in blockchain-based assets is still on centralized service providers for performance reasons.
+However this leaves the following research questions we address in this paper: (i) is secure trading (\ie resistant to front-running and price manipulation) even feasible as a fully `on-chain' service on a public blockchain, (ii) what is its performance benchmark, and (iii) what is the performance impact of novel techniques (\eg `rollups') in closing the performance gap?
+
+To answer these questions, we `learn by doing' and custom design an Ethereum-based call market (or batch auction) exchange, \cm, with favourable security properties.
+We conduct a variety of optimizations and experiments to demonstrate that this technology cannot expect to exceed a few hundred trade executions per block (\ie ~13s window of time).
+However this can be scaled dramatically with off-chain execution that is not consumer-facing.
+We also illustrate, with numerous examples throughout the paper, how blockchain deployment is full of nuances that make it quite different from developing in better understood domains (\eg cloud-based web applications).
+
 \end{abstract}

### 2021-01-12 Code/New-Truffle/test/17_Worst_Case_Matching_test.js
changed the test files accordingly

@@ -147,14 +147,9 @@ describe('CallMarket', function(accounts) {
         console.log(array.length,'bids have been succsessfully submitted');
         console.log('********************************************');
     });
-    //*******************Test 7*************************
-    it('should close the market on the Dapp Token', async() => {
-        const CallMarketInstance = await CallMarket.deployed(); 
-        await CallMarketInstance.closeMarket();
-        
-    });
+
     
-    //*******************Test 8*************************
+    //*******************Test 7*************************
     // it('should return the Gasestimate for the match() function', async() => {
         
     //     const CallMarketInstance = await CallMarket.deployed();
@@ -163,12 +158,12 @@ describe('CallMarket', function(accounts) {
     //     console.log('********************************************');
     // });  
 
-    //*******************Test 9*************************
-    it('should match the orders', async() => {
+    //*******************Test 8*************************
+    it('should close the market and match the orders', async() => {
         
         const CallMarketInstance = await CallMarket.deployed();
 
-        const receipt = await  CallMarketInstance.matchOrders();
+        const receipt = await  CallMarketInstance.closeMarket();
         const gasUsed = receipt.receipt.gasUsed;
         console.log(`GasUsed for Matching the orders: ${receipt.receipt.gasUsed}`); 
         //console.log('the tx receipt is:', receipt);
@@ -176,7 +171,7 @@ describe('CallMarket', function(accounts) {
     });//.timeout(9000000000000000000);     
     
  
-    //*******************Test 10*************************
+    //*******************Test 9*************************
     it('should print how many matches happened', async() => {
         const CallMarketInstance = await CallMarket.deployed(); 
         
@@ -187,7 +182,7 @@ describe('CallMarket', function(accounts) {
 
     });
     
-    // //*******************Test 11*************************
+    // //*******************Test 10*************************
     // it('should call the claim functions', async() => {
         
     //     const CallMarketInstance = await CallMarket.deployed(); 
@@ -199,7 +194,7 @@ describe('CallMarket', function(accounts) {
     //     await CallMarketInstance.claimTokens (tokenaddress, 14999, {from: accounts[0]});
     //     await CallMarketInstance.claimEther (9999999997, {from: accounts[1]});
     // });
-    // //*******************Test 12*************************
+    // //*******************Test 11*************************
     //  it('should show the Ether balances of traders after the trade', async() => {
     //     //const CallMarketInstance = await CallMarket.deployed(); 
     //     accounts = await web3.eth.getAccounts();

### 2021-01-12 Code/New-Truffle/test/18_Average_Case_Matching_test.js

@@ -134,17 +134,12 @@ describe('CallMarket', function(accounts) {
         console.log(array.length,'bids has been succsessfully submitted');
  
     });
-    //*******************Test 6*************************
-    it('should close the market on the Dapp Token', async() => {
-        const CallMarketInstance = await CallMarket.deployed(); 
-        await CallMarketInstance.closeMarket();
-        
-    });
 
-    //*******************Test 7*************************
-    it('should match the orders', async() => {
+
+    //*******************Test 6*************************
+    it('should close the market and match the orders', async() => {
         const CallMarketInstance = await CallMarket.deployed(); 
-        const receipt = await CallMarketInstance.matchOrders();
+        const receipt = await CallMarketInstance.closeMarket();
         console.log('********************************************');
         const gasUsed = receipt.receipt.gasUsed;
         console.log(`GasUsed for worst case matching is: ${receipt.receipt.gasUsed}`);

### 2021-01-12 LaTeX-USENIX/sections/paper.tex
more edits

@@
 
-\textblue{The only other paper similar to ours is TEX~\cite{khalil2019tex}. }
+The most similar academic work to this paper is the TEX exchange~\cite{khalil2019tex}.
+TEX is also an implementation of an orderbook however it uses on-chain and off-chain components, and does not answer our research question of how feasible an on-chain orderbook is.
+It is similar to our variant with roll-ups however it uses a different architecture where users interact directly with the off-chain component (a regulatory hook).
+The other overlap is the focus on resisting front-running attacks.
+In a recent survey on front-running attacks in blockchain~\cite{eskandari2019sok}, three solutions are proposed.
+One solution is to provide confidentiality over the content of orders which is the approach taken by TEX.
+The main downside is that honest traders cannot submit their orders and leave, they must interact in a second round to reveal their orders.
+The second solution is to sequence transactions according to some rule, either at the protocol level~\cite{MZGA20} or as a third party service~\cite{Kla20} (a regulatory hook).
+These are very recent works and are not available for experimentation on Ethereum yet (although Chainlink has announced an intention\footnote{A.
+Juels.
+\href{https://blog.chain.link/chainlink-fair-sequencing-services-enabling-a-provably-fair-defi-ecosystem/}{blog.chain.link}, 11 Sep 2020.}).
+The third solution is to design the service in a way that front-running attacks are not profitable---this is the approach we take here.
+
+% https://eprint.iacr.org/2020/269.pdf
+% Wendy, the Good Little Fairness Widget – Achieving Order Fairness for Blockchains
 
@@
 Once deployed, the bytecode of \cm is 10812 bytes plus the constructor code (6400 bytes) which is not stored.
-We cross-checked for vulnerabilities with \textit{Slither}\footnote{https://github.com/crytic/slither} and \textit{SmartCheck}\footnote{https://tool.smartdec.net} (it only fails some `informational' warnings (\eg a costly loop) that are intentional design choices).
+We cross-checked for vulnerabilities with \textit{Slither}\footnote{https://github.com/crytic/slither} and \textit{SmartCheck}\footnote{https://tool.smartdec.net} (it only fails some `informational' warnings that are intentional design choices---\eg a costly loop).
 Table~\ref{tab:cm_functions} summarizes \cm's primary operations.
@@
 In a traditional call market, a market clearing price is chosen and all trades are executed at this price.
-All bids made at a higher price will receive the assets for the lower clearing price (and conversely for lower ask prices): this is called a price improvement.
+All bids made at a higher price will receive the assets for the lower clearing price (and conversely for lower ask prices): this is called a \textit{price improvement}.
 A miner about to mine on a set of transactions, including its own orders, could drop other traders' orders to maximize its own price improvement.
 For this reason, in \cm, all price improvements are given to the miner (using \texttt{block.coinbase.transfer()}).
-This does not actively hurt traders---they always receive the same price from their orders---and it removes any incentive to front-run these profits.
+This does not actively hurt traders---they always receive the same price that they quote in their orders---and it removes any incentive for miners to front-run these profits.
 
@@
 
-Beyond the cleaning up issues with priority queues, \cm also uses mappings with each market.
+Beyond the cleaning up issues with priority queues in Section~\ref{sec:gasrefund}, \cm also uses mappings with each market.
 Traders preload their account with ERC-20 tokens and/or ETH.
@@
 
-\subsection{Token Divisibility and Volumes}
+\subsection{Token Divisibility and Ties}
 
-\textblue{Mahsa: Partial Filling: we ran the worst case matching test with random volumes between 1 and 10 on linked list with mapping (which handles maximum pairs of 80 orders with single volumes).
-With partial filling, it can clear the book that contains 70 pairs at max (which on average ends up being ~118 trades).
-SO it is moderately more expensive}
-
-We implemented a very simple market where orders all have the same volume: 1 token.
-Traders submit multiple orders to increase volume.
-To extend orders with a volume field, it must first be determined if the token is non-divisible or divisible (and to what precision).
-In this case, \texttt{closeMarket()} needs to look at multiple bids to fulfill a single ask (and vice-versa) and declare its trading rules on partial fills.
-We also simplify the market rules around ties on price: we execute them in a FIFO manner (breaking front-running resistance for ties on prices).
-A common trading rule (that does resist front-running) is to fill ties in proportion to their volume (\ie \textit{pro rata} allocation)\footnote{If Alice and Bob bid the same price for 100 tokens and 20 tokens respectively, and there are only 60 tokens left in marketable asks, Alice receives 50 and Bob 10.} however this approach is also contingent on the divisibility of tokens.
+When executing trades, if the volume of the current best bid does not match the best ask, the larger order is partially filled and the remaining volume is considered against the next best order.
+In \cm, tokens are assumed to be divisible.
+We simplify the market rules around ties on price: we execute them in a FIFO manner (breaking front-running resistance for ties on prices).
+A common trading rule (that does resist front-running) is to fill ties in proportion to their volume (\ie \textit{pro rata} allocation)\footnote{If Alice and Bob bid the same price for 100 tokens and 20 tokens respectively, and there are only 60 tokens left in marketable asks, Alice receives 50 and Bob 10.} however this approach does not always work.
 Consider the following corner-case: 3 equally priced bids of 1 non-divisible token and 1 ask at the same price.
@@
 
-As a simple module, \cm is a one-shot market.
+As a simple base class, \cm is a one-shot market.
 However it can be extended to re-open with a clean order book after \texttt{closeMarket()} is run.
@@
 Someone needs to call the \texttt{closeMarket()} for every block (we return to who this is next) but the market will only work as intended if miners execute this function after every \texttt{submitBid()} and \texttt{submitAsk()} invocation.
-Since price improvements are paid to the miners, the miner is incentivized to run \texttt{closeMarket()} last to make the most profit.
-Perhaps in a world where these markets became immensely popular, miners would actually do this, but as it stands, miners do not generally search for the transaction ordering that nets them the most profit.
+Since price improvements are paid to the miners, the miner is actually incentivized to run \texttt{closeMarket()} last to make the most profit.
+This pattern is called miner extractable value (MEV)~\cite{daian2019flash} and is usually considered in the context of attacks.
+However in our case, MEV is a feature.
+Efficient algorithms for miners to automatically find MEV opportunities is an open research problem.
 
 A close alternative is to allow markets to open and close on different blocks.
-Specifically, the \texttt{closeMarket()} function calls \texttt{openMarket()} as a subroutine and sets two modifiers: orders are only accepted in the block immediately after the current block (\ie the block that executes the \texttt{closeMarket()}) and \texttt{closeMarket()} cannot be run again until two blocks after the current block.
+In this alternative, the \texttt{closeMarket()} function calls \texttt{openMarket()} as a subroutine and sets two modifiers: orders are only accepted in the block immediately after the current block (\ie the block that executes the \texttt{closeMarket()}) and \texttt{closeMarket()} cannot be run again until two blocks after the current block.
 
@@
 There are actually two issues here: the issue of scheduling the function call and the issue of paying for it.
-For scheduling the function call, we can do one of the following: rely on market participants, who are eager to trade, to reopen the market, offer a bounty to reopen the market, or use an external service like Ethereum Alarm Clock.\footnote{\url{https://ethereum-alarm-clock-service.readthedocs.io/}} Next we consider the second issue of who pays to close the market.
+For scheduling the function call, we can do one of the following: rely on market participants, who are eager to trade, to reopen the market, offer a bounty to reopen the market, or use an external service like Ethereum Alarm Clock (which creates a regulatory hook).\footnote{\url{https://ethereum-alarm-clock-service.readthedocs.io/}} Next we consider the second issue of who pays to close the market.
 
@@
 
-It is unlikely that a mining software will become aware of specific DApps, but miners are paid all price improvements in the market and so it is possible that running \texttt{closeMarket()} would pay for itself.
-However we consider two other (more realistic) scenarios.
-One solution requires a modified closing function, \texttt{closeMarket(n)}, that only processes $n$ orders at a time (until the order book is empty).
+As miners are paid all price improvements in the market, it is possible that a miner might run \texttt{closeMarket()} and it would pay for itself.
+However we consider two other scenarios that do not assume miners can automatically find MEV opportunities.
+One solution requires a modified closing function, \texttt{closeMarket(n)}, that only processes $n$ orders at a time until the order book is empty (this is sensible design in any case to safeguard against the orderbook from locking up because the number of orders exceeds the gas limit to process them).
 Once the time window for submitting orders is past, a new market is created (without settling the previous market).
@@
 This is a better solution, although not perfect: \texttt{closeMarket()} cost does not follow a tight linear increase with the number of orders, and gas prices vary over time which could render the bounty insufficient for offsetting the \texttt{closeMarket()} cost.
-However an interested third party (such as the token issuer for a given market) might bailout the market when it halts on \texttt{closeMarket()} to facilitate further trading.
-If the contract can pay for its own functions, an interested party can also arrange for a commercial service (\eg any.sender\footnote{\url{https://github.com/PISAresearch/docs.any.sender}}) to relay the \texttt{closeMarket()} function call on Ethereum (an approach called \textit{meta-transactions}).
-
+However an interested third party (such as the token issuer for a given market) might occasionally bailout the market when it halts on \texttt{closeMarket()} to facilitate further trading.
+If the contract can pay for its own functions, an interested party can also arrange for a commercial service (\eg any.sender\footnote{\url{https://github.com/PISAresearch/docs.any.sender}}) to relay the \texttt{closeMarket()} function call on Ethereum (an approach called \textit{meta-transactions}) which introduces another regulatory hook.
 %= = = = = =  = =  =  Rollups=  = = = = = = = = =%
@@
 \label{sec:rollups}
+
+\textblue{Re-align this section}
 
@@
 By contrast to all of these, with an on-chain orderbook, you just deploy the code alongside your token and trading is immediately supported.
+This should concern regulators.
 Even if it is too slow today, there is little reason for developers not to offer it as a fallback solution that accompanies every token.
 With future improvements to blockchain scalability, it could become the defacto trading method.
+
+It may seem paradoxical or unethical to build for regulators exactly what they worry about, however we agreed that it was too difficult to answer our research questions without actual implementation and experimentation.
+\cm is proof of concept code that implements only enough to understand the feasibilty of on-chain trading and we release the code for reproducibility.
+However it is not production code, it is unpolished, it has no UI, and we have no intention of promoting it for adoption.
+Finally, by understanding the `pain points' in the design, we found we were constantly tugged toward centralized components (Ethereum alarm clock, meta-transactions, roll-up servers, \etc) which could serve as regulatory hooks even if the service is mainly on-chain.
 
@@
 We have also deployed \cm on Ethereum's testnet Rinkeby with flattened (single file) source code of just the \cm base class and priority queue implementations.
-It is visible and can be interacted with here: \href{https://rinkeby.etherscan.io/address/0xffcaae2a77254b4cd72356b27377408ab31155b4}{[etherscan.io]}; while the Arbitrum variant is here: \href{https://explorer.offchainlabs.com/#/tx/0x500bee14a58d6d602a697cb858b78b5f071320a1d544c44fbea00048124b1ea8}{[explorer.offchainlabs.com]} (both links are anonymized).
+It is visible and can be interacted with here: \href{https://rinkeby.etherscan.io/address/0x0d91de29c531d074853a5cef7cf9dfeb9c6ec4e0}{[etherscan.io]}; while the Arbitrum variant is here: \href{https://explorer.arbitrum.io/#/tx/0x1828d7eb6a7a9b9ec479f07e8149c6172bb89a101571963b5cf690132bdf009b}{[explorer.offchainlabs.com]} (both links are anonymized).
 

### 2021-01-12 LaTeX-USENIX/sections/paper.tex
candidate for submission

@@
 This positions \cm as a feasible design for only a narrow set of markets today (low liquidity, small number of traders) which is good news for regulators.
-However we caution that the technology is likely to improve vastly in the coming years and we demonstrate one avenue for improvement through `roll-ups'~\cite{kalodner2018arbitrum}.
-While roll-ups use centralized servers and are thus no fully on-chain, we consider an architecture where these servers only interface with Ethereum and never interface directly with users, which side-steps the regulatory hook that is present in many other server-augmented trading platforms (including both decentralized exchanges like 0x and EtherDelta, and roll-ups like Loopring, all described below).
+However we caution that the technology is likely to improve vastly in the coming years and we demonstrate one avenue for improvement through `rollups'~\cite{kalodner2018arbitrum}.
+While rollups use centralized servers and are thus no fully on-chain, we consider an architecture where these servers only interface with Ethereum and never interface directly with users, which side-steps the regulatory hook that is present in many other server-augmented trading platforms (including both decentralized exchanges like 0x and EtherDelta, and rollups like Loopring, all described below).
 
@@
 TEX is also an implementation of an orderbook however it uses on-chain and off-chain components, and does not answer our research question of how feasible an on-chain orderbook is.
-It is similar to our variant with roll-ups however it uses a different architecture where users interact directly with the off-chain component (a regulatory hook).
+It is similar to our variant with rollups however it uses a different architecture where users interact directly with the off-chain component (a regulatory hook).
 The other overlap is the focus on resisting front-running attacks.
@@
 
-\cm is designed as base class that can be extended and customized. We discuss potential modifications here.
+%\cm is designed as base class that can be extended and customized. We discuss potential modifications here.
 
@@
 If the contract can pay for its own functions, an interested party can also arrange for a commercial service (\eg any.sender\footnote{\url{https://github.com/PISAresearch/docs.any.sender}}) to relay the \texttt{closeMarket()} function call on Ethereum (an approach called \textit{meta-transactions}) which introduces another regulatory hook.
-%= = = = = =  = =  =  Rollups=  = = = = = = = = =%
-
-\subsection{Off-chain Closing}
-\label{sec:rollups}
-
-\textblue{Re-align this section}
-
-We have two main motivations for designing an \textit{on-chain} order book: (1) the trust model is superior to partially/fully centralized solutions, and (2) \cm can be deployed without any delay or other arrangements.
-We have relaxed (2) already by considering services like Ethereum Alarm Clock and any.sender to facilitate easy market closings.
-In this section, we present a variant that only provides (1) (however one that can be deployed without any other market stakeholders).
-
-A function can be computed off-chain and the new state of the DApp, called a \textit{rollup}, is written back to the blockchain, accompanied by either (1) a proof that the function was executed correctly, or (2) a dispute resolution process that can resolve, on-chain, functions that are not executed correctly (\eg Arbitrum~\cite{kalodner2018arbitrum}).
-In the case of (1), validating the proof must be cheaper than running the function itself.
-There are two main approaches to (1): the first is to use cryptographic proof techniques (\eg SNARKS~\cite{BCGTV13,GGPR13} and variants~\cite{BBHR19}), and the second is to execute the function in a trusted execution environment (TEE; \eg Intel SGX) and validate the TEE's quote on-chain (\eg Ekiden~\cite{cheng2019ekiden}).\footnote{The TEE-based approach is mired by recent attacks on SGX~\cite{SGX1,SGX2,SGX3,SGX4}, however these attacks do not necessarily apply to the specifics of how SGX is used here, and safer TEE technologies like Intel TXT (\cf~\cite{ZBC+19}) can be substituted.}
-
-We implemented a variant of \cm using rollups on Arbitrum.\footnote{\url{https://offchainlabs.com} for more current details than the 2018 \textit{USENIX Security} paper~\cite{kalodner2018arbitrum}.} In this model, the token issuer (or other interested party) will run a dedicated server to watch Ethereum for function invocations submitted and sequenced on-chain, perform the function call off-chain, and write the resultant state on-chain.
-Anyone capable of running EVM code can verify the result.
-If it is incorrect, a dispute can be filed (with the correct state) and an on-chain correction will be made.
-With or without disputes, participants that validate the function calls for themselves can proceed knowing that the correct state will eventually be finalized.
-
-In our \cm variant with rollups, the token issuer does all the computation (both enqueuing and dequeuing).
-Thus we switch the priority queue to use a heap with dynamic array, which balances the expense of both operations (instead of optimizing for dequeuing in \texttt{closeMarket()}).
-Recall that on-chain, such a priority queue can only match 38 pairs at a cost of 5,372,679 gas.
-With roll-ups, 38 pairs cost 38,863 gas.
-As the pairs increase, the cost is essentially constant (\eg 1000 pairs cost 38,851 as opposed to 457,326,935 on-chain).
-Submitting an order costs 39,169 gas on average as opposed to 207,932 on-chain.
-
-Our \cm variant is not the first rollup-based order book.
-Loopring 3.0\footnote{\url{https://loopring.org}} offers a continuous-time order book.
-The primary difference is that orders in Loopring 3.0 are submitted off-chain to the operator directly, whereas our variant requires on-chain submission.
-While on-chain submission is hampered by Ethereum's block limits, the threat model of reordering transactions is well-understood and our call market design mitigates most front-running attacks.
-In Loopring 3.0, the rollup proof does not ensure that the exchange did not reorder transactions, which is particularly problematic in a continuous-time order book.
-In short, we provide better protection against a malicious exchange while Loopring 3.0 provides even better performance.
 
@@
 
+%= = = = = =  = =  =  Rollups=  = = = = = = = = =%
+
+\section{\cm Variant with Off-chain Closing}
+\label{sec:rollups}
+
+We have avoided augmenting \cm with centralized components and third party services as our research question concerns the feasibility of a system with a minimum of regulatory hooks.
+However from a regulatory stance, there is a big difference between an architecture where the centralized component is publicly visible and interacted with by users (\eg most DEXes, rollup architectures like Loopring, and commit-chain solutions like TEX).
+We briefly consider an alternative design that is almost as difficult to regulate as a fully on-chain solution.
+In this design, an off-chain component is introduced to boost performance but it only interacts with the Ethereum network and never directly with traders.
+Traders still only interact with Ethereum.
+
+A function can be computed off-chain and the new state of the DApp, called a \textit{rollup}, is written back to the blockchain, accompanied by either (1) a proof that the function was executed correctly, or (2) a dispute resolution process that can resolve, on-chain, functions that are not executed correctly (\eg Arbitrum~\cite{kalodner2018arbitrum}).
+In the case of (1), validating the proof must be cheaper than running the function itself.
+There are two main approaches to (1): the first is to use cryptographic proof techniques (\eg SNARKS~\cite{BCGTV13,GGPR13} and variants~\cite{BBHR19}), and the second is to execute the function in a trusted execution environment (TEE; \eg Intel SGX) and validate the TEE's quote on-chain (\eg Ekiden~\cite{cheng2019ekiden}).\footnote{The TEE-based approach is mired by recent attacks on SGX~\cite{SGX1,SGX2,SGX3,SGX4}, however these attacks do not necessarily apply to the specifics of how SGX is used here, and safer TEE technologies like Intel TXT (\cf~\cite{ZBC+19}) can be substituted.}
+
+We implemented a variant of \cm using rollups on Arbitrum.\footnote{\url{https://offchainlabs.com} for more current details than the 2018 \textit{USENIX Security} paper~\cite{kalodner2018arbitrum}.} In this model, the token issuer (or other interested party) will run a dedicated server to watch Ethereum for function invocations submitted and sequenced on-chain, perform the function call off-chain, and write the resultant state on-chain.
+Anyone capable of running EVM code can verify the result.
+If it is incorrect, a dispute can be filed (with the correct state) and an on-chain correction will be made.
+With or without disputes, participants that validate the function calls for themselves can proceed knowing that the correct state will eventually be finalized.
+
+In our \cm variant with rollups, the token issuer does all the computation (both enqueuing and dequeuing).
+Thus we switch the priority queue to use a heap with dynamic array, which balances the expense of both operations (instead of optimizing for dequeuing in \texttt{closeMarket()}).
+Recall that on-chain, such a priority queue can only match 38 pairs at a cost of 5,372,679 gas.
+With rollups, 38 pairs cost 38,863 gas.
+As the pairs increase, the cost is essentially constant (\eg 1000 pairs cost 38,851 as opposed to 457,326,935 on-chain).
+Submitting an order costs 39,169 gas on average as opposed to 207,932 on-chain.
+
+Our \cm variant is not the first rollup-based order book.
+Loopring 3.0\footnote{\url{https://loopring.org}} offers a continuous-time order book.
+The primary difference is that orders in Loopring 3.0 are submitted off-chain to the operator directly, whereas our variant uses on-chain submission so that the rollup server does not need to be publicly reachable.
+Loopring 3.0 can operate near high frequency trading as order submission is unhampered by Ethereum, however its  rollup proof does not ensure that the exchange did not reorder transactions, which is particularly problematic in a continuous-time order book.
+Traders who prioritize trade fairness might opt for a solution like our variant, while traders who want speed would vastly prefer the Loopring architecture which offers near-CEX speed while being non-custodial.
+Loopring leaves a regulatory hook whereas our variant could be nearly as difficult to regulate as a fully on-chain solution if the rollup server was kept anonymous: Ethereum and Arbitrum themselves would be the only regulatory hooks.
+
 % = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
@@
 However it is not production code, it is unpolished, it has no UI, and we have no intention of promoting it for adoption.
-Finally, by understanding the `pain points' in the design, we found we were constantly tugged toward centralized components (Ethereum alarm clock, meta-transactions, roll-up servers, \etc) which could serve as regulatory hooks even if the service is mainly on-chain.
+Finally, by understanding the `pain points' in the design, we found we were constantly tugged toward centralized components (Ethereum alarm clock, meta-transactions, rollup servers, \etc) which could serve as regulatory hooks even if the service is mainly on-chain.
 

### 2021-01-12 LaTeX-USENIX/sections/paper.tex
proof reading

@@
 They are concerned by their limited ability to intervene when trading is conducted on decentralized networks that, like Ethereum, run on the open internet.
-While order-driven exchange could theoretically happen `on-chain' and were experimented with in the early days of Ethereum, they have been largely abandoned for performance reasons in favour of running on centralized servers---or, at least, with core functionality performed off-chain (\eg matching orders) while other aspects (\eg loading accounts, order cancellation) might be performed on-chain.
+Order-driven trading can happen fully `on-chain' and this was experimented with in the early days of Ethereum, but it has been largely abandoned for performance reasons in favour of running on centralized servers.
+More specifically, the core functionality is performed off-chain (\eg matching orders) while other aspects (\eg loading accounts, order cancellation) might be performed on-chain.
 In this world, company names, employees, addresses, and publicly addressable servers all provide regulatory hooks.
 
-Our research group has collaborated with our jurisdiction's financial regulator (name withheld for peer-review) to help them forecast how trading can be impacted by blockchain technology.
+Our research group is actively collaborating with our jurisdiction's financial regulator (name withheld for peer-review) to help them forecast how trading can be impacted by blockchain technology.
 This paper addresses their concerns about the feasibility of a `worst-case scenario' where a trading platform is anonymously deployed on a public blockchain, like Ethereum, and runs autonomously without any further intervention from an externally visible entity.
 Such a design appears feasible but is considered too slow.
-Together, we agreed it is a very good time to do a deep dive into understanding precisely \textit{how slow} for the following reasons: (1) public blockchains are becoming faster (both in theory and in practice) providing future efficiency gains for on-chain trading, (2) demand for on-chain trading is exemplified by the recent popularity of dealer quote-based trading like Uniswap and Curve Finance (reviewed below), and (3) stablecoins have become popular and allow on-chain trading with pricing in USD, alleviating another regulatory hook: the need for platforms to maintain traditional accounts for holding governmental currency and interface with the banking system.
+Together, we agreed it is a very good time to do a deep dive into understanding precisely \textit{how slow} for the following reasons: (1) public blockchains are becoming faster (both in theory and in practice) providing future efficiency gains for on-chain trading, (2) demand for on-chain trading is exemplified by the recent popularity of dealer quote-based trading like Uniswap and Curve Finance (reviewed below), and (3) stablecoins have become popular and allow on-chain trading with pricing in USD, alleviating another regulatory hook: the need for platforms to maintain traditional accounts for holding governmental currency and interfacing with the banking system.
 
@@
 We choose Ethereum as a hostile environment for an order book: Ethereum is fully decentralized (hardest to regulate), network participation is open to anyone on the internet (strongest adversarial model), and, as a result, it is slow (a lower-bound benchmark).
-Generally if an application is feasible on Ethereum, it will also be feasible and only run faster on a private (or permissioned) blockchain (\eg Hyperledger), which is operated by authorized network nodes (a regulatory hook).
+Generally if an application is feasible on Ethereum, it will also be feasible and only run faster on a private (or permissioned) blockchain (\eg Hyperledger), which is a blockchain operated by authorized network nodes only, generally visible to regulators.
 
@@
 
-While Solidity and EVM are like many common programming languages, they also have quirks that require experimentation to best optimize performance (\eg factoring in the gas costs of operations, gas refunds, limits to Solidity's object oriented design, clearing mappings).
+While Solidity and its compiled bytecode is like many common programming languages, it also has quirks that require experimentation to best optimize performance (\eg factoring in the gas costs of operations, gas refunds, limits to Solidity's object oriented design, clearing mappings, \etc).
 We test five priority queues---the core data structure of the call market---and various options for cleaning up our data once finished with it.
@@
 However we caution that the technology is likely to improve vastly in the coming years and we demonstrate one avenue for improvement through `rollups'~\cite{kalodner2018arbitrum}.
-While rollups use centralized servers and are thus no fully on-chain, we consider an architecture where these servers only interface with Ethereum and never interface directly with users, which side-steps the regulatory hook that is present in many other server-augmented trading platforms (including both decentralized exchanges like 0x and EtherDelta, and rollups like Loopring, all described below).
+While rollups use centralized servers and are not fully on-chain, an architecture where these servers only interface with Ethereum and never interface directly with users is still concerning, as it side-steps the regulatory hook that is present in many other server-augmented trading platforms.
 
@@
 A public blockchain is an open peer-to-peer network that maintains a set of transactions without a single entity in charge.
-Transactions can concern payments.
-In Ethereum, they represent the bytecode of user-written decentralized applications (DApps) to be stored on the blockchain; and the functional calls made to the DApp.
-Every functional call is a validated by all honest, participating nodes to have been correctly executed; a property that is robust against a fraction of faulty and malicious network nodes (or more precisely, their accumulated computational power).
+In Ethereum, \emph{transactions} encode the bytecode of user-written \emph{decentralized applications} (DApps) to be stored on the blockchain; and the function calls made to the DApp.
+Every execution of every function call is a validated by all honest, participating nodes to correct; a property that is robust against a fraction of faulty and malicious network nodes (or more precisely, their accumulated computational power).
 Once transactions are agreed upon, all honest participants will have identical sets of transactions in the same order.
-For Ethereum, this is conceptualized as the current state of a large virtual machine (EVM) that is running many DApps.
+For Ethereum, this is conceptualized as the current state of a large \emph{virtual machine (EVM)} that is running many DApps.
 
 Transactions are broadcast by users to the blockchain network where they are propagated to all nodes.
-Nodes that choose to `mine' will collect transactions (in the order of their choosing) into a block, and will attempt to have the network reach a consensus that their block should be added to the set (or chain) of previous blocks.
+Nodes that choose to \emph{mine} will collect transactions (in the order of their choosing) into a block, and will attempt to have the network reach a consensus that their block should be added to the set (or chain) of previous blocks.
 A transaction is considered finalized once consensus on its inclusion has held for several additional blocks.
@@
 This is not free.
-When a transaction is executed, each opcode in the execution path accrues a fixed, pre-specified amount of gas.
-The function caller will pledge to pay a certain amount of Ethereum's internal currency ETH (typically quoted in units of Gwei which is one billionth of an ETH) per unit of gas, and miners are free to choose to execute that transaction or ignore it.
-The function caller is charged for exactly the amount the transaction costs and they cap the maximum they are willing to be charged (\textit{gas limit})---if the cap is too low to complete the execution, the miner keeps the Gwei and reverts the state of the EVM (as if the function never ran).
+When a transaction is executed, each opcode in the execution path accrues a fixed, pre-specified amount of \emph{gas}.
+The function caller will pledge to pay a certain amount of Ethereum's internal currency \emph{ETH} (typically quoted in units of Gwei which is one billionth of an ETH) per unit of gas, and miners are free to choose to execute that transaction or ignore it.
+The function caller is charged for exactly what the transaction costs to execute, and they cap the maximum they are willing to be charged (\textit{gas limit}).
+If the cap is too low to complete the execution, the miner keeps the Gwei and \emph{reverts} the state of the EVM (as if the function never ran).
 
@@
 Essentially, our main research question is how many on-chain trades can be executed without exceeding that limit.
-Later we also discuss several opcodes that refund gas (or cost negative gas), which we heavily utilize in our optimizations.
+Later we also discuss several bytecode operations (\emph{opcodes}) that refund gas (\ie cost negative gas), which we heavily utilize in our optimizations.
 
@@
 
-In this paper, we focus on benchmarking an order book for a public blockchain (\eg Ethereum).
+In this paper, we focus on benchmarking an order book for the public blockchain Ethereum.
 Ethereum is widely-used and we stand to learn the most from working in a performance-hostile environment.
 Exchanges could be given their own dedicated blockchain, where trade execution logic can be coded into the network protocol.
-Trading systems on permissioned blockchains (\eg NASDAQ Linq, tZero) can also increase execution time and throughput but reduce user transparency and trust.
-Since it is a closed system, regulators will concentrate on the operators.
+Trading systems on permissioned blockchains (\eg NASDAQ Linq, tZero) can also improve execution time and throughput, but they reduce user transparency and trust if unregulated.
 
-\paragraph{On-chain Dealers.} Another on-chain advantage is that other smart contracts, not just human users, can initiate trades, enabling broader decentralized finance (DeFi) applications.
+\paragraph{On-chain Dealers.} An advantage of on-chain trading is that other smart contracts, not just human users, can initiate trades, enabling broader decentralized finance (DeFi) applications.
 This has fuelled a resurgence in on-chain exchange but through a quote-driven design rather than an order-driven one.
@@
 The trade-off is that they operate as a dealer---the DApp exchanges assets from its own inventory.
-This inventory is loaded into the DApp by an investor who cannot make money on the trades themselves but hopes their losses (termed `impermanent losses') are offset over the long-term by trading fees.
+This inventory is loaded into the DApp by an investor who will not profit from the trades themselves but hopes their losses (termed `impermanent losses') are offset over the long-term by trading fees.
 By contrast, an order book requires no upfront inventory and trading fees are optional.
@@
 \paragraph{Hybrid Designs.} Before on-chain dealers became prominent in the late 2010s, the most popular design was hybrid order-driven exchanges with some trusted off-chain components and some on-chain functionality.
-Some (\eg EtherDelta) were envisioned as operating fully on-chain, but performance limitations drove developers to move key components, such as the order matching system, off-chain to a centralized database.
+Such decentralized exchanges (DEXes) were envisioned as operating fully on-chain, but performance limitations drove developers to move key components, such as the order matching system, off-chain to a centralized database.
 A landscape of DEX designs exist (\eg EtherDelta, 0x, IDEX, \etc): many avoid taking custodianship of assets off-chain, and virtually all (for order-driven markets) operate the order book itself off-chain (a regulatory hook).
-A non-custodial DEX solves the big issue of a CEX---the operator stealing the funds---however trade execution is still not provably fair and server downtime is a common frustration for traders.
-A mitigation is to issue a proof of correct execution to the DApp (\eg Loopring) but these proofs have blindspots (discussed in section~\ref{sec:rollups}).
+A non-custodial DEX solves the big issue of a CEX---the operator stealing the funds---however trade execution is still not provably fair, funds can still be indirectly stolen by a malicious exchange executing unauthorized trades, and server downtime is a common frustration for traders.
+An enhancement is to prove that trade execution is correct (\eg Loopring) but these proofs have blindspots (discussed in section~\ref{sec:rollups}).
 
@@
 Call markets largely side-step front-running attacks from other traders because reordering trades has no impact (discussed more in section~\ref{sec:front}).
-The paper does not include an implementation and was envisioned as an alt-coin (Ethereum was still in development in 2014) with market closing being done by the miners themselves as part of the blockchain logic.
+The paper does not include an implementation and was envisioned as running on a custom blockchain (Ethereum was still in development in 2014).
+Market operations are part of the blockchain logic.
 
@@
 TEX is also an implementation of an orderbook however it uses on-chain and off-chain components, and does not answer our research question of how feasible an on-chain orderbook is.
-It is similar to our variant with rollups however it uses a different architecture where users interact directly with the off-chain component (a regulatory hook).
-The other overlap is the focus on resisting front-running attacks.
+We later compare it to our variant with rollups in Section~\ref{sec:rollups}.
+The main overlap is our common focus on resisting front-running attacks.
 In a recent survey on front-running attacks in blockchain~\cite{eskandari2019sok}, three solutions are proposed.
@@
 
-\cm is open source and written in 350 lines (SLOC) of Solidity plus the priority queue (\eg a heap with dynamic array is 282 SLOC).
+\cm is open source and written in 336 lines (SLOC) of Solidity plus the priority queue (\eg a heap with dynamic array is 282 SLOC).
 Refer to the availability section at the end of the paper.

### 2021-01-12 LaTeX-USENIX/sections/paper.tex
define erc20
edits up to section 4

@@
 They are concerned by their limited ability to intervene when trading is conducted on decentralized networks that, like Ethereum, run on the open internet.
-Order-driven trading can happen fully `on-chain' and this was experimented with in the early days of Ethereum, but it has been largely abandoned for performance reasons in favour of running on centralized servers.
+Order-driven trading can happen fully `on-chain' and this was experimented within the early days of Ethereum, but it has been largely abandoned for performance reasons in favour of running on centralized servers.
 More specifically, the core functionality is performed off-chain (\eg matching orders) while other aspects (\eg loading accounts, order cancellation) might be performed on-chain.
@@
 An older 2014 paper~\cite{clark2014decentralizing} on the `Princeton prediction market'~\cite{Bra13} motivates our work.
-The authors observe the following limitations of on-chain continuous order books: block intervals are slow and not continuous, there is no support for accurate time-stamping, transactions can be dropped or reordered by miners, fast traders can react to submitted orders/cancellations when broadcast to network but not in a block and have their orders appear first (as examined in later work on front-running: \cite{eskandari2019sok,daian2019flash}).
+The authors observe the following limitations of on-chain continuous order books: block intervals are slow and not continuous, there is no support for accurate time-stamping, transactions can be dropped or reordered by miners, and fast traders can react to submitted orders/cancellations when broadcast to network but not in a block and have their orders appear first (as examined in later work on front-running: \cite{eskandari2019sok,daian2019flash}).
 
@@
 Other exchanges, called crossing networks, also operate as a call market at various times throughout the trading day.\footnote{A crossing network uses a secondary market for determining the closing price.
-Many prominent crossing networks are operated internally within a brokerage for its clients, and often as a `dark pool' with an unpublished order book.} Call market are studied widely in finance~\cite{Har03}.
+Many prominent crossing networks are operated internally within a brokerage for its clients, and often as a `dark pool' with an unpublished order book.} Call markets are studied widely in finance~\cite{Har03}.
 Time-sensitive traders submit orders early, especially in crossing networks that close at a randomly determined time (traders risk missing the call if they wait too long).
@@
 The most similar academic work to this paper is the TEX exchange~\cite{khalil2019tex}.
-TEX is also an implementation of an orderbook however it uses on-chain and off-chain components, and does not answer our research question of how feasible an on-chain orderbook is.
+TEX is also an implementation of an order book, however it uses on-chain and off-chain components, and does not answer our research question of how feasible an on-chain order book is.
 We later compare it to our variant with rollups in Section~\ref{sec:rollups}.
@@
 All the nodes of the tree are in a specific order and the root always represents the highest priority item of the data structure (the largest and smallest values in the Max-Heap and Min-Heap respectively).
-We implement a priority queue with a heap that stores its data in a dynamically-sized array.
+We implement a PQ with a heap that stores its data in a dynamically-sized array.
 
 \item \textbf{Heap with Static Array.} A heap can be also represented by a Solidity storage array in which the storage is statically allocated.
-To do this, we pass the required size of the array as a constructor parameter to the priority queue smart contract.
+To do this, we pass the required size of the array as a constructor parameter to the PQ smart contract.
 
@@
 
-\paragraph{Enqueue Performance.} We implemented, deployed, and tested each priority queue using Truffle and Ganache.
+\paragraph{Enqueue Performance.} We implemented, deployed, and tested each PQ using Truffle and Ganache.
 We tried a variety of tests (including testing the full call market with each variant) with consistent results in performance.
@@
 \paragraph{Dequeue Performance.} For each PQ variant storing 50 random integers, the \texttt{Dequeue()} function is iterated until the data structure is empty.
-The total gas cost for fully dequeuing the priority queue variants is outlined in Table~\ref{tab:PQUnitTests}.
+The total gas cost for fully dequeuing the PQ variants is outlined in Table~\ref{tab:PQUnitTests}.
 These tests are performed using the following Ethereum gas metrics: block gas limit $=$11,741,495 and 1 gas $=$ 56 Gwei.\footnote{EthStats (July 2020): \url{https://ethstats.net/}} Dequeuing removes data from the contract's storage.
@@
 Beyond the cleaning up issues with priority queues in Section~\ref{sec:gasrefund}, \cm also uses mappings with each market.
-Traders preload their account with ERC-20 tokens and/or ETH.
+Traders preload their account with tokens to be traded (which comply with a common token standard called ERC20) and/or ETH.
 \cm tracks what they are owed using a mapping called \texttt{totalBalance} and allows traders to withdraw their tokens at any time.

### 2021-01-12 LaTeX-USENIX/sections/paper.tex
edits

--- 2021-01-12 LaTeX-USENIX/sections/paper.tex
@@
 The total gas cost for fully dequeuing the priority queue variants is outlined in Table~\ref{tab:PQUnitTests}.
-These tests are performed using the following Ethereum gas metrics: block gas limit $=$11,741,495 and 1 gas $=$ 56 Gwei.\footnote{EthStats (July 2020): \url{https://ethstats.net/}} Dequeuing removes data from the contract's storage.
+These tests are performed using the following Ethereum gas metrics: block gas limit $=$11,741,495 and 1 gas $=$ 56 Gwei.\footnote{EthStats (July 2020): \url{https://ethstats.net/}} Dequeuing removes data from the DApp's storage.
 Recall this results in a gas refund.
@@
 For these reasons, we suggest using a linked list variant for this specific application.
-As it can be seen in Figure~\ref{fig:random_insertion}, the associated cost for inserting elements into a linked list PQ is significantly greater than the linked list with mapping, as each insertion causes the creation of a new contract.
+As it can be seen in Figure~\ref{fig:random_insertion}, the associated cost for inserting elements into a linked list PQ is significantly greater than the linked list with mapping, as each insertion causes the creation of a new DApp.
 Accordingly, we choose to implement the call market with the linked list with mapping.
@@
 
-One consequence of a linked list is that a new contract is created for every node in the list.
+One consequence of a linked list is that a new DApp is created for every node in the list.
 Beyond being expensive for adding new nodes (a cost that will be bared by the trader in a call market), it also leaves a large footprint in the active Ethereum state, especially if we leave the nodes on the blockchain in perpetuity (\ie we just update the head node of the list and leave the previous head `dangling').
@@
 Another simplifying assumption is to implement a \textit{collateralized} call market.
-We assume all trades are between ETH and an ERC20 token, all orders are pre-funded in the contract with ETH (for bids) and tokens (for asks), and once ETH or tokens are committed to an order, they cannot be withdrawn until the market closes.
+We assume all trades are between ETH and an ERC20 token, all orders are pre-funded in the DApp with ETH (for bids) and tokens (for asks), and once ETH or tokens are committed to an order, they cannot be withdrawn until the market closes.
 This ensures all executed orders clear and settle (\ie no defaults on payment or delivery).
@@
 Beyond the cleaning up issues with priority queues in Section~\ref{sec:gasrefund}, \cm also uses mappings with each market.
-Traders preload their account with ERC-20 tokens and/or ETH.
+Traders preload their account with tokens to be traded (which comply with a common token standard called ERC20) and/or ETH.
 \cm tracks what they are owed using a mapping called \texttt{totalBalance} and allows traders to withdraw their tokens at any time.
-However if a trader submits an order (\ie ask for their tokens), the tokens are committed and not available for withdrawal until the market closes (after which, the tokens are either transferred to the buyer or, if the trade is not executed, returned to the trader).
+However if a trader submits an order (\ie ask for their tokens), the tokens are committed and not available for withdrawal until the market closes (after which, the balances are updated for each trade that is executed).
 Committed tokens are also tracked in a mapping called \texttt{unavailableBalance}.
@@
 \item \textbf{Manually Clearing the Mapping.} Since mappings cannot be iterated, a common design pattern used by DApp developers is to store keys in an array and iterate over the array to zero out each mapping and array entry.
-Clearing a mapping this way costs substantially more to clear than what is refunded (15,000 for each element).
+Clearing a mapping this way costs substantially more to clear than what is refunded.
 
@@
 This refunds us 24,000 gas which is less than the cost of deploying the extra contract.
-Additionally, every call to the mapping is more expensive because (1) it is an external function call, and (2) function calls  to be evaluated to ensure they only come from the market contract (if a mapping is a local variable, you get private access for free).
+Additionally, every call to the mapping is more expensive because (1) it is an external function call, and (2) the calls need access control to ensure only the market contract can write to it (if a mapping is a local variable, you get private access for free).
 
@@
 
-%\textblue{ We need to find a home for this: another solution to reopen the market immediately after the closing call is to have many similar contracts for the market and  a factory contract to guide users to the correct address (from the reviewer's comment)}
+%\textblue{ We need to find a home for this: another solution to reopen the market immediately after the closing call is to have many similar DApps for the market and  a factory DApp to guide users to the correct address (from the reviewer's comment)}
 
-%\cm is designed as base class that can be extended and customized. We discuss potential modifications here.
+\cm is designed as base class that can be extended and customized. We discuss potential modifications here.
 
@@
 However an interested third party (such as the token issuer for a given market) might occasionally bailout the market when it halts on \texttt{closeMarket()} to facilitate further trading.
-If the contract can pay for its own functions, an interested party can also arrange for a commercial service (\eg any.sender\footnote{\url{https://github.com/PISAresearch/docs.any.sender}}) to relay the \texttt{closeMarket()} function call on Ethereum (an approach called \textit{meta-transactions}) which introduces another regulatory hook.
+If the DApp can pay for its own functions, an interested party can also arrange for a commercial service (\eg any.sender\footnote{\url{https://github.com/PISAresearch/docs.any.sender}}) to relay the \texttt{closeMarket()} function call on Ethereum (an approach called \textit{meta-transactions}) which introduces another regulatory hook.
 

### 2021-01-12 LaTeX-USENIX/sections/paper.tex

@@
 \paragraph{Dequeue Performance.} For each PQ variant storing 50 random integers, the \texttt{Dequeue()} function is iterated until the data structure is empty.
-The total gas cost for fully dequeuing the priority queue variants is outlined in Table~\ref{tab:PQUnitTests}.
-These tests are performed using the following Ethereum gas metrics: block gas limit $=$11,741,495 and 1 gas $=$ 56 Gwei.\footnote{EthStats (July 2020): \url{https://ethstats.net/}} Dequeuing removes data from the DApp's storage.
+The total gas cost for fully dequeuing the PQ variants is outlined in Table~\ref{tab:PQUnitTests}.
+These tests are performed using the following Ethereum gas metrics: block gas limit $=$11,741,495 and 1 gas $=$ 56 Gwei.\footnote{EthStats (July 2020): \url{https://ethstats.net/}} Dequeuing removes data from the contract's storage.
 Recall this results in a gas refund.

### 2021-01-12 LaTeX-USENIX/sections/paper.tex
done for now
Done with edits + added the Arbitrum to the repo

@@
 The main research question is how many orders can be processed in a single Ethereum transaction when closing the call market, using Ethereum today.
-As our previous experiments indicated, the choice of priority queue (PQ) implementation is the main influence on performance (see Table~\ref{tab:worst_case_matching}).
+As our previous experiments indicated, the choice of PQ implementation is the main influence on performance (see Table~\ref{tab:worst_case_matching}).
 We implemented a generic call market that interfaces with a generic PQ (at its own contract address) and ran experiments for each PQ implementation.
@@
 
-\item \textbf{Store the mapping in a separate DApp.} We could wrap the mapping inside its own DApp and when we are done with the mapping, we can run \texttt{SELFDESTRUCT} on the contract.
+\item \textbf{Store the Mapping in a Separate DApp.} We could wrap the mapping inside its own DApp and when we are done with the mapping, we can run \texttt{SELFDESTRUCT} on the contract.
 This refunds us 24,000 gas which is less than the cost of deploying the extra contract.
@@
 However we consider two other scenarios that do not assume miners can automatically find MEV opportunities.
-One solution requires a modified closing function, \texttt{closeMarket(n)}, that only processes $n$ orders at a time until the order book is empty (this is sensible design in any case to safeguard against the orderbook from locking up because the number of orders exceeds the gas limit to process them).
+One solution requires a modified closing function, \texttt{closeMarket(n)}, that only processes $n$ orders at a time until the order book is empty (this is sensible design in any case to safeguard against the order book from locking up because the number of orders exceeds the gas limit to process them).
 Once the time window for submitting orders is past, a new market is created (without settling the previous market).
@@
 
-Imagine you have just launched a standard token on Ethereum.
-Now want your holders to be able to trade it.
+Imagine you have just launched a token on Ethereum.
+Now want to be able to trade it.
 While the barrier to entry for exchange services is low, it still exists.
@@
 For rollups, you will have to host your own servers.
-By contrast to all of these, with an on-chain orderbook, you just deploy the code alongside your token and trading is immediately supported.
+By contrast to all of these, with an on-chain order book, you just deploy the code alongside your token and trading is immediately supported.
 This should concern regulators.

### 2021-01-12 Code/arbitrum/Workspace/New-Truffle/test/13_Orderbook_V27_test.js
Create Arbitrum

@@ -1,0 +1,217 @@
+const DappToken = artifacts.require('DappToken');
+const Orderbook = artifacts.require('Orderbook_V27');
+var Orderbookaddress;
+var tokenaddress;
+var accounts;
+
+contract('Orderbook', function(accounts) {
+    it('should store the address of the orderbook into the var orderbookaddress', async() => {
+        const OrderbookInstance = await Orderbook.deployed(); 
+        Orderbookaddress = OrderbookInstance.address;
+        console.log('The address of the orderbook contract is:', OrderbookInstance.address);
+        
+    });
+
+
+
+
+});
+
+contract('DappToken', function(accounts) {
+
+    it('should approve transfer of 100 tokens from account[0] to the orderbook contract ', async ()=> {
+        const DappTokenInstance = await DappToken.deployed();
+        tokenaddress = DappTokenInstance.address;
+        const receipt = await DappTokenInstance.approve (Orderbookaddress, 15000, {from: accounts[0]});
+        const result = await DappTokenInstance.allowance(accounts[0],Orderbookaddress);
+        console.log('Account[0] allowes the orderbook contract to spend:',result.toNumber());
+        
+        console.log('********************************************');
+        const gasUsed = receipt.receipt.gasUsed;
+        console.log(`GasUsed for approving: ${receipt.receipt.gasUsed}`);
+    
+    });   
+
+});
+
+
+//*******************New test Block for the already deployed orderbook contract *************************
+describe('Orderbook', function(accounts) {
+    this.timeout(0);
+    
+    //*******************Test 1*************************
+    it('should deposit 100 tokens from accounst[0] to the orderbook contract', async() => {
+        
+        const OrderbookInstance = await Orderbook.deployed(); 
+
+        accounts = await web3.eth.getAccounts();
+       
+        const receipt = await OrderbookInstance.DepositToken (tokenaddress, 15000, {from: accounts[0]});
+        
+        const totalbalance = await OrderbookInstance.TokenBalance(accounts[0], tokenaddress);
+        
+        console.log('The token balance of account[0] is:', totalbalance.toNumber());
+        console.log('********************************************');
+        //const gasUsed = receipt.receipt.gasUsed;
+        //console.log(`GasUsed for depositting 100 tokens: ${receipt.receipt.gasUsed}`);
+
+    });
+
+    //*******************Test 2*************************
+    it('should deposit 6000 Ether from accounts[1] to the orderbook contract', async() => {
+        
[…]

### 2021-01-12 Code/arbitrum/packages/arb-avm-cpp/avm_values/include/avm_values/exceptions.hpp

@@ -1,0 +1,42 @@
+/*
+ * Copyright 2019-2020, Offchain Labs, Inc.
+ *
+ * Licensed under the Apache License, Version 2.0 (the "License");
+ * you may not use this file except in compliance with the License.
+ * You may obtain a copy of the License at
+ *
+ *    http://www.apache.org/licenses/LICENSE-2.0
+ *
+ * Unless required by applicable law or agreed to in writing, software
+ * distributed under the License is distributed on an "AS IS" BASIS,
+ * WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
+ * See the License for the specific language governing permissions and
+ * limitations under the License.
+ */
+
+#ifndef exceptions_hpp
+#define exceptions_hpp
+
+#include <nonstd/variant.hpp>
+
+class bad_tuple_index : public std::exception {
+   public:
+    virtual const char* what() const noexcept override;
+};
+
+class bad_pop_type : public std::exception {
+   public:
+    virtual const char* what() const noexcept override;
+};
+
+class int_out_of_bounds : public std::exception {
+   public:
+    virtual const char* what() const noexcept override;
+};
+
+class stack_too_small : public std::exception {
+   public:
+    virtual const char* what() const noexcept override;
+};
+
+#endif /* exceptions_hpp */

### 2021-01-12 Code/arbitrum/packages/arb-avm-cpp/avm_values/src/codepoint.cpp

@@ -1,0 +1,122 @@
+/*
+ * Copyright 2019-2020, Offchain Labs, Inc.
+ *
+ * Licensed under the Apache License, Version 2.0 (the "License");
+ * you may not use this file except in compliance with the License.
+ * You may obtain a copy of the License at
+ *
+ *    http://www.apache.org/licenses/LICENSE-2.0
+ *
+ * Unless required by applicable law or agreed to in writing, software
+ * distributed under the License is distributed on an "AS IS" BASIS,
+ * WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
+ * See the License for the specific language governing permissions and
+ * limitations under the License.
+ */
+
+#include <avm_values/codepoint.hpp>
+
+#include <avm_values/tuple.hpp>
+
+#include <ethash/keccak.hpp>
+
+#include <iostream>
+
+Operation::Operation(OpCode opcode_, value immediate_)
+    : opcode(opcode_), immediate(std::move(immediate_)) {}
+
+void Operation::marshalForProof(std::vector<unsigned char>& buf,
+                                MarshalLevel marshal_level,
+                                const Code& code) const {
+    if (immediate) {
+        buf.push_back(1);
+        buf.push_back(static_cast<uint8_t>(opcode));
+        ::marshalForProof(*immediate, marshal_level, buf, code);
+    } else {
+        buf.push_back(0);
+        buf.push_back(static_cast<uint8_t>(opcode));
+    }
+}
+
+bool operator==(const Operation& val1, const Operation& val2) {
+    if (val1.opcode != val2.opcode) {
+        return false;
+    }
+    if (!val1.immediate && !val2.immediate) {
+        return true;
+    }
+    if (!val1.immediate || !val2.immediate) {
+        return false;
+    }
+    return *val1.immediate == *val2.immediate;
+}
+
+bool operator!=(const Operation& val1, const Operation& val2) {
+    if (val1.opcode != val2.opcode) {
+        return true;
+    }
+    if (!val1.immediate && !val2.immediate) {
+        return false;
+    }
+    if (!val1.immediate || !val2.immediate) {
+        return true;
+    }
+    return *val1.immediate != *val2.immediate;
+}
+
+uint64_t pc_default = -1;
+
+bool operator==(const CodePoint& val1, const CodePoint& val2) {
+    if (hash(val1) != hash(val2)) {
[…]

### 2021-01-12 Code/arbitrum/packages/arb-avm-cpp/data_storage/src/value/referencecount.cpp

@@ -1,0 +1,135 @@
+/*
+ * Copyright 2019-2020, Offchain Labs, Inc.
+ *
+ * Licensed under the Apache License, Version 2.0 (the "License");
+ * you may not use this file except in compliance with the License.
+ * You may obtain a copy of the License at
+ *
+ *    http://www.apache.org/licenses/LICENSE-2.0
+ *
+ * Unless required by applicable law or agreed to in writing, software
+ * distributed under the License is distributed on an "AS IS" BASIS,
+ * WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
+ * See the License for the specific language governing permissions and
+ * limitations under the License.
+ */
+
+#include "referencecount.hpp"
+
+#include <data_storage/storageresult.hpp>
+
+#include <rocksdb/utilities/transaction_db.h>
+
+#include <boost/algorithm/hex.hpp>
+
+#include <iostream>
+
+namespace {
+SaveResults saveValueWithRefCount(rocksdb::Transaction& transaction,
+                                  uint32_t updated_ref_count,
+                                  const rocksdb::Slice& hash_key,
+                                  const std::vector<unsigned char>& value) {
+    std::vector<unsigned char> updated_entry(sizeof(updated_ref_count));
+    memcpy(&updated_entry[0], &updated_ref_count, sizeof(updated_ref_count));
+    updated_entry.insert(updated_entry.end(), value.begin(), value.end());
+
+    std::string value_str(updated_entry.begin(), updated_entry.end());
+    auto status = transaction.Put(hash_key, value_str);
+
+    if (status.ok()) {
+        return SaveResults{updated_ref_count, status};
+    } else {
+        return SaveResults{0, status};
+    }
+}
+}  // namespace
+
+SaveResults incrementReference(rocksdb::Transaction& transaction,
+                               const rocksdb::Slice& hash_key,
+                               uint32_t new_references) {
+    auto results = getRefCountedData(transaction, hash_key);
+
+    if (results.status.ok()) {
+        auto updated_count = results.reference_count + new_references;
+        return saveValueWithRefCount(transaction, updated_count, hash_key,
+                                     results.stored_value);
+    } else {
+        return SaveResults{0, results.status};
+    }
+}
+
+SaveResults saveRefCountedData(rocksdb::Transaction& transaction,
+                               const rocksdb::Slice& hash_key,
+                               const std::vector<unsigned char>& value,
+                               uint32_t new_references,
+                               bool allow_replacement) {
[…]

### 2021-01-12 Code/arbitrum/packages/arb-avm-cpp/data_storage/src/value/referencecount.hpp

@@ -1,0 +1,45 @@
+/*
+ * Copyright 2019-2020, Offchain Labs, Inc.
+ *
+ * Licensed under the Apache License, Version 2.0 (the "License");
+ * you may not use this file except in compliance with the License.
+ * You may obtain a copy of the License at
+ *
+ *    http://www.apache.org/licenses/LICENSE-2.0
+ *
+ * Unless required by applicable law or agreed to in writing, software
+ * distributed under the License is distributed on an "AS IS" BASIS,
+ * WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
+ * See the License for the specific language governing permissions and
+ * limitations under the License.
+ */
+
+#ifndef transaction_hpp
+#define transaction_hpp
+
+#include <data_storage/storageresultfwd.hpp>
+
+#include <memory>
+#include <vector>
+
+namespace rocksdb {
+class Transaction;
+class Status;
+struct Slice;
+}  // namespace rocksdb
+
+GetResults getRefCountedData(rocksdb::Transaction& transaction,
+                             const rocksdb::Slice& hash_key);
+SaveResults saveRefCountedData(rocksdb::Transaction& transaction,
+                               const rocksdb::Slice& hash_key,
+                               const std::vector<unsigned char>& value,
+                               uint32_t new_references = 1,
+                               bool allow_replacement = false);
+SaveResults incrementReference(rocksdb::Transaction& transaction,
+                               const rocksdb::Slice& hash_key,
+                               uint32_t new_references = 1);
+DeleteResults deleteRefCountedData(rocksdb::Transaction& transaction,
+                                   const rocksdb::Slice& hash_key,
+                                   uint32_t deleted_references = 1);
+
+#endif /* transaction_hpp */

### 2021-01-12 Code/arbitrum/packages/arb-avm-cpp/external/libff/libff/algebra/curves/mnt/mnt4/mnt4_g1.hpp

@@ -1,0 +1,103 @@
+/** @file
+ *****************************************************************************
+
+ Declaration of interfaces for the MNT4 G1 group.
+
+ *****************************************************************************
+ * @author     This file is part of libff, developed by SCIPR Lab
+ *             and contributors (see AUTHORS).
+ * @copyright  MIT license (see LICENSE file)
+ *****************************************************************************/
+
+#ifndef MNT4_G1_HPP_
+#define MNT4_G1_HPP_
+
+#include <vector>
+
+#include <libff/algebra/curves/curve_utils.hpp>
+#include <libff/algebra/curves/mnt/mnt4/mnt4_init.hpp>
+
+namespace libff {
+
+class mnt4_G1;
+std::ostream& operator<<(std::ostream &, const mnt4_G1&);
+std::istream& operator>>(std::istream &, mnt4_G1&);
+
+class mnt4_G1 {
+public:
+#ifdef PROFILE_OP_COUNTS
+    static long long add_cnt;
+    static long long dbl_cnt;
+#endif
+    static std::vector<size_t> wnaf_window_table;
+    static std::vector<size_t> fixed_base_exp_window_table;
+    static mnt4_G1 G1_zero;
+    static mnt4_G1 G1_one;
+    static bool initialized;
+    static mnt4_Fq coeff_a;
+    static mnt4_Fq coeff_b;
+
+    typedef mnt4_Fq base_field;
+    typedef mnt4_Fr scalar_field;
+
+    mnt4_Fq X, Y, Z;
+
+    // using projective coordinates
+    mnt4_G1();
+    mnt4_G1(const mnt4_Fq& X, const mnt4_Fq& Y) : X(X), Y(Y), Z(base_field::one()) {}
+    mnt4_G1(const mnt4_Fq& X, const mnt4_Fq& Y, const mnt4_Fq& Z) : X(X), Y(Y), Z(Z) {}
+
+    void print() const;
+    void print_coordinates() const;
+
+    void to_affine_coordinates();
+    void to_special();
+    bool is_special() const;
+
+    bool is_zero() const;
+
+    bool operator==(const mnt4_G1 &other) const;
+    bool operator!=(const mnt4_G1 &other) const;
+
+    mnt4_G1 operator+(const mnt4_G1 &other) const;
[…]

### 2021-01-12 Code/arbitrum/packages/arb-evm/evm/log.go

@@ -1,0 +1,186 @@
+/*
+ * Copyright 2019-2020, Offchain Labs, Inc.
+ *
+ * Licensed under the Apache License, Version 2.0 (the "License");
+ * you may not use this file except in compliance with the License.
+ * You may obtain a copy of the License at
+ *
+ *    http://www.apache.org/licenses/LICENSE-2.0
+ *
+ * Unless required by applicable law or agreed to in writing, software
+ * distributed under the License is distributed on an "AS IS" BASIS,
+ * WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
+ * See the License for the specific language governing permissions and
+ * limitations under the License.
+ */
+
+package evm
+
+import (
+	"bytes"
+	"errors"
+	"fmt"
+	"github.com/offchainlabs/arbitrum/packages/arb-util/inbox"
+	errors2 "github.com/pkg/errors"
+	"math/big"
+	"strings"
+
+	"github.com/ethereum/go-ethereum/common/hexutil"
+
+	"github.com/offchainlabs/arbitrum/packages/arb-util/common"
+	"github.com/offchainlabs/arbitrum/packages/arb-util/value"
+)
+
+type Log struct {
+	Address common.Address
+	Topics  []common.Hash
+	Data    []byte
+}
+
+func NewRandomLog(topicCount int32) Log {
+	topics := make([]common.Hash, 0, topicCount)
+	for i := int32(0); i < topicCount; i++ {
+		topics = append(topics, common.RandHash())
+	}
+	return Log{
+		Address: common.RandAddress(),
+		Topics:  topics,
+		Data:    common.RandBytes(200),
+	}
+}
+
+func (l Log) MatchesQuery(addresses []common.Address, topics [][]common.Hash) bool {
+	if len(addresses) > 0 {
+		match := false
+		for _, addr := range addresses {
+			if l.Address == addr {
+				match = true
+				break
+			}
+		}
+		if !match {
+			return false
+		}
+	}
+
+	if len(topics) > len(l.Topics) {
+		return false
+	}
+
+	for i, topicGroup := range topics {
+		if len(topicGroup) == 0 {
+			continue
+		}
+		match := false
+		for _, topic := range topicGroup {
+			if l.Topics[i] == topic {
+				match = true
+				break
+			}
+		}
+		if !match {
[…]

### 2021-01-12 Code/arbitrum/packages/arb-provider-ethers/dist/lib/abi/ArbErc721Factory.d.ts

@@ -1,0 +1,13 @@
+import { ContractFactory, Signer } from 'ethers';
+import { Provider } from 'ethers/providers';
+import { UnsignedTransaction } from 'ethers/utils/transaction';
+import { TransactionOverrides } from '.';
+import { ArbErc721 } from './ArbErc721';
+export declare class ArbErc721Factory extends ContractFactory {
+    constructor(signer?: Signer);
+    deploy(overrides?: TransactionOverrides): Promise<ArbErc721>;
+    getDeployTransaction(overrides?: TransactionOverrides): UnsignedTransaction;
+    attach(address: string): ArbErc721;
+    connect(signer: Signer): ArbErc721Factory;
+    static connect(address: string, signerOrProvider: Signer | Provider): ArbErc721;
+}

### 2021-01-12 Code/arbitrum/packages/arb-provider-ethers/dist/lib/abi/GlobalInboxFactory.d.ts

@@ -1,0 +1,13 @@
+import { ContractFactory, Signer } from 'ethers';
+import { Provider } from 'ethers/providers';
+import { UnsignedTransaction } from 'ethers/utils/transaction';
+import { TransactionOverrides } from '.';
+import { GlobalInbox } from './GlobalInbox';
+export declare class GlobalInboxFactory extends ContractFactory {
+    constructor(signer?: Signer);
+    deploy(overrides?: TransactionOverrides): Promise<GlobalInbox>;
+    getDeployTransaction(overrides?: TransactionOverrides): UnsignedTransaction;
+    attach(address: string): GlobalInbox;
+    connect(signer: Signer): GlobalInboxFactory;
+    static connect(address: string, signerOrProvider: Signer | Provider): GlobalInbox;
+}

### 2021-01-12 Code/arbitrum/packages/arb-tx-aggregator/batcher/queue.go

@@ -1,0 +1,257 @@
+package batcher
+
+import (
+	"container/heap"
+	"errors"
+	"log"
+	"math/rand"
+
+	"github.com/ethereum/go-ethereum/common"
+	"github.com/ethereum/go-ethereum/core"
+	"github.com/ethereum/go-ethereum/core/types"
+
+	"github.com/offchainlabs/arbitrum/packages/arb-evm/message"
+	"github.com/offchainlabs/arbitrum/packages/arb-tx-aggregator/snapshot"
+	arbcommon "github.com/offchainlabs/arbitrum/packages/arb-util/common"
+)
+
+// An TxHeap is a min-heap of transactions sorted by nonce.
+type TxHeap []*types.Transaction
+
+func (h TxHeap) Len() int           { return len(h) }
+func (h TxHeap) Less(i, j int) bool { return h[i].Nonce() < h[j].Nonce() }
+func (h TxHeap) Swap(i, j int)      { h[i], h[j] = h[j], h[i] }
+
+func (h *TxHeap) Push(x interface{}) {
+	*h = append(*h, x.(*types.Transaction))
+}
+
+func (h *TxHeap) Pop() interface{} {
+	old := *h
+	n := len(old)
+	x := old[n-1]
+	*h = old[0 : n-1]
+	return x
+}
+
+type txQueue struct {
+	txes        TxHeap
+	txesByNonce map[uint64]*types.Transaction
+	maxNonce    uint64
+}
+
+func newTxQueue() *txQueue {
+	return &txQueue{
+		txes:        nil,
+		txesByNonce: make(map[uint64]*types.Transaction),
+		maxNonce:    0,
+	}
+}
+
+func (q *txQueue) addTransaction(tx *types.Transaction) error {
+	if _, ok := q.txesByNonce[tx.Nonce()]; ok {
+		return errors.New("transaction replacement not supported")
+	}
+
+	q.txesByNonce[tx.Nonce()] = tx
+	heap.Push(&q.txes, tx)
+
+	if tx.Nonce() > q.maxNonce {
+		q.maxNonce = tx.Nonce()
+	}
+	return nil
+}
+
+func (q *txQueue) Empty() bool {
+	return len(q.txes) == 0
+}
+
+func (q *txQueue) Peek() *types.Transaction {
+	return q.txes[0]
+}
+
+func (q *txQueue) Pop() *types.Transaction {
[…]

### 2021-01-12 Code/arbitrum/packages/arb-validator/rollup/chainParamsSetting.go

@@ -1,0 +1,35 @@
+/*
+* Copyright 2020, Offchain Labs, Inc.
+*
+* Licensed under the Apache License, Version 2.0 (the "License");
+* you may not use this file except in compliance with the License.
+* You may obtain a copy of the License at
+*
+*    http://www.apache.org/licenses/LICENSE-2.0
+*
+* Unless required by applicable law or agreed to in writing, software
+* distributed under the License is distributed on an "AS IS" BASIS,
+* WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
+* See the License for the specific language governing permissions and
+* limitations under the License.
+ */
+
+package rollup
+
+import (
+	"math/big"
+
+	"github.com/offchainlabs/arbitrum/packages/arb-util/common"
+	"github.com/offchainlabs/arbitrum/packages/arb-validator-core/valprotocol"
+)
+
+func DefaultChainParams() valprotocol.ChainParams {
+	gracePeriodInBlocks := int64(30)
+	return valprotocol.ChainParams{
+		StakeRequirement:        big.NewInt(10 * 1000 * 1000 * 1000 * 1000 * 1000), // 0.01 Eth
+		StakeToken:              common.Address{},                                  // stake in ETH
+		GracePeriod:             common.TicksFromBlockNum(common.NewTimeBlocks(big.NewInt(gracePeriodInBlocks))),
+		MaxExecutionSteps:       10000000000,
+		ArbGasSpeedLimitPerTick: 80000000,
+	}
+}

### 2021-01-15 LaTeX-USENIX/sections/paper.tex
edits

@@
 
-Our research group is actively collaborating with our jurisdiction's financial regulator (name withheld for peer-review) to help them forecast how trading can be impacted by blockchain technology.
+Our research group is actively collaborating with our jurisdiction's financial regulator (Autorité des Marchés Financiers (AMF)) to help them forecast how trading can be impacted by blockchain technology.
 This paper addresses their concerns about the feasibility of a `worst-case scenario' where a trading platform is anonymously deployed on a public blockchain, like Ethereum, and runs autonomously without any further intervention from an externally visible entity.
@@
 It may seem paradoxical or unethical to build for regulators exactly what they worry about, however we agreed that it was too difficult to answer our research questions without actual implementation and experimentation.
-\cm is proof of concept code that implements only enough to understand the feasibilty of on-chain trading and we release the code for reproducibility.
+\cm is proof of concept code that implements only enough to understand the feasibility of on-chain trading and we release the code for reproducibility.
 However it is not production code, it is unpolished, it has no UI, and we have no intention of promoting it for adoption.
@@
 
-%\subsubsection*{Acknowledgements.} J. Clark thanks ...
+ \subsubsection*{Availability} 
+The Solidity source code for \cm, Truffle test files, and Arbitrum dependencies are available in a GitHub repository\footnote{\CallMarketRepo}.
+We have also deployed \cm on Ethereum's testnet Rinkeby with flattened (single file) source code of just the \cm base class and priority queue implementations.
+It is visible and can be interacted with here: \href{https://rinkeby.etherscan.io/address/0x0d91de29c531d074853a5cef7cf9dfeb9c6ec4e0}{[etherscan.io]}; while the Arbitrum variant is here: \href{https://explorer.arbitrum.io/#/tx/0x1828d7eb6a7a9b9ec479f07e8149c6172bb89a101571963b5cf690132bdf009b}{[explorer.offchainlabs.com]}.
 
-\subsubsection*{Availability} 
-The Solidity source code for \cm, Truffle test files, and Arbitrum dependencies are available in a GitHub repository (non-anonymous link omitted).
-We have also deployed \cm on Ethereum's testnet Rinkeby with flattened (single file) source code of just the \cm base class and priority queue implementations.
-It is visible and can be interacted with here: \href{https://rinkeby.etherscan.io/address/0x0d91de29c531d074853a5cef7cf9dfeb9c6ec4e0}{[etherscan.io]}; while the Arbitrum variant is here: \href{https://explorer.arbitrum.io/#/tx/0x1828d7eb6a7a9b9ec479f07e8149c6172bb89a101571963b5cf690132bdf009b}{[explorer.offchainlabs.com]} (both links are anonymized).
+\subsubsection*{Acknowledgements.}  The authors acknowledge support for this research project from the AMF (Autorité des Marchés Financiers), the National Sciences and Engineering Research Council (NSERC)/Raymond Chabot Grant Thornton/Catallaxy Industrial Research Chair in Blockchain Technologies, as well as NSERC through a Discovery Grant.
+M.
+Moosavi acknowledges support from Fonds de Recherche du Québec - Nature et Technologies (FRQNT) and NSERC through a Discovery Grant.
 

### 2021-01-15 LaTeX-USENIX/sections/paper.tex
minor edits

@@
 
-Our research group is actively collaborating with our jurisdiction's financial regulator (Autorité des Marchés Financiers (AMF)) to help them forecast how trading can be impacted by blockchain technology.
+Our research group is actively collaborating with our jurisdiction's (Quebec, Canada) financial regulator, the Autorité des Marchés Financiers (AMF), to help them forecast how trading can be impacted by blockchain technology.
 This paper addresses their concerns about the feasibility of a `worst-case scenario' where a trading platform is anonymously deployed on a public blockchain, like Ethereum, and runs autonomously without any further intervention from an externally visible entity.
@@
 
-\subsubsection*{Acknowledgements.}  The authors acknowledge support for this research project from the AMF (Autorité des Marchés Financiers), the National Sciences and Engineering Research Council (NSERC)/Raymond Chabot Grant Thornton/Catallaxy Industrial Research Chair in Blockchain Technologies, as well as NSERC through a Discovery Grant.
+\subsubsection*{Acknowledgements.}  The authors thanks the AMF (Autorité des Marchés Financiers) for supporting this research project.
+J.
+Clark also acknowledges partial funding from the National Sciences and Engineering Research Council (NSERC)/Raymond Chabot Grant Thornton/Catallaxy Industrial Research Chair in Blockchain Technologies, as well as NSERC through a Discovery Grant.
 M.
-Moosavi acknowledges support from Fonds de Recherche du Québec - Nature et Technologies (FRQNT) and NSERC through a Discovery Grant.
+Moosavi acknowledges support from Fonds de Recherche du Québec - Nature et Technologies (FRQNT).
 

### 2021-03-10 LaTeX-USENIX/sections/paper.tex
to do
updating the performance table + some edits
Arbitrum texts added

@@
 This positions \cm as a feasible design for only a narrow set of markets today (low liquidity, small number of traders) which is good news for regulators.
-However we caution that the technology is likely to improve vastly in the coming years and we demonstrate one avenue for improvement through `rollups'~\cite{kalodner2018arbitrum}.
-While rollups use centralized servers and are not fully on-chain, an architecture where these servers only interface with Ethereum and never interface directly with users is still concerning, as it side-steps the regulatory hook that is present in many other server-augmented trading platforms.
+However we caution that the technology is likely to improve vastly in the coming years and we demonstrate one avenue for improvement through `roll-ups'~\cite{kalodner2018arbitrum}.
+While roll-ups use centralized servers and are not fully on-chain, an architecture where these servers only interface with Ethereum and never interface directly with users is still concerning, as it side-steps the regulatory hook that is present in many other server-augmented trading platforms.
 
@@
 TEX is also an implementation of an order book, however it uses on-chain and off-chain components, and does not answer our research question of how feasible an on-chain order book is.
-We later compare it to our variant with rollups in Section~\ref{sec:rollups}.
+We later compare it to our variant with roll-ups in Section~\ref{sec:rollups}.
 The main overlap is our common focus on resisting front-running attacks.
@@
 We tested it with the Mocha testing framework using Truffle on Ganache-CLI to obtain our performance metrics.
-Once deployed, the bytecode of \cm is 10812 bytes plus the constructor code (6400 bytes) which is not stored.
+Once deployed, the bytecode of \cm is 10,812 bytes plus the constructor code (6,400 bytes) which is not stored.
 We cross-checked for vulnerabilities with \textit{Slither}\footnote{https://github.com/crytic/slither} and \textit{SmartCheck}\footnote{https://tool.smartdec.net} (it only fails some `informational' warnings that are intentional design choices---\eg a costly loop).
@@
 The Ethereum refund model should be considered further by Ethereum developers to better incentivize developers to be less wasteful in using storage.
+
+% = = = = = = = = = = = = = = = = = = = = = = = = =  %
+\section{\cm on Layer 2}\label{sec:rollups}
+
+\subsection{Roll-ups}
+
+We have avoided augmenting \cm with centralized components and third party services as our research question concerns the feasibility of a system with a minimum of regulatory hooks.
+However from a regulatory stance, there is a big difference between an architecture where the centralized component is publicly visible and interacted with by users (\eg most DEXes, roll-up architectures like Loopring, and commit-chain solutions like TEX).
+We consider an alternative design that is almost as difficult to regulate as a fully on-chain solution.
+In this design, an off-chain component is introduced to boost performance but it only interacts with the Ethereum network and never directly with traders.
+Traders still only interact with Ethereum.
+
+% = = = = = = = = = = = = = = = = = = = = = = = = =  %
+		% MM:  Dont know to merger the following paragraph with this section?
+
+%A function can be computed off-chain and the new state of the DApp, called a \textit{rollup}, is written back to the blockchain, accompanied by either (1) a proof that the function was executed correctly, or (2) a dispute resolution process that can resolve, on-chain, functions that are not executed correctly (\eg Arbitrum~\cite{kalodner2018arbitrum}).
+In the case of (1), validating the proof must be cheaper than running the function itself.
+There are two main approaches to (1): the first is to use cryptographic proof techniques (\eg SNARKS~\cite{BCGTV13,GGPR13} and variants~\cite{BBHR19}), and the second is to execute the function in a trusted execution environment (TEE; \eg Intel SGX) and validate the TEE's quote on-chain (\eg Ekiden~\cite{cheng2019ekiden}).\footnote{The TEE-based approach is mired by recent attacks on SGX~\cite{SGX1,SGX2,SGX3,SGX4}, however these attacks do not necessarily apply to the specifics of how SGX is used here, and safer TEE technologies like Intel TXT (\cf~\cite{ZBC+19}) can be substituted.}
+% = = = = = = = = = = = = = = = = = = = = = = = = =  %
+
+\textit{Layer 2} solutions are a group of technologies that are designed and proposed to address specific drawbacks of executing transactions on \textit{Layer 1} (\ie Ethereum and other blockchains)~\cite{gudgeon2020sok}.
+These technologies focus on fast transaction throughput, reducing gas costs, or educing transaction latency.
+When using \cm, we strive to reduce the gas cost as performance is the main bottleneck.
+Thus, we choose a Layer 2 technology called \textit{roll-up} which aims at reducing the gas cost for operating on Layer 1 by taking the transaction executions off-chain and only using the Ethereum blockchain for storing data.
+In a roll-up, every transaction is executed by a server or cluster of servers known as \textit{validators} that can be run by a collection of users or third party operators (here they can be run by the token issuer).
+These validators then push the result of the executions (\ie updates in the EVM state) back to the Ethereum and assure the Ethereum network that the transactions have been executed correctly.
+
+There are two broad roll-up categories (i) \textit{zero knowledge} and (ii) \textit{optimistic} roll-ups, each taking a different approach to ensure the validity of off-chain transaction executions.
+A zero knowledge roll-up (\textit{a.k.a.} ZK-rollup) uses cryptographic validity proofs (SNARKS~\cite{BCGTV13,GGPR13}) which can be later verified on-chain.
+These proofs are heavy to compute (introduce a burden to the validators who generate them) but considered valid once posted to the Ethereum.
+An optimistic roll-up uses a side chain (a roll-up chain) that is run on top of Layer 1.
+Once the executions are performed, validators assert the new states of the roll-up chain to the Ethereum and wait for anyone to dispute these assertions.
+Although the dispute time delays result in a slower transaction finality, optimistic roll-ups substantially increase the performance by decreasing the gas cost.
+Therefore, we choose this roll-up solution to for the Layer 2 implementation of \cm.
+
+% = = = = = = = = = = = = = = = = = = = = = = = = =  %
+\subsection{Arbitrum}
+
+Arbitrum is an Ethereum scaling Layer 2 solution that operates an optimistic roll-up~\cite{kalodner2018arbitrum}.
+The roll-up chain is run on top of the Ethereum blockchain and contains all the Arbitrum contracts (called ArbOS).
+There is a  bridge contract (called the EThBridge) that resides on the Ethereum and serves as a bridge between two chains.
+To execute a transaction on a DApp that is running on Arbitrum, a user first sends a transaction to the bridge contract.
+This transaction only contains the instructions for calling a function and the data required for it.
+As as soon as this transaction is included in the Ethereum block, it will get timestamped and ordered.
+A validator, who is constantly watching the bridge contract for new transactions, sees the transaction, executes it and asserts the result of the execution to the ArbOS.
+Once the dispute challenge period is over, the transaction is final and the new state of the ArbOS will be inserted into the Ethereum.
+The bridge contract maintains all the data required for verification using which anyone can compute the state of the ArbOS and assure the executions have been performed correctly.
+
+% = = = = = = = = = = = = = = = = = = = = = = = = =  %
+\subsection{\cm on Arbitrum}
+
+\textit{Testing Platforms.} Arbitrum currently operates a test newtork with a bridge contract on the Ethereum Kovan testnet.
+To experiment with Arbitrum, we implemented a variant of \cm and run the same experiments that we previously performed on Layer 1 (Ethereum).
+To call functions on \cm, traders can (i) send transactions directly to the \href{https://kovan.etherscan.io/address/0xe681857defe8b454244e701ba63efaa078d7ea85}{Arbitrum EthBridge contract}, or (ii) use a relay server (called an \textit{Aggregator}) provided by the Arbitrum.
+These aggregators will group and send all pending transactions together as a single Kovan transaction to the EthBridge contract (and pay the gas).
+
+\input{tables/performance_Arbitrum.tex}
+
+\textit{Performance Evaluations.} Table~\ref{tab:arbitrum_performance} compares the cost of executing the maximum number of trades on Ethereum (Kovan testnet) and executing the same number of trades when running \cm on Layer 2 with Arbitrum.
+The fourth column of the Table represents the Ethereum gas cost for relaying the transaction to the Arbitrum EthBridge contract and is paid in ETH.
+Note that here we report the cost of sending the transaction directly to the Arbitrum EthBridge contract and not through the aggregator~\footnote{The Layer 1 cost reported on the Kovan block explorer represents the gas cost related to the entire batch of transactions.}.
+Th last column of the Table shows the actual cost of executing the transaction that is measured in ArbGas paid by the validators.
+ArbGas is basically used to measure the validators' resource usage and is significantly cheaper than Layer 1 gas (currently the testnet has 100 ArbGas for every Layer 1 gas unit, this ratio is even likely to improve in Arbitrum's next versions).
+
+ Table~\ref{tab:arbitrum_performance} shows that Arbitrum reduces the cost for executing the trades by around 99.9\% (a \cm variant implemented with linked list can handle 152 pairs of trades at most with the cost of 5,495,265 gas, while on Arbitrum the cost is 1,325 gas).
+Note that when using \cm on Arbitrum, we can basically process an infinite number of orders.
+In our \cm variant on Arbitrum, the token issuer does all the computation (both enqueuing and dequeuing).
+Thus we switch the priority queue to use a heap with dynamic array, which balances the expense of both operations (instead of optimizing for dequeuing in \texttt{closeMarket()}).
+Recall that on-chain, such a priority queue can only match 38 pairs at a cost of 5,372,679 gas.
+With Arbitrum roll-ups, 38 pairs cost 1,544 gas and ass the pairs increase, the cost is essentially constant.
+Submitting an order costs 2,005 gas on average as opposed to 207,932 on-chain.
+
+Our \cm variant is not the first roll-up based order book.
+Loopring 3.0\footnote{\url{https://loopring.org}} offers a continuous-time order book.
+The primary difference is that orders in Loopring 3.0 are submitted off-chain to the operator directly, whereas our variant uses on-chain submission so that the roll-up server does not need to be publicly reachable.
+Loopring 3.0 can operate near high frequency trading as order submission is unhampered by Ethereum, however its  roll-up proof does not ensure that the exchange did not reorder transactions, which is particularly problematic in a continuous-time order book.
+Traders who prioritize trade fairness might opt for a solution like our variant, while traders who want speed would vastly prefer the Loopring architecture which offers near-CEX speed while being non-custodial.
+Loopring leaves a regulatory hook whereas our variant could be nearly as difficult to regulate as a fully on-chain solution if the roll-up server was kept anonymous: Ethereum and Arbitrum themselves would be the only regulatory hooks.
+
+	% JC: Incorporate this comparison to Ethereum Optimism
+	% "The choice between one-round (e.g., “optimistic rollup”) and multi-round (e.g., Arbitrum Rollup) boils down to a tradeoff between on-chain cost and time to resolve a dispute.
+A one-round approach requires emulating a full call on-chain, which can be expensive — and this limits contracts to 		calls that can be executed comfortably within Ethereum’s global gas limit." -Ed Felten
+
+% = = = = = = = = = = = = = = = = = = = = = = = = =  %
+\subsection{Front-running on Arbitrum}
+
+Recall for running functions on \cm on Arbitrum, traders must first instantiate the truncation by sending it to the Arbitrum EthBridge contract.
+As as soon as this transaction is included in the Layer 1 (Ethereum) block it will get timestamped and ordered.
+Thus, potential for front-running on Arbitrum is same as those explained in~\ref{sec:front}.
 
@@
 
-\section{\cm Variant with Off-chain Closing}
-\label{sec:rollups}
-
-We have avoided augmenting \cm with centralized components and third party services as our research question concerns the feasibility of a system with a minimum of regulatory hooks.
+%\section{\cm Variant with Off-chain Closing}
+%\label{sec:rollups}
+%
+%We have avoided augmenting \cm with centralized components and third party services as our research question concerns the feasibility of a system with a minimum of regulatory hooks.
 However from a regulatory stance, there is a big difference between an architecture where the centralized component is publicly visible and interacted with by users (\eg most DEXes, rollup architectures like Loopring, and commit-chain solutions like TEX).
@@
 Traders still only interact with Ethereum.
-
-A function can be computed off-chain and the new state of the DApp, called a \textit{rollup}, is written back to the blockchain, accompanied by either (1) a proof that the function was executed correctly, or (2) a dispute resolution process that can resolve, on-chain, functions that are not executed correctly (\eg Arbitrum~\cite{kalodner2018arbitrum}).
+%
+%A function can be computed off-chain and the new state of the DApp, called a \textit{rollup}, is written back to the blockchain, accompanied by either (1) a proof that the function was executed correctly, or (2) a dispute resolution process that can resolve, on-chain, functions that are not executed correctly (\eg Arbitrum~\cite{kalodner2018arbitrum}).
 In the case of (1), validating the proof must be cheaper than running the function itself.
 There are two main approaches to (1): the first is to use cryptographic proof techniques (\eg SNARKS~\cite{BCGTV13,GGPR13} and variants~\cite{BBHR19}), and the second is to execute the function in a trusted execution environment (TEE; \eg Intel SGX) and validate the TEE's quote on-chain (\eg Ekiden~\cite{cheng2019ekiden}).\footnote{The TEE-based approach is mired by recent attacks on SGX~\cite{SGX1,SGX2,SGX3,SGX4}, however these attacks do not necessarily apply to the specifics of how SGX is used here, and safer TEE technologies like Intel TXT (\cf~\cite{ZBC+19}) can be substituted.}
-
-We implemented a variant of \cm using rollups on Arbitrum.\footnote{\url{https://offchainlabs.com} for more current details than the 2018 \textit{USENIX Security} paper~\cite{kalodner2018arbitrum}.} In this model, the token issuer (or other interested party) will run a dedicated server to watch Ethereum for function invocations submitted and sequenced on-chain, perform the function call off-chain, and write the resultant state on-chain.
+%
+%We implemented a variant of \cm using rollups on Arbitrum.\footnote{\url{https://offchainlabs.com} for more current details than the 2018 \textit{USENIX Security} paper~\cite{kalodner2018arbitrum}.} In this model, the token issuer (or other interested party) will run a dedicated server to watch Ethereum for function invocations submitted and sequenced on-chain, perform the function call off-chain, and write the resultant state on-chain.
 Anyone capable of running EVM code can verify the result.
@@
 With or without disputes, participants that validate the function calls for themselves can proceed knowing that the correct state will eventually be finalized.
-
-In our \cm variant with rollups, the token issuer does all the computation (both enqueuing and dequeuing).
+%
+%% JC: Incorporate this comparison to Ethereum Optimism
+%% "The choice between one-round (e.g., “optimistic rollup”) and multi-round (e.g., Arbitrum Rollup) boils down to a tradeoff between on-chain cost and time to resolve a dispute.
+A one-round approach requires emulating a full call on-chain, which can be expensive — and this limits contracts to calls that can be executed comfortably within Ethereum’s global gas limit." -Ed Felten
+%
+%%Mahsa: to discuss: Withdrawing Ethers from Arbitrum takes much time!
+when withdrawing, the withdrawal will be in a "pending" state during a "challenge period" of 830 blocks (30 - 120 minutes on Kovan).
+After that, the funds will be available on layer 1 in your lockbox
+%
+%In our \cm variant with rollups, the token issuer does all the computation (both enqueuing and dequeuing).
 Thus we switch the priority queue to use a heap with dynamic array, which balances the expense of both operations (instead of optimizing for dequeuing in \texttt{closeMarket()}).
@@
 Submitting an order costs 39,169 gas on average as opposed to 207,932 on-chain.
-
-Our \cm variant is not the first rollup-based order book.
+%
+%Our \cm variant is not the first rollup-based order book.
 Loopring 3.0\footnote{\url{https://loopring.org}} offers a continuous-time order book.

### 2021-04-07 LaTeX-ACM/sections/paper.tex
updates

--- 2021-03-10 LaTeX-USENIX/sections/paper.tex
@@
 
-\paragraph{Contributions.} We study fully on-chain markets through design and implementation with Solidity---a high-level programming language for Ethereum that is syntactically similar to Java~\cite{Ethereum41:online}.
+\textbf{Contributions.} We study fully on-chain markets through design and implementation with Solidity---a high-level programming language for Ethereum that is syntactically similar to Java~\cite{Ethereum41:online}.
 We choose Ethereum as a hostile environment for an order book: Ethereum is fully decentralized (hardest to regulate), network participation is open to anyone on the internet (strongest adversarial model), and, as a result, it is slow (a lower-bound benchmark).
@@
 
-\subsubsection*{Acknowledgements.}  The authors thanks the AMF (Autorité des Marchés Financiers) for supporting this research project.
+\begin{acks} 
+The authors thanks the AMF (Autorité des Marchés Financiers) for supporting this research project.
 J.
@@
 Moosavi acknowledges support from Fonds de Recherche du Québec - Nature et Technologies (FRQNT).
-
+\end{acks}
 %GitHub repo:  \footnote{\CallMarketRepo}

### 2021-04-12 LaTeX-USENIX/sections/paper.tex
revisions

@@
 % = = = = = = = = = = = = = = = = = = = = = = = = =  %
-\section{\cm on Layer 2}\label{sec:rollups}
-
-\subsection{Roll-ups}
-
-We have avoided augmenting \cm with centralized components and third party services as our research question concerns the feasibility of a system with a minimum of regulatory hooks.
-However from a regulatory stance, there is a big difference between an architecture where the centralized component is publicly visible and interacted with by users (\eg most DEXes, roll-up architectures like Loopring, and commit-chain solutions like TEX).
-We consider an alternative design that is almost as difficult to regulate as a fully on-chain solution.
-In this design, an off-chain component is introduced to boost performance but it only interacts with the Ethereum network and never directly with traders.
-Traders still only interact with Ethereum.
-
-% = = = = = = = = = = = = = = = = = = = = = = = = =  %
-		% MM:  Dont know to merger the following paragraph with this section?
-
-%A function can be computed off-chain and the new state of the DApp, called a \textit{rollup}, is written back to the blockchain, accompanied by either (1) a proof that the function was executed correctly, or (2) a dispute resolution process that can resolve, on-chain, functions that are not executed correctly (\eg Arbitrum~\cite{kalodner2018arbitrum}).
-In the case of (1), validating the proof must be cheaper than running the function itself.
-There are two main approaches to (1): the first is to use cryptographic proof techniques (\eg SNARKS~\cite{BCGTV13,GGPR13} and variants~\cite{BBHR19}), and the second is to execute the function in a trusted execution environment (TEE; \eg Intel SGX) and validate the TEE's quote on-chain (\eg Ekiden~\cite{cheng2019ekiden}).\footnote{The TEE-based approach is mired by recent attacks on SGX~\cite{SGX1,SGX2,SGX3,SGX4}, however these attacks do not necessarily apply to the specifics of how SGX is used here, and safer TEE technologies like Intel TXT (\cf~\cite{ZBC+19}) can be substituted.}
-% = = = = = = = = = = = = = = = = = = = = = = = = =  %
-
-\textit{Layer 2} solutions are a group of technologies that are designed and proposed to address specific drawbacks of executing transactions on \textit{Layer 1} (\ie Ethereum and other blockchains)~\cite{gudgeon2020sok}.
-These technologies focus on fast transaction throughput, reducing gas costs, or educing transaction latency.
-When using \cm, we strive to reduce the gas cost as performance is the main bottleneck.
-Thus, we choose a Layer 2 technology called \textit{roll-up} which aims at reducing the gas cost for operating on Layer 1 by taking the transaction executions off-chain and only using the Ethereum blockchain for storing data.
-In a roll-up, every transaction is executed by a server or cluster of servers known as \textit{validators} that can be run by a collection of users or third party operators (here they can be run by the token issuer).
-These validators then push the result of the executions (\ie updates in the EVM state) back to the Ethereum and assure the Ethereum network that the transactions have been executed correctly.
-
-There are two broad roll-up categories (i) \textit{zero knowledge} and (ii) \textit{optimistic} roll-ups, each taking a different approach to ensure the validity of off-chain transaction executions.
-A zero knowledge roll-up (\textit{a.k.a.} ZK-rollup) uses cryptographic validity proofs (SNARKS~\cite{BCGTV13,GGPR13}) which can be later verified on-chain.
-These proofs are heavy to compute (introduce a burden to the validators who generate them) but considered valid once posted to the Ethereum.
-An optimistic roll-up uses a side chain (a roll-up chain) that is run on top of Layer 1.
-Once the executions are performed, validators assert the new states of the roll-up chain to the Ethereum and wait for anyone to dispute these assertions.
-Although the dispute time delays result in a slower transaction finality, optimistic roll-ups substantially increase the performance by decreasing the gas cost.
-Therefore, we choose this roll-up solution to for the Layer 2 implementation of \cm.
-
-% = = = = = = = = = = = = = = = = = = = = = = = = =  %
-\subsection{Arbitrum}
-
-Arbitrum is an Ethereum scaling Layer 2 solution that operates an optimistic roll-up~\cite{kalodner2018arbitrum}.
-The roll-up chain is run on top of the Ethereum blockchain and contains all the Arbitrum contracts (called ArbOS).
-There is a  bridge contract (called the EThBridge) that resides on the Ethereum and serves as a bridge between two chains.
-To execute a transaction on a DApp that is running on Arbitrum, a user first sends a transaction to the bridge contract.
-This transaction only contains the instructions for calling a function and the data required for it.
-As as soon as this transaction is included in the Ethereum block, it will get timestamped and ordered.
-A validator, who is constantly watching the bridge contract for new transactions, sees the transaction, executes it and asserts the result of the execution to the ArbOS.
-Once the dispute challenge period is over, the transaction is final and the new state of the ArbOS will be inserted into the Ethereum.
-The bridge contract maintains all the data required for verification using which anyone can compute the state of the ArbOS and assure the executions have been performed correctly.
-
-% = = = = = = = = = = = = = = = = = = = = = = = = =  %
-\subsection{\cm on Arbitrum}
-
-\textit{Testing Platforms.} Arbitrum currently operates a test newtork with a bridge contract on the Ethereum Kovan testnet.
-To experiment with Arbitrum, we implemented a variant of \cm and run the same experiments that we previously performed on Layer 1 (Ethereum).
-To call functions on \cm, traders can (i) send transactions directly to the \href{https://kovan.etherscan.io/address/0xe681857defe8b454244e701ba63efaa078d7ea85}{Arbitrum EthBridge contract}, or (ii) use a relay server (called an \textit{Aggregator}) provided by the Arbitrum.
-These aggregators will group and send all pending transactions together as a single Kovan transaction to the EthBridge contract (and pay the gas).
-
-\input{tables/performance_Arbitrum.tex}
-
-\textit{Performance Evaluations.} Table~\ref{tab:arbitrum_performance} compares the cost of executing the maximum number of trades on Ethereum (Kovan testnet) and executing the same number of trades when running \cm on Layer 2 with Arbitrum.
-The fourth column of the Table represents the Ethereum gas cost for relaying the transaction to the Arbitrum EthBridge contract and is paid in ETH.
-Note that here we report the cost of sending the transaction directly to the Arbitrum EthBridge contract and not through the aggregator~\footnote{The Layer 1 cost reported on the Kovan block explorer represents the gas cost related to the entire batch of transactions.}.
-Th last column of the Table shows the actual cost of executing the transaction that is measured in ArbGas paid by the validators.
-ArbGas is basically used to measure the validators' resource usage and is significantly cheaper than Layer 1 gas (currently the testnet has 100 ArbGas for every Layer 1 gas unit, this ratio is even likely to improve in Arbitrum's next versions).
-
- Table~\ref{tab:arbitrum_performance} shows that Arbitrum reduces the cost for executing the trades by around 99.9\% (a \cm variant implemented with linked list can handle 152 pairs of trades at most with the cost of 5,495,265 gas, while on Arbitrum the cost is 1,325 gas).
-Note that when using \cm on Arbitrum, we can basically process an infinite number of orders.
-In our \cm variant on Arbitrum, the token issuer does all the computation (both enqueuing and dequeuing).
-Thus we switch the priority queue to use a heap with dynamic array, which balances the expense of both operations (instead of optimizing for dequeuing in \texttt{closeMarket()}).
-Recall that on-chain, such a priority queue can only match 38 pairs at a cost of 5,372,679 gas.
-With Arbitrum roll-ups, 38 pairs cost 1,544 gas and ass the pairs increase, the cost is essentially constant.
-Submitting an order costs 2,005 gas on average as opposed to 207,932 on-chain.
-
-Our \cm variant is not the first roll-up based order book.
-Loopring 3.0\footnote{\url{https://loopring.org}} offers a continuous-time order book.
-The primary difference is that orders in Loopring 3.0 are submitted off-chain to the operator directly, whereas our variant uses on-chain submission so that the roll-up server does not need to be publicly reachable.
-Loopring 3.0 can operate near high frequency trading as order submission is unhampered by Ethereum, however its  roll-up proof does not ensure that the exchange did not reorder transactions, which is particularly problematic in a continuous-time order book.
-Traders who prioritize trade fairness might opt for a solution like our variant, while traders who want speed would vastly prefer the Loopring architecture which offers near-CEX speed while being non-custodial.
-Loopring leaves a regulatory hook whereas our variant could be nearly as difficult to regulate as a fully on-chain solution if the roll-up server was kept anonymous: Ethereum and Arbitrum themselves would be the only regulatory hooks.
-
-	% JC: Incorporate this comparison to Ethereum Optimism
-	% "The choice between one-round (e.g., “optimistic rollup”) and multi-round (e.g., Arbitrum Rollup) boils down to a tradeoff between on-chain cost and time to resolve a dispute.
-A one-round approach requires emulating a full call on-chain, which can be expensive — and this limits contracts to 		calls that can be executed comfortably within Ethereum’s global gas limit." -Ed Felten
-
-% = = = = = = = = = = = = = = = = = = = = = = = = =  %
-\subsection{Front-running on Arbitrum}
-
-Recall for running functions on \cm on Arbitrum, traders must first instantiate the truncation by sending it to the Arbitrum EthBridge contract.
-As as soon as this transaction is included in the Layer 1 (Ethereum) block it will get timestamped and ordered.
-Thus, potential for front-running on Arbitrum is same as those explained in~\ref{sec:front}.
-
-% = = = = = = = = = = = = = = = = = = = = = = = = =  %
 
@@
 
+% = = = = = = = = = = = = = = = = = = = = = = = = =  %
+\section{\cm on Layer 2}\label{sec:rollups}
+
+\subsection{Roll-ups}
+
+We have avoided augmenting \cm with centralized components and third party services as our research question concerns the feasibility of a system with a minimum of regulatory hooks.
+However from a regulatory stance, there is a big difference between an architecture where the centralized component is publicly visible and interacted with by users (\eg most DEXes, roll-up architectures like Loopring, and commit-chain solutions like TEX).
+We consider an alternative design that is almost as difficult to regulate as a fully on-chain solution.
+In this design, an off-chain component is introduced to boost performance but it only interacts with the Ethereum network and never directly with traders.
+Traders still only interact with Ethereum.
+
+% = = = = = = = = = = = = = = = = = = = = = = = = =  %
+		% MM:  Dont know to merger the following paragraph with this section?
+
+% = = = = = = = = = = = = = = = = = = = = = = = = =  %
+
+\textit{Layer 2} solutions are a group of technologies that are designed and proposed to address specific drawbacks of executing transactions on \textit{Layer 1} (\ie Ethereum and other blockchains)~\cite{gudgeon2020sok}.
+These technologies focus on fast transaction throughput, reducing gas costs, or educing transaction latency.
+When using \cm, we strive to reduce the gas cost as performance is the main bottleneck.
+Thus, we choose a Layer 2 technology called \textit{roll-up} which aims at reducing the gas cost for operating on Layer 1 by taking the transaction executions off-chain and only using the Ethereum blockchain for storing data.
+In a roll-up, every transaction is executed by a server or cluster of servers known as \textit{validators} that can be run by a collection of users or third party operators (here they can be run by the token issuer).
+These validators then push the result of the executions (\ie updates in the EVM state) back to the Ethereum and assure the Ethereum network that the transactions have been executed correctly.
+
+A function can be computed off-chain and the new state of the DApp, called a \textit{rollup}, is written back to the blockchain, accompanied by either (1) a proof that the function was executed correctly, or (2) a dispute resolution process that can resolve, on-chain, functions that are not executed correctly (\eg Arbitrum~\cite{kalodner2018arbitrum}).
+In the case of (1), validating the proof must be cheaper than running the function itself.
+There are two main approaches: (1a) the first is to use cryptographic proof techniques (\eg SNARKS~\cite{BCGTV13,GGPR13} and variants~\cite{BBHR19}).
+This is called a \textit{zk-rollup}.
+Note that the proofs are heavy to compute (introducing a burden to the validators who generate them) but considered valid once posted to the Ethereum.
+The second approach (1b) is to execute the function in a trusted execution environment (TEE; \eg Intel SGX) and validate the TEE's quote on-chain (\eg Ekiden~\cite{cheng2019ekiden}).\footnote{The TEE-based approach is mired by recent attacks on SGX~\cite{SGX1,SGX2,SGX3,SGX4}, however these attacks do not necessarily apply to the specifics of how SGX is used here, and safer TEE technologies like Intel TXT (\cf~\cite{ZBC+19}) can be substituted.} Approach (2) is called an \textit{optimistic roll-up}.
+Although the dispute time delays result in a slower transaction finality, optimistic roll-ups substantially increase the performance by decreasing the gas cost.
+
+%It uses a side chain (a roll-up chain) that is run on top of Layer 1.
+Once the executions are performed, validators assert the new states of the roll-up chain to the Ethereum and wait for anyone to dispute these assertions.
+
+%Therefore, we choose this roll-up solution to for the Layer 2 implementation of \cm.
+
+% = = = = = = = = = = = = = = = = = = = = = = = = =  %
+\subsection{Arbitrum}
+
+Arbitrum is an Ethereum Layer 2 scaling solution that operates as an optimistic roll-up~\cite{kalodner2018arbitrum}.
+Arbitrum runs entire DApps inside its environment, which acts like a container and requires special bridge contacts to interact with `normal' (or L1) Ethereum DApps.
+To deploy a DApp on Arbitrum, or to execute a function on an existing Arbitrum DApp, the transaction is sent to an L1 Arbitrum contract called an inbox.
+The transaction is not executed, it is only recorded (as calldata) by the inbox contract.
+Like any other transactions on Ethereum, miners determine the order of the transactions sent to the inbox.
+A set of validators (open to anyone) are watching the inbox contract for new transactions.
+Once an inbox transaction is finalized in an Ethereum block, validators will execute the transaction and asserts the result of the execution to other validators on a sidechain called ArbOS.
+Once the dispute challenge period is over, the new state of ArbOS will be inserted into Ethereum.
+As the inbox contract maintains all Arbitrum transactions, anyone can recompute the entire current state of the ArbOS and file a dispute if executions are not performed correctly.
+Disputes are adjudicated by Ethereum itself and require essentially constant gas costs, regardless of the size of the gas costs of the transaction being disputed.
+
+% = = = = = = = = = = = = = = = = = = = = = = = = =  %
+\subsection{\cm on Arbitrum}
+
+\textit{Testing Platforms.} Arbitrum currently operates a test network with a bridge contract on the Ethereum Kovan testnet.
+To experiment with Arbitrum, we implemented a variant of \cm and run the same experiments that we previously performed on Layer 1 (Ethereum).
+To call functions on \cm, traders can (i) send transactions directly to the inbox contract called the \href{https://kovan.etherscan.io/address/0xe681857defe8b454244e701ba63efaa078d7ea85}{Arbitrum EthBridge}, or (ii) use a relay server (called an \textit{Aggregator}) provided by the Arbitrum.
+These aggregators will group and send all pending transactions together as a single Kovan transaction to the EthBridge contract (and pay the gas).
+
+%\input{tables/performance_Arbitrum.tex}
+
+%Table~\ref{tab:arbitrum_performance} compares the cost of executing the maximum number of trades on Ethereum (Kovan testnet) and executing the same number of trades when running \cm on Layer 2 with Arbitrum.
+The fourth column of the Table represents the Ethereum gas cost for relaying the transaction to the Arbitrum EthBridge contract and is paid in ETH.
+Note that here we report the cost of sending the transaction directly to the Arbitrum EthBridge contract and not through the aggregator~\footnote{The Layer 1 cost reported on the Kovan block explorer represents the gas cost related to the entire batch of transactions.}.
+
+In our \cm variant on Arbitrum, the token issuer does all the computation (both enqueuing and dequeuing).
+Thus we switch the priority queue to use a heap with dynamic array, which balances the expense of both operations (instead of optimizing for dequeuing in \texttt{closeMarket()}).
+Recall that without a rollup, such a priority queue can only match 38 pairs at a cost of 5,372,679 gas.
+With Arbitrum roll-ups, 38 pairs costs only 1,544 in L1 gas (a 99.9\% savings).
+This is effectively the cost of recording the callmarket() function call in the inbox, which is 103 bytes of calldata.
+As the number of pairs increases, L1 gas cost is constant.
+For traders submitting an order, the cost is reduced from  207,932 to 2,005.
+
+While the runtime of a transaction is no longer an issue for Ethereum, it is still an issue for the validators.
+Like Ethereum miners, validators do measure the amount of gas (called ArbGas in Arbitrum) a transaction takes although Arbitrum emmulates EVM code with its own different OpCodes.
+Thus, ArbGas with a roll-up and L1 gas without a roll-up are not directly comparable but both increase and decrease proportionately with the complexity of running the function.
+Closing a market with 38 pairs costs 46,705,693 ArbGas.
+Until Arbitrum deploys on mainnet, the price of ArbGas in Gwei (or USD) is unknown but it is thought to be relatively very cheap.
+
+Our \cm variant is not the first roll-up based order book.
+Loopring 3.0\footnote{\url{https://loopring.org}} offers a continuous-time order book.
+The primary difference is that orders in Loopring 3.0 are submitted off-chain to the operator directly, whereas our variant uses on-chain submission so that the roll-up server does not need to be publicly reachable.
+Loopring 3.0 can operate near high frequency trading as order submission is unhampered by Ethereum, however its  roll-up proof does not ensure that the exchange did not reorder transactions, which is particularly problematic in a continuous-time order book.
+Traders who prioritize trade fairness might opt for a solution like our variant, while traders who want speed would vastly prefer the Loopring architecture which offers near-CEX speed while being non-custodial.
+Loopring leaves a regulatory hook whereas our variant could be nearly as difficult to regulate as a fully on-chain solution if the roll-up server was kept anonymous: Ethereum and Arbitrum themselves would be the only regulatory hooks.
+
+	% JC: Incorporate this comparison to Ethereum Optimism
+	% "The choice between one-round (e.g., “optimistic rollup”) and multi-round (e.g., Arbitrum Rollup) boils down to a tradeoff between on-chain cost and time to resolve a dispute.
+A one-round approach requires emulating a full call on-chain, which can be expensive — and this limits contracts to 		calls that can be executed comfortably within Ethereum’s global gas limit." -Ed Felten
+
+% = = = = = = = = = = = = = = = = = = = = = = = = =  %
+\subsection{Front-running on Arbitrum}
+
+Recall for running functions on \cm on Arbitrum, traders must first instantiate the truncation by sending it to the Arbitrum EthBridge contract.
+As as soon as this transaction is included in the Layer 1 (Ethereum) block it will get timestamped and ordered.
+Thus, potential for front-running on Arbitrum is same as those explained in~\ref{sec:front}.
+
 %= = = = = =  = =  =  Rollups=  = = = = = = = = =%

### 2021-04-28 LaTeX-ACM/sections/abstract.tex
edits on the paper

--- 2021-01-12 LaTeX-USENIX/sections/abstract.tex
@@
 Fortunately for regulators, most trading volume in blockchain-based assets is still on centralized service providers for performance reasons.
-However this leaves the following research questions we address in this paper: (i) is secure trading (\ie resistant to front-running and price manipulation) even feasible as a fully `on-chain' service on a public blockchain, (ii) what is its performance benchmark, and (iii) what is the performance impact of novel techniques (\eg `rollups') in closing the performance gap?
+However this leaves the following research questions we address in this paper: (i) is secure trading (\ie resistant to front-running and price manipulation) even feasible as a fully `on-chain' service on a public blockchain, (ii) what is its performance benchmark, and (iii) what is the performance impact of novel techniques (\eg `roll-ups') in closing the performance gap?
 
-To answer these questions, we `learn by doing' and custom design an Ethereum-based call market (or batch auction) exchange, \cm, with favourable security properties.
+To answer these questions, we `learn by doing' and custom design an Ethereum-based call market (or batch auction) exchange, \cm, with favorable security properties.
 We conduct a variety of optimizations and experiments to demonstrate that this technology cannot expect to exceed a few hundred trade executions per block (\ie ~13s window of time).

### 2021-04-28 LaTeX-ACM/sections/paper.tex
edits on the paper

@@
 Blockchain exchange services allow order-based trading of digital currencies, tokens, and other digital assets.
-Such exchanges are a key component to blockchain-based economic activity.
+Such exchanges are key components to blockchain-based economic activity.
 
@@
 They are concerned by their limited ability to intervene when trading is conducted on decentralized networks that, like Ethereum, run on the open internet.
-Order-driven trading can happen fully `on-chain' and this was experimented within the early days of Ethereum, but it has been largely abandoned for performance reasons in favour of running on centralized servers.
+Order-driven trading can happen fully `on-chain' and this was experimented within the early days of Ethereum, but it has been largely abandoned for performance reasons in favor of running on centralized servers.
 More specifically, the core functionality is performed off-chain (\eg matching orders) while other aspects (\eg loading accounts, order cancellation) might be performed on-chain.
@@
 We choose Ethereum as a hostile environment for an order book: Ethereum is fully decentralized (hardest to regulate), network participation is open to anyone on the internet (strongest adversarial model), and, as a result, it is slow (a lower-bound benchmark).
-Generally if an application is feasible on Ethereum, it will also be feasible and only run faster on a private (or permissioned) blockchain (\eg Hyperledger), which is a blockchain operated by authorized network nodes only, generally visible to regulators.
+Generally, if an application is feasible on Ethereum, it will also be feasible and only run faster on a private (or permissioned) blockchain (\eg Hyperledger), which is a blockchain operated by authorized network nodes only, generally visible to regulators.
 
 Our proof-of-concept, \cm, is an extensible base class suitable for experiments.
-\cm is designed from a security perspective: users only trust their assets to \cm's auditable code (non-custodial) and not to a third party; all operations are transparent; and we nearly eliminate the ability for adversarial network nodes to profit from front-running orders.
+\cm is designed from a security perspective: users only trust their assets to \cm's auditable code (non-custodial) and not to a third part, all operations are transparent, and we nearly eliminate the ability for adversarial network nodes to profit from front-running orders.
 In fact, we believe we are the first to design a decentralized application that actually leverages front-running (\ie miner extractable value~\cite{daian2019flash}) for the benefit of the system (see Section~\ref{sec:close}).
 
-While Solidity and its compiled bytecode is like many common programming languages, it also has quirks that require experimentation to best optimize performance (\eg factoring in the gas costs of operations, gas refunds, limits to Solidity's object oriented design, clearing mappings, \etc).
+While Solidity and its compiled bytecode is like many common programming languages, it also has quirks that require experimentation to best optimize performance (\eg factoring in the gas costs of operations, gas refunds, limits to Solidity's object-oriented design, clearing mappings, \etc).
 We test five priority queues---the core data structure of the call market---and various options for cleaning up our data once finished with it.
@@
 In Ethereum, \emph{transactions} encode the bytecode of user-written \emph{decentralized applications} (DApps) to be stored on the blockchain; and the function calls made to the DApp.
-Every execution of every function call is a validated by all honest, participating nodes to correct; a property that is robust against a fraction of faulty and malicious network nodes (or more precisely, their accumulated computational power).
+Every execution of every function call is validated by all honest, participating nodes to correct; a property that is robust against a fraction of faulty and malicious network nodes (or more precisely, their accumulated computational power).
 Once transactions are agreed upon, all honest participants will have identical sets of transactions in the same order.
@@
 
-\subsection{Trading Blockchain-based Assets}
+\subsection{Trading Blockchain-Based Assets}
 
@@
 Exchanges for blockchain-based assets (also called crypto assets by enthusiasts) can operate the same way, using a centralized exchange (CEX) design where a firm (\eg Binance, Bitfinex, \etc) operates the platform as a trusted third party in every aspect: custodianship over assets/currency being traded, exchanging assets fairly, offering the best possible price execution.
-Security breaches and fraud in centralized exchanges  (\eg MtGox~\cite{TheHisto45:online}, QuadrigaCX~\cite{SEBIOrde83:online}, and many others) have become a common source of lost funds for users, while accusations of unfair trade execution have been levelled but are difficult to prove.
+Security breaches and fraud in centralized exchanges  (\eg MtGox~\cite{TheHisto45:online}, QuadrigaCX~\cite{SEBIOrde83:online}, and many others) have become a common source of lost funds for users, while accusations of unfair trade execution have been leveled but are difficult to prove.
 Today, CEXes are often regulated as other money service businesses---this provides some ability for the government to conduct financial tracking but does little to provide consumer protection against fraud.
@@
 In this paper, we focus on benchmarking an order book for the public blockchain Ethereum.
-Ethereum is widely-used and we stand to learn the most from working in a performance-hostile environment.
+Ethereum is widely used and we stand to learn the most from working in a performance-hostile environment.
 Exchanges could be given their own dedicated blockchain, where trade execution logic can be coded into the network protocol.
@@
 \paragraph{On-chain Dealers.} An advantage of on-chain trading is that other smart contracts, not just human users, can initiate trades, enabling broader decentralized finance (DeFi) applications.
-This has fuelled a resurgence in on-chain exchange but through a quote-driven design rather than an order-driven one.
+This has fueled a resurgence in on-chain exchange but through a quote-driven design rather than an order-driven one.
 Automated market makers  (\eg Uniswap) have all the trust advantages of an on-chain order book, plus they are very efficient relative to an on-chain order book.
@@
 Finally, there is a complicated difference in their price dynamics (\eg market impact of a trade, slippage between the best bid/ask and actual average execution price, \etc)---deserving of an entire research paper to precisely define.
-We leave it as an assertion that with equal liquidity, order books have more favourable price dynamics for traders.
+We leave it as an assertion that with equal liquidity, order books have more favorable price dynamics for traders.
 
@@
 A non-custodial DEX solves the big issue of a CEX---the operator stealing the funds---however trade execution is still not provably fair, funds can still be indirectly stolen by a malicious exchange executing unauthorized trades, and server downtime is a common frustration for traders.
-An enhancement is to prove that trade execution is correct (\eg Loopring) but these proofs have blindspots (discussed in section~\ref{sec:rollups}).
+An enhancement is to prove that trade execution is correct (\eg Loopring) but these proofs have blind spots (discussed in section~\ref{sec:rollups}).
 
@@
 Orders are collected and placed into the order book over a window of time (\eg 1 or more blocks), then the market is closed and the orders are processed in batch: the best bids are matched to the best asks in order.
-If the prices overlap, the miner keeps the difference (which they could extract anyways through front-running).
-Call markets largely side-step front-running attacks from other traders because reordering trades has no impact (discussed more in section~\ref{sec:front}).
+If the prices overlap, the miner keeps the difference (which they could extract regardless through front-running).
+Call markets largely side step front-running attacks from other traders because reordering trades has no impact (discussed more in section~\ref{sec:front}).
 The paper does not include an implementation and was envisioned as running on a custom blockchain (Ethereum was still in development in 2014).
@@
 
-\paragraph{Other Academic Literature.} There are numerous industry projects on blockchain-based exchanges and order books but most of the academic literature is on topics that are related but tangential to the mechanics of trade execution.
+\paragraph{Other Academic Literature.} There are numerous industry projects on blockchain-based exchanges and order books, but most of the academic literature is on topics that are related but tangential to the mechanics of trade execution.
 Early (and some recent) literature consider trade execution under encryption (\ie dark markets) for securities~\cite{TP07,YSLT10,TW12,cartlidge2019mpc} and futures~\cite{massacci2018futuresmex}.
 A number of projects consider structuring derivatives in smart contracts---Velocity ~\cite{eskandari2017feasibility}, Findel ~\cite{biryukov2017findel}---but once issued, the derivative can be traded using exchanges.
-Atomic swaps (\ie payment vs delivery) are necessary for settling trades and some general approaches include Arwen~\cite{heilman2020arwen} and Tesseract~\cite{bentov2017tesseract}.
+Atomic swaps (\ie payment vs.
+delivery) are necessary for settling trades and some general approaches include Arwen~\cite{heilman2020arwen} and Tesseract~\cite{bentov2017tesseract}.
 
 The most similar academic work to this paper is the TEX exchange~\cite{khalil2019tex}.
-TEX is also an implementation of an order book, however it uses on-chain and off-chain components, and does not answer our research question of how feasible an on-chain order book is.
+TEX is also an implementation of an order book; however, it uses on-chain and off-chain components, and does not answer our research question of how feasible an on-chain order book is.
 We later compare it to our variant with roll-ups in Section~\ref{sec:rollups}.
@@
 The main downside is that honest traders cannot submit their orders and leave, they must interact in a second round to reveal their orders.
-The second solution is to sequence transactions according to some rule, either at the protocol level~\cite{MZGA20} or as a third party service~\cite{Kla20} (a regulatory hook).
+The second solution is to sequence transactions according to some rule, either at the protocol level~\cite{MZGA20} or as a third-party service~\cite{Kla20} (a regulatory hook).
 These are very recent works and are not available for experimentation on Ethereum yet (although Chainlink has announced an intention\footnote{A.
@@
 In designing \cm within Ethereum's gas model, performance is the main bottleneck.
-For a call market, closing the market and processing all the orders is the most time consuming step.
+For a call market, closing the market and processing all the orders are the most time-consuming steps.
 The most critical design decision is the data structure for holding orders.
-While data structures are well studied for many languages, Solidity/EVM has its own unique aspects (\eg gas refunds, a relatively cheap mapping data structure, only partial support for object oriented programming) that create difficulties in assessing which will perform best without actually deploying and evaluating each variant.
+While data structures are well studied for many languages, Solidity/EVM has its own unique aspects (\eg gas refunds, a relatively cheap mapping data structure, only partial support for object-oriented programming) that create difficulties in assessing which will perform best without actually deploying and evaluating each variant.
 
@@
 In most circumstances, the market closing algorithm does not have to consider any deeper bids/asks from the list when choosing whether the current best bid and ask can be fulfilled.
-The only exceptions are in the case of a tie on price or a cancelled order, both of which we return to later.
+The only exceptions are in the case of a tie on price or a canceled order, both of which we return to later.
 For this reason, the ideal data structure for storing bids/asks is a \textit{priority queue} (see Table~\ref{tab:PQ_API}) where each order's priority is its price.
@@
 \item \textbf{Heap with Dynamic Array.} A heap is a type of binary tree data structure that comes in two forms of a (i) Max-Heap and (ii) Min-Heap.
-All the nodes of the tree are in a specific order and the root always represents the highest priority item of the data structure (the largest and smallest values in the Max-Heap and Min-Heap respectively).
-We implement a PQ with a heap that stores its data in a dynamically-sized array.
+All the nodes of the tree are in a specific order, and the root always represents the highest priority item of the data structure (the largest and smallest values in the Max-Heap and Min-Heap respectively).
+We implement a PQ with a heap that stores its data in a dynamically sized array.
 
-\item \textbf{Heap with Static Array.} A heap can be also represented by a Solidity storage array in which the storage is statically allocated.
+\item \textbf{Heap with Static Array.} A heap can also be represented by a Solidity storage array in which the storage is statically allocated.
 To do this, we pass the required size of the array as a constructor parameter to the PQ smart contract.
@@
 \paragraph{Enqueue Performance.} We implemented, deployed, and tested each PQ using Truffle and Ganache.
-We tried a variety of tests (including testing the full call market with each variant) with consistent results in performance.
+We tried a variety of tests (including testing the full-call market with each variant) with consistent results in performance.
 A simple test to showcase the performance profile is shown in Figure~\ref{fig:random_insertion}.
@@
 Based on our manual estimates (EVM does not expose the refund counter), every variant receives the maximum gas refund possible (\ie half the total cost of the transaction).
-In other words, each of them actually consumes twice the \texttt{gasUsed} amount in gas before the refund, however none of them are better or worse based on how much of a refund they generate.
+In other words, each of them actually consumes twice the \texttt{gasUsed} amount in gas before the refund.
+However, none of them are better or worse based on how much of a refund they generate.
 
@@
 This is in accordance with the theoretical worst-case time complexity for each.
-However, (i) the linked list variants are materially cheaper than the heap variants at dequeuing, and (ii) dequeuing in a call market must be done as a batch, whereas enqueuing is paid for one at a time by the trader submitting the order, and (iii) Ethereum will not permit more than hundreds of orders so the asymptotic behaviour is not a significant factor.
+However, (i) the linked list variants are materially cheaper than the heap variants at dequeuing, and (ii) dequeuing in a call market must be done as a batch, whereas enqueuing is paid for one at a time by the trader submitting the order, and (iii) Ethereum will not permit more than hundreds of orders so the asymptotic behavior is not a significant factor.
 For these reasons, we suggest using a linked list variant for this specific application.
@@
 
-\subsection{Cost/Benefit of Cleaning up After Yourself}
+\subsection{Cost/Benefit of Cleaning Up After Yourself}
 \label{sec:gasrefund}
@@
 For this reason, stored variables persist for a long time and, at first glance, it seems pointless to free up variable storage (and unclear what `free up' even means).
-Once the current state of the EVM is established by a node, it can forget about every historical variable changes and only concern itself with the variables that have non-zero value (as a byte-string for non-integers) in the current state (uninitialized variables in Ethereum have the value zero by default).
+Once the current state of the EVM is established by a node, it can forget about every historical variable changes and only concern itself with the variables that have non-zero value (as a byte string for non-integers) in the current state (uninitialized variables in Ethereum have the value 0 by default).
 Therefore, freeing up variables will reduce the amount of state Ethereum nodes need to maintain going forward.
@@
 For this reason, some EVM operations cost a negative amount of gas.
-That is, the gas is refunded to the sender at the end of the transaction, however (1) the refund is capped at 50\% of the total gas cost of the transaction, and (2) the block gas limit applies to the pre-refunded amount (\ie a transaction receiving a full refund can cost up to 5.5M gas with a 11M limit).
+That is, the gas is refunded to the sender at the end of the transaction, however (1) the refund is capped at 50\% of the total gas cost of the transaction, and (2) the block gas limit applies to the pre-refunded amount (\ie a transaction receiving a full refund can cost up to 5.5M gas with an 11M limit).
 Negative gas operations include:
@@
 
-\item \texttt{SELFDESTRUCT}.
+\item \texttt{SELF-DESTRUCT}.
 This operation destroys the contract that calls it and refunds its balance (if any) to a designated receiver address.
-\texttt{SELFDESTRUCT} operation does not remove the initial byte code of the contract from the chain.
+The  \texttt{SELFDESTRUCT} operation does not remove the initial byte code of the contract from the chain.
 It always refunds 24,000 gas.
-For example, if a contract A stores a single non-zero integer and contract B stores 100 non-zero integers, the \texttt{SELFDESTRUCT} refund for both is the same (24,000 gas).
+For example, if contract A stores a single non-zero integer and contract B stores 100 non-zero integers, the \texttt{SELFDESTRUCT} refund for both is the same (24,000 gas).
 
@@
 So in order to account for refunds in Tables~\ref{tab:PQUnitTests}, we calculate them manually.
-First we need to figure out exactly how much storage is being cleared or how many smart contracts are being destroyed, then we multiply these numbers by 24,000 and 15,000 respectively.
+First, we need to figure out exactly how much storage is being cleared or how many smart contracts are being destroyed, then we multiply these numbers by 24,000 and 15,000 respectively.
 
@@
 The lesson here is that gas refunds incentivize developers to clean up storage variables they will not use again, but it is highly contextual as to whether it will pay for itself.
-Further the cap on the maximum refund means that refunds are not fully received for large cleanup operations (however removing the cap impacts the miners' incentives to include the transaction).
+Further, the cap on the maximum refund means that refunds are not fully received for large cleanup operations (however removing the cap impacts the miners' incentives to include the transaction).
 This is a complicated and under-explored area of Ethereum in the research literature.
@@
 We looked at the \textit{worst-case} for performance which is when every submitted bid and ask is marketable (\ie will require fulfillment).
-In the first two columns, we determine the highest number of orders that can be processed in a single call to the \texttt{closeMarket()} and not exceed the the current Ethereum block gas limit of 11,741,495.
-Since Ethereum will become more efficient over time, we also were interested in how much gas it would cost to execute 1000 pairs of orders which is given in the third column.
-The fourth column indicates the cost of submitting a bid or ask --- since this costs will vary depending on how many orders are already submitted (recall Figure~\ref{fig:random_insertion}), we average the cost of 200 order submissions.
+In the first two columns, we determine the highest number of orders that can be processed in a single call to the \texttt{closeMarket()} and not exceed the current Ethereum block gas limit of 11,741,495.
+Since Ethereum will become more efficient over time, we were also interested in how much gas it would cost to execute 1000 pairs of orders, which is given in the third column.
+The fourth column indicates the cost of submitting a bid or ask --- since this cost will vary depending on how many orders are already submitted (recall Figure~\ref{fig:random_insertion}), we average the cost of 200 order submissions.
 
@@
 In a call market, the outcome of A and B will be exactly equivalent.
-There is no threat from miners reordering transactions or traders offering higher gas rates to have their orders executed before other orders already broadcasted.
+There is no threat from miners reordering transactions or traders offering higher gas rates to have their orders executed before other orders already broadcast.
 
@@
 
-\subsection{Cleaning Up Revisted}
+\subsection{Cleaning Up Revisited}
 
@@
 
-In Solidity, it is not possible to delete an entire mapping without individually zero-ing out each entry key-by-key.
+In Solidity, it is not possible to delete an entire mapping without individually zeroing out each entry key-by-key.
 At the same time, it is wasteful to let an entire mapping sit in the EVM when it will never be referenced again.
@@
 
-\cm is designed as base class that can be extended and customized. We discuss potential modifications here.
+\cm is designed as a base class that can be extended and customized. We discuss potential modifications here.
 
@@
 A common trading rule (that does resist front-running) is to fill ties in proportion to their volume (\ie \textit{pro rata} allocation)\footnote{If Alice and Bob bid the same price for 100 tokens and 20 tokens respectively, and there are only 60 tokens left in marketable asks, Alice receives 50 and Bob 10.} however this approach does not always work.
-Consider the following corner-case: 3 equally priced bids of 1 non-divisible token and 1 ask at the same price.
-There is no good option: (1) the bids could all be dropped (fair but not market efficient), (2) bids could be prioritized based on time as in \cm (front-running is viable, but in this corner case only), or (3) the bid could be randomly chosen (\cf Libra~\cite{mavroudis2019libra}); blockchain `randomness' is generally deterministic and manipulatable by miners~\cite{bonneau2015random,buenz2017proofs} and counter-measures could take a few blocks to select~\cite{boneh2018verifiable}).
+Consider the following corner case: 3 equally priced bids of 1 non-divisible token and 1 ask at the same price.
+There is no good option: (1) the bids could all be dropped (fair but not market efficient), (2) bids could be prioritized based on time as in \cm (front-running is viable, but in this corner case only), or (3) the bid could be randomly chosen (\cf Libra~\cite{mavroudis2019libra}); blockchain `randomness' is generally deterministic and manipulatable by miners~\cite{bonneau2015random,buenz2017proofs} and countermeasures could take a few blocks to select~\cite{boneh2018verifiable}).
 
@@
 Finally, cancellations have a performance impact.
-Cancelled orders can be removed from the underlying data structure   or accumulated in a list that is cross-checked when closing the market.
-Removing orders requires a more verbose structure than a priority queue (\eg a binary search tree instead of a heap; or methods to traverse a linked list rather than only pulling from the head).
+Canceled orders can be removed from the underlying data structure   or accumulated in a list that is cross-checked when closing the market.
+Removing orders requires a more verbose structure than a priority queue (\eg a self-balancing binary search tree instead of a heap; or methods to traverse a linked list rather than only pulling from the head).
 While client software could help point out where the order is in the data structure, the order book can change between submitting the cancellation request and running the method.
@@
 Call markets are heralded for fair price discovery.
-This is why many exchanges use a call market at the end of the day to determine the closing price of an asset, which is an important price both optically (it is well-published) and operationally (many derivates settle based on the closing price).
+This is why many exchanges use a call market at the end of the day to determine the closing price of an asset, which is an important price both optically (it is well published) and operationally (many derivatives settle based on the closing price).
 We purposely do not compute a `market clearing price' with \cm because miners can easily manipulate the price (\ie include a single wash trade at the price they want fixed), although they forgo profit for doing so.
 This is not merely hypothetical---Uniswap (the prominent quote-drive, on-chain exchange) prices have been manipulated to exploit other DeFi applications relying on them.
-Countermeasures to protect Uniswap price integrity could also apply to \cm: (1) taking a rolling mediant of prices over time, and (2) using it alongside other sources for the same price and forming a consensus.
+Countermeasures to protect Uniswap price integrity could also apply to \cm: (1) taking a rolling median of prices over time, and (2) using it alongside other sources for the same price and forming a consensus.
 While \cm does not emit a market clearing price, it can be computed by a web application examining the order book at market close.
@@
 As a simple base class, \cm is a one-shot market.
-However it can be extended to re-open with a clean order book after \texttt{closeMarket()} is run.
+However it can be extended to reopen with a clean order book after \texttt{closeMarket()} is run.
 Modifiers can enforce when the market operates openly (collecting orders) and when close can be run.
@@
 If the call market runs as a DApp on Ethereum, it seems difficult to open and close the market every block.
-Someone needs to call the \texttt{closeMarket()} for every block (we return to who this is next) but the market will only work as intended if miners execute this function after every \texttt{submitBid()} and \texttt{submitAsk()} invocation.
+Someone needs to call the \texttt{closeMarket()} for every block (we return to who this is later) but the market will only work as intended if miners execute this function after every \texttt{submitBid()} and \texttt{submitAsk()} invocation.
 Since price improvements are paid to the miners, the miner is actually incentivized to run \texttt{closeMarket()} last to make the most profit.
@@
 One solution requires a modified closing function, \texttt{closeMarket(n)}, that only processes $n$ orders at a time until the order book is empty (this is sensible design in any case to safeguard against the order book from locking up because the number of orders exceeds the gas limit to process them).
-Once the time window for submitting orders is past, a new market is created (without settling the previous market).
+Once the time window for submitting orders has past, a new market is created (without settling the previous market).
 Every order submission on the new market also requires to run, say, \texttt{closeMarket(10)} on the older market, thus progressively closing the previous market while accepting orders to the new market.
-This solution pattern has two issues: first, amortizing the cost of closing the market amongst the early traders of the new market is an added incentive to not submit orders early to the market; the second related issue is if not enough traders submit orders in the new market, the old market never closes (resulting in a backlog of old markets waiting to close).
+This solution pattern has two issues: first, amortizing the cost of closing the market amongst the early traders of the new market is an added incentive to not submit orders early to the market; the second issue is if not enough traders submit orders in the new market, the old market never closes (resulting in a backlog of old markets waiting to close).
 
@@
 In \cm, both the tokens and ETH that a trader want to potentially use in the order book are pre-loaded into the contract.
-Consider Alice who holds a token and decides she wants to trade it for ETH.
+Consider Alice, who holds a token and decides she wants to trade it for ETH.
 In this model, she must first transfer the tokens to the contract and then submit an ask order.
@@
 If she waits for confirmation, this introduces a delay.
-This delay seems reasonable but we point out a few ways it could be addressed:
+This delay seems reasonable but we point out a few options it could be addressed:
 
@@
 If \cm is coded securely, it is unconcerning to allow the approval to stand long-term and the trader never has to lock up their tokens in the DApp.
-The issue is that there is no guarantee that the tokens are actually available when the market closes (\ie Alice can approve a DApp to spend 100 tokens even if she only has 5 tokens, or no tokens).
+The issue is that there is no guarantee that the tokens are actually available when the market closes (\ie Alice can approve a DApp to spend 100 tokens even if she only has 5 tokens or no tokens).
 In this case, \cm would optimistically try to transfer the tokens and if it fails, move onto the next order.
@@
 
-\item \textbf{Use a Fidelity Bond.} Traders could post some amount of tokens as a fidelity bond, and be allowed to submit orders up to 100x this value using approve.
+\item \textbf{Use a Fidelity Bond.} Traders could post some number of tokens as a fidelity bond, and be allowed to submit orders up to 100x this value using approve.
 If a trade fails because the pledged tokens are not available, the fidelity bond is slashed as punishment.
@@
 \end{enumerate}
+
+% = = = = = = = = = = = = = = = = = = = = = = = = =  %
+\section{\cm on Layer 2}\label{sec:rollups}
+
+\subsection{Roll-ups}
+
+We have avoided augmenting \cm with centralized components and third-party services as our research question concerns the feasibility of a system with a minimum of regulatory hooks.
+However from a regulatory stance, there is a big difference between an architecture where the centralized component is publicly visible and interacted with by users (\eg most DEXes, roll-up architectures like Loopring, and commit-chain solutions like TEX).
+We consider an alternative design that is almost as difficult to regulate as a fully on-chain solution.
+In this design, an off-chain component is introduced to improve performance, but it only interacts with the Ethereum network and never directly with traders.
+Traders still only interact with Ethereum.
+
+% = = = = = = = = = = = = = = = = = = = = = = = = =  %
+		% MM:  Dont know to merger the following paragraph with this section?
+
+% = = = = = = = = = = = = = = = = = = = = = = = = =  %
+
+\textit{Layer 2} solutions are a group of technologies that are designed and proposed to address specific drawbacks of executing transactions on \textit{Layer 1} (\ie Ethereum and other blockchains)~\cite{gudgeon2020sok}.
+These technologies focus on fast transaction throughput, reducing gas costs, or educing transaction latency.
+When using \cm, we strive to reduce the gas cost as performance is the main bottleneck.
+Thus, we choose a Layer 2 technology called \textit{roll-up} which aims at reducing the gas cost for operating on Layer 1 by taking the transaction executions off-chain and only using the Ethereum blockchain for storing data.
+In a roll-up, every transaction is executed by a server or cluster of servers known as \textit{validators} that can be run by a collection of users or third party operators (here they can be run by the token issuer).
+These validators then push the result of the executions (\ie updates in the EVM state) back to the Ethereum and assure the Ethereum network that the transactions have been executed correctly.
+
+A function can be computed off-chain and the new state of the DApp, called a \textit{rollup}, is written back to the blockchain, accompanied by either (1) a proof that the function was executed correctly, or (2) a dispute resolution process that can resolve, on-chain, functions that are not executed correctly (\eg Arbitrum~\cite{kalodner2018arbitrum}).
+In the case of (1), validating the proof must be cheaper than running the function itself.
+There are two main approaches: (1a) the first is to use cryptographic proof techniques (\eg SNARKS~\cite{BCGTV13,GGPR13} and variants~\cite{BBHR19}).
+This is called a \textit{zk-rollup}.
+Note that the proofs are heavy to compute (introducing a burden to the validators who generate them) but considered valid once posted to the Ethereum.
+The second approach (1b) is to execute the function in a trusted execution environment (TEE; \eg Intel SGX) and validate the TEE's quote on-chain (\eg Ekiden~\cite{cheng2019ekiden}).\footnote{The TEE-based approach is mired by recent attacks on SGX~\cite{SGX1,SGX2,SGX3,SGX4}, however these attacks do not necessarily apply to the specifics of how SGX is used here, and safer TEE technologies like Intel TXT (\cf~\cite{ZBC+19}) can be substituted.} Approach (2) is called an \textit{optimistic roll-up}.
+Although the dispute time delays result in a slower transaction finality, optimistic roll-ups substantially increase the performance by decreasing the gas cost.
+
+%It uses a side chain (a roll-up chain) that is run on top of Layer 1.
+Once the executions are performed, validators assert the new states of the roll-up chain to the Ethereum and wait for anyone to dispute these assertions.
+
+%Therefore, we choose this roll-up solution to for the Layer 2 implementation of \cm.
+
+% = = = = = = = = = = = = = = = = = = = = = = = = =  %
+\subsection{Arbitrum}
+
+Arbitrum is an Ethereum Layer 2 scaling solution that operates as an optimistic roll-up~\cite{kalodner2018arbitrum}.
+Arbitrum runs entire DApps inside its environment, which acts like a container and requires special bridge contacts to interact with `normal' (or L1) Ethereum DApps.
+To deploy a DApp on Arbitrum, or to execute a function on an existing Arbitrum DApp, the transaction is sent to an L1 Arbitrum contract called an inbox.
+The transaction is not executed, it is only recorded (as calldata) by the inbox contract.
+Like any other transactions on Ethereum, miners determine the order of the transactions sent to the inbox.
+A set of validators (open to anyone) are watching the inbox contract for new transactions.
+Once an inbox transaction is finalized in an Ethereum block, validators will execute the transaction and asserts the result of the execution to other validators on a sidechain called ArbOS.
+Once the dispute challenge period is over, the new state of ArbOS will be inserted into Ethereum.
+As the inbox contract maintains all Arbitrum transactions, anyone can recompute the entire current state of the ArbOS and file a dispute if executions are not performed correctly.
+Disputes are adjudicated by Ethereum itself and require essentially constant gas costs, regardless of the size of the gas costs of the transaction being disputed.
+
+% = = = = = = = = = = = = = = = = = = = = = = = = =  %
+\subsection{\cm on Arbitrum}
+
+\textit{Testing Platforms.} Arbitrum currently operates a test network with a bridge contract on the Ethereum Kovan testnet.
+To experiment with Arbitrum, we implemented a variant of \cm and run the same experiments that we previously performed on Layer 1 (Ethereum).
+To call functions on \cm, traders can (i) send transactions directly to the inbox contract called the \href{https://kovan.etherscan.io/address/0xe681857defe8b454244e701ba63efaa078d7ea85}{Arbitrum EthBridge}, or (ii) use a relay server (called an \textit{Aggregator}) provided by the Arbitrum.
+These aggregators will group and send all pending transactions together as a single Kovan transaction to the EthBridge contract (and pay the gas).
+
+%\input{tables/performance_Arbitrum.tex}
+
+%Table~\ref{tab:arbitrum_performance} compares the cost of executing the maximum number of trades on Ethereum (Kovan testnet) and executing the same number of trades when running \cm on Layer 2 with Arbitrum.
+The fourth column of the Table represents the Ethereum gas cost for relaying the transaction to the Arbitrum EthBridge contract and is paid in ETH.
+Note that here we report the cost of sending the transaction directly to the Arbitrum EthBridge contract and not through the aggregator~\footnote{The Layer 1 cost reported on the Kovan block explorer represents the gas cost related to the entire batch of transactions.}.
+
+In our \cm variant on Arbitrum, the token issuer does all the computation (both enqueuing and dequeuing).
+Thus we switch the priority queue to use a heap with dynamic array, which balances the expense of both operations (instead of optimizing for dequeuing in \texttt{closeMarket()}).
+Recall that without a roll-up, such a priority queue can only match 38 pairs at a cost of 5,372,679 gas.
+With Arbitrum roll-ups, 38 pairs costs only 1,544 in L1 gas (a 99.9\% savings).
+This is effectively the cost of recording the \texttt{closeMarket()} function call in the inbox, which is 103 bytes of calldata.
+As the number of pairs increases, L1 gas cost is constant.
+For traders submitting an order, the cost is reduced from  207,932 to 2,005.
+
+While the runtime of a transaction is no longer an issue for Ethereum, it is still an issue for the validators.
+Like Ethereum miners, validators do measure the amount of gas (called ArbGas in Arbitrum) a transaction takes although Arbitrum emulates EVM code with its own different OpCodes.
+Thus, ArbGas with a roll-up and L1 gas without a roll-up are not directly comparable but both increase and decrease proportionately with the complexity of running the function.
+Closing a market with 38 pairs costs 46,705,693 ArbGas.
+Until Arbitrum deploys on mainnet, the price of ArbGas in Gwei (or USD) is unknown but it is thought to be relatively very cheap.
+
+Our \cm variant is not the first roll-up-based order book.
+Loopring 3.0\footnote{\url{https://loopring.org}} offers a continuous-time order book.
+The primary difference is that orders in Loopring 3.0 are submitted off-chain to the operator directly, whereas our variant uses on-chain submission so that the roll-up server does not need to be publicly reachable.
+Loopring 3.0 can operate near high-frequency trading as order submission is unhampered by Ethereum.
+However its  roll-up proof does not ensure that the exchange did not reorder transactions, which is particularly problematic in a continuous-time order book.
+Traders who prioritize trade fairness might opt for a solution like our variant, while traders who want speed would vastly prefer the Loopring architecture which offers near-CEX speed while being non-custodial.
+Loopring leaves a regulatory hook whereas our variant could be nearly as difficult to regulate as a fully on-chain solution if the roll-up server was kept anonymous: Ethereum and Arbitrum themselves would be the only regulatory hooks.
+
+	% JC: Incorporate this comparison to Ethereum Optimism
+	% "The choice between one-round (e.g., “optimistic rollup”) and multi-round (e.g., Arbitrum Rollup) boils down to a tradeoff between on-chain cost and time to resolve a dispute.
+A one-round approach requires emulating a full call on-chain, which can be expensive — and this limits contracts to 		calls that can be executed comfortably within Ethereum’s global gas limit." -Ed Felten
+
+% = = = = = = = = = = = = = = = = = = = = = = = = =  %
+\subsection{Front-running on Arbitrum}
+
+Recall for running functions on \cm on Arbitrum, traders must first instantiate the truncation by sending it to the Arbitrum EthBridge contract.
+As as soon as this transaction is included in the Layer 1 (Ethereum) block, it will get time-stamped and ordered.
+Thus, potential for front-running on Arbitrum is same as those explained in~\ref{sec:front}.
 
@@
 Even if it is too slow today, there is little reason for developers not to offer it as a fallback solution that accompanies every token.
-With future improvements to blockchain scalability, it could become the defacto trading method.
+With future improvements to blockchain scalability, it could become the de facto trading method.
 
-It may seem paradoxical or unethical to build for regulators exactly what they worry about, however we agreed that it was too difficult to answer our research questions without actual implementation and experimentation.
+It may seem paradoxical or unethical to build for regulators exactly what they worry about.
+However we agreed that it was too difficult to answer our research questions without actual implementation and experimentation.
 \cm is proof of concept code that implements only enough to understand the feasibility of on-chain trading and we release the code for reproducibility.
 However it is not production code, it is unpolished, it has no UI, and we have no intention of promoting it for adoption.
-Finally, by understanding the `pain points' in the design, we found we were constantly tugged toward centralized components (Ethereum alarm clock, meta-transactions, rollup servers, \etc) which could serve as regulatory hooks even if the service is mainly on-chain.
+Finally, by understanding the `pain points' in the design, we found we were constantly tugged toward centralized components (Ethereum alarm clock, meta-transactions, roll-up servers, \etc) which could serve as regulatory hooks even if the service is mainly on-chain.
 

### 2021-05-10 LaTeX-ACM/sections/paper.tex
frontrunning attacks sketch
changes

@@
 
+%\textblue{Notes on Front-running Table:}
+%\begin{itemize}
+%\item{Mallory squeezes her order before Alice's.} Mallory sees that there is an incoming bid at 200 for 10 of an asset, and currently, the best offer is at 190 for the same volume.
+In this case, Mallory sends her bid at 190 for 10 and immediately inserts the sell order at 200.
+If Alice's transaction gets executed, Mallory will profit on the price difference.
+%\textblue{Sandwich Attacks:} These attacks apply to automated market makers (\ie UniSwap) and exploit a particular feature of AMMs, which is for every swap that takes place on an AMM, the price of the token being swapped shifts slightly.
+In this case, if Mallory realizes that there is an incoming trade of asset A for asset B, She immediately inserts a bid for asset B.
+This transaction will increase the price of asset B significantly and when Alice's transaction gets executed on the AMM, she'll receive less number of asset B as she is purchasing it at an inflated price.
+Right after Alice's transaction goes through, Mallory will sell the amount of asset B she has bought at a higher price.
+%\end{itemize}
+\input{tables/frontrunning.tex}
+
 The primary motivation for using a call market, as opposed to a continuous-time order book, is to mitigate front-running attacks~\cite{clark2014decentralizing,eskandari2019sok,daian2019flash}.
@@
 Efficient algorithms for miners to automatically find MEV opportunities is an open research problem.
+
+% JC: Add option for burning the price improvement, keeping it in Lissy, give it to charity, \etc.
 
@@
 % = = = = = = = = = = = = = = = = = = = = = = = = =  %
+\subsection{Token Bridges with Arbitrum}
+
+% = = = = = = = = = = = = = = = = = = = = = = = = =  %
 \subsection{\cm on Arbitrum}
@@
 Thus we switch the priority queue to use a heap with dynamic array, which balances the expense of both operations (instead of optimizing for dequeuing in \texttt{closeMarket()}).
-Recall that without a roll-up, such a priority queue can only match 38 pairs at a cost of 5,372,679 gas.
+\textblue{On Arbitrum, heaps are XX\% more efficient than non-Heaps for submitting orders and YY\% less efficient for closing.} Recall that without a roll-up, such a priority queue can only match 38 pairs at a cost of 5,372,679 gas.
 With Arbitrum roll-ups, 38 pairs costs only 1,544 in L1 gas (a 99.9\% savings).
@@
 As as soon as this transaction is included in the Layer 1 (Ethereum) block, it will get time-stamped and ordered.
-Thus, potential for front-running on Arbitrum is same as those explained in~\ref{sec:front}.
+Thus, potential for front-running on Arbitrum is same as those explained in~\ref{sec:front}.'
+
+\textblue{Say something about \texttt{block.coinbase()} and Arbitrum.}
 

### 2021-05-14 LaTeX-ACM/sections/paper.tex
small tweaks

@@
 
-We have avoided augmenting \cm with centralized components and third-party services as our research question concerns the feasibility of a system with a minimum of regulatory hooks.
+We have avoided augmenting \cm with centralized components and third party services as our research question concerns the feasibility of a system with a minimum of regulatory hooks.
 However from a regulatory stance, there is a big difference between an architecture where the centralized component is publicly visible and interacted with by users (\eg most DEXes, roll-up architectures like Loopring, and commit-chain solutions like TEX).
 We consider an alternative design that is almost as difficult to regulate as a fully on-chain solution.
-In this design, an off-chain component is introduced to improve performance, but it only interacts with the Ethereum network and never directly with traders.
+In this design, an off-chain component is introduced to boost performance but it only interacts with the Ethereum network and never directly with traders.
 Traders still only interact with Ethereum.
-
-% = = = = = = = = = = = = = = = = = = = = = = = = =  %
-		% MM:  Dont know to merger the following paragraph with this section?
-
-% = = = = = = = = = = = = = = = = = = = = = = = = =  %
 
@@
  \subsubsection*{Availability} 
-The Solidity source code for \cm, Truffle test files, and Arbitrum dependencies are available in a GitHub repository\footnote{\CallMarketRepo}.
+The Solidity source code for \cm, Truffle test files, and Arbitrum dependencies are available in a GitHub repository (non-anonymous link omitted).
 We have also deployed \cm on Ethereum's testnet Rinkeby with flattened (single file) source code of just the \cm base class and priority queue implementations.

### 2021-05-14 LaTeX-ACM/sections/paper.tex
front running is a mess still

@@
 
-Our research group is actively collaborating with our jurisdiction's (Quebec, Canada) financial regulator, the Autorité des Marchés Financiers (AMF), to help them forecast how trading can be impacted by blockchain technology.
+% JC: Our research group is actively collaborating with our jurisdiction's (Quebec, Canada) financial regulator, the Autorité des Marchés Financiers (AMF), to help them forecast how trading can be impacted by blockchain technology.
+
+Our research group is actively collaborating with our jurisdiction's financial regulator (name withheld for anonymity) to help them forecast how trading can be impacted by blockchain technology.
 This paper addresses their concerns about the feasibility of a `worst-case scenario' where a trading platform is anonymously deployed on a public blockchain, like Ethereum, and runs autonomously without any further intervention from an externally visible entity.
@@
 %\end{itemize}
+
 \input{tables/frontrunning.tex}
 
-The primary motivation for using a call market, as opposed to a continuous-time order book, is to mitigate front-running attacks~\cite{clark2014decentralizing,eskandari2019sok,daian2019flash}.
-Consider a sequence of 100 orders submitted within a window of time to market A, and the same sequence is randomly shuffled and submitted to market B.
-If A and B are continuous, the orders that are executed in A could be quite different from B.
-In a call market, the outcome of A and B will be exactly equivalent.
+As we illustrate in Table~\ref{tab:front}, call markets have a unique profile of resilience against \emph{front-running attacks}~\cite{clark2014decentralizing,eskandari2019sok,daian2019flash} that differs somewhat from continuous-time markets and automated market makers.
+Traders are sometimes distinguished as \emph{makers} (adds orders to a market) and \emph{takers} (trades against a pre-existing, unexecuted orders).
+A continuous market has both.
+All traders with an automated market maker are takers, while the investors who provide tokens (or liquidity) to the AMM for trading are makers.
+Under our definition, a call market only has makers: the only way to have a trade executed is to submit an order.
+The front-running attacks in Table~\ref{tab:front} are sub-categorized, using a recent SoK~\cite{eskandari2019sok}, as being \emph{Insertion}, \emph{Displacement}, and \emph{Suppression}.
+To illustrate the difference, we will consider the first three attacks in the table.
+
+ fronting attacks: 
+t
+
+(i) in an \emph{displacement attack}, Mallory knows of a transaction from Alice and inserts her transaction before Alice's and does not care what happens to Alice's transaction; (ii) in an \emph{insertion attack}, Mallory similarly inserts a transaction before Alice and ensures Alice's transaction is the next to run, and (iii) in a \emph{suppression attack}, Mallory displaces all future transactions for some period of time.
+Mallory can be a miner which can freely order transactions within the blocks it creates, or Mallory can be a fast user (or bot) who can quickly react to Alice's broadcasted but unconfirmed transactions, likely offering higher gas fees to have her transactions prioritized over Alice's.
+Later in Section~\ref{sec:frontarb}, we discuss a third kind of participant: sequencers.
+
+Consider the first two attacks in Table~\ref{tab:front}. Talk about our cattegories from front-running paper.
+
+ Call markets are less vulnerable to these basic insertion and displacement attacks because they do not have any time priority (e.g., if you were to shuffle the order of all orders submitted within a window of time to a call market, the outcome would be exactly the same).
+A different way to mitigate these attacks is to add confidentiality on the orders (cite Tex, Hisham) which
+
+ A, and the same sequence is randomly shuffled and submitted to market B.
+In a call market, the outcome of A and B will be exactly equivalent, which is not true in the other types.The remove of time priority
+
  There is no threat from miners reordering transactions or traders offering higher gas rates to have their orders executed before other orders already broadcast.
@@
 Potential for front-running still exists around ties on price and order cancellations (both discussed in the next section).
-Finally, \textit{displacement attacks}~\cite{eskandari2019sok} are possible where competitive orders are delayed long enough for the market to close without them or the adversary fills up the current market (which caps the number of orders) to ensure other orders cannot be added.
+Finally, \textit{supression attacks}~\cite{eskandari2019sok} are possible where competitive orders are delayed long enough for the market to close without them or the adversary fills up the current market (which caps the number of orders) to ensure other orders cannot be added.
 Both are expensive attacks.
@@
 \subsection{Front-running on Arbitrum}
+\label{sec:frontarb}
 

### 2021-05-19 LaTeX-ACM/sections/paper.tex
arb new data + small tweaks on text

--- 2021-05-14 LaTeX-ACM/sections/paper.tex
@@
 To experiment with Arbitrum, we implemented a variant of \cm and run the same experiments that we previously performed on Layer 1 (Ethereum).
-To call functions on \cm, traders can (i) send transactions directly to the inbox contract called the \href{https://kovan.etherscan.io/address/0xe681857defe8b454244e701ba63efaa078d7ea85}{Arbitrum EthBridge}, or (ii) use a relay server (called an \textit{Aggregator}) provided by the Arbitrum.
+To call functions on \cm, traders can (i) send transactions directly to the inbox contract \href{https://kovan.etherscan.io/address/0x76bF1345224fE606E2aB38B8E52B83512328A9DF}, or (ii) use a relay server (called an \textit{Aggregator}) provided by the Arbitrum.
 These aggregators will group and send all pending transactions together as a single Kovan transaction to the EthBridge contract (and pay the gas).
@@
 Thus we switch the priority queue to use a heap with dynamic array, which balances the expense of both operations (instead of optimizing for dequeuing in \texttt{closeMarket()}).
-\textblue{On Arbitrum, heaps are XX\% more efficient than non-Heaps for submitting orders and YY\% less efficient for closing.} Recall that without a roll-up, such a priority queue can only match 38 pairs at a cost of 5,372,679 gas.
+\textblue{On Arbitrum, heaps are XX\% more efficient than non-Heaps for submitting orders and YY\% less efficient for closing (find the \% from the data provided below )} Recall that without a roll-up, such a priority queue can only match 38 pairs at a cost of 5,372,679 gas.
 With Arbitrum roll-ups, 38 pairs costs only 1,544 in L1 gas (a 99.9\% savings).
@@
 For traders submitting an order, the cost is reduced from  207,932 to 2,005.
+
+ % Arbitrum V5 test results:
+
+ % Heap Dynamic Array: worst case matching, 48 pairs of orders: tx hash: 0x2c0f5b5ba3539eb72018c08856c156c8098edcfd35db80f929a13c0aa6f9cc01, L1 gas: 1632, L2 arbgas: 1,039,351
+ % (https://explorer5.arbitrum.io/#/tx/0x2c0f5b5ba3539eb72018c08856c156c8098edcfd35db80f929a13c0aa6f9cc01)
 
@@
 \textblue{Say something about \texttt{block.coinbase()} and Arbitrum.}
+
+\textblue{Say something about sequencer.}
 
@@
 We have also deployed \cm on Ethereum's testnet Rinkeby with flattened (single file) source code of just the \cm base class and priority queue implementations.
-It is visible and can be interacted with here: \href{https://rinkeby.etherscan.io/address/0x0d91de29c531d074853a5cef7cf9dfeb9c6ec4e0}{[etherscan.io]}; while the Arbitrum variant is here: \href{https://explorer.arbitrum.io/#/tx/0x1828d7eb6a7a9b9ec479f07e8149c6172bb89a101571963b5cf690132bdf009b}{[explorer.offchainlabs.com]}.
+It is visible and can be interacted with here: \href{https://rinkeby.etherscan.io/address/0x0d91de29c531d074853a5cef7cf9dfeb9c6ec4e0}{[etherscan.io]}; while the Arbitrum variant is here: \href{https://explorer5.arbitrum.io/#/address/0xce17be19aa80396ae1a1c9f8dd386c48c1533f52}{[explorer5.offchainlabs.com]}.
 

### 2021-05-19 Code/L2-HardHat/scripts/Submission/1_Deposits.js

@@ -1,0 +1,67 @@
+
+
+
+const hre = require("hardhat");
+const ethers = require("ethers");
+const addressDappToken ='0x9D83C3c3e39d12416c395Da096988511B57E712F'; //the address of the ERC20 token; it has the same address as Kovan
+var CallMarketaddress;
+
+
+require('dotenv').config();
+
+const main = async () => {
+   
+    const accounts = await hre.ethers.getSigners();
+
+    const infuraKey = process.env.INFURA_KEY
+    if(!infuraKey) throw new Error("No INFURA_KEY set.")
+
+    const walletPrivateKey = process.env.DEVNET_PRIVKEY
+    if(!walletPrivateKey) throw new Error("No DEVNET_PRIVKEY set.")
+
+
+    const l1Provider = new ethers.providers.JsonRpcProvider(process.env.L1RPC)
+    const l2Provider = new ethers.providers.JsonRpcProvider(process.env.L2RPC)
+    const signer = new ethers.Wallet(walletPrivateKey)
+
+    const l1Signer = signer.connect(l1Provider);
+    const l2Signer = signer.connect(l2Provider);
+
+
+
+
+    const L2CallMarket = await (await hre.ethers.getContractFactory('CallMarket')).connect(l2Signer)
+    
+    console.log("Deploying CallMarket to L2")
+    
+    const l2CallMarket = await L2CallMarket.deploy()
+    await l2CallMarket.deployed()
+    console.log(`deployed to ${l2CallMarket.address}`)
+
+    CallMarketaddress = l2CallMarket.address;
+
+    const l2DappToken = await (await hre.ethers.getContractAt('DappToken',addressDappToken )).connect(l2Signer)
+    
+    
+    await l2DappToken.connect(l2Signer).approve(CallMarketaddress, 1000000000);
+       
+    await l2CallMarket.connect(l2Signer).depositToken(addressDappToken, 1000000000);
+
+    const totalTokenbalance = await l2CallMarket.totalTokenBalance(l2Signer.address);
+    const totalEtherbalance = await l2CallMarket.totalEtherBalance(l2Signer.address);
+
+    console.log('The token balance of account[0] (Bob) is:', totalTokenbalance.toNumber());
+    console.log('The Ether balance of account[0] (Bob) is:', totalEtherbalance.toNumber());
+    console.log('********************************************');
+
+
+
+
+}
+
+main()
+  .then(() => process.exit(0))
+  .catch(error => {
+    console.error(error);
+    process.exit(1);
+  });

### 2021-05-19 Code/L2-HardHat/scripts/Submission/2_Submit_Asks.js

@@ -1,0 +1,67 @@
+
+
+
+const hre = require("hardhat");
+const ethers = require("ethers");
+const addressDappToken ='0x9D83C3c3e39d12416c395Da096988511B57E712F'; //the address of the ERC20 token; it has the same address as Kovan
+const CallMarketaddress ='0x244B16EB248cD6e8e72220BA17588A04fA418695';
+
+
+require('dotenv').config();
+
+const main = async () => {
+   
+    const accounts = await hre.ethers.getSigners();
+
+    const infuraKey = process.env.INFURA_KEY
+    if(!infuraKey) throw new Error("No INFURA_KEY set.")
+
+    const walletPrivateKey = process.env.DEVNET_PRIVKEY
+    if(!walletPrivateKey) throw new Error("No DEVNET_PRIVKEY set.")
+
+
+    const l1Provider = new ethers.providers.JsonRpcProvider(process.env.L1RPC)
+    const l2Provider = new ethers.providers.JsonRpcProvider(process.env.L2RPC)
+    const signer = new ethers.Wallet(walletPrivateKey)
+
+    const l1Signer = signer.connect(l1Provider);
+    const l2Signer = signer.connect(l2Provider);
+
+
+    var maximum = 100;
+    var minimum = 1;
+
+    const l2CallMarket = await (await hre.ethers.getContractAt('CallMarket',CallMarketaddress )).connect(l2Signer)
+
+    await l2CallMarket.openMarket();
+
+    var receipt = null;
+    var array = [];
+    
+    for(let j = 1; j <= 200  ; j++){
+
+
+        var randomnumber = Math.floor(Math.random() * (maximum - minimum + 1)) + minimum;
+        receipt = await l2CallMarket.connect(l2Signer).submitAsk(randomnumber, 1);
+            array.push(j);
+            //console.log('Ask',j,' volume is equal to:', 1);
+            console.log('Ask',j);
+            console.log('the tx receipt is:', receipt);
+            console.log('******************************');
+        } 
+        console.log(array.length,'asks have been succsessfully submitted');
+        console.log('********************************************');
+    
+   
+    
+
+
+}
+
+main()
+  .then(() => process.exit(0))
+  .catch(error => {
+    console.error(error);
+    process.exit(1);
+  });
+

### 2021-05-19 Code/L2-HardHat/scripts/closing/1_Deposits.js

@@ -1,0 +1,86 @@
+
+
+
+const hre = require("hardhat");
+const ethers = require("ethers");
+const addressDappToken ='0x9D83C3c3e39d12416c395Da096988511B57E712F'; //the address of the ERC20 token; it has the same address as Kovan
+var CallMarketaddress;
+
+
+require('dotenv').config();
+
+const main = async () => {
+   
+    const accounts = await hre.ethers.getSigners();
+
+    const infuraKey = process.env.INFURA_KEY
+    if(!infuraKey) throw new Error("No INFURA_KEY set.")
+
+    const walletPrivateKey = process.env.DEVNET_PRIVKEY
+    if(!walletPrivateKey) throw new Error("No DEVNET_PRIVKEY set.")
+
+
+    const l1Provider = new ethers.providers.JsonRpcProvider(process.env.L1RPC)
+    const l2Provider = new ethers.providers.JsonRpcProvider(process.env.L2RPC)
+    const signer = new ethers.Wallet(walletPrivateKey)
+
+    const l1Signer = signer.connect(l1Provider);
+    const l2Signer = signer.connect(l2Provider);
+
+
+
+
+    const L2CallMarket = await (await hre.ethers.getContractFactory('CallMarket')).connect(l2Signer)
+    
+    console.log("Deploying CallMarket to L2")
+    
+    const l2CallMarket = await L2CallMarket.deploy()
+    await l2CallMarket.deployed()
+    console.log(`deployed to ${l2CallMarket.address}`)
+
+    CallMarketaddress = l2CallMarket.address;
+
+    const l2DappToken = await (await hre.ethers.getContractAt('DappToken',addressDappToken )).connect(l2Signer)
+    
+    
+    await l2DappToken.connect(l2Signer).approve(CallMarketaddress, 10000000000);
+       
+    await l2CallMarket.connect(l2Signer).depositToken(addressDappToken, 10000000000);
+
+    const totalTokenbalance = await l2CallMarket.totalTokenBalance(l2Signer.address);
+    const totalEtherbalance = await l2CallMarket.totalEtherBalance(l2Signer.address);
+
+    console.log('The token balance of account[0] (Bob) is:', totalTokenbalance.toNumber());
+    console.log('The Ether balance of account[0] (Bob) is:', totalEtherbalance.toNumber());
+    console.log('********************************************');
+
+
+
+
+
+        //Following "value" is in wei.
+        //1 ether = 1,000,000,000,000,000,000 wei
[…]

### 2021-05-19 Code/L2-HardHat/scripts/closing/2_Submit_Asks.js

@@ -1,0 +1,69 @@
+
+
+
+const hre = require("hardhat");
+const ethers = require("ethers");
+const addressDappToken ='0x9D83C3c3e39d12416c395Da096988511B57E712F'; //the address of the ERC20 token; it has the same address as Kovan
+const CallMarketaddress ='0xcE17BE19aa80396Ae1A1C9f8dd386C48c1533F52';
+
+
+require('dotenv').config();
+
+const main = async () => {
+   
+    const accounts = await hre.ethers.getSigners();
+
+    const infuraKey = process.env.INFURA_KEY
+    if(!infuraKey) throw new Error("No INFURA_KEY set.")
+
+    const walletPrivateKey = process.env.DEVNET_PRIVKEY
+    if(!walletPrivateKey) throw new Error("No DEVNET_PRIVKEY set.")
+
+
+    const l1Provider = new ethers.providers.JsonRpcProvider(process.env.L1RPC)
+    const l2Provider = new ethers.providers.JsonRpcProvider(process.env.L2RPC)
+    const signer = new ethers.Wallet(walletPrivateKey)
+
+    const l1Signer = signer.connect(l1Provider);
+    const l2Signer = signer.connect(l2Provider);
+
+
+   
+
+    const l2CallMarket = await (await hre.ethers.getContractAt('CallMarket',CallMarketaddress )).connect(l2Signer)
+
+    await l2CallMarket.openMarket();
+
+    var receipt = null;
+    var array = [];
+    
+    for(let j = 38; j >= 1  ; j--){
+        
+            receipt = await l2CallMarket.connect(l2Signer).submitAsk(j, 1);
+            array.push(j);
+            //console.log('Ask',j,' volume is equal to:', 1);
+            console.log('Ask',j);
+            //console.log('the tx receipt is:', receipt);
+            console.log('******************************');
+        
+
+        }
+
+
+        
+        console.log(array.length,'asks have been succsessfully submitted');
+        console.log('********************************************');
+    
+   
+    
+
+
+}
+
+main()
+  .then(() => process.exit(0))
+  .catch(error => {
+    console.error(error);
+    process.exit(1);
+  });
+

### 2021-05-19 Code/L2-HardHat/scripts/closing/3_Submit_Bids.js

@@ -1,0 +1,69 @@
+
+
+
+const hre = require("hardhat");
+const ethers = require("ethers");
+const addressDappToken ='0x9D83C3c3e39d12416c395Da096988511B57E712F'; //the address of the ERC20 token; it has the same address as Kovan
+const CallMarketaddress ='0xcE17BE19aa80396Ae1A1C9f8dd386C48c1533F52';
+
+
+require('dotenv').config();
+
+const main = async () => {
+   
+    const accounts = await hre.ethers.getSigners();
+
+    const infuraKey = process.env.INFURA_KEY
+    if(!infuraKey) throw new Error("No INFURA_KEY set.")
+
+    const walletPrivateKey = process.env.DEVNET_PRIVKEY
+    if(!walletPrivateKey) throw new Error("No DEVNET_PRIVKEY set.")
+
+
+    const l1Provider = new ethers.providers.JsonRpcProvider(process.env.L1RPC)
+    const l2Provider = new ethers.providers.JsonRpcProvider(process.env.L2RPC)
+    const signer = new ethers.Wallet(walletPrivateKey)
+
+    const l1Signer = signer.connect(l1Provider);
+    const l2Signer = signer.connect(l2Provider);
+
+
+   
+
+    const l2CallMarket = await (await hre.ethers.getContractAt('CallMarket',CallMarketaddress )).connect(l2Signer)
+
+    //await l2CallMarket.openMarket();
+
+    var receipt = null;
+    var array = [];
+    
+    for(let j = 39; j <= 76  ; j++){
+        
+            receipt = await l2CallMarket.connect(l2Signer).submitBid(j, 1);
+            array.push(j);
+            //console.log('Ask',j,' volume is equal to:', 1);
+            console.log('Bid',j);
+            //console.log('the tx receipt is:', receipt);
+            console.log('******************************');
+        
+
+        }
+
+
+        
+        console.log(array.length,'bids have been succsessfully submitted');
+        console.log('********************************************');
+    
+   
+    
+
+
+}
+
+main()
+  .then(() => process.exit(0))
+  .catch(error => {
+    console.error(error);
+    process.exit(1);
+  });
+

### 2021-05-19 Code/L2-HardHat/scripts/closing/4_Match.js

@@ -1,0 +1,55 @@
+
+
+
+
+
+
+
+const hre = require("hardhat");
+const ethers = require("ethers");
+const addressDappToken ='0x9D83C3c3e39d12416c395Da096988511B57E712F'; //the address of the ERC20 token; it has the same address as Kovan
+const CallMarketaddress ='0xcE17BE19aa80396Ae1A1C9f8dd386C48c1533F52';
+
+
+require('dotenv').config();
+
+const main = async () => {
+   
+    const accounts = await hre.ethers.getSigners();
+
+    const infuraKey = process.env.INFURA_KEY
+    if(!infuraKey) throw new Error("No INFURA_KEY set.")
+
+    const walletPrivateKey = process.env.DEVNET_PRIVKEY
+    if(!walletPrivateKey) throw new Error("No DEVNET_PRIVKEY set.")
+
+
+    const l1Provider = new ethers.providers.JsonRpcProvider(process.env.L1RPC)
+    const l2Provider = new ethers.providers.JsonRpcProvider(process.env.L2RPC)
+    const signer = new ethers.Wallet(walletPrivateKey)
+
+    const l1Signer = signer.connect(l1Provider);
+    const l2Signer = signer.connect(l2Provider);
+
+
+   
+
+    const l2CallMarket = await (await hre.ethers.getContractAt('CallMarket',CallMarketaddress )).connect(l2Signer)
+
+    const receipt = await l2CallMarket.connect(l2Signer).closeMarket();
+    console.log('the tx receipt is:', receipt);
+    
+   
+   
+    
+
+
+}
+
+main()
+  .then(() => process.exit(0))
+  .catch(error => {
+    console.error(error);
+    process.exit(1);
+  });
+

### 2021-05-19 Code/L2-HardHat/scripts/exec.js

@@ -1,0 +1,46 @@
+const hre = require("hardhat");
+const ethers = require("ethers");
+
+require('dotenv').config();
+
+const main = async () => {
+   
+    const accounts = await hre.ethers.getSigners();
+
+    const infuraKey = process.env.INFURA_KEY
+    if(!infuraKey) throw new Error("No INFURA_KEY set.")
+
+    const walletPrivateKey = process.env.DEVNET_PRIVKEY
+    if(!walletPrivateKey) throw new Error("No DEVNET_PRIVKEY set.")
+
+
+    const l1Provider = new ethers.providers.JsonRpcProvider(process.env.L1RPC)
+    const l2Provider = new ethers.providers.JsonRpcProvider(process.env.L2RPC)
+    const signer = new ethers.Wallet(walletPrivateKey)
+
+    const l1Signer = signer.connect(l1Provider);
+
+
+    const L1Payment = await (await hre.ethers.getContractFactory('Payment')).connect(l1Signer)
+    
+    console.log("Deploying L1")
+    
+    const l1Payment = await L1Payment.deploy(process.env.INBOX_ADDR)
+    await l1Payment.deployed()
+    console.log(`deployed to ${l1Payment.address}`)
+
+    
+
+
+    await l1Payment.depositEther(signer.address, {value: 10000000});
+    console.log("ETH has been assigned to", signer.address)
+
+
+}
+
+main()
+  .then(() => process.exit(0))
+  .catch(error => {
+    console.error(error);
+    process.exit(1);
+  });

### 2021-05-20 LaTeX-ACM/sections/paper.tex
adding evaluations + small edits here and there

@@
 \section{Introductory Remarks}
-
+\textblue{add sth about the " traversing data structures with e.g., 100 elements on-chain is not possible." contribution somewhere in the intro or contribution section}
 For better or worse, blockchain technologies like Ethereum have dramatically lowered the barrier to entry for developing and deploying financial technology.
@@
 While roll-ups use centralized servers and are not fully on-chain, an architecture where these servers only interface with Ethereum and never interface directly with users is still concerning, as it side-steps the regulatory hook that is present in many other server-augmented trading platforms.
+\textblue{say sth about implementing and testing the full call market on Arbitrum}
 
@@
 
-\paragraph{On-chain Order Books.} For trades between two blockchain-based assets (\eg a digital asset priced with a cryptocurrency, stablecoin, or second digital asset), order matching can be performed `on-chain' by deploying the order-matching system either on a dedicated blockchain or inside a decentralized application (DApp; \textit{a.k.a.} smart contract).
+\paragraph{On-chain Order Books.} For trades between two blockchain-based assets (\eg a digital asset priced with a cryptocurrency, stablecoin, or second digital asset), order matching can be performed `on-chain' by deploying the order-matching system either on a dedicated blockchain or inside a decentralized application (DApp).
 In this model, traders entrust their assets to an autonomously operating DApp with known source code instead of a third party custodian that can abscond with or lose the funds.
@@
 A call market will open for a specified period of time during which it will accept a capped number of orders (\eg 100 orders---parameterized so that all orders can be processed), and these orders are added to a PQ.
-Our vision (discussed below) is the market would be open for a very short period of time, close, and then reopen immediately (\eg every other block).
+Our vision (discussed below) is the market would be open for a very short period of time, close, and then reopen immediately (\eg every other block)\textblue{should we add a reference to the section \textbf{who opens/closes the market?}}.
 We keep the design simple by not allowing cancellations which require a second transaction and front-running attacks apply to cancellation orders~\cite{eskandari2019sok}.
@@
 
-%\textblue{ We need to find a home for this: another solution to reopen the market immediately after the closing call is to have many similar DApps for the market and  a factory DApp to guide users to the correct address (from the reviewer's comment)}
-
-\cm is designed as a base class that can be extended and customized. We discuss potential modifications here.
+\cm is designed as a base class that can be extended and customized. Here, we discuss potential modifications \textblue{and provide evaluation}.  
+% = = = = = = = = = = = = = = = = = = = = = = = = =  %
 
@@
 We simplify the market rules around ties on price: we execute them in a FIFO manner (breaking front-running resistance for ties on prices).
-A common trading rule (that does resist front-running) is to fill ties in proportion to their volume (\ie \textit{pro rata} allocation)\footnote{If Alice and Bob bid the same price for 100 tokens and 20 tokens respectively, and there are only 60 tokens left in marketable asks, Alice receives 50 and Bob 10.} however this approach does not always work.
+
+\paragraph{Evaluation.} A common trading rule (that does resist front-running) is to fill ties in proportion to their volume (\ie \textit{pro rata} allocation)\footnote{If Alice and Bob bid the same price for 100 tokens and 20 tokens respectively, and there are only 60 tokens left in marketable asks, Alice receives 50 and Bob 10.} however this approach does not always work.
 Consider the following corner case: 3 equally priced bids of 1 non-divisible token and 1 ask at the same price.
@@
 
+% = = = = = = = = = = = = = = = = = = = = = = = = =  %
+
 \subsection{Order Cancellations}
 
-\cm does not support order cancellations.
-We intend to open and close markets quickly (on the order of blocks), so orders are relatively short-lived.
-Support for cancellation also opens the market to new front-running issues where other traders (or miners) can displace cancellations until after the market closes (however one benefit of a call market is that beating a cancellation with a new order has no effect, assuming the cancellation is run any time before the market closes).
-Finally, cancellations have a performance impact.
+\cm does not support order cancellations. We intend to open and close markets quickly (on the order of blocks), so orders are relatively short-lived.
+
+\paragraph{Evaluation.} Support for cancellation opens the market to new front-running issues where other traders (or miners) can displace cancellations until after the market closes (however one benefit of a call market is that beating a cancellation with a new order has no effect, assuming the cancellation is run any time before the market closes \textblue{Should we refer to the new front-running section here???} ).
+Also, cancellations have a performance impact.
 Canceled orders can be removed from the underlying data structure or accumulated in a list that is cross-checked when closing the market.
@@
 A linked list with mapping that returns the key for each submitted order seems to be the most tenable data structure.
+
+% = = = = = = = = = = = = = = = = = = = = = = = = =  %
 
@@
 
+\paragraph{Evaluation.} \textblue{???}
+% = = = = = = = = = = = = = = = = = = = = = = = = =  %
+
 \subsection{Scheduling Events}
+
+\textblue{JC: Add option for burning the price improvement, keeping it in Lissy, give it to charity, \etc.}
 
@@
 
-% JC: Add option for burning the price improvement, keeping it in Lissy, give it to charity, \etc.
-
 A close alternative is to allow markets to open and close on different blocks.
@@
 There are actually two issues here: the issue of scheduling the function call and the issue of paying for it.
-For scheduling the function call, we can do one of the following: rely on market participants, who are eager to trade, to reopen the market, offer a bounty to reopen the market, or use an external service like Ethereum Alarm Clock (which creates a regulatory hook).\footnote{\url{https://ethereum-alarm-clock-service.readthedocs.io/}} Next we consider the second issue of who pays to close the market.
+For scheduling the function call, we can do one of the following: rely on market participants, who are eager to trade, to reopen the market, offer a bounty to reopen the market, or use an external service like Ethereum Alarm Clock (which creates a regulatory hook).\footnote{\url{https://ethereum-alarm-clock-service.readthedocs.io/}} Next, we consider the second issue of who pays to close the market.
 
-% = = = = = = = = = = = =Who Pays the Cost for Closing and Reopening the Market?= = = = = = = = = = = = =  %
+\paragraph{Evaluation.} \textblue{???}
+
+% = = = = = = = = = = = = = = = = = = = = = = = = =  %
 
@@
 As miners are paid all price improvements in the market, it is possible that a miner might run \texttt{closeMarket()} and it would pay for itself.
-However we consider two other scenarios that do not assume miners can automatically find MEV opportunities.
+However, we consider two other scenarios that do not assume miners can automatically find MEV opportunities.
 One solution requires a modified closing function, \texttt{closeMarket(n)}, that only processes $n$ orders at a time until the order book is empty (this is sensible design in any case to safeguard against the order book from locking up because the number of orders exceeds the gas limit to process them).
@@
 Every order submission on the new market also requires to run, say, \texttt{closeMarket(10)} on the older market, thus progressively closing the previous market while accepting orders to the new market.
-This solution pattern has two issues: first, amortizing the cost of closing the market amongst the early traders of the new market is an added incentive to not submit orders early to the market; the second issue is if not enough traders submit orders in the new market, the old market never closes (resulting in a backlog of old markets waiting to close).
 
@@
 When the time window for the open market elapses, the user who calls \texttt{closeMarket()} receives the bounty.
-This is a better solution, although not perfect: \texttt{closeMarket()} cost does not follow a tight linear increase with the number of orders, and gas prices vary over time which could render the bounty insufficient for offsetting the \texttt{closeMarket()} cost.
-However an interested third party (such as the token issuer for a given market) might occasionally bailout the market when it halts on \texttt{closeMarket()} to facilitate further trading.
+
+\paragraph{Evaluation.} The first solution pattern has two issues: first, amortizing the cost of closing the market amongst the early traders of the new market is an added incentive to not submit orders early to the market; the second issue is if not enough traders submit orders in the new market, the old market never closes (resulting in a backlog of old markets waiting to close).
+The second solution is better, although not perfect: \texttt{closeMarket()} cost does not follow a tight linear increase with the number of orders, and gas prices vary over time which could render the bounty insufficient for offsetting the \texttt{closeMarket()} cost.
+However, an interested third party (such as the token issuer for a given market) might occasionally bailout the market when it halts on \texttt{closeMarket()} to facilitate further trading.
 If the DApp can pay for its own functions, an interested party can also arrange for a commercial service (\eg any.sender\footnote{\url{https://github.com/PISAresearch/docs.any.sender}}) to relay the \texttt{closeMarket()} function call on Ethereum (an approach called \textit{meta-transactions}) which introduces another regulatory hook.
+
+% = = = = = = = = = = = = = = = = = = = = = = = = =  %
 
@@
 \end{enumerate}
+
+\paragraph{Evaluation.} \textblue{??}
 

### 2021-05-20 Code/L2-HardHat/scripts/Submission/1_Deposits.js
finalizing arb data

@@ -3,7 +3,7 @@
 
 const hre = require("hardhat");
 const ethers = require("ethers");
-const addressDappToken ='0x9D83C3c3e39d12416c395Da096988511B57E712F'; //the address of the ERC20 token; it has the same address as Kovan
+const addressDappToken ='0x40bed42b1162EDb35A0dA7A48C32bDE014Ee0E3A'; //the address of the ERC20 token; it has the same address as Kovan
 var CallMarketaddress;
 
 
@@ -40,7 +40,7 @@ const main = async () => {
 
     CallMarketaddress = l2CallMarket.address;
 
-    const l2DappToken = await (await hre.ethers.getContractAt('DappToken',addressDappToken )).connect(l2Signer)
+    const l2DappToken = await (await hre.ethers.getContractAt('DappToken',addressDappToken)).connect(l2Signer)
     
     
     await l2DappToken.connect(l2Signer).approve(CallMarketaddress, 1000000000);

### 2021-05-20 Code/L2-HardHat/scripts/Submission/2_Submit_Asks.js

@@ -3,8 +3,8 @@
 
 const hre = require("hardhat");
 const ethers = require("ethers");
-const addressDappToken ='0x9D83C3c3e39d12416c395Da096988511B57E712F'; //the address of the ERC20 token; it has the same address as Kovan
-const CallMarketaddress ='0x244B16EB248cD6e8e72220BA17588A04fA418695';
+const addressDappToken ='0x40bed42b1162EDb35A0dA7A48C32bDE014Ee0E3A'; //the address of the ERC20 token; it has the same address as Kovan
+const CallMarketaddress ='0x36e71cB7a6B598e3C04322c222Ae632B3F42c8Cf';
 
 
 require('dotenv').config();
@@ -38,7 +38,7 @@ const main = async () => {
     var receipt = null;
     var array = [];
     
-    for(let j = 1; j <= 200  ; j++){
+    for(let j = 1; j <= 100  ; j++){
 
 
         var randomnumber = Math.floor(Math.random() * (maximum - minimum + 1)) + minimum;

### 2021-05-20 Code/L2-HardHat/scripts/Submission/3_Submit_Bids.js

@@ -1,0 +1,46 @@
+
+
+const CallMarket = artifacts.require('CallMarket.sol');
+const DappToken = artifacts.require('DappToken');
+
+const addressDappToken = '0x2dc4dea5281738a92e8de9137a1088403dd3c160'; //the address of the ERC20 token; it has the same address as Kovan
+const CallMarketaddress = '0xB3267469542f52D9F572649a734B01a7DAeE64E1';
+
+var accounts;
+var maximum = 100;
+var minimum = 1;
+
+
+
+
+//******************* Deploys the CallMaket and stores its address *************************
+contract('CallMarket', function(accounts) {
+    
+
+   
+    //*******************Test 6*************************
+    it('should submit Bids from accounst[1]', async() => {
+        
+        const CallMarketInstance = await CallMarket.at(CallMarketaddress);
+        var receipt = null;
+        var array = [];
+        
+        accounts = await web3.eth.getAccounts();
+        for(let j = 1; j <= 200  ; j++){
+           
+            
+            var randomnumber = Math.floor(Math.random() * (maximum - minimum + 1)) + minimum;
+            receipt = await CallMarketInstance.submitBid (randomnumber, 1, {from: accounts[0]});
+            array.push(j);
+            //console.log('Bid',j,' volume is equal to:', 1);
+            //console.log('Bid',j);
+            //console.log('the tx receipt is:', receipt);
+            //console.log('******************************');
+
+        } 
+        console.log(array.length,'bids have been succsessfully submitted');
+        console.log('********************************************');
+    });
+
+    
+});

### 2021-05-20 Code/L2-HardHat/scripts/Submission/4_Match.js

@@ -1,0 +1,31 @@
+
+
+const CallMarket = artifacts.require('CallMarket.sol');
+const DappToken = artifacts.require('DappToken');
+
+const addressDappToken = '0x2dc4dea5281738a92e8de9137a1088403dd3c160'; //the address of the ERC20 token; it has the same address as Kovan
+const CallMarketaddress = '0xB3267469542f52D9F572649a734B01a7DAeE64E1';
+
+var accounts;
+
+
+
+
+//******************* Deploys the CallMaket and stores its address *************************
+contract('CallMarket', function(accounts) {
+
+  
+    //*******************Test 1*************************
+    it('should close the market and match the orders', async() => {
+        
+        const CallMarketInstance = await CallMarket.at(CallMarketaddress);
+
+        const receipt = await  CallMarketInstance.closeMarket();
+        console.log('the tx receipt is:', receipt);
+    });  
+    
+ 
+
+
+
+});

### 2021-05-20 Code/L2-HardHat/scripts/closing/1_Deposits.js

@@ -3,7 +3,7 @@
 
 const hre = require("hardhat");
 const ethers = require("ethers");
-const addressDappToken ='0x9D83C3c3e39d12416c395Da096988511B57E712F'; //the address of the ERC20 token; it has the same address as Kovan
+const addressDappToken ='0x40bed42b1162EDb35A0dA7A48C32bDE014Ee0E3A'; //the address of the ERC20 token; it has the same address as Kovan
 var CallMarketaddress;
 
 

### 2021-05-20 Code/L2-HardHat/scripts/closing/3_Submit_Bids.js

@@ -3,8 +3,8 @@
 
 const hre = require("hardhat");
 const ethers = require("ethers");
-const addressDappToken ='0x9D83C3c3e39d12416c395Da096988511B57E712F'; //the address of the ERC20 token; it has the same address as Kovan
-const CallMarketaddress ='0xcE17BE19aa80396Ae1A1C9f8dd386C48c1533F52';
+const addressDappToken ='0x40bed42b1162EDb35A0dA7A48C32bDE014Ee0E3A'; //the address of the ERC20 token; it has the same address as Kovan
+const CallMarketaddress ='0x18BF65069Fdaed79f8BDB0B6EDa87d5cc46F6E28';
 
 
 require('dotenv').config();

### 2021-05-20 Code/L2-HardHat/scripts/closing/4_Match.js

@@ -7,8 +7,8 @@
 
 const hre = require("hardhat");
 const ethers = require("ethers");
-const addressDappToken ='0x9D83C3c3e39d12416c395Da096988511B57E712F'; //the address of the ERC20 token; it has the same address as Kovan
-const CallMarketaddress ='0xcE17BE19aa80396Ae1A1C9f8dd386C48c1533F52';
+//const addressDappToken ='0x9D83C3c3e39d12416c395Da096988511B57E712F'; //the address of the ERC20 token; it has the same address as Kovan
+const CallMarketaddress ='0x18BF65069Fdaed79f8BDB0B6EDa87d5cc46F6E28';
 
 
 require('dotenv').config();

### 2021-05-21 LaTeX-ACM/sections/paper.tex
finalizing arb data
adding arb %

@@
 Thus we switch the priority queue to use a heap with dynamic array, which balances the expense of both operations (instead of optimizing for dequeuing in \texttt{closeMarket()}).
-\textblue{On Arbitrum, heaps are XX\% more efficient than non-Heaps for submitting orders and YY\% less efficient for closing (find the \% from the data provided below )} Recall that without a roll-up, such a priority queue can only match 38 pairs at a cost of 5,372,679 gas.
+\textblue{On Arbitrum, heaps are 32\% more efficient than non-Heaps for submitting orders and 29\% less efficient for closing}.
+Recall that without a roll-up, such a priority queue can only match 38 pairs at a cost of 5,372,679 gas.
 With Arbitrum roll-ups, 38 pairs costs only 1,544 in L1 gas (a 99.9\% savings).
@@
 
- % Heap Dynamic Array: worst case matching, 48 pairs of orders: tx hash: 0x2c0f5b5ba3539eb72018c08856c156c8098edcfd35db80f929a13c0aa6f9cc01, L1 gas: 1632, L2 arbgas: 1,039,351
+ % Heap Dynamic Array: 100 order submissions averaged L2 arbgas: 1,659,416, L1 gas: fixed: 2656
+
+ % Linked List w/ Mapping: 100 order submissions averaged L2 arbgas: 2,452,376, L1 gas: fixed: 2656
+
+ % Heap Dynamic Array: worst case matching, 38 pairs of orders: tx hash: 0x2c0f5b5ba3539eb72018c08856c156c8098edcfd35db80f929a13c0aa6f9cc01, L1 gas: 1632, L2 arbgas: 1,039,351
  % (https://explorer5.arbitrum.io/#/tx/0x2c0f5b5ba3539eb72018c08856c156c8098edcfd35db80f929a13c0aa6f9cc01)
+
+ % Linked List w/ Mapping: worst case matching, 38 pairs of orders: tx hash: 0x96aa143aee7bfb529d35456bef86387ef2adac30f222ea6a3216ded313e00973, L1 gas: 1632, L2 arbgas: 800,529
+ % (https://explorer5.arbitrum.io/#/tx/0x96aa143aee7bfb529d35456bef86387ef2adac30f222ea6a3216ded313e00973)
 

### 2021-05-21 LaTeX-ACM/sections/paper.tex
changes from call

@@
 \section{Introductory Remarks}
-\textblue{add sth about the " traversing data structures with e.g., 100 elements on-chain is not possible." contribution somewhere in the intro or contribution section}
+
 For better or worse, blockchain technologies like Ethereum have dramatically lowered the barrier to entry for developing and deploying financial technology.
@@
 This positions \cm as a feasible design for only a narrow set of markets today (low liquidity, small number of traders) which is good news for regulators.
-However we caution that the technology is likely to improve vastly in the coming years and we demonstrate one avenue for improvement through `roll-ups'~\cite{kalodner2018arbitrum}.
-While roll-ups use centralized servers and are not fully on-chain, an architecture where these servers only interface with Ethereum and never interface directly with users is still concerning, as it side-steps the regulatory hook that is present in many other server-augmented trading platforms.
-\textblue{say sth about implementing and testing the full call market on Arbitrum}
+A broader consequence of our research is that any on-chain application that requires the traversal of hundreds of elements in a data structure in a single transaction is not feasible on Ethereum today.
+
+We also speculate that Ethereum is likely to improve vastly in the coming years and we demonstrate one avenue for improvement through `roll-ups'~\cite{kalodner2018arbitrum} which reduce gas costs by more than 99.9\% savings.
+While roll-ups are not fully on-chain and introduce new network participants, the roll-up architecture is still concerning to regulators because the participants (called validators) are not directly reachable by users; they only watch the Ethereum state and interact directly with Ethereum.
 
@@
 
-\subsection{Front-running} \label{sec:front}
+\subsection{Front-running Evaluation} \label{sec:front}
 
@@
 
-\cm is designed as a base class that can be extended and customized. Here, we discuss potential modifications \textblue{and provide evaluation}.  
+\cm is designed as a base class that can be extended and customized. Here, we evaluate potential modifications.
 % = = = = = = = = = = = = = = = = = = = = = = = = =  %
@@
 
-\textit{Testing Platforms.} Arbitrum currently operates a test network with a bridge contract on the Ethereum Kovan testnet.
+\textit{Testing Platforms.} Arbitrum currently operates a test network with a inbox contract on the Ethereum Kovan testnet.
 To experiment with Arbitrum, we implemented a variant of \cm and run the same experiments that we previously performed on Layer 1 (Ethereum).
-To call functions on \cm, traders can (i) send transactions directly to the inbox contract \href{https://kovan.etherscan.io/address/0x76bF1345224fE606E2aB38B8E52B83512328A9DF}, or (ii) use a relay server (called an \textit{Aggregator}) provided by the Arbitrum.
-These aggregators will group and send all pending transactions together as a single Kovan transaction to the EthBridge contract (and pay the gas).
+To call functions on \cm, traders can (i) send transactions directly to the inbox contract \href{https://kovan.etherscan.io/address/0x76bF1345224fE606E2aB38B8E52B83512328A9DF}, or (ii) use a relay server (called an \textit{Sequencer}) provided by the Arbitrum.
+The sequencer will group, order,  and send all pending transactions together as a single Kovan transaction to the inbox (and pay the gas).
+
+\cm implements an exchange between ETH and tokens.
+To use Layer 1 assets on Layer 2, Arbitrum provides two bridge contracts: one for ETH, and one for tokens compliant with ERC-20 or other standard interfaces.
+Prior to trading, a trader uses the bridge to move their ETH to the same address on Layer 2 and then move the ETH to \cm with a Layer 2 transaction.
+From the user's perspective, tokens work similarly although the backend details are more complex.
+Finally, withdrawals work essentially same way in reverse, but are only final on Layer 1 after a dispute challenge period (currently 1 hour).\footnote{Layer 1 users might accept assets before they are finalized if they determine their eventual emergence on Layer 1 is indisputable (\textit{eventual finality}).}
 
@@
 Thus we switch the priority queue to use a heap with dynamic array, which balances the expense of both operations (instead of optimizing for dequeuing in \texttt{closeMarket()}).
-\textblue{On Arbitrum, heaps are 32\% more efficient than non-Heaps for submitting orders and 29\% less efficient for closing}.
+On Arbitrum, heaps are 32\% more efficient than non-Heaps for submitting orders and 29\% less efficient for closing.
 Recall that without a roll-up, such a priority queue can only match 38 pairs at a cost of 5,372,679 gas.
-With Arbitrum roll-ups, 38 pairs costs only 1,544 in L1 gas (a 99.9\% savings).
+With Arbitrum roll-ups, 38 pairs costs only 1,632 in L1 gas (a 99.9\% savings).
 This is effectively the cost of recording the \texttt{closeMarket()} function call in the inbox, which is 103 bytes of calldata.

### 2021-05-21 LaTeX-ACM/sections/paper.tex
new update
added hisham's paper + fixed the extra dot(practice makes perfect lol)

@@
 
-\paragraph{Central Exchanges (CEX).} Traditional financial markets (\eg NYSE and NASDAQ) use order-matching systems to arrange trades.
+\paragraph[Centralized Exchanges (CEX)]{Centralized Exchanges (CEX)\eatpunct} Traditional financial markets (\eg NYSE and NASDAQ) use order-matching systems to arrange trades.
 An exchange will list one or more assets (stocks, bonds, derivatives, or more exotic securities) to be traded with each other, given its own order book priced in a currency (\eg USD).
@@
 
+\textblue{Jeremy to do: merge in Hisham~\cite{galalpublicly} paper here.}
 The most similar academic work to this paper is the TEX exchange~\cite{khalil2019tex}.

### 2021-05-21 LaTeX-ACM/sections/paper.tex
more edits

@@
 
-\textit{Testing Platforms.} Arbitrum currently operates a test network with a inbox contract on the Ethereum Kovan testnet.
+\textit{Testing Platforms.} Arbitrum currently operates a test network with an inbox contract on the Ethereum Kovan testnet.
 To experiment with Arbitrum, we implemented a variant of \cm and run the same experiments that we previously performed on Layer 1 (Ethereum).
-To call functions on \cm, traders can (i) send transactions directly to the inbox contract \href{https://kovan.etherscan.io/address/0x76bF1345224fE606E2aB38B8E52B83512328A9DF}, or (ii) use a relay server (called an \textit{Sequencer}) provided by the Arbitrum.
+To call functions on \cm, traders can (i) send transactions directly to the inbox contract \href{https://kovan.etherscan.io/address/0x76bF1345224fE606E2aB38B8E52B83512328A9DF}, or (ii) use a relay server (called a \textit{Sequencer}) provided by the Arbitrum.
 The sequencer will group, order,  and send all pending transactions together as a single Kovan transaction to the inbox (and pay the gas).
@@
 As the number of pairs increases, L1 gas cost is constant.
-For traders submitting an order, the cost is reduced from  207,932 to 2,005.
+For traders submitting an order, the cost is reduced from  207,932 to 2,656.
 
@@
 We have also deployed \cm on Ethereum's testnet Rinkeby with flattened (single file) source code of just the \cm base class and priority queue implementations.
-It is visible and can be interacted with here: \href{https://rinkeby.etherscan.io/address/0x0d91de29c531d074853a5cef7cf9dfeb9c6ec4e0}{[etherscan.io]}; while the Arbitrum variant is here: \href{https://explorer5.arbitrum.io/#/address/0xce17be19aa80396ae1a1c9f8dd386c48c1533f52}{[explorer5.offchainlabs.com]}.
+It is visible and can be interacted with here: \href{https://rinkeby.etherscan.io/address/0x0d91de29c531d074853a5cef7cf9dfeb9c6ec4e0}{[etherscan.io]}; while the Arbitrum variant is here: \href{https://explorer5.arbitrum.io/#/address/0x18BF65069Fdaed79f8BDB0B6EDa87d5cc46F6E28}{[explorer5.offchainlabs.com]}.
 

### 2021-05-21 LaTeX-ACM/sections/paper.tex
more edits

@@
 A call market will open for a specified period of time during which it will accept a capped number of orders (\eg 100 orders---parameterized so that all orders can be processed), and these orders are added to a PQ.
-Our vision (discussed below) is the market would be open for a very short period of time, close, and then reopen immediately (\eg every other block)\textblue{should we add a reference to the section \textbf{who opens/closes the market?}}.
+Our vision (discussed below) is the market would be open for a very short period of time, close, and then reopen immediately (\eg every other block).
+Later in Section~\ref{sec:close}, we discuss the options for who closes/reopens the market.
 We keep the design simple by not allowing cancellations which require a second transaction and front-running attacks apply to cancellation orders~\cite{eskandari2019sok}.

### 2021-05-21 Code/L2-Truffle/migrations/2_deploy_CallMarket.js

@@ -1,39 +1,0 @@
-var CallMarket = artifacts.require("./CallMarket.sol"); 
-//var PQ1 = artifacts.require("./HeapDynamicArray.sol"); 
-//var PQ2 = artifacts.require("./HeapStaticArray.sol"); 
-//var PQ3 = artifacts.require("./HeapMapping.sol");
-//var PQ4 = artifacts.require("./LinkedList.sol");
-var PQ5 = artifacts.require("./LinkedListMapping.sol");
-
-
-
-module.exports =  function (deployer) {
-    
-
-    //For PQ1:
-    //deployer.deploy(PQ1).then (function(){
-        //return deployer.deploy(CallMarket, PQ1.address)
-        //});
-    //***********************************************************/
-    //For PQ2:
-    //deployer.deploy(PQ2,84).then (function(){
-        //return deployer.deploy(CallMarket, PQ2.address)
-        //});
-    //***********************************************************/
-    //For PQ3:
-    //deployer.deploy(PQ3).then (function(){
-        //return deployer.deploy(CallMarket, PQ3.address)
-        //});
-    //***********************************************************/
-    //For PQ4:
-    //deployer.deploy(PQ4).then (function(){
-        //return deployer.deploy(CallMarket, PQ4.address)
-        //});
-    //deployer.deploy(CallMarket);
-    //***********************************************************/
-    //For PQ5:
-    deployer.deploy(PQ5).then (function(){
-        return deployer.deploy(CallMarket, PQ5.address)
-        });
-};
-

### 2021-05-21 Code/L2-Truffle/test/AverageCaseSubmission/1_Deposits.js

@@ -1,49 +1,0 @@
-
-
-const CallMarket = artifacts.require('CallMarket.sol');
-const DappToken = artifacts.require('DappToken');
-
-const addressDappToken ='0x3e9c93df1cadc164d2b2751f6874a8d3eaf68a2e'; //the address of the ERC20 token; it has the same address as Kovan
-var CallMarketaddress;
-
-var accounts;
-
-
-
-
-//******************* Deploys the CallMaket and stores its address *************************
-contract('CallMarket', function(accounts) {
-    //*******************Test 1*************************
-    it('should store the address of the CallMarket into the var CallMarketaddress', async() => {
-        const CallMarketInstance = await CallMarket.deployed(); 
-        CallMarketaddress = CallMarketInstance.address;
-        console.log('The address of the CallMarket contract is:', CallMarketInstance.address);
-        console.log('********************************************');
-        
-    });
-
-    //*******************Test 2*************************
-    it('should deposit tokens from accounst[0] to the CallMarket contract', async() => {
-
-        const CallMarketInstance = await CallMarket.deployed(); 
-       
-
-        //const CallMarketInstance = await CallMarket.at(CallMarketaddress);
-        accounts = await web3.eth.getAccounts();
-
-        const DappTokenInstance = await DappToken.at(addressDappToken); //loads the DappToken from its address
-        await DappTokenInstance.approve(CallMarketaddress, 500, {from: accounts[0]});
-       
-        const receipt = await CallMarketInstance.depositToken (addressDappToken, 500, {from: accounts[0]});
-
-        const totalTokenbalance = await CallMarketInstance.totalTokenBalance(accounts[0]);
-        const totalEtherbalance = await CallMarketInstance.totalEtherBalance(accounts[0]);
-
-        console.log('The token balance of account[0] (Bob) is:', totalTokenbalance.toNumber());
-        console.log('The Ether balance of account[0] (Bob) is:', totalEtherbalance.toNumber());
-        console.log('********************************************');
-    });
-    
-
-
-});

### 2021-05-21 Code/L2-Truffle/test/AverageCaseSubmission/2_Submit_Asks.js

@@ -1,57 +1,0 @@
-
-
-const CallMarket = artifacts.require('CallMarket.sol');
-const DappToken = artifacts.require('DappToken');
-
-const addressDappToken = '0x279dc89a3dcea80a2cdb20a87854f7820c0c2819'; //the address of the ERC20 token; it has the same address as Kovan
-const CallMarketaddress = '';
-
-var accounts;
-var maximum = 100;
-var minimum = 1;
-
-
-
-//******************* Deploys the CallMaket and stores its address *************************
-contract('CallMarket', function(accounts) {
-    
-
-    //*******************Test 4*************************
-
-    // it('should open the market on the Dapp Token', async() => {
-      
-    //     const CallMarketInstance = await CallMarket.at(CallMarketaddress);
-
-    //     const receipt = await CallMarketInstance.openMarket ();
-    //     //const gasUsed = receipt.receipt.gasUsed;
-    //     //console.log(`GasUsed for openning the market: ${receipt.receipt.gasUsed}`);
-    //     console.log('********************************************');
-    // });
-    //*******************Test 5*************************
-    
-    it('should submit asks from accounst[0]', async() => {
-        const CallMarketInstance = await CallMarket.at(CallMarketaddress);
-        var receipt = null;
-        var array = [];
-    
-        accounts = await web3.eth.getAccounts();
-        for(let j = 1; j <= 10  ; j++){
-
-
-            var randomnumber = Math.floor(Math.random() * (maximum - minimum + 1)) + minimum;
-            receipt = await CallMarketInstance.submitAsk (randomnumber, 1, {from: accounts[0]});
-            array.push(j);
-            //console.log('Ask',j,' volume is equal to:', 1);
-            console.log('Ask',j);
-            console.log('the tx receipt is:', receipt);
-            console.log('******************************');
-        } 
-        console.log(array.length,'asks have been succsessfully submitted');
-        console.log('********************************************');
-    });
-   
-    
-
-
-
-});

### 2021-05-21 Code/L2-Truffle/test/AverageCaseSubmission/5_Transfers.js

@@ -1,44 +1,0 @@
-
-
-const CallMarket = artifacts.require('CallMarket.sol');
-const DappToken = artifacts.require('DappToken');
-
-const addressDappToken = '0x2dc4dea5281738a92e8de9137a1088403dd3c160'; //the address of the ERC20 token; it has the same address as Kovan
-const CallMarketaddress = '0xAE0b960010ec76A0E9aA3F0Cea4E368c287a380d';
-
-var accounts;
-
-
-
-
-//******************* Deploys the CallMaket and stores its address *************************
-contract('CallMarket', function(accounts) {
-
-  
-//*******************Test 1*************************
-
-it('should send back the tokens and ether', async() => {
-        
-    const CallMarketInstance = await CallMarket.at(CallMarketaddress);
-
-    const totalEtherbalance = await CallMarketInstance.totalEtherBalance(accounts[0]);
-    await CallMarketInstance.claimEther(totalEtherbalance); 
-
-    const totalTokenbalance = await CallMarketInstance.totalTokenBalance(accounts[0]);
-    await CallMarketInstance.claimTokens(addressDappToken, totalTokenbalance); 
-   
-});
-
-
-        
-     
-  
-
-
-    
-
-
-
-
-
-});

### 2021-05-21 Code/L2-Truffle/test/WorstCaseMatching/1_Deploy_Market.js

@@ -1,27 +1,0 @@
-
-
-const CallMarket = artifacts.require('CallMarket.sol');
-const DappToken = artifacts.require('DappToken');
-
-const addressDappToken = '0x39228aeb624b1b2ee3703632d9bef87e100da5c6'; //the address of the ERC20 token; it has the same address as Kovan
-var CallMarketaddress;
-
-
-
-
-
-//******************* Deploys the CallMaket and stores its address *************************
-
-contract('CallMarket', function(accounts) {
-
-    it('should store the address of the CallMarket into the var CallMarketaddress', async() => {
-        
-        const CallMarketInstance = await CallMarket.deployed(); 
-        CallMarketaddress = CallMarketInstance.address;
-        console.log('The address of the CallMarket contract is:', CallMarketInstance.address);
-        
-    });
-
-
-
-});

### 2021-05-21 Code/L2-Truffle/test/WorstCaseMatching/2_Deposit_Tokens.js

@@ -1,34 +1,0 @@
-
-
-const CallMarket = artifacts.require('CallMarket.sol');
-const DappToken = artifacts.require('DappToken');
-
-const addressDappToken = '0x39228aeb624b1b2ee3703632d9bef87e100da5c6'; //the address of the ERC20 token; it has the same address as Kovan
-const CallMarketaddress = '0xbfFD1b8b307244407B250892A1d667AD8ce7Ef68';
-var accounts;
-
-
-
-
-contract('CallMarket', function(accounts) {
-   
-
-    it('should deposit tokens from accounst[0] to the CallMarket contract', async() => {
-
-        const CallMarketInstance = await CallMarket.at(CallMarketaddress);
-        accounts = await web3.eth.getAccounts();
-
-
-        const DappTokenInstance = await DappToken.at(addressDappToken); //loads the DappToken from its address
-        await DappTokenInstance.approve(CallMarketaddress, 11700, {from: accounts[0]});
-       
-        const receipt = await CallMarketInstance.depositToken (addressDappToken, 11700, {from: accounts[0]});
-
-        const totalTokenbalance = await CallMarketInstance.totalTokenBalance(accounts[0]);
-
-        console.log('The token balance of account[0] is:', totalTokenbalance.toNumber());
-    });
-    
-
-
-});

### 2021-05-21 Code/L2-Truffle/test/WorstCaseMatching/3_Deposit_ETH.js

@@ -1,40 +1,0 @@
-
-
-const CallMarket = artifacts.require('CallMarket.sol');
-const DappToken = artifacts.require('DappToken');
-
-const addressDappToken = '0x39228aeb624b1b2ee3703632d9bef87e100da5c6'; //the address of the ERC20 token; it has the same address as Kovan
-const CallMarketaddress = '0xbfFD1b8b307244407B250892A1d667AD8ce7Ef68';
-var accounts;
-
-
-
-
-contract('CallMarket', function(accounts) {
-    
-
-    it('should deposit Ethers from accounts[0] to the CallMarket contract', async() => {
-   
-        const CallMarketInstance = await CallMarket.at(CallMarketaddress);
-        accounts = await web3.eth.getAccounts();
-
-        //Following "value" is in wei.
-        //1 ether = 1,000,000,000,000,000,000 wei
-        //Note that the sender must have enough ether on Arbitrum to be able to do the transfer (This can be done using https://bridge.offchainlabs.com/)
-        await CallMarketInstance.depositEther({from: accounts[0], value: 37900}); //transferring 0.000000000000000001 eth
-        
-                
-        
-        const totalEtherbalance = await CallMarketInstance.totalEtherBalance(accounts[0]);
-
-
-        console.log('The Ether balance of accounts[0]  is:',totalEtherbalance.toNumber());
-        console.log('********************************************');
-        const num = await CallMarketInstance.getBalance();
-        console.log('The Ether balance of Lissy is:', num.toNumber()); 
-
-    });
-
-
-
-});

### 2021-05-21 Code/L2-Truffle/test/WorstCaseMatching/4_Open_Market.js

@@ -1,23 +1,0 @@
-
-
-const CallMarket = artifacts.require('CallMarket.sol');
-const DappToken = artifacts.require('DappToken');
-
-const addressDappToken = '0x39228aeb624b1b2ee3703632d9bef87e100da5c6'; //the address of the ERC20 token; it has the same address as Kovan
-const CallMarketaddress = '0xbfFD1b8b307244407B250892A1d667AD8ce7Ef68';
-
-
-
-
-
-contract('CallMarket', function(accounts) {
-
-    it('should open the market on the Dapp Token', async() => {
-      
-        const CallMarketInstance = await CallMarket.at(CallMarketaddress);
-        await CallMarketInstance.openMarket ();
-     
-    });
-
-
-});

### 2021-05-21 Code/L2-Truffle/test/WorstCaseMatching/5_Submit_Asks.js

@@ -1,39 +1,0 @@
-
-
-const CallMarket = artifacts.require('CallMarket.sol');
-const DappToken = artifacts.require('DappToken');
-
-const addressDappToken = '0x39228aeb624b1b2ee3703632d9bef87e100da5c6'; //the address of the ERC20 token; it has the same address as Kovan
-const CallMarketaddress = '0x3c9006F42e6b649ED8281b52B7Eed6D99e71a348';
-var accounts;
-
-
-
-contract('CallMarket', function(accounts) {
-    //this.timeout(0);
-
-
-    it('should submit asks from accounst[0]', async() => {
-        const CallMarketInstance = await CallMarket.at(CallMarketaddress);
-        //var receipt = null;
-        //var array = [];
-    
-        accounts = await web3.eth.getAccounts();
-        for(let j = 86; j >= 1  ; j--){
-            
-            await CallMarketInstance.submitAsk (j, 1 , {from: accounts[0]});
-            //array.push(j);
-            //console.log('Ask',j,' volume is equal to:', 1);
-            //console.log('Ask',j);
-            //console.log('the tx receipt is:', receipt);
-            //console.log('******************************');
-        } 
-        //console.log(array.length,'asks have been succsessfully submitted');
-        //console.log('********************************************');
-    });
-   
-    
-
-
-
-});

### 2021-05-21 Code/L2-Truffle/test/WorstCaseMatching/6_Submit_Bids.js

@@ -1,37 +1,0 @@
-
-
-const CallMarket = artifacts.require('CallMarket.sol');
-const DappToken = artifacts.require('DappToken');
-
-const addressDappToken = '0x39228aeb624b1b2ee3703632d9bef87e100da5c6'; //the address of the ERC20 token; it has the same address as Kovan
-const CallMarketaddress = '0xbfFD1b8b307244407B250892A1d667AD8ce7Ef68';
-var accounts;
-
-
-
-contract('CallMarket', function(accounts) {
-    //this.timeout(0);
-    
-    it('should submit Bids from accounst[1]', async() => {
-        
-        const CallMarketInstance = await CallMarket.at(CallMarketaddress);
-        //var receipt = null;
-        //var array = [];
-        
-        accounts = await web3.eth.getAccounts();
-        for(let j = 280; j <= 309  ; j++){
-           
-            await CallMarketInstance.submitBid (j, 1, {from: accounts[0]});
-            //array.push(j);
-            //console.log('Bid',j,' volume is equal to:', 1);
-            //console.log('Bid',j);
-            //console.log('the tx receipt is:', receipt);
-            //console.log('******************************');
-
-        } 
-        //console.log(array.length,'bids have been succsessfully submitted');
-        //console.log('********************************************');
-    });
-
-    
-});

### 2021-05-21 Code/L2-Truffle/test/WorstCaseMatching/7_Close_Market.js

@@ -1,28 +1,0 @@
-
-
-const CallMarket = artifacts.require('CallMarket.sol');
-const DappToken = artifacts.require('DappToken');
-
-const addressDappToken = '0x2dc4dea5281738a92e8de9137a1088403dd3c160'; //the address of the ERC20 token; it has the same address as Kovan
-const CallMarketaddress = '';
-var accounts;
-
-
-
-
-contract('CallMarket', function(accounts) {
-    this.timeout(0);
-  
-    it('should close the market and match the orders', async() => {
-        
-        const CallMarketInstance = await CallMarket.at(CallMarketaddress);
-
-        const receipt = await  CallMarketInstance.closeMarket();
-        console.log('the tx receipt is:', receipt);
-    });  
-    
- 
-
-
-
-});

### 2021-05-21 Code/L2-Truffle/test/WorstCaseMatching/8_Transfers.js

@@ -1,35 +1,0 @@
-
-
-const CallMarket = artifacts.require('CallMarket.sol');
-const DappToken = artifacts.require('DappToken');
-
-const addressDappToken = '0x2dc4dea5281738a92e8de9137a1088403dd3c160'; //the address of the ERC20 token; it has the same address as Kovan
-const CallMarketaddress = '';
-var accounts;
-
-
-
-contract('CallMarket', function(accounts) {
-
-    this.timeout(0);
-
-    it('should send back the tokens and ether', async() => {
-        
-        const CallMarketInstance = await CallMarket.at(CallMarketaddress);
-
-        const totalEtherbalance = await CallMarketInstance.totalEtherBalance(accounts[0]);
-        await CallMarketInstance.claimEther(totalEtherbalance); 
-
-        const totalTokenbalance = await CallMarketInstance.totalTokenBalance(accounts[0]);
-        await CallMarketInstance.claimTokens(addressDappToken, totalTokenbalance); 
-   
-    });
-
-
-        
-     
-
-
-
-
-});

### 2021-05-21 Code/L2-Truffle/truffle-config.js

@@ -1,46 +1,0 @@
-const wrapProvider = require('arb-ethers-web3-bridge').wrapProvider
-const HDWalletProvider = require('@truffle/hdwallet-provider')
-const mnemonic =
-  'surge ability together fruit retire harvest release turkey social coffee owner uphold panel group car'
-
-module.exports = {
-mocha: {
-    enableTimeouts: false,
-    //before_timeout: 120000 // Here is 2min but can be whatever timeout is suitable for you.
-    before_timeout: 3000000000 // Here is 5min but can be whatever timeout is suitable for you.
-    
-    },
-networks: {
-    development: {
-      host: '127.0.0.1',
-      port: 7545,
-      //port: 8545,
-      network_id: '*', // Match any network id
-    },
-    
-    remote_arbitrum: {
-      provider: function () {
-        return wrapProvider(
-          new HDWalletProvider(mnemonic, 'https://kovan3.arbitrum.io/rpc')
-        )
-      },
-      network_id: '*', // Match any network id
-      gasPrice: 0,
-      
-    },
-  },
-  compilers: {
-    solc: {
-      //version: "0.5.3", // Fetch exact version from solc-bin (default: truffle's version)
-      version: "0.6.11",
-      //docker: true, // Use "0.5.3" you've installed locally with docker (default: false)
-      settings: {
-        // See the solidity docs for advice about optimization and evmVersion
-        optimizer: {
-          enabled: true,
-          runs: 200,
-        },
-      },
-    },
-  },
-}

### 2021-05-25 Code/L2-HardHat/scripts/Submission/1_Deposits 2.js
adding cm citations

@@ -1,0 +1,67 @@
+
+
+
+const hre = require("hardhat");
+const ethers = require("ethers");
+const addressDappToken ='0x40bed42b1162EDb35A0dA7A48C32bDE014Ee0E3A'; //the address of the ERC20 token; it has the same address as Kovan
+var CallMarketaddress;
+
+
+require('dotenv').config();
+
+const main = async () => {
+   
+    const accounts = await hre.ethers.getSigners();
+
+    const infuraKey = process.env.INFURA_KEY
+    if(!infuraKey) throw new Error("No INFURA_KEY set.")
+
+    const walletPrivateKey = process.env.DEVNET_PRIVKEY
+    if(!walletPrivateKey) throw new Error("No DEVNET_PRIVKEY set.")
+
+
+    const l1Provider = new ethers.providers.JsonRpcProvider(process.env.L1RPC)
+    const l2Provider = new ethers.providers.JsonRpcProvider(process.env.L2RPC)
+    const signer = new ethers.Wallet(walletPrivateKey)
+
+    const l1Signer = signer.connect(l1Provider);
+    const l2Signer = signer.connect(l2Provider);
+
+
+
+
+    const L2CallMarket = await (await hre.ethers.getContractFactory('CallMarket')).connect(l2Signer)
+    
+    console.log("Deploying CallMarket to L2")
+    
+    const l2CallMarket = await L2CallMarket.deploy()
+    await l2CallMarket.deployed()
+    console.log(`deployed to ${l2CallMarket.address}`)
+
+    CallMarketaddress = l2CallMarket.address;
+
+    const l2DappToken = await (await hre.ethers.getContractAt('DappToken',addressDappToken)).connect(l2Signer)
+    
+    
+    await l2DappToken.connect(l2Signer).approve(CallMarketaddress, 1000000000);
+       
+    await l2CallMarket.connect(l2Signer).depositToken(addressDappToken, 1000000000);
+
+    const totalTokenbalance = await l2CallMarket.totalTokenBalance(l2Signer.address);
+    const totalEtherbalance = await l2CallMarket.totalEtherBalance(l2Signer.address);
+
+    console.log('The token balance of account[0] (Bob) is:', totalTokenbalance.toNumber());
+    console.log('The Ether balance of account[0] (Bob) is:', totalEtherbalance.toNumber());
+    console.log('********************************************');
+
+
+
+
+}
+
+main()
+  .then(() => process.exit(0))
+  .catch(error => {
+    console.error(error);
+    process.exit(1);
+  });

### 2021-05-25 Code/L2-HardHat/scripts/Submission/1_Deposits.js

@@ -1,11 +1,7 @@
-
-
-
 const hre = require("hardhat");
 const ethers = require("ethers");
-const addressDappToken ='0x40bed42b1162EDb35A0dA7A48C32bDE014Ee0E3A'; //the address of the ERC20 token; it has the same address as Kovan
-var CallMarketaddress;
-
+const utils = require ("ethers");
+const BigNumber = require ("ethers");
 
 require('dotenv').config();
 
@@ -25,35 +21,49 @@ const main = async () => {
     const signer = new ethers.Wallet(walletPrivateKey)
 
     const l1Signer = signer.connect(l1Provider);
-    const l2Signer = signer.connect(l2Provider);
 
-
-
-
-    const L2CallMarket = await (await hre.ethers.getContractFactory('CallMarket')).connect(l2Signer)
+    const ethercBridge = "0x2948ac43e4AfF448f6af0F7a11F18Bb6062dd271";
+    const addressDappToken ;
+    var CallMarketaddress;
     
-    console.log("Deploying CallMarket to L2")
-    
-    const l2CallMarket = await L2CallMarket.deploy()
-    await l2CallMarket.deployed()
-    console.log(`deployed to ${l2CallMarket.address}`)
+    const L1CallMarket = await (await hre.ethers.getContractFactory('CallMarket')).connect(l1Signer)
+    console.log("Deploying CallMarket to L1")
+    const l1CallMarket = await L1CallMarket.deploy()
+    await l1CallMarket.deployed()
+    CallMarketaddress = l1CallMarket.address;
+    console.log(`Call Market deployed to ${CallMarketaddress}`)
 
-    CallMarketaddress = l2CallMarket.address;
+   
+    //deposit tokens from signer to the CallMarket contract
 
-    const l2DappToken = await (await hre.ethers.getContractAt('DappToken',addressDappToken)).connect(l2Signer)
-    
-    
-    await l2DappToken.connect(l2Signer).approve(CallMarketaddress, 1000000000);
-       
-    await l2CallMarket.connect(l2Signer).depositToken(addressDappToken, 1000000000);
+    const L1DappToken = await (await hre.ethers.getContractFactory('DappToken')).connect(l1Signer)
+    console.log("Deploying DappToken to L1")
+    const l1DappToken = await L1DappToken.deploy(100000000000)
+    await l1DappToken.deployed()
+    addressDappToken = l1DappToken.address;
 
[…]

### 2021-05-25 Code/L2-HardHat/scripts/Submission/2_Submit_Asks 2.js

@@ -1,0 +1,67 @@
+
+
+
+const hre = require("hardhat");
+const ethers = require("ethers");
+const addressDappToken ='0x40bed42b1162EDb35A0dA7A48C32bDE014Ee0E3A'; //the address of the ERC20 token; it has the same address as Kovan
+const CallMarketaddress ='0x36e71cB7a6B598e3C04322c222Ae632B3F42c8Cf';
+
+
+require('dotenv').config();
+
+const main = async () => {
+   
+    const accounts = await hre.ethers.getSigners();
+
+    const infuraKey = process.env.INFURA_KEY
+    if(!infuraKey) throw new Error("No INFURA_KEY set.")
+
+    const walletPrivateKey = process.env.DEVNET_PRIVKEY
+    if(!walletPrivateKey) throw new Error("No DEVNET_PRIVKEY set.")
+
+
+    const l1Provider = new ethers.providers.JsonRpcProvider(process.env.L1RPC)
+    const l2Provider = new ethers.providers.JsonRpcProvider(process.env.L2RPC)
+    const signer = new ethers.Wallet(walletPrivateKey)
+
+    const l1Signer = signer.connect(l1Provider);
+    const l2Signer = signer.connect(l2Provider);
+
+
+    var maximum = 100;
+    var minimum = 1;
+
+    const l2CallMarket = await (await hre.ethers.getContractAt('CallMarket',CallMarketaddress )).connect(l2Signer)
+
+    await l2CallMarket.openMarket();
+
+    var receipt = null;
+    var array = [];
+    
+    for(let j = 1; j <= 100  ; j++){
+
+
+        var randomnumber = Math.floor(Math.random() * (maximum - minimum + 1)) + minimum;
+        receipt = await l2CallMarket.connect(l2Signer).submitAsk(randomnumber, 1);
+            array.push(j);
+            //console.log('Ask',j,' volume is equal to:', 1);
+            console.log('Ask',j);
+            console.log('the tx receipt is:', receipt);
+            console.log('******************************');
+        } 
+        console.log(array.length,'asks have been succsessfully submitted');
+        console.log('********************************************');
+    
+   
+    
+
+
+}
+
+main()
+  .then(() => process.exit(0))
+  .catch(error => {
+    console.error(error);
+    process.exit(1);
+  });
+

### 2021-05-25 Code/L2-HardHat/scripts/Submission/2_Submit_Asks.js

@@ -1,48 +1,45 @@
 
 
+const CallMarket = artifacts.require('CallMarket.sol');
+const DappToken = artifacts.require('DappToken');
 
-const hre = require("hardhat");
-const ethers = require("ethers");
-const addressDappToken ='0x40bed42b1162EDb35A0dA7A48C32bDE014Ee0E3A'; //the address of the ERC20 token; it has the same address as Kovan
-const CallMarketaddress ='0x36e71cB7a6B598e3C04322c222Ae632B3F42c8Cf';
+const addressDappToken = '0x279dc89a3dcea80a2cdb20a87854f7820c0c2819'; //the address of the ERC20 token; it has the same address as Kovan
+const CallMarketaddress = '';
 
-
-require('dotenv').config();
-
-const main = async () => {
-   
-    const accounts = await hre.ethers.getSigners();
-
-    const infuraKey = process.env.INFURA_KEY
-    if(!infuraKey) throw new Error("No INFURA_KEY set.")
-
-    const walletPrivateKey = process.env.DEVNET_PRIVKEY
-    if(!walletPrivateKey) throw new Error("No DEVNET_PRIVKEY set.")
+var accounts;
+var maximum = 100;
+var minimum = 1;
 
 
-    const l1Provider = new ethers.providers.JsonRpcProvider(process.env.L1RPC)
-    const l2Provider = new ethers.providers.JsonRpcProvider(process.env.L2RPC)
-    const signer = new ethers.Wallet(walletPrivateKey)
 
-    const l1Signer = signer.connect(l1Provider);
-    const l2Signer = signer.connect(l2Provider);
-
-
-    var maximum = 100;
-    var minimum = 1;
-
-    const l2CallMarket = await (await hre.ethers.getContractAt('CallMarket',CallMarketaddress )).connect(l2Signer)
-
-    await l2CallMarket.openMarket();
-
-    var receipt = null;
-    var array = [];
+//******************* Deploys the CallMaket and stores its address *************************
+contract('CallMarket', function(accounts) {
     
-    for(let j = 1; j <= 100  ; j++){
+
+    //*******************Test 4*************************
+
+    // it('should open the market on the Dapp Token', async() => {
+      
+    //     const CallMarketInstance = await CallMarket.at(CallMarketaddress);
+
+    //     const receipt = await CallMarketInstance.openMarket ();
+    //     //const gasUsed = receipt.receipt.gasUsed;
+    //     //console.log(`GasUsed for openning the market: ${receipt.receipt.gasUsed}`);
[…]

### 2021-05-26 LaTeX-ACM/sections/paper.tex
adding cm citations
randomz

@@
 
+% Final camera-ready
 % JC: Our research group is actively collaborating with our jurisdiction's (Quebec, Canada) financial regulator, the Autorité des Marchés Financiers (AMF), to help them forecast how trading can be impacted by blockchain technology.
@@
 
-We also speculate that Ethereum is likely to improve vastly in the coming years and we demonstrate one avenue for improvement through `roll-ups'~\cite{kalodner2018arbitrum} which reduce gas costs by more than 99.9\% savings.
+We also speculate that Ethereum is likely to improve vastly in the coming years and we demonstrate one avenue for improvement through `roll-ups'~\cite{kalodner2018arbitrum} which reduce the gas costs of \cm by more than 99.9\%.
 While roll-ups are not fully on-chain and introduce new network participants, the roll-up architecture is still concerning to regulators because the participants (called validators) are not directly reachable by users; they only watch the Ethereum state and interact directly with Ethereum.
@@
 \paragraph{On-chain Dealers.} An advantage of on-chain trading is that other smart contracts, not just human users, can initiate trades, enabling broader decentralized finance (DeFi) applications.
-This has fueled a resurgence in on-chain exchange but through a quote-driven design rather than an order-driven one.
-Automated market makers  (\eg Uniswap) have all the trust advantages of an on-chain order book, plus they are very efficient relative to an on-chain order book.
+This has fuelled a resurgence in on-chain exchange but through a quote-driven design rather than an order-driven one.
+Automated market makers  (\eg Uniswap v3) have all the trust advantages of an on-chain order book, plus they are very efficient relative to an on-chain order book.
 The trade-off is that they operate as a dealer---the DApp exchanges assets from its own inventory.
@@
 Finally, there is a complicated difference in their price dynamics (\eg market impact of a trade, slippage between the best bid/ask and actual average execution price, \etc)---deserving of an entire research paper to precisely define.
-We leave it as an assertion that with equal liquidity, order books have more favorable price dynamics for traders.
+We leave it as an assertion that with equal liquidity, order books have more favourable price dynamics for traders.
 
@@
 Other exchanges, called crossing networks, also operate as a call market at various times throughout the trading day.\footnote{A crossing network uses a secondary market for determining the closing price.
-Many prominent crossing networks are operated internally within a brokerage for its clients, and often as a `dark pool' with an unpublished order book.} Call markets are studied widely in finance~\cite{Har03}.
+Many prominent crossing networks are operated internally within a brokerage for its clients, and often as a `dark pool' with an unpublished order book.} Call markets are studied widely in finance~\cite{Har03}, with recent interest in using them to combat high frequency trading~\cite{budish2015high,aquilina2020quantifying}.
 Time-sensitive traders submit orders early, especially in crossing networks that close at a randomly determined time (traders risk missing the call if they wait too long).
@@
 
-\cm is proof of concept code.
-We try to simplify the design at every step to make it an extensible base class but still functional without any extensions.
+\cm is proof of concept code and an extensible base class that is still functional without any extensions.
 A call market will open for a specified period of time during which it will accept a capped number of orders (\eg 100 orders---parameterized so that all orders can be processed), and these orders are added to a PQ.
@@
 
+In an \emph{insertion attack}, Mallory learns of a transaction from Alice, arranges for her transaction to run first with the purpose of Alice's transaction being the next transaction to run.
+For example, if Alice was
+
  fronting attacks: 
@@
 
-(i) in an \emph{displacement attack}, Mallory knows of a transaction from Alice and inserts her transaction before Alice's and does not care what happens to Alice's transaction; (ii) in an \emph{insertion attack}, Mallory similarly inserts a transaction before Alice and ensures Alice's transaction is the next to run, and (iii) in a \emph{suppression attack}, Mallory displaces all future transactions for some period of time.
+(i) in an \emph{displacement attack}, Mallory knows of a transaction from Alice and inserts her transaction before Alice's and does not care what happens to Alice's transaction;
+
+(iii) in a \emph{suppression attack}, Mallory displaces all future transactions for some period of time.
 Mallory can be a miner which can freely order transactions within the blocks it creates, or Mallory can be a fast user (or bot) who can quickly react to Alice's broadcasted but unconfirmed transactions, likely offering higher gas fees to have her transactions prioritized over Alice's.
@@
 When executing trades, if the volume of the current best bid does not match the best ask, the larger order is partially filled and the remaining volume is considered against the next best order.
-In \cm, tokens are assumed to be divisible.
-We simplify the market rules around ties on price: we execute them in a FIFO manner (breaking front-running resistance for ties on prices).
+A common trading rule (that does resist front-running) is to fill ties in proportion to their volume (\ie \textit{pro rata} allocation)\footnote{If Alice and Bob bid the same price for 100 tokens and 20 tokens respectively, and there are only 60 tokens left in marketable asks, Alice receives 50 and Bob 10.} however this approach does not always work.
+Consider the following corner case: 3 equally priced bids of 1 non-divisible token and 1 ask at the same price.
+There is no good option: (1) the bids could all be dropped, (2) bids could be prioritized based on time, or (3) the bid could be randomly chosen (\cf Libra~\cite{mavroudis2019libra}).
 
-\paragraph{Evaluation.} A common trading rule (that does resist front-running) is to fill ties in proportion to their volume (\ie \textit{pro rata} allocation)\footnote{If Alice and Bob bid the same price for 100 tokens and 20 tokens respectively, and there are only 60 tokens left in marketable asks, Alice receives 50 and Bob 10.} however this approach does not always work.
-Consider the following corner case: 3 equally priced bids of 1 non-divisible token and 1 ask at the same price.
-There is no good option: (1) the bids could all be dropped (fair but not market efficient), (2) bids could be prioritized based on time as in \cm (front-running is viable, but in this corner case only), or (3) the bid could be randomly chosen (\cf Libra~\cite{mavroudis2019libra}); blockchain `randomness' is generally deterministic and manipulatable by miners~\cite{bonneau2015random,buenz2017proofs} and countermeasures could take a few blocks to select~\cite{boneh2018verifiable}).
+\paragraph{Evaluation.} We avoid (1) which is fair but not market efficient.
+We note the conditions under which pro rata allocation fails (\ie non-divisible assets, an exact tie on price, and part of the final allocation) are improbable.
+In \cm, tokens are assumed to be divisible but we otherwise default to (2).
+This means insertion front-running attacks are possible for this corner case.
+However if these attacks proved to be a problem in practice, (3) is a better solution with one main drawback: on-chain sources of `randomness' are generally deterministic and manipulatable by miners~\cite{bonneau2015random,buenz2017proofs}, countermeasures can take a few blocks to select~\cite{boneh2018verifiable}).
 
@@
 
-\paragraph{Evaluation.} Support for cancellation opens the market to new front-running issues where other traders (or miners) can displace cancellations until after the market closes (however one benefit of a call market is that beating a cancellation with a new order has no effect, assuming the cancellation is run any time before the market closes \textblue{Should we refer to the new front-running section here???} ).
+\paragraph{Evaluation.} Support for cancellation opens the market to new front-running issues where other traders (or miners) can displace cancellations until after the market closes (however one benefit of a call market is that beating a cancellation with a new order has no effect, assuming the cancellation is run any time before the market closes.
 Also, cancellations have a performance impact.
@@
 While client software could help point out where the order is in the data structure, the order book can change between submitting the cancellation request and running the method.
-A linked list with mapping that returns the key for each submitted order seems to be the most tenable data structure.
+%A linked list with mapping that returns the key for each submitted order seems to be the most tenable data structure.
 
@@
 
-\paragraph{Evaluation.} \textblue{???}
 % = = = = = = = = = = = = = = = = = = = = = = = = =  %
@@
 
-\textblue{JC: Add option for burning the price improvement, keeping it in Lissy, give it to charity, \etc.}
-
-As a simple base class, \cm is a one-shot market.
+\cm is a one-shot market.
 However it can be extended to reopen with a clean order book after \texttt{closeMarket()} is run.
@@
 For scheduling the function call, we can do one of the following: rely on market participants, who are eager to trade, to reopen the market, offer a bounty to reopen the market, or use an external service like Ethereum Alarm Clock (which creates a regulatory hook).\footnote{\url{https://ethereum-alarm-clock-service.readthedocs.io/}} Next, we consider the second issue of who pays to close the market.
-
-\paragraph{Evaluation.} \textblue{???}
 
@@
 
-\paragraph{Evaluation.} \textblue{??}
-
 % = = = = = = = = = = = = = = = = = = = = = = = = =  %
@@
 
-We have avoided augmenting \cm with centralized components and third party services as our research question concerns the feasibility of a system with a minimum of regulatory hooks.
-However from a regulatory stance, there is a big difference between an architecture where the centralized component is publicly visible and interacted with by users (\eg most DEXes, roll-up architectures like Loopring, and commit-chain solutions like TEX).
-We consider an alternative design that is almost as difficult to regulate as a fully on-chain solution.
+We consider an alternative design for \cm that is almost as difficult to regulate as a fully on-chain solution.
 In this design, an off-chain component is introduced to boost performance but it only interacts with the Ethereum network and never directly with traders.
 Traders still only interact with Ethereum.
+
+% For background information on different types of roll-ups, please see Appendix~\ref{app:rollup}
 
@@
 
- \subsubsection*{Availability} 
-The Solidity source code for \cm, Truffle test files, and Arbitrum dependencies are available in a GitHub repository (non-anonymous link omitted).
-We have also deployed \cm on Ethereum's testnet Rinkeby with flattened (single file) source code of just the \cm base class and priority queue implementations.
-It is visible and can be interacted with here: \href{https://rinkeby.etherscan.io/address/0x0d91de29c531d074853a5cef7cf9dfeb9c6ec4e0}{[etherscan.io]}; while the Arbitrum variant is here: \href{https://explorer5.arbitrum.io/#/address/0x18BF65069Fdaed79f8BDB0B6EDa87d5cc46F6E28}{[explorer5.offchainlabs.com]}.
-
 \begin{acks} 

### 2021-05-26 LaTeX-ACM/sections/abstract.tex
edits + resolving merge conflicts

@@
 Fortunately for regulators, most trading volume in blockchain-based assets is still on centralized service providers for performance reasons.
-However this leaves the following research questions we address in this paper: (i) is secure trading (\ie resistant to front-running and price manipulation) even feasible as a fully `on-chain' service on a public blockchain, (ii) what is its performance benchmark, and (iii) what is the performance impact of novel techniques (\eg `roll-ups') in closing the performance gap?
+However, this leaves the following research questions we address in this paper: (i) is secure trading (\ie resistant to front-running and price manipulation) even feasible as a fully `on-chain' service on a public blockchain, (ii) what is its performance benchmark, and (iii) what is the performance impact of novel techniques (\eg `roll-ups') in closing the performance gap?
 

### 2021-05-26 LaTeX-ACM/sections/appendix.tex
edits + resolving merge conflicts

--- 2021-01-15 LaTeX-USENIX/sections/paper.tex
@@
 
-\section{Introductory Remarks}
+\section{Availability} 
+The Solidity source code for \cm, Truffle test files, and Arbitrum dependencies are available in a GitHub repository (non-anonymous link omitted).
+We have also deployed \cm on Ethereum's testnet Rinkeby with flattened (single file) source code of just the \cm base class and priority queue implementations.
+It is visible and can be interacted with here: \href{https://rinkeby.etherscan.io/address/0x0d91de29c531d074853a5cef7cf9dfeb9c6ec4e0}{[etherscan.io]}; while the Arbitrum variant is here: \href{https://explorer5.arbitrum.io/#/address/0x18BF65069Fdaed79f8BDB0B6EDa87d5cc46F6E28}{[explorer5.offchainlabs.com]}.
 
-For better or worse, blockchain technologies like Ethereum have dramatically lowered the barrier to entry for developing and deploying financial technology.
-New tokens have been launched with a few clicks of a user interface, and large investment infrastructures have been developed and deployed with little regulatory oversight.
-Blockchain exchange services allow order-based trading of digital currencies, tokens, and other digital assets.
-Such exchanges are a key component to blockchain-based economic activity.
+\section{Roll-ups: Additional Background}
+\label{app:rollup}
 
-Financial regulators seek to provide consumer protection during the issuing and trading of financial products and assets.
-They are concerned by their limited ability to intervene when trading is conducted on decentralized networks that, like Ethereum, run on the open internet.
-Order-driven trading can happen fully `on-chain' and this was experimented within the early days of Ethereum, but it has been largely abandoned for performance reasons in favour of running on centralized servers.
-More specifically, the core functionality is performed off-chain (\eg matching orders) while other aspects (\eg loading accounts, order cancellation) might be performed on-chain.
-In this world, company names, employees, addresses, and publicly addressable servers all provide regulatory hooks.
+We have avoided augmenting \cm with centralized components and third party services as our research question concerns the feasibility of a system with a minimum of regulatory hooks.
+However from a regulatory stance, there is a big difference between an architecture where the centralized component is publicly visible and interacted with by users (\eg most DEXes, roll-up architectures like Loopring, and commit-chain solutions like TEX).
+We consider an alternative design that is almost as difficult to regulate as a fully on-chain solution.
+In this design, an off-chain component is introduced to boost performance but it only interacts with the Ethereum network and never directly with traders.
+Traders still only interact with Ethereum.
 
-Our research group is actively collaborating with our jurisdiction's (Quebec, Canada) financial regulator, the Autorité des Marchés Financiers (AMF), to help them forecast how trading can be impacted by blockchain technology.
-This paper addresses their concerns about the feasibility of a `worst-case scenario' where a trading platform is anonymously deployed on a public blockchain, like Ethereum, and runs autonomously without any further intervention from an externally visible entity.
-Such a design appears feasible but is considered too slow.
-Together, we agreed it is a very good time to do a deep dive into understanding precisely \textit{how slow} for the following reasons: (1) public blockchains are becoming faster (both in theory and in practice) providing future efficiency gains for on-chain trading, (2) demand for on-chain trading is exemplified by the recent popularity of dealer quote-based trading like Uniswap and Curve Finance (reviewed below), and (3) stablecoins have become popular and allow on-chain trading with pricing in USD, alleviating another regulatory hook: the need for platforms to maintain traditional accounts for holding governmental currency and interfacing with the banking system.
+\textit{Layer 2} solutions are a group of technologies that are designed and proposed to address specific drawbacks of executing transactions on \textit{Layer 1} (\ie Ethereum and other blockchains)~\cite{gudgeon2020sok}.
+These technologies focus on fast transaction throughput, reducing gas costs, or educing transaction latency.
+When using \cm, we strive to reduce the gas cost as performance is the main bottleneck.
+Thus, we choose a Layer 2 technology called \textit{roll-up} which aims at reducing the gas cost for operating on Layer 1 by taking the transaction executions off-chain and only using the Ethereum blockchain for storing data.
+In a roll-up, every transaction is executed by a server or cluster of servers known as \textit{validators} that can be run by a collection of users or third party operators (here they can be run by the token issuer).
+These validators then push the result of the executions (\ie updates in the EVM state) back to the Ethereum and assure the Ethereum network that the transactions have been executed correctly.
 
-\paragraph{Contributions.} We study fully on-chain markets through design and implementation with Solidity---a high-level programming language for Ethereum that is syntactically similar to Java~\cite{Ethereum41:online}.
-We choose Ethereum as a hostile environment for an order book: Ethereum is fully decentralized (hardest to regulate), network participation is open to anyone on the internet (strongest adversarial model), and, as a result, it is slow (a lower-bound benchmark).
-Generally if an application is feasible on Ethereum, it will also be feasible and only run faster on a private (or permissioned) blockchain (\eg Hyperledger), which is a blockchain operated by authorized network nodes only, generally visible to regulators.
+A function can be computed off-chain and the new state of the DApp, called a \textit{rollup}, is written back to the blockchain, accompanied by either (1) a proof that the function was executed correctly, or (2) a dispute resolution process that can resolve, on-chain, functions that are not executed correctly (\eg Arbitrum~\cite{kalodner2018arbitrum}).
+In the case of (1), validating the proof must be cheaper than running the function itself.
+There are two main approaches: (1a) the first is to use cryptographic proof techniques (\eg SNARKS~\cite{BCGTV13,GGPR13} and variants~\cite{BBHR19}).
+This is called a \textit{zk-rollup}.
+Note that the proofs are heavy to compute (introducing a burden to the validators who generate them) but considered valid once posted to the Ethereum.
+The second approach (1b) is to execute the function in a trusted execution environment (TEE; \eg Intel SGX) and validate the TEE's quote on-chain (\eg Ekiden~\cite{cheng2019ekiden}).\footnote{The TEE-based approach is mired by recent attacks on SGX~\cite{SGX1,SGX2,SGX3,SGX4}, however these attacks do not necessarily apply to the specifics of how SGX is used here, and safer TEE technologies like Intel TXT (\cf~\cite{ZBC+19}) can be substituted.} Approach (2) is called an \textit{optimistic roll-up}.
+Although the dispute time delays result in a slower transaction finality, optimistic roll-ups substantially increase the performance by decreasing the gas cost.
 
-Our proof-of-concept, \cm, is an extensible base class suitable for experiments.
-\cm is designed from a security perspective: users only trust their assets to \cm's auditable code (non-custodial) and not to a third party; all operations are transparent; and we nearly eliminate the ability for adversarial network nodes to profit from front-running orders.
-In fact, we believe we are the first to design a decentralized application that actually leverages front-running (\ie miner extractable value~\cite{daian2019flash}) for the benefit of the system (see Section~\ref{sec:close}).
-
-While Solidity and its compiled bytecode is like many common programming languages, it also has quirks that require experimentation to best optimize performance (\eg factoring in the gas costs of operations, gas refunds, limits to Solidity's object oriented design, clearing mappings, \etc).
-We test five priority queues---the core data structure of the call market---and various options for cleaning up our data once finished with it.
-The bottom line is that the current benchmark for a \cm-esque design is in the low hundreds of trade executions per block on Ethereum today.
-This positions \cm as a feasible design for only a narrow set of markets today (low liquidity, small number of traders) which is good news for regulators.
-However we caution that the technology is likely to improve vastly in the coming years and we demonstrate one avenue for improvement through `rollups'~\cite{kalodner2018arbitrum}.
-While rollups use centralized servers and are not fully on-chain, an architecture where these servers only interface with Ethereum and never interface directly with users is still concerning, as it side-steps the regulatory hook that is present in many other server-augmented trading platforms.
-
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
-
-\section{Preliminaries}
-
-\subsection{Ethereum and Blockchain Technology}
-
-A public blockchain is an open peer-to-peer network that maintains a set of transactions without a single entity in charge.
-In Ethereum, \emph{transactions} encode the bytecode of user-written \emph{decentralized applications} (DApps) to be stored on the blockchain; and the function calls made to the DApp.
-Every execution of every function call is a validated by all honest, participating nodes to correct; a property that is robust against a fraction of faulty and malicious network nodes (or more precisely, their accumulated computational power).
-Once transactions are agreed upon, all honest participants will have identical sets of transactions in the same order.
-For Ethereum, this is conceptualized as the current state of a large \emph{virtual machine (EVM)} that is running many DApps.
-
-Transactions are broadcast by users to the blockchain network where they are propagated to all nodes.
-Nodes that choose to \emph{mine} will collect transactions (in the order of their choosing) into a block, and will attempt to have the network reach a consensus that their block should be added to the set (or chain) of previous blocks.
-A transaction is considered finalized once consensus on its inclusion has held for several additional blocks.
-
-\textbf{Ethereum's Gas Model.} Every transaction results in the participating nodes having to execute bytecode.
-This is not free.
-When a transaction is executed, each opcode in the execution path accrues a fixed, pre-specified amount of \emph{gas}.
-The function caller will pledge to pay a certain amount of Ethereum's internal currency \emph{ETH} (typically quoted in units of Gwei which is one billionth of an ETH) per unit of gas, and miners are free to choose to execute that transaction or ignore it.
-The function caller is charged for exactly what the transaction costs to execute, and they cap the maximum they are willing to be charged (\textit{gas limit}).
-If the cap is too low to complete the execution, the miner keeps the Gwei and \emph{reverts} the state of the EVM (as if the function never ran).
-
-A miner can include as many transactions (typically preferring transactions that bid the highest for gas) that can fit under a pre-specified \textit{block gas limit}, which is algorithmically adjusted for every block.
-As of the time of writing, the limit is approximately 11M gas.
-Essentially, our main research question is how many on-chain trades can be executed without exceeding that limit.
-Later we also discuss several bytecode operations (\emph{opcodes}) that refund gas (\ie cost negative gas), which we heavily utilize in our optimizations.
-
-\subsection{Trade Execution Systems}
-
- There are three main approaches to arranging a trade~\cite{Har03}.
-In a \emph{quote-driven} market, a dealer uses its own inventory to offer a price for buying or selling an asset.
-In a \emph{brokered exchange}, a broker finds a buyer and seller.
-In an \emph{order-driven} market, offers to buy (\emph{bids}) and sell (\emph{offers}/\emph{asks}) from many traders are placed as orders in an order book.
-Order-driven markets can be \emph{continuous}, with buyers/sellers at any time adding orders to the order book (\emph{makers}) or executing against an existing order (\emph{takers}); or they can be \emph{called}, where all traders submit orders within a window of time and orders are matched in a batch (like an auction).
-
-\subsection{Trading Blockchain-based Assets}
-
-%\input{tables/eval.tex}
-
-\paragraph{Central Exchanges (CEX).} Traditional financial markets (\eg NYSE and NASDAQ) use order-matching systems to arrange trades.
-An exchange will list one or more assets (stocks, bonds, derivatives, or more exotic securities) to be traded with each other, given its own order book priced in a currency (\eg USD).
-Exchanges for blockchain-based assets (also called crypto assets by enthusiasts) can operate the same way, using a centralized exchange (CEX) design where a firm (\eg Binance, Bitfinex, \etc) operates the platform as a trusted third party in every aspect: custodianship over assets/currency being traded, exchanging assets fairly, offering the best possible price execution.
-Security breaches and fraud in centralized exchanges  (\eg MtGox~\cite{TheHisto45:online}, QuadrigaCX~\cite{SEBIOrde83:online}, and many others) have become a common source of lost funds for users, while accusations of unfair trade execution have been levelled but are difficult to prove.
-Today, CEXes are often regulated as other money service businesses---this provides some ability for the government to conduct financial tracking but does little to provide consumer protection against fraud.
-
-\paragraph{On-chain Order Books.} For trades between two blockchain-based assets (\eg a digital asset priced with a cryptocurrency, stablecoin, or second digital asset), order matching can be performed `on-chain' by deploying the order-matching system either on a dedicated blockchain or inside a decentralized application (DApp; \textit{a.k.a.} smart contract).
-In this model, traders entrust their assets to an autonomously operating DApp with known source code instead of a third party custodian that can abscond with or lose the funds.
-The trading rules will operate as coded, clearing and settling can be guaranteed, and order submission is handled by the blockchain---a reasonably fair and transparent system (but see front-running below).
-Finally, anyone can create an on-chain order book for any asset (on the same chain) at any time.
-While they sound ideal, performance is a substantial issue and the main subject of this paper.
-Since it is an open system, there is no obvious regulatory hook (beyond the blockchain itself).
-
-In this paper, we focus on benchmarking an order book for the public blockchain Ethereum.
-Ethereum is widely-used and we stand to learn the most from working in a performance-hostile environment.
-Exchanges could be given their own dedicated blockchain, where trade execution logic can be coded into the network protocol.
-Trading systems on permissioned blockchains (\eg NASDAQ Linq, tZero) can also improve execution time and throughput, but they reduce user transparency and trust if unregulated.
-
-\paragraph{On-chain Dealers.} An advantage of on-chain trading is that other smart contracts, not just human users, can initiate trades, enabling broader decentralized finance (DeFi) applications.
-This has fuelled a resurgence in on-chain exchange but through a quote-driven design rather than an order-driven one.
-Automated market makers  (\eg Uniswap) have all the trust advantages of an on-chain order book, plus they are very efficient relative to an on-chain order book.
-The trade-off is that they operate as a dealer---the DApp exchanges assets from its own inventory.
-This inventory is loaded into the DApp by an investor who will not profit from the trades themselves but hopes their losses (termed `impermanent losses') are offset over the long-term by trading fees.
-By contrast, an order book requires no upfront inventory and trading fees are optional.
-Finally, there is a complicated difference in their price dynamics (\eg market impact of a trade, slippage between the best bid/ask and actual average execution price, \etc)---deserving of an entire research paper to precisely define.
-We leave it as an assertion that with equal liquidity, order books have more favourable price dynamics for traders.
-
-\paragraph{Hybrid Designs.} Before on-chain dealers became prominent in the late 2010s, the most popular design was hybrid order-driven exchanges with some trusted off-chain components and some on-chain functionality.
-Such decentralized exchanges (DEXes) were envisioned as operating fully on-chain, but performance limitations drove developers to move key components, such as the order matching system, off-chain to a centralized database.
-A landscape of DEX designs exist (\eg EtherDelta, 0x, IDEX, \etc): many avoid taking custodianship of assets off-chain, and virtually all (for order-driven markets) operate the order book itself off-chain (a regulatory hook).
-A non-custodial DEX solves the big issue of a CEX---the operator stealing the funds---however trade execution is still not provably fair, funds can still be indirectly stolen by a malicious exchange executing unauthorized trades, and server downtime is a common frustration for traders.
-An enhancement is to prove that trade execution is correct (\eg Loopring) but these proofs have blindspots (discussed in section~\ref{sec:rollups}).
-
-\subsection{Related Works}
-
-\paragraph{Blockchain Limitations and Solution.} While an order book is a ledger and blockchains provide a distributed ledger, it is not straightforward to drop a continuous-time order book onto a blockchain.
-An older 2014 paper~\cite{clark2014decentralizing} on the `Princeton prediction market'~\cite{Bra13} motivates our work.
-The authors observe the following limitations of on-chain continuous order books: block intervals are slow and not continuous, there is no support for accurate time-stamping, transactions can be dropped or reordered by miners, and fast traders can react to submitted orders/cancellations when broadcast to network but not in a block and have their orders appear first (as examined in later work on front-running: \cite{eskandari2019sok,daian2019flash}).
-
-\paragraph{Call Markets.} The researchers propose using a call market instead of a continuous-time market~\cite{clark2014decentralizing}.
-Orders are collected and placed into the order book over a window of time (\eg 1 or more blocks), then the market is closed and the orders are processed in batch: the best bids are matched to the best asks in order.
-If the prices overlap, the miner keeps the difference (which they could extract anyways through front-running).
-Call markets largely side-step front-running attacks from other traders because reordering trades has no impact (discussed more in section~\ref{sec:front}).
-The paper does not include an implementation and was envisioned as running on a custom blockchain (Ethereum was still in development in 2014).
-Market operations are part of the blockchain logic.
-
-Large exchanges, like the NYSE and NASDAQ, run two call markets every trading day in parallel with a continuous-time market.
-One call market closes at market open to produce the opening price for each stock, while the other closes at the end of the day to produce the closing price.
-Other exchanges, called crossing networks, also operate as a call market at various times throughout the trading day.\footnote{A crossing network uses a secondary market for determining the closing price.
-Many prominent crossing networks are operated internally within a brokerage for its clients, and often as a `dark pool' with an unpublished order book.} Call markets are studied widely in finance~\cite{Har03}.
-Time-sensitive traders submit orders early, especially in crossing networks that close at a randomly determined time (traders risk missing the call if they wait too long).
-A blockchain happens to provide this function naturally, as blocks are published unpredictably.
-Price-sensitive traders wait to base their pricing off the already submitted orders and do not mind missing a call if it obtains them a better price.
-
-\paragraph{Other Academic Literature.} There are numerous industry projects on blockchain-based exchanges and order books but most of the academic literature is on topics that are related but tangential to the mechanics of trade execution.
-Early (and some recent) literature consider trade execution under encryption (\ie dark markets) for securities~\cite{TP07,YSLT10,TW12,cartlidge2019mpc} and futures~\cite{massacci2018futuresmex}.
-A number of projects consider structuring derivatives in smart contracts---Velocity ~\cite{eskandari2017feasibility}, Findel ~\cite{biryukov2017findel}---but once issued, the derivative can be traded using exchanges.
-Atomic swaps (\ie payment vs delivery) are necessary for settling trades and some general approaches include Arwen~\cite{heilman2020arwen} and Tesseract~\cite{bentov2017tesseract}.
-
-The most similar academic work to this paper is the TEX exchange~\cite{khalil2019tex}.
-TEX is also an implementation of an order book, however it uses on-chain and off-chain components, and does not answer our research question of how feasible an on-chain order book is.
-We later compare it to our variant with rollups in Section~\ref{sec:rollups}.
-The main overlap is our common focus on resisting front-running attacks.
-In a recent survey on front-running attacks in blockchain~\cite{eskandari2019sok}, three solutions are proposed.
-One solution is to provide confidentiality over the content of orders which is the approach taken by TEX.
-The main downside is that honest traders cannot submit their orders and leave, they must interact in a second round to reveal their orders.
-The second solution is to sequence transactions according to some rule, either at the protocol level~\cite{MZGA20} or as a third party service~\cite{Kla20} (a regulatory hook).
-These are very recent works and are not available for experimentation on Ethereum yet (although Chainlink has announced an intention\footnote{A.
-Juels.
-\href{https://blog.chain.link/chainlink-fair-sequencing-services-enabling-a-provably-fair-defi-ecosystem/}{blog.chain.link}, 11 Sep 2020.}).
-The third solution is to design the service in a way that front-running attacks are not profitable---this is the approach we take here.
-
-% https://eprint.iacr.org/2020/269.pdf
-% Wendy, the Good Little Fairness Widget – Achieving Order Fairness for Blockchains
-
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
-
-\section{Priority Queues}\label{sec:pq}
-
-\input{tables/pq.tex}
-
-In designing \cm within Ethereum's gas model, performance is the main bottleneck.
-For a call market, closing the market and processing all the orders is the most time consuming step.
-The most critical design decision is the data structure for holding orders.
-While data structures are well studied for many languages, Solidity/EVM has its own unique aspects (\eg gas refunds, a relatively cheap mapping data structure, only partial support for object oriented programming) that create difficulties in assessing which will perform best without actually deploying and evaluating each variant.
-
-When closing a call market, the orders are examined in order: highest to lowest price for bids, and lowest to highest price for asks.
-In most circumstances, the market closing algorithm does not have to consider any deeper bids/asks from the list when choosing whether the current best bid and ask can be fulfilled.
-The only exceptions are in the case of a tie on price or a cancelled order, both of which we return to later.
-For this reason, the ideal data structure for storing bids/asks is a \textit{priority queue} (see Table~\ref{tab:PQ_API}) where each order's priority is its price.
-Specifically, we use two PQs---one for bids where the highest price is the highest priority, and one for asks where the lowest price is the highest priority.
-
-There are numerous ways of implementing a PQ.
-A PQ has an underlying list---common options include a static array, dynamic array, and linked list.
-The most expensive operation is keeping the data sorted---common options include (i) sorting during each enqueue, (ii) sorting for each dequeue, or (iii) splitting the difference by using a heap as the underlying data structure.
-Respectively, the time complexities are (i) linear enqueue and constant dequeue, (ii) constant enqueue and linear dequeue, and (iii) logarithmic enqueue and logarithmic dequeue.
-As closing the market is very expensive with any PQ, we rule out using (ii) as fully sorting while dequeuing would be prohibitive.
-We experiment with the following 5 options for (i) and (iii):
-
-\begin{enumerate}
-
-\item \textbf{Heap with Dynamic Array.} A heap is a type of binary tree data structure that comes in two forms of a (i) Max-Heap and (ii) Min-Heap.
-All the nodes of the tree are in a specific order and the root always represents the highest priority item of the data structure (the largest and smallest values in the Max-Heap and Min-Heap respectively).
-We implement a PQ with a heap that stores its data in a dynamically-sized array.
-
-\item \textbf{Heap with Static Array.} A heap can be also represented by a Solidity storage array in which the storage is statically allocated.
-To do this, we pass the required size of the array as a constructor parameter to the PQ smart contract.
-
-\item \textbf{Heap with Mapping.} In the above implementations, the entire order is stored (as a struct) in the heap.
-In this variant, we store the order struct in a Solidity mapping and store the mapping keys in the heap.
-
-\item \textbf{Linked List.} In this variant, we insert a new element into its correct position (based on its price) when running enqueue.
-The PQ itself stores elements in a linked list (enabling us to efficiently insert a new element between two existing elements).
-Solidity is described as object-oriented but the equivalent of an object is an entire smart contract.
-Therefore an object-oriented linked list must either (i) create each node in the list as a struct---but this is not possible as Solidity does not support recursive structs---or (ii) make every node in the list its own contract.
-The latter option seems wasteful and unusual, but we try it out anyways.
-Thus each node is its own contract and contains the order data and a pointer to the address of the next contract in the list.
-
-\item \textbf{Linked List with Mapping.} Finally, we try a variant of a linked list using a Solidity mapping.
-The value of the mapping is a struct with order data and the key of the next (and previous) node in the list.
-The contract stores the key of the first node (head) and last node (tail) in the list.
-
-\end{enumerate}
-
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
-
-\subsection{Priority Queue Evaluation}
-
-\paragraph{Enqueue Performance.} We implemented, deployed, and tested each PQ using Truffle and Ganache.
-We tried a variety of tests (including testing the full call market with each variant) with consistent results in performance.
-A simple test to showcase the performance profile is shown in Figure~\ref{fig:random_insertion}.
-We simply enqueue 50 integers chosen at random from a fixed interval in each PQ variant.
-The bigger the PQ gets, the longer enqueue takes---a linear increase for the linked list variants, and logarithmic for the heap variants.
-
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
-
-\begin{figure}[t]
-\centering
-\includegraphics[width=0.5\textwidth]{fig/random_insertion3.png}
-\caption{Gas costs for enqueuing 50 random integers into five priority queue variants.
-For the x-axis, a value of 9 indicates it is the 9th integer entered in the priority queue.
-The y-axis is the cost of enqueuing in gas.
-\label{fig:random_insertion}}
-\end{figure}
-
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
-
-\input{tables/dequeue.tex}
-
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
-
-\paragraph{Dequeue Performance.} For each PQ variant storing 50 random integers, the \texttt{Dequeue()} function is iterated until the data structure is empty.
-The total gas cost for fully dequeuing the PQ variants is outlined in Table~\ref{tab:PQUnitTests}.
-These tests are performed using the following Ethereum gas metrics: block gas limit $=$11,741,495 and 1 gas $=$ 56 Gwei.\footnote{EthStats (July 2020): \url{https://ethstats.net/}} Dequeuing removes data from the contract's storage.
-Recall this results in a gas refund.
-Based on our manual estimates (EVM does not expose the refund counter), every variant receives the maximum gas refund possible (\ie half the total cost of the transaction).
-In other words, each of them actually consumes twice the \texttt{gasUsed} amount in gas before the refund, however none of them are better or worse based on how much of a refund they generate.
-
-\paragraph{Discussion.} Based on enqueuing, the heap variants are the cheapest in terms of gas, while based on dequeuing, the link list variants are the cheapest.
-This is in accordance with the theoretical worst-case time complexity for each.
-However, (i) the linked list variants are materially cheaper than the heap variants at dequeuing, and (ii) dequeuing in a call market must be done as a batch, whereas enqueuing is paid for one at a time by the trader submitting the order, and (iii) Ethereum will not permit more than hundreds of orders so the asymptotic behaviour is not a significant factor.
-For these reasons, we suggest using a linked list variant for this specific application.
-As it can be seen in Figure~\ref{fig:random_insertion}, the associated cost for inserting elements into a linked list PQ is significantly greater than the linked list with mapping, as each insertion causes the creation of a new DApp.
-Accordingly, we choose to implement the call market with the linked list with mapping.
-Overall this PQ balances a moderate gas cost for insertion (\ie order submission) with one for removal (\ie matching the orders).
-
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
-
-\subsection{Cost/Benefit of Cleaning up After Yourself}
-\label{sec:gasrefund}
-
-\input{tables/cleaning.tex}
-
-\paragraph{Gas Refunds.} In order to reconstruct the current state of Ethereum's EVM, a node must obtain a copy of every variable change since the genesis block (or a more recent `checkpoint' that is universally agreed to).
-For this reason, stored variables persist for a long time and, at first glance, it seems pointless to free up variable storage (and unclear what `free up' even means).
-Once the current state of the EVM is established by a node, it can forget about every historical variable changes and only concern itself with the variables that have non-zero value (as a byte-string for non-integers) in the current state (uninitialized variables in Ethereum have the value zero by default).
-Therefore, freeing up variables will reduce the amount of state Ethereum nodes need to maintain going forward.
-
-For this reason, some EVM operations cost a negative amount of gas.
-That is, the gas is refunded to the sender at the end of the transaction, however (1) the refund is capped at 50\% of the total gas cost of the transaction, and (2) the block gas limit applies to the pre-refunded amount (\ie a transaction receiving a full refund can cost up to 5.5M gas with a 11M limit).
-Negative gas operations include:
-
-\begin{itemize}
-
-\item \texttt{SELFDESTRUCT}.
-This operation destroys the contract that calls it and refunds its balance (if any) to a designated receiver address.
-\texttt{SELFDESTRUCT} operation does not remove the initial byte code of the contract from the chain.
-It always refunds 24,000 gas.
-For example, if a contract A stores a single non-zero integer and contract B stores 100 non-zero integers, the \texttt{SELFDESTRUCT} refund for both is the same (24,000 gas).
-
-\item \texttt{SSTORE}.
-This operation loads a storage slot with a value.
-Using \texttt{SSTORE} to load a zero into a storage slot means the nodes can start ignoring it (recall that all variables, even if uninitialized, have zero by default).
-Doing this refunds 15,000 gas per slot.
-
-\end{itemize}
-
-At the time of this writing, Ethereum transaction receipts only account for the \texttt{gasUsed}, which is the total amount of gas units spent during a transaction, and users are not able to obtain the value of the EVM's refund counter from inside the EVM~\cite{signer2018gas}.
-So in order to account for refunds in Tables~\ref{tab:PQUnitTests}, we calculate them manually.
-First we need to figure out exactly how much storage is being cleared or how many smart contracts are being destroyed, then we multiply these numbers by 24,000 and 15,000 respectively.
-
-\paragraph{Refunds and PQs.}
-
-One consequence of a linked list is that a new DApp is created for every node in the list.
-Beyond being expensive for adding new nodes (a cost that will be bared by the trader in a call market), it also leaves a large footprint in the active Ethereum state, especially if we leave the nodes on the blockchain in perpetuity (\ie we just update the head node of the list and leave the previous head `dangling').
-However in a PQ, nodes are only removed from the head of the list; thus the node contracts could be `destroyed' one by one using an extra operation, \texttt{SELFDESTRUCT}, in the \texttt{Dequeue()} function.
-As shown in Table~\ref{tab:cleaning}, the refund from doing this outweighs to the cost of the extra computation: gas costs are reduced from 721K to 557K.
-This suggests a general principle: cleaning up after yourself will pay for itself in gas refunds.
-Unfortunately, this is not universally true as shown by applying the same principle to the linked list with mapping.
-
-Dequeuing in a linked list with mapping can be implemented in two ways.
-The simplest approach is to process a node, update the head pointer, and leave the `removed' node's data behind in the mapping untouched (where it will never be referenced again).
-Alternatively, we can call \texttt{DELETE} on each mapping entry once we are done processing a node in the PQ.
-As it can be seen in the last two rows of Table~\ref{tab:cleaning}, leaving the data on chain is cheaper than cleaning it up.
-
-The lesson here is that gas refunds incentivize developers to clean up storage variables they will not use again, but it is highly contextual as to whether it will pay for itself.
-Further the cap on the maximum refund means that refunds are not fully received for large cleanup operations (however removing the cap impacts the miners' incentives to include the transaction).
-This is a complicated and under-explored area of Ethereum in the research literature.
-For our own work, we strive to be good citizens of Ethereum and clean up to the extent that we can---thus all PQs in Table~\ref{tab:PQUnitTests} implement some cleanup.
-
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
-
-\section{Call Market Design}
-
-\input{tables/functions.tex}
-
-\cm is proof of concept code.
-We try to simplify the design at every step to make it an extensible base class but still functional without any extensions.
-A call market will open for a specified period of time during which it will accept a capped number of orders (\eg 100 orders---parameterized so that all orders can be processed), and these orders are added to a PQ.
-Our vision (discussed below) is the market would be open for a very short period of time, close, and then reopen immediately (\eg every other block).
-We keep the design simple by not allowing cancellations which require a second transaction and front-running attacks apply to cancellation orders~\cite{eskandari2019sok}.
-As markets are relatively short-lived, orders simply expire when the market call period ends.
-
-Another simplifying assumption is to implement a \textit{collateralized} call market.
-We assume all trades are between ETH and an ERC20 token, all orders are pre-funded in the DApp with ETH (for bids) and tokens (for asks), and once ETH or tokens are committed to an order, they cannot be withdrawn until the market closes.
-This ensures all executed orders clear and settle (\ie no defaults on payment or delivery).
-
-% Volume of 1
-% Ties?
-
-\cm is open source and written in 336 lines (SLOC) of Solidity plus the priority queue (\eg a heap with dynamic array is 282 SLOC).
-Refer to the availability section at the end of the paper.
-We tested it with the Mocha testing framework using Truffle on Ganache-CLI to obtain our performance metrics.
-Once deployed, the bytecode of \cm is 10812 bytes plus the constructor code (6400 bytes) which is not stored.
-We cross-checked for vulnerabilities with \textit{Slither}\footnote{https://github.com/crytic/slither} and \textit{SmartCheck}\footnote{https://tool.smartdec.net} (it only fails some `informational' warnings that are intentional design choices---\eg a costly loop).
-Table~\ref{tab:cm_functions} summarizes \cm's primary operations.
-
-%============= Performance =================== %
-
- \subsection{Measurements}
-
- \input{tables/performance.tex}
-
-The main research question is how many orders can be processed in a single Ethereum transaction when closing the call market, using Ethereum today.
-As our previous experiments indicated, the choice of PQ implementation is the main influence on performance (see Table~\ref{tab:worst_case_matching}).
-We implemented a generic call market that interfaces with a generic PQ (at its own contract address) and ran experiments for each PQ implementation.
-We looked at the \textit{worst-case} for performance which is when every submitted bid and ask is marketable (\ie will require fulfillment).
-In the first two columns, we determine the highest number of orders that can be processed in a single call to the \texttt{closeMarket()} and not exceed the the current Ethereum block gas limit of 11,741,495.
-Since Ethereum will become more efficient over time, we also were interested in how much gas it would cost to execute 1000 pairs of orders which is given in the third column.
-The fourth column indicates the cost of submitting a bid or ask --- since this costs will vary depending on how many orders are already submitted (recall Figure~\ref{fig:random_insertion}), we average the cost of 200 order submissions.
-
-As expected, the numbers closely track the performance of the PQ itself suggesting the PQ is indeed the main influence on performance.
-In Ethereum today, call markets appear to be limited to processing about a hundred orders per transaction.
-If markets open on every other block and the call market could monopolize an entire block to close, a few hundred orders per minute (worst-case) can be processed.
-The main takeaway is that the transparency, front-running resistance, and low barrier to entry of Ethereum come with an enormous cost (\ie an institutional exchange like NASDAQ can process 100K trades per second).
-That said, many exchanges trade the same assets under different trading rules (\ie market fragmentation) because traders have different preferences.
-\cm can work today in some circumstances like very low liquidity tokens, or markets with high volumes and a small number of traders (\eg liquidation auctions).
-
-\subsection{Front-running} \label{sec:front}
-
-The primary motivation for using a call market, as opposed to a continuous-time order book, is to mitigate front-running attacks~\cite{clark2014decentralizing,eskandari2019sok,daian2019flash}.
-Consider a sequence of 100 orders submitted within a window of time to market A, and the same sequence is randomly shuffled and submitted to market B.
-If A and B are continuous, the orders that are executed in A could be quite different from B.
-In a call market, the outcome of A and B will be exactly equivalent.
-There is no threat from miners reordering transactions or traders offering higher gas rates to have their orders executed before other orders already broadcasted.
-
-In a traditional call market, a market clearing price is chosen and all trades are executed at this price.
-All bids made at a higher price will receive the assets for the lower clearing price (and conversely for lower ask prices): this is called a \textit{price improvement}.
-A miner about to mine on a set of transactions, including its own orders, could drop other traders' orders to maximize its own price improvement.
-For this reason, in \cm, all price improvements are given to the miner (using \texttt{block.coinbase.transfer()}).
-This does not actively hurt traders---they always receive the same price that they quote in their orders---and it removes any incentive for miners to front-run these profits.
-
-Potential for front-running still exists around ties on price and order cancellations (both discussed in the next section).
-Finally, \textit{displacement attacks}~\cite{eskandari2019sok} are possible where competitive orders are delayed long enough for the market to close without them or the adversary fills up the current market (which caps the number of orders) to ensure other orders cannot be added.
-Both are expensive attacks.
-For all these reasons, we say \cm reduces front-running attacks but stop short of saying this issue is completely solved by \cm.
-
-\subsection{Cleaning Up Revisted}
+\subsection{Cleaning Up Revisited}
+\label{app:clean}
 
@@
 The Ethereum refund model should be considered further by Ethereum developers to better incentivize developers to be less wasteful in using storage.
-
-% = = = = = = = = = = = = = = = = = = = = = = = = =  %
-
-\section{Design Alternatives and Extensions}
-
-%\textblue{ We need to find a home for this: another solution to reopen the market immediately after the closing call is to have many similar DApps for the market and  a factory DApp to guide users to the correct address (from the reviewer's comment)}
-
-\cm is designed as base class that can be extended and customized. We discuss potential modifications here.
-
-\subsection{Token Divisibility and Ties}
-
-When executing trades, if the volume of the current best bid does not match the best ask, the larger order is partially filled and the remaining volume is considered against the next best order.
-In \cm, tokens are assumed to be divisible.
-We simplify the market rules around ties on price: we execute them in a FIFO manner (breaking front-running resistance for ties on prices).
-A common trading rule (that does resist front-running) is to fill ties in proportion to their volume (\ie \textit{pro rata} allocation)\footnote{If Alice and Bob bid the same price for 100 tokens and 20 tokens respectively, and there are only 60 tokens left in marketable asks, Alice receives 50 and Bob 10.} however this approach does not always work.
-Consider the following corner-case: 3 equally priced bids of 1 non-divisible token and 1 ask at the same price.
-There is no good option: (1) the bids could all be dropped (fair but not market efficient), (2) bids could be prioritized based on time as in \cm (front-running is viable, but in this corner case only), or (3) the bid could be randomly chosen (\cf Libra~\cite{mavroudis2019libra}); blockchain `randomness' is generally deterministic and manipulatable by miners~\cite{bonneau2015random,buenz2017proofs} and counter-measures could take a few blocks to select~\cite{boneh2018verifiable}).
-
-\subsection{Order Cancellations}
-
-\cm does not support order cancellations.
-We intend to open and close markets quickly (on the order of blocks), so orders are relatively short-lived.
-Support for cancellation also opens the market to new front-running issues where other traders (or miners) can displace cancellations until after the market closes (however one benefit of a call market is that beating a cancellation with a new order has no effect, assuming the cancellation is run any time before the market closes).
-Finally, cancellations have a performance impact.
-Cancelled orders can be removed from the underlying data structure   or accumulated in a list that is cross-checked when closing the market.
-Removing orders requires a more verbose structure than a priority queue (\eg a binary search tree instead of a heap; or methods to traverse a linked list rather than only pulling from the head).
-While client software could help point out where the order is in the data structure, the order book can change between submitting the cancellation request and running the method.
-A linked list with mapping that returns the key for each submitted order seems to be the most tenable data structure.
-
-\subsection{Market Clearing Price}
-
-Call markets are heralded for fair price discovery.
-This is why many exchanges use a call market at the end of the day to determine the closing price of an asset, which is an important price both optically (it is well-published) and operationally (many derivates settle based on the closing price).
-We purposely do not compute a `market clearing price' with \cm because miners can easily manipulate the price (\ie include a single wash trade at the price they want fixed), although they forgo profit for doing so.
-This is not merely hypothetical---Uniswap (the prominent quote-drive, on-chain exchange) prices have been manipulated to exploit other DeFi applications relying on them.
-Countermeasures to protect Uniswap price integrity could also apply to \cm: (1) taking a rolling mediant of prices over time, and (2) using it alongside other sources for the same price and forming a consensus.
-While \cm does not emit a market clearing price, it can be computed by a web application examining the order book at market close.
-
-\subsection{Scheduling Events}
-
-As a simple base class, \cm is a one-shot market.
-However it can be extended to re-open with a clean order book after \texttt{closeMarket()} is run.
-Modifiers can enforce when the market operates openly (collecting orders) and when close can be run.
-In the Princeton paper~\cite{clark2014decentralizing}, the call market is envisioned to run as an alt-coin, where orders accumulate within a block and a miner closes the market as part of the logic of producing a new block (\ie within the same portion of code as computing their coinbase transaction in Bitcoin or gasUsed in Ethereum).
-
-If the call market runs as a DApp on Ethereum, it seems difficult to open and close the market every block.
-Someone needs to call the \texttt{closeMarket()} for every block (we return to who this is next) but the market will only work as intended if miners execute this function after every \texttt{submitBid()} and \texttt{submitAsk()} invocation.
-Since price improvements are paid to the miners, the miner is actually incentivized to run \texttt{closeMarket()} last to make the most profit.
-This pattern is called miner extractable value (MEV)~\cite{daian2019flash} and is usually considered in the context of attacks.
-However in our case, MEV is a feature.
-Efficient algorithms for miners to automatically find MEV opportunities is an open research problem.
-
-A close alternative is to allow markets to open and close on different blocks.
-In this alternative, the \texttt{closeMarket()} function calls \texttt{openMarket()} as a subroutine and sets two modifiers: orders are only accepted in the block immediately after the current block (\ie the block that executes the \texttt{closeMarket()}) and \texttt{closeMarket()} cannot be run again until two blocks after the current block.
-
-The final issue is who invokes \texttt{closeMarket()} every other block?
-There are actually two issues here: the issue of scheduling the function call and the issue of paying for it.
-For scheduling the function call, we can do one of the following: rely on market participants, who are eager to trade, to reopen the market, offer a bounty to reopen the market, or use an external service like Ethereum Alarm Clock (which creates a regulatory hook).\footnote{\url{https://ethereum-alarm-clock-service.readthedocs.io/}} Next we consider the second issue of who pays to close the market.
-
-% = = = = = = = = = = = =Who Pays the Cost for Closing and Reopening the Market?= = = = = = = = = = = = =  %
-
-\subsection{Who Pays to Close/Reopen the Market?}
-\label{sec:close}
-
-As miners are paid all price improvements in the market, it is possible that a miner might run \texttt{closeMarket()} and it would pay for itself.
-However we consider two other scenarios that do not assume miners can automatically find MEV opportunities.
-One solution requires a modified closing function, \texttt{closeMarket(n)}, that only processes $n$ orders at a time until the order book is empty (this is sensible design in any case to safeguard against the order book from locking up because the number of orders exceeds the gas limit to process them).
-Once the time window for submitting orders is past, a new market is created (without settling the previous market).
-Every order submission on the new market also requires to run, say, \texttt{closeMarket(10)} on the older market, thus progressively closing the previous market while accepting orders to the new market.
-This solution pattern has two issues: first, amortizing the cost of closing the market amongst the early traders of the new market is an added incentive to not submit orders early to the market; the second related issue is if not enough traders submit orders in the new market, the old market never closes (resulting in a backlog of old markets waiting to close).
-
-The second solution is to levy a carefully computed fee against the traders for every new order they submit.
-These fees are accumulated by the DApp to use as a bounty.
-When the time window for the open market elapses, the user who calls \texttt{closeMarket()} receives the bounty.
-This is a better solution, although not perfect: \texttt{closeMarket()} cost does not follow a tight linear increase with the number of orders, and gas prices vary over time which could render the bounty insufficient for offsetting the \texttt{closeMarket()} cost.
-However an interested third party (such as the token issuer for a given market) might occasionally bailout the market when it halts on \texttt{closeMarket()} to facilitate further trading.
-If the DApp can pay for its own functions, an interested party can also arrange for a commercial service (\eg any.sender\footnote{\url{https://github.com/PISAresearch/docs.any.sender}}) to relay the \texttt{closeMarket()} function call on Ethereum (an approach called \textit{meta-transactions}) which introduces another regulatory hook.
-
-\subsection{Collateralization Options}
-
-In \cm, both the tokens and ETH that a trader want to potentially use in the order book are pre-loaded into the contract.
-Consider Alice who holds a token and decides she wants to trade it for ETH.
-In this model, she must first transfer the tokens to the contract and then submit an ask order.
-If she does this within the same block, there is a chance that a miner will execute the ask before the transfer and the ask will revert.
-If she waits for confirmation, this introduces a delay.
-This delay seems reasonable but we point out a few ways it could be addressed:
-
-\begin{enumerate}
-
-\item \textbf{Use \texttt{msg.value}.} For the ETH side of a trade (\ie for bids), ETH could be sent with the function call to \texttt{submitBid()} to remove the need for    \texttt{depositEther()}.
-This works for markets that trade ERC-20 tokens for ETH, but would not work for ERC-20 to ERC-20 exchanges.
-
-\item \textbf{Merge Deposits with Bids/Asks.} \cm could have an additional function that atomically runs the functionality of \texttt{depositToken()} followed by the functionality of \texttt{submitAsk()}.
-This removes the chance that the deposit and order submission are ordered incorrectly.
-
-\item \textbf{Use ERC-20 Approval.} Instead of \cm taking custody of the tokens, the token holder could simply approve \cm to transfer tokens on her behalf.
-If \cm is coded securely, it is unconcerning to allow the approval to stand long-term and the trader never has to lock up their tokens in the DApp.
-The issue is that there is no guarantee that the tokens are actually available when the market closes (\ie Alice can approve a DApp to spend 100 tokens even if she only has 5 tokens, or no tokens).
-In this case, \cm would optimistically try to transfer the tokens and if it fails, move onto the next order.
-This also gives Alice an indirect way to cancel an order, by removing the tokens backing the order---this could be a feature or it could be considered an abuse.
-
-\item \textbf{Use a Fidelity Bond.} Traders could post some amount of tokens as a fidelity bond, and be allowed to submit orders up to 100x this value using approve.
-If a trade fails because the pledged tokens are not available, the fidelity bond is slashed as punishment.
-This lets traders side-step time-consuming transfers to and from \cm while still incentivizing them to ensure that submitted orders can actually be executed.
-The trade-off  is that \cm needs to update balances with external calls to the ERC-20 contract instead of simply updating its internal ledger.
-
-\end{enumerate}
-
-%= = = = = =  = =  =  Rollups=  = = = = = = = = =%
-
-\section{\cm Variant with Off-chain Closing}
-\label{sec:rollups}
-
-We have avoided augmenting \cm with centralized components and third party services as our research question concerns the feasibility of a system with a minimum of regulatory hooks.
-However from a regulatory stance, there is a big difference between an architecture where the centralized component is publicly visible and interacted with by users (\eg most DEXes, rollup architectures like Loopring, and commit-chain solutions like TEX).
-We briefly consider an alternative design that is almost as difficult to regulate as a fully on-chain solution.
-In this design, an off-chain component is introduced to boost performance but it only interacts with the Ethereum network and never directly with traders.
-Traders still only interact with Ethereum.
-
-A function can be computed off-chain and the new state of the DApp, called a \textit{rollup}, is written back to the blockchain, accompanied by either (1) a proof that the function was executed correctly, or (2) a dispute resolution process that can resolve, on-chain, functions that are not executed correctly (\eg Arbitrum~\cite{kalodner2018arbitrum}).
-In the case of (1), validating the proof must be cheaper than running the function itself.
-There are two main approaches to (1): the first is to use cryptographic proof techniques (\eg SNARKS~\cite{BCGTV13,GGPR13} and variants~\cite{BBHR19}), and the second is to execute the function in a trusted execution environment (TEE; \eg Intel SGX) and validate the TEE's quote on-chain (\eg Ekiden~\cite{cheng2019ekiden}).\footnote{The TEE-based approach is mired by recent attacks on SGX~\cite{SGX1,SGX2,SGX3,SGX4}, however these attacks do not necessarily apply to the specifics of how SGX is used here, and safer TEE technologies like Intel TXT (\cf~\cite{ZBC+19}) can be substituted.}
-
-We implemented a variant of \cm using rollups on Arbitrum.\footnote{\url{https://offchainlabs.com} for more current details than the 2018 \textit{USENIX Security} paper~\cite{kalodner2018arbitrum}.} In this model, the token issuer (or other interested party) will run a dedicated server to watch Ethereum for function invocations submitted and sequenced on-chain, perform the function call off-chain, and write the resultant state on-chain.
-Anyone capable of running EVM code can verify the result.
-If it is incorrect, a dispute can be filed (with the correct state) and an on-chain correction will be made.
-With or without disputes, participants that validate the function calls for themselves can proceed knowing that the correct state will eventually be finalized.
-
-In our \cm variant with rollups, the token issuer does all the computation (both enqueuing and dequeuing).
-Thus we switch the priority queue to use a heap with dynamic array, which balances the expense of both operations (instead of optimizing for dequeuing in \texttt{closeMarket()}).
-Recall that on-chain, such a priority queue can only match 38 pairs at a cost of 5,372,679 gas.
-With rollups, 38 pairs cost 38,863 gas.
-As the pairs increase, the cost is essentially constant (\eg 1000 pairs cost 38,851 as opposed to 457,326,935 on-chain).
-Submitting an order costs 39,169 gas on average as opposed to 207,932 on-chain.
-
-Our \cm variant is not the first rollup-based order book.
-Loopring 3.0\footnote{\url{https://loopring.org}} offers a continuous-time order book.
-The primary difference is that orders in Loopring 3.0 are submitted off-chain to the operator directly, whereas our variant uses on-chain submission so that the rollup server does not need to be publicly reachable.
-Loopring 3.0 can operate near high frequency trading as order submission is unhampered by Ethereum, however its  rollup proof does not ensure that the exchange did not reorder transactions, which is particularly problematic in a continuous-time order book.
-Traders who prioritize trade fairness might opt for a solution like our variant, while traders who want speed would vastly prefer the Loopring architecture which offers near-CEX speed while being non-custodial.
-Loopring leaves a regulatory hook whereas our variant could be nearly as difficult to regulate as a fully on-chain solution if the rollup server was kept anonymous: Ethereum and Arbitrum themselves would be the only regulatory hooks.
-
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
-
-\section{Concluding Remarks}
-
-Imagine you have just launched a token on Ethereum.
-Now want to be able to trade it.
-While the barrier to entry for exchange services is low, it still exists.
-For a centralized or decentralized exchange, you have to convince the operators to list your token and you will be delayed while they process your request.
-For an automated market maker, you will have to lock up a large amount of ETH into the DApp, along with your tokens.
-For rollups, you will have to host your own servers.
-By contrast to all of these, with an on-chain order book, you just deploy the code alongside your token and trading is immediately supported.
-This should concern regulators.
-Even if it is too slow today, there is little reason for developers not to offer it as a fallback solution that accompanies every token.
-With future improvements to blockchain scalability, it could become the defacto trading method.
-
-It may seem paradoxical or unethical to build for regulators exactly what they worry about, however we agreed that it was too difficult to answer our research questions without actual implementation and experimentation.
-\cm is proof of concept code that implements only enough to understand the feasibility of on-chain trading and we release the code for reproducibility.
-However it is not production code, it is unpolished, it has no UI, and we have no intention of promoting it for adoption.
-Finally, by understanding the `pain points' in the design, we found we were constantly tugged toward centralized components (Ethereum alarm clock, meta-transactions, rollup servers, \etc) which could serve as regulatory hooks even if the service is mainly on-chain.
-
- \subsubsection*{Availability} 
-The Solidity source code for \cm, Truffle test files, and Arbitrum dependencies are available in a GitHub repository\footnote{\CallMarketRepo}.
-We have also deployed \cm on Ethereum's testnet Rinkeby with flattened (single file) source code of just the \cm base class and priority queue implementations.
-It is visible and can be interacted with here: \href{https://rinkeby.etherscan.io/address/0x0d91de29c531d074853a5cef7cf9dfeb9c6ec4e0}{[etherscan.io]}; while the Arbitrum variant is here: \href{https://explorer.arbitrum.io/#/tx/0x1828d7eb6a7a9b9ec479f07e8149c6172bb89a101571963b5cf690132bdf009b}{[explorer.offchainlabs.com]}.
-
-\subsubsection*{Acknowledgements.}  The authors thanks the AMF (Autorité des Marchés Financiers) for supporting this research project.
-J.
-Clark also acknowledges partial funding from the National Sciences and Engineering Research Council (NSERC)/Raymond Chabot Grant Thornton/Catallaxy Industrial Research Chair in Blockchain Technologies, as well as NSERC through a Discovery Grant.
-M.
-Moosavi acknowledges support from Fonds de Recherche du Québec - Nature et Technologies (FRQNT).
-
-%GitHub repo:  \footnote{\CallMarketRepo}

### 2021-05-26 LaTeX-ACM/sections/paper.tex
edits + resolving merge conflicts

@@
 The most critical design decision is the data structure for holding orders.
-While data structures are well studied for many languages, Solidity/EVM has its own unique aspects (\eg gas refunds, a relatively cheap mapping data structure, only partial support for object-oriented programming) that create difficulties in assessing which will perform best without actually deploying and evaluating each variant.
+While data structures are well-studied for many languages, Solidity/EVM has its own unique aspects (\eg gas refunds, a relatively cheap mapping data structure, only partial support for object-oriented programming) that create difficulties in assessing which will perform best without actually deploying and evaluating each variant.
 
@@
 For this reason, the ideal data structure for storing bids/asks is a \textit{priority queue} (see Table~\ref{tab:PQ_API}) where each order's priority is its price.
-Specifically, we use two PQs---one for bids where the highest price is the highest priority, and one for asks where the lowest price is the highest priority.
+Specifically, we use two PQs---one for bids, where the highest price is the highest priority, and one for asks, where the lowest price is the highest priority.
 
@@
 Solidity is described as object-oriented but the equivalent of an object is an entire smart contract.
-Therefore an object-oriented linked list must either (i) create each node in the list as a struct---but this is not possible as Solidity does not support recursive structs---or (ii) make every node in the list its own contract.
-The latter option seems wasteful and unusual, but we try it out anyways.
-Thus each node is its own contract and contains the order data and a pointer to the address of the next contract in the list.
+Therefore, an object-oriented linked list must either (i) create each node in the list as a struct---but this is not possible as Solidity does not support recursive structs---or (ii) make every node in the list its own contract.
+\textblue{The latter option seems wasteful and unusual, but we try it out anyways.} Thus, each node is its own contract and contains the incoming order's data and a pointer to the address of the next contract in the list.
 
 \item \textbf{Linked List with Mapping.} Finally, we try a variant of a linked list using a Solidity mapping.
-The value of the mapping is a struct with order data and the key of the next (and previous) node in the list.
+The value of the mapping is a struct with the incoming order's data and the key of the next (and previous) node in the list.
 The contract stores the key of the first node (head) and last node (tail) in the list.
@@
 
-\paragraph{Enqueue Performance.} We implemented, deployed, and tested each PQ using Truffle and Ganache.
-We tried a variety of tests (including testing the full-call market with each variant) with consistent results in performance.
+\paragraph{Enqueue Performance.} We implemented, deployed, and tested each PQ using the Truffle development framework~\cite{TruffleO71:online} and Ganache~\cite{GanacheT25:online}.
+We tried a variety of tests (including testing the full call market with each variant) with consistent results in performance.
 A simple test to showcase the performance profile is shown in Figure~\ref{fig:random_insertion}.
-We simply enqueue 50 integers chosen at random from a fixed interval in each PQ variant.
+We enqueue 50 integers chosen at random from a fixed interval in each PQ variant.
 The bigger the PQ gets, the longer enqueue takes---a linear increase for the linked list variants, and logarithmic for the heap variants.
@@
 Accordingly, we choose to implement the call market with the linked list with mapping.
-Overall this PQ balances a moderate gas cost for insertion (\ie order submission) with one for removal (\ie matching the orders).
+Overall this PQ balances a moderate gas cost for insertion (\ie order submission) with one for removal (\ie closing the market and matching the orders).
 
@@
 For this reason, stored variables persist for a long time and, at first glance, it seems pointless to free up variable storage (and unclear what `free up' even means).
-Once the current state of the EVM is established by a node, it can forget about every historical variable changes and only concern itself with the variables that have non-zero value (as a byte string for non-integers) in the current state (uninitialized variables in Ethereum have the value 0 by default).
-Therefore, freeing up variables will reduce the amount of state Ethereum nodes need to maintain going forward.
+Once the current state of the EVM is established by a node, it can forget about every historical variable changes and only concern itself with the variables that have non-zero value (as a byte string for non-integers) in the current state (uninitialized variables in Ethereum have the value 0 by default).\textblue{ Therefore, freeing up variables will reduce the amount of state Ethereum nodes need to maintain going forward.}
 
@@
 
-\item \texttt{SELF-DESTRUCT}.
+\item \texttt{SELFDESTRUCT}.
 This operation destroys the contract that calls it and refunds its balance (if any) to a designated receiver address.
@@
 The simplest approach is to process a node, update the head pointer, and leave the `removed' node's data behind in the mapping untouched (where it will never be referenced again).
-Alternatively, we can call \texttt{DELETE} on each mapping entry once we are done processing a node in the PQ.
+Alternatively, we can call \texttt{DELETE} on each mapping entry once we finish processing a node in the PQ.
 As it can be seen in the last two rows of Table~\ref{tab:cleaning}, leaving the data on chain is cheaper than cleaning it up.
@@
 
-As expected, the numbers closely track the performance of the PQ itself suggesting the PQ is indeed the main influence on performance.
+As expected, the numbers closely track the performance of the PQ itself, suggesting the PQ is indeed the main influence on performance.
 In Ethereum today, call markets appear to be limited to processing about a hundred orders per transaction.
@@
 
-Beyond the cleaning up issues with priority queues in Section~\ref{sec:gasrefund}, \cm also uses mappings with each market.
-Traders preload their account with tokens to be traded (which comply with a common token standard called ERC20) and/or ETH.
+\textblue{Beyond the cleaning up issues with priority queues in Section~\ref{sec:gasrefund}, \cm also uses mappings with each market.} Traders preload their account with tokens to be traded (which comply with a common token standard called ERC20) and/or ETH.
 \cm tracks what they are owed using a mapping called \texttt{totalBalance} and allows traders to withdraw their tokens at any time.
@@
 
-As the DApp runs \texttt{closeMarket()}, it starts matching the best bids to the best asks.
+\textblue{As the DApp runs \texttt{closeMarket()}}, it starts matching the best bids to the best asks.
 As orders execute, \texttt{totalBalance} and \texttt{unavailableBalance} are updated.
 At a certain point, the bids and asks will stop matching in price.
-At this point, every order left in the order book cannot execute (because the priority queue sorts orders by price, and so orders deeper in the queue have worst prices than the order at the head of the queue).
+At this point, every order left in the order book cannot execute (the priority queue sorts orders by price, so orders deeper in the queue have worst prices than the order at the head of the queue).
 Therefore all remaining entries in \texttt{unavailableBalance} can be cleared.
@@
 
-\item \textbf{Store the Mapping in a Separate DApp.} We could wrap the mapping inside its own DApp and when we are done with the mapping, we can run \texttt{SELFDESTRUCT} on the contract.
+\item \textbf{Store the Mapping in a Separate DApp.} We could wrap the mapping inside its own DApp and run \texttt{SELFDESTRUCT} on the contract once we finish processing the mapping.
 This refunds us 24,000 gas which is less than the cost of deploying the extra contract.
@@
 Call markets are heralded for fair price discovery.
-This is why many exchanges use a call market at the end of the day to determine the closing price of an asset, which is an important price both optically (it is well published) and operationally (many derivatives settle based on the closing price).
+This is why many exchanges use a call market at the end of the day to determine the closing price of an asset, which is an important price both optically (it is well-published) and operationally (many derivatives settle based on the closing price).
 We purposely do not compute a `market clearing price' with \cm because miners can easily manipulate the price (\ie include a single wash trade at the price they want fixed), although they forgo profit for doing so.
@@
 
-In \cm, both the tokens and ETH that a trader want to potentially use in the order book are pre-loaded into the contract.
+In \cm, both the tokens and ETH that a trader wants to potentially use in the order book are pre-loaded into the contract.
 Consider Alice, who holds a token and decides she wants to trade it for ETH.
@@
 Arbitrum is an Ethereum Layer 2 scaling solution that operates as an optimistic roll-up~\cite{kalodner2018arbitrum}.
-Arbitrum runs entire DApps inside its environment, which acts like a container and requires special bridge contacts to interact with `normal' (or L1) Ethereum DApps.
-To deploy a DApp on Arbitrum, or to execute a function on an existing Arbitrum DApp, the transaction is sent to an L1 Arbitrum contract called an inbox.
-The transaction is not executed, it is only recorded (as calldata) by the inbox contract.
-Like any other transactions on Ethereum, miners determine the order of the transactions sent to the inbox.
-A set of validators (open to anyone) are watching the inbox contract for new transactions.
+Arbitrum runs entire DApps inside its environment, which acts like a container and requires special bridge contacts to interact with `normal' (or Layer 1) Ethereum DApps.
+To deploy a DApp on Arbitrum, or to execute a function on an existing Arbitrum DApp, the transaction is sent to a Layer 1 Arbitrum contract called Inbox.
+The transaction is not executed, it is only recorded (as calldata) by the Inbox contract.
+Like any other transactions on Ethereum, miners determine the order of the transactions sent to this contract.
+A set of validators (open to anyone) are watching the Inbox contract for new transactions.
 Once an inbox transaction is finalized in an Ethereum block, validators will execute the transaction and asserts the result of the execution to other validators on a sidechain called ArbOS.
 Once the dispute challenge period is over, the new state of ArbOS will be inserted into Ethereum.
-As the inbox contract maintains all Arbitrum transactions, anyone can recompute the entire current state of the ArbOS and file a dispute if executions are not performed correctly.
+As the Inbox contract maintains all Arbitrum transactions, anyone can recompute the entire current state of the ArbOS and file a dispute if executions are not performed correctly.
 Disputes are adjudicated by Ethereum itself and require essentially constant gas costs, regardless of the size of the gas costs of the transaction being disputed.
@@
 
-\textit{Testing Platforms.} Arbitrum currently operates a test network with an inbox contract on the Ethereum Kovan testnet.
-To experiment with Arbitrum, we implemented a variant of \cm and run the same experiments that we previously performed on Layer 1 (Ethereum).
-To call functions on \cm, traders can (i) send transactions directly to the inbox contract \href{https://kovan.etherscan.io/address/0x76bF1345224fE606E2aB38B8E52B83512328A9DF}, or (ii) use a relay server (called a \textit{Sequencer}) provided by the Arbitrum.
-The sequencer will group, order,  and send all pending transactions together as a single Kovan transaction to the inbox (and pay the gas).
+\textit{Testing Platforms.} Arbitrum currently operates a test network with an Inbox contract on the Ethereum Kovan testnet.
+To experiment with Arbitrum, we implemented a variant of \cm and ran the same experiments that we previously performed on Layer 1 (Ethereum).
+To call functions on \cm, traders can (i) send transactions directly to the Inbox contract \href{https://kovan.etherscan.io/address/0x76bF1345224fE606E2aB38B8E52B83512328A9DF}, or (ii) use a relay server (called a \textit{Sequencer}) provided by the Arbitrum.
+The sequencer will group, order,  and send all pending transactions together as a single Kovan transaction to the Inbox (and pay the gas).
 
-\cm implements an exchange between ETH and tokens.
+Recall that \cm implements an exchange between ETH and tokens.
 To use Layer 1 assets on Layer 2, Arbitrum provides two bridge contracts: one for ETH, and one for tokens compliant with ERC-20 or other standard interfaces.
@@
 In our \cm variant on Arbitrum, the token issuer does all the computation (both enqueuing and dequeuing).
-Thus we switch the priority queue to use a heap with dynamic array, which balances the expense of both operations (instead of optimizing for dequeuing in \texttt{closeMarket()}).
-On Arbitrum, heaps are 32\% more efficient than non-Heaps for submitting orders and 29\% less efficient for closing.
+Thus, we switch the priority queue to use a heap with dynamic array, which balances the expense of both operations (instead of optimizing for dequeuing in \texttt{closeMarket()}).
+Our experiments show that on Arbitrum, heaps are 32\% more efficient than non-Heaps for submitting orders and 29\% less efficient for closing.
 Recall that without a roll-up, such a priority queue can only match 38 pairs at a cost of 5,372,679 gas.
-With Arbitrum roll-ups, 38 pairs costs only 1,632 in L1 gas (a 99.9\% savings).
-This is effectively the cost of recording the \texttt{closeMarket()} function call in the inbox, which is 103 bytes of calldata.
-As the number of pairs increases, L1 gas cost is constant.
+With Arbitrum roll-ups, 38 pairs cost only 1,632 in Layer 1 gas (a 99.9\% savings).
+This is effectively the cost of recording the \texttt{closeMarket()} function call in the Inbox, which is 103 bytes of calldata.
+As the number of pairs increases, Layer 1 gas cost is constant.
 For traders submitting an order, the cost is reduced from  207,932 to 2,656.
@@
 While the runtime of a transaction is no longer an issue for Ethereum, it is still an issue for the validators.
-Like Ethereum miners, validators do measure the amount of gas (called ArbGas in Arbitrum) a transaction takes although Arbitrum emulates EVM code with its own different OpCodes.
-Thus, ArbGas with a roll-up and L1 gas without a roll-up are not directly comparable but both increase and decrease proportionately with the complexity of running the function.
+Similar to Ethereum miners, validators do measure the amount of gas (called ArbGas in Arbitrum) a transaction takes, although Arbitrum emulates EVM code with its own different opcodes.
+Thus, ArbGas with a roll-up and Layer 1 gas without a roll-up are not directly comparable but both increase and decrease proportionately with the complexity of running the function.
 Closing a market with 38 pairs costs 46,705,693 ArbGas.

### 2021-05-26 LaTeX-ACM/sections/paper.tex
minor edits

@@
 The final issue is who invokes \texttt{closeMarket()} every other block?
-There are actually two issues here: the issue of scheduling the function call and the issue of paying for it.
+There are two issues here: the issue of scheduling the function call and the issue of paying for it.
 For scheduling the function call, we can do one of the following: rely on market participants, who are eager to trade, to reopen the market, offer a bounty to reopen the market, or use an external service like Ethereum Alarm Clock (which creates a regulatory hook).\footnote{\url{https://ethereum-alarm-clock-service.readthedocs.io/}} Next, we consider the second issue of who pays to close the market.
@@
 \textit{Layer 2} solutions are a group of technologies that are designed and proposed to address specific drawbacks of executing transactions on \textit{Layer 1} (\ie Ethereum and other blockchains)~\cite{gudgeon2020sok}.
-These technologies focus on fast transaction throughput, reducing gas costs, or educing transaction latency.
+These technologies focus on fast transaction throughput, reducing gas costs, and reducing transaction latency.
 When using \cm, we strive to reduce the gas cost as performance is the main bottleneck.
-Thus, we choose a Layer 2 technology called \textit{roll-up} which aims at reducing the gas cost for operating on Layer 1 by taking the transaction executions off-chain and only using the Ethereum blockchain for storing data.
+Thus, we choose a Layer 2 technology called \textit{roll-up}.
+This technology aims at reducing the gas cost for operating on Layer 1 by taking the transaction executions off-chain and only using the Ethereum blockchain for storing data.
 In a roll-up, every transaction is executed by a server or cluster of servers known as \textit{validators} that can be run by a collection of users or third party operators (here they can be run by the token issuer).

### 2021-05-26 LaTeX-ACM/sections/paper.tex
edits

@@
 Our proof-of-concept, \cm, is an extensible base class suitable for experiments.
-\cm is designed from a security perspective: users only trust their assets to \cm's auditable code (non-custodial) and not to a third part, all operations are transparent, and we nearly eliminate the ability for adversarial network nodes to profit from front-running orders.
+\cm is designed from a security perspective: users only trust their assets to \cm's auditable code (non-custodial) and not to a third party, all operations are transparent, and we nearly eliminate the ability for adversarial network nodes to profit from front-running orders.
 In fact, we believe we are the first to design a decentralized application that actually leverages front-running (\ie miner extractable value~\cite{daian2019flash}) for the benefit of the system (see Section~\ref{sec:close}).
@@
 A public blockchain is an open peer-to-peer network that maintains a set of transactions without a single entity in charge.
-In Ethereum, \emph{transactions} encode the bytecode of user-written \emph{decentralized applications} (DApps) to be stored on the blockchain; and the function calls made to the DApp.
+In Ethereum, \emph{transactions} encode the bytecode of user-written \emph{decentralized applications (DApps)} to be stored on the blockchain; and the function calls made to the DApp.
 Every execution of every function call is validated by all honest, participating nodes to correct; a property that is robust against a fraction of faulty and malicious network nodes (or more precisely, their accumulated computational power).
@@
 Essentially, our main research question is how many on-chain trades can be executed without exceeding that limit.
-Later we also discuss several bytecode operations (\emph{opcodes}) that refund gas (\ie cost negative gas), which we heavily utilize in our optimizations.
+Later, we also discuss several bytecode operations (\emph{opcodes}) that refund gas (\ie cost negative gas), which we heavily utilize in our optimizations.
 
@@
 Exchanges for blockchain-based assets (also called crypto assets by enthusiasts) can operate the same way, using a centralized exchange (CEX) design where a firm (\eg Binance, Bitfinex, \etc) operates the platform as a trusted third party in every aspect: custodianship over assets/currency being traded, exchanging assets fairly, offering the best possible price execution.
-Security breaches and fraud in centralized exchanges  (\eg MtGox~\cite{TheHisto45:online}, QuadrigaCX~\cite{SEBIOrde83:online}, and many others) have become a common source of lost funds for users, while accusations of unfair trade execution have been leveled but are difficult to prove.
+Security breaches and fraud in centralized exchanges  (\eg MtGox~\cite{TheHisto45:online}, QuadrigaCX~\cite{SEBIOrde83:online}, and many others) have become a common source of lost funds for users, while accusations of unfair trade execution have been levelled but are difficult to prove.
 Today, CEXes are often regulated as other money service businesses---this provides some ability for the government to conduct financial tracking but does little to provide consumer protection against fraud.
@@
 
-\paragraph{Hybrid Designs.} Before on-chain dealers became prominent in the late 2010s, the most popular design was hybrid order-driven exchanges with some trusted off-chain components and some on-chain functionality.
+\paragraph{Hybrid Designs.} Before on-chain dealers became prominent in the late 2010s, the most popular design was hybrid order-driven exchanges with some trusted off-chain components and some on-chain functionalities.
 Such decentralized exchanges (DEXes) were envisioned as operating fully on-chain, but performance limitations drove developers to move key components, such as the order matching system, off-chain to a centralized database.

### 2021-05-26 LaTeX-ACM/sections/paper.tex
related work

@@
 
-\paragraph{Other Academic Literature.} There are numerous industry projects on blockchain-based exchanges and order books, but most of the academic literature is on topics that are related but tangential to the mechanics of trade execution.
-Early (and some recent) literature consider trade execution under encryption (\ie dark markets) for securities~\cite{TP07,YSLT10,TW12,cartlidge2019mpc} and futures~\cite{massacci2018futuresmex}.
-A number of projects consider structuring derivatives in smart contracts---Velocity ~\cite{eskandari2017feasibility}, Findel ~\cite{biryukov2017findel}---but once issued, the derivative can be traded using exchanges.
-Atomic swaps (\ie payment vs.
-delivery) are necessary for settling trades and some general approaches include Arwen~\cite{heilman2020arwen} and Tesseract~\cite{bentov2017tesseract}.
+\paragraph{Other Academic Literature.}
 
-\textblue{Jeremy to do: merge in Hisham~\cite{galalpublicly} paper here.}
-The most similar academic work to this paper is the TEX exchange~\cite{khalil2019tex}.
-TEX is also an implementation of an order book; however, it uses on-chain and off-chain components, and does not answer our research question of how feasible an on-chain order book is.
-We later compare it to our variant with roll-ups in Section~\ref{sec:rollups}.
-The main overlap is our common focus on resisting front-running attacks.
-In a recent survey on front-running attacks in blockchain~\cite{eskandari2019sok}, three solutions are proposed.
-One solution is to provide confidentiality over the content of orders which is the approach taken by TEX.
+The most similar academic work to this paper is the Ethereum-based periodic auction by Galal \etal~\cite{galalpublicly} and the continuous-time exchange TEX~\cite{khalil2019tex}.
+As with us, front-running is a main consideration of these works.
+In a recent SoK on front-running attacks in blockchain~\cite{eskandari2019sok}, three general mitigations are proposed.
+Both of these papers use the solution of providing confidentiality over the content of orders.
 The main downside is that honest traders cannot submit their orders and leave, they must interact in a second round to reveal their orders.
-The second solution is to sequence transactions according to some rule, either at the protocol level~\cite{MZGA20} or as a third-party service~\cite{Kla20} (a regulatory hook).
+The second mitigation approach is to sequence transactions according to some rule, either at the protocol level~\cite{MZGA20} or as a third-party service~\cite{Kla20} (a regulatory hook).
 These are very recent works and are not available for experimentation on Ethereum yet (although Chainlink has announced an intention\footnote{A.
@@
 \href{https://blog.chain.link/chainlink-fair-sequencing-services-enabling-a-provably-fair-defi-ecosystem/}{blog.chain.link}, 11 Sep 2020.}).
-The third solution is to design the service in a way that front-running attacks are not profitable---this is the approach we take here.
+The third solution is to design the service in a way that front-running attacks are not profitable---this is the approach with \cm which uses \textit{no cryptography} and is \textit{submit-and-go} for traders.
+A detailed comparison of front-running is provided in Section~\ref{sec:front}.
+
+Our paper also emphasizes implementation details: Galal \etal do not provide a full implementation, and TEX uses both on-chain and off-chain components, and thus does not answer our research question of how feasible an on-chain orderbook is.
+
+Less related are papers on topics tangential to the mechanics of trade execution.
+Early (and some recent) literature consider trade execution under encryption (\ie dark markets) for securities~\cite{TP07,YSLT10,TW12,cartlidge2019mpc} and futures~\cite{massacci2018futuresmex}.
+Velocity~\cite{eskandari2017feasibility} and Findel~\cite{biryukov2017findel} consider structuring derivatives in smart contracts.
+Atomic swaps (\ie payment vs.
+delivery) are necessary for settling trades and some general approaches include Arwen~\cite{heilman2020arwen} and Tesseract~\cite{bentov2017tesseract}.
 
@@
 Therefore, an object-oriented linked list must either (i) create each node in the list as a struct---but this is not possible as Solidity does not support recursive structs---or (ii) make every node in the list its own contract.
-\textblue{The latter option seems wasteful and unusual, but we try it out anyways.} Thus, each node is its own contract and contains the incoming order's data and a pointer to the address of the next contract in the list.
+The latter option seems wasteful and unusual, but it ends up being the most gas efficient data structure to dequeue.
+Thus, each node is its own contract and contains the incoming order's data and a pointer to the address of the next contract in the list.
 

### 2021-05-27 LaTeX-ACM/sections/paper.tex
finally done the front-running analysis 😅💦

@@
 Call markets largely side step front-running attacks from other traders because reordering trades has no impact (discussed more in section~\ref{sec:front}).
-The paper does not include an implementation and was envisioned as running on a custom blockchain (Ethereum was still in development in 2014).
-Market operations are part of the blockchain logic.
+The paper does not include an implementation, was envisioned as running on a custom blockchain (Ethereum was still in development in 2014) and market operations are part of the blockchain logic.
 
@@
 Other exchanges, called crossing networks, also operate as a call market at various times throughout the trading day.\footnote{A crossing network uses a secondary market for determining the closing price.
-Many prominent crossing networks are operated internally within a brokerage for its clients, and often as a `dark pool' with an unpublished order book.} Call markets are studied widely in finance~\cite{Har03}, with recent interest in using them to combat high frequency trading~\cite{budish2015high,aquilina2020quantifying}.
+Many prominent crossing networks are operated internally within a brokerage for its clients, and often as a `dark pool' with an unpublished order book.} Call markets are studied widely in finance~\cite{Har03}, with recent interest in expanding their use to combat high frequency trading~\cite{budish2015high,aquilina2020quantifying}.
 Time-sensitive traders submit orders early, especially in crossing networks that close at a randomly determined time (traders risk missing the call if they wait too long).
 A blockchain happens to provide this function naturally, as blocks are published unpredictably.
-Price-sensitive traders wait to base their pricing off the already submitted orders and do not mind missing a call if it obtains them a better price.
+%Price-sensitive traders wait to base their pricing off the already submitted orders and do not mind missing a call if it obtains them a better price.
 
@@
 The front-running attacks in Table~\ref{tab:front} are sub-categorized, using a recent SoK~\cite{eskandari2019sok}, as being \emph{Insertion}, \emph{Displacement}, and \emph{Suppression}.
-To illustrate the difference, we will consider the first three attacks in the table.
+To explain the difference, we will illustrate the first three attacks in the table.
 
-In an \emph{insertion attack}, Mallory learns of a transaction from Alice, arranges for her transaction to run first with the purpose of Alice's transaction being the next transaction to run.
-For example, if Alice was
+In an \emph{insertion attack}, Mallory learns of a transaction from Alice.
+Consider Alice submitting a bid order for 100 tokens at any price (market order).
+Mallory decides to add new ask orders to the book (limit orders) at the maximum price reachable by Alice's order given the rest of the asks in the book.
+Mallory must arrange for her orders to be added before Alice's transaction and then arrange for Alice's transaction to be the next (relevant) transaction to run (\eg before competing asks from other traders are added).
 
- fronting attacks: 
-t
+In a centralized exchange, Mallory would collude with the \emph{authority} running the exchange to conduct this attack.
+On-chain, Mallory could be a fast \emph{trader} who sees Alice's transaction in the mempool and adds her transaction with a higher gas fee to bribe miners to execute her's first (insertion is probabilist and not guaranteed).
+Finally Mallory could be the \emph{miner} of the block that includes Alice's transaction allowing her to insert with high fidelity.
+Roll-ups use \emph{sequencers} discussed in Section~\ref{sec:frontarb}.
 
-(i) in an \emph{displacement attack}, Mallory knows of a transaction from Alice and inserts her transaction before Alice's and does not care what happens to Alice's transaction;
+A \emph{displacement attack} is like an insertion attack, except Mallory does not care what happens to Alice's original transaction---she only cares about being first.
+If Mallory sees Alice try to execute a trade at good price, she could try to beat Alice and execute the trade first.
+Mallory is indifferent to whether Alice can then execute her trade or not.
+The analysis of both insertion and suppression attacks are similar.
+Call markets mitigate these basic insertion and displacement attacks because they do not have any time priority (e.g., if you were to shuffle the order of all orders submitted within the same call, the outcome would be exactly the same).
+A different way to mitigate these attacks is to seal orders with confidentiality (a \textit{dark} market).
 
-(iii) in a \emph{suppression attack}, Mallory displaces all future transactions for some period of time.
-Mallory can be a miner which can freely order transactions within the blocks it creates, or Mallory can be a fast user (or bot) who can quickly react to Alice's broadcasted but unconfirmed transactions, likely offering higher gas fees to have her transactions prioritized over Alice's.
-Later in Section~\ref{sec:frontarb}, we discuss a third kind of participant: sequencers.
+In a \emph{suppression attack}, Mallory floods the network with transactions until a trader executes her order.
+Such selective denial of service is possible by an off-chain operator.
+With on-chain continuous markets, it is not possible to suppress Alice's transaction while also letting through a transaction from a taker---suppression applies to all Ethereum transactions or none.
+A call market is uniquely vulnerable because it eventually times out (which does not require an on-chain transaction) and new orders cannot be added.
+We still award a call market partial mitigation since suppression attacks are expensive (\cf Fomo3D attack~\cite{eskandari2019sok}).
+If the aim of suppression is a temporary denial of service (captured by attack 5 in the table), then all on-chain markets are vulnerable to this expensive attack.
 
-Consider the first two attacks in Table~\ref{tab:front}. Talk about our cattegories from front-running paper.
-
- Call markets are less vulnerable to these basic insertion and displacement attacks because they do not have any time priority (e.g., if you were to shuffle the order of all orders submitted within a window of time to a call market, the outcome would be exactly the same).
-A different way to mitigate these attacks is to add confidentiality on the orders (cite Tex, Hisham) which
-
- A, and the same sequence is randomly shuffled and submitted to market B.
-In a call market, the outcome of A and B will be exactly equivalent, which is not true in the other types.The remove of time priority
-
- There is no threat from miners reordering transactions or traders offering higher gas rates to have their orders executed before other orders already broadcast.
-
+Some attacks combine more than one insertion, displacement, and/or suppression attacks.
+AMMs are vulnerable to a double insertion called a sandwich attack~\cite{ZQFLG21} which bookends a victim's trade with the frontrunner's trades.
 In a traditional call market, a market clearing price is chosen and all trades are executed at this price.
-All bids made at a higher price will receive the assets for the lower clearing price (and conversely for lower ask prices): this is called a \textit{price improvement}.
-A miner about to mine on a set of transactions, including its own orders, could drop other traders' orders to maximize its own price improvement.
-For this reason, in \cm, all price improvements are given to the miner (using \texttt{block.coinbase.transfer()}).
+All bids made at a higher price will receive the assets for the lower clearing price (and conversely for lower ask prices): this is called a \textit{price improvement} and it allows traders to submit at their best price.
+A hybrid front-running attack allows Mallory to extract any price improvements.
+Consider the case where Alice's ask crosses Bob's bid with a material price improvement.
+Mallory inserts a bid at Alice's price, suppresses Bob's bid until the next call, and places an ask at Bob's price.
+She keeps buys and sells the asset and nets the price improvement as arbitrage.
+To mitigate this in \cm, all price improvements are given to the miner (using \texttt{block.coinbase.transfer()}).
 This does not actively hurt traders---they always receive the same price that they quote in their orders---and it removes any incentive for miners to front-run these profits.
 
-Potential for front-running still exists around ties on price and order cancellations (both discussed in the next section).
-Finally, \textit{supression attacks}~\cite{eskandari2019sok} are possible where competitive orders are delayed long enough for the market to close without them or the adversary fills up the current market (which caps the number of orders) to ensure other orders cannot be added.
-Both are expensive attacks.
-For all these reasons, we say \cm reduces front-running attacks but stop short of saying this issue is completely solved by \cm.
+Other front-running attacks use order cancellations (discussed in the next section) which \cm mitigates by running short-lived markets with no cancellations.
+
+There are two main takeaways from Table~\ref{tab:front}.
+Call markets provide strong resilience to front-running only bested slightly by dark markets like TEX~\cite{khalil2019tex}, however they do it through design---no cryptography and no two-round protocols.
+A second observation is that dark call markets, like Galal \etal~\cite{}, are no more resilience to front-running than a lit market (however confidentiality could provide resilience to predatory trading algorithms that are reactionary but do not front-run).
 

### 2021-05-27 LaTeX-ACM/sections/paper.tex
some edits

@@
 The main downside is that honest traders cannot submit their orders and leave, they must interact in a second round to reveal their orders.
-The second mitigation approach is to sequence transactions according to some rule, either at the protocol level~\cite{MZGA20} or as a third-party service~\cite{Kla20} (a regulatory hook).
+The second mitigation approach is to sequence transactions according to some rule, either at the protocol level~\cite{kelkar2020order} or as a third-party service~\cite{Kla20} (a regulatory hook).
 These are very recent works and are not available for experimentation on Ethereum yet (although Chainlink has announced an intention\footnote{A.
@@
 Call markets provide strong resilience to front-running only bested slightly by dark markets like TEX~\cite{khalil2019tex}, however they do it through design---no cryptography and no two-round protocols.
-A second observation is that dark call markets, like Galal \etal~\cite{}, are no more resilience to front-running than a lit market (however confidentiality could provide resilience to predatory trading algorithms that are reactionary but do not front-run).
+A second observation is that dark call markets, like \textblue{Galal \etal~\cite{galal2018verifiable}}, are no more resilience to front-running than a lit market (however confidentiality could provide resilience to predatory trading algorithms that are reactionary but do not front-run).
 
-\subsection{Cleaning Up Revisited}
+\textblue{\subsection{Cleaning Up Revisited}}
 

### 2021-05-27 LaTeX-ACM/sections/paper.tex
frontrunning on arb

--- 2021-05-27 LaTeX-ACM/sections/paper.tex
@@
 A continuous market has both.
-All traders with an automated market maker are takers, while the investors who provide tokens (or liquidity) to the AMM for trading are makers.
+All traders using an automated market maker are takers, while the investors who provide tokens to the AMM (liquidity providers) are makers.
 Under our definition, a call market only has makers: the only way to have a trade executed is to submit an order.
@@
 Some attacks combine more than one insertion, displacement, and/or suppression attacks.
-AMMs are vulnerable to a double insertion called a sandwich attack~\cite{ZQFLG21} which bookends a victim's trade with the frontrunner's trades.
+AMMs are vulnerable to a double insertion called a sandwich attack~\cite{ZQFLG21} which bookends a victim's trade with the frontrunner's trades (plus additional variants).
 In a traditional call market, a market clearing price is chosen and all trades are executed at this price.
@@
 Call markets provide strong resilience to front-running only bested slightly by dark markets like TEX~\cite{khalil2019tex}, however they do it through design---no cryptography and no two-round protocols.
-A second observation is that dark call markets, like Galal \etal~\cite{}, are no more resilience to front-running than a lit market (however confidentiality could provide resilience to predatory trading algorithms that are reactionary but do not front-run).
+A second observation is that dark call markets, like Galal \etal~\cite{galalpublicly}, are no more resilience to front-running than a lit market (however confidentiality could provide resilience to predatory trading algorithms that are reactionary but do not front-run).
 
@@
 Arbitrum runs entire DApps inside its environment, which acts like a container and requires special bridge contacts to interact with `normal' (or Layer 1) Ethereum DApps.
-To deploy a DApp on Arbitrum, or to execute a function on an existing Arbitrum DApp, the transaction is sent to a Layer 1 Arbitrum contract called Inbox.
-The transaction is not executed, it is only recorded (as calldata) by the Inbox contract.
+To deploy a DApp on Arbitrum, or to execute a function on an existing Arbitrum DApp, the transaction is sent to an \textit{inbox contract} on Layer 1.
+The transaction is not executed, it is only recorded (as calldata) in the inbox.
 Like any other transactions on Ethereum, miners determine the order of the transactions sent to this contract.
-A set of validators (open to anyone) are watching the Inbox contract for new transactions.
+A set of validators (open to anyone) are watching the inbox contract for new transactions.
 Once an inbox transaction is finalized in an Ethereum block, validators will execute the transaction and asserts the result of the execution to other validators on a sidechain called ArbOS.
 Once the dispute challenge period is over, the new state of ArbOS will be inserted into Ethereum.
-As the Inbox contract maintains all Arbitrum transactions, anyone can recompute the entire current state of the ArbOS and file a dispute if executions are not performed correctly.
+As the inbox contract maintains all Arbitrum transactions, anyone can recompute the entire current state of the ArbOS and file a dispute if executions are not performed correctly.
 Disputes are adjudicated by Ethereum itself and require essentially constant gas costs, regardless of the size of the gas costs of the transaction being disputed.
@@
 
-\textit{Testing Platforms.} Arbitrum currently operates a test network with an Inbox contract on the Ethereum Kovan testnet.
+\textit{Testing Platforms.} Arbitrum currently operates a test network with an inbox contract on the Ethereum Kovan testnet.
 To experiment with Arbitrum, we implemented a variant of \cm and ran the same experiments that we previously performed on Layer 1 (Ethereum).
-To call functions on \cm, traders can (i) send transactions directly to the Inbox contract \href{https://kovan.etherscan.io/address/0x76bF1345224fE606E2aB38B8E52B83512328A9DF}, or (ii) use a relay server (called a \textit{Sequencer}) provided by the Arbitrum.
-The sequencer will group, order,  and send all pending transactions together as a single Kovan transaction to the Inbox (and pay the gas).
+To call functions on \cm, traders can (i) send transactions directly to the inbox contract \href{https://kovan.etherscan.io/address/0x76bF1345224fE606E2aB38B8E52B83512328A9DF}, or (ii) use a relay server (called a \textit{Sequencer}) provided by the Arbitrum.
+The sequencer will group, order, and send all pending transactions together as a single Kovan transaction to the inbox (and pay the gas).
 
@@
 With Arbitrum roll-ups, 38 pairs cost only 1,632 in Layer 1 gas (a 99.9\% savings).
-This is effectively the cost of recording the \texttt{closeMarket()} function call in the Inbox, which is 103 bytes of calldata.
+This is effectively the cost of recording the \texttt{closeMarket()} function call in the inbox, which is 103 bytes of calldata.
 As the number of pairs increases, Layer 1 gas cost is constant.
@@
 
-Recall for running functions on \cm on Arbitrum, traders must first instantiate the truncation by sending it to the Arbitrum EthBridge contract.
-As as soon as this transaction is included in the Layer 1 (Ethereum) block, it will get time-stamped and ordered.
-Thus, potential for front-running on Arbitrum is same as those explained in~\ref{sec:front}.'
+In the \cm variant, traders can submit transactions to the L1 inbox contract instead of directly to the \cm DApp.
+This has the same front-running profile as \cm itself; only the L1 destination address is different.
+If a sequencer is mandatory, it acts with the same privilege as an L1 Ethereum miner in ordering the transactions it receives.
+Technically, sequencers are not limited to roll-ups and could be used in the context of normal L1 DApps, but they are more apparent in the context of roll-ups.
+A sequencer could be trusted to execute transactions in the order it receives them, outsource to a fair ordering service, or (in an tacit acknowledge of the difficulties of preventing frontrunning) auction off permission to order transactions to the highest bidder.
+As shown in Table~\ref{tab:front}, a sequencer is an additional frontrunning actor but does not otherwise change the kinds of attacks that are possible.
 
-\textblue{Say something about \texttt{block.coinbase()} and Arbitrum.}
-
-\textblue{Say something about sequencer.}
+% JC: I think too minor to mention
+%Finally, we note a minor technical issue.
+Recall that in \cm, price improvements are given to miners to prevent a hybrid frontrunning attack.
+As Arbitrum does not run on L1, it burns (bridged) ETH sent via \texttt{block.coinbase()}.
+With some effort, Arbitrium could be updated to route the payment to the L1 miner of the block that added closeMarket() to the inbox.
 

### 2021-05-27 LaTeX-ACM/sections/paper.tex

@@
 
-\subsection{Cleaning Up Revisited}
+\textblue{\subsection{Cleaning Up Revisited}}
 

### 2021-05-27 LaTeX-ACM/sections/paper.tex
camera ready 📸 ✅

@@
 
-\textbf{Contributions.} We study fully on-chain markets through design and implementation with Solidity---a high-level programming language for Ethereum that is syntactically similar to Java~\cite{Ethereum41:online}.
+\textbf{Contributions.} We study fully on-chain markets through design and implementation with Solidity---a high-level programming language for Ethereum that is syntactically similar to Java.
 We choose Ethereum as a hostile environment for an order book: Ethereum is fully decentralized (hardest to regulate), network participation is open to anyone on the internet (strongest adversarial model), and, as a result, it is slow (a lower-bound benchmark).
@@
 For this reason, stored variables persist for a long time and, at first glance, it seems pointless to free up variable storage (and unclear what `free up' even means).
-Once the current state of the EVM is established by a node, it can forget about every historical variable changes and only concern itself with the variables that have non-zero value (as a byte string for non-integers) in the current state (uninitialized variables in Ethereum have the value 0 by default).\textblue{ Therefore, freeing up variables will reduce the amount of state Ethereum nodes need to maintain going forward.}
+Once the current state of the EVM is established by a node, it can forget about every historical variable changes and only concern itself with the variables that have non-zero value (as a byte string for non-integers) in the current state (uninitialized variables in Ethereum have the value 0 by default).
+Therefore, freeing up variables will reduce the amount of state Ethereum nodes need to maintain going forward.
 
@@
 
-\textblue{\subsection{Cleaning Up Revisited}}
+\subsection{Cleaning Up Revisited}
 
-\textblue{Beyond the cleaning up issues with priority queues in Section~\ref{sec:gasrefund}, \cm also uses mappings with each market.} Traders preload their account with tokens to be traded (which comply with a common token standard called ERC20) and/or ETH.
+Recall the issue of cleaning up with priority queues in Section~\ref{sec:gasrefund}.
+Every time a market opens, \cm creates new mappings that are no longer needed after a market closes.
+Traders preload their account with tokens to be traded (which comply with a common token standard called ERC20) and/or ETH.
 \cm tracks what they are owed using a mapping called \texttt{totalBalance} and allows traders to withdraw their tokens at any time.
@@
 
-\textblue{As the DApp runs \texttt{closeMarket()}}, it starts matching the best bids to the best asks.
+When \texttt{closeMarket()} runs, \cm starts matching the best bids to the best asks.
 As orders execute, \texttt{totalBalance} and \texttt{unavailableBalance} are updated.
@@
 As the inbox contract maintains all Arbitrum transactions, anyone can recompute the entire current state of the ArbOS and file a dispute if executions are not performed correctly.
-Disputes are adjudicated by Ethereum itself and require essentially constant gas costs, regardless of the size of the gas costs of the transaction being disputed.
-
-% = = = = = = = = = = = = = = = = = = = = = = = = =  %
-\subsection{Token Bridges with Arbitrum}
+Disputes are adjudicated by Ethereum itself and require essentially constant gas costs, regardless of the size of the gas costs of the transaction being disputed
 
@@
 
+\section{Availability} 
+The Solidity source code for \cm, Truffle test files, and Arbitrum dependencies are available in a GitHub repository (non-anonymous link omitted).
+We have also deployed \cm on Ethereum's testnet Rinkeby with flattened (single file) source code of just the \cm base class and priority queue implementations.
+It is visible and can be interacted with here: \href{https://rinkeby.etherscan.io/address/0x0d91de29c531d074853a5cef7cf9dfeb9c6ec4e0}{[etherscan.io]}; while the Arbitrum variant is here: \href{https://explorer5.arbitrum.io/#/address/0x18BF65069Fdaed79f8BDB0B6EDa87d5cc46F6E28}{[explorer5.offchainlabs.com]}.
+
 \begin{acks}

### 2021-05-27 LaTeX-ACM/sections/paper.tex
camera ready ready

@@
 
-Our proof-of-concept, \cm, is an extensible base class suitable for experiments.
+Our proof of concept, \cm, is an extensible base class suitable for experiments.
 \cm is designed from a security perspective: users only trust their assets to \cm's auditable code (non-custodial) and not to a third party, all operations are transparent, and we nearly eliminate the ability for adversarial network nodes to profit from front-running orders.
@@
 
-\paragraph{On-chain Order Books.} For trades between two blockchain-based assets (\eg a digital asset priced with a cryptocurrency, stablecoin, or second digital asset), order matching can be performed `on-chain' by deploying the order-matching system either on a dedicated blockchain or inside a decentralized application (DApp).
+\paragraph{On-chain Order Books.} For trades between two blockchain-based assets (\eg a digital asset priced in a cryptocurrency, stablecoin, or second digital asset), order matching can be performed `on-chain' by deploying the order-matching system either on a dedicated blockchain or inside a decentralized application (DApp).
 In this model, traders entrust their assets to an autonomously operating DApp with known source code instead of a third party custodian that can abscond with or lose the funds.
@@
 Finally, anyone can create an on-chain order book for any asset (on the same chain) at any time.
-While they sound ideal, performance is a substantial issue and the main subject of this paper.
+While these sound ideal, performance is a substantial issue and the main subject of this paper.
 Since it is an open system, there is no obvious regulatory hook (beyond the blockchain itself).
@@
 This has fuelled a resurgence in on-chain exchange but through a quote-driven design rather than an order-driven one.
-Automated market makers  (\eg Uniswap v3) have all the trust advantages of an on-chain order book, plus they are very efficient relative to an on-chain order book.
+Automated market makers  (\eg Uniswap v3) have all the trust advantages of an on-chain order book, plus they are relatively more efficient.
 The trade-off is that they operate as a dealer---the DApp exchanges assets from its own inventory.
@@
 
-Our paper also emphasizes implementation details: Galal \etal do not provide a full implementation, and TEX uses both on-chain and off-chain components, and thus does not answer our research question of how feasible an on-chain orderbook is.
+Our paper also emphasizes implementation details: Galal \etal do not provide a full implementation, and TEX uses both on-chain and off-chain components, and thus does not answer our research question of how feasible an on-chain order book is.
 
@@
 For these reasons, we suggest using a linked list variant for this specific application.
-As it can be seen in Figure~\ref{fig:random_insertion}, the associated cost for inserting elements into a linked list PQ is significantly greater than the linked list with mapping, as each insertion causes the creation of a new DApp.
+As it can be seen in Figure~\ref{fig:random_insertion}, the associated cost for inserting elements into a linked list PQ is significantly greater than the linked list with mapping, as each insertion causes the creation of a new contract.
 Accordingly, we choose to implement the call market with the linked list with mapping.
-Overall this PQ balances a moderate gas cost for insertion (\ie order submission) with one for removal (\ie closing the market and matching the orders).
+Overall, this PQ balances a moderate gas cost for insertion (\ie order submission) with one for removal (\ie closing the market and matching the orders).
 
@@
 So in order to account for refunds in Tables~\ref{tab:PQUnitTests}, we calculate them manually.
-First, we need to figure out exactly how much storage is being cleared or how many smart contracts are being destroyed, then we multiply these numbers by 24,000 and 15,000 respectively.
+First, we need to figure out exactly how much storage is being cleared or how many smart contracts are being destroyed, then we multiply these numbers by 24,000 or 15,000 respectively.
 
@@
 
-One consequence of a linked list is that a new DApp is created for every node in the list.
+One consequence of a linked list is that a new contract is created for every node in the list.
 Beyond being expensive for adding new nodes (a cost that will be bared by the trader in a call market), it also leaves a large footprint in the active Ethereum state, especially if we leave the nodes on the blockchain in perpetuity (\ie we just update the head node of the list and leave the previous head `dangling').
@@
 Alternatively, we can call \texttt{DELETE} on each mapping entry once we finish processing a node in the PQ.
-As it can be seen in the last two rows of Table~\ref{tab:cleaning}, leaving the data on chain is cheaper than cleaning it up.
+As it can be seen in the last two rows of Table~\ref{tab:cleaning}, leaving the data on the blockchain is cheaper than cleaning it up.
 
@@
 
-\cm is proof of concept code and an extensible base class that is still functional without any extensions.
+\cm is a proof of concept code and an extensible base class that is still functional without any extensions.
 A call market will open for a specified period of time during which it will accept a capped number of orders (\eg 100 orders---parameterized so that all orders can be processed), and these orders are added to a PQ.
@@
 Another simplifying assumption is to implement a \textit{collateralized} call market.
-We assume all trades are between ETH and an ERC20 token, all orders are pre-funded in the DApp with ETH (for bids) and tokens (for asks), and once ETH or tokens are committed to an order, they cannot be withdrawn until the market closes.
+We assume all trades are between ETH and an ERC20 token, all orders are pre-funded in the contract with ETH (for bids) and tokens (for asks), and once ETH or tokens are committed to an order, they cannot be withdrawn until the market closes.
 This ensures all executed orders clear and settle (\ie no defaults on payment or delivery).
@@
 
-\cm is open source and written in 336 lines (SLOC) of Solidity plus the priority queue (\eg a heap with dynamic array is 282 SLOC).
-Refer to the availability section at the end of the paper.
+\cm is open source and written in 336 lines (SLOC) of Solidity plus the priority queue (\eg a heap with dynamic array is 282 SLOC)(see Section~\ref{sec:avai}).
 We tested it with the Mocha testing framework using Truffle on Ganache-CLI to obtain our performance metrics.
@@
 We looked at the \textit{worst-case} for performance which is when every submitted bid and ask is marketable (\ie will require fulfillment).
-In the first two columns, we determine the highest number of orders that can be processed in a single call to the \texttt{closeMarket()} and not exceed the current Ethereum block gas limit of 11,741,495.
+In the first two columns, we determine the highest number of trades that can be executed and processed in a single call to the \texttt{closeMarket()} and not exceed the current Ethereum block gas limit of 11,741,495.
 Since Ethereum will become more efficient over time, we were also interested in how much gas it would cost to execute 1000 pairs of orders, which is given in the third column.
@@
 In a centralized exchange, Mallory would collude with the \emph{authority} running the exchange to conduct this attack.
-On-chain, Mallory could be a fast \emph{trader} who sees Alice's transaction in the mempool and adds her transaction with a higher gas fee to bribe miners to execute her's first (insertion is probabilist and not guaranteed).
-Finally Mallory could be the \emph{miner} of the block that includes Alice's transaction allowing her to insert with high fidelity.
+On-chain, Mallory could be a fast \emph{trader} who sees Alice's transaction in the mempool and adds her transaction with a higher gas fee to bribe miners to execute hers first (insertion is probabilist and not guaranteed).
+Finally, Mallory could be the \emph{miner} of the block that includes Alice's transaction allowing her to insert with high fidelity.
 Roll-ups use \emph{sequencers} discussed in Section~\ref{sec:frontarb}.
@@
 A \emph{displacement attack} is like an insertion attack, except Mallory does not care what happens to Alice's original transaction---she only cares about being first.
-If Mallory sees Alice try to execute a trade at good price, she could try to beat Alice and execute the trade first.
+If Mallory sees Alice trying to execute a trade at a good price, she could try to beat Alice and execute the trade first.
 Mallory is indifferent to whether Alice can then execute her trade or not.
@@
 Some attacks combine more than one insertion, displacement, and/or suppression attacks.
-AMMs are vulnerable to a double insertion called a sandwich attack~\cite{ZQFLG21} which bookends a victim's trade with the frontrunner's trades (plus additional variants).
+AMMs are vulnerable to a double insertion called a sandwich attack~\cite{ZQFLG21} which bookends a victim's trade with the front-runner's trades (plus additional variants).
 In a traditional call market, a market clearing price is chosen and all trades are executed at this price.
@@
 Mallory inserts a bid at Alice's price, suppresses Bob's bid until the next call, and places an ask at Bob's price.
-She keeps buys and sells the asset and nets the price improvement as arbitrage.
+She buys and then immediately sells the asset and nets the price improvement as arbitrage.
 To mitigate this in \cm, all price improvements are given to the miner (using \texttt{block.coinbase.transfer()}).
@@
 Call markets provide strong resilience to front-running only bested slightly by dark markets like TEX~\cite{khalil2019tex}, however they do it through design---no cryptography and no two-round protocols.
-A second observation is that dark call markets, like Galal \etal~\cite{galalpublicly}, are no more resilience to front-running than a lit market (however confidentiality could provide resilience to predatory trading algorithms that are reactionary but do not front-run).
+A second observation is that dark call markets, like Galal \etal~\cite{galalpublicly}, are no more resilient to front-running than a lit market (however confidentiality could provide resilience to predatory trading algorithms that are reactionary but do not front-run).
 
@@
 At a certain point, the bids and asks will stop matching in price.
-At this point, every order left in the order book cannot execute (the priority queue sorts orders by price, so orders deeper in the queue have worst prices than the order at the head of the queue).
-Therefore all remaining entries in \texttt{unavailableBalance} can be cleared.
+At this point, every order left in the order book cannot execute (the priority queue sorts orders by price, so orders deeper in the queue have worse prices than the orders at the head of the queue).
+Therefore, all remaining entries in \texttt{unavailableBalance} can be cleared.
 
@@
 At the same time, it is wasteful to let an entire mapping sit in the EVM when it will never be referenced again.
-The following are some options for addressing this conflict.
+The following are some options for addressing this conflict:
 
@@
 
-\item \textbf{Manually Clearing the Mapping.} Since mappings cannot be iterated, a common design pattern used by DApp developers is to store keys in an array and iterate over the array to zero out each mapping and array entry.
+\item \textbf{Manually Clear the Mapping.} Since mappings cannot be iterated, a common design pattern used by DApp developers is to store the keys in an array and iterate over the array to zero out each mapping and array entry.
 Clearing a mapping this way costs substantially more to clear than what is refunded.
 
-\item \textbf{Store the Mapping in a Separate DApp.} We could wrap the mapping inside its own DApp and run \texttt{SELFDESTRUCT} on the contract once we finish processing the mapping.
+\item \textbf{Store the Mapping in a Separate DApp.} We could wrap the mapping inside its own DApp and run the \texttt{SELFDESTRUCT} operation on the contract once we finish processing the mapping.
 This refunds us 24,000 gas which is less than the cost of deploying the extra contract.
@@
 
-Clearing storage is important for reducing EVM bloat.
-The Ethereum refund model should be considered further by Ethereum developers to better incentivize developers to be less wasteful in using storage.
+Clearing storage is important for reducing EVM bloat. The Ethereum refund model should be considered further by Ethereum developers to provide a better incentive to be less wasteful in using storage.
 
@@
 When executing trades, if the volume of the current best bid does not match the best ask, the larger order is partially filled and the remaining volume is considered against the next best order.
-A common trading rule (that does resist front-running) is to fill ties in proportion to their volume (\ie \textit{pro rata} allocation)\footnote{If Alice and Bob bid the same price for 100 tokens and 20 tokens respectively, and there are only 60 tokens left in marketable asks, Alice receives 50 and Bob 10.} however this approach does not always work.
+A common trading rule (that does resist front-running) is to fill ties in proportion to their volume (\ie \textit{pro rata} allocation)\footnote{If Alice and Bob bid the same price for 100 tokens and 20 tokens respectively, and there are only 60 tokens left in marketable asks, Alice receives 50 and Bob 10.}, however this approach does not always work.
 Consider the following corner case: 3 equally priced bids of 1 non-divisible token and 1 ask at the same price.
-There is no good option: (1) the bids could all be dropped, (2) bids could be prioritized based on time, or (3) the bid could be randomly chosen (\cf Libra~\cite{mavroudis2019libra}).
+There is no good option: (1) the bids could all be dropped, (2) the bids could be prioritized based on time, or (3) the bid could be randomly chosen (\cf Libra~\cite{mavroudis2019libra}).
 
@@
 This means insertion front-running attacks are possible for this corner case.
-However if these attacks proved to be a problem in practice, (3) is a better solution with one main drawback: on-chain sources of `randomness' are generally deterministic and manipulatable by miners~\cite{bonneau2015random,buenz2017proofs}, countermeasures can take a few blocks to select~\cite{boneh2018verifiable}).
+However if these attacks proved to be a problem in practice, (3) is a better solution with one main drawback: on-chain sources of `randomness' are generally deterministic and manipulatable by miners~\cite{bonneau2015random,buenz2017proofs}, countermeasures can take a few blocks to select~\cite{boneh2018verifiable}.
 
@@
 
-\paragraph{Evaluation.} Support for cancellation opens the market to new front-running issues where other traders (or miners) can displace cancellations until after the market closes (however one benefit of a call market is that beating a cancellation with a new order has no effect, assuming the cancellation is run any time before the market closes.
+\paragraph{Evaluation.} Support for cancellation opens the market to new front-running issues where other traders (or miners) can displace cancellations until after the market closes.
+However, one benefit of a call market is that beating a cancellation with a new order has no effect, assuming the cancellation is run any time before the market closes.
 Also, cancellations have a performance impact.
-Canceled orders can be removed from the underlying data structure or accumulated in a list that is cross-checked when closing the market.
+Cancelled orders can be removed from the underlying data structure or accumulated in a list that is cross-checked when closing the market.
 Removing orders requires a more verbose structure than a priority queue (\eg a self-balancing binary search tree instead of a heap; or methods to traverse a linked list rather than only pulling from the head).
@@
 Modifiers can enforce when the market operates openly (collecting orders) and when close can be run.
-In the Princeton paper~\cite{clark2014decentralizing}, the call market is envisioned to run as an alt-coin, where orders accumulate within a block and a miner closes the market as part of the logic of producing a new block (\ie within the same portion of code as computing their coinbase transaction in Bitcoin or gasUsed in Ethereum).
+In the Princeton paper~\cite{clark2014decentralizing}, the call market is envisioned to run as an alt-coin, where orders accumulate within a block and a miner closes the market as part of the logic of producing a new block (\ie within the same portion of code as computing their coinbase transaction in Bitcoin or \texttt{gasUsed} in Ethereum).
 
-If the call market runs as a DApp on Ethereum, it seems difficult to open and close the market every block.
-Someone needs to call the \texttt{closeMarket()} for every block (we return to who this is later) but the market will only work as intended if miners execute this function after every \texttt{submitBid()} and \texttt{submitAsk()} invocation.
+If the call market runs as a DApp on Ethereum, it seems difficult to open and close the market on every block.
+Someone needs to call the \texttt{closeMarket()} for every block (we return to who this is later), but the market will only work as intended if miners execute this function after every \texttt{submitBid()} and \texttt{submitAsk()} invocation.
 Since price improvements are paid to the miners, the miner is actually incentivized to run \texttt{closeMarket()} last to make the most profit.
@@
 These fees are accumulated by the DApp to use as a bounty.
-When the time window for the open market elapses, the user who calls \texttt{closeMarket()} receives the bounty.
+When the time window for the open market elapses, the user who calls the \texttt{closeMarket()} function receives the bounty.
 
@@
 \item \textbf{Use \texttt{msg.value}.} For the ETH side of a trade (\ie for bids), ETH could be sent with the function call to \texttt{submitBid()} to remove the need for    \texttt{depositEther()}.
-This works for markets that trade ERC-20 tokens for ETH, but would not work for ERC-20 to ERC-20 exchanges.
+This works for markets that trade ERC20 tokens for ETH, but would not work for ERC20 to ERC20 exchanges.
 
@@
 
-\item \textbf{Use ERC-20 Approval.} Instead of \cm taking custody of the tokens, the token holder could simply approve \cm to transfer tokens on her behalf.
+\item \textbf{Use ERC20 Approval.} Instead of \cm taking custody of the tokens, the token holder could simply approve \cm to transfer tokens on her behalf.
 If \cm is coded securely, it is unconcerning to allow the approval to stand long-term and the trader never has to lock up their tokens in the DApp.
@@
 If a trade fails because the pledged tokens are not available, the fidelity bond is slashed as punishment.
-This lets traders side-step time-consuming transfers to and from \cm while still incentivizing them to ensure that submitted orders can actually be executed.
-The trade-off  is that \cm needs to update balances with external calls to the ERC-20 contract instead of simply updating its internal ledger.
+This allows traders to side-step time-consuming transfers to and from \cm while still incentivizing them to ensure that submitted orders can actually be executed.
+The trade-off  is that \cm needs to update balances with external calls to the ERC20 contract instead of simply updating its internal ledger.
 
@@
 We consider an alternative design for \cm that is almost as difficult to regulate as a fully on-chain solution.
-In this design, an off-chain component is introduced to boost performance but it only interacts with the Ethereum network and never directly with traders.
+In this design, an off-chain component is introduced to boost the performance but it only interacts with the Ethereum network and never directly with traders.
 Traders still only interact with Ethereum.
@@
 \textit{Layer 2} solutions are a group of technologies that are designed and proposed to address specific drawbacks of executing transactions on \textit{Layer 1} (\ie Ethereum and other blockchains)~\cite{gudgeon2020sok}.
-These technologies focus on fast transaction throughput, reducing gas costs, and reducing transaction latency.
+These technologies focus on fast transaction throughput, reducing gas costs, or reducing transaction latency.
 When using \cm, we strive to reduce the gas cost as performance is the main bottleneck.
@@
 Arbitrum runs entire DApps inside its environment, which acts like a container and requires special bridge contacts to interact with `normal' (or Layer 1) Ethereum DApps.
-To deploy a DApp on Arbitrum, or to execute a function on an existing Arbitrum DApp, the transaction is sent to an \textit{inbox contract} on Layer 1.
-The transaction is not executed, it is only recorded (as calldata) in the inbox.
+To deploy a DApp on Arbitrum, or to execute a function on an existing Arbitrum DApp, the transaction is sent to an \textit{Inbox contract} on Layer 1.
+The transaction is not executed, it is only recorded (as calldata) in the Inbox.
 Like any other transactions on Ethereum, miners determine the order of the transactions sent to this contract.
-A set of validators (open to anyone) are watching the inbox contract for new transactions.
-Once an inbox transaction is finalized in an Ethereum block, validators will execute the transaction and asserts the result of the execution to other validators on a sidechain called ArbOS.
+A set of validators (open to anyone) are watching the Inbox contract for new transactions.
+Once an Inbox transaction is finalized in an Ethereum block, validators will execute the transaction and assert the result of the execution to other validators on a sidechain called ArbOS.
 Once the dispute challenge period is over, the new state of ArbOS will be inserted into Ethereum.
-As the inbox contract maintains all Arbitrum transactions, anyone can recompute the entire current state of the ArbOS and file a dispute if executions are not performed correctly.
+As the Inbox contract maintains all Arbitrum transactions, anyone can recompute the entire current state of the ArbOS and file a dispute if executions are not performed correctly.
 Disputes are adjudicated by Ethereum itself and require essentially constant gas costs, regardless of the size of the gas costs of the transaction being disputed
@@
 
-\textit{Testing Platforms.} Arbitrum currently operates a test network with an inbox contract on the Ethereum Kovan testnet.
+\textit{Testing Platforms.} Arbitrum currently operates a test network with an Inbox contract on the Ethereum Kovan testnet.
 To experiment with Arbitrum, we implemented a variant of \cm and ran the same experiments that we previously performed on Layer 1 (Ethereum).
-To call functions on \cm, traders can (i) send transactions directly to the inbox contract \href{https://kovan.etherscan.io/address/0x76bF1345224fE606E2aB38B8E52B83512328A9DF}, or (ii) use a relay server (called a \textit{Sequencer}) provided by the Arbitrum.
-The sequencer will group, order, and send all pending transactions together as a single Kovan transaction to the inbox (and pay the gas).
+To call functions on \cm, traders can (i) send transactions directly to the Inbox contract \href{https://kovan.etherscan.io/address/0x76bF1345224fE606E2aB38B8E52B83512328A9DF}, or (ii) use a relay server (called a \textit{Sequencer}) provided by the Arbitrum.
+The sequencer will group, order, and send all pending transactions together as a single Kovan transaction to the Inbox (and pay the gas).
 
 Recall that \cm implements an exchange between ETH and tokens.
-To use Layer 1 assets on Layer 2, Arbitrum provides two bridge contracts: one for ETH, and one for tokens compliant with ERC-20 or other standard interfaces.
+To use Layer 1 assets on Layer 2, Arbitrum provides two bridge contracts: one for ETH, and one for tokens compliant with ERC20 or other standard interfaces.
 Prior to trading, a trader uses the bridge to move their ETH to the same address on Layer 2 and then move the ETH to \cm with a Layer 2 transaction.
@@
 With Arbitrum roll-ups, 38 pairs cost only 1,632 in Layer 1 gas (a 99.9\% savings).
-This is effectively the cost of recording the \texttt{closeMarket()} function call in the inbox, which is 103 bytes of calldata.
+This is effectively the cost of recording the \texttt{closeMarket()} function call in the Inbox, which is 103 bytes of calldata.
 As the number of pairs increases, Layer 1 gas cost is constant.
@@
 Loopring 3.0 can operate near high-frequency trading as order submission is unhampered by Ethereum.
-However its  roll-up proof does not ensure that the exchange did not reorder transactions, which is particularly problematic in a continuous-time order book.
+However, its  roll-up proof does not ensure that the exchange did not reorder transactions, which is particularly problematic in a continuous-time order book.
 Traders who prioritize trade fairness might opt for a solution like our variant, while traders who want speed would vastly prefer the Loopring architecture which offers near-CEX speed while being non-custodial.
@@
 
-In the \cm variant, traders can submit transactions to the L1 inbox contract instead of directly to the \cm DApp.
-This has the same front-running profile as \cm itself; only the L1 destination address is different.
-If a sequencer is mandatory, it acts with the same privilege as an L1 Ethereum miner in ordering the transactions it receives.
-Technically, sequencers are not limited to roll-ups and could be used in the context of normal L1 DApps, but they are more apparent in the context of roll-ups.
-A sequencer could be trusted to execute transactions in the order it receives them, outsource to a fair ordering service, or (in an tacit acknowledge of the difficulties of preventing frontrunning) auction off permission to order transactions to the highest bidder.
-As shown in Table~\ref{tab:front}, a sequencer is an additional frontrunning actor but does not otherwise change the kinds of attacks that are possible.
+In our \cm variant on the Arbitrum, traders can submit transactions to the Layer 1 Inbox contract instead of directly to the \cm DApp.
+This has the same front-running profile as \cm itself; only the Layer 1 destination address is different.
+If a sequencer is mandatory, it acts with the same privilege as a Layer 1 Ethereum miner in ordering the transactions it receives.
+Technically, sequencers are not limited to roll-ups and could be used in the context of normal Layer 1 DApps, but they are more apparent in the context of roll-ups.
+A sequencer could be trusted to execute transactions in the order it receives them, outsource to a fair ordering service, or (in a tacit acknowledge of the difficulties of preventing front-running) auction off permission to order transactions to the highest bidder.
+As shown in Table~\ref{tab:front}, a sequencer is an additional front-running actor but does not otherwise change the kinds of attacks that are possible.
 
@@
 For an automated market maker, you will have to lock up a large amount of ETH into the DApp, along with your tokens.
-For rollups, you will have to host your own servers.
+For roll-ups, you will have to host your own servers.
 By contrast to all of these, with an on-chain order book, you just deploy the code alongside your token and trading is immediately supported.
@@
 It may seem paradoxical or unethical to build for regulators exactly what they worry about.
-However we agreed that it was too difficult to answer our research questions without actual implementation and experimentation.
-\cm is proof of concept code that implements only enough to understand the feasibility of on-chain trading and we release the code for reproducibility.
-However it is not production code, it is unpolished, it has no UI, and we have no intention of promoting it for adoption.
+However, we agreed that it was too difficult to answer our research questions without actual implementation and experimentation.
+\cm is a proof of concept code that implements only enough to understand the feasibility of on-chain trading and we release the code for reproducibility.
+However it is not production code, it is unpolished, it has no user interface (UI), and we have no intention of promoting it for adoption.
 Finally, by understanding the `pain points' in the design, we found we were constantly tugged toward centralized components (Ethereum alarm clock, meta-transactions, roll-up servers, \etc) which could serve as regulatory hooks even if the service is mainly on-chain.
@@
 \section{Availability} 
+\label{sec:avai}
 The Solidity source code for \cm, Truffle test files, and Arbitrum dependencies are available in a GitHub repository (non-anonymous link omitted).

### 2021-08-18 LaTeX-LNCS-2022/main.tex
lnc format + fix the table

\documentclass[envcountsect]{llncs}
\pagestyle{headings} 
\bibliographystyle{abbrv}

% = = = = = Packages = = = = = %

\input{setup/packages}
\input{setup/macros}
\input{setup/table}

%Get out of jail free:
%\usepackage[all=normal,floats=tight,paragraphs=tight]{savetrees}

% = = = = = Title = = = = = %

\begin{document}

\frontmatter
\mainmatter

\title{\Large \bf Trading On-chain: How Feasible Is Regulators' Worst-Case Scenario?}

\author{Mahsa Moosavi\inst{1} \and Jeremy Clark\inst{1}}
\institute{Concordia University, Montreal, Canada}

\maketitle

% = = = = = Abstract = = = = = %

\input{sections/abstract}

% = = = = = Main Body = = = = = %

\input{sections/paper}

% = = = = = Bibliography = = = = = %

\clearpage
\bibliography{bib/DEX}
%\nocite{*}

% = = = = = End Notes = = = = = %

\clearpage
\appendix
\input{sections/appendix.tex}

\end{document}

### 2021-08-18 LaTeX-LNCS-2022/sections/appendix.tex
lnc format + fix the table

--- 2021-05-26 LaTeX-ACM/sections/appendix.tex
@@
 % !TEX root = ../main.tex
-
-\section{Availability} 
-The Solidity source code for \cm, Truffle test files, and Arbitrum dependencies are available in a GitHub repository (non-anonymous link omitted).
-We have also deployed \cm on Ethereum's testnet Rinkeby with flattened (single file) source code of just the \cm base class and priority queue implementations.
-It is visible and can be interacted with here: \href{https://rinkeby.etherscan.io/address/0x0d91de29c531d074853a5cef7cf9dfeb9c6ec4e0}{[etherscan.io]}; while the Arbitrum variant is here: \href{https://explorer5.arbitrum.io/#/address/0x18BF65069Fdaed79f8BDB0B6EDa87d5cc46F6E28}{[explorer5.offchainlabs.com]}.
 
@@
 
-\subsection{Cleaning Up Revisited}
+\section{Cleaning Up Revisited}
 \label{app:clean}
 
-Beyond the cleaning up issues with priority queues in Section~\ref{sec:gasrefund}, \cm also uses mappings with each market.
+Beyond the cleaning up issues with priority queues in Section~\ref{sec:gasrefund}, \textblue{\cm also uses mappings with each market}.
 Traders preload their account with tokens to be traded (which comply with a common token standard called ERC20) and/or ETH.

### 2021-08-18 LaTeX-LNCS-2022/sections/paper.tex
lnc format + fix the table

--- 2021-05-27 LaTeX-ACM/sections/paper.tex
@@
 
-\paragraph[Centralized Exchanges (CEX)]{Centralized Exchanges (CEX)\eatpunct} Traditional financial markets (\eg NYSE and NASDAQ) use order-matching systems to arrange trades.
+\paragraph{Centralized Exchanges (CEX).} Traditional financial markets (\eg NYSE and NASDAQ) use order-matching systems to arrange trades.
 An exchange will list one or more assets (stocks, bonds, derivatives, or more exotic securities) to be traded with each other, given its own order book priced in a currency (\eg USD).
@@
 
-\begin{acks}
-The authors thanks the AMF (Autorité des Marchés Financiers) for supporting this research project.
+%ACK
+%The authors thanks the AMF (Autorité des Marchés Financiers) for supporting this research project.
 J.
@@
 Moosavi acknowledges support from Fonds de Recherche du Québec - Nature et Technologies (FRQNT).
-\end{acks}
+
 %GitHub repo:  \footnote{\CallMarketRepo}

### 2021-08-18 LaTeX-LNCS-2022/tables/functions.tex
lnc format + fix the table

--- 2020-09-24 LaTeX/tables/functions.tex
@@
 \begin{table}[t]
-\begin{tabular}{|l|l|}
+%\setlength{\tabcolsep}{0.7\tabcolsep}% Shrink \tabcolsep
+
+\centering
+\footnotesize
+\begin{tabular}{|>{\centering}m{2.2cm} |>{\centering\arraybackslash}m{9cm}|}%{|c|c|}
+
 \hline
@@
 % = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
-	depositToken()                           & Deposits ERC20 standard compliant tokens in \cm smart contract \\ \hline
+	depositToken()                           & Deposits ERC20 tokens in \cm smart contract \\ \hline
 % = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
@@
 % = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
-	submitBid()                              & Inserts the upcoming bid order messages inside the priority queue    \\ \hline
+	submitBid()                              & Inserts the upcoming bids inside the priority queue   \\ \hline
 % = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
-	submitAsk()                              & Inserts the upcoming ask order messages inside the priority queue    \\ \hline
+	submitAsk()                              & Inserts the upcoming asks inside the priority queue  \\ \hline
 % = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
@@
 \end{tabular}
-\caption{\footnotesize{Primary operations of \cm smart contract.}
+\caption{Primary operations of \cm smart contract.
 \label{tab:cm_functions}}

### 2021-08-25 LaTeX-LNCS-2022/sections/paper.tex
some notes/comments added

@@
 \section{Introductory Remarks}
+\textblue{Edits to be made:}
+\begin{enumerate}
+\item \textblue{Different market participants would have different preference about various markets. Which one is best for which? Jeremy in proposal: could be a chart}
+\item  \textblue{Add a subsection on latency }
+\item  \textblue{For enqueue and dequeue performance tests, justify why you picked 50 integers}
+
+\end{enumerate}
 
@@
 \textbf{Contributions.} We study fully on-chain markets through design and implementation with Solidity---a high-level programming language for Ethereum that is syntactically similar to Java.
-We choose Ethereum as a hostile environment for an order book: Ethereum is fully decentralized (hardest to regulate), network participation is open to anyone on the internet (strongest adversarial model), and, as a result, it is slow (a lower-bound benchmark).
+We choose Ethereum as a hostile environment for an order book: Ethereum is fully decentralized (hardest to regulate), network participation is open to anyone on the internet (\textblue{define the strongest adversarial model} strongest adversarial model), and, as a result, it is slow (a lower-bound benchmark).
 Generally, if an application is feasible on Ethereum, it will also be feasible and only run faster on a private (or permissioned) blockchain (\eg Hyperledger), which is a blockchain operated by authorized network nodes only, generally visible to regulators.
@@
 Our proof of concept, \cm, is an extensible base class suitable for experiments.
-\cm is designed from a security perspective: users only trust their assets to \cm's auditable code (non-custodial) and not to a third party, all operations are transparent, and we nearly eliminate the ability for adversarial network nodes to profit from front-running orders.
+\cm is designed from a security perspective: users only trust their assets to \cm's auditable code (non-custodial) and not to a third party, all operations are transparent, and we \textblue{nearly} eliminate the ability for adversarial network nodes to profit from front-running orders \textblue{Either say where \cm is vul to front-running or refer to the front-running section (would that be enough though?)}.
 In fact, we believe we are the first to design a decentralized application that actually leverages front-running (\ie miner extractable value~\cite{daian2019flash}) for the benefit of the system (see Section~\ref{sec:close}).
@@
 \includegraphics[width=0.5\textwidth]{fig/random_insertion3.png}
-\caption{Gas costs for enqueuing 50 random integers into five priority queue variants.
+\caption{\textblue{put the block gas limit in the chart} Gas costs for enqueuing 50 random integers into five priority queue variants.
 For the x-axis, a value of 9 indicates it is the 9th integer entered in the priority queue.
@@
 She buys and then immediately sells the asset and nets the price improvement as arbitrage.
-To mitigate this in \cm, all price improvements are given to the miner (using \texttt{block.coinbase.transfer()}).
+To mitigate this in \cm, all price improvements are given to the miner (using \texttt{block.coinbase.transfer()})\textblue{traders would have to pay for that}.
 This does not actively hurt traders---they always receive the same price that they quote in their orders---and it removes any incentive for miners to front-run these profits.
@@
 
-Clearing storage is important for reducing EVM bloat. The Ethereum refund model should be considered further by Ethereum developers to provide a better incentive to be less wasteful in using storage.
+Clearing storage is important for reducing EVM bloat\textblue{and who gets hurt with that?}.
+The Ethereum refund model should be considered further by Ethereum developers to provide a better incentive to be less wasteful in using storage.
 

### 2021-08-25 Code/L1-HardHat/migrations/3_deploy_CallMarket.js

@@ -1,0 +1,73 @@
+var CallMarket = artifacts.require("./CallMarket.sol"); 
+// var PQ1 = artifacts.require("./HeapDynamicArray.sol"); 
+// var PQ2 = artifacts.require("./HeapStaticArray.sol"); 
+// var PQ3 = artifacts.require("./HeapMapping.sol");
+// var PQ4 = artifacts.require("./LinkedList.sol");
+// var PQ5 = artifacts.require("./LinkedListMapping.sol");
+// var MP = artifacts.require("./Mapping.sol");
+// var PQaddress;
+
+//const BN = require('bn.js');
+
+
+// module.exports = async function(deployer) {
+//     deployer.deploy(modularExp).then(() => {
+//         return deployer.deploy(modularExp);
+//     }).then(async () => {
+//         //var modularExp = await modularExp.deployed();
+//         await modularExp.js_call();       
+//     });      
+//     };
+// module.exports = function (deployer) {
+//     deployer.deploy(PQ1);
+//     console.log("I was deployed!");
+// };
+
+// // module.exports =  function (deployer) {
+    
+// //     deployer.deploy(PQ2, 60).then (function(){
+// //         return deployer.deploy(CallMarket, PQ2.address)
+
+// //     });
+   
+// //     console.log("I was deployed!");
+
+
+
+// // };
+// module.exports = function (deployer) {
+//     deployer.deploy(PQ2);
+//     console.log("I was deployed!");
+// };
+// module.exports = function (deployer) {
+//     deployer.deploy(PQ3);
+//     console.log("I was deployed!");
+// };
+// module.exports = function (deployer) {
+//     deployer.deploy(PQ4);
+//     console.log("I was deployed!");
+// };
+
+
+
+module.exports =  function (deployer) {
+    
+    //deployer.deploy(CallMarket,{overwrite: false});
+    deployer.deploy(CallMarket);
+    console.log("CallMarket was deployed!");
+
+
+};
+
+// module.exports = function (deployer) {
+//     deployer.deploy(MP);
+//     console.log("I was deployed!");
+// };
+
+
+// module.exports = function (deployer) {
+//     deployer.deploy(Int).then(() => {
+//         deployer.deploy(CallMarket);
+//     });
+//     deployer.link(Int, User);
+// };

### 2021-08-25 Code/L1-HardHat/test/11_Orderbook_V26_test.js

@@ -1,0 +1,126 @@
+const Orderbook = artifacts.require('Orderbook_V26');
+//var assert = require('assert');
+
+
+contract('Orderbook', function(accounts) {
+
+    // it('should find out the gas limit for the latest block', async ()  =>{
+    //     const OrderbookInstance = await Orderbook.deployed(); 
+        
+    //     var block = web3.eth.getBlock();
+    //     console.log("gasLimit: " + block.gasLimit);
+        
+        
+
+    // });
+    
+   //*******************Test 1*************************
+    it('should submit 1 Buys from accounst[1]', async ()  =>{
+        const OrderbookInstance = await Orderbook.deployed(); 
+        var receipt = null;
+        var array = [];
+   
+        accounts = await web3.eth.getAccounts();
+        for(let j = 1; j <= 375 ; j++){
+
+            receipt = await OrderbookInstance.submitBid (j, {from: accounts[1]});
+
+            const gasUsed = receipt.receipt.gasUsed;
+            array.push(gasUsed);
+            console.log(`GasUsed for a submibid tx is: ${receipt.receipt.gasUsed}`);
+
+        } 
+        console.log(array.length,'bids has been succsessfully submitted');
+        console.log('Gas used for submitting the', array.length,'th bid is:');
+        console.log(`${receipt.receipt.gasUsed}`);
+        
+
+    });
+    //*******************Test temp*************************
+    // it ('is just a test to check the head of the buylist', async ()  =>{
+    //     const OrderbookInstance = await Orderbook.deployed(); 
+        
+
+    //     await  OrderbookInstance.changetest();
+    //     result = await OrderbookInstance.test();
+    //     console.log('********************************************');
+    //     console.log("the price of the buylist head is", result.toNumber());
+
+    // });
+
+    //*******************Test 2*************************
+
+    // it('should should pass if the Buylist contains the data ', async ()  =>{
+        
+    //     const OrderbookInstance = await Orderbook.deployed(); 
+    //     const result = await  OrderbookInstance.BuyListContains.call(35); 
+    //     assert.equal( result, true, "The data does not exist in the list"); //actual,expected
+    // });
+     
+    //*******************Test 3*************************
+    it('should submit 1 asks from accounst[0]', async() => {
+        const OrderbookInstance = await Orderbook.deployed(); 
+        var receipt = null;
+        var array = [];
+        
+
+        accounts = await web3.eth.getAccounts();
+        for(let j = 375; j >= 1  ; j--){
[…]

### 2021-08-25 Code/L1-HardHat/test/14_Orderbook_V28_test.js

@@ -1,0 +1,59 @@
+const Orderbook = artifacts.require('Orderbook_V28');
+
+
+contract('Orderbook', function(accounts) {
+    
+   //*******************Test 1*************************
+    it('should insert asks', async ()  =>{
+        const OrderbookInstance = await Orderbook.deployed(); 
+        
+        var receipt = null;
+        var array = [];
+        
+
+        accounts = await web3.eth.getAccounts();
+        for(let j = 20; j >= 1  ; j--){
+            receipt = await OrderbookInstance.SellListInsert (j, {from: accounts[0]});
+        
+            const gasUsed = receipt.receipt.gasUsed;
+            array.push(gasUsed);
+            console.log(`GasUsed for a submitask tx is: ${receipt.receipt.gasUsed}`);
+
+        } 
+
+        console.log(array.length,'asks has been succsessfully submitted');
+        console.log('Gas used for submitting the', array.length,'th ask is:');
+        console.log(`${receipt.receipt.gasUsed}`);
+        console.log('********************************************');
+        
+    });
+    //*******************Test 2*************************
+    it('should insert Buys', async ()  =>{
+        const OrderbookInstance = await Orderbook.deployed(); 
+        
+        var receipt = null;
+        var array = [];
+        
+
+        accounts = await web3.eth.getAccounts();
+        for(let j = 1; j <= 20  ; j++){
+            receipt = await OrderbookInstance.BuyListInsert (j, {from: accounts[1]});
+        
+            const gasUsed = receipt.receipt.gasUsed;
+            array.push(gasUsed);
+            console.log(`GasUsed for a submitbid tx is: ${receipt.receipt.gasUsed}`);
+
+        } 
+
+        console.log(array.length,'bids has been succsessfully submitted');
+        console.log('Gas used for submitting the', array.length,'th ask is:');
+        console.log(`${receipt.receipt.gasUsed}`);
+        console.log('********************************************');
+        
+        await OrderbookInstance.testfunction();
+        const test = await OrderbookInstance.buytest();
+        console.log('test is', test.toNumber());
+    });
+    
+
+});

### 2021-08-25 Code/L1-HardHat/test/16_Call_Market_test.js

@@ -1,0 +1,170 @@
+const CallMarket = artifacts.require('Call_Market.sol');
+const DappToken = artifacts.require('DappToken');
+var CallMarketaddress;
+var tokenaddress;
+var accounts;
+
+
+
+contract('CallMarket', function(accounts) {
+    it('should store the address of the CallMarket into the var CallMarketaddress', async() => {
+        const CallMarketInstance = await CallMarket.deployed(); 
+        CallMarketaddress = CallMarketInstance.address;
+        console.log('The address of the CallMarket contract is:', CallMarketInstance.address);
+        
+    });
+
+});
+
+contract('DappToken', function(accounts) {
+
+    it('should approve transfer of 100 tokens from account[0] to the CallMarket contract ', async ()=> {
+        const DappTokenInstance = await DappToken.deployed();
+        tokenaddress = DappTokenInstance.address;
+        const receipt = await DappTokenInstance.approve (CallMarketaddress, 15000, {from: accounts[0]});
+        const result = await DappTokenInstance.allowance(accounts[0],CallMarketaddress);
+        console.log('Account[0] allowes the CallMarket contract to spend:',result.toNumber());
+        console.log('********************************************');
+        //const gasUsed = receipt.receipt.gasUsed;
+        //console.log(`GasUsed for approving: ${receipt.receipt.gasUsed}`);
+    
+    });   
+
+});
+
+//*******************New test Block for the already deployed CallMarket contract *************************
+describe('CallMarket', function(accounts) {
+    this.timeout(0);
+   
+    //*******************Test 1*************************
+    it('should deposit tokens from accounst[0] to the CallMarket contract', async() => {
+        
+        const CallMarketInstance = await CallMarket.deployed(); 
+
+        accounts = await web3.eth.getAccounts();
+       
+        const receipt = await CallMarketInstance.DepositToken (tokenaddress, 15000, {from: accounts[0]});
+        
+        const totalbalance = await CallMarketInstance.TotalTokenBalance(accounts[0]);
+        
+        console.log('The token balance of account[0] is:', totalbalance.toNumber());
+        console.log('********************************************');
+        //const gasUsed = receipt.receipt.gasUsed;
+        //console.log(`GasUsed for depositting 100 tokens: ${receipt.receipt.gasUsed}`);
+
+    });
+
+    //*******************Test 2*************************
+    it('should deposit Ethers from accounts[1] to the CallMarket contract', async() => {
+        
[…]

### 2021-08-25 Code/L1-HardHat/test/2_OrderBook_V22_test.js

@@ -1,0 +1,281 @@
+const DappToken = artifacts.require('DappToken');
+const Orderbook = artifacts.require('Orderbook_V22');
+var Orderbookaddress;
+var tokenaddress;
+var accounts;
+
+contract('Orderbook', function(accounts) {
+    it('should store the address of the orderbook into the var orderbookaddress', async() => {
+        const OrderbookInstance = await Orderbook.deployed(); 
+        Orderbookaddress = OrderbookInstance.address;
+        console.log('The address of the orderbook contract is:', OrderbookInstance.address);
+        
+    });
+
+
+
+
+});
+
+contract('DappToken', function(accounts) {
+
+    it('should approve transfer of 100 tokens from account[0] to the orderbook contract ', async ()=> {
+        const DappTokenInstance = await DappToken.deployed();
+        tokenaddress = DappTokenInstance.address;
+        const receipt = await DappTokenInstance.approve (Orderbookaddress, 100000, {from: accounts[0]});
+        const result = await DappTokenInstance.allowance(accounts[0],Orderbookaddress);
+        console.log('Account[0] allowes the orderbook contract to spend:',result.toNumber());
+        
+        console.log('********************************************');
+        const gasUsed = receipt.receipt.gasUsed;
+        console.log(`GasUsed for approving: ${receipt.receipt.gasUsed}`);
+    
+    });   
+
+});
+
+
+//*******************New test Block for the already deployed orderbook contract *************************
+describe('Orderbook', function(accounts) {
+    this.timeout(0);
+    
+    //*******************Test 1*************************
+    it('should deposit 100 tokens from accounst[0] to the orderbook contract', async() => {
+        
+        const OrderbookInstance = await Orderbook.deployed(); 
+
+        accounts = await web3.eth.getAccounts();
+       
+        const receipt = await OrderbookInstance.DepositToken (tokenaddress, 100000, {from: accounts[0]});
+        
+        const totalbalance = await OrderbookInstance.TokenBalance(accounts[0], tokenaddress);
+        //const availablebalance = await OrderbookInstance.AvailableTokenBalance(accounts[0], tokenaddress);
+        
+        console.log('The total token balance of account[0] is:', totalbalance.toNumber());
+        console.log('********************************************');
+        //console.log('The available token balance of account[0] is:', availablebalance.toNumber());
+        //console.log('********************************************');
+        const gasUsed = receipt.receipt.gasUsed;
[…]

### 2021-08-26 LaTeX-LNCS-2022/sections/paper.tex
cutting the text down to 23 pages

@@
 \section{Introductory Remarks}
-\textblue{Edits to be made:}
-\begin{enumerate}
-\item \textblue{Different market participants would have different preference about various markets. Which one is best for which? Jeremy in proposal: could be a chart}
-\item  \textblue{Add a subsection on latency }
-\item  \textblue{For enqueue and dequeue performance tests, justify why you picked 50 integers}
 
-\end{enumerate}
+% EDITS TO BE MADE:
+% 1- Different market participants would have different preference about various markets. Which one is best for which? Jeremy in proposal: could be a chart
+% 2- Add a subsection on latency
+% 3- For enqueue and dequeue performance tests, justify why you picked 50 integers
 
@@
 
-\begin{figure}[t]
-\centering
-\includegraphics[width=0.5\textwidth]{fig/random_insertion3.png}
-\caption{\textblue{put the block gas limit in the chart} Gas costs for enqueuing 50 random integers into five priority queue variants.
+%\begin{figure}[t]
+%\centering
+%\includegraphics[width=0.5\textwidth]{fig/random_insertion3.png}
+%\caption{\textblue{put the block gas limit in the chart} Gas costs for enqueuing 50 random integers into five priority queue variants.
 For the x-axis, a value of 9 indicates it is the 9th integer entered in the priority queue.
@@
 \label{fig:random_insertion}}
-\end{figure}
+%\end{figure}
 
@@
 
-\input{tables/dequeue.tex}
+%\input{tables/dequeue.tex}
+
+\textblue{put the block gas limit in the chart}
+
+\begin{figure}
+\begin{floatrow}
+\ffigbox{%
+\includegraphics[width=6cm]{fig/2.png}%
+}{%
+  \caption{\scriptsize{Gas costs for enqueuing 50 random integers into five priority queue variants.
+For the x-axis, a value of 9 indicates it is the 9th integer entered in the priority queue.
+The y-axis is the cost of enqueuing in gas}.
+\label{fig:random_insertion}}%
+
+}
+\capbtabbox{%
+\scriptsize
+\begin{tabular}{|>{\centering}m{2cm} |>{\centering}m{1.15cm} |>{\centering}m{1.15cm} |>{\centering\arraybackslash}m{0.2cm}|}%{|c|c|c|c|}
+
+\multicolumn{1}{c}{} & \headrowsidebyside{\scriptsize{\shortstack{Gas Costs \\\textit{(gwei)}}}} & \headrowsidebyside{\scriptsize{\shortstack{Refund \textit{(gwei)} \\\textblue{(Manual)}}}} & \headrowsidebyside{\scriptsize{Full Refund?}} \\ \hline
+
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
+\shortstack{Heap with\\Dynamic Array}        	& 2,518,131          & 750,000     &\full                  \\ \hline
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
+\shortstack{Heap with\\ Static Array}          	& 1,385,307                             & 750,000      &\full                \\ \hline
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
+\shortstack{Heap with\\ Mapping}  		& 2,781,684                            & 1,500,000    &\full                 \\ \hline
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
+Linked List                     		& 557,085               	           & 1,200,000      &\full                \\ \hline
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
+\shortstack{Linked List with\\ Mapping}       	& 731,514              	     	  &  3,765,000      &\full                 \\ \hline
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
+
+\end{tabular}
+}{%
+ \caption{\scriptsize{The gas metrics associated with dequeuing 50 integers from five priority queue variants.}
+\label{tab:PQUnitTests}}%
+}
+\end{floatrow}
+\end{figure}
+
+%\vspace{-3em}
 
@@
 
-\input{tables/frontrunning.tex}
+%\input{tables/frontrunning.tex}
+\input{tables/frontrunning2.tex}
 
@@
 We have also deployed \cm on Ethereum's testnet Rinkeby with flattened (single file) source code of just the \cm base class and priority queue implementations.
-It is visible and can be interacted with here: \href{https://rinkeby.etherscan.io/address/0x0d91de29c531d074853a5cef7cf9dfeb9c6ec4e0}{[etherscan.io]}; while the Arbitrum variant is here: \href{https://explorer5.arbitrum.io/#/address/0x18BF65069Fdaed79f8BDB0B6EDa87d5cc46F6E28}{[explorer5.offchainlabs.com]}.
+It is visible and can be interacted with here: \href{https://rinkeby.etherscan.io/address/0x0d91de29c531d074853a5cef7cf9dfeb9c6ec4e0}{[etherscan.io]}; while the Arbitrum variant is here\textblue{the link is broken @Mahsa dont forget to re-run the test}: \href{https://explorer5.arbitrum.io/#/address/0x18BF65069Fdaed79f8BDB0B6EDa87d5cc46F6E28}{[explorer5.offchainlabs.com]}.
 

### 2021-08-26 LaTeX-LNCS-2022/tables/frontrunning2.tex
cutting the text down to 23 pages

% !TEX root = ../main.tex

\begin{table*}[t]

\centering
\tiny
%\resizebox{1.7\columnwidth}{!}{

\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|c|}

\multicolumn{1}{c}{} &
\multicolumn{1}{c}{} &
\multicolumn{1}{c}{} &
\headrowfrontTwo{\shortstack{Centralized Continuous\\ Market (Coinbase)}} &
\headrowfrontTwo{\shortstack{Partially Off-chain Continuous\\ Market (EtherDelta)}} & 
\headrowfrontTwo{\shortstack{Partially Off-chain Continuous \\Market w/ Roll-up (Loopring)}} & 
\headrowfrontTwo{\shortstack{On-chain Continuous \\Market (OasisDex)}}  &
\headrowfrontTwo{\shortstack{On-chain Dark \\Continuous Market (TEX)}} &
\headrowfrontTwo{\shortstack{On-chain Automated \\Market Maker (Uniswap)}}  & 
\headrowfrontTwo{\shortstack{On-chain Call Market \\w/ Price Improvement}} &
\headrowfrontTwo{\shortstack{On-chain Call Market (\cm)}}  & 
\headrowfrontTwo{\shortstack{On-chain Call Market  \\w/ Roll-up (\cm variant)}}  &
\headrowfrontTwo{\shortstack{On-chain Dark \\Call Market (Galal \etal)}}
\\

%\hhline{-----------}
\hline
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = == = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %								 											
%\parbox[t]{1mm}{\multirow{10}{*}{\rotatebox[origin=c]{90}{Attack Example}}} 	&&&&&&&&&&&														\\ \hline

% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = == = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %

%	     
%	     & \multicolumn{2}{c?{1mm}}{Classification}             																											&\multicolumn{1}{c|}{LOB}		&\multicolumn{1}{c|}{LOB}		&\multicolumn{1}{c|}{LOB}		&\multicolumn{1}{c|}{LOB}		&\multicolumn{1}{c|}{LOB}		&\multicolumn{1}{c|}{AMM}		&\multicolumn{1}{c|}{CM}		&\multicolumn{1}{c|}{CM}	&\multicolumn{1}{c|}{CM}								  										&\multicolumn{1}{c|}{CM}	 \\ \hhline{~------------}

% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = == = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %

\multicolumn{3}{|c?{1mm}}{\makecell{Who is Mallory? \\ \underline{A}uthority,  \underline{T}rader, \underline{M}iner, \underline{S}equencer	}}   	&A&A,T,M&A,T,M,S&T,M&T,M&T,M&T,M&T,M&T,M,S	&T,M	 \\ \cmidrule[1mm]{1-13}

% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = == = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %

\multirow{17}{*}{\rotatebox[origin=c]{90}{\textbf{Attack Example}}}		&\multicolumn{1}{c|}{\makecell{Mallory (\textit{maker}) squeezes in a\\ transaction before Alice's  (\textit{taker})  order}}  						&\multicolumn{1}{c?{1mm}}{Ins.}		&\empt	&\empt &\empt &\empt &\full &\empt &\full &\full  &\full &\full		\\ \hhline{~------------}					 					
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = == = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %

&\multicolumn{1}{c|}{\makecell{Mallory (\textit{taker}) squeezes in a \\transaction before Bob's (\textit{taker 2})}   }	  								&\multicolumn{1}{c?{1mm}}{  Disp.}				&\empt &\empt &\empt &\empt &\full &\empt &\full &\full &\full	&\full		\\ \hhline{~------------}	
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = == = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %

&\multicolumn{1}{c|}{\makecell{Mallory (\textit{maker 1}) suppresses a better \\ incoming order from Alice (\textit{maker 2}) \\ until Mallory's order is executed}}																&\multicolumn{1}{c?{1mm}}{Supp.} 				&\empt &\empt &\empt &\full &\full &\full &\prt &\prt &\prt &\prt	\\ 	\hhline{~------------}				 											
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = == = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %

&\multicolumn{1}{c|}{\makecell{A hybrid attack based on the above \\ (\eg sandwich attacks, scalping)}}																		&\multicolumn{1}{c?{1mm}}{I/S/D}																		&\empt &\empt &\empt &\empt &\full &\empt &\empt &\full &\full	&\full												\\ 	\hhline{~------------}
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = == = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %

&\multicolumn{1}{c|}{\makecell{Mallory suspends the market \\for a period of time}}																										&\multicolumn{1}{c?{1mm}}{Supp.}    				&\empt  &\empt  &\empt  &\prt  &\prt  &\prt  &\prt  & \prt &\prt &\prt 	\\ 	\hhline{~------------}
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = == = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %

&\multicolumn{1}{c|}{\makecell{Spoofing: Mallory (\textit{maker}) puts an \\ order as bait, sees Alice (\textit{taker}) \\ tries to execute it, and cancels it first}}													&\multicolumn{1}{c?{1mm}}{S\&D} 				&\empt &\empt &\empt &\empt &\full &\empt &\full &\full &\full &\full \\ 	\hhline{~------------}
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = == = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %

&\multicolumn{1}{c|}{\makecell{Cancellation Griefing: Alice (\textit{maker}) \\ cancels an order and Mallory \\ (\textit{taker}) fulfills it first}}													&\multicolumn{1}{c?{1mm}}{Disp.} 							&\empt &\empt &\empt &\empt &\full &\empt &\full & \full &\full	&\full \\ 	\hline
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = == = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %

\end{tabular}

%} %end resizebox

\caption{\footnotesize{An evaluation of front-running attacks (rows) for different types of order books (columns). Front-running attacks are in three categories: \underline{Ins}ertion, \underline{disp}lacement, and \underline{supp}ression. A full dot (\tinyfull) means the front-running attack is mitigated or not applicable to the order book type, a partial mitigation (\tinyprt) is awarded when the front-running attack is possible but expensive, and we give no award (\tinyempt) if the attack is feasible}. 
\label{tab:front}}
\end{table*}

### 2021-08-30 LaTeX-LNCS-2022/sections/paper.tex
Entire "trade execution system" section rewritten

@@
 
-\subsection{Trade Execution Systems}
+\subsection{Trade Execution Systems} %NEW:@Mahsa
 
@@
 Order-driven markets can be \emph{continuous}, with buyers/sellers at any time adding orders to the order book (\emph{makers}) or executing against an existing order (\emph{takers}); or they can be \emph{called}, where all traders submit orders within a window of time and orders are matched in a batch (like an auction).
+Table~\ref{tab:exchanges} presents three prominent order-driven exchanges and provides a brief comparison between them.
+We describe each below:
 
-\subsection{Trading Blockchain-Based Assets}
+\input{tables/tradeexecutions.tex}
+\begin{itemize}
+
+\item\textbf{Centralized Exchanges (CEX).} Here, a firm (\eg Binance, Bitfinex, \etc) operates the platform as a trusted third party in every aspect: custodianship over assets/currency being traded, exchanging assets fairly, offering the best possible price execution.
+
+\item\textbf{Decentralized Exchanges (DEX).} These are hybrid order-driven exchanges with some trusted off-chain components and some on-chain functionalities.
+DEXes were first envisioned as operating fully on-chain, but performance limitations drove developers to move key components, such as the order matching system, off-chain to a centralized database.
+A landscape of DEX designs exist (\eg EtherDelta, 0x, IDEX, \etc): many avoid taking custodianship of assets off-chain, and virtually all (for order-driven markets) operate the order book itself off-chain (a regulatory hook).
+
+\item\textbf{Fully On-chain Exchanges.} Order matching can be performed `on-chain' by deploying the order-matching system either on a dedicated blockchain or inside a decentralized application (DApp).
+In this model, traders entrust their assets to an autonomously operating DApp with known source code instead of a third party custodian that can abscond with or lose the funds.
+The trading rules will operate as coded, clearing and settling can be guaranteed, and order submission is handled by the blockchain---a reasonably fair and transparent system (but see front-running; Section~\ref{sec:front}).
+Finally, anyone can create an on-chain order book for any asset (on the same chain) at any time.
+\end{itemize}
+Fully on-chain order-driven exchanges have a superior threat model and were experimented with in the early days of Ethereum, but they have been largely abandoned for performance reasons (see Table~\ref{tab:exchanges}).
+In this paper, we focus on benchmarking an order book for the public blockchain Ethereum.
+Specifically, we answer the following research questions:
+\begin{enumerate}
+\item Is secure trading (\ie resistant to front-running and price manipulation) even feasible as a fully ‘on-chain’ service on a public blockchain?
+\item What is its performance benchmark?
+\item What is the performance impact of novel techniques (\eg ‘rollups’) in closing the performance gap?
+
+\end{enumerate}
 
@@
 
-\paragraph{Centralized Exchanges (CEX).} Traditional financial markets (\eg NYSE and NASDAQ) use order-matching systems to arrange trades.
+%\subsection{Trade Execution Systems}
+%
+%There are three main approaches to arranging a trade~\cite{Har03}.
+In a \emph{quote-driven} market, a dealer uses its own inventory to offer a price for buying or selling an asset.
+In a \emph{brokered exchange}, a broker finds a buyer and seller.
+In an \emph{order-driven} market, offers to buy (\emph{bids}) and sell (\emph{offers}/\emph{asks}) from many traders are placed as orders in an order book.
+Order-driven markets can be \emph{continuous}, with buyers/sellers at any time adding orders to the order book (\emph{makers}) or executing against an existing order (\emph{takers}); or they can be \emph{called}, where all traders submit orders within a window of time and orders are matched in a batch (like an auction).
+%
+%\subsection{Trading Blockchain-Based Assets}
+%
+%%\input{tables/eval.tex}
+%
+%\paragraph{Centralized Exchanges (CEX).} Traditional financial markets (\eg NYSE and NASDAQ) use order-matching systems to arrange trades.
 An exchange will list one or more assets (stocks, bonds, derivatives, or more exotic securities) to be traded with each other, given its own order book priced in a currency (\eg USD).
@@
 Today, CEXes are often regulated as other money service businesses---this provides some ability for the government to conduct financial tracking but does little to provide consumer protection against fraud.
-
-\paragraph{On-chain Order Books.} For trades between two blockchain-based assets (\eg a digital asset priced in a cryptocurrency, stablecoin, or second digital asset), order matching can be performed `on-chain' by deploying the order-matching system either on a dedicated blockchain or inside a decentralized application (DApp).
+%
+%\paragraph{On-chain Order Books.} For trades between two blockchain-based assets (\eg a digital asset priced in a cryptocurrency, stablecoin, or second digital asset), order matching can be performed `on-chain' by deploying the order-matching system either on a dedicated blockchain or inside a decentralized application (DApp).
 In this model, traders entrust their assets to an autonomously operating DApp with known source code instead of a third party custodian that can abscond with or lose the funds.
@@
 Since it is an open system, there is no obvious regulatory hook (beyond the blockchain itself).
-
-In this paper, we focus on benchmarking an order book for the public blockchain Ethereum.
+%
+%In this paper, we focus on benchmarking an order book for the public blockchain Ethereum.
 Ethereum is widely used and we stand to learn the most from working in a performance-hostile environment.
@@
 Trading systems on permissioned blockchains (\eg NASDAQ Linq, tZero) can also improve execution time and throughput, but they reduce user transparency and trust if unregulated.
-
-\paragraph{On-chain Dealers.} An advantage of on-chain trading is that other smart contracts, not just human users, can initiate trades, enabling broader decentralized finance (DeFi) applications.
+%
+%\paragraph{On-chain Dealers.} An advantage of on-chain trading is that other smart contracts, not just human users, can initiate trades, enabling broader decentralized finance (DeFi) applications.
 This has fuelled a resurgence in on-chain exchange but through a quote-driven design rather than an order-driven one.
@@
 We leave it as an assertion that with equal liquidity, order books have more favorable price dynamics for traders.
-
-\paragraph{Hybrid Designs.} Before on-chain dealers became prominent in the late 2010s, the most popular design was hybrid order-driven exchanges with some trusted off-chain components and some on-chain functionalities.
+%
+%\paragraph{Hybrid Designs.} Before on-chain dealers became prominent in the late 2010s, the most popular design was hybrid order-driven exchanges with some trusted off-chain components and some on-chain functionalities.
 Such decentralized exchanges (DEXes) were envisioned as operating fully on-chain, but performance limitations drove developers to move key components, such as the order matching system, off-chain to a centralized database.

### 2021-08-30 LaTeX-LNCS-2022/tables/tradeexecutions.tex
Entire "trade execution system" section rewritten

% !TEX root = ../main.tex

% = = = = = = = = = = = =Comparison Trade Executions = = =  = = = = = = = = = = = %
\begin{table}[t]
%\setlength{\tabcolsep}{1pt}% Shrink \tabcolsep
\centering
\scriptsize
%\begin{tabular}{|c|c|c|c|c|}
\begin{tabular}{|>{\centering}m{4.5cm} |>{\centering}m{1cm} |>{\centering}m{1cm} |>{\centering}m{1cm} |>{\centering\arraybackslash}m{1cm}|}

\multicolumn{1}{c}{\scriptsize{Trade Execution System}}  & \headrowcleaning{\scriptsize {High Performance}} & \headrowcleaning{\scriptsize {High Security}} & \headrowcleaning{\scriptsize {Easy to Regulate}} & \headrowcleaning{\scriptsize {Easy to Realize}}\\ \hline
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
	\textbf{Centralized Exchange (CEX)}       		 & \footnotesize\Smiley     	&\footnotesize\Sadey 		&\footnotesize\Smiley 		& \footnotesize\Smiley                 \\ \hline
	\textbf{Decentralized Exchange (DEX)}		 &\footnotesize\Smiley 		&\footnotesize\Sadey 		&\footnotesize\Smiley 		&\footnotesize\Smiley		\\ \hline
	\textbf{Fully On-chain Exchange}			 &\footnotesize\Sadey 		&\footnotesize\Smiley 		&\footnotesize\Sadey 		&\footnotesize\Sadey					\\ \hline
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
\end{tabular}
\caption{\footnotesize{}.
\label{tab:exchanges}}
\end{table}
% = = = = = = = = = = = = = = = = = = = = =  = = = = = = = = = = =  = = = = = = = = = == = = =  = =%

### 2021-08-30 LaTeX-LNCS-2022/sections/abstract.tex
reorg / new sections added (down to 21 pages)

--- 2021-04-28 LaTeX-ACM/sections/abstract.tex
@@
 
-To answer these questions, we `learn by doing' and custom design an Ethereum-based call market (or batch auction) exchange, \cm, with favorable security properties.
+To answer these questions, we custom design an Ethereum-based call market (or batch auction) exchange, \cm, with favourable security properties.
 We conduct a variety of optimizations and experiments to demonstrate that this technology cannot expect to exceed a few hundred trade executions per block (\ie ~13s window of time).
-However this can be scaled dramatically with off-chain execution that is not consumer-facing.
-We also illustrate, with numerous examples throughout the paper, how blockchain deployment is full of nuances that make it quite different from developing in better understood domains (\eg cloud-based web applications).
+However, this can be scaled dramatically with off-chain execution that is not consumer-facing.
+We illustrate, with numerous examples throughout the paper, how blockchain deployment is full of nuances that make it quite different from developing in better understood domains (\eg cloud-based web applications).
+We also provide a thorough front-running evaluation between \cm and other types of markets.
 

### 2021-08-30 LaTeX-LNCS-2022/sections/appendix.tex
reorg / new sections added (down to 21 pages)

@@
 % !TEX root = ../main.tex
+
+\textbf{Ethereum's Gas Model.} Every transaction results in the participating nodes having to execute bytecode.
+This is not free.
+When a transaction is executed, each opcode in the execution path accrues a fixed, pre-specified amount of \emph{gas}.
+The function caller will pledge to pay a certain amount of Ethereum's internal currency \emph{ETH} (typically quoted in units of Gwei which is one billionth of an ETH) per unit of gas, and miners are free to choose to execute that transaction or ignore it.
+The function caller is charged for exactly what the transaction costs to execute, and they cap the maximum they are willing to be charged (\textit{gas limit}).
+If the cap is too low to complete the execution, the miner keeps the Gwei and \emph{reverts} the state of the EVM (as if the function never ran).
+
+A miner can include as many transactions (typically preferring transactions that bid the highest for gas) that can fit under a pre-specified \textit{block gas limit}, which is algorithmically adjusted for every block.
+As of the time of writing, the limit is approximately 11M gas.
+Essentially, our main research question is how many on-chain trades can be executed without exceeding that limit.
+Later, we also discuss several bytecode operations (\emph{opcodes}) that refund gas (\ie cost negative gas), which we heavily utilize in our optimizations.
+
+\section{Gas Refunds.} In order to reconstruct the current state of Ethereum's EVM, a node must obtain a copy of every variable change since the genesis block (or a more recent `checkpoint' that is universally agreed to).
+For this reason, stored variables persist for a long time and, at first glance, it seems pointless to free up variable storage (and unclear what `free up' even means).
+Once the current state of the EVM is established by a node, it can forget about every historical variable changes and only concern itself with the variables that have non-zero value (as a byte string for non-integers) in the current state (uninitialized variables in Ethereum have the value 0 by default).
+Therefore, freeing up variables will reduce the amount of state Ethereum nodes need to maintain going forward.
+
+For this reason, some EVM operations cost a negative amount of gas.
+That is, the gas is refunded to the sender at the end of the transaction, however (1) the refund is capped at 50\% of the total gas cost of the transaction, and (2) the block gas limit applies to the pre-refunded amount (\ie a transaction receiving a full refund can cost up to 5.5M gas with an 11M limit).
+Negative gas operations include:
+
+\begin{itemize}
+
+\item \texttt{SELFDESTRUCT}.
+This operation destroys the contract that calls it and refunds its balance (if any) to a designated receiver address.
+The  \texttt{SELFDESTRUCT} operation does not remove the initial byte code of the contract from the chain.
+It always refunds 24,000 gas.
+For example, if contract A stores a single non-zero integer and contract B stores 100 non-zero integers, the \texttt{SELFDESTRUCT} refund for both is the same (24,000 gas).
+
+\item \texttt{SSTORE}.
+This operation loads a storage slot with a value.
+Using \texttt{SSTORE} to load a zero into a storage slot means the nodes can start ignoring it (recall that all variables, even if uninitialized, have zero by default).
+Doing this refunds 15,000 gas per slot.
+
+\end{itemize}
 

### 2021-08-30 LaTeX-LNCS-2022/sections/paper.tex
reorg / new sections added (down to 21 pages)

@@
 \textbf{Contributions.} We study fully on-chain markets through design and implementation with Solidity---a high-level programming language for Ethereum that is syntactically similar to Java.
-We choose Ethereum as a hostile environment for an order book: Ethereum is fully decentralized (hardest to regulate), network participation is open to anyone on the internet (\textblue{define the strongest adversarial model} strongest adversarial model), and, as a result, it is slow (a lower-bound benchmark).
+We choose Ethereum as a hostile environment for an order book: Ethereum is fully decentralized (hardest to regulate), network participation is open to anyone on the internet (strongest adversarial model), and, as a result, it is slow (a lower-bound benchmark).
 Generally, if an application is feasible on Ethereum, it will also be feasible and only run faster on a private (or permissioned) blockchain (\eg Hyperledger), which is a blockchain operated by authorized network nodes only, generally visible to regulators.
@@
 Our proof of concept, \cm, is an extensible base class suitable for experiments.
-\cm is designed from a security perspective: users only trust their assets to \cm's auditable code (non-custodial) and not to a third party, all operations are transparent, and we \textblue{nearly} eliminate the ability for adversarial network nodes to profit from front-running orders \textblue{Either say where \cm is vul to front-running or refer to the front-running section (would that be enough though?)}.
+\cm is designed from a security perspective: users only trust their assets to \cm's auditable code (non-custodial) and not to a third party, all operations are transparent, and we nearly eliminate the ability for adversarial network nodes to profit from front-running orders (see Section~\ref{sec:front} for in-depth front-running analysis).
 In fact, we believe we are the first to design a decentralized application that actually leverages front-running (\ie miner extractable value~\cite{daian2019flash}) for the benefit of the system (see Section~\ref{sec:close}).
@@
 
-\textbf{Ethereum's Gas Model.} Every transaction results in the participating nodes having to execute bytecode.
+%\textbf{Ethereum's Gas Model.} Every transaction results in the participating nodes having to execute bytecode.
 This is not free.
@@
 If the cap is too low to complete the execution, the miner keeps the Gwei and \emph{reverts} the state of the EVM (as if the function never ran).
-
-A miner can include as many transactions (typically preferring transactions that bid the highest for gas) that can fit under a pre-specified \textit{block gas limit}, which is algorithmically adjusted for every block.
+%
+%A miner can include as many transactions (typically preferring transactions that bid the highest for gas) that can fit under a pre-specified \textit{block gas limit}, which is algorithmically adjusted for every block.
 As of the time of writing, the limit is approximately 11M gas.
@@
 
-There are three main approaches to arranging a trade~\cite{Har03}.
-In a \emph{quote-driven} market, a dealer uses its own inventory to offer a price for buying or selling an asset.
-In a \emph{brokered exchange}, a broker finds a buyer and seller.
-In an \emph{order-driven} market, offers to buy (\emph{bids}) and sell (\emph{offers}/\emph{asks}) from many traders are placed as orders in an order book.
-Order-driven markets can be \emph{continuous}, with buyers/sellers at any time adding orders to the order book (\emph{makers}) or executing against an existing order (\emph{takers}); or they can be \emph{called}, where all traders submit orders within a window of time and orders are matched in a batch (like an auction).
-Table~\ref{tab:exchanges} presents three prominent order-driven exchanges and provides a brief comparison between them.
-We describe each below:
+\emph{Order-driven} markets are a  group of trade execution systems where offers to buy (\emph{bids}) and sell (\emph{offers}/\emph{asks}) from many traders are placed as orders in an order book and executed based on matching rules enforced by the market.
+These markets can be \emph{continuous}, with buyers/sellers at any time adding orders to the order book (\emph{makers}) or executing against an existing order (\emph{takers}); or they can be \emph{called}, where all traders submit orders within a window of time and orders are matched in a batch (like an auction).
+Table~\ref{tab:exchanges} presents three types of order-driven exchanges:
 
@@
 \end{itemize}
-Fully on-chain order-driven exchanges have a superior threat model and were experimented with in the early days of Ethereum, but they have been largely abandoned for performance reasons (see Table~\ref{tab:exchanges}).
+Despite having a superior threat model, fully on-chain order-driven exchanges are slow, difficult to regulate and implement (see Table~\ref{tab:exchanges}).
 In this paper, we focus on benchmarking an order book for the public blockchain Ethereum.
-Specifically, we answer the following research questions:
-\begin{enumerate}
-\item Is secure trading (\ie resistant to front-running and price manipulation) even feasible as a fully ‘on-chain’ service on a public blockchain?
-\item What is its performance benchmark?
-\item What is the performance impact of novel techniques (\eg ‘rollups’) in closing the performance gap?
-
-\end{enumerate}
 
@@
 
-\section{Priority Queues}\label{sec:pq}
+\section{Call Market Design}
+
+\input{tables/functions.tex}
+
+Our proof of concept, \cm, is a call market that will open for a specified period of time during which it will accept a capped number of orders (\eg 100 orders---parameterized so that all orders can be processed), and these orders are added to a priority queue (discussed in Section~\ref{sec:pq} ).
+Our vision is the market would be open for a very short period of time, close, and then reopen immediately (\eg every other block).
+\cm is open source and written in 336 lines (SLOC) of Solidity plus the priority queue (\eg a heap with dynamic array is 282 SLOC)\footnote{Github: Link removed for anonymity.}.
+We tested it with the Mocha testing framework using Truffle on Ganache-CLI to obtain our performance metrics.
+Once deployed, the bytecode of \cm is 10,812 bytes plus the constructor code (6,400 bytes) which is not stored.
+We cross-checked for vulnerabilities with \textit{Slither}\footnote{https://github.com/crytic/slither} and \textit{SmartCheck}\footnote{https://tool.smartdec.net} (it only fails some `informational' warnings that are intentional design choices---\eg a costly loop).
+Table~\ref{tab:cm_functions} summarizes \cm's primary operations.
+Also, \cm is an extensible base class that is still functional without any extensions. Figure\textblue{mindmap} represents a design  landscape and extensions.
+
+%is an extensible base class that is still functional without any extensions. 
+%
+%Later in Section~\ref{sec:close}, we discuss the options for who closes/reopens the market.
+We keep the design simple by not allowing cancellations which require a second transaction and front-running attacks apply to cancellation orders~\cite{eskandari2019sok}.
+As markets are relatively short-lived, orders simply expire when the market call period ends.
+%
+%Another simplifying assumption is to implement a \textit{collateralized} call market.
+We assume all trades are between ETH and an ERC20 token, all orders are pre-funded in the contract with ETH (for bids) and tokens (for asks), and once ETH or tokens are committed to an order, they cannot be withdrawn until the market closes.
+This ensures all executed orders clear and settle (\ie no defaults on payment or delivery).
+
+% Volume of 1
+% Ties?
+
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
+
+\subsection{Priority Queues}\label{sec:pq}
 
@@
 
-\textblue{put the block gas limit in the chart}
-
 \begin{figure}
@@
 
-\multicolumn{1}{c}{} & \headrowsidebyside{\scriptsize{\shortstack{Gas Costs \\\textit{(gwei)}}}} & \headrowsidebyside{\scriptsize{\shortstack{Refund \textit{(gwei)} \\\textblue{(Manual)}}}} & \headrowsidebyside{\scriptsize{Full Refund?}} \\ \hline
+\multicolumn{1}{c}{} & \headrowsidebyside{\scriptsize{\shortstack{Gas Costs \\\textit{(gwei)}}}} & \headrowsidebyside{\scriptsize{Refund \textit{(gwei)} }} & \headrowsidebyside{\scriptsize{Full Refund?}} \\ \hline
 
@@
 
-\paragraph{Gas Refunds.} In order to reconstruct the current state of Ethereum's EVM, a node must obtain a copy of every variable change since the genesis block (or a more recent `checkpoint' that is universally agreed to).
-For this reason, stored variables persist for a long time and, at first glance, it seems pointless to free up variable storage (and unclear what `free up' even means).
-Once the current state of the EVM is established by a node, it can forget about every historical variable changes and only concern itself with the variables that have non-zero value (as a byte string for non-integers) in the current state (uninitialized variables in Ethereum have the value 0 by default).
-Therefore, freeing up variables will reduce the amount of state Ethereum nodes need to maintain going forward.
-
-For this reason, some EVM operations cost a negative amount of gas.
-That is, the gas is refunded to the sender at the end of the transaction, however (1) the refund is capped at 50\% of the total gas cost of the transaction, and (2) the block gas limit applies to the pre-refunded amount (\ie a transaction receiving a full refund can cost up to 5.5M gas with an 11M limit).
-Negative gas operations include:
-
-\begin{itemize}
-
-\item \texttt{SELFDESTRUCT}.
-This operation destroys the contract that calls it and refunds its balance (if any) to a designated receiver address.
-The  \texttt{SELFDESTRUCT} operation does not remove the initial byte code of the contract from the chain.
-It always refunds 24,000 gas.
-For example, if contract A stores a single non-zero integer and contract B stores 100 non-zero integers, the \texttt{SELFDESTRUCT} refund for both is the same (24,000 gas).
-
-\item \texttt{SSTORE}.
-This operation loads a storage slot with a value.
-Using \texttt{SSTORE} to load a zero into a storage slot means the nodes can start ignoring it (recall that all variables, even if uninitialized, have zero by default).
-Doing this refunds 15,000 gas per slot.
-
-\end{itemize}
-
+\paragraph{Gas Refunds.}\label{para-ref}To incentivize for deleting unused storage on the blockchain, some EVM operations cost a negative amount of gas.
+These include \texttt{SELFDESTRUCT} that destroys contract and refunds 24,000 gas, and  \texttt{SSTORE} that resets storage values from non-zero to zero and refunds 15,000 gas.
+The gas is refunded to the sender at the end of the transaction, however (1) the refund is capped at 50\% of the total gas cost of the transaction, and (2) the block gas limit applies to the pre-refunded amount (\ie a transaction receiving a full refund can cost up to 5.5M gas with an 11M limit).
 At the time of this writing, Ethereum transaction receipts only account for the \texttt{gasUsed}, which is the total amount of gas units spent during a transaction, and users are not able to obtain the value of the EVM's refund counter from inside the EVM~\cite{signer2018gas}.
 So in order to account for refunds in  Tables~\ref{tab:PQUnitTests}, we calculate them manually.
-First, we need to figure out exactly how much storage is being cleared or how many smart contracts are being destroyed, then we multiply these numbers by 24,000 or 15,000 respectively.
+First, we need to figure out exactly how much storage is being cleared or how many smart contracts are being destroyed, then we multiply these numbers by 24,000 or15,000 respectively.
 
@@
 
-\section{Call Market Design}
-
-\input{tables/functions.tex}
-
-\cm is a proof of concept code and an extensible base class that is still functional without any extensions.
-A call market will open for a specified period of time during which it will accept a capped number of orders (\eg 100 orders---parameterized so that all orders can be processed), and these orders are added to a PQ.
-Our vision (discussed below) is the market would be open for a very short period of time, close, and then reopen immediately (\eg every other block).
-Later in Section~\ref{sec:close}, we discuss the options for who closes/reopens the market.
-We keep the design simple by not allowing cancellations which require a second transaction and front-running attacks apply to cancellation orders~\cite{eskandari2019sok}.
-As markets are relatively short-lived, orders simply expire when the market call period ends.
-
-Another simplifying assumption is to implement a \textit{collateralized} call market.
-We assume all trades are between ETH and an ERC20 token, all orders are pre-funded in the contract with ETH (for bids) and tokens (for asks), and once ETH or tokens are committed to an order, they cannot be withdrawn until the market closes.
-This ensures all executed orders clear and settle (\ie no defaults on payment or delivery).
-
-% Volume of 1
-% Ties?
-
-\cm is open source and written in 336 lines (SLOC) of Solidity plus the priority queue (\eg a heap with dynamic array is 282 SLOC)(see Section~\ref{sec:avai}).
-We tested it with the Mocha testing framework using Truffle on Ganache-CLI to obtain our performance metrics.
-Once deployed, the bytecode of \cm is 10,812 bytes plus the constructor code (6,400 bytes) which is not stored.
-We cross-checked for vulnerabilities with \textit{Slither}\footnote{https://github.com/crytic/slither} and \textit{SmartCheck}\footnote{https://tool.smartdec.net} (it only fails some `informational' warnings that are intentional design choices---\eg a costly loop).
-Table~\ref{tab:cm_functions} summarizes \cm's primary operations.
-
 %============= Performance =================== %
 
- \subsection{Measurements}
+ \section{\cm Performance Measurements}
 
@@
 The main research question is how many orders can be processed in a single Ethereum transaction when closing the call market, using Ethereum today.
-As our previous experiments indicated, the choice of PQ implementation is the main influence on performance (see Table~\ref{tab:worst_case_matching}).
+As our previous experiments indicated, the choice of PQ implementation is the main influence on performance.
 We implemented a generic call market that interfaces with a generic PQ (at its own contract address) and ran experiments for each PQ implementation.
 We looked at the \textit{worst-case} for performance which is when every submitted bid and ask is marketable (\ie will require fulfillment).
+Table~\ref{tab:worst_case_matching} shows the performance results of \cm for each PQ variant.
 In the first two columns, we determine the highest number of trades that can be executed and processed in a single call to the \texttt{closeMarket()} and not exceed the current Ethereum block gas limit of 11,741,495.
@@
 
-\subsection{Front-running Evaluation} \label{sec:front}
+\section{Front-running Evaluation} \label{sec:front}
 
@@
 A second observation is that dark call markets, like Galal \etal~\cite{galalpublicly}, are no more resilient to front-running than a lit market (however confidentiality could provide resilience to predatory trading algorithms that are reactionary but do not front-run).
-
-\subsection{Cleaning Up Revisited}
-
-Recall the issue of cleaning up with priority queues in Section~\ref{sec:gasrefund}.
-Every time a market opens, \cm creates new mappings that are no longer needed after a market closes.
-Traders preload their account with tokens to be traded (which comply with a common token standard called ERC20) and/or ETH.
-\cm tracks what they are owed using a mapping called \texttt{totalBalance} and allows traders to withdraw their tokens at any time.
-However if a trader submits an order (\ie ask for their tokens), the tokens are committed and not available for withdrawal until the market closes (after which, the balances are updated for each trade that is executed).
-Committed tokens are also tracked in a mapping called \texttt{unavailableBalance}.
-Sellers can request a token withdrawal up to their total balance subtracted by their unavailable balance.
-
-When \texttt{closeMarket()} runs, \cm starts matching the best bids to the best asks.
-As orders execute, \texttt{totalBalance} and \texttt{unavailableBalance} are updated.
-At a certain point, the bids and asks will stop matching in price.
-At this point, every order left in the order book cannot execute (the priority queue sorts orders by price, so orders deeper in the queue have worse prices than the orders at the head of the queue).
-Therefore, all remaining entries in \texttt{unavailableBalance} can be cleared.
-
-In Solidity, it is not possible to delete an entire mapping without individually zeroing out each entry key-by-key.
-At the same time, it is wasteful to let an entire mapping sit in the EVM when it will never be referenced again.
-The following are some options for addressing this conflict:
-
-\begin{enumerate}
-
-\item \textbf{Manually Clear the Mapping.} Since mappings cannot be iterated, a common design pattern used by DApp developers is to store the keys in an array and iterate over the array to zero out each mapping and array entry.
-Clearing a mapping this way costs substantially more to clear than what is refunded.
-
-\item \textbf{Store the Mapping in a Separate DApp.} We could wrap the mapping inside its own DApp and run the \texttt{SELFDESTRUCT} operation on the contract once we finish processing the mapping.
-This refunds us 24,000 gas which is less than the cost of deploying the extra contract.
-Additionally, every call to the mapping is more expensive because (1) it is an external function call, and (2) the calls need access control to ensure only the market contract can write to it (if a mapping is a local variable, you get private access for free).
-
-\item \textbf{Leave and Ignore the Mapping.} The final option is to not clear the mapping and just create a new one (or create a new prefix for all mapping keys to reflect the new version of the mapping).
-Unfortunately, this is the most economical option for DApp developers even if it is the worst option for Ethereum nodes.
-
-\end{enumerate}
-
-Clearing storage is important for reducing EVM bloat\textblue{and who gets hurt with that?}.
-The Ethereum refund model should be considered further by Ethereum developers to provide a better incentive to be less wasteful in using storage.
 

### 2021-08-31 LaTeX-ACM/sections/paper.tex
comparison table done (down to 20 pages)

@@
 
-\paragraph[Centralized Exchanges (CEX)]{Centralized Exchanges (CEX)\eatpunct} Traditional financial markets (\eg NYSE and NASDAQ) use order-matching systems to arrange trades.
+\paragraph[Centralized Exchanges (CEX).] Traditional financial markets (\eg NYSE and NASDAQ) use order-matching systems to arrange trades.
 An exchange will list one or more assets (stocks, bonds, derivatives, or more exotic securities) to be traded with each other, given its own order book priced in a currency (\eg USD).

### 2021-08-31 LaTeX-LNCS-2022/sections/paper.tex
comparison table penciled in (needs edits)
comparison table done (down to 20 pages)

@@
 Later, we also discuss several bytecode operations (\emph{opcodes}) that refund gas (\ie cost negative gas), which we heavily utilize in our optimizations.
+\subsection{Trade Execution Systems}
 
-\subsection{Trade Execution Systems} %NEW:@Mahsa
-
-\emph{Order-driven} markets are a  group of trade execution systems where offers to buy (\emph{bids}) and sell (\emph{offers}/\emph{asks}) from many traders are placed as orders in an order book and executed based on matching rules enforced by the market.
-These markets can be \emph{continuous}, with buyers/sellers at any time adding orders to the order book (\emph{makers}) or executing against an existing order (\emph{takers}); or they can be \emph{called}, where all traders submit orders within a window of time and orders are matched in a batch (like an auction).
-Table~\ref{tab:exchanges} presents three types of order-driven exchanges:
-
-\input{tables/tradeexecutions.tex}
-\begin{itemize}
-
-\item\textbf{Centralized Exchanges (CEX).} Here, a firm (\eg Binance, Bitfinex, \etc) operates the platform as a trusted third party in every aspect: custodianship over assets/currency being traded, exchanging assets fairly, offering the best possible price execution.
-
-\item\textbf{Decentralized Exchanges (DEX).} These are hybrid order-driven exchanges with some trusted off-chain components and some on-chain functionalities.
-DEXes were first envisioned as operating fully on-chain, but performance limitations drove developers to move key components, such as the order matching system, off-chain to a centralized database.
-A landscape of DEX designs exist (\eg EtherDelta, 0x, IDEX, \etc): many avoid taking custodianship of assets off-chain, and virtually all (for order-driven markets) operate the order book itself off-chain (a regulatory hook).
-
-\item\textbf{Fully On-chain Exchanges.} Order matching can be performed `on-chain' by deploying the order-matching system either on a dedicated blockchain or inside a decentralized application (DApp).
-In this model, traders entrust their assets to an autonomously operating DApp with known source code instead of a third party custodian that can abscond with or lose the funds.
-The trading rules will operate as coded, clearing and settling can be guaranteed, and order submission is handled by the blockchain---a reasonably fair and transparent system (but see front-running; Section~\ref{sec:front}).
-Finally, anyone can create an on-chain order book for any asset (on the same chain) at any time.
-\end{itemize}
-Despite having a superior threat model, fully on-chain order-driven exchanges are slow, difficult to regulate and implement (see Table~\ref{tab:exchanges}).
-In this paper, we focus on benchmarking an order book for the public blockchain Ethereum.
-
-%\input{tables/eval.tex}
-
-%\subsection{Trade Execution Systems}
-%
-%There are three main approaches to arranging a trade~\cite{Har03}.
+There are three main approaches to arranging a trade~\cite{Har03}.
 In a \emph{quote-driven} market, a dealer uses its own inventory to offer a price for buying or selling an asset.
@@
 Order-driven markets can be \emph{continuous}, with buyers/sellers at any time adding orders to the order book (\emph{makers}) or executing against an existing order (\emph{takers}); or they can be \emph{called}, where all traders submit orders within a window of time and orders are matched in a batch (like an auction).
-%
+Table~\ref{tab:eval2} illustrates various trade execution systems and summerizes their advantages and disadvantages.
+
+\input{tables/eval2.tex}
+%========================Following section is already covered in the table========================%
 %\subsection{Trading Blockchain-Based Assets}
 %
-%%\input{tables/eval.tex}
-%
-%\paragraph{Centralized Exchanges (CEX).} Traditional financial markets (\eg NYSE and NASDAQ) use order-matching systems to arrange trades.
+%\paragraph{Centralized Exchanges (CEX)}Traditional financial markets (\eg NYSE and NASDAQ) use order-matching systems to arrange trades.
 An exchange will list one or more assets (stocks, bonds, derivatives, or more exotic securities) to be traded with each other, given its own order book priced in a currency (\eg USD).

### 2021-08-31 LaTeX-LNCS-2022/tables/eval2.tex
comparison table done (down to 20 pages)

% !TEX root = ../main.tex
 \newcolumntype{P}[1]{>{\centering\arraybackslash}p{#1}}
% = = = = = = = = = = = = = = = = = = = = =Call market operations Table = = = = = = = = = = = =  = = = = = =  %
\begin{table}[t]
%\setlength{\tabcolsep}{0.7\tabcolsep}% Shrink \tabcolsep

\centering
\scriptsize
%\begin{tabular}{|>{\centering}m{3cm} |>{\centering}m{3cm} |>{\centering}m{3cm} |>{\centering}m{4cm} |}
\begin{tabular}{|c|c|c|c|}

\hline
\textbf{Exchange Platform}			 &\textbf{Description}   				& \textbf{Advantages}      				& \textbf{Disadvantages}                   \\ \hline

% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = == = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = == = = = = = = = = = = = = = = = = = = = = = = = = == = = = = =%
\multirow{4}{*}{\shortstack{Centralized \\Exchanges}}                            & \multirow{4}{*}{\shortstack{Exchange acts as a \\trusted third party\\ between traders}} 	& High Liquidity			& Third party custodian				\\  
											&																		& High trade performance		& Low security				\\ 
											 &																		& Low price slippage		& No instant settlement	 		\\
											 &																		& Easy to regulate			& Server downtime							\\ \hline

% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = == = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = == = = = = = = = = = = = = = = = = = = = = = = = = == = = = = =%
\multirow{6}{*}{\shortstack{On-chain \\Order Books}}                         		& \multirow{6}{*}{\shortstack{Exchange operates\\fully \\on-chain as coded}}	& High security							&	\\
												&																		& Non-custodial						& 					\\
												&																		& No trusted third party					& Low trade performance						\\
												&																		& Fully Autonomous						&Hard to regulate			\\
												&																		& No Impermanent Loss					&					\\
												&																		& Low price slippage					&					\\ \hline

% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = == = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = == = = = = = = = = = = = = = = = = = = = = = = = = == = = = = =%
\multirow{5}{*}{\shortstack{On-chain \\Dealers} }                     	 & \multirow{5}{*}{ \shortstack{A dealer uses its \\own inventory to offer \\a price for assets \\being traded}}	& High security				& 				\\										
											&																						& Non-custodial			&  Impermanent Loss\\
											&																						& No trusted third party		&	High price slippage				\\
											&																						& Fully Autonomous			&	 No support for limit orders			\\
											&																						& High performance			&					\\ \hline

% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = == = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = == = = = = = = = = = = = = = = = = = = = = = = = = == = = = = =%
\multirow{3}{*}{\shortstack{Hybrid\\ Designs}}                            &  \multirow{3}{*}{\shortstack{Exchange operates \\partially on-chain}}  								& High trade performance				& Low security										\\
									&																									& Easy to regulate					& Server downtime \\
									&																									& Non-custodial 					& \shortstack{Uncertain fair execution}	\\ \hline
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
\end{tabular}
\caption{ A simple comparison among different trade execution systems.
\label{tab:eval2}}
\end{table}

% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %

### 2021-08-31 LaTeX-LNCS-2022/sections/paper.tex
arbitrum texts updated + mind map penciled in + random edits

@@
 \cm is designed as a base class that can be extended and customized. Here, we evaluate potential modifications.
+
+\begin{figure}[t]
+\centering
+\includegraphics[width=1\textwidth]{fig/MindMapDraft3.png}
+\caption{\footnotesize{Mind Map Draft}  \label{fig:rmindmap}}
+\end{figure}
 % = = = = = = = = = = = = = = = = = = = = = = = = =  %
@@
 
-\textit{Testing Platforms.} Arbitrum currently operates a test network with an Inbox contract on the Ethereum Kovan testnet.
-To experiment with Arbitrum, we implemented a variant of \cm and ran the same experiments that we previously performed on Layer 1 (Ethereum).
-To call functions on \cm, traders can (i) send transactions directly to the Inbox contract \href{https://kovan.etherscan.io/address/0x76bF1345224fE606E2aB38B8E52B83512328A9DF}, or (ii) use a relay server (called a \textit{Sequencer}) provided by the Arbitrum.
-The sequencer will group, order, and send all pending transactions together as a single Kovan transaction to the Inbox (and pay the gas).
+\textit{Testing Platforms.} To experiment with Arbitrum, we used the Arbitrum Rollup chain hosted on the Rinkeby testnet.
+We implemented a variant of \cm and ran the same experiments that we previously performed on Layer 1 (Ethereum).
+To call functions on \cm, traders can (i) send transactions directly to the Inbox contract \href{https://rinkeby.etherscan.io/address/0x578BAde599406A8fE3d24Fd7f7211c0911F5B29e}, or (ii) use a relay server (called a \textit{Sequencer}) provided by the Arbitrum.
+The sequencer will group, order, and send all pending transactions together as a single Rinkeby transaction to the Inbox (and pays the gas).
 
@@
 Closing a market with 38 pairs costs 46,705,693 ArbGas.
-Until Arbitrum deploys on mainnet, the price of ArbGas in Gwei (or USD) is unknown but it is thought to be relatively very cheap.
+%Until Arbitrum deploys on mainnet, the price of ArbGas in Gwei (or USD) is unknown but it is thought to be relatively very cheap.
 

### 2021-09-01 LaTeX-LNCS-2022/sections/paper.tex
L2 links updated

@@
 
- % Arbitrum V5 test results:
+ % Arbitrum Rinkeby test results:
 
@@
 We have also deployed \cm on Ethereum's testnet Rinkeby with flattened (single file) source code of just the \cm base class and priority queue implementations.
-It is visible and can be interacted with here: \href{https://rinkeby.etherscan.io/address/0x0d91de29c531d074853a5cef7cf9dfeb9c6ec4e0}{[etherscan.io]}; while the Arbitrum variant is here\textblue{the link is broken @Mahsa dont forget to re-run the test}: \href{https://explorer5.arbitrum.io/#/address/0x18BF65069Fdaed79f8BDB0B6EDa87d5cc46F6E28}{[explorer5.offchainlabs.com]}.
+It is visible and can be interacted with here: \href{https://rinkeby.etherscan.io/address/0x0d91de29c531d074853a5cef7cf9dfeb9c6ec4e0}{[etherscan.io]}; while the Arbitrum variant is here: \href{https://rinkeby-explorer.arbitrum.io/address/0x0aa5449a9f7fa34a81ce1dc720563938a27e8b03}{[https://rinkeby-explorer.arbitrum.io/]}.
 

### 2021-09-01 Code/L2-HardHat/hardhat.config.js

@@ -1,30 +1,16 @@
-require("@nomiclabs/hardhat-ethers");
-
-
-const accounts = {
-  mnemonic:
-    "rule nation tired logic palace city picnic bubble ridge grain problem pilot",
-  path: "m/44'/60'/0'/0",
-  initialIndex: 0,
-  count: 10,
-};
-
-/**
- * @type import('hardhat/config').HardhatUserConfig
- */
+require('dotenv').config()
+require("@nomiclabs/hardhat-waffle");
 module.exports = {
-  solidity: "0.7.0",
+  solidity: '0.7.0',
   networks: {
-    kovan: {
-      url: "https://kovan.infura.io/v3/" + process.env["INFURA_KEY"],
-      accounts: accounts,
+    l1: {
+      url: process.env['L1RPC'] || '',
+      accounts: [process.env['DEVNET_PRIVKEY']],
     },
-    arbkovan4: {
+    l2: {
       gasPrice: 0,
-      url: "https://kovan4.arbitrum.io/rpc",
-      accounts: accounts,
+      url: process.env['L2RPC'] || '',
+      accounts: [process.env['DEVNET_PRIVKEY']],
     },
-  }
-};
-
-
+  },
+}

### 2021-09-01 Code/L2-HardHat/scripts/Closing/1_Deposits.js

@@ -1,86 +1,0 @@
-
-
-
-const hre = require("hardhat");
-const ethers = require("ethers");
-const addressDappToken ='0x40bed42b1162EDb35A0dA7A48C32bDE014Ee0E3A'; //the address of the ERC20 token; it has the same address as Kovan
-var CallMarketaddress;
-
-
-require('dotenv').config();
-
-const main = async () => {
-   
-    const accounts = await hre.ethers.getSigners();
-
-    const infuraKey = process.env.INFURA_KEY
-    if(!infuraKey) throw new Error("No INFURA_KEY set.")
-
-    const walletPrivateKey = process.env.DEVNET_PRIVKEY
-    if(!walletPrivateKey) throw new Error("No DEVNET_PRIVKEY set.")
-
-
-    const l1Provider = new ethers.providers.JsonRpcProvider(process.env.L1RPC)
-    const l2Provider = new ethers.providers.JsonRpcProvider(process.env.L2RPC)
-    const signer = new ethers.Wallet(walletPrivateKey)
-
-    const l1Signer = signer.connect(l1Provider);
-    const l2Signer = signer.connect(l2Provider);
-
-
-
-
-    const L2CallMarket = await (await hre.ethers.getContractFactory('CallMarket')).connect(l2Signer)
-    
-    console.log("Deploying CallMarket to L2")
-    
-    const l2CallMarket = await L2CallMarket.deploy()
-    await l2CallMarket.deployed()
-    console.log(`deployed to ${l2CallMarket.address}`)
-
-    CallMarketaddress = l2CallMarket.address;
-
-    const l2DappToken = await (await hre.ethers.getContractAt('DappToken',addressDappToken )).connect(l2Signer)
-    
-    
-    await l2DappToken.connect(l2Signer).approve(CallMarketaddress, 10000000000);
-       
-    await l2CallMarket.connect(l2Signer).depositToken(addressDappToken, 10000000000);
-
-    const totalTokenbalance = await l2CallMarket.totalTokenBalance(l2Signer.address);
-    const totalEtherbalance = await l2CallMarket.totalEtherBalance(l2Signer.address);
-
-    console.log('The token balance of account[0] (Bob) is:', totalTokenbalance.toNumber());
-    console.log('The Ether balance of account[0] (Bob) is:', totalEtherbalance.toNumber());
-    console.log('********************************************');
-
-
-
-
-
-        //Following "value" is in wei.
-        //1 ether = 1,000,000,000,000,000,000 wei
[…]

### 2021-09-01 Code/L2-HardHat/scripts/Closing/2_Submit_Asks.js

@@ -1,69 +1,0 @@
-
-
-
-const hre = require("hardhat");
-const ethers = require("ethers");
-const addressDappToken ='0x40bed42b1162EDb35A0dA7A48C32bDE014Ee0E3A'; //the address of the ERC20 token; it has the same address as Kovan
-const CallMarketaddress ='0x18BF65069Fdaed79f8BDB0B6EDa87d5cc46F6E28';
-
-
-require('dotenv').config();
-
-const main = async () => {
-   
-    const accounts = await hre.ethers.getSigners();
-
-    const infuraKey = process.env.INFURA_KEY
-    if(!infuraKey) throw new Error("No INFURA_KEY set.")
-
-    const walletPrivateKey = process.env.DEVNET_PRIVKEY
-    if(!walletPrivateKey) throw new Error("No DEVNET_PRIVKEY set.")
-
-
-    const l1Provider = new ethers.providers.JsonRpcProvider(process.env.L1RPC)
-    const l2Provider = new ethers.providers.JsonRpcProvider(process.env.L2RPC)
-    const signer = new ethers.Wallet(walletPrivateKey)
-
-    const l1Signer = signer.connect(l1Provider);
-    const l2Signer = signer.connect(l2Provider);
-
-
-   
-
-    const l2CallMarket = await (await hre.ethers.getContractAt('CallMarket',CallMarketaddress )).connect(l2Signer)
-
-    await l2CallMarket.openMarket();
-
-    var receipt = null;
-    var array = [];
-    
-    for(let j = 38; j >= 1  ; j--){
-        
-            receipt = await l2CallMarket.connect(l2Signer).submitAsk(j, 1);
-            array.push(j);
-            //console.log('Ask',j,' volume is equal to:', 1);
-            console.log('Ask',j);
-            //console.log('the tx receipt is:', receipt);
-            console.log('******************************');
-        
-
-        }
-
-
-        
-        console.log(array.length,'asks have been succsessfully submitted');
-        console.log('********************************************');
-    
-   
-    
-
-
-}
-
-main()
-  .then(() => process.exit(0))
-  .catch(error => {
-    console.error(error);
-    process.exit(1);
-  });
-

### 2021-09-01 Code/L2-HardHat/scripts/Closing/3_Submit_Bids.js

@@ -1,69 +1,0 @@
-
-
-
-const hre = require("hardhat");
-const ethers = require("ethers");
-const addressDappToken ='0x40bed42b1162EDb35A0dA7A48C32bDE014Ee0E3A'; //the address of the ERC20 token; it has the same address as Kovan
-const CallMarketaddress ='0x18BF65069Fdaed79f8BDB0B6EDa87d5cc46F6E28';
-
-
-require('dotenv').config();
-
-const main = async () => {
-   
-    const accounts = await hre.ethers.getSigners();
-
-    const infuraKey = process.env.INFURA_KEY
-    if(!infuraKey) throw new Error("No INFURA_KEY set.")
-
-    const walletPrivateKey = process.env.DEVNET_PRIVKEY
-    if(!walletPrivateKey) throw new Error("No DEVNET_PRIVKEY set.")
-
-
-    const l1Provider = new ethers.providers.JsonRpcProvider(process.env.L1RPC)
-    const l2Provider = new ethers.providers.JsonRpcProvider(process.env.L2RPC)
-    const signer = new ethers.Wallet(walletPrivateKey)
-
-    const l1Signer = signer.connect(l1Provider);
-    const l2Signer = signer.connect(l2Provider);
-
-
-   
-
-    const l2CallMarket = await (await hre.ethers.getContractAt('CallMarket',CallMarketaddress )).connect(l2Signer)
-
-    //await l2CallMarket.openMarket();
-
-    var receipt = null;
-    var array = [];
-    
-    for(let j = 39; j <= 76  ; j++){
-        
-            receipt = await l2CallMarket.connect(l2Signer).submitBid(j, 1);
-            array.push(j);
-            //console.log('Ask',j,' volume is equal to:', 1);
-            console.log('Bid',j);
-            //console.log('the tx receipt is:', receipt);
-            console.log('******************************');
-        
-
-        }
-
-
-        
-        console.log(array.length,'bids have been succsessfully submitted');
-        console.log('********************************************');
-    
-   
-    
-
-
-}
-
-main()
-  .then(() => process.exit(0))
-  .catch(error => {
-    console.error(error);
-    process.exit(1);
-  });
-

### 2021-09-01 Code/L2-HardHat/scripts/Closing/4_Match.js

@@ -1,55 +1,0 @@
-
-
-
-
-
-
-
-const hre = require("hardhat");
-const ethers = require("ethers");
-//const addressDappToken ='0x9D83C3c3e39d12416c395Da096988511B57E712F'; //the address of the ERC20 token; it has the same address as Kovan
-const CallMarketaddress ='0x18BF65069Fdaed79f8BDB0B6EDa87d5cc46F6E28';
-
-
-require('dotenv').config();
-
-const main = async () => {
-   
-    const accounts = await hre.ethers.getSigners();
-
-    const infuraKey = process.env.INFURA_KEY
-    if(!infuraKey) throw new Error("No INFURA_KEY set.")
-
-    const walletPrivateKey = process.env.DEVNET_PRIVKEY
-    if(!walletPrivateKey) throw new Error("No DEVNET_PRIVKEY set.")
-
-
-    const l1Provider = new ethers.providers.JsonRpcProvider(process.env.L1RPC)
-    const l2Provider = new ethers.providers.JsonRpcProvider(process.env.L2RPC)
-    const signer = new ethers.Wallet(walletPrivateKey)
-
-    const l1Signer = signer.connect(l1Provider);
-    const l2Signer = signer.connect(l2Provider);
-
-
-   
-
-    const l2CallMarket = await (await hre.ethers.getContractAt('CallMarket',CallMarketaddress )).connect(l2Signer)
-
-    const receipt = await l2CallMarket.connect(l2Signer).closeMarket();
-    console.log('the tx receipt is:', receipt);
-    
-   
-   
-    
-
-
-}
-
-main()
-  .then(() => process.exit(0))
-  .catch(error => {
-    console.error(error);
-    process.exit(1);
-  });
-

### 2021-09-01 Code/L2-HardHat/scripts/Submission/1_Deposits 2.js

@@ -1,67 +1,0 @@
-
-
-
-const hre = require("hardhat");
-const ethers = require("ethers");
-const addressDappToken ='0x40bed42b1162EDb35A0dA7A48C32bDE014Ee0E3A'; //the address of the ERC20 token; it has the same address as Kovan
-var CallMarketaddress;
-
-
-require('dotenv').config();
-
-const main = async () => {
-   
-    const accounts = await hre.ethers.getSigners();
-
-    const infuraKey = process.env.INFURA_KEY
-    if(!infuraKey) throw new Error("No INFURA_KEY set.")
-
-    const walletPrivateKey = process.env.DEVNET_PRIVKEY
-    if(!walletPrivateKey) throw new Error("No DEVNET_PRIVKEY set.")
-
-
-    const l1Provider = new ethers.providers.JsonRpcProvider(process.env.L1RPC)
-    const l2Provider = new ethers.providers.JsonRpcProvider(process.env.L2RPC)
-    const signer = new ethers.Wallet(walletPrivateKey)
-
-    const l1Signer = signer.connect(l1Provider);
-    const l2Signer = signer.connect(l2Provider);
-
-
-
-
-    const L2CallMarket = await (await hre.ethers.getContractFactory('CallMarket')).connect(l2Signer)
-    
-    console.log("Deploying CallMarket to L2")
-    
-    const l2CallMarket = await L2CallMarket.deploy()
-    await l2CallMarket.deployed()
-    console.log(`deployed to ${l2CallMarket.address}`)
-
-    CallMarketaddress = l2CallMarket.address;
-
-    const l2DappToken = await (await hre.ethers.getContractAt('DappToken',addressDappToken)).connect(l2Signer)
-    
-    
-    await l2DappToken.connect(l2Signer).approve(CallMarketaddress, 1000000000);
-       
-    await l2CallMarket.connect(l2Signer).depositToken(addressDappToken, 1000000000);
-
-    const totalTokenbalance = await l2CallMarket.totalTokenBalance(l2Signer.address);
-    const totalEtherbalance = await l2CallMarket.totalEtherBalance(l2Signer.address);
-
-    console.log('The token balance of account[0] (Bob) is:', totalTokenbalance.toNumber());
-    console.log('The Ether balance of account[0] (Bob) is:', totalEtherbalance.toNumber());
-    console.log('********************************************');
-
-
-
-
-}
-
-main()
-  .then(() => process.exit(0))
-  .catch(error => {
-    console.error(error);
-    process.exit(1);
-  });

### 2021-09-01 Code/L2-HardHat/scripts/Submission/1_Deposits.js

@@ -1,116 +1,0 @@
-const hre = require("hardhat");
-const ethers = require("ethers");
-const utils = require ("ethers");
-const BigNumber = require ("ethers");
-
-require('dotenv').config();
-
-const main = async () => {
-   
-    const accounts = await hre.ethers.getSigners();
-
-    const infuraKey = process.env.INFURA_KEY
-    if(!infuraKey) throw new Error("No INFURA_KEY set.")
-
-    const walletPrivateKey = process.env.DEVNET_PRIVKEY
-    if(!walletPrivateKey) throw new Error("No DEVNET_PRIVKEY set.")
-
-
-    const l1Provider = new ethers.providers.JsonRpcProvider(process.env.L1RPC)
-    const l2Provider = new ethers.providers.JsonRpcProvider(process.env.L2RPC)
-    const signer = new ethers.Wallet(walletPrivateKey)
-
-    const l1Signer = signer.connect(l1Provider);
-
-    const ethercBridge = "0x2948ac43e4AfF448f6af0F7a11F18Bb6062dd271";
-    const addressDappToken ;
-    var CallMarketaddress;
-    
-    const L1CallMarket = await (await hre.ethers.getContractFactory('CallMarket')).connect(l1Signer)
-    console.log("Deploying CallMarket to L1")
-    const l1CallMarket = await L1CallMarket.deploy()
-    await l1CallMarket.deployed()
-    CallMarketaddress = l1CallMarket.address;
-    console.log(`Call Market deployed to ${CallMarketaddress}`)
-
-   
-    //deposit tokens from signer to the CallMarket contract
-
-    const L1DappToken = await (await hre.ethers.getContractFactory('DappToken')).connect(l1Signer)
-    console.log("Deploying DappToken to L1")
-    const l1DappToken = await L1DappToken.deploy(100000000000)
-    await l1DappToken.deployed()
-    addressDappToken = l1DappToken.address;
-
-    //const DappTokenInstance = await ethers.getContractAt("DappToken", addressDappToken); //loads the DappToken from its address
-
-
-    const ethrbidge = await ethers.getContractAt("EthERC20Bridge", ethercBridge); 
-
-    await ethrbidge.deposit(addressDappToken, signer.address, BigNumber.from(1000000), BigNumber.from(10000000000000), BigNumber.from(0), utils.parseUnits('10', 'gwei'), '0x');
-    const L2address = await ethrbidge.calculateL2TokenAddress(addressDappToken)
[…]

### 2021-09-01 Code/L2-HardHat/scripts/Submission/2_Submit_Asks 2.js

@@ -1,67 +1,0 @@
-
-
-
-const hre = require("hardhat");
-const ethers = require("ethers");
-const addressDappToken ='0x40bed42b1162EDb35A0dA7A48C32bDE014Ee0E3A'; //the address of the ERC20 token; it has the same address as Kovan
-const CallMarketaddress ='0x36e71cB7a6B598e3C04322c222Ae632B3F42c8Cf';
-
-
-require('dotenv').config();
-
-const main = async () => {
-   
-    const accounts = await hre.ethers.getSigners();
-
-    const infuraKey = process.env.INFURA_KEY
-    if(!infuraKey) throw new Error("No INFURA_KEY set.")
-
-    const walletPrivateKey = process.env.DEVNET_PRIVKEY
-    if(!walletPrivateKey) throw new Error("No DEVNET_PRIVKEY set.")
-
-
-    const l1Provider = new ethers.providers.JsonRpcProvider(process.env.L1RPC)
-    const l2Provider = new ethers.providers.JsonRpcProvider(process.env.L2RPC)
-    const signer = new ethers.Wallet(walletPrivateKey)
-
-    const l1Signer = signer.connect(l1Provider);
-    const l2Signer = signer.connect(l2Provider);
-
-
-    var maximum = 100;
-    var minimum = 1;
-
-    const l2CallMarket = await (await hre.ethers.getContractAt('CallMarket',CallMarketaddress )).connect(l2Signer)
-
-    await l2CallMarket.openMarket();
-
-    var receipt = null;
-    var array = [];
-    
-    for(let j = 1; j <= 100  ; j++){
-
-
-        var randomnumber = Math.floor(Math.random() * (maximum - minimum + 1)) + minimum;
-        receipt = await l2CallMarket.connect(l2Signer).submitAsk(randomnumber, 1);
-            array.push(j);
-            //console.log('Ask',j,' volume is equal to:', 1);
-            console.log('Ask',j);
-            console.log('the tx receipt is:', receipt);
-            console.log('******************************');
-        } 
-        console.log(array.length,'asks have been succsessfully submitted');
-        console.log('********************************************');
-    
-   
-    
-
-
-}
-
-main()
-  .then(() => process.exit(0))
-  .catch(error => {
-    console.error(error);
-    process.exit(1);
-  });
-

### 2021-09-01 Code/L2-HardHat/scripts/Submission/3_Submit_Bids.js

@@ -1,46 +1,0 @@
-
-
-const CallMarket = artifacts.require('CallMarket.sol');
-const DappToken = artifacts.require('DappToken');
-
-const addressDappToken = '0x2dc4dea5281738a92e8de9137a1088403dd3c160'; //the address of the ERC20 token; it has the same address as Kovan
-const CallMarketaddress = '0xB3267469542f52D9F572649a734B01a7DAeE64E1';
-
-var accounts;
-var maximum = 100;
-var minimum = 1;
-
-
-
-
-//******************* Deploys the CallMaket and stores its address *************************
-contract('CallMarket', function(accounts) {
-    
-
-   
-    //*******************Test 6*************************
-    it('should submit Bids from accounst[1]', async() => {
-        
-        const CallMarketInstance = await CallMarket.at(CallMarketaddress);
-        var receipt = null;
-        var array = [];
-        
-        accounts = await web3.eth.getAccounts();
-        for(let j = 1; j <= 200  ; j++){
-           
-            
-            var randomnumber = Math.floor(Math.random() * (maximum - minimum + 1)) + minimum;
-            receipt = await CallMarketInstance.submitBid (randomnumber, 1, {from: accounts[0]});
-            array.push(j);
-            //console.log('Bid',j,' volume is equal to:', 1);
-            //console.log('Bid',j);
-            //console.log('the tx receipt is:', receipt);
-            //console.log('******************************');
-
-        } 
-        console.log(array.length,'bids have been succsessfully submitted');
-        console.log('********************************************');
-    });
-
-    
-});

### 2021-09-01 Code/L2-HardHat/scripts/Submission/4_Match.js

@@ -1,31 +1,0 @@
-
-
-const CallMarket = artifacts.require('CallMarket.sol');
-const DappToken = artifacts.require('DappToken');
-
-const addressDappToken = '0x2dc4dea5281738a92e8de9137a1088403dd3c160'; //the address of the ERC20 token; it has the same address as Kovan
-const CallMarketaddress = '0xB3267469542f52D9F572649a734B01a7DAeE64E1';
-
-var accounts;
-
-
-
-
-//******************* Deploys the CallMaket and stores its address *************************
-contract('CallMarket', function(accounts) {
-
-  
-    //*******************Test 1*************************
-    it('should close the market and match the orders', async() => {
-        
-        const CallMarketInstance = await CallMarket.at(CallMarketaddress);
-
-        const receipt = await  CallMarketInstance.closeMarket();
-        console.log('the tx receipt is:', receipt);
-    });  
-    
- 
-
-
-
-});

### 2021-09-01 Code/L2-HardHat/scripts/depositToken.js

@@ -1,0 +1,80 @@
+const { BigNumber, providers, Wallet } = require('ethers')
+const { ethers } = require('hardhat')
+const { Bridge } = require('arb-ts')
+require('dotenv').config()
+
+
+const walletPrivateKey = process.env.DEVNET_PRIVKEY
+const l1Provider = new providers.JsonRpcProvider(process.env.L1RPC)
+const l2Provider = new providers.JsonRpcProvider(process.env.L2RPC)
+
+const l1Wallet = new Wallet(walletPrivateKey, l1Provider)
+const l2Wallet = new Wallet(walletPrivateKey, l2Provider)
+
+
+const tokenDepositAmount = BigNumber.from(1000000000)
+
+const main = async () => {
+ 
+  const bridge = await Bridge.init(l1Wallet, l2Wallet)
+
+
+  const L1DappToken = await (await ethers.getContractFactory('DappToken')).connect(l1Wallet)
+  console.log('Deploying the test DappToken to L1')
+  const l1DappToken = await L1DappToken.deploy(1000000000000000)
+  await l1DappToken.deployed()
+  console.log(`DappToken is deployed to L1 at ${l1DappToken.address}`)
+  const erc20Address = l1DappToken.address
+
+  
+  const approveTx = await bridge.approveToken(erc20Address)
+  const approveRec = await approveTx.wait()
+  console.log(`You successfully allowed the Arbitrum Bridge to spend DappToken ${approveRec.transactionHash}`)
+
+
+  const depositTx = await bridge.deposit(erc20Address, tokenDepositAmount)
+  const depositRec = await depositTx.wait()
+
+  
+
+  const seqNumArr = await bridge.getInboxSeqNumFromContractTransaction(
+    depositRec
+  )
+
+ 
+  const seqNum = seqNumArr[0]
+  console.log(
+    `Sequence number for your transaction found: ${seqNum.toNumber()}`
+  )
+
+  const redeemTransaction = await bridge.calculateL2RetryableTransactionHash(seqNum)
+
+  
+  console.log('waiting for L2 transaction:')
+  const l2TxnRec = await l2Provider.waitForTransaction(
+    redeemTransaction,
+    undefined,
+    1000 * 60 * 12
+  )
+
+  console.log( `L2 transaction found! Your DappToken balance is updated! ${l2TxnRec.transactionHash}`)
+
+ 
+
[…]

### 2021-09-02 LaTeX-LNCS-2022/sections/paper.tex
availability section removed

@@
 Our vision is the market would be open for a very short period of time, close, and then reopen immediately (\eg every other block).
-\cm is open source and written in 336 lines (SLOC) of Solidity plus the priority queue (\eg a heap with dynamic array is 282 SLOC)\footnote{Github: Link removed for anonymity.}.
+\cm is open source and written in 336 lines (SLOC) of Solidity plus the priority queue (\eg a heap with dynamic array is 282 SLOC).
 We tested it with the Mocha testing framework using Truffle on Ganache-CLI to obtain our performance metrics.
 Once deployed, the bytecode of \cm is 10,812 bytes plus the constructor code (6,400 bytes) which is not stored.
+The Solidity source code for \cm and Truffle test files are available in a GitHub repository.\footnote{Github: Link removed for anonymity.} We have also deployed \cm on Ethereum's testnet Rinkeby with flattened (single file) source code of just the \cm base class and priority queue implementations.
+It is visible and can be interacted with here: \href{https://rinkeby.etherscan.io/address/0x0d91de29c531d074853a5cef7cf9dfeb9c6ec4e0}{[etherscan.io]}.
 We cross-checked for vulnerabilities with \textit{Slither}\footnote{https://github.com/crytic/slither} and \textit{SmartCheck}\footnote{https://tool.smartdec.net} (it only fails some `informational' warnings that are intentional design choices---\eg a costly loop).
@@
 \textit{Testing Platforms.} To experiment with Arbitrum, we used the Arbitrum Rollup chain hosted on the Rinkeby testnet.
-We implemented a variant of \cm and ran the same experiments that we previously performed on Layer 1 (Ethereum).
-To call functions on \cm, traders can (i) send transactions directly to the Inbox contract \href{https://rinkeby.etherscan.io/address/0x578BAde599406A8fE3d24Fd7f7211c0911F5B29e}, or (ii) use a relay server (called a \textit{Sequencer}) provided by the Arbitrum.
+We implemented a variant of \cm(\href{https://rinkeby-explorer.arbitrum.io/address/0x0aa5449a9f7fa34a81ce1dc720563938a27e8b03}{[https://rinkeby-explorer.arbitrum.io/]}) and ran the same experiments that we previously performed on Layer 1.
+To call functions on \cm, traders can (i) send transactions directly to the \href{https://rinkeby.etherscan.io/address/0x578BAde599406A8fE3d24Fd7f7211c0911F5B29e}{Inbox contract}, or (ii) use a relay server (called a \textit{Sequencer}) provided by the Arbitrum.
 The sequencer will group, order, and send all pending transactions together as a single Rinkeby transaction to the Inbox (and pays the gas).
@@
 
-\section{Availability} 
-\label{sec:avai}
-The Solidity source code for \cm, Truffle test files, and Arbitrum dependencies are available in a GitHub repository (non-anonymous link omitted).
-We have also deployed \cm on Ethereum's testnet Rinkeby with flattened (single file) source code of just the \cm base class and priority queue implementations.
-It is visible and can be interacted with here: \href{https://rinkeby.etherscan.io/address/0x0d91de29c531d074853a5cef7cf9dfeb9c6ec4e0}{[etherscan.io]}; while the Arbitrum variant is here: \href{https://rinkeby-explorer.arbitrum.io/address/0x0aa5449a9f7fa34a81ce1dc720563938a27e8b03}{[https://rinkeby-explorer.arbitrum.io/]}.
-
 %ACK

### 2021-09-08 LaTeX-LNCS-2022/sections/paper.tex
added the L2 diagram fig/LissyL2.md)
L2 new hardhat code + numbers + table (text updated as well)

@@
 Table~\ref{tab:cm_functions} summarizes \cm's primary operations.
-Also, \cm is an extensible base class that is still functional without any extensions. Figure\textblue{mindmap} represents a design  landscape and extensions.
+\textblue{Figuremindmap represents a design  landscape and extensions.}
 
@@
 \subsection{\cm on Arbitrum}
+\input{tables/performance_Arbitrum}
 
@@
 Recall that without a roll-up, such a priority queue can only match 38 pairs at a cost of 5,372,679 gas.
-With Arbitrum roll-ups, 38 pairs cost only 1,632 in Layer 1 gas (a 99.9\% savings).
-This is effectively the cost of recording the \texttt{closeMarket()} function call in the Inbox, which is 103 bytes of calldata.
+With Arbitrum roll-ups, 38 pairs cost only 6,569 in Layer 1 gas (a 99.9\% savings).
+This is effectively the cost of submitting \texttt{closeMarket()} transaction to the inbox and recording the function call, which is 103 bytes of calldata.
 As the number of pairs increases, Layer 1 gas cost is constant.
-For traders submitting an order, the cost is reduced from  207,932 to 2,656.
-
- % Arbitrum Rinkeby test results:
-
- % Heap Dynamic Array: 100 order submissions averaged L2 arbgas: 1,659,416, L1 gas: fixed: 2656
-
- % Linked List w/ Mapping: 100 order submissions averaged L2 arbgas: 2,452,376, L1 gas: fixed: 2656
-
- % Heap Dynamic Array: worst case matching, 38 pairs of orders: tx hash: 0x2c0f5b5ba3539eb72018c08856c156c8098edcfd35db80f929a13c0aa6f9cc01, L1 gas: 1632, L2 arbgas: 1,039,351
- % (https://explorer5.arbitrum.io/#/tx/0x2c0f5b5ba3539eb72018c08856c156c8098edcfd35db80f929a13c0aa6f9cc01)
-
- % Linked List w/ Mapping: worst case matching, 38 pairs of orders: tx hash: 0x96aa143aee7bfb529d35456bef86387ef2adac30f222ea6a3216ded313e00973, L1 gas: 1632, L2 arbgas: 800,529
- % (https://explorer5.arbitrum.io/#/tx/0x96aa143aee7bfb529d35456bef86387ef2adac30f222ea6a3216ded313e00973)
+For traders submitting an order, the cost is reduced from  207,932 to 6,917.
 

### 2021-09-08 Code/L2-HardHat/scripts/random_submission.js

@@ -1,0 +1,65 @@
+const { providers, Wallet } = require('ethers')
+const { ethers } = require('hardhat')
+
+require('dotenv').config();
+
+const main = async () => {
+  const addressDappToken ='0x0391de5c475479bD9E7a0355AA022D864C57d876'; //the address of the DAppToken on L2
+  var CallMarketaddress;  
+  
+  const walletPrivateKey = process.env.DEVNET_PRIVKEY
+
+  const l2Provider = new providers.JsonRpcProvider(process.env.L2RPC)
+
+  const l2Wallet = new Wallet(walletPrivateKey, l2Provider)
+   
+
+
+  const L2CallMarket = await ( await ethers.getContractFactory('CallMarket')).connect(l2Wallet)
+  const l2CallMarket = await L2CallMarket.deploy()
+  console.log("Deploying CallMarket to L2")
+  await l2CallMarket.deployed()
+  console.log(`Call Market is deployed to ${l2CallMarket.address}`)
+
+  CallMarketaddress = l2CallMarket.address;
+
+  const l2DappToken = await (await hre.ethers.getContractAt('DappToken',addressDappToken )).connect(l2Wallet)
+    
+  await l2DappToken.approve(CallMarketaddress, 10000000000);
+       
+  await l2CallMarket.depositToken(addressDappToken, 10000000000);
+
+  const totalTokenbalance = await l2CallMarket.totalTokenBalance(l2Wallet.address);
+  const totalEtherbalance = await l2CallMarket.totalEtherBalance(l2Wallet.address);
+
+  console.log('The token balance of account[0] is:', totalTokenbalance.toNumber());
+  console.log('The Ether balance of account[0] is:', totalEtherbalance.toNumber());
+  console.log('********************************************');
+
+  
+  console.log("token deposits done! Let's submit orders now")
+  await l2CallMarket.openMarket();
+
+
+
+  var array = [];
+
+  for(let j = 1; j <= 200  ; j++)
+  {
+    var randomnumber = Math.floor(Math.random() * (maximum - minimum + 1)) + minimum;
+    await l2CallMarket.submitAsk(randomnumber, 1);
+  } 
+  console.log(array.length,'asks have been succsessfully submitted');
+    
+  
+
+
+
+}
+
+main()
+  .then(() => process.exit(0))
+  .catch(error => {
+    console.error(error);
+    process.exit(1);
+  });

### 2021-09-08 Code/Test/hardhat.config.js

@@ -1,0 +1,16 @@
+require('dotenv').config()
+require("@nomiclabs/hardhat-waffle");
+module.exports = {
+  solidity: '0.7.0',
+  networks: {
+    l1: {
+      url: process.env['L1RPC'] || '',
+      accounts: [process.env['DEVNET_PRIVKEY']],
+    },
+    l2: {
+      gasPrice: 0,
+      url: process.env['L2RPC'] || '',
+      accounts: [process.env['DEVNET_PRIVKEY']],
+    },
+  },
+}

### 2021-09-08 Code/Test/scripts/closing.js

@@ -1,0 +1,95 @@
+const { providers, Wallet } = require('ethers')
+const { ethers } = require('hardhat')
+
+require('dotenv').config();
+
+const main = async () => {
+  const addressDappToken ='0x0391de5c475479bD9E7a0355AA022D864C57d876'; //the address of the DAppToken on L2
+  var CallMarketaddress;  
+  
+  const walletPrivateKey = process.env.DEVNET_PRIVKEY
+
+  const l2Provider = new providers.JsonRpcProvider(process.env.L2RPC)
+
+  const l2Wallet = new Wallet(walletPrivateKey, l2Provider)
+   
+
+
+  const L2CallMarket = await ( await ethers.getContractFactory('CallMarket')).connect(l2Wallet)
+  const l2CallMarket = await L2CallMarket.deploy()
+  console.log("Deploying CallMarket to L2")
+  await l2CallMarket.deployed()
+  console.log(`Call Market is deployed to ${l2CallMarket.address}`)
+
+  CallMarketaddress = l2CallMarket.address;
+
+  const l2DappToken = await (await hre.ethers.getContractAt('DappToken',addressDappToken )).connect(l2Wallet)
+    
+  await l2DappToken.approve(CallMarketaddress, 10000000000);
+       
+  await l2CallMarket.depositToken(addressDappToken, 10000000000);
+
+  const totalTokenbalance = await l2CallMarket.totalTokenBalance(l2Wallet.address);
+  const totalEtherbalance = await l2CallMarket.totalEtherBalance(l2Wallet.address);
+
+  console.log('The token balance of account[0] is:', totalTokenbalance.toNumber());
+  console.log('The Ether balance of account[0] is:', totalEtherbalance.toNumber());
+  console.log('********************************************');
+
+  await l2CallMarket.depositEther({value: 2200}); //transferring 0.000000000000000001 eth
+  const totalEtherbalance2 = await l2CallMarket.totalEtherBalance(l2Wallet.address);
+  console.log('The Ether balance of accounts[0]  is:',totalEtherbalance2.toNumber());
+  console.log('********************************************');
+  const num = await l2CallMarket.getBalance();
+  console.log('The Ether balance of Lissy is:', num.toNumber()); 
+
+  console.log("ETH and token deposits done! Let's submit orders now")
+  await l2CallMarket.openMarket();
+
+
+
+  var array1 = [];
+    
+  for(let j = 38; j >= 1  ; j--)
[…]

### 2021-09-08 Code/Test/scripts/depositToken.js

@@ -1,0 +1,81 @@
+const { BigNumber, providers, Wallet } = require('ethers')
+const { ethers } = require('hardhat')
+const { Bridge } = require('arb-ts')
+require('dotenv').config()
+
+
+const walletPrivateKey = process.env.DEVNET_PRIVKEY
+const l1Provider = new providers.JsonRpcProvider(process.env.L1RPC)
+const l2Provider = new providers.JsonRpcProvider(process.env.L2RPC)
+
+const l1Wallet = new Wallet(walletPrivateKey, l1Provider)
+const l2Wallet = new Wallet(walletPrivateKey, l2Provider)
+
+
+const tokenDepositAmount = BigNumber.from(1000000000)
+
+const main = async () => {
+ 
+  const bridge = await Bridge.init(l1Wallet, l2Wallet)
+  var maximum = 100;
+  var minimum = 1;
+
+  const L1DappToken = await (await ethers.getContractFactory('DappToken')).connect(l1Wallet)
+  console.log('Deploying the test DappToken to L1')
+  const l1DappToken = await L1DappToken.deploy(1000000000000000)
+  await l1DappToken.deployed()
+  console.log(`DappToken is deployed to L1 at ${l1DappToken.address}`)
+  const erc20Address = l1DappToken.address
+
+  
+  const approveTx = await bridge.approveToken(erc20Address)
+  const approveRec = await approveTx.wait()
+  console.log(`You successfully allowed the Arbitrum Bridge to spend DappToken ${approveRec.transactionHash}`)
+
+
+  const depositTx = await bridge.deposit(erc20Address, tokenDepositAmount)
+  const depositRec = await depositTx.wait()
+
+  
+
+  const seqNumArr = await bridge.getInboxSeqNumFromContractTransaction(
+    depositRec
+  )
+
+ 
+  const seqNum = seqNumArr[0]
+  console.log(
+    `Sequence number for your transaction found: ${seqNum.toNumber()}`
+  )
+
+  const redeemTransaction = await bridge.calculateL2RetryableTransactionHash(seqNum)
+
+  
+  console.log('waiting for L2 transaction:')
+  const l2TxnRec = await l2Provider.waitForTransaction(
+    redeemTransaction,
+    undefined,
+    1000 * 60 * 12
+  )
+
+  console.log( `L2 transaction found! Your DappToken balance is updated! ${l2TxnRec.transactionHash}`)
+
+ 
+
[…]

### 2021-09-08 Code/Test/scripts/random_submission.js

@@ -1,0 +1,75 @@
+const { providers, Wallet } = require('ethers')
+const { ethers } = require('hardhat')
+
+require('dotenv').config();
+
+const main = async () => {
+  const addressDappToken ='0xb3a8791b48FcEAec736330dfc4dF38Cf06D1f183'; //the address of the DAppToken on L2
+  const CallMarketaddress = '0x45F5F09364F5cc7D12F49d40814000b1fF9c6cc2';
+  
+  const walletPrivateKey = process.env.DEVNET_PRIVKEY
+
+  const l2Provider = new providers.JsonRpcProvider(process.env.L2RPC)
+
+  const l2Wallet = new Wallet(walletPrivateKey, l2Provider)
+   
+
+
+  // const L2CallMarket = await ( await ethers.getContractFactory('CallMarket')).connect(l2Wallet)
+  // const l2CallMarket = await L2CallMarket.deploy()
+  // console.log("Deploying CallMarket to L2")
+  // await l2CallMarket.deployed()
+  // console.log(`Call Market is deployed to ${l2CallMarket.address}`)
+
+  // CallMarketaddress = l2CallMarket.address;
+  const l2CallMarket = await (await hre.ethers.getContractAt('CallMarket',CallMarketaddress)).connect(l2Wallet)
+
+  // const l2DappToken = await (await hre.ethers.getContractAt('DappToken',addressDappToken )).connect(l2Wallet)
+  // const DapptokenBalanace = await l2DappToken.balanceOf(l2Wallet.address) 
+  // console.log('The DappToken balance of  l2wallet is:', DapptokenBalanace.toNumber());
+
+  // const result = await l2DappToken.allowance(l2Wallet.address,CallMarketaddress);
+  // console.log('l2wallet allowes the CallMarket contract to spend:',result.toNumber());
+
+  // //await l2DappToken.approve(CallMarketaddress, 10000000000);
+       
+  // await l2CallMarket.depositToken(addressDappToken, 1000000000);
+
+  // const totalTokenbalance = await l2CallMarket.totalTokenBalance(l2Wallet.address);
+  // // //const totalEtherbalance = await l2CallMarket.totalEtherBalance(l2Wallet.address);
+
+  // console.log('The token balance of account[0] is:', totalTokenbalance.toNumber());
+  // //console.log('The Ether balance of account[0] is:', totalEtherbalance.toNumber());
+  // console.log('********************************************');
+
+  
[…]

### 2021-09-10 LaTeX-LNCS-2022/sections/abstract.tex
top matter [19 pages total]

--- 2021-04-28 LaTeX-ACM/sections/abstract.tex
@@
 
-When consumers trade financial products, they typically use well-identified service providers that operate under government regulation.
-In theory, decentralized platforms like Ethereum can offer trading services `on-chain' without an obvious entry point for regulators.
-Fortunately for regulators, most trading volume in blockchain-based assets is still on centralized service providers for performance reasons.
-However this leaves the following research questions we address in this paper: (i) is secure trading (\ie resistant to front-running and price manipulation) even feasible as a fully `on-chain' service on a public blockchain, (ii) what is its performance benchmark, and (iii) what is the performance impact of novel techniques (\eg `roll-ups') in closing the performance gap?
-
-To answer these questions, we `learn by doing' and custom design an Ethereum-based call market (or batch auction) exchange, \cm, with favorable security properties.
-We conduct a variety of optimizations and experiments to demonstrate that this technology cannot expect to exceed a few hundred trade executions per block (\ie ~13s window of time).
-However this can be scaled dramatically with off-chain execution that is not consumer-facing.
-We also illustrate, with numerous examples throughout the paper, how blockchain deployment is full of nuances that make it quite different from developing in better understood domains (\eg cloud-based web applications).
+Financial regulators have long-standing concerns about fully decentralized exchanges that run `on-chain' without any obvious regulatory hooks.
+Uniswap's open protocol and the next generation of such automated market makers (AMMs) made these concerns a reality.
+AMMs implement a lightweight dealer-based trading system, but it is unlike anything on Wall Street, requires fees intrinsically, and is susceptible to front-running attacks.
+This leaves the following research questions we address in this paper: (i) are conventional (\ie orderbooks) and secure (\ie resistant to front-running and price manipulation) exchanges feasible as a fully on-chain service on a public blockchain, (ii) what is the performance profile, and (iii) how much do Layer 2 techniques (\eg Arbitrum) increase performance?
+To answer these questions, we implement, benchmark, and experiment with an Ethereum-based call market (or batch auction) exchange called \cm, demonstrating many of Ethereum's nuances.
+We confirm the functionality is too heavy for Ethereum today (you cannot expect to exceed a few hundred trade executions per block) but show it scales dramatically (99.88\% gas cost reduction) on Arbitrum.
 

### 2021-09-10 LaTeX-LNCS-2022/sections/appendix.tex
L2 diagram added to appendix
top matter [19 pages total]

@@
 
-\textbf{Ethereum's Gas Model.} Every transaction results in the participating nodes having to execute bytecode.
+\section{Additional background}
+\label{app:back}
+
+\subsection{Ethereum and Blockchain Technology}
+
+A public blockchain is an open peer-to-peer network that maintains a set of transactions without a single entity in charge.
+In Ethereum, \emph{transactions} encode the bytecode of user-written \emph{decentralized applications (DApps)} to be stored on the blockchain; and the function calls made to the DApp.
+Every execution of every function call is validated by all honest, participating nodes to correct; a property that is robust against a fraction of faulty and malicious network nodes (or more precisely, their accumulated computational power).
+Once transactions are agreed upon, all honest participants will have identical sets of transactions in the same order.
+For Ethereum, this is conceptualized as the current state of a large \emph{virtual machine (EVM)} that is running many DApps.
+
+Transactions are broadcast by users to the blockchain network where they are propagated to all nodes.
+Nodes that choose to \emph{mine} will collect transactions (in the order of their choosing) into a block, and will attempt to have the network reach a consensus that their block should be added to the set (or chain) of previous blocks.
+A transaction is considered finalized once consensus on its inclusion has held for several additional blocks.
+
+% JC: Should explain what "calldata" is as it is important for gas costs on Arbitrum
+
+\paragraph{Ethereum's Gas Model.}
+
+Every transaction results in the participating nodes having to execute bytecode.
 This is not free.
@@
 
-\section{Gas Refunds.} In order to reconstruct the current state of Ethereum's EVM, a node must obtain a copy of every variable change since the genesis block (or a more recent `checkpoint' that is universally agreed to).
+\paragraph{Gas Refunds.}
+
+In order to reconstruct the current state of Ethereum's EVM, a node must obtain a copy of every variable change since the genesis block (or a more recent `checkpoint' that is universally agreed to).
 For this reason, stored variables persist for a long time and, at first glance, it seems pointless to free up variable storage (and unclear what `free up' even means).
@@
 For this reason, some EVM operations cost a negative amount of gas.
-That is, the gas is refunded to the sender at the end of the transaction, however (1) the refund is capped at 50\% of the total gas cost of the transaction, and (2) the block gas limit applies to the pre-refunded amount (\ie a transaction receiving a full refund can cost up to 5.5M gas with an 11M limit).
+That is, the gas is \textit{refunded} to the sender at the end of the transaction, however (1) the refund is capped at 50\% of the total gas cost of the transaction, and (2) the block gas limit applies to the pre-refunded amount (\ie a transaction receiving a full refund can cost up to 5.5M gas with an 11M limit).
 Negative gas operations include:
@@
 
-\section{Roll-ups: Additional Background}
+\subsection{Trade Execution Systems}
+\label{app:markets}
+
+\paragraph{Centralized Exchanges (CEX).} Traditional financial markets (\eg NYSE and NASDAQ) use order-matching systems to arrange trades.
+An exchange will list one or more assets (stocks, bonds, derivatives, or more exotic securities) to be traded with each other, given its own order book priced in a currency (\eg USD).
+Exchanges for blockchain-based assets (also called crypto assets by enthusiasts) can operate the same way, using a centralized exchange (CEX) design where a firm (\eg Binance, Bitfinex, \etc) operates the platform as a trusted third party in every aspect: custodianship over assets/currency being traded, exchanging assets fairly, offering the best possible price execution.
+Security breaches and fraud in centralized exchanges  (\eg MtGox~\cite{TheHisto45:online}, QuadrigaCX~\cite{SEBIOrde83:online}, and many others) have become a common source of lost funds for users, while accusations of unfair trade execution have been levelled but are difficult to prove.
+Today, CEXes are often regulated as other money service businesses---this provides some ability for the government to conduct financial tracking but does little to provide consumer protection against fraud.
+
+\paragraph{On-chain Order Books.} For trades between two blockchain-based assets (\eg a digital asset priced in a cryptocurrency, stablecoin, or second digital asset), order matching can be performed `on-chain' by deploying the order-matching system either on a dedicated blockchain or inside a decentralized application (DApp).
+In this model, traders entrust their assets to an autonomously operating DApp with known source code instead of a third party custodian that can abscond with or lose the funds.
+The trading rules will operate as coded, clearing and settling can be guaranteed, and order submission is handled by the blockchain---a reasonably fair and transparent system (but see front-running below).
+Finally, anyone can create an on-chain order book for any asset (on the same chain) at any time.
+While these sound ideal, performance is a substantial issue and the main subject of this paper.
+Since it is an open system, there is no obvious regulatory hook (beyond the blockchain itself).
+
+In this paper, we focus on benchmarking an order book for the public blockchain Ethereum.
+Ethereum is widely used and we stand to learn the most from working in a performance-hostile environment.
+Exchanges could be given their own dedicated blockchain, where trade execution logic can be coded into the network protocol.
+Trading systems on permissioned blockchains (\eg NASDAQ Linq, tZero) can also improve execution time and throughput, but they reduce user transparency and trust if unregulated.
+
+\paragraph{On-chain Dealers.} An advantage of on-chain trading is that other smart contracts, not just human users, can initiate trades, enabling broader decentralized finance (DeFi) applications.
+This has fuelled a resurgence in on-chain exchange but through a quote-driven design rather than an order-driven one.
+Automated market makers  (\eg Uniswap v3) have all the trust advantages of an on-chain order book, plus they are relatively more efficient.
+The trade-off is that they operate as a dealer---the DApp exchanges assets from its own inventory.
+This inventory is loaded into the DApp by an investor who will not profit from the trades themselves but hopes their losses (termed `impermanent losses') are offset over the long-term by trading fees.
+By contrast, an order book requires no upfront inventory and trading fees are optional.
+Finally, there is a complicated difference in their price dynamics (\eg market impact of a trade, slippage between the best bid/ask and actual average execution price, \etc)---deserving of an entire research paper to precisely define.
+We leave it as an assertion that with equal liquidity, order books have more favorable price dynamics for traders.
+
+\paragraph{Hybrid Designs.} Before on-chain dealers became prominent in the late 2010s, the most popular design was hybrid order-driven exchanges with some trusted off-chain components and some on-chain functionalities.
+Such decentralized exchanges (DEXes) were envisioned as operating fully on-chain, but performance limitations drove developers to move key components, such as the order matching system, off-chain to a centralized database.
+A landscape of DEX designs exist (\eg EtherDelta, 0x, IDEX, \etc): many avoid taking custodianship of assets off-chain, and virtually all (for order-driven markets) operate the order book itself off-chain (a regulatory hook).
+A non-custodial DEX solves the big issue of a CEX---the operator stealing the funds---however trade execution is still not provably fair, funds can still be indirectly stolen by a malicious exchange executing unauthorized trades, and server downtime is a common frustration for traders.
+An enhancement is to prove that trade execution is correct (\eg Loopring) but these proofs have blind spots (discussed in section~\ref{sec:rollups}).
+
+\subsection{Optimistic Roll-Ups}
 \label{app:rollup}
+
+\begin{figure}[t]
+\centering
+\includegraphics[width=1\textwidth]{fig/lissyL2.pdf}
+\caption{\footnotesize{\cm L2 Diagram}  \label{fig:lissyl2}}
+\end{figure}
 
@@
 
-\section{Cleaning Up Revisited}
+\section{Cleaning Up Revisited: Clearing Mappings}
 \label{app:clean}
 
-Beyond the cleaning up issues with priority queues in Section~\ref{sec:gasrefund}, \textblue{\cm also uses mappings with each market}.
+Beyond the cleaning up issues with priority queues in Section~\ref{sec:gasrefund}, \cm also uses mappings with each market.
 Traders preload their account with tokens to be traded (which comply with a common token standard called ERC20) and/or ETH.

### 2021-09-10 LaTeX-LNCS-2022/sections/paper.tex
top matter [19 pages total]

@@
 % !TEX root = ../main.tex
-
-\section{Introductory Remarks}
 
@@
 
-For better or worse, blockchain technologies like Ethereum have dramatically lowered the barrier to entry for developing and deploying financial technology.
+\section{Introductory Remarks}
+
+There are three main approaches to arranging a trade~\cite{Har03}.
+In a \emph{quote-driven} market, a dealer uses its own inventory to offer a price for buying or selling an asset.
+In a \emph{brokered exchange}, a broker finds a buyer and seller.
+In an \emph{order-driven} market, offers to buy (\emph{bids}) and sell (\emph{offers}/\emph{asks}) from many traders are placed as orders in an order book.
+Order-driven markets can be \emph{continuous}, with buyers/sellers at any time adding orders to the order book (\emph{makers}) or executing against an existing order (\emph{takers}); or they can be \emph{called}, where all traders submit orders within a window of time and orders are matched in a batch (like an auction).
+
+Conventional financial markets (\eg NYSE, NASDAQ) use both continuous time trading during open hours, and a call market before and during open hours to establish an opening price and a closing price.
+After early experiments at implementing continuous time trading on Ethereum (\eg EtherDelta, OasisDEX), it was generally accepted that conventional trading is infeasible on Ethereum for performance reasons.
+Centralized exchanges continued their predominance, while slowly some exchanges moved partial functionality on-chain (\eg custody of assets) while executing trades off-chain.
+
+A clever quote-driven alternative, called an automatic market maker (AMM), was developed that only requires data structures and traversals with low gas-complexity.
+This approach has undesirable price dynamics (\eg market impact of a trade, slippage between the best bid/ask and actual average execution price, \etc) which explains why there is no Wall Street equivalent, however it is efficient on Ethereum and works `good enough' to attract trading.
+First generation AMMs provide makers (called liquidity providers) with no ability to act on price information---they are uninformed traders that can only lose (called impermanent loss) on trades but make money on fees.
+Current generation AMMs (\eg Uniswap v3) provided informed makers with a limited ability (called concentrated liquidity) to act on proprietary information without breaking Ethereum's performance limitations.
+Ironically, the logical extension of this is a move back to where it all started---a full-fledged order-driven exchange that allows informed makers the fullest ability to trade strategically.
+
+%For better or worse, blockchain technologies like Ethereum have dramatically lowered the barrier to entry for developing and deploying financial technology.
 New tokens have been launched with a few clicks of a user interface, and large investment infrastructures have been developed and deployed with little regulatory oversight.
@@
 
-Financial regulators seek to provide consumer protection during the issuing and trading of financial products and assets.
+%Financial regulators seek to provide consumer protection during the issuing and trading of financial products and assets.
 They are concerned by their limited ability to intervene when trading is conducted on decentralized networks that, like Ethereum, run on the open internet.
@@
 
-Our research group is actively collaborating with our jurisdiction's financial regulator (name withheld for anonymity) to help them forecast how trading can be impacted by blockchain technology.
+%Our research group is actively collaborating with our jurisdiction's financial regulator (name withheld for anonymity) to help them forecast how trading can be impacted by blockchain technology.
 This paper addresses their concerns about the feasibility of a `worst-case scenario' where a trading platform is anonymously deployed on a public blockchain, like Ethereum, and runs autonomously without any further intervention from an externally visible entity.
@@
 
-\textbf{Contributions.} We study fully on-chain markets through design and implementation with Solidity---a high-level programming language for Ethereum that is syntactically similar to Java.
-We choose Ethereum as a hostile environment for an order book: Ethereum is fully decentralized (hardest to regulate), network participation is open to anyone on the internet (strongest adversarial model), and, as a result, it is slow (a lower-bound benchmark).
+\textbf{Contributions.} In this paper, we experiment with on-chain markets to understand in detail if they remain infeasible on Ethereum and what the limiting factors are.
+Some highlights from our research include answering the following questions:
+\begin{itemize}
+\item What type of exchange has the best properties on balance? (A call market.)
+\item How many orders can be processed on-chain? (Upper-bounded by 152 per block.)
+\item How much efficiency can be squeezed from diligently choosing the best data structures? (Somewhat limited: turn 38 trades into 152.)
+\item To what extent can we mitigate front-running attacks? (Almost entirely.)
+\item Can we stop the exchange's storage footprint on Ethereum from bloating? (Yes, but it is so expensive that it is not worth it.)
+\item Are on-chain order books feasible on layer 2? (Yes! Optimistic roll-ups reduce gas costs by 99.88\%.)
+\item Which aspects of Ethereum were encountered that required deeper than surface-level knowledge to navigate?
+(Optimizing gas refunds, Solidity is not truly object-oriented, miner extractable value (MEV) can be leveraged for good, \textblue{add more?})
+\item How hard is an on-chain exchange to regulate? (The design leaves almost no regulatory hooks beyond miners and sequencers on layer 2.)
+\end{itemize}
+
+ % design and implementation with Solidity---a high-level programming language for Ethereum that is syntactically similar to Java.
+
+ % We choose Ethereum as a hostile environment for an order book: Ethereum is fully decentralized (hardest to regulate), network participation is open to anyone on the internet (strongest adversarial model), and, as a result, it is slow (a lower-bound benchmark).
 Generally, if an application is feasible on Ethereum, it will also be feasible and only run faster on a private (or permissioned) blockchain (\eg Hyperledger), which is a blockchain operated by authorized network nodes only, generally visible to regulators.
 
-Our proof of concept, \cm, is an extensible base class suitable for experiments.
+% Our proof of concept, \cm, is an extensible base class suitable for experiments.
 \cm is designed from a security perspective: users only trust their assets to \cm's auditable code (non-custodial) and not to a third party, all operations are transparent, and we nearly eliminate the ability for adversarial network nodes to profit from front-running orders (see Section~\ref{sec:front} for in-depth front-running analysis).
@@
 
-While Solidity and its compiled bytecode is like many common programming languages, it also has quirks that require experimentation to best optimize performance (\eg factoring in the gas costs of operations, gas refunds, limits to Solidity's object-oriented design, clearing mappings, \etc).
+%While Solidity and its compiled bytecode is like many common programming languages, it also has quirks that require experimentation to best optimize performance (\eg factoring in the gas costs of operations, gas refunds, limits to Solidity's object-oriented design, clearing mappings, \etc).
 We test five priority queues---the core data structure of the call market---and various options for cleaning up our data once finished with it.
@@
 
-We also speculate that Ethereum is likely to improve vastly in the coming years and we demonstrate one avenue for improvement through `roll-ups'~\cite{kalodner2018arbitrum} which reduce the gas costs of \cm by more than 99.9\%.
+%We also speculate that Ethereum is likely to improve vastly in the coming years and we demonstrate one avenue for improvement through `roll-ups'~\cite{kalodner2018arbitrum} which reduce the gas costs of \cm by more than 99.9\%.
 While roll-ups are not fully on-chain and introduce new network participants, the roll-up architecture is still concerning to regulators because the participants (called validators) are not directly reachable by users; they only watch the Ethereum state and interact directly with Ethereum.
@@
 
-\subsection{Ethereum and Blockchain Technology}
+\subsection{Ethereum}
 
-A public blockchain is an open peer-to-peer network that maintains a set of transactions without a single entity in charge.
-In Ethereum, \emph{transactions} encode the bytecode of user-written \emph{decentralized applications (DApps)} to be stored on the blockchain; and the function calls made to the DApp.
-Every execution of every function call is validated by all honest, participating nodes to correct; a property that is robust against a fraction of faulty and malicious network nodes (or more precisely, their accumulated computational power).
-Once transactions are agreed upon, all honest participants will have identical sets of transactions in the same order.
-For Ethereum, this is conceptualized as the current state of a large \emph{virtual machine (EVM)} that is running many DApps.
+We assume the reader is familiar with the following concepts: blockchain technology; smart contracts and decentralized applications (DApps) on Ethereum; how Ethereum transactions are structured, broadcasted, and finalized; the gas model including the gas limit (approximately 11M gwei at the time of our experiments) per block.
+A \textbf{gas refund} is a more esoteric subject (not covered thoroughly in any academic work to our knowledge) that we use heavily in our optimizations.
+Briefly, certain EVM operations (\texttt{SELFDESTRUCT} and \texttt{SSTORE 0}) cost negative gas, with the follow caveats: the refund is capped at 50\% of the total gas cost of the transaction, and (2) the block gas limit applies to the pre-refunded amount (\ie a transaction receiving a full refund can cost up to 5.5M gas with an 11M limit).
+We provide full details of all of these topics in Appendix~\ref{app:back}.
 
-Transactions are broadcast by users to the blockchain network where they are propagated to all nodes.
-Nodes that choose to \emph{mine} will collect transactions (in the order of their choosing) into a block, and will attempt to have the network reach a consensus that their block should be added to the set (or chain) of previous blocks.
-A transaction is considered finalized once consensus on its inclusion has held for several additional blocks.
-
-%\textbf{Ethereum's Gas Model.} Every transaction results in the participating nodes having to execute bytecode.
-This is not free.
-When a transaction is executed, each opcode in the execution path accrues a fixed, pre-specified amount of \emph{gas}.
-The function caller will pledge to pay a certain amount of Ethereum's internal currency \emph{ETH} (typically quoted in units of Gwei which is one billionth of an ETH) per unit of gas, and miners are free to choose to execute that transaction or ignore it.
-The function caller is charged for exactly what the transaction costs to execute, and they cap the maximum they are willing to be charged (\textit{gas limit}).
-If the cap is too low to complete the execution, the miner keeps the Gwei and \emph{reverts} the state of the EVM (as if the function never ran).
-%
-%A miner can include as many transactions (typically preferring transactions that bid the highest for gas) that can fit under a pre-specified \textit{block gas limit}, which is algorithmically adjusted for every block.
-As of the time of writing, the limit is approximately 11M gas.
-Essentially, our main research question is how many on-chain trades can be executed without exceeding that limit.
-Later, we also discuss several bytecode operations (\emph{opcodes}) that refund gas (\ie cost negative gas), which we heavily utilize in our optimizations.
 \subsection{Trade Execution Systems}
 
-There are three main approaches to arranging a trade~\cite{Har03}.
-In a \emph{quote-driven} market, a dealer uses its own inventory to offer a price for buying or selling an asset.
-In a \emph{brokered exchange}, a broker finds a buyer and seller.
-In an \emph{order-driven} market, offers to buy (\emph{bids}) and sell (\emph{offers}/\emph{asks}) from many traders are placed as orders in an order book.
-Order-driven markets can be \emph{continuous}, with buyers/sellers at any time adding orders to the order book (\emph{makers}) or executing against an existing order (\emph{takers}); or they can be \emph{called}, where all traders submit orders within a window of time and orders are matched in a batch (like an auction).
-Table~\ref{tab:eval2} illustrates various trade execution systems and summerizes their advantages and disadvantages.
+\input{tables/eval2.tex}
 
-\input{tables/eval2.tex}
-%========================Following section is already covered in the table========================%
-%\subsection{Trading Blockchain-Based Assets}
-%
-%\paragraph{Centralized Exchanges (CEX)}Traditional financial markets (\eg NYSE and NASDAQ) use order-matching systems to arrange trades.
-An exchange will list one or more assets (stocks, bonds, derivatives, or more exotic securities) to be traded with each other, given its own order book priced in a currency (\eg USD).
-Exchanges for blockchain-based assets (also called crypto assets by enthusiasts) can operate the same way, using a centralized exchange (CEX) design where a firm (\eg Binance, Bitfinex, \etc) operates the platform as a trusted third party in every aspect: custodianship over assets/currency being traded, exchanging assets fairly, offering the best possible price execution.
-Security breaches and fraud in centralized exchanges  (\eg MtGox~\cite{TheHisto45:online}, QuadrigaCX~\cite{SEBIOrde83:online}, and many others) have become a common source of lost funds for users, while accusations of unfair trade execution have been levelled but are difficult to prove.
-Today, CEXes are often regulated as other money service businesses---this provides some ability for the government to conduct financial tracking but does little to provide consumer protection against fraud.
-%
-%\paragraph{On-chain Order Books.} For trades between two blockchain-based assets (\eg a digital asset priced in a cryptocurrency, stablecoin, or second digital asset), order matching can be performed `on-chain' by deploying the order-matching system either on a dedicated blockchain or inside a decentralized application (DApp).
-In this model, traders entrust their assets to an autonomously operating DApp with known source code instead of a third party custodian that can abscond with or lose the funds.
-The trading rules will operate as coded, clearing and settling can be guaranteed, and order submission is handled by the blockchain---a reasonably fair and transparent system (but see front-running below).
-Finally, anyone can create an on-chain order book for any asset (on the same chain) at any time.
-While these sound ideal, performance is a substantial issue and the main subject of this paper.
-Since it is an open system, there is no obvious regulatory hook (beyond the blockchain itself).
-%
-%In this paper, we focus on benchmarking an order book for the public blockchain Ethereum.
-Ethereum is widely used and we stand to learn the most from working in a performance-hostile environment.
-Exchanges could be given their own dedicated blockchain, where trade execution logic can be coded into the network protocol.
-Trading systems on permissioned blockchains (\eg NASDAQ Linq, tZero) can also improve execution time and throughput, but they reduce user transparency and trust if unregulated.
-%
-%\paragraph{On-chain Dealers.} An advantage of on-chain trading is that other smart contracts, not just human users, can initiate trades, enabling broader decentralized finance (DeFi) applications.
-This has fuelled a resurgence in on-chain exchange but through a quote-driven design rather than an order-driven one.
-Automated market makers  (\eg Uniswap v3) have all the trust advantages of an on-chain order book, plus they are relatively more efficient.
-The trade-off is that they operate as a dealer---the DApp exchanges assets from its own inventory.
-This inventory is loaded into the DApp by an investor who will not profit from the trades themselves but hopes their losses (termed `impermanent losses') are offset over the long-term by trading fees.
-By contrast, an order book requires no upfront inventory and trading fees are optional.
-Finally, there is a complicated difference in their price dynamics (\eg market impact of a trade, slippage between the best bid/ask and actual average execution price, \etc)---deserving of an entire research paper to precisely define.
-We leave it as an assertion that with equal liquidity, order books have more favorable price dynamics for traders.
-%
-%\paragraph{Hybrid Designs.} Before on-chain dealers became prominent in the late 2010s, the most popular design was hybrid order-driven exchanges with some trusted off-chain components and some on-chain functionalities.
-Such decentralized exchanges (DEXes) were envisioned as operating fully on-chain, but performance limitations drove developers to move key components, such as the order matching system, off-chain to a centralized database.
-A landscape of DEX designs exist (\eg EtherDelta, 0x, IDEX, \etc): many avoid taking custodianship of assets off-chain, and virtually all (for order-driven markets) operate the order book itself off-chain (a regulatory hook).
-A non-custodial DEX solves the big issue of a CEX---the operator stealing the funds---however trade execution is still not provably fair, funds can still be indirectly stolen by a malicious exchange executing unauthorized trades, and server downtime is a common frustration for traders.
-An enhancement is to prove that trade execution is correct (\eg Loopring) but these proofs have blind spots (discussed in section~\ref{sec:rollups}).
+Table~\ref{tab:eval2} illustrates various trade execution systems and summarizes their advantages and disadvantages.
+Appendix~\ref{app:markets} provides a full justification for the table.
+Briefly, fully decentralized, on-chain exchanges require the lowest trust, provide instant settlement, and have transparent trading rules that will always execute correctly.
+Front-running attacks (see Section~\ref{sec:front} for a very thorough discussion) are a weakness inherent in blockchains that require specific mitigation.
 
-\subsection{Related Works}
+\subsection{Related Work}
 
-\paragraph{Blockchain Limitations and Solution.} While an order book is a ledger and blockchains provide a distributed ledger, it is not straightforward to drop a continuous-time order book onto a blockchain.
+Call markets are studied widely in finance and provide high integrity prices (\eg closing prices that are highly referenced and used in derivative products)~\cite{HS04,PS03,FH21}.
+They can also combat high frequency trading~\cite{budish2015high,aquilina2020quantifying}.
+An older 2014 paper~\cite{clark2014decentralizing} on the `Princeton prediction market'~\cite{Bra13} show that call markets  mitigate most blockchain-based front-running attacks present in an on-chain continuous-trading exchange as well as other limitations: block intervals are slow and not continuous, there is no support for accurate time-stamping, transactions can be dropped or reordered by miners, and fast traders can react to submitted orders/cancellations when broadcast to network but not in a block and have their orders appear first.
+The paper does not include an implementation, was envisioned as running on a custom blockchain (Ethereum was still in development in 2014) and market operations are part of the blockchain logic.
+
+%\paragraph{Blockchain Limitations and Solution.} While an order book is a ledger and blockchains provide a distributed ledger, it is not straightforward to drop a continuous-time order book onto a blockchain.
 An older 2014 paper~\cite{clark2014decentralizing} on the `Princeton prediction market'~\cite{Bra13} motivates our work.
 The authors observe the following limitations of on-chain continuous order books: block intervals are slow and not continuous, there is no support for accurate time-stamping, transactions can be dropped or reordered by miners, and fast traders can react to submitted orders/cancellations when broadcast to network but not in a block and have their orders appear first (as examined in later work on front-running: \cite{eskandari2019sok,daian2019flash}).
-
-\paragraph{Call Markets.} The researchers propose using a call market instead of a continuous-time market~\cite{clark2014decentralizing}.
+%
+%\paragraph{Call Markets.} The researchers propose using a call market instead of a continuous-time market~\cite{clark2014decentralizing}.
 Orders are collected and placed into the order book over a window of time (\eg 1 or more blocks), then the market is closed and the orders are processed in batch: the best bids are matched to the best asks in order.
@@
 The paper does not include an implementation, was envisioned as running on a custom blockchain (Ethereum was still in development in 2014) and market operations are part of the blockchain logic.
-
-Large exchanges, like the NYSE and NASDAQ, run two call markets every trading day in parallel with a continuous-time market.
+%
+%Large exchanges, like the NYSE and NASDAQ, run two call markets every trading day in parallel with a continuous-time market.
 One call market closes at market open to produce the opening price for each stock, while the other closes at the end of the day to produce the closing price.
@@
 
-\paragraph{Other Academic Literature.}
-
 The most similar academic work to this paper is the Ethereum-based periodic auction by Galal \etal~\cite{galalpublicly} and the continuous-time exchange TEX~\cite{khalil2019tex}.
@@
 In a recent SoK on front-running attacks in blockchain~\cite{eskandari2019sok}, three general mitigations are proposed.
-Both of these papers use the solution of providing confidentiality over the content of orders.
+Both of these papers use the solution of providing confidentiality over the content of orders~\cite{TP07,YSLT10,TW12,cartlidge2019mpc,massacci2018futuresmex}.
 The main downside is that honest traders cannot submit their orders and leave, they must interact in a second round to reveal their orders.
@@
 A detailed comparison of front-running is provided in Section~\ref{sec:front}.
-
 Our paper also emphasizes implementation details: Galal \etal do not provide a full implementation, and TEX uses both on-chain and off-chain components, and thus does not answer our research question of how feasible an on-chain order book is.
-
-Less related are papers on topics tangential to the mechanics of trade execution.
-Early (and some recent) literature consider trade execution under encryption (\ie dark markets) for securities~\cite{TP07,YSLT10,TW12,cartlidge2019mpc} and futures~\cite{massacci2018futuresmex}.
-Velocity~\cite{eskandari2017feasibility} and Findel~\cite{biryukov2017findel} consider structuring derivatives in smart contracts.
-Atomic swaps (\ie payment vs.
-delivery) are necessary for settling trades and some general approaches include Arwen~\cite{heilman2020arwen} and Tesseract~\cite{bentov2017tesseract}.
-
-% https://eprint.iacr.org/2020/269.pdf
-% Wendy, the Good Little Fairness Widget – Achieving Order Fairness for Blockchains
 
@@
 
+%For better or worse, blockchain technologies like Ethereum have dramatically lowered the barrier to entry for developing and deploying financial technology.
+New tokens have been launched with a few clicks of a user interface, and large investment infrastructures have been developed and deployed with little regulatory oversight.
+Blockchain exchange services allow order-based trading of digital currencies, tokens, and other digital assets.
+Such exchanges are key components to blockchain-based economic activity.
+
+%Financial regulators seek to provide consumer protection during the issuing and trading of financial products and assets.
+They are concerned by their limited ability to intervene when trading is conducted on decentralized networks that, like Ethereum, run on the open internet.
+Order-driven trading can happen fully `on-chain' and this was experimented within the early days of Ethereum, but it has been largely abandoned for performance reasons in favor of running on centralized servers.
+More specifically, the core functionality is performed off-chain (\eg matching orders) while other aspects (\eg loading accounts, order cancellation) might be performed on-chain.
+In this world, company names, employees, addresses, and publicly addressable servers all provide regulatory hooks.
+
+% Final camera-ready
+% JC: Our research group is actively collaborating with our jurisdiction's (Quebec, Canada) financial regulator, the Autorité des Marchés Financiers (AMF), to help them forecast how trading can be impacted by blockchain technology.
+
+%Our research group is actively collaborating with our jurisdiction's financial regulator (name withheld for anonymity) to help them forecast how trading can be impacted by blockchain technology.
+This paper addresses their concerns about the feasibility of a `worst-case scenario' where a trading platform is anonymously deployed on a public blockchain, like Ethereum, and runs autonomously without any further intervention from an externally visible entity.
+Such a design appears feasible but is considered too slow.
+Together, we agreed it is a very good time to do a deep dive into understanding precisely \textit{how slow} for the following reasons: (1) public blockchains are becoming faster (both in theory and in practice) providing future efficiency gains for on-chain trading, (2) demand for on-chain trading is exemplified by the recent popularity of dealer quote-based trading like Uniswap and Curve Finance (reviewed below), and (3) stablecoins have become popular and allow on-chain trading with pricing in USD, alleviating another regulatory hook: the need for platforms to maintain traditional accounts for holding governmental currency and interfacing with the banking system.
+
 %ACK

### 2021-09-10 LaTeX-LNCS-2022/tables/eval2.tex
arbitrum texts updated + mind map penciled in + random edits
top matter [19 pages total]

@@
 % !TEX root = ../main.tex
- \newcolumntype{P}[1]{>{\centering\arraybackslash}p{#1}}
 % = = = = = = = = = = = = = = = = = = = = =Call market operations Table = = = = = = = = = = = =  = = = = = =  %
 \begin{table}[t]
-%\setlength{\tabcolsep}{0.7\tabcolsep}% Shrink \tabcolsep
-
 \centering
 \scriptsize
-%\begin{tabular}{|>{\centering}m{3cm} |>{\centering}m{3cm} |>{\centering}m{3cm} |>{\centering}m{4cm} |}
-\begin{tabular}{|c|c|c|c|}
+\begin{tabular}{|p{1.5cm}|p{3cm}|p{3.5cm}|p{3.5cm}|}
 
 \hline
-\textbf{Exchange Platform}			 &\textbf{Description}   				& \textbf{Advantages}      				& \textbf{Disadvantages}                   \\ \hline
+\textbf{Type}			 &\textbf{Description}   				& \textbf{Advantages}      				& \textbf{Disadvantages}                   \\ \hline
 
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = == = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = == = = = = = = = = = = = = = = = = = = = = = = = = == = = = = =%
-\multirow{4}{*}{\shortstack{Centralized \\Exchanges}}                            & \multirow{4}{*}{\shortstack{Exchange acts as a \\trusted third party\\ between traders}} 	& High Liquidity			& Third party custodian				\\
-											&																		& High trade performance		& Low security				\\ 
-											 &																		& Low price slippage		& No instant settlement	 		\\
-											 &																		& Easy to regulate			& Server downtime							\\ \hline
+% = = = = = = = = = = = =%
+Centralized Exchanges (CEX)
+& Order-driven exchange acts as a trusted third party (\eg Binance, Bitfinex)
+& Conventional \newline
+Highest performance \newline
+Low fees \newline
+Easy to regulate \newline
+Low price slippage  \newline
+Verbose trading strategies 
+&  Fully trusted custodian \newline
+Slow withdrawals \newline
+Server downtime \newline
+Uncertain fair execution 
+\\ 
+\hline
 
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = == = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = == = = = = = = = = = = = = = = = = = = = = = = = = == = = = = =%
-\multirow{6}{*}{\shortstack{On-chain \\Order Books}}                         		& \multirow{6}{*}{\shortstack{Exchange operates\\fully \\on-chain as coded}}	& High security							&	\\
-												&																		& Non-custodial						& 					\\
-												&																		& No trusted third party					& Low trade performance						\\
-												&																		& Fully Autonomous						&Hard to regulate			\\
-												&																		& No Impermanent Loss					&					\\
-												&																		& Low price slippage					&					\\ \hline
+% = = = = = = = = = = = =%
+Partially On-chain Exchange
+& Order-driven exchange acts as a semi-trusted (\eg EtherDelta, 0x, IDEX, Loopring)
+&  High performance \newline
+Low fees \newline
+Easy to regulate \newline
+Low price slippage \newline
+Verbose trading strategies \newline
+Semi-custodial
+& 
+Slow withdrawals \newline
+Server downtime \newline
+Front-running attacks \newline
+Uncertain fair execution
+\\ 
+\hline
 
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = == = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = == = = = = = = = = = = = = = = = = = = = = = = = = == = = = = =%
-\multirow{5}{*}{\shortstack{On-chain \\Dealers} }                     	 & \multirow{5}{*}{ \shortstack{A dealer uses its \\own inventory to offer \\a price for assets \\being traded}}	& High security				& 				\\
-											&																						& Non-custodial			&  Impermanent Loss\\
-											&																						& No trusted third party		&	High price slippage				\\
-											&																						& Fully Autonomous			&	 No support for limit orders			\\
-											&																						& High performance			&					\\ \hline
+% = = = = = = = = = = = =%
+On-Chain Dealers
+& Quote-driven decentralized exchange trades from inventory with public pricing rule (\eg Uniswap v3)
+&  Non-custodial \newline
+Instant settlement \newline
+Moderate performance \newline
+Fair execution 
+&  Unconventional \newline
+Impermanent loss \newline
+High price slippage \newline
+Intrinsic fees \newline
+Front-running attacks \newline
+Limited trading strategies 
+\\ 
+\hline
 
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = == = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = == = = = = = = = = = = = = = = = = = = = = = = = = == = = = = =%
-\multirow{3}{*}{\shortstack{Hybrid\\ Designs}}                            &  \multirow{3}{*}{\shortstack{Exchange operates \\partially on-chain}}  								& High trade performance				& Low security										\\
-									&																									& Easy to regulate					& Server downtime \\
-									&																									& Non-custodial 					& \shortstack{Uncertain fair execution}	\\ \hline
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
+% = = = = = = = = = = = =%
+On-chain Order-Driven Exchanges 
+& Order-driven decentralized exchange executes trades between buyers and sellers (\eg \cm)
+&  Conventional \newline
+Non-custodial \newline
+Instant settlement \newline
+Low price slippage \newline
+Fair execution \newline
+Verbose trading strategies \newline
+Front-running is mitigable 
+& Very low performance \newline
+\\ 
+\hline
+
 \end{tabular}
-\caption{ A simple comparison among different trade execution systems.
+\caption{ Comparison among different trade execution systems.
 \label{tab:eval2}}

### 2021-09-10 LaTeX-LNCS-2022/sections/abstract.tex
abstract tweaks

@@
 Financial regulators have long-standing concerns about fully decentralized exchanges that run `on-chain' without any obvious regulatory hooks.
-Uniswap's open protocol and the next generation of such automated market makers (AMMs) made these concerns a reality.
-AMMs implement a lightweight dealer-based trading system, but it is unlike anything on Wall Street, requires fees intrinsically, and is susceptible to front-running attacks.
-This leaves the following research questions we address in this paper: (i) are conventional (\ie orderbooks) and secure (\ie resistant to front-running and price manipulation) exchanges feasible as a fully on-chain service on a public blockchain, (ii) what is the performance profile, and (iii) how much do Layer 2 techniques (\eg Arbitrum) increase performance?
-To answer these questions, we implement, benchmark, and experiment with an Ethereum-based call market (or batch auction) exchange called \cm, demonstrating many of Ethereum's nuances.
+The popularity of Uniswap, an automated market makers (AMM), made these concerns a reality.
+AMMs implement a lightweight dealer-based trading system, but they are unlike anything on Wall Street, require fees intrinsically, and are susceptible to front-running attacks.
+This leaves the following research questions we address in this paper: (i) are conventional (\ie orderbooks), secure (\ie resistant to front-running and price manipulation) and fully decentralized exchanges feasible on a public blockchain like Ethereum, (ii) what is the performance profile, and (iii) how much do Layer 2 techniques (\eg Arbitrum) increase performance?
+To answer these questions, we implement, benchmark, and experiment with an Ethereum-based call market exchange called \cm.
 We confirm the functionality is too heavy for Ethereum today (you cannot expect to exceed a few hundred trade executions per block) but show it scales dramatically (99.88\% gas cost reduction) on Arbitrum.

### 2021-09-10 LaTeX-LNCS-2022/sections/appendix.tex
morre changes

@@
 This operation loads a storage slot with a value.
-Using \texttt{SSTORE} to load a zero into a storage slot means the nodes can start ignoring it (recall that all variables, even if uninitialized, have zero by default).
+Using \texttt{SSTORE} to load a zero into a storage slot with a non-zero value means the nodes can start ignoring it (recall that all variables, even if uninitialized, have zero by default).
 Doing this refunds 15,000 gas per slot.
@@
 \end{itemize}
+
+At the time of this writing, Ethereum transaction receipts only account for the \texttt{gasUsed}, which is the total amount of gas units spent during a transaction, and users are not able to obtain the value of the EVM's refund counter from inside the EVM~\cite{signer2018gas}.
+So in order to account for refunds in  Tables~\ref{tab:PQUnitTests}, we calculate them manually.
+First, we determine exactly how many storage slots are being cleared or how many smart contracts are being destroyed, then we multiply these numbers by 24,000 or 15,000 respectively.
 

### 2021-09-10 LaTeX-LNCS-2022/sections/paper.tex
abstract tweaks
morre changes

@@
 First generation AMMs provide makers (called liquidity providers) with no ability to act on price information---they are uninformed traders that can only lose (called impermanent loss) on trades but make money on fees.
-Current generation AMMs (\eg Uniswap v3) provided informed makers with a limited ability (called concentrated liquidity) to act on proprietary information without breaking Ethereum's performance limitations.
+Current generation AMMs (\eg Uniswap v3) provided informed makers with a limited ability (called concentrated liquidity) to act on proprietary information~\cite{Park21} without breaking Ethereum's performance limitations.
 Ironically, the logical extension of this is a move back to where it all started---a full-fledged order-driven exchange that allows informed makers the fullest ability to trade strategically.
@@
 (Optimizing gas refunds, Solidity is not truly object-oriented, miner extractable value (MEV) can be leveraged for good, \textblue{add more?})
-\item How hard is an on-chain exchange to regulate? (The design leaves almost no regulatory hooks beyond miners and sequencers on layer 2.)
+\item How hard is an on-chain exchange to regulate? (The design leaves almost no regulatory hooks beyond miners (and sequencers on layer 2).)
 \end{itemize}
@@
 
-%\paragraph{Blockchain Limitations and Solution.} While an order book is a ledger and blockchains provide a distributed ledger, it is not straightforward to drop a continuous-time order book onto a blockchain.
-An older 2014 paper~\cite{clark2014decentralizing} on the `Princeton prediction market'~\cite{Bra13} motivates our work.
-The authors observe the following limitations of on-chain continuous order books: block intervals are slow and not continuous, there is no support for accurate time-stamping, transactions can be dropped or reordered by miners, and fast traders can react to submitted orders/cancellations when broadcast to network but not in a block and have their orders appear first (as examined in later work on front-running: \cite{eskandari2019sok,daian2019flash}).
-%
-%\paragraph{Call Markets.} The researchers propose using a call market instead of a continuous-time market~\cite{clark2014decentralizing}.
-Orders are collected and placed into the order book over a window of time (\eg 1 or more blocks), then the market is closed and the orders are processed in batch: the best bids are matched to the best asks in order.
-If the prices overlap, the miner keeps the difference (which they could extract regardless through front-running).
-Call markets largely side step front-running attacks from other traders because reordering trades has no impact (discussed more in section~\ref{sec:front}).
-The paper does not include an implementation, was envisioned as running on a custom blockchain (Ethereum was still in development in 2014) and market operations are part of the blockchain logic.
-%
-%Large exchanges, like the NYSE and NASDAQ, run two call markets every trading day in parallel with a continuous-time market.
-One call market closes at market open to produce the opening price for each stock, while the other closes at the end of the day to produce the closing price.
-Other exchanges, called crossing networks, also operate as a call market at various times throughout the trading day.\footnote{A crossing network uses a secondary market for determining the closing price.
-Many prominent crossing networks are operated internally within a brokerage for its clients, and often as a `dark pool' with an unpublished order book.} Call markets are studied widely in finance~\cite{Har03}, with recent interest in expanding their use to combat high frequency trading~\cite{budish2015high,aquilina2020quantifying}.
-Time-sensitive traders submit orders early, especially in crossing networks that close at a randomly determined time (traders risk missing the call if they wait too long).
-A blockchain happens to provide this function naturally, as blocks are published unpredictably.
-%Price-sensitive traders wait to base their pricing off the already submitted orders and do not mind missing a call if it obtains them a better price.
-
 The most similar academic work to this paper is the Ethereum-based periodic auction by Galal \etal~\cite{galalpublicly} and the continuous-time exchange TEX~\cite{khalil2019tex}.
 As with us, front-running is a main consideration of these works.
-In a recent SoK on front-running attacks in blockchain~\cite{eskandari2019sok}, three general mitigations are proposed.
-Both of these papers use the solution of providing confidentiality over the content of orders~\cite{TP07,YSLT10,TW12,cartlidge2019mpc,massacci2018futuresmex}.
+In a recent SoK on front-running attacks in blockchain~\cite{eskandari2019sok}, three general mitigations are proposed: confidentiality, sequencing, and design.
+Both of these papers use confidentiality over the content of orders~(\cf \cite{TP07,YSLT10,TW12,cartlidge2019mpc,massacci2018futuresmex}).
 The main downside is that honest traders cannot submit their orders and leave, they must interact in a second round to reveal their orders.
-The second mitigation approach is to sequence transactions according to some rule, either at the protocol level~\cite{kelkar2020order} or as a third-party service~\cite{Kla20} (a regulatory hook).
-These are very recent works and are not available for experimentation on Ethereum yet (although Chainlink has announced an intention\footnote{A.
+The second mitigation approach is to sequence transactions according to some rule akin to first-in-first-out~\cite{kelkar2020order,Kla20}.
+These are not available for experimentation on Ethereum yet (although Chainlink has announced an intention\footnote{A.
 Juels.
@@
 
-Our proof of concept, \cm, is a call market that will open for a specified period of time during which it will accept a capped number of orders (\eg 100 orders---parameterized so that all orders can be processed), and these orders are added to a priority queue (discussed in Section~\ref{sec:pq} ).
+For our experiments and measurements, we implement an exchange from scratch.
+\cm is a call market that will open for a specified period of time during which it will accept a capped number of orders (\eg 100 orders---parameterized so that all orders can be processed), and these orders are added to a priority queue (discussed in Section~\ref{sec:pq} ).
 Our vision is the market would be open for a very short period of time, close, and then reopen immediately (\eg every other block).
-\cm is open source and written in 336 lines (SLOC) of Solidity plus the priority queue (\eg a heap with dynamic array is 282 SLOC).
-We tested it with the Mocha testing framework using Truffle on Ganache-CLI to obtain our performance metrics.
+\cm is open source and written in 336 lines (SLOC) of Solidity plus the priority queue (\eg we implement 5 variants, each around 300 SLOC).
+We tested it with the Mocha testing framework using Truffle~\cite{TruffleO71:online} on Ganache-CLI~\cite{GanacheT25:online} to obtain our performance metrics.
 Once deployed, the bytecode of \cm is 10,812 bytes plus the constructor code (6,400 bytes) which is not stored.
@@
 It is visible and can be interacted with here: \href{https://rinkeby.etherscan.io/address/0x0d91de29c531d074853a5cef7cf9dfeb9c6ec4e0}{[etherscan.io]}.
-We cross-checked for vulnerabilities with \textit{Slither}\footnote{https://github.com/crytic/slither} and \textit{SmartCheck}\footnote{https://tool.smartdec.net} (it only fails some `informational' warnings that are intentional design choices---\eg a costly loop).
-Table~\ref{tab:cm_functions} summarizes \cm's primary operations.
-\textblue{Figuremindmap represents a design  landscape and extensions.}
+We cross-checked for vulnerabilities with \textit{Slither}\footnote{https://github.com/crytic/slither} and \textit{SmartCheck}\footnote{https://tool.smartdec.net} and it only fails some `informational' warnings that are intentional design choices (\eg a costly loop).
+All measurements assume a block gas limit of $11\,741\,495$ and 1 gas $=$ 56 Gwei.\footnote{EthStats (July 2020): \url{https://ethstats.net/}} Table~\ref{tab:cm_functions} summarizes \cm's primary operations.
+
+%\textblue{Figuremindmap represents a design  landscape and extensions.}
 
@@
 
-\input{tables/pq.tex}
+%\input{tables/pq.tex}
 
@@
 For a call market, closing the market and processing all the orders are the most time-consuming steps.
-The most critical design decision is the data structure for holding orders.
-While data structures are well-studied for many languages, Solidity/EVM has its own unique aspects (\eg gas refunds, a relatively cheap mapping data structure, only partial support for object-oriented programming) that create difficulties in assessing which will perform best without actually deploying and evaluating each variant.
+Assessing which data structures will perform best is hard (\eg gas refunds, a relatively cheap mapping data structure, only partial support for object-oriented programming) without actually deploying and evaluating several variants.
 
-When closing a call market, the orders are examined in order: highest to lowest price for bids, and lowest to highest price for asks.
-In most circumstances, the market closing algorithm does not have to consider any deeper bids/asks from the list when choosing whether the current best bid and ask can be fulfilled.
-The only exceptions are in the case of a tie on price or a cancelled order, both of which we return to later.
-For this reason, the ideal data structure for storing bids/asks is a \textit{priority queue} (see Table~\ref{tab:PQ_API}) where each order's priority is its price.
+We first observe that orders are executed in order: highest to lowest price for bids, and lowest to highest price for asks.
+This means random access to the data structure holding the orders is unnecessary (we discuss cancelling orders later in Section~\ref{sec:cancel}).
+We can use a lightweight \textit{priority queue} (PQ) which has only two functions: \textsf{Enqueue()} inserts an element into the priority queue; and \textsf{Dequeue()} removes and returns the highest priority element.
 Specifically, we use two PQs---one for bids, where the highest price is the highest priority, and one for asks, where the lowest price is the highest priority.
 
-There are numerous ways of implementing a PQ.
+As closing the market is very expensive with any PQ, we rule out sorting the elements while dequeuing and sort during each enqueue. We then implement the following 5 PQ variants:
+
+%There are numerous ways of implementing a PQ.
 A PQ has an underlying list---common options include a static array, dynamic array, and linked list.
@@
 
-\item \textbf{Heap with Dynamic Array.} A heap is a type of binary tree data structure that comes in two forms of a (i) Max-Heap and (ii) Min-Heap.
-All the nodes of the tree are in a specific order, and the root always represents the highest priority item of the data structure (the largest and smallest values in the Max-Heap and Min-Heap respectively).
-We implement a PQ with a heap that stores its data in a dynamically sized array.
+\item \textbf{Heap with Dynamic Array.} A heap is a binary tree where data is stored in nodes in a specific order where the root always represents the highest priority item (\ie highest bid price / lowest ask price).
+Our heap stores its data in a Solidity-provided dynamically sized array.
+The theoretic time complexity is logarithmic enqueue and logarithmic dequeue.
 
-\item \textbf{Heap with Static Array.} A heap can also be represented by a Solidity storage array in which the storage is statically allocated.
-To do this, we pass the required size of the array as a constructor parameter to the PQ smart contract.
+\item \textbf{Heap with Static Array.} This variant replaces the dynamic array with a Solidity storage array where the size is statically allocated.
+This is asymptotically the same and marginally faster in practice.
+% the size can be accurately predicted.
+has the same asympotic complexity.
+%To do this, we pass the required size of the array as a constructor parameter to the PQ smart contract.
 
-\item \textbf{Heap with Mapping.} In the above implementations, the entire order is stored (as a struct) in the heap.
-In this variant, we store the order struct in a Solidity mapping and store the mapping keys in the heap.
+\item \textbf{Heap with Mapping.} In this variant, we store a key for the order in the heap instead of the entire order itself.
+Once a key is dequeued, the order struct is drawn from a Solidity mapping (which stores key-value pairs very efficiently).
+This is asymptotically the same and faster with variable-sized data.
 
-\item \textbf{Linked List.} In this variant, we insert a new element into its correct position (based on its price) when running enqueue.
-The PQ itself stores elements in a linked list (enabling us to efficiently insert a new element between two existing elements).
-Solidity is described as object-oriented but the equivalent of an object is an entire smart contract.
+\item \textbf{Linked List.} In this variant, elements are stored in a linked list (enabling us to efficiently insert a new element between two existing elements during enqueue).
+Solidity is described as object-oriented but the Solidity equivalent of an object is an entire smart contract.
 Therefore, an object-oriented linked list must either (i) create each node in the list as a struct---but this is not possible as Solidity does not support recursive structs---or (ii) make every node in the list its own contract.
-The latter option seems wasteful and unusual, but it ends up being the most gas efficient data structure to dequeue.
-Thus, each node is its own contract and contains the incoming order's data and a pointer to the address of the next contract in the list.
+The latter option seems wasteful and unusual, but it surprisingly ends up being the most gas efficient data structure to dequeue.
+The theoretic time complexity is linear enqueue and constant dequeue.
 
@@
 The contract stores the key of the first node (head) and last node (tail) in the list.
+Asymptotically, it is linear enqueue and constant dequeue.
 
@@
 % = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
-
-\subsection{Priority Queue Evaluation}
-
-\paragraph{Enqueue Performance.} We implemented, deployed, and tested each PQ using the Truffle development framework~\cite{TruffleO71:online} and Ganache~\cite{GanacheT25:online}.
-We tried a variety of tests (including testing the full call market with each variant) with consistent results in performance.
-A simple test to showcase the performance profile is shown in Figure~\ref{fig:random_insertion}.
-We enqueue 50 integers chosen at random from a fixed interval in each PQ variant.
-The bigger the PQ gets, the longer enqueue takes---a linear increase for the linked list variants, and logarithmic for the heap variants.
+We implemented, deployed, and tested each PQ.
+A simple test of enqueuing 50 integers chosen at random from a fixed interval is in Figure~\ref{fig:random_insertion} and dequeing them all is in Table~\ref{tab:PQUnitTests}.
+Dequeuing removes data from the contract's storage resulting in a gas refund.
+Based on our manual estimates,\footnote{EVM does not expose the refund counter.
+We determine how many storage slots are being cleared and how many smart contracts destroyed, then we multiply these numbers by 24,000 or 15,000 respectively.} every variant receives the maximum gas refund possible (\ie half the total cost of the transaction).
+In other words, each of them actually consumes twice the \texttt{gasUsed} amount in gas before the refund.
+However, none of them are better or worse based on how much of a refund they generate.
 
@@
 
-\begin{figure}
+\begin{figure}[t]
 \begin{floatrow}
@@
 }{%
- \caption{\scriptsize{The gas metrics associated with dequeuing 50 integers from five priority queue variants.}
+ \caption{\scriptsize{The gas metrics associated with dequeuing 50 integers from five priority queue variants. Full refund amount is shown but the actual refund that is applied is capped.}
 \label{tab:PQUnitTests}}%
@@
 
-\paragraph{Dequeue Performance.} For each PQ variant storing 50 random integers, the \texttt{Dequeue()} function is iterated until the data structure is empty.
-The total gas cost for fully dequeuing the PQ variants is outlined in Table~\ref{tab:PQUnitTests}.
-These tests are performed using the following Ethereum gas metrics: block gas limit $=$11,741,495 and 1 gas $=$ 56 Gwei.\footnote{EthStats (July 2020): \url{https://ethstats.net/}} Dequeuing removes data from the contract's storage.
-Recall this results in a gas refund.
-Based on our manual estimates (EVM does not expose the refund counter), every variant receives the maximum gas refund possible (\ie half the total cost of the transaction).
-In other words, each of them actually consumes twice the \texttt{gasUsed} amount in gas before the refund.
-However, none of them are better or worse based on how much of a refund they generate.
-
-\paragraph{Discussion.} Based on enqueuing, the heap variants are the cheapest in terms of gas, while based on dequeuing, the link list variants are the cheapest.
-This is in accordance with the theoretical worst-case time complexity for each.
-However, (i) the linked list variants are materially cheaper than the heap variants at dequeuing, and (ii) dequeuing in a call market must be done as a batch, whereas enqueuing is paid for one at a time by the trader submitting the order, and (iii) Ethereum will not permit more than hundreds of orders so the asymptotic behavior is not a significant factor.
-For these reasons, we suggest using a linked list variant for this specific application.
+We observe that (i) the linked list variants are materially cheaper than the heap variants at dequeuing; (ii) dequeuing in a call market must be done as a batch, whereas enqueuing is paid for one at a time by the trader submitting the order; and (iii) Ethereum will not permit more than hundreds of orders so asymptotic behaviour is not significant.
+For these reasons, we suggest using one of the linked list variants.
 As it can be seen in Figure~\ref{fig:random_insertion}, the associated cost for inserting elements into a linked list PQ is significantly greater than the linked list with mapping, as each insertion causes the creation of a new contract.
-Accordingly, we choose to implement the call market with the linked list with mapping.
-Overall, this PQ balances a moderate gas cost for insertion (\ie order submission) with one for removal (\ie closing the market and matching the orders).
+Accordingly, we choose to implement the call market with the linked list with mapping which balances a moderate gas cost for insertion (\ie order submission) with one for removal (\ie closing the market and matching the orders).
+In Section~\ref{sec:rollups}, we implement \cm on Layer 2.
+There the PQ variant does not change the layer 1 gas costs and the the number of orders can be substantially increased.
+In this new context, we reconsider asymptotics and choose a heap (with dynamic array) to lower costs L2 gas costs across both enqueuing and dequeuing.
 
@@
 \input{tables/cleaning.tex}
-
-\paragraph{Gas Refunds.}\label{para-ref}To incentivize for deleting unused storage on the blockchain, some EVM operations cost a negative amount of gas.
-These include \texttt{SELFDESTRUCT} that destroys contract and refunds 24,000 gas, and  \texttt{SSTORE} that resets storage values from non-zero to zero and refunds 15,000 gas.
-The gas is refunded to the sender at the end of the transaction, however (1) the refund is capped at 50\% of the total gas cost of the transaction, and (2) the block gas limit applies to the pre-refunded amount (\ie a transaction receiving a full refund can cost up to 5.5M gas with an 11M limit).
-At the time of this writing, Ethereum transaction receipts only account for the \texttt{gasUsed}, which is the total amount of gas units spent during a transaction, and users are not able to obtain the value of the EVM's refund counter from inside the EVM~\cite{signer2018gas}.
-So in order to account for refunds in  Tables~\ref{tab:PQUnitTests}, we calculate them manually.
-First, we need to figure out exactly how much storage is being cleared or how many smart contracts are being destroyed, then we multiply these numbers by 24,000 or15,000 respectively.
 
@@
 
- \section{\cm Performance Measurements}
+ \subsection{\cm Performance Measurements}
 
@@
 
-The main research question is how many orders can be processed in a single Ethereum transaction when closing the call market, using Ethereum today.
-As our previous experiments indicated, the choice of PQ implementation is the main influence on performance.
-We implemented a generic call market that interfaces with a generic PQ (at its own contract address) and ran experiments for each PQ implementation.
-We looked at the \textit{worst-case} for performance which is when every submitted bid and ask is marketable (\ie will require fulfillment).
+The main research question is how many orders can be processed in a single Ethereum transaction when closing the call market.
+The choice of PQ implementation is the main influence on performance and the results are shown in Table~\ref{tab:worst_case_matching}.
+These numbers are for the \textit{worst-case}---when every submitted bid and ask is marketable (\ie will require fulfillment).
+In practice, once \texttt{closeMarket()} hits the first bid or ask that cannot be executed, it can stop processing all remaining orders.
+Premised on Ethereum becoming more efficient over time, we were interested in how much gas it would cost to execute 1000 pairs of orders, which is given in the third column.
+The fourth column indicates the cost of submitting a bid or ask --- since this cost will vary depending on how many orders are already submitted (recall Figure~\ref{fig:random_insertion}), we average the cost of 200 order submissions.
+
+% We implemented a generic call market that interfaces with a generic PQ (at its own contract address) and ran experiments for each PQ implementation.
+We looked at .
 Table~\ref{tab:worst_case_matching} shows the performance results of \cm for each PQ variant.
@@
 \subsection{Order Cancellations}
+\label{sec:cancel}
 
@@
 \subsection{Market Clearing Price}
+
+% JC: Not part of design landscape, find a new home for it
 

### 2021-09-10 LaTeX-LNCS-2022/sections/appendix.tex
more changes

@@
 \subsection{Ethereum and Blockchain Technology}
+\label{app:ethback}
 
@@
 
-\paragraph{Ethereum's Gas Model.}
+\subsubsection{Ethereum's Gas Model.}
 
@@
 
-\paragraph{Gas Refunds.}
+\subsubsection{Gas Refunds.}
 
@@
 First, we determine exactly how many storage slots are being cleared or how many smart contracts are being destroyed, then we multiply these numbers by 24,000 or 15,000 respectively.
+
+\subsubsection{Optimistic Roll-Ups.}
+\label{app:rollup}
+
+\begin{figure}[t]
+\centering
+\includegraphics[width=1\textwidth]{fig/lissyL2.pdf}
+\caption{\footnotesize{\cm L2 Diagram}  \label{fig:lissyl2}}
+\end{figure}
+
+%We have avoided augmenting \cm with centralized components and third party services as our research question concerns the feasibility of a system with a minimum of regulatory hooks.
+However from a regulatory stance, there is a big difference between an architecture where the centralized component is publicly visible and interacted with by users (\eg most DEXes, roll-up architectures like Loopring, and commit-chain solutions like TEX).
+We consider an alternative design that is almost as difficult to regulate as a fully on-chain solution.
+In this design, an off-chain component is introduced to boost performance but it only interacts with the Ethereum network and never directly with traders.
+Traders still only interact with Ethereum.
+
+\textit{Layer 2} solutions are a group of technologies that are designed and proposed to address specific drawbacks of executing transactions on \textit{Layer 1} (\ie Ethereum and other blockchains)~\cite{gudgeon2020sok}.
+These technologies focus on fast transaction throughput, reducing gas costs, or educing transaction latency.
+When using \cm, we strive to reduce the gas cost as performance is the main bottleneck.
+Thus, we choose a Layer 2 technology called \textit{roll-up} which aims at reducing the gas cost for operating on Layer 1 by taking the transaction executions off-chain and only using the Ethereum blockchain for storing data.
+In a roll-up, every transaction is executed by a server or cluster of servers known as \textit{validators} that can be run by a collection of users or third party operators (here they can be run by the token issuer).
+These validators then push the result of the executions (\ie updates in the EVM state) back to the Ethereum and assure the Ethereum network that the transactions have been executed correctly.
+
+A function can be computed off-chain and the new state of the DApp, called a \textit{rollup}, is written back to the blockchain, accompanied by either (1) a proof that the function was executed correctly, or (2) a dispute resolution process that can resolve, on-chain, functions that are not executed correctly (\eg Arbitrum~\cite{kalodner2018arbitrum}).
+In the case of (1), validating the proof must be cheaper than running the function itself.
+There are two main approaches: (1a) the first is to use cryptographic proof techniques (\eg SNARKS~\cite{BCGTV13,GGPR13} and variants~\cite{BBHR19}).
+This is called a \textit{zk-rollup}.
+Note that the proofs are heavy to compute (introducing a burden to the validators who generate them) but considered valid once posted to the Ethereum.
+The second approach (1b) is to execute the function in a trusted execution environment (TEE; \eg Intel SGX) and validate the TEE's quote on-chain (\eg Ekiden~\cite{cheng2019ekiden}).\footnote{The TEE-based approach is mired by recent attacks on SGX~\cite{SGX1,SGX2,SGX3,SGX4}, however these attacks do not necessarily apply to the specifics of how SGX is used here, and safer TEE technologies like Intel TXT (\cf~\cite{ZBC+19}) can be substituted.} Approach (2) is called an \textit{optimistic roll-up}.
+Although the dispute time delays result in a slower transaction finality, optimistic roll-ups substantially increase the performance by decreasing the gas cost.
+
+\subsubsection{Arbitrum}
+
+Arbitrum is an Ethereum Layer 2 scaling solution that operates as an optimistic roll-up~\cite{kalodner2018arbitrum}.
+Arbitrum runs entire DApps inside its environment, which acts like a container and requires special bridge contacts to interact with `normal' (or Layer 1) Ethereum DApps.
+To deploy a DApp on Arbitrum, or to execute a function on an existing Arbitrum DApp, the transaction is sent to an \textit{Inbox contract} on Layer 1.
+The transaction is not executed, it is only recorded (as calldata) in the Inbox.
+Like any other transactions on Ethereum, miners determine the order of the transactions sent to this contract.
+A set of validators (open to anyone) are watching the Inbox contract for new transactions.
+Once an Inbox transaction is finalized in an Ethereum block, validators will execute the transaction and assert the result of the execution to other validators on a sidechain called ArbOS.
+Once the dispute challenge period is over, the new state of ArbOS will be inserted into Ethereum.
+As the Inbox contract maintains all Arbitrum transactions, anyone can recompute the entire current state of the ArbOS and file a dispute if executions are not performed correctly.
+Disputes are adjudicated by Ethereum itself and require essentially constant gas costs, regardless of the size of the gas costs of the transaction being disputed
 
@@
 
-\subsection{Optimistic Roll-Ups}
-\label{app:rollup}
-
-\begin{figure}[t]
-\centering
-\includegraphics[width=1\textwidth]{fig/lissyL2.pdf}
-\caption{\footnotesize{\cm L2 Diagram}  \label{fig:lissyl2}}
-\end{figure}
-
-We have avoided augmenting \cm with centralized components and third party services as our research question concerns the feasibility of a system with a minimum of regulatory hooks.
-However from a regulatory stance, there is a big difference between an architecture where the centralized component is publicly visible and interacted with by users (\eg most DEXes, roll-up architectures like Loopring, and commit-chain solutions like TEX).
-We consider an alternative design that is almost as difficult to regulate as a fully on-chain solution.
-In this design, an off-chain component is introduced to boost performance but it only interacts with the Ethereum network and never directly with traders.
-Traders still only interact with Ethereum.
-
-\textit{Layer 2} solutions are a group of technologies that are designed and proposed to address specific drawbacks of executing transactions on \textit{Layer 1} (\ie Ethereum and other blockchains)~\cite{gudgeon2020sok}.
-These technologies focus on fast transaction throughput, reducing gas costs, or educing transaction latency.
-When using \cm, we strive to reduce the gas cost as performance is the main bottleneck.
-Thus, we choose a Layer 2 technology called \textit{roll-up} which aims at reducing the gas cost for operating on Layer 1 by taking the transaction executions off-chain and only using the Ethereum blockchain for storing data.
-In a roll-up, every transaction is executed by a server or cluster of servers known as \textit{validators} that can be run by a collection of users or third party operators (here they can be run by the token issuer).
-These validators then push the result of the executions (\ie updates in the EVM state) back to the Ethereum and assure the Ethereum network that the transactions have been executed correctly.
-
-A function can be computed off-chain and the new state of the DApp, called a \textit{rollup}, is written back to the blockchain, accompanied by either (1) a proof that the function was executed correctly, or (2) a dispute resolution process that can resolve, on-chain, functions that are not executed correctly (\eg Arbitrum~\cite{kalodner2018arbitrum}).
-In the case of (1), validating the proof must be cheaper than running the function itself.
-There are two main approaches: (1a) the first is to use cryptographic proof techniques (\eg SNARKS~\cite{BCGTV13,GGPR13} and variants~\cite{BBHR19}).
-This is called a \textit{zk-rollup}.
-Note that the proofs are heavy to compute (introducing a burden to the validators who generate them) but considered valid once posted to the Ethereum.
-The second approach (1b) is to execute the function in a trusted execution environment (TEE; \eg Intel SGX) and validate the TEE's quote on-chain (\eg Ekiden~\cite{cheng2019ekiden}).\footnote{The TEE-based approach is mired by recent attacks on SGX~\cite{SGX1,SGX2,SGX3,SGX4}, however these attacks do not necessarily apply to the specifics of how SGX is used here, and safer TEE technologies like Intel TXT (\cf~\cite{ZBC+19}) can be substituted.} Approach (2) is called an \textit{optimistic roll-up}.
-Although the dispute time delays result in a slower transaction finality, optimistic roll-ups substantially increase the performance by decreasing the gas cost.
-
-\section{Cleaning Up Revisited: Clearing Mappings}
+\section{Cleaning-Up Revisited: Clearing Mappings}
 \label{app:clean}

### 2021-09-10 LaTeX-LNCS-2022/sections/paper.tex
more changes

@@
 Briefly, certain EVM operations (\texttt{SELFDESTRUCT} and \texttt{SSTORE 0}) cost negative gas, with the follow caveats: the refund is capped at 50\% of the total gas cost of the transaction, and (2) the block gas limit applies to the pre-refunded amount (\ie a transaction receiving a full refund can cost up to 5.5M gas with an 11M limit).
-We provide full details of all of these topics in Appendix~\ref{app:back}.
+We provide full details of all of these topics in Appendix~\ref{app:ethback}.
 
@@
 
-\paragraph{Refunds and PQs.}
-
 One consequence of a linked list is that a new contract is created for every node in the list.
@@
 The simplest approach is to process a node, update the head pointer, and leave the `removed' node's data behind in the mapping untouched (where it will never be referenced again).
-Alternatively, we can call \texttt{DELETE} on each mapping entry once we finish processing a node in the PQ.
+Alternatively, we can call \texttt{DELETE} on each mapping entry once we finish processing a trade.
 As it can be seen in the last two rows of Table~\ref{tab:cleaning}, leaving the data on the blockchain is cheaper than cleaning it up.
@@
 Further, the cap on the maximum refund means that refunds are not fully received for large cleanup operations (however removing the cap impacts the miners' incentives to include the transaction).
-This is a complicated and under-explored area of Ethereum in the research literature.
+In Appendix~\ref{app:clean}, we present a second case study of the cost-benefits of clearing a mapping when it is no longer needed (including our idea to store the mapping in its own contract so it can \texttt{SELFDESTRUCT} with a single function call).
+The unfortunate takeaway is, again, that it is cheapest to leave the mapping in place.
+Cleaning up EVM state is a complicated and under-explored area of Ethereum in the research literature.
 For our own work, we strive to be good citizens of Ethereum and clean up to the extent that we can---thus all PQs in Table~\ref{tab:PQUnitTests} implement some cleanup.
@@
 
-The main research question is how many orders can be processed in a single Ethereum transaction when closing the call market.
+The main research question is how many orders can be processed under the Ethereum block gas limit.
 The choice of PQ implementation is the main influence on performance and the results are shown in Table~\ref{tab:worst_case_matching}.
@@
 
-% We implemented a generic call market that interfaces with a generic PQ (at its own contract address) and ran experiments for each PQ implementation.
-We looked at .
-Table~\ref{tab:worst_case_matching} shows the performance results of \cm for each PQ variant.
-In the first two columns, we determine the highest number of trades that can be executed and processed in a single call to the \texttt{closeMarket()} and not exceed the current Ethereum block gas limit of 11,741,495.
-Since Ethereum will become more efficient over time, we were also interested in how much gas it would cost to execute 1000 pairs of orders, which is given in the third column.
-The fourth column indicates the cost of submitting a bid or ask --- since this cost will vary depending on how many orders are already submitted (recall Figure~\ref{fig:random_insertion}), we average the cost of 200 order submissions.
-
-As expected, the numbers closely track the performance of the PQ itself, suggesting the PQ is indeed the main influence on performance.
-In Ethereum today, call markets appear to be limited to processing about a hundred orders per transaction.
-If markets open on every other block and the call market could monopolize an entire block to close, a few hundred orders per minute (worst-case) can be processed.
-The main takeaway is that the transparency, front-running resistance, and low barrier to entry of Ethereum come with an enormous cost (\ie an institutional exchange like NASDAQ can process 100K trades per second).
-That said, many exchanges trade the same assets under different trading rules (\ie market fragmentation) because traders have different preferences.
-\cm can work today in some circumstances like very low liquidity tokens, or markets with high volumes and a small number of traders (\eg liquidation auctions).
-
-\section{Front-running Evaluation} \label{sec:front}
-
-%\textblue{Notes on Front-running Table:}
-%\begin{itemize}
-%\item{Mallory squeezes her order before Alice's.} Mallory sees that there is an incoming bid at 200 for 10 of an asset, and currently, the best offer is at 190 for the same volume.
-In this case, Mallory sends her bid at 190 for 10 and immediately inserts the sell order at 200.
-If Alice's transaction gets executed, Mallory will profit on the price difference.
-%\textblue{Sandwich Attacks:} These attacks apply to automated market makers (\ie UniSwap) and exploit a particular feature of AMMs, which is for every swap that takes place on an AMM, the price of the token being swapped shifts slightly.
-In this case, if Mallory realizes that there is an incoming trade of asset A for asset B, She immediately inserts a bid for asset B.
-This transaction will increase the price of asset B significantly and when Alice's transaction gets executed on the AMM, she'll receive less number of asset B as she is purchasing it at an inflated price.
-Right after Alice's transaction goes through, Mallory will sell the amount of asset B she has bought at a higher price.
-%\end{itemize}
-
-%\input{tables/frontrunning.tex}
-\input{tables/frontrunning2.tex}
-
-As we illustrate in Table~\ref{tab:front}, call markets have a unique profile of resilience against \emph{front-running attacks}~\cite{clark2014decentralizing,eskandari2019sok,daian2019flash} that differs somewhat from continuous-time markets and automated market makers.
-Traders are sometimes distinguished as \emph{makers} (adds orders to a market) and \emph{takers} (trades against a pre-existing, unexecuted orders).
-A continuous market has both.
-All traders using an automated market maker are takers, while the investors who provide tokens to the AMM (liquidity providers) are makers.
-Under our definition, a call market only has makers: the only way to have a trade executed is to submit an order.
-The front-running attacks in Table~\ref{tab:front} are sub-categorized, using a recent SoK~\cite{eskandari2019sok}, as being \emph{Insertion}, \emph{Displacement}, and \emph{Suppression}.
-To explain the difference, we will illustrate the first three attacks in the table.
-
-In an \emph{insertion attack}, Mallory learns of a transaction from Alice.
-Consider Alice submitting a bid order for 100 tokens at any price (market order).
-Mallory decides to add new ask orders to the book (limit orders) at the maximum price reachable by Alice's order given the rest of the asks in the book.
-Mallory must arrange for her orders to be added before Alice's transaction and then arrange for Alice's transaction to be the next (relevant) transaction to run (\eg before competing asks from other traders are added).
-
-In a centralized exchange, Mallory would collude with the \emph{authority} running the exchange to conduct this attack.
-On-chain, Mallory could be a fast \emph{trader} who sees Alice's transaction in the mempool and adds her transaction with a higher gas fee to bribe miners to execute hers first (insertion is probabilist and not guaranteed).
-Finally, Mallory could be the \emph{miner} of the block that includes Alice's transaction allowing her to insert with high fidelity.
-Roll-ups use \emph{sequencers} discussed in Section~\ref{sec:frontarb}.
-
-A \emph{displacement attack} is like an insertion attack, except Mallory does not care what happens to Alice's original transaction---she only cares about being first.
-If Mallory sees Alice trying to execute a trade at a good price, she could try to beat Alice and execute the trade first.
-Mallory is indifferent to whether Alice can then execute her trade or not.
-The analysis of both insertion and suppression attacks are similar.
-Call markets mitigate these basic insertion and displacement attacks because they do not have any time priority (e.g., if you were to shuffle the order of all orders submitted within the same call, the outcome would be exactly the same).
-A different way to mitigate these attacks is to seal orders with confidentiality (a \textit{dark} market).
-
-In a \emph{suppression attack}, Mallory floods the network with transactions until a trader executes her order.
-Such selective denial of service is possible by an off-chain operator.
-With on-chain continuous markets, it is not possible to suppress Alice's transaction while also letting through a transaction from a taker---suppression applies to all Ethereum transactions or none.
-A call market is uniquely vulnerable because it eventually times out (which does not require an on-chain transaction) and new orders cannot be added.
-We still award a call market partial mitigation since suppression attacks are expensive (\cf Fomo3D attack~\cite{eskandari2019sok}).
-If the aim of suppression is a temporary denial of service (captured by attack 5 in the table), then all on-chain markets are vulnerable to this expensive attack.
-
-Some attacks combine more than one insertion, displacement, and/or suppression attacks.
-AMMs are vulnerable to a double insertion called a sandwich attack~\cite{ZQFLG21} which bookends a victim's trade with the front-runner's trades (plus additional variants).
-In a traditional call market, a market clearing price is chosen and all trades are executed at this price.
-All bids made at a higher price will receive the assets for the lower clearing price (and conversely for lower ask prices): this is called a \textit{price improvement} and it allows traders to submit at their best price.
-A hybrid front-running attack allows Mallory to extract any price improvements.
-Consider the case where Alice's ask crosses Bob's bid with a material price improvement.
-Mallory inserts a bid at Alice's price, suppresses Bob's bid until the next call, and places an ask at Bob's price.
-She buys and then immediately sells the asset and nets the price improvement as arbitrage.
-To mitigate this in \cm, all price improvements are given to the miner (using \texttt{block.coinbase.transfer()})\textblue{traders would have to pay for that}.
-This does not actively hurt traders---they always receive the same price that they quote in their orders---and it removes any incentive for miners to front-run these profits.
-
-Other front-running attacks use order cancellations (discussed in the next section) which \cm mitigates by running short-lived markets with no cancellations.
-
-There are two main takeaways from Table~\ref{tab:front}.
-Call markets provide strong resilience to front-running only bested slightly by dark markets like TEX~\cite{khalil2019tex}, however they do it through design---no cryptography and no two-round protocols.
-A second observation is that dark call markets, like Galal \etal~\cite{galalpublicly}, are no more resilient to front-running than a lit market (however confidentiality could provide resilience to predatory trading algorithms that are reactionary but do not front-run).
-
-% = = = = = = = = = = = = = = = = = = = = = = = = =  %
-
-\section{Design Alternatives and Extensions}
-
-\cm is designed as a base class that can be extended and customized. Here, we evaluate potential modifications.
-
-\begin{figure}[t]
-\centering
-\includegraphics[width=1\textwidth]{fig/MindMapDraft3.png}
-\caption{\footnotesize{Mind Map Draft}  \label{fig:rmindmap}}
-\end{figure}
-% = = = = = = = = = = = = = = = = = = = = = = = = =  %
-
-\subsection{Token Divisibility and Ties}
-
-When executing trades, if the volume of the current best bid does not match the best ask, the larger order is partially filled and the remaining volume is considered against the next best order.
-A common trading rule (that does resist front-running) is to fill ties in proportion to their volume (\ie \textit{pro rata} allocation)\footnote{If Alice and Bob bid the same price for 100 tokens and 20 tokens respectively, and there are only 60 tokens left in marketable asks, Alice receives 50 and Bob 10.}, however this approach does not always work.
-Consider the following corner case: 3 equally priced bids of 1 non-divisible token and 1 ask at the same price.
-There is no good option: (1) the bids could all be dropped, (2) the bids could be prioritized based on time, or (3) the bid could be randomly chosen (\cf Libra~\cite{mavroudis2019libra}).
-
-\paragraph{Evaluation.} We avoid (1) which is fair but not market efficient.
-We note the conditions under which pro rata allocation fails (\ie non-divisible assets, an exact tie on price, and part of the final allocation) are improbable.
-In \cm, tokens are assumed to be divisible but we otherwise default to (2).
-This means insertion front-running attacks are possible for this corner case.
-However if these attacks proved to be a problem in practice, (3) is a better solution with one main drawback: on-chain sources of `randomness' are generally deterministic and manipulatable by miners~\cite{bonneau2015random,buenz2017proofs}, countermeasures can take a few blocks to select~\cite{boneh2018verifiable}.
-
-% = = = = = = = = = = = = = = = = = = = = = = = = =  %
-
-\subsection{Order Cancellations}
-\label{sec:cancel}
-
-\cm does not support order cancellations. We intend to open and close markets quickly (on the order of blocks), so orders are relatively short-lived.
-
-\paragraph{Evaluation.} Support for cancellation opens the market to new front-running issues where other traders (or miners) can displace cancellations until after the market closes.
-However, one benefit of a call market is that beating a cancellation with a new order has no effect, assuming the cancellation is run any time before the market closes.
-Also, cancellations have a performance impact.
-Cancelled orders can be removed from the underlying data structure or accumulated in a list that is cross-checked when closing the market.
-Removing orders requires a more verbose structure than a priority queue (\eg a self-balancing binary search tree instead of a heap; or methods to traverse a linked list rather than only pulling from the head).
-While client software could help point out where the order is in the data structure, the order book can change between submitting the cancellation request and running the method.
-%A linked list with mapping that returns the key for each submitted order seems to be the most tenable data structure.
-
-% = = = = = = = = = = = = = = = = = = = = = = = = =  %
-
-\subsection{Market Clearing Price}
-
-% JC: Not part of design landscape, find a new home for it
-
-Call markets are heralded for fair price discovery.
-This is why many exchanges use a call market at the end of the day to determine the closing price of an asset, which is an important price both optically (it is well-published) and operationally (many derivatives settle based on the closing price).
-We purposely do not compute a `market clearing price' with \cm because miners can easily manipulate the price (\ie include a single wash trade at the price they want fixed), although they forgo profit for doing so.
-This is not merely hypothetical---Uniswap (the prominent quote-drive, on-chain exchange) prices have been manipulated to exploit other DeFi applications relying on them.
-Countermeasures to protect Uniswap price integrity could also apply to \cm: (1) taking a rolling median of prices over time, and (2) using it alongside other sources for the same price and forming a consensus.
-While \cm does not emit a market clearing price, it can be computed by a web application examining the order book at market close.
-
-% = = = = = = = = = = = = = = = = = = = = = = = = =  %
-
-\subsection{Scheduling Events}
-
-\cm is a one-shot market.
-However it can be extended to reopen with a clean order book after \texttt{closeMarket()} is run.
-Modifiers can enforce when the market operates openly (collecting orders) and when close can be run.
-In the Princeton paper~\cite{clark2014decentralizing}, the call market is envisioned to run as an alt-coin, where orders accumulate within a block and a miner closes the market as part of the logic of producing a new block (\ie within the same portion of code as computing their coinbase transaction in Bitcoin or \texttt{gasUsed} in Ethereum).
-
-If the call market runs as a DApp on Ethereum, it seems difficult to open and close the market on every block.
-Someone needs to call the \texttt{closeMarket()} for every block (we return to who this is later), but the market will only work as intended if miners execute this function after every \texttt{submitBid()} and \texttt{submitAsk()} invocation.
-Since price improvements are paid to the miners, the miner is actually incentivized to run \texttt{closeMarket()} last to make the most profit.
-This pattern is called miner extractable value (MEV)~\cite{daian2019flash} and is usually considered in the context of attacks.
-However in our case, MEV is a feature.
-Efficient algorithms for miners to automatically find MEV opportunities is an open research problem.
-
-A close alternative is to allow markets to open and close on different blocks.
-In this alternative, the \texttt{closeMarket()} function calls \texttt{openMarket()} as a subroutine and sets two modifiers: orders are only accepted in the block immediately after the current block (\ie the block that executes the \texttt{closeMarket()}) and \texttt{closeMarket()} cannot be run again until two blocks after the current block.
-
-The final issue is who invokes \texttt{closeMarket()} every other block?
-There are two issues here: the issue of scheduling the function call and the issue of paying for it.
-For scheduling the function call, we can do one of the following: rely on market participants, who are eager to trade, to reopen the market, offer a bounty to reopen the market, or use an external service like Ethereum Alarm Clock (which creates a regulatory hook).\footnote{\url{https://ethereum-alarm-clock-service.readthedocs.io/}} Next, we consider the second issue of who pays to close the market.
-
-% = = = = = = = = = = = = = = = = = = = = = = = = =  %
-
-\subsection{Who Pays to Close/Reopen the Market?}
-\label{sec:close}
-
-As miners are paid all price improvements in the market, it is possible that a miner might run \texttt{closeMarket()} and it would pay for itself.
-However, we consider two other scenarios that do not assume miners can automatically find MEV opportunities.
-One solution requires a modified closing function, \texttt{closeMarket(n)}, that only processes $n$ orders at a time until the order book is empty (this is sensible design in any case to safeguard against the order book from locking up because the number of orders exceeds the gas limit to process them).
-Once the time window for submitting orders has past, a new market is created (without settling the previous market).
-Every order submission on the new market also requires to run, say, \texttt{closeMarket(10)} on the older market, thus progressively closing the previous market while accepting orders to the new market.
-
-The second solution is to levy a carefully computed fee against the traders for every new order they submit.
-These fees are accumulated by the DApp to use as a bounty.
-When the time window for the open market elapses, the user who calls the \texttt{closeMarket()} function receives the bounty.
-
-\paragraph{Evaluation.} The first solution pattern has two issues: first, amortizing the cost of closing the market amongst the early traders of the new market is an added incentive to not submit orders early to the market; the second issue is if not enough traders submit orders in the new market, the old market never closes (resulting in a backlog of old markets waiting to close).
-The second solution is better, although not perfect: \texttt{closeMarket()} cost does not follow a tight linear increase with the number of orders, and gas prices vary over time which could render the bounty insufficient for offsetting the \texttt{closeMarket()} cost.
-However, an interested third party (such as the token issuer for a given market) might occasionally bailout the market when it halts on \texttt{closeMarket()} to facilitate further trading.
-If the DApp can pay for its own functions, an interested party can also arrange for a commercial service (\eg any.sender\footnote{\url{https://github.com/PISAresearch/docs.any.sender}}) to relay the \texttt{closeMarket()} function call on Ethereum (an approach called \textit{meta-transactions}) which introduces another regulatory hook.
-
-% = = = = = = = = = = = = = = = = = = = = = = = = =  %
-
-\subsection{Collateralization Options}
-
-In \cm, both the tokens and ETH that a trader wants to potentially use in the order book are pre-loaded into the contract.
-Consider Alice, who holds a token and decides she wants to trade it for ETH.
-In this model, she must first transfer the tokens to the contract and then submit an ask order.
-If she does this within the same block, there is a chance that a miner will execute the ask before the transfer and the ask will revert.
-If she waits for confirmation, this introduces a delay.
-This delay seems reasonable but we point out a few options it could be addressed:
-
-\begin{enumerate}
-
-\item \textbf{Use \texttt{msg.value}.} For the ETH side of a trade (\ie for bids), ETH could be sent with the function call to \texttt{submitBid()} to remove the need for    \texttt{depositEther()}.
-This works for markets that trade ERC20 tokens for ETH, but would not work for ERC20 to ERC20 exchanges.
-
-\item \textbf{Merge Deposits with Bids/Asks.} \cm could have an additional function that atomically runs the functionality of \texttt{depositToken()} followed by the functionality of \texttt{submitAsk()}.
-This removes the chance that the deposit and order submission are ordered incorrectly.
-
-\item \textbf{Use ERC20 Approval.} Instead of \cm taking custody of the tokens, the token holder could simply approve \cm to transfer tokens on her behalf.
-If \cm is coded securely, it is unconcerning to allow the approval to stand long-term and the trader never has to lock up their tokens in the DApp.
-The issue is that there is no guarantee that the tokens are actually available when the market closes (\ie Alice can approve a DApp to spend 100 tokens even if she only has 5 tokens or no tokens).
-In this case, \cm would optimistically try to transfer the tokens and if it fails, move onto the next order.
-This also gives Alice an indirect way to cancel an order, by removing the tokens backing the order---this could be a feature or it could be considered an abuse.
-
-\item \textbf{Use a Fidelity Bond.} Traders could post some number of tokens as a fidelity bond, and be allowed to submit orders up to 100x this value using approve.
-If a trade fails because the pledged tokens are not available, the fidelity bond is slashed as punishment.
-This allows traders to side-step time-consuming transfers to and from \cm while still incentivizing them to ensure that submitted orders can actually be executed.
-The trade-off  is that \cm needs to update balances with external calls to the ERC20 contract instead of simply updating its internal ledger.
-
-\end{enumerate}
+The main takeaway is that call markets appear to be limited to processing about a hundred orders per transaction and even that is at the enormous cost of monopolizing an entire Ethereum block just to close the market.
+Perhaps \cm can work today in some circumstances like very low liquidity tokens, or markets with high volumes and a small number of traders (\eg liquidation auctions).
 
@@
 \section{\cm on Layer 2}\label{sec:rollups}
+
+We consider an alternative design for \cm that is almost as difficult to regulate as a fully on-chain solution.
+In this design, an off-chain component is introduced to boost performance but it only interacts with the Ethereum network and never directly with traders.
+Traders still only interact with Ethereum.
 
@@
 
+% = = = = = = = = = = = = = = = = = = = = = = = = =  %
+
+\section{Design Alternatives and Extensions}
+
+\cm is designed as a base class that can be extended and customized. Here, we evaluate potential modifications.
+
+\begin{figure}[t]
+\centering
+\includegraphics[width=1\textwidth]{fig/MindMapDraft3.png}
+\caption{\footnotesize{Mind Map Draft}  \label{fig:rmindmap}}
+\end{figure}
+% = = = = = = = = = = = = = = = = = = = = = = = = =  %
+
+\subsection{Token Divisibility and Ties}
+
+When executing trades, if the volume of the current best bid does not match the best ask, the larger order is partially filled and the remaining volume is considered against the next best order.
+A common trading rule (that does resist front-running) is to fill ties in proportion to their volume (\ie \textit{pro rata} allocation)\footnote{If Alice and Bob bid the same price for 100 tokens and 20 tokens respectively, and there are only 60 tokens left in marketable asks, Alice receives 50 and Bob 10.}, however this approach does not always work.
+Consider the following corner case: 3 equally priced bids of 1 non-divisible token and 1 ask at the same price.
+There is no good option: (1) the bids could all be dropped, (2) the bids could be prioritized based on time, or (3) the bid could be randomly chosen (\cf Libra~\cite{mavroudis2019libra}).
+
+\paragraph{Evaluation.} We avoid (1) which is fair but not market efficient.
+We note the conditions under which pro rata allocation fails (\ie non-divisible assets, an exact tie on price, and part of the final allocation) are improbable.
+In \cm, tokens are assumed to be divisible but we otherwise default to (2).
+This means insertion front-running attacks are possible for this corner case.
+However if these attacks proved to be a problem in practice, (3) is a better solution with one main drawback: on-chain sources of `randomness' are generally deterministic and manipulatable by miners~\cite{bonneau2015random,buenz2017proofs}, countermeasures can take a few blocks to select~\cite{boneh2018verifiable}.
+
+% = = = = = = = = = = = = = = = = = = = = = = = = =  %
+
+\subsection{Order Cancellations}
+\label{sec:cancel}
+
+\cm does not support order cancellations. We intend to open and close markets quickly (on the order of blocks), so orders are relatively short-lived.
+
+\paragraph{Evaluation.} Support for cancellation opens the market to new front-running issues where other traders (or miners) can displace cancellations until after the market closes.
+However, one benefit of a call market is that beating a cancellation with a new order has no effect, assuming the cancellation is run any time before the market closes.
+Also, cancellations have a performance impact.
+Cancelled orders can be removed from the underlying data structure or accumulated in a list that is cross-checked when closing the market.
+Removing orders requires a more verbose structure than a priority queue (\eg a self-balancing binary search tree instead of a heap; or methods to traverse a linked list rather than only pulling from the head).
+While client software could help point out where the order is in the data structure, the order book can change between submitting the cancellation request and running the method.
+%A linked list with mapping that returns the key for each submitted order seems to be the most tenable data structure.
+
+% = = = = = = = = = = = = = = = = = = = = = = = = =  %
+
+\subsection{Market Clearing Price}
+
+% JC: Not part of design landscape, find a new home for it
+
+Call markets are heralded for fair price discovery.
+This is why many exchanges use a call market at the end of the day to determine the closing price of an asset, which is an important price both optically (it is well-published) and operationally (many derivatives settle based on the closing price).
+We purposely do not compute a `market clearing price' with \cm because miners can easily manipulate the price (\ie include a single wash trade at the price they want fixed), although they forgo profit for doing so.
+This is not merely hypothetical---Uniswap (the prominent quote-drive, on-chain exchange) prices have been manipulated to exploit other DeFi applications relying on them.
+Countermeasures to protect Uniswap price integrity could also apply to \cm: (1) taking a rolling median of prices over time, and (2) using it alongside other sources for the same price and forming a consensus.
+While \cm does not emit a market clearing price, it can be computed by a web application examining the order book at market close.
+
+% = = = = = = = = = = = = = = = = = = = = = = = = =  %
+
+\subsection{Scheduling Events}
+
+\cm is a one-shot market.
+However it can be extended to reopen with a clean order book after \texttt{closeMarket()} is run.
+Modifiers can enforce when the market operates openly (collecting orders) and when close can be run.
+In the Princeton paper~\cite{clark2014decentralizing}, the call market is envisioned to run as an alt-coin, where orders accumulate within a block and a miner closes the market as part of the logic of producing a new block (\ie within the same portion of code as computing their coinbase transaction in Bitcoin or \texttt{gasUsed} in Ethereum).
+
+If the call market runs as a DApp on Ethereum, it seems difficult to open and close the market on every block.
+Someone needs to call the \texttt{closeMarket()} for every block (we return to who this is later), but the market will only work as intended if miners execute this function after every \texttt{submitBid()} and \texttt{submitAsk()} invocation.
+Since price improvements are paid to the miners, the miner is actually incentivized to run \texttt{closeMarket()} last to make the most profit.
+This pattern is called miner extractable value (MEV)~\cite{daian2019flash} and is usually considered in the context of attacks.
+However in our case, MEV is a feature.
+Efficient algorithms for miners to automatically find MEV opportunities is an open research problem.
+
+A close alternative is to allow markets to open and close on different blocks.
+In this alternative, the \texttt{closeMarket()} function calls \texttt{openMarket()} as a subroutine and sets two modifiers: orders are only accepted in the block immediately after the current block (\ie the block that executes the \texttt{closeMarket()}) and \texttt{closeMarket()} cannot be run again until two blocks after the current block.
+
+The final issue is who invokes \texttt{closeMarket()} every other block?
+There are two issues here: the issue of scheduling the function call and the issue of paying for it.
+For scheduling the function call, we can do one of the following: rely on market participants, who are eager to trade, to reopen the market, offer a bounty to reopen the market, or use an external service like Ethereum Alarm Clock (which creates a regulatory hook).\footnote{\url{https://ethereum-alarm-clock-service.readthedocs.io/}} Next, we consider the second issue of who pays to close the market.
+
+% = = = = = = = = = = = = = = = = = = = = = = = = =  %
+
+\subsection{Who Pays to Close/Reopen the Market?}
+\label{sec:close}
+
+As miners are paid all price improvements in the market, it is possible that a miner might run \texttt{closeMarket()} and it would pay for itself.
+However, we consider two other scenarios that do not assume miners can automatically find MEV opportunities.
+One solution requires a modified closing function, \texttt{closeMarket(n)}, that only processes $n$ orders at a time until the order book is empty (this is sensible design in any case to safeguard against the order book from locking up because the number of orders exceeds the gas limit to process them).
+Once the time window for submitting orders has past, a new market is created (without settling the previous market).
+Every order submission on the new market also requires to run, say, \texttt{closeMarket(10)} on the older market, thus progressively closing the previous market while accepting orders to the new market.
+
+The second solution is to levy a carefully computed fee against the traders for every new order they submit.
+These fees are accumulated by the DApp to use as a bounty.
+When the time window for the open market elapses, the user who calls the \texttt{closeMarket()} function receives the bounty.
+
+\paragraph{Evaluation.} The first solution pattern has two issues: first, amortizing the cost of closing the market amongst the early traders of the new market is an added incentive to not submit orders early to the market; the second issue is if not enough traders submit orders in the new market, the old market never closes (resulting in a backlog of old markets waiting to close).
+The second solution is better, although not perfect: \texttt{closeMarket()} cost does not follow a tight linear increase with the number of orders, and gas prices vary over time which could render the bounty insufficient for offsetting the \texttt{closeMarket()} cost.
+However, an interested third party (such as the token issuer for a given market) might occasionally bailout the market when it halts on \texttt{closeMarket()} to facilitate further trading.
+If the DApp can pay for its own functions, an interested party can also arrange for a commercial service (\eg any.sender\footnote{\url{https://github.com/PISAresearch/docs.any.sender}}) to relay the \texttt{closeMarket()} function call on Ethereum (an approach called \textit{meta-transactions}) which introduces another regulatory hook.
+
+% = = = = = = = = = = = = = = = = = = = = = = = = =  %
+
+\subsection{Collateralization Options}
+
+In \cm, both the tokens and ETH that a trader wants to potentially use in the order book are pre-loaded into the contract.
+Consider Alice, who holds a token and decides she wants to trade it for ETH.
+In this model, she must first transfer the tokens to the contract and then submit an ask order.
+If she does this within the same block, there is a chance that a miner will execute the ask before the transfer and the ask will revert.
+If she waits for confirmation, this introduces a delay.
+This delay seems reasonable but we point out a few options it could be addressed:
+
+\begin{enumerate}
+
+\item \textbf{Use \texttt{msg.value}.} For the ETH side of a trade (\ie for bids), ETH could be sent with the function call to \texttt{submitBid()} to remove the need for    \texttt{depositEther()}.
+This works for markets that trade ERC20 tokens for ETH, but would not work for ERC20 to ERC20 exchanges.
+
+\item \textbf{Merge Deposits with Bids/Asks.} \cm could have an additional function that atomically runs the functionality of \texttt{depositToken()} followed by the functionality of \texttt{submitAsk()}.
+This removes the chance that the deposit and order submission are ordered incorrectly.
+
+\item \textbf{Use ERC20 Approval.} Instead of \cm taking custody of the tokens, the token holder could simply approve \cm to transfer tokens on her behalf.
+If \cm is coded securely, it is unconcerning to allow the approval to stand long-term and the trader never has to lock up their tokens in the DApp.
+The issue is that there is no guarantee that the tokens are actually available when the market closes (\ie Alice can approve a DApp to spend 100 tokens even if she only has 5 tokens or no tokens).
+In this case, \cm would optimistically try to transfer the tokens and if it fails, move onto the next order.
+This also gives Alice an indirect way to cancel an order, by removing the tokens backing the order---this could be a feature or it could be considered an abuse.
+
+\item \textbf{Use a Fidelity Bond.} Traders could post some number of tokens as a fidelity bond, and be allowed to submit orders up to 100x this value using approve.
+If a trade fails because the pledged tokens are not available, the fidelity bond is slashed as punishment.
+This allows traders to side-step time-consuming transfers to and from \cm while still incentivizing them to ensure that submitted orders can actually be executed.
+The trade-off  is that \cm needs to update balances with external calls to the ERC20 contract instead of simply updating its internal ledger.
+
+\end{enumerate}
+
 % = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
+
+\section{Front-running Evaluation} 
+\label{sec:front}
+
+\input{tables/frontrunning2.tex}
+
+As we illustrate in Table~\ref{tab:front}, call markets have a unique profile of resilience against \emph{front-running attacks}~\cite{clark2014decentralizing,eskandari2019sok,daian2019flash} that differs somewhat from continuous-time markets and automated market makers.
+Traders are sometimes distinguished as \emph{makers} (adds orders to a market) and \emph{takers} (trades against a pre-existing, unexecuted orders).
+A continuous market has both.
+All traders using an automated market maker are takers, while the investors who provide tokens to the AMM (liquidity providers) are makers.
+Under our definition, a call market only has makers: the only way to have a trade executed is to submit an order.
+The front-running attacks in Table~\ref{tab:front} are sub-categorized, using a recent SoK~\cite{eskandari2019sok}, as being \emph{Insertion}, \emph{Displacement}, and \emph{Suppression}.
+To explain the difference, we will illustrate the first three attacks in the table.
+
+In an \emph{insertion attack}, Mallory learns of a transaction from Alice.
+Consider Alice submitting a bid order for 100 tokens at any price (market order).
+Mallory decides to add new ask orders to the book (limit orders) at the maximum price reachable by Alice's order given the rest of the asks in the book.
+Mallory must arrange for her orders to be added before Alice's transaction and then arrange for Alice's transaction to be the next (relevant) transaction to run (\eg before competing asks from other traders are added).
+
+In a centralized exchange, Mallory would collude with the \emph{authority} running the exchange to conduct this attack.
+On-chain, Mallory could be a fast \emph{trader} who sees Alice's transaction in the mempool and adds her transaction with a higher gas fee to bribe miners to execute hers first (insertion is probabilist and not guaranteed).
+Finally, Mallory could be the \emph{miner} of the block that includes Alice's transaction allowing her to insert with high fidelity.
+Roll-ups use \emph{sequencers} discussed in Section~\ref{sec:frontarb}.
+
+A \emph{displacement attack} is like an insertion attack, except Mallory does not care what happens to Alice's original transaction---she only cares about being first.
+If Mallory sees Alice trying to execute a trade at a good price, she could try to beat Alice and execute the trade first.
+Mallory is indifferent to whether Alice can then execute her trade or not.
+The analysis of both insertion and suppression attacks are similar.
+Call markets mitigate these basic insertion and displacement attacks because they do not have any time priority (e.g., if you were to shuffle the order of all orders submitted within the same call, the outcome would be exactly the same).
+A different way to mitigate these attacks is to seal orders with confidentiality (a \textit{dark} market).
+
+In a \emph{suppression attack}, Mallory floods the network with transactions until a trader executes her order.
+Such selective denial of service is possible by an off-chain operator.
+With on-chain continuous markets, it is not possible to suppress Alice's transaction while also letting through a transaction from a taker---suppression applies to all Ethereum transactions or none.
+A call market is uniquely vulnerable because it eventually times out (which does not require an on-chain transaction) and new orders cannot be added.
+We still award a call market partial mitigation since suppression attacks are expensive (\cf Fomo3D attack~\cite{eskandari2019sok}).
+If the aim of suppression is a temporary denial of service (captured by attack 5 in the table), then all on-chain markets are vulnerable to this expensive attack.
+
+Some attacks combine more than one insertion, displacement, and/or suppression attacks.
+AMMs are vulnerable to a double insertion called a sandwich attack~\cite{ZQFLG21} which bookends a victim's trade with the front-runner's trades (plus additional variants).
+In a traditional call market, a market clearing price is chosen and all trades are executed at this price.
+All bids made at a higher price will receive the assets for the lower clearing price (and conversely for lower ask prices): this is called a \textit{price improvement} and it allows traders to submit at their best price.
+A hybrid front-running attack allows Mallory to extract any price improvements.
+Consider the case where Alice's ask crosses Bob's bid with a material price improvement.
+Mallory inserts a bid at Alice's price, suppresses Bob's bid until the next call, and places an ask at Bob's price.
+She buys and then immediately sells the asset and nets the price improvement as arbitrage.
+To mitigate this in \cm, all price improvements are given to the miner (using \texttt{block.coinbase.transfer()}).
+This does not actively hurt traders---they always receive the same price that they quote in their orders---and it removes any incentive for miners to front-run these profits.
+
+Other front-running attacks use order cancellations (see Section~\ref{sec:cancel}) which \cm mitigates by running short-lived markets with no cancellations.
+
+There are two main takeaways from Table~\ref{tab:front}.
+Call markets provide strong resilience to front-running only bested slightly by dark markets like TEX~\cite{khalil2019tex}, however they do it through design---no cryptography and no two-round protocols.
+A second observation is that dark call markets, like Galal \etal~\cite{galalpublicly}, are no more resilient to front-running than a lit market (however confidentiality could provide resilience to predatory trading algorithms that react quickly to trades without acutally front-running).
+
+% = = = = =
 

### 2021-09-11 LaTeX-LNCS-2022/sections/appendix.tex
Done up to Section 5

@@
 
-\subsubsection{Arbitrum}
+Arbitrum and Ethereum Optimism are the two prominent deployments of an optimistic roll-up.
+Arbitrum  uses a multi-round dispute process that results in very minimal L1 gas costs to resolve a dispute.
+Specifically, if a dispute over a transaction arrises, the L1 cost of resolving the dispute is a small fraction of the cost of executing the transaction itself (whereas in Optimism, the dispute resolution cost is essentially the same as executing the transaction).
 
-Arbitrum is an Ethereum Layer 2 scaling solution that operates as an optimistic roll-up~\cite{kalodner2018arbitrum}.
-Arbitrum runs entire DApps inside its environment, which acts like a container and requires special bridge contacts to interact with `normal' (or Layer 1) Ethereum DApps.
-To deploy a DApp on Arbitrum, or to execute a function on an existing Arbitrum DApp, the transaction is sent to an \textit{Inbox contract} on Layer 1.
-The transaction is not executed, it is only recorded (as calldata) in the Inbox.
-Like any other transactions on Ethereum, miners determine the order of the transactions sent to this contract.
-A set of validators (open to anyone) are watching the Inbox contract for new transactions.
-Once an Inbox transaction is finalized in an Ethereum block, validators will execute the transaction and assert the result of the execution to other validators on a sidechain called ArbOS.
-Once the dispute challenge period is over, the new state of ArbOS will be inserted into Ethereum.
-As the Inbox contract maintains all Arbitrum transactions, anyone can recompute the entire current state of the ArbOS and file a dispute if executions are not performed correctly.
-Disputes are adjudicated by Ethereum itself and require essentially constant gas costs, regardless of the size of the gas costs of the transaction being disputed
+Our \cm variant is not the first roll-up-based order book.
+Loopring 3.0\footnote{\url{https://loopring.org}} offers a continuous-time order book.
+The primary difference is that orders in Loopring 3.0 are submitted off-chain to the operator directly, whereas our variant uses on-chain submission so that the roll-up server does not need to be publicly reachable.
+Loopring 3.0 can operate near high-frequency trading as order submission is unhampered by Ethereum.
+However, its  roll-up proof does not ensure that the exchange did not reorder transactions, which is particularly problematic in a continuous-time order book.
+Traders who prioritize trade fairness might opt for a solution like our variant, while traders who want speed would vastly prefer the Loopring architecture which offers near-CEX speed while being non-custodial.
+Loopring leaves a regulatory hook whereas our variant could be nearly as difficult to regulate as a fully on-chain solution if the roll-up server was kept anonymous: Ethereum and Arbitrum themselves would be the only regulatory hooks.
 

### 2021-09-11 LaTeX-LNCS-2022/sections/paper.tex
Done up to Section 5

@@
 
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
-% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
-
 %============= Performance =================== %
@@
 
-% = = = = = = = = = = = = = = = = = = = = = = = = =  %
-\section{\cm on Layer 2}\label{sec:rollups}
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
 
-We consider an alternative design for \cm that is almost as difficult to regulate as a fully on-chain solution.
-In this design, an off-chain component is introduced to boost performance but it only interacts with the Ethereum network and never directly with traders.
-Traders still only interact with Ethereum.
+\section{\cm on Arbitrum}
+\label{sec:rollups}
 
-\subsection{Roll-ups}
+\textit{Layer 2 (L2)} solutions~\cite{gudgeon2020sok} are a group of scaling technologies proposed to address specific drawbacks of executing transactions on Ethereum, which is considered \textit{Layer 1 (L1)}.
+Among these proposals, \textit{roll-ups} prioritize reducing gas costs (as opposed to other valid concerns like latency and throughput, which are secondary for \cm).
+We review two variants, \textit{optimistic roll-ups} and \textit{zk roll-ups}, in Appendix~\ref{app:rollup}.
+Briefly, in a roll-up, every transaction is stored (but not executed) on Ethereum, then executed off-chain, and the independently verifiable result is pushed back to Ethereum, with some evidence of being executed correctly.
+In the Appendix, we also compare \cm on Arbitrum to Loopring 3.0.
 
-We consider an alternative design for \cm that is almost as difficult to regulate as a fully on-chain solution.
-In this design, an off-chain component is introduced to boost the performance but it only interacts with the Ethereum network and never directly with traders.
-Traders still only interact with Ethereum.
-
-% For background information on different types of roll-ups, please see Appendix~\ref{app:rollup}
-
-\textit{Layer 2} solutions are a group of technologies that are designed and proposed to address specific drawbacks of executing transactions on \textit{Layer 1} (\ie Ethereum and other blockchains)~\cite{gudgeon2020sok}.
-These technologies focus on fast transaction throughput, reducing gas costs, or reducing transaction latency.
-When using \cm, we strive to reduce the gas cost as performance is the main bottleneck.
-Thus, we choose a Layer 2 technology called \textit{roll-up}.
-This technology aims at reducing the gas cost for operating on Layer 1 by taking the transaction executions off-chain and only using the Ethereum blockchain for storing data.
-In a roll-up, every transaction is executed by a server or cluster of servers known as \textit{validators} that can be run by a collection of users or third party operators (here they can be run by the token issuer).
-These validators then push the result of the executions (\ie updates in the EVM state) back to the Ethereum and assure the Ethereum network that the transactions have been executed correctly.
-
-A function can be computed off-chain and the new state of the DApp, called a \textit{rollup}, is written back to the blockchain, accompanied by either (1) a proof that the function was executed correctly, or (2) a dispute resolution process that can resolve, on-chain, functions that are not executed correctly (\eg Arbitrum~\cite{kalodner2018arbitrum}).
-In the case of (1), validating the proof must be cheaper than running the function itself.
-There are two main approaches: (1a) the first is to use cryptographic proof techniques (\eg SNARKS~\cite{BCGTV13,GGPR13} and variants~\cite{BBHR19}).
-This is called a \textit{zk-rollup}.
-Note that the proofs are heavy to compute (introducing a burden to the validators who generate them) but considered valid once posted to the Ethereum.
-The second approach (1b) is to execute the function in a trusted execution environment (TEE; \eg Intel SGX) and validate the TEE's quote on-chain (\eg Ekiden~\cite{cheng2019ekiden}).\footnote{The TEE-based approach is mired by recent attacks on SGX~\cite{SGX1,SGX2,SGX3,SGX4}, however these attacks do not necessarily apply to the specifics of how SGX is used here, and safer TEE technologies like Intel TXT (\cf~\cite{ZBC+19}) can be substituted.} Approach (2) is called an \textit{optimistic roll-up}.
-Although the dispute time delays result in a slower transaction finality, optimistic roll-ups substantially increase the performance by decreasing the gas cost.
-
-%It uses a side chain (a roll-up chain) that is run on top of Layer 1.
-Once the executions are performed, validators assert the new states of the roll-up chain to the Ethereum and wait for anyone to dispute these assertions.
-
-%Therefore, we choose this roll-up solution to for the Layer 2 implementation of \cm.
+We choose to experiment with \cm on the optimistic rollup Arbitrum.\footnote{See \url{https://offchainlabs.com} for more current details than the 2018 \textit{USENIX Security} paper~\cite{kalodner2018arbitrum}.} To deploy a DApp on Arbitrum, or to execute a function on an existing Arbitrum DApp, the transaction is sent to an \textit{inbox} on L1.
+It is not executed on L1, it is only recorded (as calldata) in the inbox.
+An open network of \textit{validators} watch the inbox for new transactions.
+Once inbox transactions are finalized in an Ethereum block, validators will execute the transactions and assert the result of the execution to other validators on a sidechain called \textsf{ArbOS}.
+As the Inbox contract maintains all Arbitrum transactions, anyone can recompute the entire current state of the ArbOS and file a dispute if executions are not correctly reported on ArbOS.
+Disputes are adjudicated by Ethereum itself and require a small, constant amount of gas, invariant to how expensive the transaction being disputed is.
+When the dispute challenge period is over, the new state of ArbOS is stored as a checkpoint on Ethereum.
 
 % = = = = = = = = = = = = = = = = = = = = = = = = =  %
-\subsection{Arbitrum}
-
-Arbitrum is an Ethereum Layer 2 scaling solution that operates as an optimistic roll-up~\cite{kalodner2018arbitrum}.
-Arbitrum runs entire DApps inside its environment, which acts like a container and requires special bridge contacts to interact with `normal' (or Layer 1) Ethereum DApps.
-To deploy a DApp on Arbitrum, or to execute a function on an existing Arbitrum DApp, the transaction is sent to an \textit{Inbox contract} on Layer 1.
-The transaction is not executed, it is only recorded (as calldata) in the Inbox.
-Like any other transactions on Ethereum, miners determine the order of the transactions sent to this contract.
-A set of validators (open to anyone) are watching the Inbox contract for new transactions.
-Once an Inbox transaction is finalized in an Ethereum block, validators will execute the transaction and assert the result of the execution to other validators on a sidechain called ArbOS.
-Once the dispute challenge period is over, the new state of ArbOS will be inserted into Ethereum.
-As the Inbox contract maintains all Arbitrum transactions, anyone can recompute the entire current state of the ArbOS and file a dispute if executions are not performed correctly.
-Disputes are adjudicated by Ethereum itself and require essentially constant gas costs, regardless of the size of the gas costs of the transaction being disputed
-
-% = = = = = = = = = = = = = = = = = = = = = = = = =  %
-\subsection{\cm on Arbitrum}
+\subsection{\cm Performance Measurements on Arbitrum}
 \input{tables/performance_Arbitrum}
 
-\textit{Testing Platforms.} To experiment with Arbitrum, we used the Arbitrum Rollup chain hosted on the Rinkeby testnet.
-We implemented a variant of \cm(\href{https://rinkeby-explorer.arbitrum.io/address/0x0aa5449a9f7fa34a81ce1dc720563938a27e8b03}{[https://rinkeby-explorer.arbitrum.io/]}) and ran the same experiments that we previously performed on Layer 1.
+\textit{Testing Platforms.} We implement \cm using the Arbitrum Rollup chain hosted on the Rinkeby testnet.
+It is visible and can be interacted with here: \href{https://rinkeby-explorer.arbitrum.io/address/0x0aa5449a9f7fa34a81ce1dc720563938a27e8b03}{[Arbitrum Explorer]}.
 To call functions on \cm, traders can (i) send transactions directly to the \href{https://rinkeby.etherscan.io/address/0x578BAde599406A8fE3d24Fd7f7211c0911F5B29e}{Inbox contract}, or (ii) use a relay server (called a \textit{Sequencer}) provided by the Arbitrum.
-The sequencer will group, order, and send all pending transactions together as a single Rinkeby transaction to the Inbox (and pays the gas).
+The sequencer will group, order, and send all pending transactions together as a single Rinkeby transaction to the inbox (and pays the gas).
 
-Recall that \cm implements an exchange between ETH and tokens.
-To use Layer 1 assets on Layer 2, Arbitrum provides two bridge contracts: one for ETH, and one for tokens compliant with ERC20 or other standard interfaces.
-Prior to trading, a trader uses the bridge to move their ETH to the same address on Layer 2 and then move the ETH to \cm with a Layer 2 transaction.
-From the user's perspective, tokens work similarly although the backend details are more complex.
-Finally, withdrawals work essentially same way in reverse, but are only final on Layer 1 after a dispute challenge period (currently 1 hour).\footnote{Layer 1 users might accept assets before they are finalized if they determine their eventual emergence on Layer 1 is indisputable (\textit{eventual finality}).}
+In our \cm variant on Arbitrum, the validators do all computations (both enqueuing and dequeuing) so we choose to use a heap with dynamic array for our priority queue, which balances the expense of both operations.
+Heaps are 32\% more efficient than linked lists for submitting orders and 29\% less efficient for closing.
+Recall that without a roll-up, such a priority queue can only match 38 pairs at a cost of 5,372,679 gas.
+Table~\ref{tab:arbitrum_performance} shows that 38 pairs cost only 6,569 in L1 gas (a 99.88\% savings).
+This is the cost of submitting the \texttt{closeMarket()} transaction to the inbox to be recorded, which is 103 bytes of calldata.
+Most importantly, \texttt{closeMarket()} always costs 6,569 even as the number of trades increase from 38 pairs.
+Of course, as the number of trades increase, the work for the validators on L2 increases, as measured in ArbGas.
+The price of ArbGas in Gwei is not well-established but is anticipated to be relatively cheap.
+Finally, for traders submitting an order, the L1 cost is reduced from 207,932 to 6,917.
 
-%\input{tables/performance_Arbitrum.tex}
-
-%Table~\ref{tab:arbitrum_performance} compares the cost of executing the maximum number of trades on Ethereum (Kovan testnet) and executing the same number of trades when running \cm on Layer 2 with Arbitrum.
-The fourth column of the Table represents the Ethereum gas cost for relaying the transaction to the Arbitrum EthBridge contract and is paid in ETH.
-Note that here we report the cost of sending the transaction directly to the Arbitrum EthBridge contract and not through the aggregator~\footnote{The Layer 1 cost reported on the Kovan block explorer represents the gas cost related to the entire batch of transactions.}.
-
-In our \cm variant on Arbitrum, the token issuer does all the computation (both enqueuing and dequeuing).
-Thus, we switch the priority queue to use a heap with dynamic array, which balances the expense of both operations (instead of optimizing for dequeuing in \texttt{closeMarket()}).
-Our experiments show that on Arbitrum, heaps are 32\% more efficient than non-Heaps for submitting orders and 29\% less efficient for closing.
-Recall that without a roll-up, such a priority queue can only match 38 pairs at a cost of 5,372,679 gas.
-With Arbitrum roll-ups, 38 pairs cost only 6,569 in Layer 1 gas (a 99.9\% savings).
-This is effectively the cost of submitting \texttt{closeMarket()} transaction to the inbox and recording the function call, which is 103 bytes of calldata.
-As the number of pairs increases, Layer 1 gas cost is constant.
-For traders submitting an order, the cost is reduced from  207,932 to 6,917.
-
-While the runtime of a transaction is no longer an issue for Ethereum, it is still an issue for the validators.
-Similar to Ethereum miners, validators do measure the amount of gas (called ArbGas in Arbitrum) a transaction takes, although Arbitrum emulates EVM code with its own different opcodes.
-Thus, ArbGas with a roll-up and Layer 1 gas without a roll-up are not directly comparable but both increase and decrease proportionately with the complexity of running the function.
-Closing a market with 38 pairs costs 46,705,693 ArbGas.
-%Until Arbitrum deploys on mainnet, the price of ArbGas in Gwei (or USD) is unknown but it is thought to be relatively very cheap.
-
-Our \cm variant is not the first roll-up-based order book.
-Loopring 3.0\footnote{\url{https://loopring.org}} offers a continuous-time order book.
-The primary difference is that orders in Loopring 3.0 are submitted off-chain to the operator directly, whereas our variant uses on-chain submission so that the roll-up server does not need to be publicly reachable.
-Loopring 3.0 can operate near high-frequency trading as order submission is unhampered by Ethereum.
-However, its  roll-up proof does not ensure that the exchange did not reorder transactions, which is particularly problematic in a continuous-time order book.
-Traders who prioritize trade fairness might opt for a solution like our variant, while traders who want speed would vastly prefer the Loopring architecture which offers near-CEX speed while being non-custodial.
-Loopring leaves a regulatory hook whereas our variant could be nearly as difficult to regulate as a fully on-chain solution if the roll-up server was kept anonymous: Ethereum and Arbitrum themselves would be the only regulatory hooks.
-
-	% JC: Incorporate this comparison to Ethereum Optimism
-	% "The choice between one-round (e.g., “optimistic rollup”) and multi-round (e.g., Arbitrum Rollup) boils down to a tradeoff between on-chain cost and time to resolve a dispute.
-A one-round approach requires emulating a full call on-chain, which can be expensive — and this limits contracts to 		calls that can be executed comfortably within Ethereum’s global gas limit." -Ed Felten
-
-% = = = = = = = = = = = = = = = = = = = = = = = = =  %
-\subsection{Front-running on Arbitrum}
-\label{sec:frontarb}
-
-In our \cm variant on the Arbitrum, traders can submit transactions to the Layer 1 Inbox contract instead of directly to the \cm DApp.
-This has the same front-running profile as \cm itself; only the Layer 1 destination address is different.
-If a sequencer is mandatory, it acts with the same privilege as a Layer 1 Ethereum miner in ordering the transactions it receives.
-Technically, sequencers are not limited to roll-ups and could be used in the context of normal Layer 1 DApps, but they are more apparent in the context of roll-ups.
-A sequencer could be trusted to execute transactions in the order it receives them, outsource to a fair ordering service, or (in a tacit acknowledge of the difficulties of preventing front-running) auction off permission to order transactions to the highest bidder.
-As shown in Table~\ref{tab:front}, a sequencer is an additional front-running actor but does not otherwise change the kinds of attacks that are possible.
-
-% JC: I think too minor to mention
-%Finally, we note a minor technical issue.
-Recall that in \cm, price improvements are given to miners to prevent a hybrid frontrunning attack.
-As Arbitrum does not run on L1, it burns (bridged) ETH sent via \texttt{block.coinbase()}.
-With some effort, Arbitrium could be updated to route the payment to the L1 miner of the block that added closeMarket() to the inbox.
-
-%= = = = = =  = =  =  Rollups=  = = = = = = = = =%
-
-%\section{\cm Variant with Off-chain Closing}
-%\label{sec:rollups}
-%
-%We have avoided augmenting \cm with centralized components and third party services as our research question concerns the feasibility of a system with a minimum of regulatory hooks.
-However from a regulatory stance, there is a big difference between an architecture where the centralized component is publicly visible and interacted with by users (\eg most DEXes, rollup architectures like Loopring, and commit-chain solutions like TEX).
-We briefly consider an alternative design that is almost as difficult to regulate as a fully on-chain solution.
-In this design, an off-chain component is introduced to boost performance but it only interacts with the Ethereum network and never directly with traders.
-Traders still only interact with Ethereum.
-%
-%A function can be computed off-chain and the new state of the DApp, called a \textit{rollup}, is written back to the blockchain, accompanied by either (1) a proof that the function was executed correctly, or (2) a dispute resolution process that can resolve, on-chain, functions that are not executed correctly (\eg Arbitrum~\cite{kalodner2018arbitrum}).
-In the case of (1), validating the proof must be cheaper than running the function itself.
-There are two main approaches to (1): the first is to use cryptographic proof techniques (\eg SNARKS~\cite{BCGTV13,GGPR13} and variants~\cite{BBHR19}), and the second is to execute the function in a trusted execution environment (TEE; \eg Intel SGX) and validate the TEE's quote on-chain (\eg Ekiden~\cite{cheng2019ekiden}).\footnote{The TEE-based approach is mired by recent attacks on SGX~\cite{SGX1,SGX2,SGX3,SGX4}, however these attacks do not necessarily apply to the specifics of how SGX is used here, and safer TEE technologies like Intel TXT (\cf~\cite{ZBC+19}) can be substituted.}
-%
-%We implemented a variant of \cm using rollups on Arbitrum.\footnote{\url{https://offchainlabs.com} for more current details than the 2018 \textit{USENIX Security} paper~\cite{kalodner2018arbitrum}.} In this model, the token issuer (or other interested party) will run a dedicated server to watch Ethereum for function invocations submitted and sequenced on-chain, perform the function call off-chain, and write the resultant state on-chain.
-Anyone capable of running EVM code can verify the result.
-If it is incorrect, a dispute can be filed (with the correct state) and an on-chain correction will be made.
-With or without disputes, participants that validate the function calls for themselves can proceed knowing that the correct state will eventually be finalized.
-%
-%% JC: Incorporate this comparison to Ethereum Optimism
-%% "The choice between one-round (e.g., “optimistic rollup”) and multi-round (e.g., Arbitrum Rollup) boils down to a tradeoff between on-chain cost and time to resolve a dispute.
-A one-round approach requires emulating a full call on-chain, which can be expensive — and this limits contracts to calls that can be executed comfortably within Ethereum’s global gas limit." -Ed Felten
-%
-%%Mahsa: to discuss: Withdrawing Ethers from Arbitrum takes much time!
-when withdrawing, the withdrawal will be in a "pending" state during a "challenge period" of 830 blocks (30 - 120 minutes on Kovan).
-After that, the funds will be available on layer 1 in your lockbox
-%
-%In our \cm variant with rollups, the token issuer does all the computation (both enqueuing and dequeuing).
-Thus we switch the priority queue to use a heap with dynamic array, which balances the expense of both operations (instead of optimizing for dequeuing in \texttt{closeMarket()}).
-Recall that on-chain, such a priority queue can only match 38 pairs at a cost of 5,372,679 gas.
-With rollups, 38 pairs cost 38,863 gas.
-As the pairs increase, the cost is essentially constant (\eg 1000 pairs cost 38,851 as opposed to 457,326,935 on-chain).
-Submitting an order costs 39,169 gas on average as opposed to 207,932 on-chain.
-%
-%Our \cm variant is not the first rollup-based order book.
-Loopring 3.0\footnote{\url{https://loopring.org}} offers a continuous-time order book.
-The primary difference is that orders in Loopring 3.0 are submitted off-chain to the operator directly, whereas our variant uses on-chain submission so that the rollup server does not need to be publicly reachable.
-Loopring 3.0 can operate near high frequency trading as order submission is unhampered by Ethereum, however its  rollup proof does not ensure that the exchange did not reorder transactions, which is particularly problematic in a continuous-time order book.
-Traders who prioritize trade fairness might opt for a solution like our variant, while traders who want speed would vastly prefer the Loopring architecture which offers near-CEX speed while being non-custodial.
-Loopring leaves a regulatory hook whereas our variant could be nearly as difficult to regulate as a fully on-chain solution if the rollup server was kept anonymous: Ethereum and Arbitrum themselves would be the only regulatory hooks.
+Running \cm on Arbitrum has one large caveat.
+If the ERC20 tokens being traded are not issued on ArbOS, which is nearly always the case today, they first need to be \textit{bridged} onto ArbOS, as does the ETH.
+Traders send ETH or tokens to Arbitrum's bridge contracts which create the equivalent amount at the same address on L2.
+Withdrawals work the same way in reverse, but are only final on Layer 1 after a dispute challenge period (currently 1 hour).\footnote{Layer 1 users might accept assets before they are finalized as they can determine their eventual emergence on Layer 1 is indisputable (\textit{eventual finality}).}
 
@@
 
+% = = = = = = = = = = = = = = = = = = = = = = = = =  %
+\subsection{Front-running on Arbitrum}
+\label{sec:frontarb}
+
+In our \cm variant on the Arbitrum, traders can submit transactions to the Layer 1 Inbox contract instead of directly to the \cm DApp.
+This has the same front-running profile as \cm itself; only the Layer 1 destination address is different.
+If a sequencer is mandatory, it acts with the same privilege as a Layer 1 Ethereum miner in ordering the transactions it receives.
+Technically, sequencers are not limited to roll-ups and could be used in the context of normal Layer 1 DApps, but they are more apparent in the context of roll-ups.
+A sequencer could be trusted to execute transactions in the order it receives them, outsource to a fair ordering service, or (in a tacit acknowledge of the difficulties of preventing front-running) auction off permission to order transactions to the highest bidder (called a \textit{MEV auction}).
+As shown in Table~\ref{tab:front}, a sequencer is an additional front-running actor but does not otherwise change the kinds of attacks that are possible.
+
+% JC: I think too minor to mention
+%Finally, we note a minor technical issue.
+Recall that in \cm, price improvements are given to miners to prevent a hybrid frontrunning attack.
+As Arbitrum does not run on L1, it burns (bridged) ETH sent via \texttt{block.coinbase()}.
+With some effort, Arbitrium could be updated to route the payment to the L1 miner of the block that added closeMarket() to the inbox.
+
 % = = = = =

### 2021-09-11 LaTeX-LNCS-2022/sections/appendix.tex
candidate draft

@@
 \includegraphics[width=1\textwidth]{fig/lissyL2.pdf}
-\caption{\footnotesize{\cm L2 Diagram}  \label{fig:lissyl2}}
+\caption{\footnotesize{\textblue{Modify with inbox, sequencer as well}}  \label{fig:lissyl2}}
 \end{figure}
@@
 A non-custodial DEX solves the big issue of a CEX---the operator stealing the funds---however trade execution is still not provably fair, funds can still be indirectly stolen by a malicious exchange executing unauthorized trades, and server downtime is a common frustration for traders.
-An enhancement is to prove that trade execution is correct (\eg Loopring) but these proofs have blind spots (discussed in section~\ref{sec:rollups}).
+An enhancement is to prove that trade execution is correct (\eg Loopring) but these proofs have blind spots (discussed above in Appendix~\ref{app:rollup}).
 
@@
 The Ethereum refund model should be considered further by Ethereum developers to better incentivize developers to be less wasteful in using storage.
+
+% = = = = = = = 
+% = = = = = = = 
+% = = = = = = =
+
+\section{Collateralization Options in Call Markets}
+\label{app:collateral}
+
+in \cm, both the tokens and ETH that a trader wants to potentially use in the order book are pre-loaded into the contract.
+Consider Alice, who holds a token and decides she wants to trade it for ETH.
+In this model, she must first transfer the tokens to the contract and then submit an ask order.
+If she does this within the same block, there is a chance that a miner will execute the ask before the transfer and the ask will revert.
+If she waits for confirmation, this introduces a delay.
+This delay seems reasonable but we point out a few options it could be addressed:
+
+\begin{enumerate}
+
+\item \textbf{Use \texttt{msg.value}.} For the ETH side of a trade (\ie for bids), ETH could be sent with the function call to \texttt{submitBid()} to remove the need for    \texttt{depositEther()}.
+This works for markets that trade ERC20 tokens for ETH, but would not work for ERC20 to ERC20 exchanges.
+
+\item \textbf{Merge Deposits with Bids/Asks.} \cm could have an additional function that atomically runs the functionality of \texttt{depositToken()} followed by the functionality of \texttt{submitAsk()}.
+This removes the chance that the deposit and order submission are ordered incorrectly.
+
+\item \textbf{Use ERC20 Approval.} Instead of \cm taking custody of the tokens, the token holder could simply approve \cm to transfer tokens on her behalf.
+If \cm is coded securely, it is unconcerning to allow the approval to stand long-term and the trader never has to lock up their tokens in the DApp.
+The issue is that there is no guarantee that the tokens are actually available when the market closes (\ie Alice can approve a DApp to spend 100 tokens even if she only has 5 tokens or no tokens).
+In this case, \cm would optimistically try to transfer the tokens and if it fails, move onto the next order.
+This also gives Alice an indirect way to cancel an order, by removing the tokens backing the order---this could be a feature or it could be considered an abuse.
+
+\item \textbf{Use a Fidelity Bond.} Traders could post some number of tokens as a fidelity bond, and be allowed to submit orders up to 100x this value using approve.
+If a trade fails because the pledged tokens are not available, the fidelity bond is slashed as punishment.
+This allows traders to side-step time-consuming transfers to and from \cm while still incentivizing them to ensure that submitted orders can actually be executed.
+The trade-off  is that \cm needs to update balances with external calls to the ERC20 contract instead of simply updating its internal ledger.
+
+\end{enumerate}
+
+\section{Market Clearing Prices}
+
+% JC: Not part of design landscape, find a new home for it
+
+Call markets are heralded for fair price discovery.
+This is why many exchanges use a call market at the end of the day to determine the closing price of an asset, which is an important price both optically (it is well-published) and operationally (many derivatives settle based on the closing price).
+We purposely do not compute a `market clearing price' with \cm because miners can easily manipulate the price (\ie include a single wash trade at the price they want fixed), although they forgo profit for doing so.
+This is not merely hypothetical---Uniswap (the prominent quote-drive, on-chain exchange) prices have been manipulated to exploit other DeFi applications relying on them.
+Countermeasures to protect Uniswap price integrity could also apply to \cm: (1) taking a rolling median of prices over time, and (2) using it alongside other sources for the same price and forming a consensus.
+While \cm does not emit a market clearing price, it can be computed by a web application examining the order book at market close.

### 2021-09-11 LaTeX-LNCS-2022/sections/paper.tex
candidate draft

@@
 This is the cost of submitting the \texttt{closeMarket()} transaction to the inbox to be recorded, which is 103 bytes of calldata.
-Most importantly, \texttt{closeMarket()} always costs 6,569 even as the number of trades increase from 38 pairs.
+Most importantly, \texttt{closeMarket()} always costs 6,569 even as the number of trades increase from 38 pairs to thousands or millions of pairs.
 Of course, as the number of trades increase, the work for the validators on L2 increases, as measured in ArbGas.
 The price of ArbGas in Gwei is not well-established but is anticipated to be relatively cheap.
-Finally, for traders submitting an order, the L1 cost is reduced from 207,932 to 6,917.
+Arbitrum also reduces the costs for traders to submit an order: from 207,932 to 6,917 in L1 gas.
 
@@
 Traders send ETH or tokens to Arbitrum's bridge contracts which create the equivalent amount at the same address on L2.
-Withdrawals work the same way in reverse, but are only final on Layer 1 after a dispute challenge period (currently 1 hour).\footnote{Layer 1 users might accept assets before they are finalized as they can determine their eventual emergence on Layer 1 is indisputable (\textit{eventual finality}).}
+Withdrawals work the same way in reverse, but are only final on L1 after a dispute challenge period (currently 1 hour).\footnote{L1 users might accept assets before they are finalized as they can determine their eventual emergence on L1 is indisputable (\textit{eventual finality}).}
 
-% = = = = = = = = = = = = = = = = = = = = = = = = =  %
-
-\section{Design Alternatives and Extensions}
-
-\cm is designed as a base class that can be extended and customized. Here, we evaluate potential modifications.
-
-\begin{figure}[t]
-\centering
-\includegraphics[width=1\textwidth]{fig/MindMapDraft3.png}
-\caption{\footnotesize{Mind Map Draft}  \label{fig:rmindmap}}
-\end{figure}
-% = = = = = = = = = = = = = = = = = = = = = = = = =  %
-
-\subsection{Token Divisibility and Ties}
-
-When executing trades, if the volume of the current best bid does not match the best ask, the larger order is partially filled and the remaining volume is considered against the next best order.
-A common trading rule (that does resist front-running) is to fill ties in proportion to their volume (\ie \textit{pro rata} allocation)\footnote{If Alice and Bob bid the same price for 100 tokens and 20 tokens respectively, and there are only 60 tokens left in marketable asks, Alice receives 50 and Bob 10.}, however this approach does not always work.
-Consider the following corner case: 3 equally priced bids of 1 non-divisible token and 1 ask at the same price.
-There is no good option: (1) the bids could all be dropped, (2) the bids could be prioritized based on time, or (3) the bid could be randomly chosen (\cf Libra~\cite{mavroudis2019libra}).
-
-\paragraph{Evaluation.} We avoid (1) which is fair but not market efficient.
-We note the conditions under which pro rata allocation fails (\ie non-divisible assets, an exact tie on price, and part of the final allocation) are improbable.
-In \cm, tokens are assumed to be divisible but we otherwise default to (2).
-This means insertion front-running attacks are possible for this corner case.
-However if these attacks proved to be a problem in practice, (3) is a better solution with one main drawback: on-chain sources of `randomness' are generally deterministic and manipulatable by miners~\cite{bonneau2015random,buenz2017proofs}, countermeasures can take a few blocks to select~\cite{boneh2018verifiable}.
-
-% = = = = = = = = = = = = = = = = = = = = = = = = =  %
-
-\subsection{Order Cancellations}
-\label{sec:cancel}
-
-\cm does not support order cancellations. We intend to open and close markets quickly (on the order of blocks), so orders are relatively short-lived.
-
-\paragraph{Evaluation.} Support for cancellation opens the market to new front-running issues where other traders (or miners) can displace cancellations until after the market closes.
-However, one benefit of a call market is that beating a cancellation with a new order has no effect, assuming the cancellation is run any time before the market closes.
-Also, cancellations have a performance impact.
-Cancelled orders can be removed from the underlying data structure or accumulated in a list that is cross-checked when closing the market.
-Removing orders requires a more verbose structure than a priority queue (\eg a self-balancing binary search tree instead of a heap; or methods to traverse a linked list rather than only pulling from the head).
-While client software could help point out where the order is in the data structure, the order book can change between submitting the cancellation request and running the method.
-%A linked list with mapping that returns the key for each submitted order seems to be the most tenable data structure.
-
-% = = = = = = = = = = = = = = = = = = = = = = = = =  %
-
-\subsection{Market Clearing Price}
-
-% JC: Not part of design landscape, find a new home for it
-
-Call markets are heralded for fair price discovery.
-This is why many exchanges use a call market at the end of the day to determine the closing price of an asset, which is an important price both optically (it is well-published) and operationally (many derivatives settle based on the closing price).
-We purposely do not compute a `market clearing price' with \cm because miners can easily manipulate the price (\ie include a single wash trade at the price they want fixed), although they forgo profit for doing so.
-This is not merely hypothetical---Uniswap (the prominent quote-drive, on-chain exchange) prices have been manipulated to exploit other DeFi applications relying on them.
-Countermeasures to protect Uniswap price integrity could also apply to \cm: (1) taking a rolling median of prices over time, and (2) using it alongside other sources for the same price and forming a consensus.
-While \cm does not emit a market clearing price, it can be computed by a web application examining the order book at market close.
-
-% = = = = = = = = = = = = = = = = = = = = = = = = =  %
-
-\subsection{Scheduling Events}
-
-\cm is a one-shot market.
-However it can be extended to reopen with a clean order book after \texttt{closeMarket()} is run.
-Modifiers can enforce when the market operates openly (collecting orders) and when close can be run.
-In the Princeton paper~\cite{clark2014decentralizing}, the call market is envisioned to run as an alt-coin, where orders accumulate within a block and a miner closes the market as part of the logic of producing a new block (\ie within the same portion of code as computing their coinbase transaction in Bitcoin or \texttt{gasUsed} in Ethereum).
-
-If the call market runs as a DApp on Ethereum, it seems difficult to open and close the market on every block.
-Someone needs to call the \texttt{closeMarket()} for every block (we return to who this is later), but the market will only work as intended if miners execute this function after every \texttt{submitBid()} and \texttt{submitAsk()} invocation.
-Since price improvements are paid to the miners, the miner is actually incentivized to run \texttt{closeMarket()} last to make the most profit.
-This pattern is called miner extractable value (MEV)~\cite{daian2019flash} and is usually considered in the context of attacks.
-However in our case, MEV is a feature.
-Efficient algorithms for miners to automatically find MEV opportunities is an open research problem.
-
-A close alternative is to allow markets to open and close on different blocks.
-In this alternative, the \texttt{closeMarket()} function calls \texttt{openMarket()} as a subroutine and sets two modifiers: orders are only accepted in the block immediately after the current block (\ie the block that executes the \texttt{closeMarket()}) and \texttt{closeMarket()} cannot be run again until two blocks after the current block.
-
-The final issue is who invokes \texttt{closeMarket()} every other block?
-There are two issues here: the issue of scheduling the function call and the issue of paying for it.
-For scheduling the function call, we can do one of the following: rely on market participants, who are eager to trade, to reopen the market, offer a bounty to reopen the market, or use an external service like Ethereum Alarm Clock (which creates a regulatory hook).\footnote{\url{https://ethereum-alarm-clock-service.readthedocs.io/}} Next, we consider the second issue of who pays to close the market.
-
-% = = = = = = = = = = = = = = = = = = = = = = = = =  %
-
-\subsection{Who Pays to Close/Reopen the Market?}
-\label{sec:close}
-
-As miners are paid all price improvements in the market, it is possible that a miner might run \texttt{closeMarket()} and it would pay for itself.
-However, we consider two other scenarios that do not assume miners can automatically find MEV opportunities.
-One solution requires a modified closing function, \texttt{closeMarket(n)}, that only processes $n$ orders at a time until the order book is empty (this is sensible design in any case to safeguard against the order book from locking up because the number of orders exceeds the gas limit to process them).
-Once the time window for submitting orders has past, a new market is created (without settling the previous market).
-Every order submission on the new market also requires to run, say, \texttt{closeMarket(10)} on the older market, thus progressively closing the previous market while accepting orders to the new market.
-
-The second solution is to levy a carefully computed fee against the traders for every new order they submit.
-These fees are accumulated by the DApp to use as a bounty.
-When the time window for the open market elapses, the user who calls the \texttt{closeMarket()} function receives the bounty.
-
-\paragraph{Evaluation.} The first solution pattern has two issues: first, amortizing the cost of closing the market amongst the early traders of the new market is an added incentive to not submit orders early to the market; the second issue is if not enough traders submit orders in the new market, the old market never closes (resulting in a backlog of old markets waiting to close).
-The second solution is better, although not perfect: \texttt{closeMarket()} cost does not follow a tight linear increase with the number of orders, and gas prices vary over time which could render the bounty insufficient for offsetting the \texttt{closeMarket()} cost.
-However, an interested third party (such as the token issuer for a given market) might occasionally bailout the market when it halts on \texttt{closeMarket()} to facilitate further trading.
-If the DApp can pay for its own functions, an interested party can also arrange for a commercial service (\eg any.sender\footnote{\url{https://github.com/PISAresearch/docs.any.sender}}) to relay the \texttt{closeMarket()} function call on Ethereum (an approach called \textit{meta-transactions}) which introduces another regulatory hook.
-
-% = = = = = = = = = = = = = = = = = = = = = = = = =  %
-
-\subsection{Collateralization Options}
-
-In \cm, both the tokens and ETH that a trader wants to potentially use in the order book are pre-loaded into the contract.
-Consider Alice, who holds a token and decides she wants to trade it for ETH.
-In this model, she must first transfer the tokens to the contract and then submit an ask order.
-If she does this within the same block, there is a chance that a miner will execute the ask before the transfer and the ask will revert.
-If she waits for confirmation, this introduces a delay.
-This delay seems reasonable but we point out a few options it could be addressed:
-
-\begin{enumerate}
-
-\item \textbf{Use \texttt{msg.value}.} For the ETH side of a trade (\ie for bids), ETH could be sent with the function call to \texttt{submitBid()} to remove the need for    \texttt{depositEther()}.
-This works for markets that trade ERC20 tokens for ETH, but would not work for ERC20 to ERC20 exchanges.
-
-\item \textbf{Merge Deposits with Bids/Asks.} \cm could have an additional function that atomically runs the functionality of \texttt{depositToken()} followed by the functionality of \texttt{submitAsk()}.
-This removes the chance that the deposit and order submission are ordered incorrectly.
-
-\item \textbf{Use ERC20 Approval.} Instead of \cm taking custody of the tokens, the token holder could simply approve \cm to transfer tokens on her behalf.
-If \cm is coded securely, it is unconcerning to allow the approval to stand long-term and the trader never has to lock up their tokens in the DApp.
-The issue is that there is no guarantee that the tokens are actually available when the market closes (\ie Alice can approve a DApp to spend 100 tokens even if she only has 5 tokens or no tokens).
-In this case, \cm would optimistically try to transfer the tokens and if it fails, move onto the next order.
-This also gives Alice an indirect way to cancel an order, by removing the tokens backing the order---this could be a feature or it could be considered an abuse.
-
-\item \textbf{Use a Fidelity Bond.} Traders could post some number of tokens as a fidelity bond, and be allowed to submit orders up to 100x this value using approve.
-If a trade fails because the pledged tokens are not available, the fidelity bond is slashed as punishment.
-This allows traders to side-step time-consuming transfers to and from \cm while still incentivizing them to ensure that submitted orders can actually be executed.
-The trade-off  is that \cm needs to update balances with external calls to the ERC20 contract instead of simply updating its internal ledger.
-
-\end{enumerate}
-
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
 % = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
@@
 
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
+
+\section{Design Landscape}
+
+\begin{figure}[t]
+\centering
+\includegraphics[width=1\textwidth]{fig/MindMapDraft4.pdf}
+\caption{\footnotesize{A design landscape for on-chain call markets.}  \label{fig:rmindmap}}
+\end{figure}
+
+\cm is a simple base class that implements the core functionality of a call market.
+To use it in the real world, design decisions need to be made about how it will be used.
+Figure~\ref{fig:rmindmap} provides a design landscape for \cm deployment, with possible extensions and customizations.
+
+% = = = = = = = = = = = = = = = = = = = = = = = = =  %
+
+\subsection{Token Divisibility and Ties}
+
+A common trading rule is to fill ties in proportion to their volume (\ie \textit{pro rata} allocation)\footnote{If Alice and Bob bid the same price for 100 tokens and 20 tokens respectively, and there are only 60 tokens left in marketable asks, Alice receives 50 and Bob 10.}.
+This can fail when tokens are not divisible.
+Consider the following corner case: 3 equally priced bids of 1 non-divisible token and 1 ask at the same price: (1) the bid could be randomly chosen (\cf Libra~\cite{mavroudis2019libra}), or (2) the bid could be prioritized based on time.
+In \cm, tokens are assumed to be divisible.
+If the volume of the current best bid does not match the best ask, the larger order is partially filled and the remaining volume is considered against the next best order.
+We note the conditions under which pro rata allocation fails (\ie non-divisible assets, an exact tie on price, and part of the final allocation) are improbable.
+(1) is the fairest solution with one main drawback: on-chain sources of `randomness' are generally deterministic and manipulatable by miners~\cite{bonneau2015random,buenz2017proofs}, while countermeasures can take a few blocks to select~\cite{boneh2018verifiable}.
+We implement (2) which means front-running attacks are possible in this one improbable case.
+
+% = = = = = = = = = = = = = = = = = = = = = = = = =  %
+
+\subsection{Order Cancellations}
+\label{sec:cancel}
+
+Support for cancellation opens the market to new front-running issues where other traders (or miners) can displace cancellations until after the market closes.
+However, one benefit of a call market is that beating a cancellation with a new order has no effect, assuming the cancellation is run any time before the market closes.
+Also, cancellations have a performance impact.
+Cancelled orders can be removed from the underlying data structure or accumulated in a list that is cross-checked when closing the market.
+Removing orders requires a more verbose structure than a priority queue (\eg a self-balancing binary search tree instead of a heap; or methods to traverse a linked list rather than only pulling from the head).
+\cm does not support order cancellations.
+We intend to open and close markets quickly (on the order of blocks), so orders are relatively short-lived.
+
+%While client software could help point out where the order is in the data structure, the order book can change between submitting the cancellation request and running the method.
+%A linked list with mapping that returns the key for each submitted order seems to be the most tenable data structure.
+
+% = = = = = = = = = = = = = = = = = = = = = = = = =  %
+
+% = = = = = = = = = = = = = = = = = = = = = = = = =  %
+
+\subsection{Who Pays to Close/Reopen the Market?}
+\label{sec:close}
+
+In the Princeton paper~\cite{clark2014decentralizing}, the call market is envisioned as an alt-coin, where orders accumulate within a block and a miner closes the market as part of the logic of producing a new block (\ie within the same portion of code as computing their coinbase transaction in Bitcoin or \texttt{gasUsed} in Ethereum).
+In \cm, someone needs to execute  \texttt{closeMarket()} at the right time and pay for it, which is probably the most significant design challenge for \cm.
+
+Since price improvements are paid to the miners, the miner is incentivized to run \texttt{closeMarket()} if it pays for itself.
+Efficient algorithms for miners to automatically find `miner extractable value (MEV)' opportunities~\cite{daian2019flash} is an open research problem.
+Even if someone else pays to close the market, MEV smooths out some market functionality.
+Assume several orders are submitted and then \texttt{closeMarket()}.
+A naive miner might order the \texttt{closeMarket()} before the submitted orders, effectively killing those orders and hurting its own potential profit.
+MEV encourages miners to make sure a profitable \texttt{closeMarket()} in the mempool executes within its current block (to claim the reward for itself) and that it runs after other orders in the mempool to maximize its profit.
+
+Without MEV, markets should open and close on different blocks.
+In this alternative, the \texttt{closeMarket()} function calls \texttt{openMarket()} as a subroutine and sets two modifiers: orders are only accepted in the block immediately after the current block (\ie the block that executes the \texttt{closeMarket()}) and \texttt{closeMarket()} cannot be run again until two blocks after the current block.
+
+Another option is to have traders in the next call market pay to incrementally close the current market.
+For example, each order in the next market needs to pay to execute the next $x$ orders in the current market until the order book is empty.
+This has two issues: first, amortizing the cost of closing the market amongst the early traders of the new market disincentives trading early in the market; the second issue is if not enough traders submit orders in the new market, the old market never closes (resulting in a backlog of old markets waiting to close).
+
+A closely related option is to levy a carefully computed fee against the traders for every new order they submit.
+These fees are accumulated by the DApp to use as a bounty.
+When the time window for the open market elapses, the sender of the first \texttt{closeMarket()} function to be confirmed recieves the bounty.
+This is still not perfect: \texttt{closeMarket()} cost does not follow a tight linear increase with the number of orders, and gas prices vary over time which could render the bounty insufficient for offsetting the \texttt{closeMarket()} cost.
+If the DApp can pay for its own functions, an interested party can also arrange for a commercial service (\eg any.sender\footnote{\url{https://github.com/PISAresearch/docs.any.sender}}) to relay the \texttt{closeMarket()} function call on Ethereum (an approach called \textit{meta-transactions}).
+This creates a regulatory hook.
+
+The final option is to rely on an interested third party (such as the token issuer for a given market) to always close the market, or  occasionally bailout the market when one of the above mechanisms fail.
+An external service like Ethereum Alarm Clock\footnote{\url{https://ethereum-alarm-clock-service.readthedocs.io/}}  (which also creates a regulatory hook) can be used to schedule regular \texttt{closeMarket()} calls.
+
+% = = = = = = = = = = = = = = = = = = = = = = = = =  %
+
+\subsection{Collateralization Options}
+
+In \cm, both the tokens and ETH that a trader wants to potentially use in the order book are pre-loaded into the contract. We discuss some alternative designs in Appendix~\ref{app:collateral}.
+
+% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
+
 \section{Concluding Remarks}
@@
 Imagine you have just launched a token on Ethereum.
-Now want to be able to trade it.
+Now you want to be able to trade it.
 While the barrier to entry for exchange services is low, it still exists.
@@
 
-It may seem paradoxical or unethical to build for regulators exactly what they worry about.
+% It may seem paradoxical or unethical to build for regulators exactly what they worry about.
 However, we agreed that it was too difficult to answer our research questions without actual implementation and experimentation.

### 2021-09-11 LaTeX-LNCS-2022/sections/paper.tex
adding a textblue

@@
 This is the cost of submitting the \texttt{closeMarket()} transaction to the inbox to be recorded, which is 103 bytes of calldata.
-Most importantly, \texttt{closeMarket()} always costs 6,569 even as the number of trades increase from 38 pairs to thousands or millions of pairs.
+\textblue{Most importantly, \texttt{closeMarket()} always costs 6,569 even as the number of trades increase from 38 pairs to thousands or millions of pairs}.
 Of course, as the number of trades increase, the work for the validators on L2 increases, as measured in ArbGas.

### 2021-09-13 LaTeX-LNCS-2022/sections/paper.tex
changed the L2 diagram, added some texts and a ref to appendix

@@
 The price of ArbGas in Gwei is not well-established but is anticipated to be relatively cheap.
-Arbitrum also reduces the costs for traders to submit an order: from 207,932 to 6,917 in L1 gas.
+Arbitrum also reduces the costs for traders to submit an order: from 207,932 to 6,917 in L1 gas.\textblue{ Figure~\ref{fig:lissyl2} illustrates a high level overview of how traders interact with \cm on Arbitrum (\ie  bridge ETH into Arbitrum chain, execute functions on \cm \etc) in Appendix~\ref{app:rollup}.}
 

### 2021-09-13 LaTeX-LNCS-2022/sections/paper.tex
small tweaks
fixed the mindmap branch colors
hooks for improvements

--- 2021-09-11 LaTeX-LNCS-2022/sections/paper.tex
@@
 \item Which aspects of Ethereum were encountered that required deeper than surface-level knowledge to navigate?
-(Optimizing gas refunds, Solidity is not truly object-oriented, miner extractable value (MEV) can be leveraged for good, \textblue{add more?})
+(Optimizing gas refunds, Solidity is not truly object-oriented, miner extractable value (MEV) can be leveraged for good, and bridging assets for layer 2.)
 \item How hard is an on-chain exchange to regulate? (The design leaves almost no regulatory hooks beyond miners (and sequencers on layer 2).)
@@
 We cross-checked for vulnerabilities with \textit{Slither}\footnote{https://github.com/crytic/slither} and \textit{SmartCheck}\footnote{https://tool.smartdec.net} and it only fails some `informational' warnings that are intentional design choices (\eg a costly loop).
-All measurements assume a block gas limit of $11\,741\,495$ and 1 gas $=$ 56 Gwei.\footnote{EthStats (July 2020): \url{https://ethstats.net/}} Table~\ref{tab:cm_functions} summarizes \cm's primary operations.
+All measurements assume a block gas limit of $11\,741\,495$ and 1 gas $=$ 56 Gwei.\footnote{EthStats (July 2020): \url{https://ethstats.net/}} Table~\ref{tab:cm_functions} summarizes \cm's primary operations.\
+
+\textblue{Add call market basics.}
 
@@
 }{%
-  \caption{\scriptsize{Gas costs for enqueuing 50 random integers into five priority queue variants.
+  \caption{\scriptsize{\textblue{RESIZE THIS} Gas costs for enqueuing 50 random integers into five priority queue variants.
 For the x-axis, a value of 9 indicates it is the 9th integer entered in the priority queue.
@@
 This is the cost of submitting the \texttt{closeMarket()} transaction to the inbox to be recorded, which is 103 bytes of calldata.
-Most importantly, \texttt{closeMarket()} always costs 6,569 even as the number of trades increase from 38 pairs to thousands or millions of pairs.
+Most importantly, recording \texttt{closeMarket()} in the inbox will alway cost around 6,569 even as the number of trades increase from 38 pairs to thousands or millions of pairs.
 Of course, as the number of trades increase, the work for the validators on L2 increases, as measured in ArbGas.
@@
 Arbitrum also reduces the costs for traders to submit an order: from 207,932 to 6,917 in L1 gas.
+In Appendix~\ref{app:rollup}, the full interaction is shown in Figure~\ref{fig:lissyl2}, which illustrate how traders interact with \cm on Arbitrum including bridges, inboxes, sequencers and validators.
 

### 2021-09-13 LaTeX-LNCS-2022/tables/eval2.tex
hooks for improvements

@@
 &  Non-custodial \newline
-Instant settlement \newline
+Instant trading \newline
 Moderate performance \newline
@@
 Front-running attacks \newline
-Limited trading strategies 
+Limited trading strategies \newline
+Hard to regulate
 \\ 
@@
 Non-custodial \newline
-Instant settlement \newline
 Low price slippage \newline
@@
 & Very low performance \newline
+Hard to regulate
 \\ 

### 2021-09-13 LaTeX-LNCS-2022/sections/paper.tex
new diagram

@@
 \ffigbox{%
-\includegraphics[width=6cm]{fig/2.png}%
+\includegraphics[width=6cm]{fig/2b.png}%
 }{%
-  \caption{\scriptsize{\textblue{RESIZE THIS} Gas costs for enqueuing 50 random integers into five priority queue variants.
+  \caption{\footnotesize{ Gas costs for enqueuing 50 random integers into five priority queue variants.
 For the x-axis, a value of 9 indicates it is the 9th integer entered in the priority queue.
@@
 
-\multicolumn{1}{c}{} & \headrowsidebyside{\scriptsize{\shortstack{Gas Costs \\\textit{(gwei)}}}} & \headrowsidebyside{\scriptsize{Refund \textit{(gwei)} }} & \headrowsidebyside{\scriptsize{Full Refund?}} \\ \hline
+\multicolumn{1}{c}{} & \headrowsidebyside{\scriptsize{\shortstack{Gas Used}}} & \headrowsidebyside{\scriptsize{Refund}} & \headrowsidebyside{\scriptsize{Full Refund?}} \\ \hline
 
@@
 }{%
- \caption{\scriptsize{The gas metrics associated with dequeuing 50 integers from five priority queue variants. Full refund amount is shown but the actual refund that is applied is capped.}
+ \caption{\footnotesize{The gas metrics associated with dequeuing 50 integers from five priority queue variants. Full refund amount is shown but the actual refund that is applied is capped.}
 \label{tab:PQUnitTests}}%
@@
 \centering
-\includegraphics[width=1\textwidth]{fig/MindMapDraft4.pdf}
+\includegraphics[width=1\textwidth]{fig/MindMapDraft5.pdf}
 \caption{\footnotesize{A design landscape for on-chain call markets.}  \label{fig:rmindmap}}

### 2021-09-13 LaTeX-LNCS-2022/sections/appendix.tex
changed the L2 diagram, added some texts and a ref to appendix
hooks for improvements
added the cm to appendix

@@
 \includegraphics[width=1\textwidth]{fig/lissyL2.pdf}
-\caption{\footnotesize{\textblue{Modify with inbox, sequencer as well}}  \label{fig:lissyl2}}
+\caption{\footnotesize{Overview of \cm on Arbitrum.}  \label{fig:lissyl2}}
 \end{figure}
@@
 An enhancement is to prove that trade execution is correct (\eg Loopring) but these proofs have blind spots (discussed above in Appendix~\ref{app:rollup}).
+
+\subsection{Call Markets}
+\label{app:cm}
+\begin{itemize}
+\item The call market first Matches Alice ask order to sell 1 at 10 with Eric's bid order to Buy 3 at 12.
+The trader happens at the price Alice asks for; 10, and 2 will be given to the miner as a price improvement.
+This trade fills Alice's order and leaves Eric with a remainder of 2 to buy at 12.
+\item Next, the call market matches Eric's remainder of 2 with the next highest priority ask order in the list which is Bob's order to sell 4 at 10.15.
+Trade occurs at 10.15 and 1.85 will be given to the miner as a price improvement.
+This trade fills the remainder of Eric's bid order and leaves Bob with a remainder of 2 to sell at 10.15.
+\item The market now matches the next highest bid order in the list, Alex's bid order to buy 1 at 12.15, with the remainder of Bob's ask order to sell 2 at 10.15.
+Trader occurs at 10.15 and 2 will be given to minder as a price improvement.
+This trader fills Alex bis order and leaves Bob with a remainder of 1 to sell at 10.15.
+\item Next, the market matches Adam's bid order to buy 3 at 13 with the remainder of Bob's ask order to sell 1 at 10.15.
+Trade occurs at 10.15 and 2.85 will be given to miner as a price improvement.
+This match fills the Bob order and leaves Adam with a remainder of 2 to buy at 13.
+\item The market then matches Sam's ask order to sell 4 at 10.18 with the remainder of Adam's bid order to buy 2 at 13.
+Trade occurs at 10.18 and 2.82 is given to miner as a price improvement.
+This trade fills Adam's order and leaves Sam with a remainder of 2 to sell at 10.18 unfilled.
+\end{itemize}
 

### 2021-09-13 LaTeX-LNCS-2022/sections/paper.tex
call market basics

@@
 \begin{itemize}
-\item What type of exchange has the best properties on balance? (A call market.)
+\item What type of exchange has the fairest price execution on balance? (A call market.)
 \item How many orders can be processed on-chain? (Upper-bounded by 152 per block.)
@@
 
-For our experiments and measurements, we implement an exchange from scratch.
-\cm is a call market that will open for a specified period of time during which it will accept a capped number of orders (\eg 100 orders---parameterized so that all orders can be processed), and these orders are added to a priority queue (discussed in Section~\ref{sec:pq} ).
+A call market opens for traders to submit bids and asks which are enqueued until the market closes.
+Trades are executed by matching the best priced bid to the best priced ask until the best bid is less than the best ask, then all remaining trades are discarded.
+See Appendix~\ref{app:cm} for a numeric example.
+If Alice's bid of \$100 is executed against Bob's ask of \$90, Alice pays \$100, Bob receives \$90 and the \$10 difference (called a price improvement) is given to miners for reasons in explained in the front-running evaluation (Section~\ref{sec:front}).
+
+For our experiments and measurements, we implement a call market from scratch.
+\cm will open for a specified period of time during which it will accept a capped number of orders (\eg 100 orders---parameterized so that all orders can be processed), and these orders are added to a priority queue (discussed in Section~\ref{sec:pq} ).
 Our vision is the market would be open for a very short period of time, close, and then reopen immediately (\eg every other block).
@@
 All measurements assume a block gas limit of $11\,741\,495$ and 1 gas $=$ 56 Gwei.\footnote{EthStats (July 2020): \url{https://ethstats.net/}} Table~\ref{tab:cm_functions} summarizes \cm's primary operations.\
-
-\textblue{Add call market basics.}
 

### 2021-09-13 LaTeX-LNCS-2022/sections/appendix.tex
edits on cm sample

--- 2021-09-11 LaTeX-LNCS-2022/sections/appendix.tex
@@
 
-\begin{figure}[t]
+\begin{sidewaysfigure}
 \centering
 \includegraphics[width=1\textwidth]{fig/lissyL2.pdf}
-\caption{\footnotesize{\textblue{Modify with inbox, sequencer as well}}  \label{fig:lissyl2}}
-\end{figure}
+\caption{\footnotesize{Overview of \cm on Arbitrum.}  \label{fig:lissyl2}}
+\end{sidewaysfigure}
 
@@
 An enhancement is to prove that trade execution is correct (\eg Loopring) but these proofs have blind spots (discussed above in Appendix~\ref{app:rollup}).
+
+\subsection{Call Markets}
+Assume traders submit their orders in Table~\ref{tab:cmsample} to a call market once it is open. In the following, we explain how these orders are executed.
+\input{tables/cm.tex}
+
+\label{app:cm}
+\begin{itemize}
+\item The call market first matches Alice ask order to sell 1 at 10 with Avni's bid order to Buy 3 at 12.
+The trader happens at the price Alice asks for; 10, and 2 will be given to the miner as a price improvement.
+This trade fills Alice's order and leaves Avni with a remainder of 2 to buy at 12.
+\item Next, the call market matches Avni's remainder of 2 with the next highest priority ask order in the list which is Navjot's order to sell 4 at 10.15.
+Trade occurs at 10.15 and 1.85 will be given to the miner as a price improvement.
+This trade fills the remainder of Avni's bid order and leaves Navjot with a remainder of 2 to sell at 10.15.
+\item The market now matches the next highest bid order in the list, Bob's bid order to buy 1 at 12.15, with the remainder of Navjot ask order to sell 2 at 10.15.
+Trader occurs at 10.15 and 2 will be given to minder as a price improvement.
+This trader fills Bob bid order and leaves Navjot with a remainder of 1 to sell at 10.15.
+\item Next, the market matches Kritee's bid order to buy 3 at 13 with the remainder of Navjot's ask order to sell 1 at 10.15.
+Trade occurs at 10.15 and 2.85 will be given to miner as a price improvement.
+This match fills the Navjot's order and leaves Kritee with a remainder of 2 to buy at 13.
+\item The market then matches Mehdi's ask order to sell 4 at 10.18 with the remainder of Kritee's bid order to buy 2 at 13.
+Trade occurs at 10.18 and 2.82 is given to miner as a price improvement.
+This trade fills Kritee's order and leaves Mehdi with a remainder of 2 to sell at 10.18 unfilled.
+\end{itemize}
 

### 2021-09-13 LaTeX-LNCS-2022/sections/abstract.tex
Finalized :boom:

@@
 AMMs implement a lightweight dealer-based trading system, but they are unlike anything on Wall Street, require fees intrinsically, and are susceptible to front-running attacks.
-This leaves the following research questions we address in this paper: (i) are conventional (\ie orderbooks), secure (\ie resistant to front-running and price manipulation) and fully decentralized exchanges feasible on a public blockchain like Ethereum, (ii) what is the performance profile, and (iii) how much do Layer 2 techniques (\eg Arbitrum) increase performance?
+This leaves the following research questions we address in this paper: (1) are conventional (\ie order books), secure (\ie resistant to front-running and price manipulation) and fully decentralized exchanges feasible on a public blockchain like Ethereum, (2) what is the performance profile, and (3) how much do Layer 2 techniques (\eg Arbitrum) increase performance?
 To answer these questions, we implement, benchmark, and experiment with an Ethereum-based call market exchange called \cm.

### 2021-09-13 LaTeX-LNCS-2022/sections/appendix.tex
edits on L2 diagram and table
Finalized :boom:

@@
 At the time of this writing, Ethereum transaction receipts only account for the \texttt{gasUsed}, which is the total amount of gas units spent during a transaction, and users are not able to obtain the value of the EVM's refund counter from inside the EVM~\cite{signer2018gas}.
-So in order to account for refunds in  Tables~\ref{tab:PQUnitTests}, we calculate them manually.
+So in order to account for refunds in Table~\ref{tab:PQUnitTests}, we calculate them manually.
 First, we determine exactly how many storage slots are being cleared or how many smart contracts are being destroyed, then we multiply these numbers by 24,000 or 15,000 respectively.
@@
 
-\begin{sidewaysfigure}
+\begin{figure}[htb]
+  \centering
+  \begin{turn}{90}
+  \begin{minipage}{8in}
   \centering
 \includegraphics[width=1\textwidth]{fig/lissyL2.pdf}
-\caption{\footnotesize{Overview of \cm on Arbitrum.}  \label{fig:lissyl2}}
-\end{sidewaysfigure}
+  \caption{\footnotesize{Overview of \cm on Arbitrum.}
+\label{fig:lissyl2}}
+  \end{minipage}
+  \end{turn}
+\end{figure}
 
@@
 \paragraph{On-chain Dealers.} An advantage of on-chain trading is that other smart contracts, not just human users, can initiate trades, enabling broader decentralized finance (DeFi) applications.
-This has fuelled a resurgence in on-chain exchange but through a quote-driven design rather than an order-driven one.
+This has fueled a resurgence in on-chain exchange but through a quote-driven design rather than an order-driven one.
 Automated market makers  (\eg Uniswap v3) have all the trust advantages of an on-chain order book, plus they are relatively more efficient.
@@
 \subsection{Call Markets}
-Assume traders submit their orders in Table~\ref{tab:cmsample} to a call market once it is open. In the following, we explain how these orders are executed.
+Assume traders submit their orders in Table~\ref{tab:cmsample} to a call market when it is open. In the following, we explain how these orders are executed:
 \input{tables/cm.tex}
@@
 \begin{itemize}
-\item The call market first matches Alice ask order to sell 1 at 10 with Avni's bid order to Buy 3 at 12.
-The trader happens at the price Alice asks for; 10, and 2 will be given to the miner as a price improvement.
+\item The call market first matches Alice's ask order to sell 1 at 10 with Avni's bid order to buy 3 at 12.
+Trade occurs at the price Alice asks for; 10, and 2 will be given to the miner as a price improvement.
 This trade fills Alice's order and leaves Avni with a remainder of 2 to buy at 12.
@@
 This trade fills the remainder of Avni's bid order and leaves Navjot with a remainder of 2 to sell at 10.15.
-\item The market now matches the next highest bid order in the list, Bob's bid order to buy 1 at 12.15, with the remainder of Navjot ask order to sell 2 at 10.15.
-Trader occurs at 10.15 and 2 will be given to minder as a price improvement.
-This trader fills Bob bid order and leaves Navjot with a remainder of 1 to sell at 10.15.
+\item The market now matches the next highest bid order in the list, Bob's bid order to buy 1 at 12.15, with the remainder of Navjot's ask order to sell 2 at 10.15.
+Trader occurs at 10.15 and 2 will be given to miner as a price improvement.
+This trade fills Bob's bid order and leaves Navjot with a remainder of 1 to sell at 10.15.
 \item Next, the market matches Kritee's bid order to buy 3 at 13 with the remainder of Navjot's ask order to sell 1 at 10.15.
 Trade occurs at 10.15 and 2.85 will be given to miner as a price improvement.
-This match fills the Navjot's order and leaves Kritee with a remainder of 2 to buy at 13.
+This trade fills Navjot's order and leaves Kritee with a remainder of 2 to buy at 13.
 \item The market then matches Mehdi's ask order to sell 4 at 10.18 with the remainder of Kritee's bid order to buy 2 at 13.
@@
 
-in \cm, both the tokens and ETH that a trader wants to potentially use in the order book are pre-loaded into the contract.
+in \cm, both the tokens and ETH that a trader wants to potentially use in the order book are preloaded into the contract.
 Consider Alice, who holds a token and decides she wants to trade it for ETH.
@@
 Call markets are heralded for fair price discovery.
-This is why many exchanges use a call market at the end of the day to determine the closing price of an asset, which is an important price both optically (it is well-published) and operationally (many derivatives settle based on the closing price).
+This is why many exchanges use a call market at the end of the day to determine the closing price of an asset, which is an important price both optically (it is well published) and operationally (many derivatives settle based on the closing price).
 We purposely do not compute a `market clearing price' with \cm because miners can easily manipulate the price (\ie include a single wash trade at the price they want fixed), although they forgo profit for doing so.

### 2021-09-13 LaTeX-LNCS-2022/sections/paper.tex
Finalized :boom:

@@
 
-A clever quote-driven alternative, called an automatic market maker (AMM), was developed that only requires data structures and traversals with low gas-complexity.
-This approach has undesirable price dynamics (\eg market impact of a trade, slippage between the best bid/ask and actual average execution price, \etc) which explains why there is no Wall Street equivalent, however it is efficient on Ethereum and works `good enough' to attract trading.
+A clever quote-driven alternative, called an automatic market maker (AMM), was developed that only requires data structures and traversals with low gas complexity.
+This approach has undesirable price dynamics (\eg market impact of a trade, slippage between the best bid/ask and actual average execution price, \etc) which explains why there is no Wall Street equivalent, however, it is efficient on Ethereum and works `good enough' to attract trading.
 First generation AMMs provide makers (called liquidity providers) with no ability to act on price information---they are uninformed traders that can only lose (called impermanent loss) on trades but make money on fees.
@@
 \item How many orders can be processed on-chain? (Upper-bounded by 152 per block.)
-\item How much efficiency can be squeezed from diligently choosing the best data structures? (Somewhat limited: turn 38 trades into 152.)
+\item How much efficiency can be squeezed from diligently choosing the best data structures? (Somewhat limited; turn 38 trades into 152.)
 \item To what extent can we mitigate front-running attacks? (Almost entirely.)
@@
 
-We assume the reader is familiar with the following concepts: blockchain technology; smart contracts and decentralized applications (DApps) on Ethereum; how Ethereum transactions are structured, broadcasted, and finalized; the gas model including the gas limit (approximately 11M gwei at the time of our experiments) per block.
+We assume the reader is familiar with the following concepts: blockchain technology; smart contracts and decentralized applications (DApps) on Ethereum; how Ethereum transactions are structured, broadcast, and finalized; the gas model including the gas limit (approximately 11M gwei at the time of our experiments) per block.
 A \textbf{gas refund} is a more esoteric subject (not covered thoroughly in any academic work to our knowledge) that we use heavily in our optimizations.
@@
 Briefly, fully decentralized, on-chain exchanges require the lowest trust, provide instant settlement, and have transparent trading rules that will always execute correctly.
-Front-running attacks (see Section~\ref{sec:front} for a very thorough discussion) are a weakness inherent in blockchains that require specific mitigation.
+Front-running attacks (see Section~\ref{sec:front} for a very thorough discussion) are weaknesses inherent in blockchains that require specific mitigation.
 
@@
 For our experiments and measurements, we implement a call market from scratch.
-\cm will open for a specified period of time during which it will accept a capped number of orders (\eg 100 orders---parameterized so that all orders can be processed), and these orders are added to a priority queue (discussed in Section~\ref{sec:pq} ).
+\cm will open for a specified period of time during which it will accept a capped number of orders (\eg 100 orders---parameterized so that all orders can be processed), and these orders are added to a priority queue (discussed in Section~\ref{sec:pq}).
 Our vision is the market would be open for a very short period of time, close, and then reopen immediately (\eg every other block).
@@
 
-\item \textbf{Heap with Dynamic Array.} A heap is a binary tree where data is stored in nodes in a specific order where the root always represents the highest priority item (\ie highest bid price / lowest ask price).
+\item \textbf{Heap with Dynamic Array.} A heap is a binary tree where data is stored in nodes in a specific order where the root always represents the highest priority item (\ie highest bid price/lowest ask price).
 Our heap stores its data in a Solidity-provided dynamically sized array.
-The theoretic time complexity is logarithmic enqueue and logarithmic dequeue.
+The theoretical time complexity is logarithmic enqueue and logarithmic dequeue.
 
@@
 Solidity is described as object-oriented but the Solidity equivalent of an object is an entire smart contract.
-Therefore, an object-oriented linked list must either (i) create each node in the list as a struct---but this is not possible as Solidity does not support recursive structs---or (ii) make every node in the list its own contract.
+Therefore, an object-oriented linked list must either (1) create each node in the list as a struct---but this is not possible as Solidity does not support recursive structs---or (2) make every node in the list its own contract.
 The latter option seems wasteful and unusual, but it surprisingly ends up being the most gas efficient data structure to dequeue.
-The theoretic time complexity is linear enqueue and constant dequeue.
+The theoretical time complexity is linear enqueue and constant dequeue.
 
@@
 
-We observe that (i) the linked list variants are materially cheaper than the heap variants at dequeuing; (ii) dequeuing in a call market must be done as a batch, whereas enqueuing is paid for one at a time by the trader submitting the order; and (iii) Ethereum will not permit more than hundreds of orders so asymptotic behaviour is not significant.
+We observe that (1) the linked list variants are materially cheaper than the heap variants at dequeuing; (2) dequeuing in a call market must be done as a batch, whereas enqueuing is paid for one at a time by the trader submitting the order; and (3) Ethereum will not permit more than hundreds of orders so asymptotic behaviour is not significant.
 For these reasons, we suggest using one of the linked list variants.
@@
 In Section~\ref{sec:rollups}, we implement \cm on Layer 2.
-There the PQ variant does not change the layer 1 gas costs and the the number of orders can be substantially increased.
-In this new context, we reconsider asymptotics and choose a heap (with dynamic array) to lower costs L2 gas costs across both enqueuing and dequeuing.
+There, the PQ variant does not change the layer 1 gas costs (as calldata size is the same) and the number of orders can be substantially increased.
+thus, we reconsider asymptotic and choose a heap (with dynamic array) to lower L2 gas costs across both enqueuing and dequeuing.
 
@@
 Further, the cap on the maximum refund means that refunds are not fully received for large cleanup operations (however removing the cap impacts the miners' incentives to include the transaction).
-In Appendix~\ref{app:clean}, we present a second case study of the cost-benefits of clearing a mapping when it is no longer needed (including our idea to store the mapping in its own contract so it can \texttt{SELFDESTRUCT} with a single function call).
+In Appendix~\ref{app:clean}, we present a second case study of the cost-benefit of clearing a mapping when it is no longer needed (including our idea to store the mapping in its own contract so it can \texttt{SELFDESTRUCT} with a single function call).
 The unfortunate takeaway is, again, that it is cheapest to leave the mapping in place.
@@
 It is visible and can be interacted with here: \href{https://rinkeby-explorer.arbitrum.io/address/0x0aa5449a9f7fa34a81ce1dc720563938a27e8b03}{[Arbitrum Explorer]}.
-To call functions on \cm, traders can (i) send transactions directly to the \href{https://rinkeby.etherscan.io/address/0x578BAde599406A8fE3d24Fd7f7211c0911F5B29e}{Inbox contract}, or (ii) use a relay server (called a \textit{Sequencer}) provided by the Arbitrum.
-The sequencer will group, order, and send all pending transactions together as a single Rinkeby transaction to the inbox (and pays the gas).
+To call functions on \cm, traders can (1) send transactions directly to the \href{https://rinkeby.etherscan.io/address/0x578BAde599406A8fE3d24Fd7f7211c0911F5B29e}{Inbox contract}, or (2) use a relay server (called a \textit{Sequencer}) provided by the Arbitrum.
+The sequencer will group, order, and send all pending transactions together as a single Rinkeby transaction to the Inbox (and pays the gas).
 
@@
 Table~\ref{tab:arbitrum_performance} shows that 38 pairs cost only 6,569 in L1 gas (a 99.88\% savings).
-This is the cost of submitting the \texttt{closeMarket()} transaction to the inbox to be recorded, which is 103 bytes of calldata.
-Most importantly, recording \texttt{closeMarket()} in the inbox will alway cost around 6,569 even as the number of trades increase from 38 pairs to thousands or millions of pairs.
+This is the cost of submitting the \texttt{closeMarket()} transaction to the Inbox to be recorded, which is 103 bytes of calldata.
+Most importantly, recording \texttt{closeMarket()} in the Inbox will always cost around 6,569 even as the number of trades increases from 38 pairs to thousands or millions of pairs.
 Of course, as the number of trades increase, the work for the validators on L2 increases, as measured in ArbGas.
-The price of ArbGas in Gwei is not well-established but is anticipated to be relatively cheap.
+The price of ArbGas in Gwei is not well established but is anticipated to be relatively cheap.
 Arbitrum also reduces the costs for traders to submit an order: from 207,932 to 6,917 in L1 gas.
-In Appendix~\ref{app:rollup}, the full interaction is shown in Figure~\ref{fig:lissyl2}, which illustrate how traders interact with \cm on Arbitrum including bridges, inboxes, sequencers and validators.
+In Appendix~\ref{app:rollup}, the full interaction is shown in Figure~\ref{fig:lissyl2}, which illustrates how traders interact with \cm on Arbitrum including bridges, inboxes, sequencers and validators.
 
@@
 Under our definition, a call market only has makers: the only way to have a trade executed is to submit an order.
-The front-running attacks in Table~\ref{tab:front} are sub-categorized, using a recent SoK~\cite{eskandari2019sok}, as being \emph{Insertion}, \emph{Displacement}, and \emph{Suppression}.
+The front-running attacks in Table~\ref{tab:front} are subcategorized, using a recent SoK~\cite{eskandari2019sok}, as being \emph{Insertion}, \emph{Displacement}, and \emph{Suppression}.
 To explain the difference, we will illustrate the first three attacks in the table.
@@
 There are two main takeaways from Table~\ref{tab:front}.
-Call markets provide strong resilience to front-running only bested slightly by dark markets like TEX~\cite{khalil2019tex}, however they do it through design---no cryptography and no two-round protocols.
+Call markets provide strong resilience to front-running only bested slightly by dark markets like TEX~\cite{khalil2019tex}, however, they do it through design---no cryptography and no two-round protocols.
 A second observation is that dark call markets, like Galal \etal~\cite{galalpublicly}, are no more resilient to front-running than a lit market (however confidentiality could provide resilience to predatory trading algorithms that react quickly to trades without acutally front-running).
@@
 To use it in the real world, design decisions need to be made about how it will be used.
-Figure~\ref{fig:rmindmap} provides a design landscape for \cm deployment, with possible extensions and customizations.
+Figure~\ref{fig:rmindmap} provides a design landscape for \cm deployment, with possible extensions and customization.
 
@@
 These fees are accumulated by the DApp to use as a bounty.
-When the time window for the open market elapses, the sender of the first \texttt{closeMarket()} function to be confirmed recieves the bounty.
+When the time window for the open market elapses, the sender of the first \texttt{closeMarket()} function to be confirmed receives the bounty.
 This is still not perfect: \texttt{closeMarket()} cost does not follow a tight linear increase with the number of orders, and gas prices vary over time which could render the bounty insufficient for offsetting the \texttt{closeMarket()} cost.
@@
 
-The final option is to rely on an interested third party (such as the token issuer for a given market) to always close the market, or  occasionally bailout the market when one of the above mechanisms fail.
+The final option is to rely on an interested third party (such as the token issuer for a given market) to always close the market, or  occasionally bailout the market when one of the above mechanisms fails.
 An external service like Ethereum Alarm Clock\footnote{\url{https://ethereum-alarm-clock-service.readthedocs.io/}}  (which also creates a regulatory hook) can be used to schedule regular \texttt{closeMarket()} calls.
@@
 
-In \cm, both the tokens and ETH that a trader wants to potentially use in the order book are pre-loaded into the contract. We discuss some alternative designs in Appendix~\ref{app:collateral}.
+In \cm, both the tokens and ETH that a trader wants to potentially use in the order book are preloaded into the contract. We discuss some alternative designs in Appendix~\ref{app:collateral}.
 

### 2021-09-13 LaTeX-LNCS-2022/tables/eval2.tex
Finalized :boom:

@@
 Partially On-chain Exchange
-& Order-driven exchange acts as a semi-trusted (\eg EtherDelta, 0x, IDEX, Loopring)
+& Order-driven exchange acts as a semi-trusted party (\eg EtherDelta, 0x, IDEX, Loopring)
 &  High performance \newline

### 2021-10-06 arxiv-draft/sections/appendix.tex
arxiv draft

--- 2021-09-13 LaTeX-LNCS-2022/sections/appendix.tex
@@
 Specifically, if a dispute over a transaction arrises, the L1 cost of resolving the dispute is a small fraction of the cost of executing the transaction itself (whereas in Optimism, the dispute resolution cost is essentially the same as executing the transaction).
+
+Figure~\ref{fig:lissyl2} shows how traders interact with \cm on Arbitrum.
+First, a trader sends a \texttt{depositETH} transaction on Ethereum to the Inbox contract to deposit \textit{X} amount of ETH to the Arbitrum chain.
+Once the transaction is confirmed, \textit{X} amount of ETH will be credited to the trader's address on the Arbitrum chain.
+Trader can now interact with \cm and execute its functions by sending the instruction and data required for those executions to either (1) the Arbitrum regular Inbox on Ethereum, or (2) the sequencer.
+In our example, trader uses the regular Inbox to execute \texttt{depositEther()} and the sequencer to execute \texttt{submitBid()} from \cm that lives entirely on Arbitrum chain.
+Accordingly, trader deposits ETH to \cm smart contract by sending the instruction and data for executing the \texttt{depositEther()} to the Arbitrum Inbox contract that lives on Ethereum.
+A validator fetches this transaction from the Inbox, executes it, and asserts the result to ArbOS.
+Next, trader sends the instruction and data for execution of \texttt{submitBid()} to the sequencer.
+The sequencer then inserts this message into the Inbox that it owns.
+This Inbox contract has the same interface as the regular Inbox contract, however, it is \textit{owned} by the sequencer.
+A validator sees the transaction in the sequencer Inbox of the bridge, executes it,  and asserts the result to ArbOS.
+Periodically, the entire state of ArbOS is committed back to Ethereum.
 

### 2021-10-06 arxiv-draft/sections/paper.tex
arxiv draft

--- 2021-09-13 LaTeX-LNCS-2022/sections/paper.tex
@@
 Once deployed, the bytecode of \cm is 10,812 bytes plus the constructor code (6,400 bytes) which is not stored.
-The Solidity source code for \cm and Truffle test files are available in a GitHub repository.\footnote{Github: Link removed for anonymity.} We have also deployed \cm on Ethereum's testnet Rinkeby with flattened (single file) source code of just the \cm base class and priority queue implementations.
+The Solidity source code for \cm and Truffle test files are available in a GitHub repository.\footnote{https://github.com/MadibaGroup/2020-Orderbook} We have also deployed \cm on Ethereum's testnet Rinkeby with flattened (single file) source code of just the \cm base class and priority queue implementations.
 It is visible and can be interacted with here: \href{https://rinkeby.etherscan.io/address/0x0d91de29c531d074853a5cef7cf9dfeb9c6ec4e0}{[etherscan.io]}.
@@
 
+\subsubsection*{Acknowledgements.}  The authors thank the AMF (Autorité des Marchés Financiers) for supporting this research project.
+J.
+Clark also acknowledges partial funding from the National Sciences and Engineering Research Council (NSERC)/Raymond Chabot Grant Thornton/Catallaxy Industrial Research Chair in Blockchain Technologies, as well as NSERC through a Discovery Grant.
+M.
+Moosavi acknowledges support from Fonds de Recherche du Québec - Nature et Technologies (FRQNT).
+
 % It may seem paradoxical or unethical to build for regulators exactly what they worry about.

### 2021-10-06 arxiv-draft/tables/frontrunning.tex
arxiv draft

--- 2021-08-26 LaTeX-LNCS-2022/tables/frontrunning2.tex
@@
 
-\begin{table*}[t]
+%\begin{adjustbox}{center} %horizontal display
+\begin{landscape} %vertical display
+\begin{table}[t]
+\setlength{\tabcolsep}{3\tabcolsep}
+\centering
 
-\centering
-\tiny
-%\resizebox{1.7\columnwidth}{!}{
+\footnotesize
 
@@
 \multicolumn{1}{c}{} &
-\headrowfrontTwo{\shortstack{Centralized Continuous\\ Market (Coinbase)}} &
-\headrowfrontTwo{\shortstack{Partially Off-chain Continuous\\ Market (EtherDelta)}} & 
-\headrowfrontTwo{\shortstack{Partially Off-chain Continuous \\Market w/ Roll-up (Loopring)}} & 
-\headrowfrontTwo{\shortstack{On-chain Continuous \\Market (OasisDex)}}  &
-\headrowfrontTwo{\shortstack{On-chain Dark \\Continuous Market (TEX)}} &
-\headrowfrontTwo{\shortstack{On-chain Automated \\Market Maker (Uniswap)}}  & 
-\headrowfrontTwo{\shortstack{On-chain Call Market \\w/ Price Improvement}} &
-\headrowfrontTwo{\shortstack{On-chain Call Market (\cm)}}  & 
-\headrowfrontTwo{\shortstack{On-chain Call Market  \\w/ Roll-up (\cm variant)}}  &
-\headrowfrontTwo{\shortstack{On-chain Dark \\Call Market (Galal \etal)}}
+\headrowfront{\scriptsize{Centralized Continuous Market (Coinbase)}} &
+\headrowfront{\scriptsize{Partially Off-chain Continuous Market (EtherDelta)} } & 
+\headrowfront{\scriptsize{Partially Off-chain Continuous Market w/ Roll-up (Loopring)} } & 
+\headrowfront{\scriptsize{On-chain Continuous Market (OasisDex)} } &
+\headrowfront{\scriptsize{On-chain Dark Continuous Market (TEX)} }&
+\headrowfront{\scriptsize{On-chain Automated Market Maker (Uniswap)} } & 
+\headrowfront{\scriptsize{On-chain Call Market w/ Price Improvement}} &
+\headrowfront{\scriptsize{On-chain Call Market (\cm)}}  & 
+\headrowfront{\scriptsize{On-chain Call Market w/ Roll-up (\cm variant)}}  &
+\headrowfront{\scriptsize{On-chain Dark Call Market (Galal \etal)}} 
 \\
@@
 
-\caption{\footnotesize{An evaluation of front-running attacks (rows) for different types of order books (columns).
+%\end{adjustbox}
+
+\caption{An evaluation of front-running attacks (rows) for different types of order books (columns).
 Front-running attacks are in three categories: \underline{Ins}ertion, \underline{disp}lacement, and \underline{supp}ression.
-A full dot (\tinyfull) means the front-running attack is mitigated or not applicable to the order book type, a partial mitigation (\tinyprt) is awarded when the front-running attack is possible but expensive, and we give no award (\tinyempt) if the attack is feasible}.
+A full dot (\full) means the front-running attack is mitigated or not applicable to the order book type, a partial mitigation (\prt) is awarded when the front-running attack is possible but expensive, and we give no award (\empt) if the attack is feasible.
 \label{tab:front}}
-\end{table*}
+\end{table}
+
+\end{landscape}

### 2021-10-06 arxiv-draft/tables/frontrunning2.tex
arxiv draft

--- 2021-08-26 LaTeX-LNCS-2022/tables/frontrunning2.tex
@@
 \centering
-\tiny
+%\tiny %commented for the arxiv version
 %\resizebox{1.7\columnwidth}{!}{
@@
 
-\caption{\footnotesize{An evaluation of front-running attacks (rows) for different types of order books (columns).
+\caption{An evaluation of front-running attacks (rows) for different types of order books (columns).
 Front-running attacks are in three categories: \underline{Ins}ertion, \underline{disp}lacement, and \underline{supp}ression.
-A full dot (\tinyfull) means the front-running attack is mitigated or not applicable to the order book type, a partial mitigation (\tinyprt) is awarded when the front-running attack is possible but expensive, and we give no award (\tinyempt) if the attack is feasible}.
+A full dot (\full) means the front-running attack is mitigated or not applicable to the order book type, a partial mitigation (\prt) is awarded when the front-running attack is possible but expensive, and we give no award (\empt) if the attack is feasible.
 \label{tab:front}}

### 2022-06-01 LaTeX-LNCS-2022/main.tex
some notes/comments added
cutting the text down to 23 pages
reorg / new sections added (down to 21 pages)
top matter [19 pages total]
morre changes
hooks for improvements
wtsc changes

@@
 
-\title{\Large \bf Trading On-chain: How Feasible Is Regulators' Worst-Case Scenario?}
+\title{\Large \bf Lissy: Experimenting with on-chain order books}
 
-\author{Mahsa Moosavi\inst{1} \and Jeremy Clark\inst{1}}
-\institute{Concordia University, Montreal, Canada}
+\author{Mahsa Moosavi \and Jeremy Clark}
+\institute{Concordia University, Montreal, Canada \\ \email{seye\_moo@encs.concordia.ca}}
 
@@
 
+% = = = = = Acknowledgements = = = = = %
+
+\subsubsection*{Acknowledgements.}  The authors thank the AMF (Autorité des Marchés Financiers) for supporting this research project.
+J.
+Clark also acknowledges partial funding from the National Sciences and Engineering Research Council (NSERC)/Raymond Chabot Grant Thornton/Catallaxy Industrial Research Chair in Blockchain Technologies, as well as NSERC through a Discovery Grant.
+M.
+Moosavi acknowledges support from Fonds de Recherche du Québec - Nature et Technologies (FRQNT).
+
 % = = = = = Bibliography = = = = = %
 
-\clearpage
 \bibliography{bib/DEX}
@@
 
-\clearpage
 \appendix

### 2022-06-02 LaTeX-LNCS-2022/sections/paper.tex
preparing for wtsc

@@
 Briefly, certain EVM operations (\texttt{SELFDESTRUCT} and \texttt{SSTORE 0}) cost negative gas, with the follow caveats: the refund is capped at 50\% of the total gas cost of the transaction, and (2) the block gas limit applies to the pre-refunded amount (\ie a transaction receiving a full refund can cost up to 5.5M gas with an 11M limit).
-We provide full details of all of these topics in Appendix~\ref{app:ethback}.
+We provide full details of all of these topics in the full version~\cite{https://doi.org/10.48550/arxiv.2101.06291}.
 
@@
 Table~\ref{tab:eval2} illustrates various trade execution systems and summarizes their advantages and disadvantages.
-Appendix~\ref{app:markets} provides a full justification for the table.
+A full justification for the table can be found in~\cite{https://doi.org/10.48550/arxiv.2101.06291}.
 Briefly, fully decentralized, on-chain exchanges require the lowest trust, provide instant settlement, and have transparent trading rules that will always execute correctly.
@@
 Trades are executed by matching the best priced bid to the best priced ask until the best bid is less than the best ask, then all remaining trades are discarded.
-See Appendix~\ref{app:cm} for a numeric example.
+See~\cite{https://doi.org/10.48550/arxiv.2101.06291} for a numeric example.
 If Alice's bid of \$100 is executed against Bob's ask of \$90, Alice pays \$100, Bob receives \$90 and the \$10 difference (called a price improvement) is given to miners for reasons in explained in the front-running evaluation (Section~\ref{sec:front}).
@@
 
-\item \textbf{Heap with Mapping.} In this variant, we store a key for the order in the heap instead of the entire order itself.
+\item \textbf{Heap with Mapping.} In this variant, we store a key for the order in the heap instead of the entire order.
 Once a key is dequeued, the order struct is drawn from a Solidity mapping (which stores key-value pairs very efficiently).
@@
 Further, the cap on the maximum refund means that refunds are not fully received for large cleanup operations (however removing the cap impacts the miners' incentives to include the transaction).
-In Appendix~\ref{app:clean}, we present a second case study of the cost-benefit of clearing a mapping when it is no longer needed (including our idea to store the mapping in its own contract so it can \texttt{SELFDESTRUCT} with a single function call).
+We present a second case study of the cost-benefit of clearing a mapping when it is no longer needed (including our idea to store the mapping in its own contract so it can \texttt{SELFDESTRUCT} with a single function call) in~\cite{https://doi.org/10.48550/arxiv.2101.06291}.
 The unfortunate takeaway is, again, that it is cheapest to leave the mapping in place.
@@
 Among these proposals, \textit{roll-ups} prioritize reducing gas costs (as opposed to other valid concerns like latency and throughput, which are secondary for \cm).
-We review two variants, \textit{optimistic roll-ups} and \textit{zk roll-ups}, in Appendix~\ref{app:rollup}.
+We review two variants, \textit{optimistic roll-ups} and \textit{zk roll-ups}, in~\cite{https://doi.org/10.48550/arxiv.2101.06291}.
 Briefly, in a roll-up, every transaction is stored (but not executed) on Ethereum, then executed off-chain, and the independently verifiable result is pushed back to Ethereum, with some evidence of being executed correctly.
-In the Appendix, we also compare \cm on Arbitrum to Loopring 3.0.
+We also compare \cm on Arbitrum to Loopring 3.0 in~\cite{https://doi.org/10.48550/arxiv.2101.06291}.
 
@@
 Arbitrum also reduces the costs for traders to submit an order: from 207,932 to 6,917 in L1 gas.
-In Appendix~\ref{app:rollup}, the full interaction is shown in Figure~\ref{fig:lissyl2}, which illustrates how traders interact with \cm on Arbitrum including bridges, inboxes, sequencers and validators.
+We illustrate the interaction between the traders and \cm on Arbitrum including bridges, inboxes, sequencers and validators in~\cite{https://doi.org/10.48550/arxiv.2101.06291}.
 
@@
 
-In \cm, both the tokens and ETH that a trader wants to potentially use in the order book are preloaded into the contract. We discuss some alternative designs in Appendix~\ref{app:collateral}.
+In \cm, both the tokens and ETH that a trader wants to potentially use in the order book are preloaded into the contract.
+We discuss some alternative designs in~\cite{https://doi.org/10.48550/arxiv.2101.06291}.
 

### 2022-06-02 LaTeX-LNCS-2022/sections/paper.tex
small changes

@@
 
-In \cm, both the tokens and ETH that a trader wants to potentially use in the order book are preloaded into the contract.
-We discuss some alternative designs in~\cite{https://doi.org/10.48550/arxiv.2101.06291}.
+In \cm, both the tokens and ETH that a trader wants to potentially use are preloaded into the contract. We discuss alternative designs in~\cite{https://doi.org/10.48550/arxiv.2101.06291}.
 
@@
 By contrast to all of these, with an on-chain order book, you just deploy the code alongside your token and trading is immediately supported.
-This should concern regulators.
 Even if it is too slow today, there is little reason for developers not to offer it as a fallback solution that accompanies every token.

### 2022-06-03 LaTeX-LNCS-2022/sections/paper.tex
removed anon GitHub link -- finalized

@@
 % !TEX root = ../main.tex
-
-% EDITS TO BE MADE:
-% 1- Different market participants would have different preference about various markets. Which one is best for which? Jeremy in proposal: could be a chart
-% 2- Add a subsection on latency
-% 3- For enqueue and dequeue performance tests, justify why you picked 50 integers
 
@@
 Order-driven markets can be \emph{continuous}, with buyers/sellers at any time adding orders to the order book (\emph{makers}) or executing against an existing order (\emph{takers}); or they can be \emph{called}, where all traders submit orders within a window of time and orders are matched in a batch (like an auction).
-
+fa
 Conventional financial markets (\eg NYSE, NASDAQ) use both continuous time trading during open hours, and a call market before and during open hours to establish an opening price and a closing price.
